### 2023-03-17 README.Rmd
Change rulemap to .svg and add to README

---
title: Turkey Hemorrhagic Enteritis Virus transcription profiling
author: Abraham Quaye
date: 2023-03-16
output: html_document
---

# THEV transcriptome studies

## Background

**Hemorrhagic enteritis (HE)** is a disease affecting 6-12-week-old turkeys characterized by bloody diarrhea, **immunosuppression (IS)**, and up to 60% mortality. This disease is caused by **_Turkey Hemorrhagic Enteritis Virus (THEV)_** of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated. The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties. **_Our objective is to understand the genetic basis by which VAS brings about IS_**. However, the **transcriptome of THEV** has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical as the viral splicing and gene expression patterns are unknown. To identify such viral factors, a well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.

## Methods

After infecting a turkey B-cell line (RP-19) with THEV, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection. Total RNA was subsequently extracted using Thermofishers’s RNAqueous-4PCR Total RNA Isolation Kit, and poly-A-tailed mRNA sequencing done at LC Sciences, Houston TX. The raw sequencing reads were trimmed with the FastQC program, mapped to the THEV genome using Hisat2 and transcripts assembled with StringTie. The `--merge` function of StringTie was used to consolidate transcripts from all timepoints, generating the final THEV transcriptome.

## Data analysis
This project is run from the `Snakefile`. Full analysis pipeline shown below in diagram:

![project_map](./project_map.svg){width=720px height=620px}

## Results

Over 18 million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped. All predicted genes in the genome were represented. Interestingly, all were spliced with either with 5’- or 3’-multi exon UTRs hitherto unknown. Thirteen novel exons were identified which require additional verification. The splicing patterns strongly suggest that there are 3 main promoters (E1a-, E3, and major late promoters) driving expression of most of the genes with 2 possible minor promoters driving single genes (ORF7 and ORF8).

We have performed the first RNA-sequencing experiment aimed at characterizing THEV’s transcriptome, which has yielded the only experimentally determined and the most detailed insight of THEV gene expression. In keeping with all Adenoviruses, our data shows that almost all THEV genes are spliced, and under the control of a promoter, several genes are expressed as one transcription unit. This insight of THEV’s transcriptome may allow the engineering of VAS to provide immune protection with less or no associated IS.

### Navigate the project:

```{r include = FALSE}

script_dir <- for(item in list.files("scripts")){
    print(item, quote = FALSE)}

rawfiles_dir <- for(item in list.files("raw_files")){
    print(item, quote = FALSE)}

results_dir <- for(item in list.files("results")){
    print(item, quote = FALSE)
}
```
* **`ROOT (thev_transcriptome)`**
    * **Directories:**
        * *`scripts`*
        * *`raw_files`*
        * *`results`*
        * *`trimmedReads`*
    * **Files**
        * *`Snakefile`*
        * *`driver_script`* - *`deprecated`*
        * *`README.Rmd`*
        * *`project_map.pdf`* 
        * *`project_jobmap.pdf`*
        * *`thev_transcriptome.Rproj`* - *not on Git*
    * **Hidden files**
        * `.gitignore`
        * `.Rproj.user` - *not tracked*
        * `.snakemake` - *not tracked*

### Dependencies:

- `Hisat-2`
- `StringTie`
- `R`
- `Snakemake`
- `zsh shell`

### 2023-03-17 README.Rmd
Update Project README.Rmd

@@
 
-```{r include = FALSE}
+```{r list_dirs, exclude=TRUE}
 
-script_dir <- for(item in list.files("scripts")){
-    print(item, quote = FALSE)}
+script_dir <- list.files("scripts")
+rawfiles_dir <- list.files("raw_files")
+results_dir <- list.files("results")
+reads_dir <- list.files("trimmedReads")
 
-rawfiles_dir <- for(item in list.files("raw_files")){
-    print(item, quote = FALSE)}
-
-results_dir <- for(item in list.files("results")){
-    print(item, quote = FALSE)
-}
 ```
-* **`ROOT (thev_transcriptome)`**
+* **`ROOT (thev_transcriptome)/`**
     * **Directories:**
-        * *`scripts`*
-        * *`raw_files`*
-        * *`results`*
-        * *`trimmedReads`*
+        * *`raw_files`/* - Add README for more details
+            * ``r rawfiles_dir[1]`/`
+            * ``r rawfiles_dir[2]`/`
+            * ``r rawfiles_dir[3]`/`
+        * *`results/`* - Add README for more details
+            * ``r results_dir[1]`/`
+            * ``r results_dir[2]`/`
+            * ``r results_dir[3]`/`
+        * *`scripts/`* - Add README for more details
+            * ``r script_dir[1]`/`
+            * ``r script_dir[2]`/`
+            * ``r script_dir[3]`/`
+        * *`trimmedReads/`* - Add README for more details
+            * ``r reads_dir[1]`/`
+            * ``r reads_dir[2]`/`
     * **Files**
@@
         * *`driver_script`* - *`deprecated`*
+        * *`README.html`*
         * *`README.Rmd`*
-        * *`project_map.pdf`* 
-        * *`project_jobmap.pdf`*
+        * *`project_map.svg`* 
+        * *`project_jobmap.svg`*
         * *`thev_transcriptome.Rproj`* - *not on Git*
@@
         * `.gitignore`
-        * `.Rproj.user` - *not tracked*
-        * `.snakemake` - *not tracked*
+        * `.Rproj.user` - *not on Git*
+        * `.snakemake` - *not on Git*
+
+`r script_dir`
 

### 2023-03-17 README.Rmd
Update Project README.Rmd

--- 2023-03-17 README.Rmd
@@
 
-![project_map](./project_map.svg){width=720px height=620px}
+![project_map](./project_map.svg){width=620px height=480px}
 
@@
 
-```{r include = FALSE}
+```{r list_dirs, exclude=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
+library(tidyverse)
+dirs <- list.dirs(".", recursive = F, full.names = F)
+all_files <- list.files(".", all.files = T)
+root_files <- subset(all_files, all_files %in% dirs == FALSE)
+script_dir <- list.files("scripts")
+rawfiles_dir <- list.files("raw_files")
+results_dir <- list.files("results")
+reads_dir <- list.files("trimmedReads")
 
-script_dir <- for(item in list.files("scripts")){
-    print(item, quote = FALSE)}
+```
+* **`ROOT (thev_transcriptome)/`**
+    * **Directories:**
+        * *``r dirs[4]`/`* - Add README for more details
+            * ``r rawfiles_dir[1]`/`
+            * ``r rawfiles_dir[2]`/`
+            * ``r rawfiles_dir[3]`/`
+        * *``r dirs[5]`/`* - Add README for more details
+            * ``r results_dir[1]`/`
+            * ``r results_dir[2]`/`
+            * ``r results_dir[3]`/`
+        * *``r dirs[6]`/`* - Add README for more details
+            * ``r script_dir[1]`/`
+            * ``r script_dir[2]`/`
+            * ``r script_dir[3]`/`
+        * *``r dirs[7]`/`* - Add README for more details
+            * ``r reads_dir[1]`/`
+            * ``r reads_dir[2]`/`
+    * **Files**
+        * *``r root_files[5]``* - *`deprecated`*: replaced by `Snakefile`
+        * *``r root_files[6]``*
+        * *``r root_files[7]``*
+        * *``r root_files[8]``*
+        * *``r root_files[9]``*
+        * *``r root_files[10]``*
+        * *``r root_files[11]``*
+        * *``r root_files[12]``*
+        * *``r root_files[13]``* - *not on Git*
+    * **Hidden files** - *not on Git*
+        * *``r root_files[3]``*
+        * *``r root_files[4]``*
+        * ``r dirs[1]`/`
+        * ``r dirs[2]`/`
+        * ``r dirs[3]`/`
 
-rawfiles_dir <- for(item in list.files("raw_files")){
-    print(item, quote = FALSE)}
-
-results_dir <- for(item in list.files("results")){
-    print(item, quote = FALSE)
-}
-```
-* **`ROOT (thev_transcriptome)`**
-    * **Directories:**
-        * *`scripts`*
-        * *`raw_files`*
-        * *`results`*
-        * *`trimmedReads`*
-    * **Files**
-        * *`Snakefile`*
-        * *`driver_script`* - *`deprecated`*
-        * *`README.Rmd`*
-        * *`project_map.pdf`* 
-        * *`project_jobmap.pdf`*
-        * *`thev_transcriptome.Rproj`* - *not on Git*
-    * **Hidden files**
-        * `.gitignore`
-        * `.Rproj.user` - *not tracked*
-        * `.snakemake` - *not tracked*
+`r script_dir`
 
@@
 - `zsh shell`
+- See `environment.yml` for `conda env` dependencies

### 2023-03-17 README.Rmd
Update project README

@@
 ---
-title: Turkey Hemorrhagic Enteritis Virus transcription profiling
+title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
 author: Abraham Quaye
@@
 ---
-
-# THEV transcriptome studies
+```{css echo=FALSE}
+body {
+    font-size: 2vw
+}
+```
+<!-- # THEV transcriptome studies -->
 
@@
 
-![project_map](./project_map.svg){width=620px height=480px}
+![project_map](./project_map.svg){width=920px height=680px}
 
@@
 
-`r script_dir`
-
 ### Dependencies:

### 2023-03-17 README.Rmd
Add gff3 file downloaded from NCBI
update project DAG maps

--- 2023-03-17 README.Rmd
@@
 ---
-
-# THEV transcriptome studies
+```{css echo=FALSE}
+body {
+    <!-- background-color: #262626; -->
+    <!-- color: white; -->
+    font-size: 2vw
+}
+```
+<!-- # THEV transcriptome studies -->
 
@@
 
-![project_map](./project_map.svg){width=720px height=620px}
+![project_map](./project_map.svg){width=920px height=680px}
 
@@
 
-```{r list_dirs, exclude=TRUE}
-
+```{r list_dirs, exclude=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
+library(tidyverse)
+dirs <- list.dirs(".", recursive = FALSE, full.names = FALSE)
+all_files <- list.files(".", all.files = TRUE)
+root_files <- subset(all_files, all_files %in% dirs == FALSE)
 script_dir <- list.files("scripts")
@@
 reads_dir <- list.files("trimmedReads")
-
 ```
@@
     * **Directories:**
-        * *`raw_files`/* - Add README for more details
+        * *``r dirs[4]`/`* - Add README for more details
             * ``r rawfiles_dir[1]`/`
@@
             * ``r rawfiles_dir[3]`/`
-        * *`results/`* - Add README for more details
+        * *``r dirs[5]`/`* - Add README for more details
             * ``r results_dir[1]`/`
@@
             * ``r results_dir[3]`/`
-        * *`scripts/`* - Add README for more details
+        * *``r dirs[6]`/`* - Add README for more details
             * ``r script_dir[1]`/`
@@
             * ``r script_dir[3]`/`
-        * *`trimmedReads/`* - Add README for more details
+        * *``r dirs[7]`/`* - Add README for more details
             * ``r reads_dir[1]`/`
@@
     * **Files**
-        * *`Snakefile`*
-        * *`driver_script`* - *`deprecated`*
-        * *`README.html`*
-        * *`README.Rmd`*
-        * *`project_map.svg`* 
-        * *`project_jobmap.svg`*
-        * *`thev_transcriptome.Rproj`* - *not on Git*
-    * **Hidden files**
-        * `.gitignore`
-        * `.Rproj.user` - *not on Git*
-        * `.snakemake` - *not on Git*
-
-`r script_dir`
+        * *``r root_files[5]``* - *`deprecated`*: replaced by `Snakefile`
+        * *``r root_files[6]``*
+        * *``r root_files[7]``*
+        * *``r root_files[8]``*
+        * *``r root_files[9]``*
+        * *``r root_files[10]``*
+        * *``r root_files[11]``*
+        * *``r root_files[12]``*
+        * *``r root_files[13]``* - *not on Git*
+    * **Hidden files** - *not on Git*
+        * *``r root_files[3]``*
+        * *``r root_files[4]``*
+        * ``r dirs[1]`/`
+        * ``r dirs[2]`/`
+        * ``r dirs[3]`/`
 
@@
 
-- `Hisat-2`
+- `AGAT`
+- `Hisat2`
 - `StringTie`

### 2023-03-29 README.Rmd
Make READMe.Rmd into github_document

--- 2023-03-17 README.Rmd
@@
 ---
-title: Turkey Hemorrhagic Enteritis Virus transcription profiling
+title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
 author: Abraham Quaye
 date: 2023-03-16
-output: html_document
+output:
+    github_document:
+        html_preview: FALSE
 ---
-
-# THEV transcriptome studies
+```{css echo=FALSE}
+body {
+    <!-- background-color: #262626; -->
+    <!-- color: white; -->
+    font-size: 2vw
+}
+```
+<!-- # THEV transcriptome studies -->
 
@@
 
-![project_map](./project_map.svg){width=620px height=480px}
+![](./project_map.pdf){width=920px height=680px}
 
@@
 library(tidyverse)
-dirs <- list.dirs(".", recursive = F, full.names = F)
-all_files <- list.files(".", all.files = T)
+library(rmarkdown)
+dirs <- list.dirs(".", recursive = FALSE, full.names = FALSE)
+all_files <- list.files(".", all.files = TRUE)
 root_files <- subset(all_files, all_files %in% dirs == FALSE)
@@
 
-`r script_dir`
-
 ### Dependencies:
 
-- `Hisat-2`
+- `AGAT`
+- `Hisat2`
 - `StringTie`
-- `R`
+- `r R.version.string`
+- `tidyverse`(v.`r packageVersion("tidyverse")`)
+- `rmarkdown`(v.`r packageVersion("rmarkdown")`)
 - `Snakemake`

### 2023-03-29 README.Rmd
Edit project README.Rmd and revert DAG graphs to SVG

@@
 - `StringTie`
-- `r R.version.string`
+- ``r R.version.string``
 - `tidyverse`(v.`r packageVersion("tidyverse")`)

### 2023-03-29 README.Rmd
Add here package to environment.yml  Edit project README.Rmd with updated info  and unsource Rscript for generating figures  Regenerate figures; ensure no changes

--- 2023-03-17 README.Rmd
@@
 title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
-author: Abraham Quaye
+author: <strong>Abraham Quaye</strong><br>
 date: 2023-03-16
-output: html_document
+output: github_document
 ---
-```{css echo=FALSE}
+```{css aesthetics, echo=FALSE, include=FALSE}
 body {
@@
 ```
-<!-- # THEV transcriptome studies -->
+```{r call_libs, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
+library(tidyverse)
+library(here)
 
+cov_all <- read_tsv("results/hisat2/coverage/bulk_coverage.txt",
+                    comment = "Coverage", show_col_types = FALSE) %>% 
+  map_at(c(2:9), as.numeric) %>% 
+  as_tibble()
+
+total_mapped <- round(sum(cov_all$numreads)/1e6)
+```
 ## Background
@@
 After infecting a turkey B-cell line (RP-19) with THEV, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
-Total RNA was subsequently extracted using Thermofishers’s RNAqueous-4PCR Total RNA Isolation Kit, and poly-A-tailed mRNA sequencing done at LC Sciences, Houston TX.
-The raw sequencing reads were trimmed with the FastQC program, mapped to the THEV genome using Hisat2 and transcripts assembled with StringTie.
-The `--merge` function of StringTie was used to consolidate transcripts from all timepoints, generating the final THEV transcriptome.
+Total RNA was subsequently extracted using Thermofishers’s `RNAqueous-4PCR Total RNA Isolation Kit`, and poly-A-tailed mRNA sequencing done at `LC Sciences, Houston TX`.
+The raw sequencing reads were trimmed with the `FastQC` program, mapped to the THEV genome using `Hisat2` and transcripts assembled with `StringTie`.
+A custom `Rscript` was used to consolidate all transcripts from all time-points and remove duplicated features, generating the final THEV transcriptome map.
 
@@
 
-![project_map](./project_map.svg){width=920px height=680px}
+![](project_map.svg){width=920px height=680px}
 
@@
 
-Over 18 million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
-All predicted genes in the genome were represented.
-Interestingly, all were spliced with either with 5’- or 3’-multi exon UTRs hitherto unknown.
-Thirteen novel exons were identified which require additional verification.
-The splicing patterns strongly suggest that there are 3 main promoters (E1a-, E3, and major late promoters) driving expression of most of the genes with 2 possible minor promoters driving single genes (ORF7 and ORF8).
+Over `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
+The assembled transcripts fully covered almost all predicted genes in the genome except *33K*, *22K*, *100K*, and *ORF1*, which were either partially represented or showed a slightly different CDS due to internal splicing.
+Interestingly, all genes were spliced with either with 5’- or 3’-multi exon UTRs hitherto unknown in THEV, albeit, consistent with *mastadenoviridae*.
+35 unique novel exons were identified which require additional verification.
+The splicing patterns strongly suggest that there are 4 main promoters (E1a-, E2, E3, and major late promoter [MLP]) driving expression of most of the genes with 1 minor promoter driving the gene, ORF8.
 
-We have performed the first RNA-sequencing experiment aimed at characterizing THEV’s transcriptome, which has yielded the only experimentally determined and the most detailed insight of THEV gene expression.
-In keeping with all Adenoviruses, our data shows that almost all THEV genes are spliced, and under the control of a promoter, several genes are expressed as one transcription unit.
-This insight of THEV’s transcriptome may allow the engineering of VAS to provide immune protection with less or no associated IS.
+We have performed the first RNA-sequencing experiment aimed at characterizing THEV’s transcriptome, which has yielded the only experimentally determined and the most detailed insight of THEV's gene expression map.
+In keeping with all *Adenoviruses*, our data shows that all but one (UXP) of THEV genes are spliced, and under the control of a promoter, several genes are expressed as one transcription unit.
+Hence, THEV has four major transcription units, with an extra promoter for ORF8.
+This insight of THEV’s transcriptome is essential for elucidating the functions of individual genes, and may eventually allow the engineering of VAS to provide immune protection with less or no associated IS.
 
@@
 library(tidyverse)
+library(rmarkdown)
 dirs <- list.dirs(".", recursive = FALSE, full.names = FALSE)
-all_files <- list.files(".", all.files = TRUE)
+all_files <- list.files(".", all.files = TRUE, pattern = "\\.\\w+.+")
 root_files <- subset(all_files, all_files %in% dirs == FALSE)
@@
 reads_dir <- list.files("trimmedReads")
+wetlab_dir <- list.files("wet_lab_validation")
 ```
@@
             * ``r results_dir[3]`/`
+            * ``r results_dir[4]`/`
         * *``r dirs[6]`/`* - Add README for more details
@@
             * ``r reads_dir[2]`/`
+        * *``r dirs[8]`/`* - Add README for more details
+            * ``r wetlab_dir[1]`/`
+            * ``r wetlab_dir[2]`/`
     * **Files**
-        * *``r root_files[5]``* - *`deprecated`*: replaced by `Snakefile`
+        * *``r root_files[3]``*
+        * *``r root_files[4]``*
+        * *``r root_files[5]``*
         * *``r root_files[6]``*
@@
         * *``r root_files[8]``*
-        * *``r root_files[9]``*
-        * *``r root_files[10]``*
-        * *``r root_files[11]``*
-        * *``r root_files[12]``*
-        * *``r root_files[13]``* - *not on Git*
+        * *``r root_files[9]``* - *not on Git*
     * **Hidden files** - *not on Git*
-        * *``r root_files[3]``*
-        * *``r root_files[4]``*
+        * *``r root_files[1]``*
+        * *``r root_files[2]``*
         * ``r dirs[1]`/`
@@
 
+- `FastQC`
 - `AGAT`
@@
 - `StringTie`
-- `R`
+- ``r R.version.string``
+- `tidyverse`(v.`r packageVersion("tidyverse")`)
+- `rmarkdown`(v.`r packageVersion("rmarkdown")`)
 - `Snakemake`

### 2023-05-17 README.Rmd
update readme file to include uninfected reads analysis

@@
             * ``r reads_dir[2]`/`
+            * ``r reads_dir[3]`/`
         * *``r dirs[8]`/`* - Add README for more details

### 2023-05-18 manuscript_thev_transcriptome.Rmd
start writing manuscript for publication

---
output:
  word_document: default
  pdf_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
---

# Turkey Hemorrhagic Enteritis Virus transcriptome profiling

\vspace{10mm}

**Running Title:** Novel Insights into Turkey Hemorrhagic Enteritis Virus Transcriptome

\vspace{25mm}
Abraham Quaye${^1}$, Bret Pickett, Joel S. Griffitts, Bradford K. Berges, Brian D. Poole${^\dagger}$

\vspace{5mm}
${\dagger}$ Corresponding Author

\vspace{10mm}
Department of Microbiology and Molecular Biology,  
Brigham Young University,  
A-153ASB Provo, Utah

\newpage

```{r call_libs, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

## Abstract

\newpage
## Introduction

\newpage
## Methods
### Cell culture and THEV Infection  
### RNA extraction and Sequencing  
### Computational Analysis of Sequencing Data  
### PCR Validation of Novel Splice Sites and Sanger Sequencing  
### 3' Rapid Amplification of cDNA Ends (3'RACE)

\newpage
## Results

\newpage
## Discussion/Conclusions

\newpage
## Scripts and Supplementary Materials

\newpage
## Figures

\newpage
## Acknowledgements

\newpage
## References

### 2023-05-20 manuscript_thev_transcriptome.Rmd
Start writing manuscript for publication, make required files

@@
   - \linenumbers
+bibliography: transcriptome_refs.bib
+csl: asm.csl
 ---
@@
 \vspace{25mm}
-Abraham Quaye${^1}$, Bret Pickett, Joel S. Griffitts, Bradford K. Berges, Brian D. Poole${^\dagger}$
+Abraham Quaye^1^, Bret Pickett, Joel S. Griffitts, Bradford K. Berges, Brian D. Poole${^\dagger}$
 
 \vspace{5mm}
-${\dagger}$ Corresponding Author
+${\dagger}$ **Corresponding Author**
 
@@
 library(tidyverse)
+library(here)
+library(knitr)
+opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+
+inline_hook <- function(x) {
+  paste0("***", x, "***")
+}
+knit_hooks$set(iniline = inline_hook)
 ```
 
-## Abstract
+## ABSTRACT
+#### Background:
+Hemorrhagic enteritis (HE)is a disease affecting 6-12-week-old turkeys characterized by **immunosuppression (IS)**, bloody diarrhea, and up to 60% mortality.
+This disease is caused by **_Turkey Hemorrhagic Enteritis Virus (THEV)_** of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
+The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
+**_Our objective is to understand the genetic basis by which VAS brings about IS_**.
+The **transcriptome of THEV** was studied to set the stage for further experimentation with specific viral genes that may mediate IS.
 
+#### Methods:
+After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
+Total RNA was subsequently extracted, and poly-A-tailed mRNA sequencing done at LC Sciences.
+The raw sequencing reads were trimmed with the FastQC program, mapped to the THEV genome using Hisat2 and transcripts assembled with StringTie.
+An in-house script was used to consolidate transcripts from all timepoints, generating the final transcriptome.
+
+#### Results:
+Over 18 millionXXXXXX reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
+All predicted genes in the genome were represented.
+In keeping with all adenoviruses, all transcripts were spliced with either with 5'- or 3'-multi exon UTRs hitherto unknown.
+ThirteenXXXXX novel exons were identified which were validated by PCR and Sanger sequencing.
+The splicing patterns strongly suggest that there are 3XXXXX main promoters (E1, E3, and major late promoters) driving expression of most of the genes with 2XXXXXX possible minor promoters driving single genes (ORF7 and ORF8).
+
+#### Conclusions:
+This RNA-sequencing experiment is the first study of THEV gene expression to date.
+In keeping with other Adenoviruses, almost all THEV genes are spliced, and several genes are expressed as one transcription unit under a single promoter.
+This insight into THEV's transcriptome may allow the engineering of the VAS to provide immune protection with less or no associated IS.
 \newpage
-## Introduction
 
+## INTRODUCTION   
+Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all vertebrates.
+Their double-stranded linear DNA genomes range between 26 and 45kb in size, with wide variations in the number of proteins encoded and producing a broad repertoire of proteins via a highly complex alternative splicing mechanism [@Davison2003; @Harrach2008].
+The AdV genome is one of the most optimally economized; both the forward and reverse DNA strands harbor protein-coding genes making it highly gene-dense.
+There are 16 genes termed "genus-common" that are homologous in all AdVs; these are thought to be inherited from a common ancestor.
+All other genes are termed "genus-specific".
+"Genus-specific" genes tend to be located at the termini of the genome while "genus-common" genes are usually central [@Davison2003].
+This pattern is observed in *Adenoviridae*, *Poxviridae*, and *Herpesviridae* [@Davison2003; @Upton2003; @McGeoch1999].
+The family *Adenoviridae* consists of five genera: *Mastadenovirus* (MAdV), *Aviadenovirus*, *Atadenovirus*, *Ichtadenovirus*, and *Siadenovirus* (SiAdV) [@Harrach2011; @Guimet2016].
+Currently, there are three recognized members of the genus SiAdV: frog adenovirus 1, raptor adenovirus 1, and turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009].
+Members of SiAdV have the smallest genome size (~26 kb) and gene content (~23 genes) of all known AdVs, and many “genus-specific” putative genes of unknown functions have been annotated [@Harrach2008; @Kovács2011].
+The genomic map of THEV showing details of the "genus-specific" and "genus-common" genes, and the gene distribution patterns described above is shown in __Figure 1__.
+
+ Virulent strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants.
+They infect via the fecal-oral route, and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
+In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 60% mortality [@Beach2006; @Gross1967].
+HE is the most economically significant disease caused by any strain of THEV [@Beach2006].
+While the current vaccine strain (a THEV-A isolated from a pheasant, Virginia Avirulent Strain [VAS]) have proven effective at preventing HE in young turkey poults, it still retains the immunosuppressive ability.
+Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
+The induced IS also interferes with vaccination schemes for other infections of turkeys [@Beach2006; @Rautenschlein2000].
+To eliminate this immunossupressive side-effect of the vaccine, a thorough understanding of the viral factors (genes) mediating this phenomenon is essential.
+However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
+To identify such viral factors, a well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.
+
+MAdVs - specifically human adenoviruses - are by far the most extensively studied; hence, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is used representatively for all other AdVs [@Guimet2016; @Wolfrum2013].
+MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate units (pIX and IVa2), and one major late unit (MLTU), generating five families of late mRNAs (L1-L5).
+An additional gene (UXP or U exon) is located on the reverse strand.
+The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins.
+The immediate early gene E1A is expressed first, followed by the the delayed early genes, E1B, E2, E3 and E4.
+Then the intermediate early genes, IVa2 and pIX are expressed, after which the late genes are expressed [@Zhao2014; @Donovan2020; @Guimet2016].
+MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs; all but pIX mRNA undergo at least one splicing event.
+The MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
+There is an alternate 5' three non-coding exons present in varying amounts on a subset of MLTU mRNAs (known as the x-, y- and z-leaders).
+Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
+Thus, the MLTU produces a complex repertoire of mRNA with diverse 5'-UTRs, spliced onto different 3' coding exons grouped into five different 3'-end classes (L1-L5).
+Each transcription unit contains its own promoter that drives the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
+
+Almost all AdV mRNAs are generated by the excision of one or more introns and most of these introns are located in the 5' or 3' UTRs of pre-mRNA.
+Thus the viral introns do only in a few cases interrupt the open reading frames (ORFs) [@Davison2003; @Zhao2014].
+The development of high throughput sequencing methods has facilitated the discovery of many novel transcribed regions and splicing isoforms.
+It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014].
+Here, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
+Our paired-end sequencing allowed for reading 150bp long sequences from each end of cDNA fragments.
+The data generated from paired-end sequencing, utilized in our experiment, should thus be reliable.
 \newpage
-## Methods
+
+## METHODS   
 ### Cell culture and THEV Infection   
+The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium with 10% fetal bovine serum (FBS), 20% chicken serum (ChS), 5% tryptose phosphate broth (TPB), and 1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin), at 41^o^C in a humidified atmosphere with 5% CO~2~.
+When infected, the cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and  1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin).
+A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A.
+The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL.
+Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA sequencing.
+A second infection was done but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
+
 ### RNA extraction and Sequencing   
-### Computational Analysis of Sequencing Data  
+Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` as per manufacturer's instructions.
+The RNA quantity and purity was initially assessed using nanodrop, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
+Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA sequencing library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
+Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.
+
+### Computational Analysis of RNA Sequencing Data: Mapping and Transcript characterization
+Analysis of our sequencing reads were analyzed following a well established general outline described by Pertea _et al_ [@Pertea2016].
+Briefly, sequencing reads were trimmed with the `FastQC`[@FastQC] program to acheive an overall `Mean Sequence Quality (Phred Score)` of 36.
+Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2` [@Pertea2016] with default settings except increasing the CPU cores to 10.
+The generated `BAM` files from each infection timepoint were fed into `StringTie` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
+A custom script was used to consolidate all transcripts from all timepoints without redundancy, generating the final transcriptome of THEV.
+
 ### PCR Validation of Novel Splice Sites and Sanger Sequencing  
+All splice sites identified in this work are novel except one splice site predicted for pTP, DBP, and 33K each.
+However, these predictions fell short of the full splicing of these genes and were not experimentally validated.
+We designed primers that crossed a range of novel exon–exon boundaries for all transcripts in a transcription units with their respective universal primers (supplementary PCR methodsXXXXXXXXX).
+After first-strand cDNA synthesis with Thermofishers' SuperScript™ III First-Strand Synthesis System (`#18080051`), these primers were used in a targeted PCR experiment, the PCR products were analysed on agarose gels, cloned by traditional restriction enzyme-ligation method and sanger sequenced at `Eton Bioscience, Inc, San Diego, CA` to validate these splice junctions at the sequence level.
+
 ### 3' Rapid Amplification of cDNA Ends (3'RACE)
@@
 \newpage
-## Results
+
+## RESULTS
 
 \newpage
-## Discussion/Conclusions
+
+## DISCUSSION/CONCLUSIONS
 
 \newpage
-## Scripts and Supplementary Materials
+
+## SCRIPTS AND SUPPLEMENTARY MATERIALS
+
+### DATA AVAILABILITY
+
+### CODE AVAILABILITY    
+All the code/scripts written for analysis of the data is available on github (linkXXXXXX)
+\newpage
+
+## ACKNOWLEDGMENTS
 
 \newpage
-## Figures
 
+## REFERENCES     
+\setlength{\parindent}{-0.25in}
+\setlength{\leftskip}{0.25in}
+\noindent
+<div id="refs"></div>
+\setlength{\parindent}{0in}
+\setlength{\leftskip}{0in}
 \newpage
-## Acknowledgements
 
-\newpage
-## References
+## FIGURES     
+![Fig.1](results/r/thev_genomic_map.png)  
+**Figure 1.
+_Genomic map of THEV avirulent strain_**.
+The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
+Blocks represent viral genes.
+Blocks above the DNA line are transcribed rightward, those below are transcribed leftward.
+pTP, DBP and 33K predicted to be spliced are shown as having tails.
+Shaded regions indicates regions containing genes (colored red) that are not conserved across adenovirus genera (i.e.
+"genus-specific").
+Genes colored in blue are "genus-common".
+Gene colored in light green is conserved in all but Atadenoviruses.
+The U exon (light blue) is an incomplete gene present in almost all AdVs.

### 2023-05-21 manuscript_thev_transcriptome.Rmd
Rerun uninfected samples

@@
 ## METHODS
+
 ### Cell culture and THEV Infection   

### 2023-05-21 manuscript_thev_transcriptome.Rmd
Continue writing manuscript; write scripts to insert stats

--- 2023-05-20 manuscript_thev_transcriptome.Rmd
@@
 ```{r call_libs, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
+library(knitr)
 library(tidyverse)
-library(here)
-library(knitr)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 
+```{r inline_values}
+
+# extract paired-end sequencing read length
+bam_info <- read_tsv("results/sgseq/bam_extracted_sampleData.tsv",
+                     show_col_types = F) 
+seq_len <- bam_info %>% select(read_length) %>% slice_head() %>% pull()
+
+# extract coverage and mapping information
+cov_all <- read_tsv("results/hisat2/coverage/bulk_coverage.txt",
+                    comment = "Coverage", show_col_types = FALSE) %>%
+  rename("organism" = "#rname") %>%
+  filter(organism != "#rname") %>%
+  mutate(timepoint = c("4hpi", "12hpi", "24hpi", "72hpi"),
+         timepoint = factor(timepoint,
+            levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>%
+  map_at(c(2:9), as.numeric) %>%
+  as_tibble()
+
+cov_4hr <- cov_all %>% filter(timepoint == "4hpi") %>%
+              select(numreads) %>% pull()
+cov_72hr <- cov_all %>% filter(timepoint == "72hpi") %>%
+              select(numreads) %>% pull()
+cov_72hr <- round(cov_72hr / 1e6, 2)
+total_mapped <- round(sum(cov_all$numreads) / 1e6, 2)
+
+load_count <- read_table("results/hisat2/coverage/bulk_counts.txt",
+                         col_names = T, show_col_types = F) %>% pull()
+tot_count <- round(mean(load_count) / 1e6, 2)
+````
 ## ABSTRACT
@@
 #### Results:
-Over 18 millionXXXXXX reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
+A total of `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
 All predicted genes in the genome were represented.
@@
 Here, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
-Our paired-end sequencing allowed for reading 150bp long sequences from each end of cDNA fragments.
+Our paired-end sequencing allowed for reading `r seq_len` bp long sequences from each end of cDNA fragments.
 The data generated from paired-end sequencing, utilized in our experiment, should thus be reliable.
+\newpage
+
+## RESULTS      
+**Overview of sequencing data and analysis pipeline outputs**     
+A previous study by Zeinab *et al* showed that most THEV transcripts were detectable beginning at 4 hours[@Aboezz2019]; hence, infected MDTC-RP19 cells were collected in triplicates at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide window for transcript capture.
+Our `r seq_len`bp paired-end RNA sequencing experiment yielded an average of `r tot_count` million total reads per timepoint and the reads mapping to the virus genome increased dramatically from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i.
+Altogether, `r total_mapped` million reads from all timepoints mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
+
 \newpage
@@
 When infected, the cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and  1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin).
-A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A.
+A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
 The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL.
@@
 Briefly, sequencing reads were trimmed with the `FastQC`[@FastQC] program to acheive an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2` [@Pertea2016] with default settings except increasing the CPU cores to 10.
+Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2` (version `xxxxxx`) [@Pertea2016] with default settings except increasing the CPU cores to 10 without relying on known splice sites.
 The generated `BAM` files from each infection timepoint were fed into `StringTie` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
@@
 ### 3' Rapid Amplification of cDNA Ends (3'RACE)
-
-\newpage
-
-## RESULTS
 

### 2023-05-21 scripts/r/sgseq_spliceAnalysis.R

@@ -1,3 +1,4 @@
+#!/usr/bin/env Rscript
 
 library(SGSeq)
 library(tidyverse)
@@ -14,33 +15,18 @@ library(tidyverse)
 # ## extract information from bam files. This is a slow function so I'll save the data
 # # as a tsv and load it henceforth
 # sample_info <- getBamInfo(sample, cores = 8)
+
 # write.table(sample_info, "results/sgseq/bam_extracted_sampleData.tsv",
 #             col.names = T, row.names = F, quote = F, sep = "\t")
 
 ### ====================================
 # load in sample/bam information
 
-bam_info <- read_tsv("results/sgseq/bam_extracted_sampleData.tsv", show_col_types = F) %>%
-  slice(3)
+bam_info <- read_tsv("results/sgseq/bam_extracted_sampleData.tsv",
+  show_col_types = F) 
 
-### ====================================
-# load in predicted genes from ncbi
-
-features <- importTranscripts("raw_files/annotations/thev_from_NCBI.gtf")
-dtx_features <- convertToTxFeatures(features)
-sg_features <- convertToSGFeatures(tx_features)
-
-### ====================================
-# analyze splice sites
-
-spliceSites24 <- analyzeFeatures(bam_info, tx_features, cores = 8, verbose = T)
-
-
-# visualize
-plotFeatures(spliceSites24, geneID = 1, heightPanels = c(3, 1), square = T,
-             toscale = "exon",
-             col = colorRampPalette(c("blue", "red"))(256), cex = 0.5)
-
-
-
+bam_info %>%
+  select(read_length) %>%
+  slice(1) %>%
+  pull()
 

### 2023-05-22 manuscript_thev_transcriptome.Rmd
Rerun entire analysis including mock switched mock fastq N1 with infected fastq S3 due to probable sample mixup or contamination of mock with virus.

@@
 ---
+title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
 output:
@@
 csl: asm.csl
+editor_options:
+  chunck_output_type: console
 ---
-
-# Turkey Hemorrhagic Enteritis Virus transcriptome profiling
-
 \vspace{10mm}
@@
 }
-knit_hooks$set(iniline = inline_hook)
+knit_hooks$set(inline = inline_hook)
 ```
@@
 **Overview of sequencing data and analysis pipeline outputs**     
-A previous study by Zeinab *et al* showed that most THEV transcripts were detectable beginning at 4 hours[@Aboezz2019]; hence, infected MDTC-RP19 cells were collected in triplicates at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide window for transcript capture.
-Our `r seq_len`bp paired-end RNA sequencing experiment yielded an average of `r tot_count` million total reads per timepoint and the reads mapping to the virus genome increased dramatically from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i.
-Altogether, `r total_mapped` million reads from all timepoints mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
+A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours[@Aboezz2019]; hence, infected MDTC-RP19 cells were collected in triplicates at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide window to sample all transcripts.
+Our `r seq_len` bp paired-end RNA sequencing experiment yielded an average of `r tot_count` million total reads per timepoint and the reads mapping to the virus genome increased dramatically from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i.
+Altogether, `r total_mapped` million reads from all timepoints mapped to THEV genome providing good coverage/depth, leaving no regions unmapped (__Table 1__).
 
@@
 Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` as per manufacturer's instructions.
+An agarose gel electrophoresis was performed to check RNA integrity.
 The RNA quantity and purity was initially assessed using nanodrop, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
@@
 Analysis of our sequencing reads were analyzed following a well established general outline described by Pertea _et al_ [@Pertea2016].
-Briefly, sequencing reads were trimmed with the `FastQC`[@FastQC] program to acheive an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2` (version `xxxxxx`) [@Pertea2016] with default settings except increasing the CPU cores to 10 without relying on known splice sites.
-The generated `BAM` files from each infection timepoint were fed into `StringTie` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
+Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to acheive an overall `Mean Sequence Quality (Phred Score)` of 36.
+Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings except increasing the CPU cores to 10 without relying on known splice sites.
+The generated `BAM` files from each infection timepoint were fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
 A custom script was used to consolidate all transcripts from all timepoints without redundancy, generating the final transcriptome of THEV.
@@
 
-## FIGURES     
+## TABLES AND FIGURES     
 ![Fig.1](results/r/thev_genomic_map.png)  

### 2023-05-26 manuscript_thev_transcriptome.Rmd
Add validation sequencing results for orf8 and E2B

@@
 ---
-\vspace{10mm}
+\vspace{5mm}
 
@@
 
-\vspace{25mm}
-Abraham Quaye^1^, Bret Pickett, Joel S. Griffitts, Bradford K. Berges, Brian D. Poole${^\dagger}$
+\vspace{10mm}
+Abraham Quaye^1\*^, Bret Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
 
 \vspace{5mm}
-${\dagger}$ **Corresponding Author**
 
-\vspace{10mm}
+^\*^Department of Microbiology and Molecular Biology, Brigham Young University       
+^1^First-author      
+${^\dagger}$ Corresponding Author
+
+\vspace{5mm}
+**Corresponding Author Information**     
+[brian_poole@byu.edu](mailto:brian_poole@byu.edu)       
 Department of Microbiology and Molecular Biology,       
+4007 Life Sciences Building (LSB),    
 Brigham Young University,   
-A-153ASB Provo, Utah
-
+Provo, Utah  
 \newpage
@@
 inline_hook <- function(x) {
-  paste0("***", x, "***")
+  if(is.numeric(x)){
+    formatted <- format(x, big.mark = ",")
+  }else{formatted <- x}
+  paste0("**", formatted, "**")
 }
@@
               select(numreads) %>% pull()
-cov_72hr <- round(cov_72hr / 1e6, 2)
-total_mapped <- round(sum(cov_all$numreads) / 1e6, 2)
+cov_72hr <- round(cov_72hr / 1e6, 1)
+total_mapped <- round(sum(cov_all$numreads) / 1e6, 1)
 
@@
                          col_names = T, show_col_types = F) %>% pull()
-tot_count <- round(mean(load_count) / 1e6, 2)
-````
+tot_count <- round(mean(load_count) / 1e6, 1)
+```
 ## ABSTRACT        
-#### Background:
-Hemorrhagic enteritis (HE)is a disease affecting 6-12-week-old turkeys characterized by **immunosuppression (IS)**, bloody diarrhea, and up to 60% mortality.
-This disease is caused by **_Turkey Hemorrhagic Enteritis Virus (THEV)_** of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
+**Background:** Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by _immunosuppression (IS)_ and bloody diarrhea.
+This disease is caused by _Turkey Hemorrhagic Enteritis Virus (THEV)_ of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
 The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
-**_Our objective is to understand the genetic basis by which VAS brings about IS_**.
-The **transcriptome of THEV** was studied to set the stage for further experimentation with specific viral genes that may mediate IS.
-
-#### Methods:
-After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
-Total RNA was subsequently extracted, and poly-A-tailed mRNA sequencing done at LC Sciences.
-The raw sequencing reads were trimmed with the FastQC program, mapped to the THEV genome using Hisat2 and transcripts assembled with StringTie.
-An in-house script was used to consolidate transcripts from all timepoints, generating the final transcriptome.
-
-#### Results:
-A total of `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
+_Our objective is to understand the genetic basis by which VAS induces IS_.
+The _transcriptome of THEV_ was studied to set the stage for further experimentation with specific viral genes that may mediate IS.
+**Methods:** After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
+Total RNA was subsequently extracted, and poly-A-tailed mRNA sequencing done.
+After trimming the raw sequencing reads with the `FastQC`, reads were mapped to the THEV genome using `Hisat2` and transcripts assembled with `StringTie`.
+An in-house script was used to consolidate transcripts from all time-points, generating the final transcriptome.
+PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.
+**Results and Conclusions:** A total of `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
 All predicted genes in the genome were represented.
 In keeping with all adenoviruses, all transcripts were spliced with either with 5'- or 3'-multi exon UTRs hitherto unknown.
-ThirteenXXXXX novel exons were identified which were validated by PCR and Sanger sequencing.
-The splicing patterns strongly suggest that there are 3XXXXX main promoters (E1, E3, and major late promoters) driving expression of most of the genes with 2XXXXXX possible minor promoters driving single genes (ORF7 and ORF8).
-
-#### Conclusions:
+*~~Thirteen~~* novel exons were identified which were validated by PCR and Sanger sequencing.
+The splicing patterns strongly suggest that there are *~~three~~* main promoters (E1, E3, and major late promoters) driving expression of most of the genes with *~~two~~* possible minor promoters driving single genes (ORF7 and ORF8).
 This RNA-sequencing experiment is the first study of THEV gene expression to date.
@@
 Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all vertebrates.
-Their double-stranded linear DNA genomes range between 26 and 45kb in size, with wide variations in the number of proteins encoded and producing a broad repertoire of proteins via a highly complex alternative splicing mechanism [@Davison2003; @Harrach2008].
-The AdV genome is one of the most optimally economized; both the forward and reverse DNA strands harbor protein-coding genes making it highly gene-dense.
+Their double-stranded linear DNA genomes range between 26 and 45kb in size, producing a broad repertoire of transcripts via a highly complex alternative splicing pattern [@Davison2003; @Harrach2008].
+The AdV genome is one of the most optimally economized; both the forward and reverse DNA strands harbor protein-coding genes, making it highly gene-dense.
 There are 16 genes termed "genus-common" that are homologous in all AdVs; these are thought to be inherited from a common ancestor.
@@
 The induced IS also interferes with vaccination schemes for other infections of turkeys [@Beach2006; @Rautenschlein2000].
-To eliminate this immunossupressive side-effect of the vaccine, a thorough understanding of the viral factors (genes) mediating this phenomenon is essential.
+To eliminate this immunossupressive side-effect of the vaccine, a thorough investigation of the culprit viral factors (genes) mediating this phenomenon is essential.
 However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
@@
 
-MAdVs - specifically human adenoviruses - are by far the most extensively studied; hence, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is used representatively for all other AdVs [@Guimet2016; @Wolfrum2013].
+Myriads of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
+However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generally applied to all other AdVs [@Guimet2016; @Wolfrum2013].
 MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate units (pIX and IVa2), and one major late unit (MLTU), generating five families of late mRNAs (L1-L5).
@@
 The immediate early gene E1A is expressed first, followed by the the delayed early genes, E1B, E2, E3 and E4.
-Then the intermediate early genes, IVa2 and pIX are expressed, after which the late genes are expressed [@Zhao2014; @Donovan2020; @Guimet2016].
+Then the intermediate early genes, IVa2 and pIX are expressed followed by the late genes [@Zhao2014; @Donovan2020; @Guimet2016].
 MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs; all but pIX mRNA undergo at least one splicing event.
@@
 It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014].
-Here, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
-Our paired-end sequencing allowed for reading `r seq_len` bp long sequences from each end of cDNA fragments.
-The data generated from paired-end sequencing, utilized in our experiment, should thus be reliable.
+In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
+Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36 using `FastQC`) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
+The data generated from our paired-end sequencing experiment should thus be reliable.
 \newpage
@@
 **Overview of sequencing data and analysis pipeline outputs**     
-A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours[@Aboezz2019]; hence, infected MDTC-RP19 cells were collected in triplicates at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide window to sample all transcripts.
-Our `r seq_len` bp paired-end RNA sequencing experiment yielded an average of `r tot_count` million total reads per timepoint and the reads mapping to the virus genome increased dramatically from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i.
-Altogether, `r total_mapped` million reads from all timepoints mapped to THEV genome providing good coverage/depth, leaving no regions unmapped (__Table 1__).
+A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
+Therefore, infected MDTC-RP19 cells were harvested in triplicates at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
+Our paired-end RNA sequencing experiment yielded an average of `r tot_count` million total reads of `r seq_len`bp in length per time-point.
+A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
+Also, the mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__ and __Figure 2__).
 
@@
 
-## METHODS   
+## MATERIALS AND METHODS   
 ### Cell culture and THEV Infection   
@@
 An agarose gel electrophoresis was performed to check RNA integrity.
-The RNA quantity and purity was initially assessed using nanodrop, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
+The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
 Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA sequencing library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
@@
 Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings except increasing the CPU cores to 10 without relying on known splice sites.
-The generated `BAM` files from each infection timepoint were fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
-A custom script was used to consolidate all transcripts from all timepoints without redundancy, generating the final transcriptome of THEV.
+The generated `BAM` files from each infection time-point were fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
+A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
 
-### PCR Validation of Novel Splice Sites and Sanger Sequencing  
+### Validation of Novel Splice Sites 
 All splice sites identified in this work are novel except one splice site predicted for pTP, DBP, and 33K each.
 However, these predictions fell short of the full splicing of these genes and were not experimentally validated.
-We designed primers that crossed a range of novel exon–exon boundaries for all transcripts in a transcription units with their respective universal primers (supplementary PCR methodsXXXXXXXXX).
-After first-strand cDNA synthesis with Thermofishers' SuperScript™ III First-Strand Synthesis System (`#18080051`), these primers were used in a targeted PCR experiment, the PCR products were analysed on agarose gels, cloned by traditional restriction enzyme-ligation method and sanger sequenced at `Eton Bioscience, Inc, San Diego, CA` to validate these splice junctions at the sequence level.
+We designed primers that crossed a range of novel exon–exon boundaries for all transcripts in a transcription units with their respective universal primers (~~supplementary, PCR methods~~).
+After first-strand cDNA synthesis with Thermofishers' SuperScript™ III First-Strand Synthesis System (`#18080051`), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme-ligation method and Sanger sequenced at `Eton Bioscience, Inc, San Diego, CA` to validate these splice junctions at the sequence level.
 

### 2023-05-26 scripts/r/bam_file_analysis.R

@@ -1,0 +1,4 @@
+library(Rsamtools)
+library(GenomicAlignments)
+library(tidyverse)
+library(GenomicRanges)

### 2023-05-30 manuscript_thev_transcriptome.Rmd
Modify stringtie to create count tables modify putative genomic map to show region labels update some text in manuscript

@@
 They infect via the fecal-oral route, and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
-In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 60% mortality [@Beach2006; @Gross1967].
+In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967].
 HE is the most economically significant disease caused by any strain of THEV [@Beach2006].
@@
 ## TABLES AND FIGURES     
-![Fig.1](results/r/thev_genomic_map.png)  
+![Fig.1](results/thev_genomic_map.png)  
 **Figure 1.
@@
 pTP, DBP and 33K predicted to be spliced are shown as having tails.
-Shaded regions indicates regions containing genes (colored red) that are not conserved across adenovirus genera (i.e.
-"genus-specific").
+Shaded regions indicates regions containing "genus-specific" genes (colored red).
 Genes colored in blue are "genus-common".
 Gene colored in light green is conserved in all but Atadenoviruses.
-The U exon (light blue) is an incomplete gene present in almost all AdVs.
+The UXP (light blue) is an incomplete gene present in almost all AdVs.
+XXXXX add text to expalain region labels here or in the intro.

### 2023-06-19 manuscript_thev_transcriptome.Rmd
Update transcript filter script and manuscript

@@
 cov_72hr <- round(cov_72hr / 1e6, 1)
+
 total_mapped <- round(sum(cov_all$numreads) / 1e6, 1)

### 2023-06-19 scripts/r/bam_file_analysis.R

@@ -16,7 +16,7 @@ single_junc_stats <- map_dfr(single_jun_files, read_tsv,
 
 bulk_jun_files <- list.files("results/hisat2/bulk", full.names = T,
                              pattern = "\\w+\\.bed") %>% 
-  setNames(c("t12hrs", "t24hrs", "t4hrs", "t72hrs"))
+  setNames(c("12hpi", "24hpi", "4hpi", "72hpi"))
 
 bulk_junc_stats <- map_dfr(bulk_jun_files, read_tsv,
                            col_names = F,
@@ -28,10 +28,33 @@ bulk_junc_stats <- map_dfr(bulk_jun_files, read_tsv,
 bulk_sum_stats <- bulk_junc_stats %>% 
   group_by(timepoint) %>%
   summarize(total_junctions = n(),
+            reads10  = sum(read_count > 10),
+            reads100  = sum(read_count > 100),
+            reads1000  = sum(read_count > 1000),
             total_reads_supporting = sum(read_count),
-            mean_read_supporting = total_reads_supporting/total_junctions)
+            mean_read_supporting = total_reads_supporting/total_junctions) %>% 
+  mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>% 
+  arrange(total_junctions)
   
-stats_per_timepoint
+cov_all <- read_tsv("results/hisat2/coverage/bulk_coverage.txt",
+                    comment = "Coverage", show_col_types = FALSE) %>%
+  rename("organism" = "#rname") %>%
+  filter(organism != "#rname") %>%
+  mutate(timepoint = c("4hpi", "12hpi", "24hpi", "72hpi"),
+         timepoint = factor(timepoint,
+                            levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>%
+  map_at(c(2:9), as.numeric) %>%
+  as_tibble() %>% 
+  select(Timepoint = timepoint, "Total Mapped" = numreads, "Mean Depth" = meandepth)
   
-  
-  
+total_seq_reads <- read_table("results/hisat2/coverage/bulk_counts.txt",
+                              col_names = T, show_col_types = F)
+
+join_stats <- left_join(cov_all, bulk_sum_stats, by = c("Timepoint" = "timepoint")) %>% 
+  bind_cols(total_seq_reads) %>%
+  mutate(perc_map = (`Total Mapped`/total_reads) * 100) %>% 
[…]

### 2023-06-19 scripts/r/filter_real_transcripts.R

@@ -17,7 +17,7 @@ merged_gtf <- read_tsv("results/stringtie/all_merged.gtf",
                        col_names = FALSE,
                        show_col_types = FALSE) 
 
-duplicates <- 'gene_id "24S2.11"|gene_id "24S1.11"|gene_id "72S1.9"|gene_id "72S3.10"|gene_id "24S1.2"|transcript_id "24S3.2.5"|gene_id "12S1.2"|transcript_id "24S1.1.1"|gene_id "24S2.1"|transcript_id "24S2.2.5"|transcript_id "72S1.8.1"|transcript_id "72S2.8.1"|transcript_id "4S2.3.1"|transcript_id "72S1.10.1"|transcript_id "24S1.12.1"|transcript_id "72S2.9.1"'
+duplicates <- 'gene_id "24S2.11"|gene_id "24S1.11"|gene_id "72S1.9"|gene_id "72S3.10"|gene_id "24S1.2"|transcript_id "24S3.2.5"|gene_id "12S1.2"|transcript_id "24S1.1.1"|gene_id "24S2.1"|transcript_id "24S2.2.5"|transcript_id "72S1.8.1"|transcript_id "72S2.8.1"|transcript_id "4S2.3.1"|transcript_id "72S1.10.1"|transcript_id "24S1.12.1"|transcript_id "72S2.9.1"|transcript_id "72S1.1.1"|transcript_id "72S3.1.1"|transcript_id "24S3.1.1"|transcript_id "24S1.1.2"|transcript_id "12S1.1.1"|transcript_id "24S2.2.1"|transcript_id "4S1.4.1"'
 
 filter_real_transcripts <- merged_gtf %>% 
   filter(!str_detect(X9,"ref_gene_name")) %>% 

### 2023-07-18 manuscript_thev_transcriptome.Rmd
Generate summary info, accounting for host Continue writing manuscript Add more figures and data to paper

@@
 library(tidyverse)
+library(gt)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 
-# extract coverage and mapping information
-cov_all <- read_tsv("results/hisat2/coverage/bulk_coverage.txt",
-                    comment = "Coverage", show_col_types = FALSE) %>%
-  rename("organism" = "#rname") %>%
-  filter(organism != "#rname") %>%
-  mutate(timepoint = c("4hpi", "12hpi", "24hpi", "72hpi"),
-         timepoint = factor(timepoint,
-            levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>%
-  map_at(c(2:9), as.numeric) %>%
-  as_tibble()
+source("scripts/r/bam_file_analysis.R")
+cov_thev <- all_covs %>% filter(organism == "thev")
 
-cov_4hr <- cov_all %>% filter(timepoint == "4hpi") %>%
-              select(numreads) %>% pull()
-cov_72hr <- cov_all %>% filter(timepoint == "72hpi") %>%
-              select(numreads) %>% pull()
+cov_4hr <- cov_thev %>% filter(timepoint == "4hpi") %>%
+              select(total_mapped) %>% pull()
+cov_72hr <- cov_thev %>% filter(timepoint == "72hpi") %>%
+              select(total_mapped) %>% pull()
 cov_72hr <- round(cov_72hr / 1e6, 1)
 
-total_mapped <- round(sum(cov_all$numreads) / 1e6, 1)
+total_mapped <- round(sum(cov_thev$total_mapped) / 1e6, 1)
 
-load_count <- read_table("results/hisat2/coverage/bulk_counts.txt",
-                         col_names = T, show_col_types = F) %>% pull()
-tot_count <- round(mean(load_count) / 1e6, 1)
+avg_tot_count <- round(mean(total_reads$total_reads) / 1e6, 1)
 ```
@@
 Currently, there are three recognized members of the genus SiAdV: frog adenovirus 1, raptor adenovirus 1, and turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009].
-Members of SiAdV have the smallest genome size (~26 kb) and gene content (~23 genes) of all known AdVs, and many “genus-specific” putative genes of unknown functions have been annotated [@Harrach2008; @Kovács2011].
-The genomic map of THEV showing details of the "genus-specific" and "genus-common" genes, and the gene distribution patterns described above is shown in __Figure 1__.
+Members of SiAdV have the smallest genome size (~26 kb) and gene content (~23 genes) of all known AdVs, and many “genus-specific” putative genes of unknown functions have been annotated (see __Figure 1__)[@Harrach2008; @Kovács2011; @Davison2003].
 
@@
 However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
-To identify such viral factors, a well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.
+A well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.
 
 Myriads of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
-However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generally applied to all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate units (pIX and IVa2), and one major late unit (MLTU), generating five families of late mRNAs (L1-L5).
+However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
+MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate units (pIX and IVa2), and one major late unit (MLTU), which generates five families of late mRNAs (L1-L5).
 An additional gene (UXP or U exon) is located on the reverse strand.
@@
 The MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
-There is an alternate 5' three non-coding exons present in varying amounts on a subset of MLTU mRNAs (known as the x-, y- and z-leaders).
+There is also an alternate 5' three non-coding exons present in varying amounts on a subset of MLTU mRNAs (known as the x-, y- and z-leaders).
 Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
@@
 In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
-Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36 using `FastQC`) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
-The data generated from our paired-end sequencing experiment should thus be reliable.
+Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
+The generated data from our paired-end sequencing experiment should thus be reliable.
 \newpage
@@
 A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
-Therefore, infected MDTC-RP19 cells were harvested in triplicates at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing experiment yielded an average of `r tot_count` million total reads of `r seq_len`bp in length per time-point.
-A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
-Also, the mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__ and __Figure 2__).
+Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
+Our paired-end RNA sequencing experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point.
+Using the `HISAT2` alignment program, a total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
+The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2__).
+After mapping, we identified an overall total of `r bulk_junc_stats %>% nrow()` THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
+The substantial increases in mapping reads to the THEV genome and splice junctions from earlier time-points to later time-points corresponds to the progression of the infection and correlates with our qPCR assay quantifying the total number of virus genome copies over time (__Figure 3__).
+The complete list of splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
+XXXXXX**.
 
@@
 A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
-The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL.
+The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al*[@Mahsoub2017] with modifications.
 Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA sequencing.
@@
 ### Computational Analysis of RNA Sequencing Data: Mapping and Transcript characterization
-Analysis of our sequencing reads were analyzed following a well established general outline described by Pertea _et al_ [@Pertea2016].
-Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to acheive an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings except increasing the CPU cores to 10 without relying on known splice sites.
-The generated `BAM` files from each infection time-point were fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted genes of THEV as a guide.
+Analysis of our sequence reads were analyzed following a well established protocol described by Pertea _et al_ [@Pertea2016], using `SNAKEMAKE 7.24.0` to drive the pipeline.
+Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
+Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) and *Meleagris gallopavo* (https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings without relying on known splice sites.
+The generated `BAM` files from each infection time-point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted ORFs of THEV as a guide.
 A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
 
-### Validation of Novel Splice Sites 
-All splice sites identified in this work are novel except one splice site predicted for pTP, DBP, and 33K each.
-However, these predictions fell short of the full splicing of these genes and were not experimentally validated.
-We designed primers that crossed a range of novel exon–exon boundaries for all transcripts in a transcription units with their respective universal primers (~~supplementary, PCR methods~~).
-After first-strand cDNA synthesis with Thermofishers' SuperScript™ III First-Strand Synthesis System (`#18080051`), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme-ligation method and Sanger sequenced at `Eton Bioscience, Inc, San Diego, CA` to validate these splice junctions at the sequence level.
+### Validation of Novel Splice Junctions 
+All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
+However, these predicted splice junctions have not been experimentally validated hitherto, and we identified additional novel splice junctions beside the predicted junctions, giving a more complete picture of the transcripts.
+
+The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in ~~Table###1~~.
+We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit with their respective universal primers (~~supplementary, PCR methods~~).
+Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
+After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method and Sanger sequenced to validate these splice junctions at the sequence level.
 
@@
 ## ACKNOWLEDGMENTS  
-
+LC Sciences
+`Eton Bioscience, Inc, San Diego, CA`
 \newpage
@@
 ## TABLES AND FIGURES     
-![Fig.1](results/thev_genomic_map.png)  
+![](results/thev_genomic_map.png)
+
 **Figure 1.
@@
 The UXP (light blue) is an incomplete gene present in almost all AdVs.
-XXXXX add text to expalain region labels here or in the intro.
+XXXXX add text to explain region labels here or in the introduction.
+
+```{r fig.width=12}
+tab1 %>% 
+  gt(rowname_col = "Metric") %>% 
+  tab_header(title = md("**Table 1**"),
+             subtitle = "Summary of sequence alignment metrics") %>%
+  opt_align_table_header(align = "left") %>% 
+  fmt_number(suffixing = T,
+             rows = everything(),
+             columns = everything()) %>% 
+  cols_width(Metric ~ px(150)) %>% 
+  opt_row_striping(row_striping = T) %>% 
+  tab_options(table.layout = "auto",
+              table.align = "left",
+              column_labels.font.size = "18px",
+              column_labels.font.weight = "bold",
+              table_body.vlines.style = "solid") %>% 
+  tab_stubhead(label = md("Metric"))
+
+```
+
+![](results/r/figures/patch_alltimes.png)
+
+**Figure 2. _Sequence reads mapping to THEV genome by time-point_**. Description ######
+
+![](results/r/figures/thev_growth_curve.png)
+**Figure 3. _One-step growth of THEV_**. Description###. GCN: genome copy number.

### 2023-07-18 scripts/r/bam_file_analysis.R

@@ -1,5 +1,6 @@
 
 library(magrittr)
+library(glue)
 library(tidyverse)
 
 
@@ -32,29 +33,48 @@ bulk_sum_stats <- bulk_junc_stats %>%
             reads100  = sum(read_count > 100),
             reads1000  = sum(read_count > 1000),
             total_reads_supporting = sum(read_count),
-            mean_read_supporting = total_reads_supporting/total_junctions) %>% 
+            mean_read_supporting = total_reads_supporting/total_junctions,
+            organism = "thev") %>% 
   mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>% 
   arrange(total_junctions)
-  
-cov_all <- read_tsv("results/hisat2/coverage/bulk_coverage.txt",
-                    comment = "Coverage", show_col_types = FALSE) %>%
-  rename("organism" = "#rname") %>%
-  filter(organism != "#rname") %>%
-  mutate(timepoint = c("4hpi", "12hpi", "24hpi", "72hpi"),
-         timepoint = factor(timepoint,
-                            levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>%
-  map_at(c(2:9), as.numeric) %>%
-  as_tibble() %>% 
-  select(Timepoint = timepoint, "Total Mapped" = numreads, "Mean Depth" = meandepth)
-  
-total_seq_reads <- read_table("results/hisat2/coverage/bulk_counts.txt",
-                              col_names = T, show_col_types = F)
 
-join_stats <- left_join(cov_all, bulk_sum_stats, by = c("Timepoint" = "timepoint")) %>% 
-  bind_cols(total_seq_reads) %>%
-  mutate(perc_map = (`Total Mapped`/total_reads) * 100) %>% 
-  select(Timepoint, "Total Reads" = total_reads, `Total Mapped`, "Mapped (%)" = perc_map, `Mean Depth`,
-         "Splice Junctions" = total_junctions, "Total Junction Reads" = total_reads_supporting,
-         reads10, reads100, reads1000) %>%
-  map_at(c(2), format, big.mark = ",") %>% as_tibble()
+total_reads <- read_table("results/hisat2/coverage/bulk_counts.txt",
+                          col_names = T, show_col_types = F)
+
+### find all the coverage files
[…]

### 2023-07-18 scripts/r/filter_real_transcripts.R

@@ -17,12 +17,13 @@ merged_gtf <- read_tsv("results/stringtie/all_merged.gtf",
                        col_names = FALSE,
                        show_col_types = FALSE) 
 
-duplicates <- 'gene_id "24S2.11"|gene_id "24S1.11"|gene_id "72S3.10"|transcript_id "24S1.2.1"|transcript_id "24S3.2.5"|gene_id "12S1.2"|transcript_id "24S1.1.1"|gene_id "24S2.1"|transcript_id "24S2.2.5"|transcript_id "72S1.8.1"|transcript_id "72S2.8.1"|transcript_id "4S2.3.1"|transcript_id "72S1.10.1"|transcript_id "24S1.12.1"|transcript_id "72S2.9.1"|transcript_id "72S1.1.1"|transcript_id "72S1.2.2"|transcript_id "72S3.1.1"|transcript_id "24S3.1.1"|transcript_id "24S1.1.2"|transcript_id "12S1.1.1"|transcript_id "24S2.10.1"|transcript_id "12S1.10.2"|transcript_id "24S2.2.1"|transcript_id "4S1.4.1"'
+duplicates <- 'gene_id "24S2.11"|gene_id "24S1.11"|gene_id "72S3.10"|transcript_id "24S1.2.1"|transcript_id "24S3.2.5"|gene_id "12S1.2"|transcript_id "24S1.1.1"|gene_id "24S2.1"|transcript_id "24S2.2.5"|transcript_id "72S1.8.1"|transcript_id "72S2.8.1"|transcript_id "4S2.3.1"|transcript_id "72S1.10.1"|transcript_id "24S1.12.1"|transcript_id "72S2.9.1"|transcript_id "72S1.1.1"|transcript_id "72S3.2.1"|transcript_id "72S3.1.1"|transcript_id "24S3.1.1"|transcript_id "24S1.1.2"|transcript_id "12S1.1.1"|transcript_id "24S2.10.1"|transcript_id "12S1.10.2"|transcript_id "24S2.2.1"|transcript_id "4S1.4.1"'
 
 filter_real_transcripts <- merged_gtf %>% 
   filter(!str_detect(X9,"ref_gene_name")) %>% 
   filter(!str_detect(X9, duplicates)) %>%
-  arrange(X4)
+  group_by(X7) %>% 
+  arrange(X4, .by_group = T)
 
 # save modified .gtf
 write.table(filter_real_transcripts, "results/stringtie/all_real_transcripts_merged.gtf",

### 2023-07-18 scripts/r/merge_all_gtf.R

@@ -1,18 +1,0 @@
-######## Merge gtf files of all time-points from stringtie ------
-
-library(tidyverse)
-
-all_gtfs <- list.files(path = "results/stringtie",
-                       pattern = "[a-z_]+\\d+[a-zA-Z]+\\d\\.gtf",
-                       full.names = TRUE)
-
-names(all_gtfs) <- c("t12s1", "t12s2", "t24s1", "t24s2", "t24s3",
-                     "t4s1", "t4s2", "t4s3", "t72s1", "t72s2", "t72s3")
-
-all_merged <- map_dfr(all_gtfs, read_tsv, comment = "#", col_names = FALSE)
-
-write.table(all_merged, "results/stringtie/all_real_transcripts_mergedRR.gtf",
-            col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
-
-
-

### 2023-07-18 scripts/r/thev_cov_depth.R

@@ -20,7 +20,7 @@ unlink(files, recursive = FALSE, force = FALSE)
 
 ### find all the depth files
 all_depth_files <- list.files("results/hisat2/coverage",
-                              pattern = "thev_+\\d+[a-z]+\\.txt",
+                              pattern = "thev_\\d+[a-z]+\\.txt",
                               full.names = TRUE) %>% 
   setNames(c("12hpi", "24hpi", "4hpi", "72hpi"))
 
@@ -74,21 +74,21 @@ each_plot <- all_depths %>%
 
 # save plot for each time-point
 
-ggsave("depth_4hrs.pdf",
-       plot = each_plot$`4hpi`, path = "results/r/figures",
-       width = 10, height = 5)
-
-ggsave("depth_12hrs.pdf",
-       plot = each_plot$`12hpi`, path = "results/r/figures",
-       width = 10, height = 5)
-
-ggsave("depth_24hrs.pdf",
-       plot = each_plot$`24hpi`, path = "results/r/figures",
-       width = 10, height = 5)
-
-ggsave("depth_72hrs.pdf",
-       plot = each_plot$`72hpi`, path = "results/r/figures",
-       width = 10, height = 5)
+# ggsave("depth_4hrs.png",
+#        plot = each_plot$`4hpi`, path = "results/r/figures",
+#        width = 10, height = 5)
+# 
+# ggsave("depth_12hrs.png",
+#        plot = each_plot$`12hpi`, path = "results/r/figures",
+#        width = 10, height = 5)
+# 
+# ggsave("depth_24hrs.png",
+#        plot = each_plot$`24hpi`, path = "results/r/figures",
+#        width = 10, height = 5)
+# 
+# ggsave("depth_72hrs.png",
+#        plot = each_plot$`72hpi`, path = "results/r/figures",
+#        width = 10, height = 5)
 
 # genomic map plot
 genome <- make_genomic_map("raw_files/annotations/THEVannotated_genesOnly.bed")
@@ -108,9 +108,9 @@ p_alltime <- (each_plot$`4hpi`/each_plot$`12hpi`/each_plot$`24hpi`/each_plot$`72
                               size = 16),
     plot.title.position = "panel")
 
-ggsave("patch_alltimes.pdf",
+ggsave("patch_alltimes.png",
        plot = p_alltime, path = "results/r/figures",
-       width = 10, height = 14)
+       width = 12, height = 14, dpi = 1000)
 
 
 
@@ -153,44 +153,56 @@ compare_all <- all_depths %>%
[…]

### 2023-07-18 scripts/r/thev_genomic_map.R

@@ -22,7 +22,7 @@ make_genomic_map <- function(bedfile){
            exon1end = ifelse(blockCount > 1, (start + exon1Size), thickEnd),
            exon2start = thickEnd - exon2Size,
            exon2end = thickEnd,
-           color = ifelse(strand == "+", "#B897A4", "#8B62D1"),
+           color = ifelse(strand == "+", "#FF0000", "skyblue"),
            gene_name = case_match(gene_name,
                                   "33K_spliced" ~ "33K",
                                   "pVIII gene" ~ "pVIII",
@@ -67,7 +67,7 @@ make_genomic_map <- function(bedfile){
           )
 }
 
-
+make_genomic_map("raw_files/annotations/THEVannotated_genesOnly.bed")
 
 ## position the plus strand genes above genome line and minus strand genes below
 make_genomic_map2 <- function(bedfile){

### 2023-07-18 scripts/r/thev_growthcurve.R

@@ -1,0 +1,194 @@
+#!/usr/bin/env Rscript
+
+library(readxl)
+library(ggsci)
+library(glue)
+library(lubridate)
+library(tidyverse)
+
+exp2 <- "raw_files/wetlab_data/thev_growthcurve04_2023.xls"
+replicate_data <- read_excel(exp2,
+                          sheet = "Results",
+                          skip = 6,
+                          trim_ws = TRUE) %>% 
+  rename(well = "Well", sample_name = "Sample Name", conc = "Quantity") %>%
+  select(well, sample_name, conc) %>% 
+  drop_na(sample_name) %>% 
+  mutate(sample_name = str_replace(string = sample_name,
+                                   pattern = "(\\d{2})[a-z]{3}(\\w{2})",
+                                   replacement = "\\2_\\1")) %>% 
+  separate(sample_name, into = c("condition", "hrs_pi"),
+           sep = "_") %>% 
+  mutate(condition = ifelse(str_detect(condition, "S"), "Inf", "Neg"),
+         inf_hrs = paste0(condition, "_", hrs_pi),
+         inf_hrs = case_match(inf_hrs,
+                              "Inf_00" ~ "Inf_0",
+                              "Neg_00" ~ "Neg_0",
+                              .default = inf_hrs),
+         hrs_pi = as.numeric(hrs_pi)) %>% 
+  select(condition, conc, hrs_pi, inf_hrs)
+
+
+plot_prepped <- replicate_data %>%
+  group_by(inf_hrs, hrs_pi) %>% 
+  summarize(mean_conc = mean(conc), 
+            mean_conc_per_mL = (mean_conc * 10 * 1000),
+            replicates = n(),
+            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000,
+            .groups = "drop") %>% 
+  mutate(treatment = str_replace(inf_hrs, "([a-zA-Z]{3})_\\d{1,2}", "\\1"))
+
+#================= visualize data just data from exp 2 ========================
+#=================                                     ========================
+# plot 1 ---------------------
+# plot_prepped %>% 
+#   ggplot(aes(hrs_pi, mean_conc_per_mL, color = treatment)) +
+#   geom_errorbar(aes(ymax = mean_conc_per_mL + stderr_conc_perML,
+#                     ymin = mean_conc_per_mL - stderr_conc_perML),
+#                 width = 0.8, show.legend = F,
[…]

### 2023-07-20 manuscript_thev_transcriptome.Rmd
Use R to make thev ORF mapand update manuscript

@@
 However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate units (pIX and IVa2), and one major late unit (MLTU), which generates five families of late mRNAs (L1-L5).
+MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU), which generates five families of late mRNAs (L1-L5).
 An additional gene (UXP or U exon) is located on the reverse strand.
@@
 Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point.
+Our paired-end RNA sequencing (RNA-Seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point.
 Using the `HISAT2` alignment program, a total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
 The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2__).
-After mapping, we identified an overall total of `r bulk_junc_stats %>% nrow()` THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
-The substantial increases in mapping reads to the THEV genome and splice junctions from earlier time-points to later time-points corresponds to the progression of the infection and correlates with our qPCR assay quantifying the total number of virus genome copies over time (__Figure 3__).
+From the mapped reads, we identified an overall total of `r bulk_junc_stats %>% nrow()` THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
+The substantial increases in splice junctions and mapping reads to the THEV genome from earlier time-points to later time-points corresponds to the progression of the infection and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 3__).
+Using `STRINGTIE`, an assembler of RNA-Seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the location of the predicted ORFs within the viral genome.
+The transcripts were consolidated to generate the final transcriptome of THEV (~~Maybe put the figure of the final transcriptome here?
+XXXXXXXXXXXXXXX~~).
+
 The complete list of splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
@@
 The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al*[@Mahsoub2017] with modifications.
-Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA sequencing.
+Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-Seq.
 A second infection was done but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
@@
 The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
-Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA sequencing library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
+Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-Seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
 Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.
@@
 ## TABLES AND FIGURES     
-![](results/thev_genomic_map.png)
-
+![](results/r/figures/thev_orf_map.png)
 **Figure 1.
@@
 pTP, DBP and 33K predicted to be spliced are shown as having tails.
-Shaded regions indicates regions containing "genus-specific" genes (colored red).
+Shaded regions indicate regions containing "genus-specific" genes (colored red).
 Genes colored in blue are "genus-common".
@@
 The UXP (light blue) is an incomplete gene present in almost all AdVs.
-XXXXX add text to explain region labels here or in the introduction.
+Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.
 
-```{r fig.width=12}
+```{r}
 tab1 %>% 

### 2023-07-20 scripts/r/thev_genomic_map.R

@@ -50,7 +50,7 @@ make_genomic_map <- function(bedfile){
                        breaks = seq(0,26000,2000), 
                        labels = paste0(seq(0,26, 2), "kb")) +
     scale_y_continuous(expand = c(0, 0),
-                       limits = c(0, 1.6)) +
+                       limits = c(0, 20)) +
     theme(plot.margin = margin(rep(15, 4)),
           plot.background = element_blank(),
           panel.background = element_blank(),
@@ -65,77 +65,4 @@ make_genomic_map <- function(bedfile){
           axis.line.x = element_blank(),
           axis.ticks.y = element_blank()
           )
-}
-
-make_genomic_map("raw_files/annotations/THEVannotated_genesOnly.bed")
-
-## position the plus strand genes above genome line and minus strand genes below
-make_genomic_map2 <- function(bedfile){
-  thev_genome2 <- read_tsv(bedfile,
-                          col_names = FALSE,
-                          col_types = "ciiciciicicc") %>% 
-    set_colnames(c("chr", "start", "end", "gene_name", "score", "strand", "thickStart",
-                   "thickEnd", "color", "blockCount", "blockSizes", "blockStarts")) %>% 
-    mutate(exon1Size = str_replace(blockSizes, pattern = "(\\d+),\\d+", replacement = "\\1"),
-           exon1Size = as.numeric(exon1Size),
-           exon2Size = str_replace(blockSizes, pattern = "\\d+,(\\d+)", replacement = "\\1"),
-           exon2Size  = as.numeric(exon2Size),
-           exon2Size = ifelse(exon2Size == exon1Size, NA_real_, exon2Size),
-           exon1start = thickStart,
-           exon1end = ifelse(blockCount > 1, (start + exon1Size), thickEnd),
-           exon2start = thickEnd - exon2Size,
-           exon2end = thickEnd,
-           color = ifelse(strand == "+", "#B897A4", "#8B62D1"),
-           gene_name = case_match(gene_name,
-                                  "33K_spliced" ~ "33K",
-                                  "pVIII gene" ~ "pVIII",
-                                  .default = gene_name),
-           ypos = ifelse(strand == "-", c(2, 3), c(6, 7)),
-           ypos = ifelse(gene_name == "22K", 8, ypos))
-  
-  spliced2 <- thev_genome2 %>% filter(blockCount > 1)
-  
-  genome_ruler <- tibble(x = seq(0,26000,2000),
-                         xend = seq(0,26000,2000),
[…]

### 2023-07-20 scripts/r/thev_orf_map.R

@@ -1,0 +1,108 @@
+#!/usr/bin/env Rscript
+
+
+library(magrittr)
+library(ggtext)
+library(tidyverse)
+
+## position the plus strand genes above genome line and minus strand genes below
+make_genomic_map2 <- function(bedfile){
+  genus_specific <- c("ORF1", "Hyd", "E3", "ORF7", "ORF8")
+  thev_genome2 <- read_tsv(bedfile,
+                          col_names = FALSE,
+                          col_types = "ciiciciicicc") %>% 
+    set_colnames(c("chr", "start", "end", "gene_name", "score", "strand", "thickStart",
+                   "thickEnd", "color", "blockCount", "blockSizes", "blockStarts")) %>% 
+    mutate(exon1Size = str_replace(blockSizes, pattern = "(\\d+),\\d+", replacement = "\\1"),
+           exon1Size = as.numeric(exon1Size),
+           exon2Size = str_replace(blockSizes, pattern = "\\d+,(\\d+)", replacement = "\\1"),
+           exon2Size  = as.numeric(exon2Size),
+           exon2Size = ifelse(exon2Size == exon1Size, NA_real_, exon2Size),
+           exon1start = thickStart,
+           exon1end = ifelse(blockCount > 1, (start + exon1Size), thickEnd),
+           exon2start = thickEnd - exon2Size,
+           exon2end = thickEnd,
+           color = "#6D58F5",
+           color = ifelse(gene_name %in% genus_specific, "red", color),
+           color = ifelse(gene_name == "U exon", "skyblue", color),
+           color = ifelse(gene_name == "22K", "green", color),
+           gene_name = case_match(gene_name,
+                                  "33K_spliced" ~ "33K",
+                                  "pVIII gene" ~ "pVIII",
+                                  .default = gene_name),
+           ypos = ifelse(strand == "-", c(22, 23), c(26, 27)),
+           ypos = ifelse(gene_name == "22K", 28, ypos))
+  
+  spliced2 <- thev_genome2 %>% filter(blockCount > 1)
+  
+  genome_ruler <- tibble(x = seq(0,26000,2000),
+                         y = 24.8,
+                         yend = 25.3,
+                         lab = paste0(seq(0,26, 2), "kb"))
+  
+  shade_regions <- tribble(~xmin, ~xmax, ~ymin, ~ymax,
+                           0, thev_genome2$end[2], 20, 30,
+                           thev_genome2$start[19], thev_genome2$end[19], 20, 30,
[…]

### 2023-07-21 manuscript_thev_transcriptome.Rmd
Update scripts to generate pertinent info for manuscript

@@
 cov_4hr <- cov_thev %>% filter(timepoint == "4hpi") %>%
-              select(total_mapped) %>% pull()
+              select(total_mapped) %>% pull() %>% as.numeric(.)
 cov_72hr <- cov_thev %>% filter(timepoint == "72hpi") %>%
-              select(total_mapped) %>% pull()
+              select(total_mapped) %>% pull() %>% as.numeric(.)
 cov_72hr <- round(cov_72hr / 1e6, 1)
 
-total_mapped <- round(sum(cov_thev$total_mapped) / 1e6, 1)
+total_mapped <- round(sum(as.numeric(cov_thev$total_mapped)) / 1e6, 1)
 
@@
   opt_align_table_header(align = "left") %>%
-  fmt_number(suffixing = T,
-             rows = everything(),
-             columns = everything()) %>% 
   cols_width(Metric ~ px(150)) %>% 

### 2023-07-21 scripts/r/bam_file_analysis.R

@@ -13,8 +13,30 @@ single_junc_stats <- map_dfr(single_jun_files, read_tsv,
                              show_col_types = F,
                              .id = "timepoint") %>% 
   set_colnames(c("timepoint", "chrom", "start", "end", "junc_name", "read_count", "strand",
-                 "thickStart", "thickEnd", "color", "exons", "exon_sizes", "exon_starts"))
+                 "thickStart", "thickEnd", "color", "exons", "exon_sizes", "exon_starts")) %>% 
+  arrange(start, end)
 
+single_junclist <- single_junc_stats %>% group_by(start, end) %>% summarise(repeated = n(),
+                                                                            .groups = "drop")
+ 
+single_sum_stats <- single_junc_stats %>% 
+  mutate(timepoint = case_when(timepoint %in% c("t72s1", "t72s2", "t72s3") ~ "72hpi",
+                               timepoint %in% c("t24s1", "t24s2", "t24s3") ~ "24hpi",
+                               timepoint %in% c("t12s1", "t12s3") ~ "12hpi",
+                               timepoint %in% c("t4s1", "t4s2", "t4s3") ~ "4hpi",
+                               .default = timepoint)) %>% 
+  group_by(timepoint) %>%
+  summarize(total_junctions = n(),
+            reads10  = sum(read_count > 10),
+            reads100  = sum(read_count > 100),
+            reads1000  = sum(read_count > 1000),
+            total_reads_supporting = sum(read_count),
+            mean_read_supporting = total_reads_supporting/total_junctions,
+            organism = "thev") %>%
+  # mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>% 
+  arrange(total_junctions)
+
+# ============================BULK=============================================
 bulk_jun_files <- list.files("results/hisat2/bulk", full.names = T,
                              pattern = "\\w+\\.bed") %>% 
   setNames(c("12hpi", "24hpi", "4hpi", "72hpi"))
@@ -24,7 +46,11 @@ bulk_junc_stats <- map_dfr(bulk_jun_files, read_tsv,
                            show_col_types = F,
[…]

### 2023-08-14 manuscript_thev_transcriptome.Rmd
splice-sites extracted for indexing genome was inaccurate; custom script used to extract splice-sites, and whole pipeline rerun
GFF file modfied to allow transcripts to hold ORF names

New scripts to analyze splice sites counts
and transcript abundances with ballgown and python

figure of hAdV5 splice map downloaded for comparison

New splice junctions validated with Sanger sequencing

@@
   word_document: default
-  pdf_document: default
+  html_document: default
 geometry: margin=1in
@@
 library(gt)
+library(tibble)
+library(scales)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 
-```{r inline_values}
+```{r inline_values, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
 
@@
 
+## load in variables to be used inline 
 source("scripts/r/bam_file_analysis.R")
+source("scripts/r/thev_splicing_fullMap.R")
+
 cov_thev <- all_covs %>% filter(organism == "thev")
@@
 avg_tot_count <- round(mean(total_reads$total_reads) / 1e6, 1)
+
+### inline code for figure 2: depth graph
+dep_4 <- as.numeric(tab1$"4h.p.i"[4])
+dep_72 <- as.numeric(str_replace(tab1$"72h.p.i"[4], ",", "")) %>% comma(.)
+
+## inline code of junction stats
+tot_jun_4 <- tab1$`4h.p.i`[5]
+tot_jun_72 <- tab1$`72h.p.i`[5]
+mean_juncreads_4 <- tab1$`4h.p.i`[7]
+mean_juncreads_72 <- round(as.numeric(tab1$`72h.p.i`[7]), 1)
+max_junread72 <- bulk_junc_stats %>% filter(timepoint == "72hpi") %>%
+  pull(read_count) %>% max(.) %>% comma(.)
+
 ```
@@
 
-Virulent strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants.
-They infect via the fecal-oral route, and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
+Virulent strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
 In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967].
@@
 However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
-A well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.
+A well-characterized transcriptome of THEV is required to enable the next leap forward in THEV research - experimentation with specific viral genes that may mediate IS.
 
@@
 Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
-Thus, the MLTU produces a complex repertoire of mRNA with diverse 5'-UTRs, spliced onto different 3' coding exons grouped into five different 3'-end classes (L1-L5).
-Each transcription unit contains its own promoter that drives the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
+Thus, the MLTU produces a complex repertoire of mRNA with diverse 5'-UTRs spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5).
+Each transcription unit contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
+Almost all AdV mRNAs are generated by the excision of one or more introns and most of these introns are located in the 5' or 3' UTRs of pre-mRNA.
+Thus the viral introns scarcely interrupt the open reading frames (ORFs) [@Davison2003; @Zhao2014].
 
-Almost all AdV mRNAs are generated by the excision of one or more introns and most of these introns are located in the 5' or 3' UTRs of pre-mRNA.
-Thus the viral introns do only in a few cases interrupt the open reading frames (ORFs) [@Davison2003; @Zhao2014].
-The development of high throughput sequencing methods has facilitated the discovery of many novel transcribed regions and splicing isoforms.
+High throughput sequencing methods have facilitated the discovery of many novel transcribed regions and splicing isoforms.
 It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014].
-In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
+In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS vaccine strain) during different phases of the infection, yielding the first THEV splicing map.
 Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
@@
 Our paired-end RNA sequencing (RNA-Seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point.
-Using the `HISAT2` alignment program, a total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
+Using the `HISAT2` [@Pertea2016] alignment program, a total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
 The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2__).
 From the mapped reads, we identified an overall total of `r bulk_junc_stats %>% nrow()` THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
-The substantial increases in splice junctions and mapping reads to the THEV genome from earlier time-points to later time-points corresponds to the progression of the infection and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 3__).
-Using `STRINGTIE`, an assembler of RNA-Seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the location of the predicted ORFs within the viral genome.
-The transcripts were consolidated to generate the final transcriptome of THEV (~~Maybe put the figure of the final transcriptome here?
-XXXXXXXXXXXXXXX~~).
-
+For example all the `r tot_jun_4` unique junctions at 4 h.p.i had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads/junction.
+Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having as high as `r max_junread72` reads in support.
+The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes the progression of the infection and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 3__).
+Using `StringTie` [@Pertea2016], an assembler of RNA-Seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
+In the final consolidated transcriptome of THEV generated from transcripts from all time points, we counted a total of `r nrow(combined_gtf)` transcripts all of which are novel.
+Although some exons in some transcripts match the predicted ORFs of THEV exactly, most of the exons are longer, spanning multiple predicted ORFs (__Figure 4__).
 The complete list of splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
 XXXXXX**.
+
+**Early Region 1 (E1) transcripts**.
+This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell.
+The host transcription machinery is lobbied for the transcription of the region.
+No viral proteins are available at this stage; hence, host transcription factors play the key roles of mobilizing the transcription machinery.
+After their translation, the E1 proteins in concert with the host transcription factors activate the other viral promoters [@Guimet2016].
+We identified four novel transcripts in this region ~~and also validated the predicted ORF (sialidase; ORF1)~~.
+
+Early Region 2A (E2A) transcripts.
+
+Early Region 2B (E2B) transcripts.
+
+Early Region 3 (E3) transcripts.
+
+Early Region 4 (E4) transcripts.
+
+Intermediate Region (IM) transcripts.
+
+Major Late Promoter Region (MLP) transcripts.
 
@@
 The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium with 10% fetal bovine serum (FBS), 20% chicken serum (ChS), 5% tryptose phosphate broth (TPB), and 1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin), at 41^o^C in a humidified atmosphere with 5% CO~2~.
-When infected, the cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and  1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin).
+Infected cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and  1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin).
 A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
@@
 Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-Seq.
-A second infection was done but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
+The infection was repeated but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
 
@@
 ```{r}
-tab1 %>% 
-  gt(rowname_col = "Metric") %>% 
-  tab_header(title = md("**Table 1**"),
-             subtitle = "Summary of sequence alignment metrics") %>%
-  opt_align_table_header(align = "left") %>%
-  cols_width(Metric ~ px(150)) %>% 
-  opt_row_striping(row_striping = T) %>% 
-  tab_options(table.layout = "auto",
-              table.align = "left",
-              column_labels.font.size = "18px",
-              column_labels.font.weight = "bold",
-              table_body.vlines.style = "solid") %>% 
-  tab_stubhead(label = md("Metric"))
-
+kable(tab1)
 ```
@@
 
-**Figure 2. _Sequence reads mapping to THEV genome by time-point_**. Description ######
+**Figure 2.
+_Per base coverage of sequence reads mapping to THEV genome by time point_**.
+The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point show remarkable difference in terms of quantities.
+There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection.
+Unexpectedly, the pileup of reads seems consistently skewed over similar regions of the genome.
+We could speculate that the temporal gene expression regulation of THEV is different from MAdVs or this could simply mean that the infection was not well synchronized.
+However, the relative proportions over these similar regions shows some variation over time.
 
 ![](results/r/figures/thev_growth_curve.png)
-**Figure 3. _One-step growth of THEV_**. Description###. GCN: genome copy number.
+**Figure 3.
+_One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
+After infecting cells at an MOI of 100 GCN/cell, triplicates of harvested infected cells were quantified with an in-house qPCR assay measuring the total copies of THEV genome.
+There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured.
+The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i, probably due to high cell death.
+GCN: genome copy number.
+
+![](results/r/figures/thev_spliced_map.png)
+**Figure 4a.
+__Full transcriptome of THEV__**.
+THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map).
+Transcripts belonging to the same transcription unit (TU) are located in close proximity on the genome and are color coded and labeled in this figure as such.
+The organization of TUs in the THEV genome is unsurprisingly similar to MAdVs; however, the MAdV genome shows significantly more transcripts.
+The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark grey, E4 - green, MLP - blue.
+Predicted ORFs are also indicated here, colored light grey.
+
+![](results/r/figures/thev_patched_timepoints_spliced_map.png)
+**Figure 4b. __THEV transcripts identified at given time points__**. Transcripts are color coded as explained in Fig.4a.

### 2023-08-14 scripts/python/pile_reads_to_orfs.py

@@ -1,0 +1,86 @@
+import pysam
+import csv
+from collections import defaultdict
+
+# Set the file paths for the bam and gtf files
+bam_files = ["results/hisat2/bulk/subsetTHEV_4hrs.bam", \
+"results/hisat2/bulk/subsetTHEV_12hrs.bam", \
+"results/hisat2/bulk/subsetTHEV_24hrs.bam", \
+"results/hisat2/bulk/subsetTHEV_72hrs.bam"]
+gtf_file = "raw_files/annotations/thev_predicted_genes.gtf"
+
+# Iterate over the bam files
+for bam_file in bam_files:
+    # Initialize a dictionary to store the counts and coordinates for each gene
+    gene_counts = defaultdict(lambda: {"count": 0, "start": float("inf"), "end": float("-inf"), "size": 0})
+    
+    # Read in the bam file
+    bam = pysam.AlignmentFile(bam_file, "rb")
+    
+    # Iterate over the records in the gtf file
+    with open(gtf_file, "r") as gtf:
+        for line in gtf:
+            # Skip comment lines
+            if line.startswith("#"):
+                continue
+            
+            # Split the line into fields
+            fields = line.strip().split("\t")
+            
+            # Check if the record is a gene feature
+            if fields[2] == "gene":
+                # Get the gene ID from the attributes field
+                attributes = dict(item.split(" ") for item in fields[8].split("; "))
+                gene_name = attributes["Name"].strip("\"")
+                
+                # Get the chromosome, start, and end positions of the gene
+                chrom = fields[0]
+                start = int(fields[3])
+                end = int(fields[4])
+                
+                # Update the start and end coordinates for the gene
+                gene_counts[gene_name]["start"] = min(gene_counts[gene_name]["start"], start)
+                gene_counts[gene_name]["end"] = max(gene_counts[gene_name]["end"], end)
+                
+                # Calculate the size of the gene using the blockSizes attribute
+                block_sizes = [int(size.strip("\"")) for size in attributes["blockSizes"].split(",")]
+                gene_counts[gene_name]["size"] = sum(block_sizes)
+                
+                # Count the number of reads mapping to the gene
+                for read in bam.fetch(chrom, start, end):
+                    gene_counts[gene_name]["count"] += 1
+    
+    # Calculate the total number of reads in the bam file
+    total_reads = sum(data["count"] for data in gene_counts.values())
+    
[…]

### 2023-08-14 scripts/r/ballgown.R

@@ -1,0 +1,115 @@
+
+
+library(ballgown)
+library(devtools)
+library(genefilter)
+library(ggsci)
+library(tidyverse)
+
+# make experimental data dataframe
+exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
+                      "abund_12hrsS1", "12h.p.i", "Rep1",
+                      "abund_12hrsS3", "12h.p.i", "Rep3",
+                      "abund_24hrsS1", "24h.p.i", "Rep1",
+                      "abund_24hrsS2", "24h.p.i", "Rep2",
+                      "abund_24hrsS3", "24h.p.i", "Rep3",
+                      "abund_4hrsS1", "4h.p.i", "Rep1",
+                      "abund_4hrsS2", "4h.p.i", "Rep2",
+                      "abund_72hrsS1", "72h.p.i", "Rep1",
+                      "abund_72hrsS2", "72h.p.i", "Rep2",
+                      "abund_72hrsS3", "72h.p.i", "Rep3") %>% data.frame()
+
+# load in expression level files for making ballgown object
+bam_files <- list.files("results/hisat2",
+                        pattern = "^thev_subset_\\d+hrsS\\d\\.bam$",
+                        full.names = T) %>%
+  .[c(1:7, 9:11)]
+  
+raw_data <- ballgown(dataDir = "results/ballgown",
+                        samplePattern = "abund_",
+                        pData = exp_info,
+                       bamfiles = bam_files)
+
+# load in annotated ORFs from NCBI
+pred_orfs <- gffReadGR("raw_files/annotations/thev_predicted_genes.gtf",
+                       splitByTranscript = T)
+
+# annotate assembled transcripts with predicted ORFs from NCBI
+assembled_trxpts <- structure(raw_data)$trans
+trxpt_anno <- annotate_assembly(assembled_trxpts, pred_orfs)
+
+ballgown::plotMeans("XLOC_000001", raw_data, groupvar = "timepoint",
+                    groupname = "all" ,labelTranscripts = T)
+
+
+structure(raw_data)$exon
+
+ex_exp_levels <- eexpr(raw_data)
+
+# plot transcript expression levels
+t_exp_levels <- texpr(raw_data, meas = "all")
+
+t_exp_levels %>%
+  as_tibble() %>%
+  pivot_longer(cols = starts_with("FPKM"),
+               names_to = "samples",
+               values_to = "fpkm") %>%
+  mutate(fpkm = log2(fpkm + 1),
[…]

### 2023-08-14 scripts/r/bam_file_analysis.R

@@ -2,75 +2,88 @@
 library(magrittr)
 library(glue)
 library(tidyverse)
+library(scales)
 
 
-single_jun_files <- list.files("results/hisat2", full.names = T,
-                               pattern = "\\w+\\.bed") %>% 
-  setNames(c("t12s1","t12s3", "t24s1", "t24s2", "t24s3", "t4s1", "t4s2", "t4s3", "t72s1", "t72s2", "t72s3"))
-
-single_junc_stats <- map_dfr(single_jun_files, read_tsv,
-                             col_names = F,
-                             show_col_types = F,
-                             .id = "timepoint") %>% 
-  set_colnames(c("timepoint", "chrom", "start", "end", "junc_name", "read_count", "strand",
-                 "thickStart", "thickEnd", "color", "exons", "exon_sizes", "exon_starts")) %>% 
-  arrange(start, end)
-
-single_junclist <- single_junc_stats %>% group_by(start, end) %>% summarise(repeated = n(),
-                                                                            .groups = "drop")
- 
-single_sum_stats <- single_junc_stats %>% 
-  mutate(timepoint = case_when(timepoint %in% c("t72s1", "t72s2", "t72s3") ~ "72hpi",
-                               timepoint %in% c("t24s1", "t24s2", "t24s3") ~ "24hpi",
-                               timepoint %in% c("t12s1", "t12s3") ~ "12hpi",
-                               timepoint %in% c("t4s1", "t4s2", "t4s3") ~ "4hpi",
-                               .default = timepoint)) %>% 
-  group_by(timepoint) %>%
-  summarize(total_junctions = n(),
-            reads10  = sum(read_count > 10),
-            reads100  = sum(read_count > 100),
-            reads1000  = sum(read_count > 1000),
-            total_reads_supporting = sum(read_count),
-            mean_read_supporting = total_reads_supporting/total_junctions,
-            organism = "thev") %>%
-  # mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>% 
-  arrange(total_junctions)
+# single_jun_files <- list.files("results/hisat2", full.names = T,
+#                                pattern = "\\w+\\.bed") %>%
+#   setNames(c("t12s1","t12s3", "t24s1", "t24s2", "t24s3","t4s1",
+#              "t4s2", "t4s3", "t72s1", "t72s2", "t72s3"))
+# 
[…]

### 2023-08-14 scripts/r/extract_thev_exons.R

@@ -1,0 +1,24 @@
+#!/usr/bin/env Rscript
+
+
+library(tidyverse)
+
+
+gtf <-  read_tsv("raw_files/annotations/thev_predicted_genes.gtf",
+                 col_names = FALSE,
+                 comment = "#",
+                 show_col_types = FALSE) %>%
+  filter(X3 == "gene") %>% 
+  select(X1, X4, X5, X7) %>% 
+  mutate(X4 = X4 -1,
+         X5 = X5 -1)
+
+
+write.table(gtf, "raw_files/annotations/thev_predicted_genes.exons",
+            col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE
+)
+
+
+
+
+

### 2023-08-14 scripts/r/filter_real_transcripts.R

@@ -16,12 +16,25 @@ library(tidyverse)
 merged_gtf <- read_tsv("results/stringtie/all_merged.gtf",
                        comment = "#",
                        col_names = FALSE,
-                       show_col_types = FALSE)
+                       show_col_types = FALSE) 
+
+duplicates <- 'gene_id "24S2.11"|gene_id "24S1.11"|gene_id "72S3.10"|transcript_id "24S3.2.5"|gene_id "12S1.2"|transcript_id "24S1.1.1"|gene_id "24S2.1"|transcript_id "24S2.2.5"|transcript_id "72S1.8.1"|transcript_id "72S2.8.1"|transcript_id "4S2.3.1"|transcript_id "72S1.10.1"|transcript_id "24S1.12.1"|transcript_id "72S2.9.1"|transcript_id "72S1.1.1"|transcript_id "72S3.1.1"|transcript_id "24S3.1.1"|transcript_id "24S1.1.2"|transcript_id "12S1.1.1"|transcript_id "24S2.10.1"|transcript_id "12S1.10.2"|transcript_id "24S2.2.1"|transcript_id "4S1.4.1"|transcript_id "24S2.2.2"|transcript_id "24S3.2.1"|transcript_id "72S1.12.1"|transcript_id "24S1.2.4"|transcript_id "12S1.11.3"|transcript_id "24S3.11.1"|transcript_id "72S1.13.1"|transcript_id "72S1.13.2"|transcript_id "24S1.14.1"|transcript_id "12S1.4.2"'
+
+filter_real_transcripts <- merged_gtf %>% 
+  filter(str_detect(X9, "reference_id", negate = T)) %>%
+  filter(!str_detect(X9, duplicates)) %>%
+  group_by(X7) %>% 
+  arrange(X4, .by_group = T)
+
+# save modified .gtf of all unique transcripts across all time-points
+write.table(filter_real_transcripts, "results/stringtie/all_real_transcripts_merged.gtf",
+            col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
+
 
 # function to filter any given time-point
 sub_timepoint <- function(timepoint){
   out <- merged_gtf %>%
-    filter(str_detect(X9, "ref_gene_name", negate = T)) %>% 
+    filter(str_detect(X9, "reference_id", negate = T)) %>%
     filter(str_detect(X9, paste0('gene_id\\s"', timepoint)))
   
   # save filtered results

### 2023-08-14 scripts/r/makingGFFfile.R

@@ -3,10 +3,10 @@
 
 library(tidyverse)
 
-# bedfile <- read_tsv("raw_files/annotations/THEVannotated_genesOnly.txt",
-# col_names = FALSE, col_types = cols(X11 = "c"))
-# write.table(bedfile, "THEVannotated_genesOnly.bed",
-# col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
+bedfile <- read_tsv("raw_files/annotations/THEVannotated_genesOnly.txt",
+                    col_names = FALSE, col_types = cols(X11 = "c"))
+write.table(bedfile, "THEVannotated_genesOnly.bed",
+col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
 
 ## agat used to convert .bed to .gff
 
@@ -22,17 +22,27 @@ library(tidyverse)
 #     show_col_types = FALSE
 # ) %>%
 #     filter(!X3 %in% c("three_prime_UTR", "five_prime_UTR"))
-# 
+#
 # # replace old .gff with modified .gff
-# write.table(gfffile, "raw_files/annotations/thev_predicted_genes2.gff",
-#     col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE
-# )
 
 
 
 
+gff <-  read_tsv("raw_files/annotations/thev_from_NCBI.gff3",
+                 col_names = FALSE,
+                 comment = "#",
+                 show_col_types = FALSE) %>%
+  filter(!X3 %in% c("region", "inverted_repeat", "sequence_feature"))
 
 
+  # mutate(X9 = case_when(str_detect(X9, "AAX51188.1") ~ "UXP",
+  #                       str_detect(X9, "EP") ~ "Protease",
+  #                       str_detect(X9, "gene-II;") ~ "gene-Hexon",
+  #                       str_detect(X9, "=II;") ~ "=Hexon"))
+
+write.table(gff, "raw_files/annotations/thev_NCBI_2.gff",
+            col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE
+)
 
 
 

### 2023-08-14 scripts/r/plot_thev_timepoint_splicing.R

@@ -1,0 +1,210 @@
+library(magrittr)
+library(glue)
+library(tidyverse)
+library(rtracklayer)
+library(patchwork)
+library(ggtext)
+
+# table of transcript ids for different genome regions here for transcription unit assignment
+
+trxpt_ids_repo <- tribble(~region, ~`4hpi`, ~`12hpi`, ~`24hpi`, ~`72hpi`,
+                     "e1", NA, c("12S1.1.2", "12S1.1.1"), c("24S1.1.1", "24S2.1.1",
+                                                            "24S2.1.2", "24S3.1.2",
+                                                            "24S3.1.1", "24S1.1.2"), c("72S1.1.1", "72S2.1.1", "72S2.1.2", "72S3.1.1"),
+                     "e2", c("4S1.4.1",
+                             "4S2.3.1"), NA, c("24S2.2.2", "24S3.2.2", "24S3.2.1",
+                                               "24S1.2.1", "24S1.2.2", "24S2.2.1",
+                                               "24S1.2.4", "24S3.2.5", "24S2.2.4"), c("72S1.12.1", "72S2.8.1", "72S3.10.1", "72S3.3.2"),
+                     "e3", c("4S1.5.1"), c("12S3.6.2",
+                                           "12S1.4.7",
+                                           "12S1.4.8"), c("24S3.11.1", "24S1.11.1", "24S2.11.1",
+                                                          "24S1.11.2", "24S3.11.2", "24S2.11.2"), c("72S1.13.4", "72S3.11.3", "72S1.13.1", "72S3.11.2", "72S1.13.2"),
+                     "e4", NA, c("12S3.8.1"), NA, NA,
+                     "im", NA, c("12S1.2.2"), NA, c("72S3.2.1")
+                     ) %>% 
+  pivot_longer(-region, names_to = "timepoint", values_to = "ids")
+  
+  duplicate_trxpts <- c("24S1.1.1", "24S1.1.2", "24S3.1.1", "72S3.1.1",
+                        "72S1.1.1", "24S3.11.1", "24S1.11.1", "24S1.11.2",
+                        "24S3.11.2", "72S1.13.1")
+# "results/stringtie/transcripts_merged_72hrs.gtf"
+# Import GTF and Wrangle for plotting ==========================================
+#===============================================================================
+
+graph_trxpts <- function(gtf){
+  
+  # detect timepoint from gtf name and pass onto next funtion 
+  # to avail the appropriate trxpt ids
[…]

### 2023-08-14 scripts/r/sgseq_spliceAnalysis.R

@@ -1,32 +1,0 @@
-#!/usr/bin/env Rscript
-
-library(SGSeq)
-library(tidyverse)
-
-## make list of samples with corresponding bam files to extract information
-# sample <- tibble(sample_name = c(paste0("12hrs", c("S1", "S3")),
-#                                  paste0(c("24hrs"), c("S1", "S2", "S3")),
-#                                  paste0(c("4hrs"), c("S1", "S2", "S3")),
-#                                  paste0(c("72hrs"), c("S1", "S2", "S3"))),
-#                  file_bam = list.files("results/hisat2", "^thev_sorted_.+bam$",
-#                                        full.names = T)
-#                  )
-
-# ## extract information from bam files. This is a slow function so I'll save the data
-# # as a tsv and load it henceforth
-# sample_info <- getBamInfo(sample, cores = 8)
-
-# write.table(sample_info, "results/sgseq/bam_extracted_sampleData.tsv",
-#             col.names = T, row.names = F, quote = F, sep = "\t")
-
-### ====================================
-# load in sample/bam information
-
-bam_info <- read_tsv("results/sgseq/bam_extracted_sampleData.tsv",
-  show_col_types = F) 
-
-bam_info %>%
-  select(read_length) %>%
-  slice(1) %>%
-  pull()
-

### 2023-08-14 scripts/r/splice_site_analyses.R

@@ -1,0 +1,152 @@
+#!/usr/bin/env Rscript
+
+library(magrittr)
+library(scales)
+library(tidyverse)
+library(rtracklayer)
+library(glue)
+library(ggsci)
+
+# load in data from from full transcriptome to access the splice sites
+all_spliced_gtf <- import("results/gffcompare/gffcomp_alltimes.combined.gtf") %>%
+  as_tibble() %>%
+  select(chr = seqnames, start, end, orf_size = width, strand, type, gene_id,
+         transcript_id, exon_number) %>% 
+  group_by(transcript_id, strand) %>%
+  reframe(start = list(start),
+          end = list(end)) %>%
+  unnest_wider(c(start, end), names_sep = "_") %>%
+  mutate(region = case_when(transcript_id %in% paste0("TCONS_000000", c('15', '16', '04', '05')) ~ "E1",
+                            transcript_id %in% paste0("TCONS_000000", c('03', '17', '18', '28')) ~ "E2",
+                            transcript_id %in% paste0("TCONS_000000", c('26', '27', '12', '10', '11', '02')) ~ "E3",
+                            transcript_id == "TCONS_00000014" ~ "E4",
+                            transcript_id == "TCONS_00000013" ~ "IM",
+                            TRUE ~ "MLP")) %>% 
+  arrange(strand, region) %>%
+  mutate(j1_ss = end_2, j1_ts = start_3,
+         j2_ss = end_3, j2_ts = start_4,
+         j3_ss = end_4, j3_ts = start_5,
+         j4_ss = end_5, j4_ts = start_6,
+         j5_ss = end_6, j5_ts = start_7,
+         j6_ss = end_7, j6_ts = start_8
+         ) %>% 
+  select(-ends_with("_1"), -starts_with("start"), -starts_with("end"))
+
+# extract junction pairs (start and end) to make long format
+get_junc_pair <- function(j_ss, j_ts){
+  return(data.frame(transcript_id = all_spliced_gtf$transcript_id,
+             strand = all_spliced_gtf$strand,
+             region = all_spliced_gtf$region,
+             junc_ss = all_spliced_gtf %>% select(all_of(j_ss)),
+             junc_ts = all_spliced_gtf %>% select(all_of(j_ts))
+             ) %>%
+           set_colnames(c("transcript_id", "strand", "region",
+                                  "junc_ss", "junc_ts")) %>%
+           as_tibble()
+  )
+}
+
+
[…]

### 2023-08-14 scripts/r/stringtie_abundances.R

@@ -1,0 +1,76 @@
+
+library(tidyverse)
+library(magrittr)
+library(ggsci)
+
+# load in stringtie abundance tables
+files <- list.files("results/stringtie/", pattern = "t\\d{1,2}S\\d\\.tab",
+                    full.names = T) %>% 
+  setNames(c("12h.p.i", "12h.p.i", "24h.p.i", "24h.p.i", "24h.p.i", "4h.p.i",
+             "4h.p.i", "72h.p.i", "72h.p.i", "72h.p.i"))
+
+stringtie_abun <- map_dfr(files, read_tsv,
+                          show_col_types = F,
+                          .id = "timepoint") %>%
+  dplyr::rename(gene_name = "Gene Name", gene_id = "Gene ID", strand = Strand,
+         start = Start, end = End, coverage = Coverage, fpkm = FPKM, tpm = TPM) %>% 
+  mutate(gene_name = ifelse(gene_name == "-", "unknown", gene_name)) %>% 
+  split(.$timepoint) %>% 
+  map(mutate, tot_fpkm_time = sum(fpkm)) %>% 
+  do.call("rbind", .) %>% 
+  as_tibble() %>%
+  select(-c(gene_id)) %>%
+  group_by(timepoint, gene_name) %>%
+  reframe(count = n(),
+          tot_fpkm_time = tot_fpkm_time,
+          sum_fpkm = sum(fpkm),
+          perc_fpkm = (sum_fpkm / tot_fpkm_time) * 100) %>% 
+  unique()
+
+stringtie_abun %>% 
+  filter(!gene_name == "unknown") %>%
+  mutate(timepoint = factor(timepoint,
+                            levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>% 
+  ggplot(aes(gene_name, perc_fpkm, fill = timepoint)) +
+  geom_col(position = position_dodge(0.7), width = 0.4) +
+  scale_fill_jama() +
+  theme_classic()
+
+
+## plotting values from python script: pile_reads_to_orfs.py
+
+
+# load in stringtie abundance tables
+py_files <- list.files("results/hisat2/bulk", pattern = "subsetTHEV_\\d{1,2}hrs.bam_pileup.csv",
+                    full.names = T) %>% 
+  setNames(c("12h.p.i", "24h.p.i","4h.p.i", "72h.p.i"))
+
+orf_read_pileups <- map_dfr(py_files, read_csv,
[…]

### 2023-08-14 scripts/r/thev_growthcurve.R

@@ -11,7 +11,9 @@ replicate_data <- read_excel(exp2,
                           sheet = "Results",
                           skip = 6,
                           trim_ws = TRUE) %>% 
-  rename(well = "Well", sample_name = "Sample Name", conc = "Quantity") %>%
+  dplyr::rename(well = "Well",
+                sample_name = "Sample Name",
+                conc = "Quantity") %>%
   select(well, sample_name, conc) %>% 
   drop_na(sample_name) %>% 
   mutate(sample_name = str_replace(string = sample_name,
@@ -105,7 +107,9 @@ rep1_data <- read_excel(exp1,
                         sheet = "Results",
                         skip = 6,
                         trim_ws = TRUE) %>% 
-  rename(well = "Well", sample_name = "Sample Name",task = "Task", conc = "Quantity") %>% 
+  dplyr::rename(well = "Well",
+                sample_name = "Sample Name",
+                task = "Task", conc = "Quantity") %>% 
   select(well, task, sample_name, conc) %>% 
   drop_na(sample_name) %>% 
   filter(!str_detect(sample_name, ".*DNA.*")) %>% 
@@ -144,15 +148,14 @@ growth_curve <- full_prepped %>%
   geom_point(size = 5) +
   geom_line(linewidth  = 1.5) +
   scale_color_aaas(breaks = c("Inf", "Neg"),
-                   labels = c("Infected", "Mock-Infected"),
-                   guide = guide_legend(title = "Treatment")) +
+                   labels = c("Infected", "Mock-Infected")) +
   scale_x_continuous(expand = c(0.01, 0.01),
                      breaks = full_prepped$hrs_pi,
                      labels = c(paste(full_prepped$hrs_pi, "hpi"))) +
   scale_y_continuous(expand = c(0.02, 0.02)) +
   labs(title = "THEV One-Step Growth Curve in RP-19 Turkey B-Cells",
        x = element_blank(),
-       y = "Virus Titer (GCN/\U00B5L)",
+       y = "Virus Titer (GCN/mL)",
        size = element_blank()
   ) +
   theme(plot.background = element_rect(fill = "#ffffff"),
@@ -174,8 +177,7 @@ growth_curve <- full_prepped %>%
         axis.title.y = element_text(size = 22, face = "bold", colour = "#000000",
                                     margin = margin(r = 10)),
         axis.ticks.length.y = unit(0, "cm"),
-        legend.title = element_text(size = 18, face = "bold", colour = "#000000",
[…]

### 2023-08-14 scripts/r/thev_orf_map.R

@@ -30,29 +30,29 @@ make_genomic_map2 <- function(bedfile){
                                   "33K_spliced" ~ "33K",
                                   "pVIII gene" ~ "pVIII",
                                   .default = gene_name),
-           ypos = ifelse(strand == "-", c(22, 23), c(26, 27)),
-           ypos = ifelse(gene_name == "22K", 28, ypos))
+           ypos = ifelse(strand == "-", c(24, 24.5), c(25.5, 26)),
+           ypos = ifelse(gene_name == "22K", 26.5, ypos))
   
   spliced2 <- thev_genome2 %>% filter(blockCount > 1)
   
   genome_ruler <- tibble(x = seq(0,26000,2000),
-                         y = 24.8,
-                         yend = 25.3,
+                         y = 24.9,
+                         yend = 25.1,
                          lab = paste0(seq(0,26, 2), "kb"))
   
   shade_regions <- tribble(~xmin, ~xmax, ~ymin, ~ymax,
-                           0, thev_genome2$end[2], 20, 30,
-                           thev_genome2$start[19], thev_genome2$end[19], 20, 30,
-                           thev_genome2$start[22], 26266, 20, 30
+                           0, thev_genome2$end[2], 23, 27,
+                           thev_genome2$start[19], thev_genome2$end[19], 23, 27,
+                           thev_genome2$start[22], 26266, 23, 27
                            )
   
   trxpt_units <- tribble(~x, ~xend, ~y, ~labb, ~ylabb,
-                         0, thev_genome2$end[2], 19.5, "E1", 19,
-                         thev_genome2$start[19], thev_genome2$end[19], 19.5, "E3", 19,
-                         thev_genome2$start[22], 26266, 19.5, "E4", 19,
-                         thev_genome2$start[3], thev_genome2$end[3], 19.5, "IM", 19,
-                         thev_genome2$start[4], thev_genome2$exon1end[4], 19.5, "E2B", 19,
-                         thev_genome2$start[14], thev_genome2$end[14], 19.5, "E2A", 19
+                         0, thev_genome2$end[2], 23, "E1", 22.85,
+                         thev_genome2$start[19], thev_genome2$end[19], 23, "E3", 22.85,
+                         thev_genome2$start[22], 26266, 23, "E4", 22.85,
+                         thev_genome2$start[3], thev_genome2$end[3], 23, "IM", 22.85,
[…]

### 2023-08-14 scripts/r/thev_splicing_fullMap.R

@@ -1,0 +1,241 @@
+
+library(magrittr)
+library(ggtext)
+library(glue)
+library(rtracklayer)
+library(ggbrace)
+library(patchwork)
+library(plyr)
+library(tidyverse)
+
+# Import GTF and Wrangle for plotting ==========================================
+#===============================================================================
+
+spliced_gtf <- import("results/gffcompare/gffcomp_alltimes.combined.gtf") %>%
+  as_tibble() %>%
+  select(chr = seqnames, start, end, orf_size = width, strand, type, gene_id,
+         transcript_id, exon_number) %>% 
+  group_by(transcript_id, strand) %>%
+  reframe(start = list(start),
+          end = list(end)) %>%
+  unnest_wider(c(start, end), names_sep = "_") %>%
+  mutate(region = case_when(transcript_id %in% paste0("TCONS_000000", c('15', '16', '04', '05')) ~ "E1",
+                            transcript_id %in% paste0("TCONS_000000", c('03', '17', '18', '28')) ~ "E2",
+                            transcript_id %in% paste0("TCONS_000000", c('26', '27', '12', '10', '11', '02')) ~ "E3",
+                            transcript_id == "TCONS_00000014" ~ "E4",
+                            transcript_id == "TCONS_00000013" ~ "IM",
+                            TRUE ~ "MLP")) %>% 
+  arrange(strand, region)
+
+# load in data and prepare predicted ORFs only
+
+predicted_orfs <- import("results/stringtie/all_merged.gtf") %>% 
+  as_tibble() %>% 
+  drop_na(reference_id) %>% 
+  distinct(start, end, width, .keep_all = T) %>% 
+  select(chr = seqnames, start, end, orf_size = width, strand, type, gene_id,
+         transcript_id, reference_id, exon_number) %>% 
+  group_by(transcript_id, strand) %>%
+  reframe(start = list(start),
+          end = list(end)) %>%
+  unnest_wider(c(start, end), names_sep = "_")
+
+# pull out the orf names
+orf_names <- import("results/stringtie/all_merged.gtf") %>% 
+  as_tibble() %>%
+  drop_na(reference_id) %>% 
+  distinct(start, end, width, .keep_all = T) %>% 
+  select(gene_name = reference_id, transcript_id) %>%
+  distinct(gene_name, .keep_all = T)
+
+# assign orf names back to orf data
[…]

### 2023-08-14 scripts/r/trim_gff.R

@@ -1,0 +1,35 @@
+#!/usr/bin/env Rscript
+
+
+library(tidyverse)
+
+
+gff <-  read_tsv("raw_files/annotations/thev_predicted_genes.gff",
+                 col_names = FALSE,
+                 comment = "#",
+                 show_col_types = FALSE) %>%
+  filter(!X3 %in% c("three_prime_UTR", "five_prime_UTR")) %>% 
+  separate_wider_delim(X9, delim = ";", names = c("id", "name", "others"),
+                       too_many = "merge", too_few = "align_start") %>%
+  separate_wider_delim(name, delim = "=", names = c("attr", "gene_name")) %>% 
+  rename(chr = X1, source = X2, feature = X3) %>% 
+  mutate(id = ifelse(feature == "gene", paste0("ID=", gene_name), id),
+         gene_name = ifelse(attr == "Parent",
+                            ifelse(lag(gene_name, n = 1) %in% c(as.character(c(1:23))),
+                                   lag(gene_name, n = 2), lag(gene_name, n = 1)), 
+                            gene_name),
+         gene_name = ifelse(gene_name %in% c(as.character(c(1:23))), lag(gene_name, n = 1), gene_name),
+         gene_name = ifelse(gene_name %in% c(as.character(c(1:23))), lag(gene_name, n = 1), gene_name),
+         gene_attr = paste0("gene=", gene_name)
+         ) %>%
+  unite(col = "attr1", attr:gene_name, sep = "=", remove = T) %>% 
+  unite(col = "attributes", id:gene_attr, sep = ";", na.rm = T)
+
+# Save table
+write.table(gff, "raw_files/annotations/thev_predicted_genes.gff",
+            col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
+
+
+
+
+

### 2023-08-23 manuscript_thev_transcriptome.Rmd
used regtools to extract splice-site seq for juncs and used the resulting files to perform junction analyses. Created a new Rmd file to write supplementary data

@@
 ---
-title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
+title: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus
+always_allow_html: true
 output:
-  word_document: default
+  # word_document: default
   html_document: default
@@
 library(tidyverse)
-library(gt)
 library(tibble)
 library(scales)
+library(gt)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 
+most_sig_12 <- bulk_junc_stats %>% filter(timepoint == "12hpi", region == "E2") %>% pull(read_count) %>% sum()/as.numeric(tab1$`12h.p.i`[6])*100
+
+most_sig_24 <- bulk_junc_stats %>% filter(timepoint == "24hpi", region == "MLP") %>% pull(read_count) %>% sum()/as.numeric(tab1$`24h.p.i`[6])*100
+
+most_sig_72 <- bulk_junc_stats %>% filter(timepoint == "72hpi", region == "MLP") %>% pull(read_count) %>% sum()/as.numeric(tab1$`72h.p.i`[6])*100
 ```
@@
 Thus, the MLTU produces a complex repertoire of mRNA with diverse 5'-UTRs spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5).
-Each transcription unit contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
+Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
 Almost all AdV mRNAs are generated by the excision of one or more introns and most of these introns are located in the 5' or 3' UTRs of pre-mRNA.
@@
 Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-Seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point.
-Using the `HISAT2` [@Pertea2016] alignment program, a total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
-The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2__).
-From the mapped reads, we identified an overall total of `r bulk_junc_stats %>% nrow()` THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
+Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*M.gallopavo*) genomes using the `HISAT2` [@Pertea2016] alignment program.
+A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
+The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2a__).
+From the mapped reads, we identified an overall total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
 For example all the `r tot_jun_4` unique junctions at 4 h.p.i had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads/junction.
-Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having as high as `r max_junread72` reads in support.
-The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes the progression of the infection and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 3__).
-Using `StringTie` [@Pertea2016], an assembler of RNA-Seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
-In the final consolidated transcriptome of THEV generated from transcripts from all time points, we counted a total of `r nrow(combined_gtf)` transcripts all of which are novel.
-Although some exons in some transcripts match the predicted ORFs of THEV exactly, most of the exons are longer, spanning multiple predicted ORFs (__Figure 4__).
-The complete list of splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
+Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having coverage as high as `r max_junread72` reads.
+The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes an active infection, and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 2b__).
+Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
+In the final consolidated transcriptome of THEV, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` transcripts all of which are novel.
+Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (__Figure 3__).
+The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
 XXXXXX**.
+
+**Changes in THEV splice junction profile over time**   
+AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU).
+Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs.
+To evaluate the activity of each promoter over time, we estimate relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point.
+Very few unique splice junctions and reads were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
+At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were predominantly early region (E1, E2, and E3) junctions, albeit a significant proportion are MLP-derived (__Table 2a__).
+Junctions from the E2 region were the most abundant at this time point, constituting `r round(most_sig_12, 1)`% of all junctions.
+The two most abundant junctions at 12 h.p.i were maintained at 24 h.p.i also as the most significantly expressed.
+However, the MLP-derived junctions were unsurprisingly the most preponderant overall at this time point, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__).
+At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions was not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
+Also see __Supplementary Tables 1a-c__; __Figure 4a__).
+When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 4b__).
+
+Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
+This revealed that, with the exception of one junction (which was a T-G donor-acceptor pair), all splice donor-acceptor pairs in the final transcriptome were the canonical T-A pair.
 
@@
 This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell.
-The host transcription machinery is lobbied for the transcription of the region.
-No viral proteins are available at this stage; hence, host transcription factors play the key roles of mobilizing the transcription machinery.
-After their translation, the E1 proteins in concert with the host transcription factors activate the other viral promoters [@Guimet2016].
-We identified four novel transcripts in this region ~~and also validated the predicted ORF (sialidase; ORF1)~~.
+The host transcription machinery is solely responsible for the transcription of this region.
+After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
+We discovered four novel transcripts in this region with varying protein-coding potential (PCP).
+
+~~and also validated the predicted ORF (sialidase; ORF1)~~.
 
@@
 The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al*[@Mahsoub2017] with modifications.
-Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-Seq.
+Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-seq.
 The infection was repeated but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
@@
 The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
-Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-Seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
+Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
 Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.
@@
 ```{r}
-kable(tab1)
+gt(tab1) %>%
+  fmt_markdown()
 ```
 
-![](results/r/figures/patch_alltimes.png)
-
+![](results/r/figures/overlay_alltimes.png)
+![](results/r/figures/thev_growth_curve.png)
 **Figure 2.
-_Per base coverage of sequence reads mapping to THEV genome by time point_**.
+a) _Per base coverage of sequence reads mapping to THEV genome by time point_**.
 The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point show remarkable difference in terms of quantities.
@@
 However, the relative proportions over these similar regions shows some variation over time.
-
-![](results/r/figures/thev_growth_curve.png)
-**Figure 3.
-_One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
+**b) _One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
 After infecting cells at an MOI of 100 GCN/cell, triplicates of harvested infected cells were quantified with an in-house qPCR assay measuring the total copies of THEV genome.
@@
 ![](results/r/figures/thev_spliced_map.png)
-**Figure 4a.
-__Full transcriptome of THEV__**.
+![](results/r/figures/thev_patched_timepoints_spliced_map.png)
+**Figure 3.
+a) __Full transcriptome of THEV__**.
 THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map).
@@
 Predicted ORFs are also indicated here, colored light grey.
+**b) __THEV transcripts identified at given time points__**.
+Transcripts are color coded as explained in **a**.
 
-![](results/r/figures/thev_patched_timepoints_spliced_map.png)
-**Figure 4b. __THEV transcripts identified at given time points__**. Transcripts are color coded as explained in Fig.4a.
+**Table 2A**
+
+```{r}
+gt(sig_12_juncs)
+```
+
+**Table 2B**
+
+```{r}
+gt(sig_24_juncs)
+```
+
+**Table 2C**
+
+```{r}
+gt(sig_72_juncs)
+```
+
+![](results/r/figures/junc_abundances.png)
+**Figure 4.
+a) Relative abundances of splice junctions over time as a proxy of estimating activity levels of THEV promoters**.
+## Description here ##########.
+**b) Relative abundances of junctions in final transcriptome**.
+##Description here #######.

### 2023-08-23 supplementary_thev_trxptome.Rmd
used regtools to extract splice-site seq for juncs and used the resulting files to perform junction analyses. Created a new Rmd file to write supplementary data

--- 2023-07-21 manuscript_thev_transcriptome.Rmd
@@
 ---
-title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
-output:
-  word_document: default
-  pdf_document: default
+title: "Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus"
+output: pdf_document
 geometry: margin=1in
@@
   - \linenumbers
-bibliography: transcriptome_refs.bib
-csl: asm.csl
 editor_options:
@@
 
-```{r call_libs, echo=FALSE,include=FALSE, message=FALSE, warning=FALSE}
+```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 library(knitr)
@@
 library(gt)
-opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 
-inline_hook <- function(x) {
-  if(is.numeric(x)){
-    formatted <- format(x, big.mark = ",")
-  }else{formatted <- x}
-  paste0("**", formatted, "**")
-}
-knit_hooks$set(inline = inline_hook)
+source("scripts/r/bam_file_analysis.R")
 ```
 
-```{r inline_values}
+## Supplementary Table 1A
 
-# extract paired-end sequencing read length
-bam_info <- read_tsv("results/sgseq/bam_extracted_sampleData.tsv",
-                     show_col_types = F) 
-seq_len <- bam_info %>% select(read_length) %>% slice_head() %>% pull()
-
-source("scripts/r/bam_file_analysis.R")
-cov_thev <- all_covs %>% filter(organism == "thev")
-
-cov_4hr <- cov_thev %>% filter(timepoint == "4hpi") %>%
-              select(total_mapped) %>% pull() %>% as.numeric(.)
-cov_72hr <- cov_thev %>% filter(timepoint == "72hpi") %>%
-              select(total_mapped) %>% pull() %>% as.numeric(.)
-cov_72hr <- round(cov_72hr / 1e6, 1)
-
-total_mapped <- round(sum(as.numeric(cov_thev$total_mapped)) / 1e6, 1)
-
-avg_tot_count <- round(mean(total_reads$total_reads) / 1e6, 1)
-```
-## ABSTRACT        
-**Background:** Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by _immunosuppression (IS)_ and bloody diarrhea.
-This disease is caused by _Turkey Hemorrhagic Enteritis Virus (THEV)_ of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
-The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
-_Our objective is to understand the genetic basis by which VAS induces IS_.
-The _transcriptome of THEV_ was studied to set the stage for further experimentation with specific viral genes that may mediate IS.
-**Methods:** After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
-Total RNA was subsequently extracted, and poly-A-tailed mRNA sequencing done.
-After trimming the raw sequencing reads with the `FastQC`, reads were mapped to the THEV genome using `Hisat2` and transcripts assembled with `StringTie`.
-An in-house script was used to consolidate transcripts from all time-points, generating the final transcriptome.
-PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.
-**Results and Conclusions:** A total of `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
-All predicted genes in the genome were represented.
-In keeping with all adenoviruses, all transcripts were spliced with either with 5'- or 3'-multi exon UTRs hitherto unknown.
-*~~Thirteen~~* novel exons were identified which were validated by PCR and Sanger sequencing.
-The splicing patterns strongly suggest that there are *~~three~~* main promoters (E1, E3, and major late promoters) driving expression of most of the genes with *~~two~~* possible minor promoters driving single genes (ORF7 and ORF8).
-This RNA-sequencing experiment is the first study of THEV gene expression to date.
-In keeping with other Adenoviruses, almost all THEV genes are spliced, and several genes are expressed as one transcription unit under a single promoter.
-This insight into THEV's transcriptome may allow the engineering of the VAS to provide immune protection with less or no associated IS.
-\newpage
-
-## INTRODUCTION   
-Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all vertebrates.
-Their double-stranded linear DNA genomes range between 26 and 45kb in size, producing a broad repertoire of transcripts via a highly complex alternative splicing pattern [@Davison2003; @Harrach2008].
-The AdV genome is one of the most optimally economized; both the forward and reverse DNA strands harbor protein-coding genes, making it highly gene-dense.
-There are 16 genes termed "genus-common" that are homologous in all AdVs; these are thought to be inherited from a common ancestor.
-All other genes are termed "genus-specific".
-"Genus-specific" genes tend to be located at the termini of the genome while "genus-common" genes are usually central [@Davison2003].
-This pattern is observed in *Adenoviridae*, *Poxviridae*, and *Herpesviridae* [@Davison2003; @Upton2003; @McGeoch1999].
-The family *Adenoviridae* consists of five genera: *Mastadenovirus* (MAdV), *Aviadenovirus*, *Atadenovirus*, *Ichtadenovirus*, and *Siadenovirus* (SiAdV) [@Harrach2011; @Guimet2016].
-Currently, there are three recognized members of the genus SiAdV: frog adenovirus 1, raptor adenovirus 1, and turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009].
-Members of SiAdV have the smallest genome size (~26 kb) and gene content (~23 genes) of all known AdVs, and many “genus-specific” putative genes of unknown functions have been annotated (see __Figure 1__)[@Harrach2008; @Kovács2011; @Davison2003].
-
-Virulent strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants.
-They infect via the fecal-oral route, and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
-In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967].
-HE is the most economically significant disease caused by any strain of THEV [@Beach2006].
-While the current vaccine strain (a THEV-A isolated from a pheasant, Virginia Avirulent Strain [VAS]) have proven effective at preventing HE in young turkey poults, it still retains the immunosuppressive ability.
-Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
-The induced IS also interferes with vaccination schemes for other infections of turkeys [@Beach2006; @Rautenschlein2000].
-To eliminate this immunossupressive side-effect of the vaccine, a thorough investigation of the culprit viral factors (genes) mediating this phenomenon is essential.
-However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
-A well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.
-
-Myriads of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
-However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU), which generates five families of late mRNAs (L1-L5).
-An additional gene (UXP or U exon) is located on the reverse strand.
-The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins.
-The immediate early gene E1A is expressed first, followed by the the delayed early genes, E1B, E2, E3 and E4.
-Then the intermediate early genes, IVa2 and pIX are expressed followed by the late genes [@Zhao2014; @Donovan2020; @Guimet2016].
-MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs; all but pIX mRNA undergo at least one splicing event.
-The MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
-There is also an alternate 5' three non-coding exons present in varying amounts on a subset of MLTU mRNAs (known as the x-, y- and z-leaders).
-Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
-Thus, the MLTU produces a complex repertoire of mRNA with diverse 5'-UTRs, spliced onto different 3' coding exons grouped into five different 3'-end classes (L1-L5).
-Each transcription unit contains its own promoter that drives the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
-
-Almost all AdV mRNAs are generated by the excision of one or more introns and most of these introns are located in the 5' or 3' UTRs of pre-mRNA.
-Thus the viral introns do only in a few cases interrupt the open reading frames (ORFs) [@Davison2003; @Zhao2014].
-The development of high throughput sequencing methods has facilitated the discovery of many novel transcribed regions and splicing isoforms.
-It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014].
-In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS strain) during different phases of the infection, yielding a complete THEV splicing map.
-Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
-The generated data from our paired-end sequencing experiment should thus be reliable.
-\newpage
-
-## RESULTS   
-**Overview of sequencing data and analysis pipeline outputs**     
-A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
-Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-Seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point.
-Using the `HISAT2` alignment program, a total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
-The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2__).
-From the mapped reads, we identified an overall total of `r bulk_junc_stats %>% nrow()` THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
-The substantial increases in splice junctions and mapping reads to the THEV genome from earlier time-points to later time-points corresponds to the progression of the infection and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 3__).
-Using `STRINGTIE`, an assembler of RNA-Seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the location of the predicted ORFs within the viral genome.
-The transcripts were consolidated to generate the final transcriptome of THEV (~~Maybe put the figure of the final transcriptome here?
-XXXXXXXXXXXXXXX~~).
-
-The complete list of splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
-XXXXXX**.
-
-\newpage
-
-## MATERIALS AND METHODS   
-### Cell culture and THEV Infection   
-The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium with 10% fetal bovine serum (FBS), 20% chicken serum (ChS), 5% tryptose phosphate broth (TPB), and 1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin), at 41^o^C in a humidified atmosphere with 5% CO~2~.
-When infected, the cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and  1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin).
-A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
-The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al*[@Mahsoub2017] with modifications.
-Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-Seq.
-A second infection was done but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
-
-### RNA extraction and Sequencing   
-Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` as per manufacturer's instructions.
-An agarose gel electrophoresis was performed to check RNA integrity.
-The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
-Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-Seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
-Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.
-
-### Computational Analysis of RNA Sequencing Data: Mapping and Transcript characterization
-Analysis of our sequence reads were analyzed following a well established protocol described by Pertea _et al_ [@Pertea2016], using `SNAKEMAKE 7.24.0` to drive the pipeline.
-Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) and *Meleagris gallopavo* (https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings without relying on known splice sites.
-The generated `BAM` files from each infection time-point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted ORFs of THEV as a guide.
-A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
-
-### Validation of Novel Splice Junctions 
-All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
-However, these predicted splice junctions have not been experimentally validated hitherto, and we identified additional novel splice junctions beside the predicted junctions, giving a more complete picture of the transcripts.
-
-The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in ~~Table###1~~.
-We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit with their respective universal primers (~~supplementary, PCR methods~~).
-Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
-After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method and Sanger sequenced to validate these splice junctions at the sequence level.
-
-### 3' Rapid Amplification of cDNA Ends (3'RACE)
-
-\newpage
-
-## DISCUSSION/CONCLUSIONS
-
-\newpage
-
-## SCRIPTS AND SUPPLEMENTARY MATERIALS
-
-### DATA AVAILABILITY
-
-### CODE AVAILABILITY    
-All the code/scripts written for analysis of the data is available on github (linkXXXXXX)
-\newpage
-
-## ACKNOWLEDGMENTS  
-LC Sciences
-`Eton Bioscience, Inc, San Diego, CA`
-\newpage
-
-## REFERENCES     
-\setlength{\parindent}{-0.25in}
-\setlength{\leftskip}{0.25in}
-\noindent
-<div id="refs"></div>
-\setlength{\parindent}{0in}
-\setlength{\leftskip}{0in}
-\newpage
-
-## TABLES AND FIGURES     
-![](results/r/figures/thev_orf_map.png)
-**Figure 1.
-_Genomic map of THEV avirulent strain_**.
-The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
-Blocks represent viral genes.
-Blocks above the DNA line are transcribed rightward, those below are transcribed leftward.
-pTP, DBP and 33K predicted to be spliced are shown as having tails.
-Shaded regions indicate regions containing "genus-specific" genes (colored red).
-Genes colored in blue are "genus-common".
-Gene colored in light green is conserved in all but Atadenoviruses.
-The UXP (light blue) is an incomplete gene present in almost all AdVs.
-Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.
-
-```{r}
-tab1 %>% 
-  gt(rowname_col = "Metric") %>% 
-  tab_header(title = md("**Table 1**"),
-             subtitle = "Summary of sequence alignment metrics") %>%
-  opt_align_table_header(align = "left") %>%
-  cols_width(Metric ~ px(150)) %>% 
-  opt_row_striping(row_striping = T) %>% 
-  tab_options(table.layout = "auto",
-              table.align = "left",
-              column_labels.font.size = "18px",
-              column_labels.font.weight = "bold",
-              table_body.vlines.style = "solid") %>% 
-  tab_stubhead(label = md("Metric"))
-
+```{r Sup Table 1A}
+gt(tp_reg_expr_12)
 ```
 
-![](results/r/figures/patch_alltimes.png)
+## Supplementary Table 1B
 
-**Figure 2. _Sequence reads mapping to THEV genome by time-point_**. Description ######
+```{r Sup Table 1B}
+gt(tp_reg_expr_24)
+```
 
-![](results/r/figures/thev_growth_curve.png)
-**Figure 3. _One-step growth of THEV_**. Description###. GCN: genome copy number.
+## Supplementary Table 1C
+
+```{r Sup Table 1C}
+gt(tp_reg_expr_72)
+```

### 2023-08-23 scripts/r/add_region_to_trxptome.R

@@ -1,0 +1,58 @@
+#!/usr/bin/env Rscript
+
+library(tidyverse)
+
+
+ updated_trxptome_gtf <- read_tsv("results/gffcompare/gffcomp_alltimes.combined.gtf",
+              col_names = F, show_col_types = F) %>%
+  separate_wider_delim(X9, delim = "; ", names = c("t_id", "others"),
+                       too_many = "merge") %>%
+  mutate(region = case_when(t_id %in% paste0("transcript_id \"TCONS_000000", c('15', '16', '04', '05'), "\"") ~ "gene_name \"E1\"",
+                            t_id %in% paste0("transcript_id \"TCONS_000000", c('03', '17', '18', '28'), "\"") ~ "gene_name \"E2\"",
+                            t_id %in% paste0("transcript_id \"TCONS_000000", c('26', '27', '12', '10', '11', '02'), "\"") ~ "gene_name \"E3\"",
+                            t_id == "transcript_id \"TCONS_00000014\"" ~ "gene_name \"E4\"",
+                            t_id == "transcript_id \"TCONS_00000013\"" ~ "gene_name \"IM\"",
+                            TRUE ~ "gene_name \"MLP\""),
+         
+         t_id = case_when(t_id == "transcript_id \"TCONS_00000015\"" ~ "transcript_id \"trxptB_ORF1\"",
+                          t_id == "transcript_id \"TCONS_00000016\"" ~ "transcript_id \"trxptC_hyd\"",
+                          t_id == "transcript_id \"TCONS_00000004\"" ~ "transcript_id \"trxptA_novel\"",
+                          t_id == "transcript_id \"TCONS_00000005\"" ~ "transcript_id \"trxptD_ORF4\"",
+                          # E2
+                          t_id == "transcript_id \"TCONS_00000003\"" ~ "transcript_id \"DBP\"",
+                          t_id == "transcript_id \"TCONS_00000017\"" ~ "transcript_id \"ptp_pol2\"",
+                          t_id == "transcript_id \"TCONS_00000018\"" ~ "transcript_id \"ptp_pol1\"",
+                          t_id == "transcript_id \"TCONS_00000028\"" ~ "transcript_id \"trunc_hypothetical\"",
+                          # E3
+                          t_id == "transcript_id \"TCONS_00000026\"" ~ "transcript_id \"33K_pVIII_E3_Fib\"",
[…]

### 2023-08-23 scripts/r/bam_file_analysis.R

@@ -1,15 +1,16 @@
+#!/usr/bin/env Rscript
 
 library(magrittr)
 library(glue)
 library(tidyverse)
 library(scales)
 
-
+# -------------
 # single_jun_files <- list.files("results/hisat2", full.names = T,
 #                                pattern = "\\w+\\.bed") %>%
 #   setNames(c("t12s1","t12s3", "t24s1", "t24s2", "t24s3","t4s1",
 #              "t4s2", "t4s3", "t72s1", "t72s2", "t72s3"))
-# 
+# # 
 # single_junc_stats <- map_dfr(single_jun_files, read_tsv,
 #                              col_names = F,
 #                              show_col_types = F,
@@ -18,7 +19,7 @@ library(scales)
 #                  "read_count", "strand", "thickStart", "thickEnd",
 #                  "color", "exons", "exon_sizes", "exon_starts")) %>%
 #   arrange(start, end) %>%
-#   distinct(start, end, .keep_all = T) %>% 
+#   distinct(start, end, .keep_all = T) %>%
 #   # convert from 0-base indexing of .bed format to 1-base indexing
 #   mutate(start = start + 1)
 # 
@@ -43,52 +44,113 @@ library(scales)
 # ============================BULK=============================================
 # =============================================================================
 bulk_jun_files <- list.files("results/hisat2/bulk", full.names = T,
-                             pattern = "\\w+\\.bed") %>% 
+                             pattern = "annot_\\d+hrsSS\\.txt") %>% 
   setNames(c("12hpi", "24hpi", "4hpi", "72hpi"))
 
+
 bulk_junc_stats <- map_dfr(bulk_jun_files, read_tsv,
-                           col_names = F,
-                           col_types = c("ciiciciicicc"),
+                           col_types = c("ciicicciiiciiiccc"),
                            show_col_types = F,
                            .id = "timepoint") %>% 
-  set_colnames(c("timepoint", "chrom", "start", "end", "junc_name",
-                 "read_count", "strand", "thickStart", "thickEnd",
-                 "color", "exons", "exon_sizes", "exon_starts")) %>%
-  distinct(start, end, .keep_all = T) %>%
-  # convert from 0-base indexing of .bed format to 1-base indexing
-  mutate(start = start + 1) %>% 
-  arrange(start, end)
+  dplyr::rename(read_count = score) %>%
+  arrange(start, end) %>%
+  mutate(exact_ss = str_replace(splice_site,
[…]

### 2023-08-23 scripts/r/plot_thev_timepoint_splicing.R

@@ -1,3 +1,5 @@
+#!/usr/bin/env Rscript
+
 library(magrittr)
 library(glue)
 library(tidyverse)

### 2023-08-23 scripts/r/splice_site_analyses.R

@@ -3,42 +3,41 @@
 library(magrittr)
 library(scales)
 library(tidyverse)
+library(plyr)
 library(rtracklayer)
 library(glue)
 library(ggsci)
+library(patchwork)
 
 # load in data from from full transcriptome to access the splice sites
-all_spliced_gtf <- import("results/gffcompare/gffcomp_alltimes.combined.gtf") %>%
+all_trxptome_ss <- import("results/gffcompare/updated_alltimes.combined.gtf") %>%
   as_tibble() %>%
-  select(chr = seqnames, start, end, orf_size = width, strand, type, gene_id,
-         transcript_id, exon_number) %>% 
-  group_by(transcript_id, strand) %>%
+  select(chr = seqnames, gene_id, transcript_id, gene_name, strand, type,
+         start, end, orf_size = width, exon_number) %>%
+  filter(type != "transcript") %>%
+  mutate(type = glue("{type}_{exon_number}")) %>%
+  group_by(transcript_id, strand, region = gene_name) %>%
   reframe(start = list(start),
           end = list(end)) %>%
   unnest_wider(c(start, end), names_sep = "_") %>%
-  mutate(region = case_when(transcript_id %in% paste0("TCONS_000000", c('15', '16', '04', '05')) ~ "E1",
-                            transcript_id %in% paste0("TCONS_000000", c('03', '17', '18', '28')) ~ "E2",
-                            transcript_id %in% paste0("TCONS_000000", c('26', '27', '12', '10', '11', '02')) ~ "E3",
-                            transcript_id == "TCONS_00000014" ~ "E4",
-                            transcript_id == "TCONS_00000013" ~ "IM",
-                            TRUE ~ "MLP")) %>% 
-  arrange(strand, region) %>%
-  mutate(j1_ss = end_2, j1_ts = start_3,
-         j2_ss = end_3, j2_ts = start_4,
-         j3_ss = end_4, j3_ts = start_5,
-         j4_ss = end_5, j4_ts = start_6,
-         j5_ss = end_6, j5_ts = start_7,
-         j6_ss = end_7, j6_ts = start_8
-         ) %>% 
+  arrange(region) %>%
+  mutate(j1_ss = end_1, j1_ts = start_2,
+         j2_ss = end_2, j2_ts = start_3,
+         j3_ss = end_3, j3_ts = start_4,
+         j4_ss = end_4, j4_ts = start_5,
+         j5_ss = end_5, j5_ts = start_6,
[…]

### 2023-08-23 scripts/r/thev_cov_depth.R

@@ -6,6 +6,7 @@ library(glue)
 library(patchwork)
 library(ggsci)
 library(ggtext)
+library(grDevices)
 library(tidyverse)
 
 source("scripts/r/thev_genomic_map.R")
@@ -45,7 +46,7 @@ all_depths <- map_dfr(all_depth_files, read_tsv,
   set_colnames(c("timepoint", "genome", "position",
                  "depth", "color", "titles"))
   
-
+# -------------------
 ## split the table into individual time-points and plot iteratively with map()
 each_plot <- all_depths %>% 
   split(.$timepoint) %>% 
@@ -112,22 +113,22 @@ ggsave("patch_alltimes.png",
        plot = p_alltime, path = "results/r/figures",
        width = 12, height = 14, dpi = 1000)
 
+## --------------------
 
-
-compare_all <- all_depths %>%
-  ggplot(aes(position, depth, fill = timepoint, color = timepoint)) +
-  geom_col() +
-  scale_fill_igv(guide = guide_legend(
-    keywidth = unit(1, "cm"),
-    keyheight = unit(1.2, "cm"))) +
+comp_all <- all_depths %>%
+  select(timepoint, position, depth) %>% 
+  mutate(depth = ifelse(depth < 1, 1, depth)) %>% 
+  ggplot(aes(position, sqrt(depth), group = timepoint, fill = timepoint, color = timepoint)) +
+  geom_area(key_glyph = "crossbar") +
+  scale_fill_igv(guide = guide_legend(keywidth = unit(1, "cm"))) +
   scale_color_igv() +
-  scale_y_sqrt(expand = c(0, 0)) +
   scale_x_continuous(expand = c(0, 0),
                      breaks = seq(1000, 26000, 1000),
                      labels = glue("{seq(1,26,1)}kb")) +
-  labs(title = "All timepoint samples",
+  coord_trans(clip = "off", expand = F) +
+  labs(title = "RNA-seq Mapping Depth of THEV Genome",
        x = element_blank(),
-       y = "Mapping Depth",
+       y = expression(sqrt("Mapping Depth")),
        fill = element_blank(),
        color = element_blank()) +
   theme_classic() +
@@ -143,7 +144,7 @@ compare_all <- all_depths %>%
                                   face = "bold", 
                                   hjust = 0.5,
                                   margin = margin(t = 10)),
-        axis.title.y = element_text(size = 18, face = "bold",
+        axis.title.y = element_text(size = 22, face = "bold",
[…]

### 2023-08-23 scripts/r/thev_growthcurve.R

@@ -33,7 +33,7 @@ replicate_data <- read_excel(exp2,
 
 plot_prepped <- replicate_data %>%
   group_by(inf_hrs, hrs_pi) %>% 
-  summarize(mean_conc = mean(conc), 
+  reframe(mean_conc = mean(conc), 
             mean_conc_per_mL = (mean_conc * 10 * 1000),
             replicates = n(),
             stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000,
@@ -101,7 +101,7 @@ plot_prepped <- replicate_data %>%
        # width = 14, height = 8, dpi = 1000)
 
 # add data from first experiment with more time-points (use only extra time-points)
-
+# ---------------------
 exp1 <- "raw_files/wetlab_data/thev_growthcurve2021.xls"
 rep1_data <- read_excel(exp1,
                         sheet = "Results",
@@ -118,8 +118,9 @@ rep1_data <- read_excel(exp1,
          sample_name = str_replace(sample_name,
                                    "([a-zA-Z]+)\\d?-D(\\d)",
                                    "\\1_\\2")) %>% 
-  separate(sample_name, into = c("condition", "day"),
-           sep = "_") %>% 
+  separate_wider_delim(sample_name,
+                       names = c("condition", "day"),
+                       delim = "_") %>% 
   mutate(inf_day = paste0(condition, "_", day),
          day = as.numeric(day),
          hrs_pi = day * 24,
@@ -130,17 +131,15 @@ rep1_data <- read_excel(exp1,
 fulltimes <- bind_rows(replicate_data, rep1_data)
 
 
-full_prepped <- fulltimes %>% 
-group_by(inf_hrs, hrs_pi) %>% 
-  summarize(mean_conc = mean(conc), 
+full_prepped <- fulltimes %>%
+group_by(condition, hrs_pi) %>% 
+  reframe(mean_conc = mean(conc), 
             mean_conc_per_mL = (mean_conc * 10 * 1000),
             replicates = n(),
-            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000,
-            .groups = "drop") %>% 
-  mutate(treatment = str_replace(inf_hrs, "([a-zA-Z]{3})_\\d{1,3}", "\\1"))
+            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000)
 
 growth_curve <- full_prepped %>% 
[…]

### 2023-08-23 scripts/r/thev_splicing_fullMap.R

@@ -1,3 +1,4 @@
+#!/usr/bin/env Rscript
 
 library(magrittr)
 library(ggtext)

### 2023-08-30 manuscript_thev_transcriptome.Rmd
Ballgown trxpt expression analysis and figs

@@
 Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*M.gallopavo*) genomes using the `HISAT2` [@Pertea2016] alignment program.
+Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*M.gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
 A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
@@
 Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs.
-To evaluate the activity of each promoter over time, we estimate relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point.
+To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes, was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time.
+This revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
+Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly overexpressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
+Secondly, we estimated relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point.
 Very few unique splice junctions and reads were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
@@
 At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions was not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
-Also see __Supplementary Tables 1a-c__; __Figure 4a__).
-When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 4b__).
-
+Also see __Supplementary Tables 1a-c__; __Figure 5a__).
+When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 5b__).
 Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
@@
 
+![](results/r/figures/trxpt_fpkm_percent_abund.png)
+
+![](results/r/figures/region_fpkm_percent_abund.png)
+**Figure 4 Overview of change in expression of THEV transcripts over time.** 
+**a)** 
+**b)**
+
 ![](results/r/figures/junc_abundances.png)
-**Figure 4.
+**Figure 5.
 a) Relative abundances of splice junctions over time as a proxy of estimating activity levels of THEV promoters**.

### 2023-08-30 scripts/r/ballgown.R

@@ -30,41 +30,160 @@ raw_data <- ballgown(dataDir = "results/ballgown",
                         pData = exp_info,
                        bamfiles = bam_files)
 
-# load in annotated ORFs from NCBI
-pred_orfs <- gffReadGR("raw_files/annotations/thev_predicted_genes.gtf",
-                       splitByTranscript = T)
 
-# annotate assembled transcripts with predicted ORFs from NCBI
-assembled_trxpts <- structure(raw_data)$trans
-trxpt_anno <- annotate_assembly(assembled_trxpts, pred_orfs)
-
-ballgown::plotMeans("XLOC_000001", raw_data, groupvar = "timepoint",
-                    groupname = "all" ,labelTranscripts = T)
-
-
-structure(raw_data)$exon
-
-ex_exp_levels <- eexpr(raw_data)
-
-# plot transcript expression levels
-t_exp_levels <- texpr(raw_data, meas = "all")
-
-t_exp_levels %>%
+# extract transcript expression level data
+t_exp_levels <- texpr(raw_data, meas = "all") %>%
   as_tibble() %>%
   pivot_longer(cols = starts_with("FPKM"),
                names_to = "samples",
                values_to = "fpkm") %>%
-  mutate(fpkm = log2(fpkm + 1),
-         samples = factor(samples,
-                          levels = c("FPKM.abund_4hrsS1", "FPKM.abund_4hrsS2",
-                                     "FPKM.abund_12hrsS1", "FPKM.abund_12hrsS3",
-                                     "FPKM.abund_24hrsS1", "FPKM.abund_24hrsS2",
-                                     "FPKM.abund_24hrsS3", "FPKM.abund_72hrsS1",
-                                     "FPKM.abund_72hrsS2", "FPKM.abund_72hrsS3")),
-         timepoint = case_when(str_detect(samples, "_4hrs") ~ "4h.p.i",
+  mutate(timepoint = case_when(str_detect(samples, "_4hrs") ~ "4h.p.i",
                                str_detect(samples, "_12hrs") ~ "12h.p.i",
                                str_detect(samples, "_24hrs") ~ "24h.p.i",
-                               str_detect(samples, "_72hrs") ~ "72h.p.i"),
+                               str_detect(samples, "_72hrs") ~ "72h.p.i",
+                               TRUE ~ NA_character_),
+         timepoint = factor(timepoint,
[…]

### 2023-08-31 manuscript_thev_transcriptome.Rmd
Reduce figure resolutions and fix mardown pdf

@@
 title: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus
-always_allow_html: true
 output:
-  # word_document: default
-  html_document: default
+  word_document: default
+  pdf_document: default
 geometry: margin=1in
@@
   - \linenumbers
+  - \usepackage{booktabs}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
+  - \usepackage{wrapfig}
+  - \usepackage{float}
+  - \usepackage{colortbl}
+  - \usepackage{pdflscape}
+  - \usepackage{tabu}
+  - \usepackage{threeparttable}
+  - \usepackage{threeparttablex}
+  - \usepackage[normalem]{ulem}
+  - \usepackage{makecell}
+  - \usepackage{xcolor}
 bibliography: transcriptome_refs.bib
@@
 library(scales)
-library(gt)
+library(kableExtra)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 ```{r}
-gt(tab1) %>%
-  fmt_markdown()
+tab1 %>%
+kbl(format = "latex", booktabs = T) %>%
+  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
+  row_spec(0, font_size = 15) %>%
+  column_spec(1, bold = T)
+
 ```
@@
 ```{r}
-gt(sig_12_juncs)
+sig_12_juncs%>%
+  kbl(format = "latex", booktabs = T) %>%
+  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
+  row_spec(0, font_size = 15)
 ```
@@
 ```{r}
-gt(sig_24_juncs)
+sig_24_juncs %>%
+  kbl(format = "latex", booktabs = T) %>%
+  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
+  row_spec(0, font_size = 15)
 ```
@@
 ```{r}
-gt(sig_72_juncs)
+sig_72_juncs %>%
+  kbl(format = "latex") %>%
+  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
+  row_spec(0, font_size = 15)
 ```

### 2023-08-31 scripts/r/ballgown.R

@@ -1,4 +1,4 @@
-
+#!/usr/bin/env Rscript
 
 library(ballgown)
 library(devtools)
@@ -95,7 +95,7 @@ reg_fpkms <- t_exp_lev_byregion %>%
   ))
 
 ggsave(plot = reg_fpkms, "results/r/figures/region_fpkm_percent_abund.png",
-       width = 18, height = 12, dpi = 1000)
+       width = 18, height = 12, dpi = 500)
 ## ---------------------
 # expression levels by transcript
 t_expr_each <- t_exp_levels %>%
@@ -177,7 +177,7 @@ trxpt_fpkms <- t_expr_each %>%
         legend.text.align = 0)
 
 ggsave(plot = trxpt_fpkms, "results/r/figures/trxpt_fpkm_percent_abund.png",
-       width = 18, height = 12, dpi = 1000)
+       width = 18, height = 12, dpi = 500)
 
 # ------------------------------
 # distribution of fpkm levels in samples
@@ -206,15 +206,8 @@ fpkm_dist <- t_exp_levels %>%
         legend.key.size = unit(1, "cm"),
         legend.text = element_text(size = 14, face = "bold"))
 
-# plot transcript maps
-plotTranscripts(unique(geneIDs(raw_data))[1], raw_data, 
-                samples = c(pData(raw_data) %>% select(sample_name) %>% pull()),
-                legend = T,
-                labelTranscripts = T)
-
-
 ggsave(plot = fpkm_dist, "results/r/figures/fpkm_dist_by_time.png",
-       width = 14, height = 10, dpi = 1000)
+       width = 14, height = 10, dpi = 500)
 
 
 

### 2023-08-31 scripts/r/bam_file_analysis.R

@@ -184,18 +184,18 @@ join_stats <- left_join(all_covs, bulk_sum_stats, by = c("timepoint", "organism"
 # ------------------
 # For Table 1
 tab1 <- tibble(Metric = c("Total reads",
-                          "Mapped<br>(Host)",
-                          "Mapped<br>(THEV)",
-                          "Mean Per Base<br>Coverage/Depth",
-                          "Total unique <br>splice junctions",
-                          "Junction coverage<br>Total (≥ 1 read)",
-                          "Junction coverage<br> Mean reads",
-                          "Junction coverage<br>≥ 10 reads",
-                          "Junction coverage<br>≥ 100 reads",
-                          "Junction coverage<br>≥ 1000 reads"),
+                          "Mapped\n(Host)",
+                          "Mapped\n(THEV)",
+                          "Mean Per Base\nCoverage/Depth",
+                          "Total unique \nsplice junctions",
+                          "Junction coverage\nTotal (at least 1 read)",
+                          "Junction coverage\nMean reads",
+                          "Junction coverage\n(at least 10 reads)",
+                          "Junction coverage\n(at least 100 reads)",
+                          "Junction coverage\n(at least 1000 reads)"),
               "4h.p.i" = c(all_covs$total_reads[1],
-                           glue("{all_covs$total_mapped[1]}<br>({all_covs$perc_mapped[1]}%)"),
-                           glue("{all_covs$total_mapped[5]}<br>({all_covs$perc_mapped[5]}%)"),
+                           glue("{all_covs$total_mapped[1]}\n({all_covs$perc_mapped[1]}%)"),
+                           glue("{all_covs$total_mapped[5]}\n({all_covs$perc_mapped[5]}%)"),
                            as.numeric(join_stats$mean_depth[5]),
                            join_stats$total_unq_juncs[5],
                            join_stats$total_reads_tp[5],
@@ -204,8 +204,8 @@ tab1 <- tibble(Metric = c("Total reads",
                            join_stats$reads100[5],
                            join_stats$reads1000[5]),
               "12h.p.i" = c(all_covs$total_reads[2],
-                            glue("{all_covs$total_mapped[2]}<br>({all_covs$perc_mapped[2]}%)"),
-                            glue("{all_covs$total_mapped[6]}<br>({all_covs$perc_mapped[6]}%)"),
[…]

### 2023-08-31 scripts/r/plot_thev_timepoint_splicing.R

@@ -192,7 +192,7 @@ tp_trxptome <- list.files("results/stringtie",
 #   catch_timepoint <- str_extract(gtf_file, "\\d+") %>% paste0(., "hpi")
 #   graph_trxpts(gtf_file)
 #   ggsave(filename = glue("results/r/figures/thev_spliced_map_{catch_timepoint}.png"),
-#          dpi = 1000, width = 12, height = 8)
+#          dpi = 500, width = 12, height = 8)
 # }
 
 p12 <- graph_trxpts(tp_trxptome[1])
@@ -206,7 +206,8 @@ all_plots <- (p4/ p12 / p24 / p72) +
   plot_annotation(tag_levels = "1", tag_prefix = "B") &
   theme(plot.tag = element_text(size = 22, face = "bold"))
 
-ggsave(plot = all_plots, filename = "results/r/figures/thev_patched_timepoints_spliced_map.png",
-                dpi = 1000, width = 12, height = 10.5)
+ggsave(plot = all_plots,
+       filename = "results/r/figures/thev_patched_timepoints_spliced_map.png",
+       dpi = 500, width = 12, height = 10.5)
 
 

### 2023-08-31 scripts/r/splice_site_analyses.R

@@ -217,7 +217,7 @@ trxptome_juncs <- plot_time_genexpression(bulk_count_trxptome_ss) +
 
 # ggsave(plot = trxptome_juncs,
 #        filename = "results/r/figures/temporal_gene_expression.png",
-#        dpi = 1000, width = 14, height = 12)
+#        dpi = 500, width = 14, height = 12)
 
 
 # prepare data to plot abundances of all juncs extracted from BAM files
@@ -254,7 +254,7 @@ patch_expr <- (all_juncs | trxptome_juncs) +
 
 ggsave("junc_abundances.png",
        plot = patch_expr, path = "results/r/figures",
-       width = 20, height = 12, dpi = 1000)
+       width = 20, height = 12, dpi = 500)
 
 
 # -------------------

### 2023-08-31 scripts/r/thev_cov_depth.R

@@ -111,7 +111,7 @@ p_alltime <- (each_plot$`4hpi`/each_plot$`12hpi`/each_plot$`24hpi`/each_plot$`72
 
 ggsave("patch_alltimes.png",
        plot = p_alltime, path = "results/r/figures",
-       width = 12, height = 14, dpi = 1000)
+       width = 12, height = 14, dpi = 500)
 
 ## --------------------
 
@@ -160,7 +160,7 @@ compare_all <- (comp_all/genome) +
 
 ggsave("overlay_alltimes.png",
        plot = compare_all, path = "results/r/figures",
-       width = 15, height = 10, dpi = 1000)
+       width = 15, height = 10, dpi = 500)
 
 
 ################# coverage data #########################
@@ -243,4 +243,4 @@ corr <- cov_thev %>%
 
 ggsave("correlate_alltimes.png",
        plot = corr, path = "results/r/figures",
-       width = 20, height = 14, dpi = 1000)
+       width = 20, height = 14, dpi = 500)

### 2023-08-31 scripts/r/thev_growthcurve.R

@@ -98,7 +98,7 @@ plot_prepped <- replicate_data %>%
 #         legend.position = c(0.1, 0.7)
 #   )
 # ggsave(filename = "qpcr/plots/thev_growth_curve_2023.png",
-       # width = 14, height = 8, dpi = 1000)
+       # width = 14, height = 8, dpi = 500)
 
 # add data from first experiment with more time-points (use only extra time-points)
 # ---------------------
@@ -191,6 +191,6 @@ growth_curve <- full_prepped %>%
   )
 
 ggsave(plot = growth_curve, filename = "results/r/figures/thev_growth_curve.png",
-       width = 14, height = 8, dpi = 1000)
+       width = 14, height = 8, dpi = 500)
 
 

### 2023-08-31 scripts/r/thev_orf_map.R

@@ -105,4 +105,4 @@ make_genomic_map2 <- function(bedfile){
 predicted_genemap <- make_genomic_map2("raw_files/annotations/THEVannotated_genesOnly.bed")
 
 ggsave(plot = predicted_genemap, filename = "results/r/figures/thev_orf_map.png",
-       dpi = 1000, width = 12, height = 7)
+       dpi = 500, width = 12, height = 7)

### 2023-08-31 scripts/r/thev_splicing_fullMap.R

@@ -237,6 +237,6 @@ plot_full_trxptome <- function(combined_gtf){
 
 ggsave(plot = plot_full_trxptome(combined_gtf),
        filename = "results/r/figures/thev_spliced_map.png",
-       dpi = 1000, width = 12, height = 8)
+       dpi = 500, width = 12, height = 8)
 
 

### 2023-08-31 scripts/r/stringtie_abundances.R
removed trxpt abund counts from stringtie assembly

@@ -1,76 +1,0 @@
-
-library(tidyverse)
-library(magrittr)
-library(ggsci)
-
-# load in stringtie abundance tables
-files <- list.files("results/stringtie/", pattern = "t\\d{1,2}S\\d\\.tab",
-                    full.names = T) %>% 
-  setNames(c("12h.p.i", "12h.p.i", "24h.p.i", "24h.p.i", "24h.p.i", "4h.p.i",
-             "4h.p.i", "72h.p.i", "72h.p.i", "72h.p.i"))
-
-stringtie_abun <- map_dfr(files, read_tsv,
-                          show_col_types = F,
-                          .id = "timepoint") %>%
-  dplyr::rename(gene_name = "Gene Name", gene_id = "Gene ID", strand = Strand,
-         start = Start, end = End, coverage = Coverage, fpkm = FPKM, tpm = TPM) %>% 
-  mutate(gene_name = ifelse(gene_name == "-", "unknown", gene_name)) %>% 
-  split(.$timepoint) %>% 
-  map(mutate, tot_fpkm_time = sum(fpkm)) %>% 
-  do.call("rbind", .) %>% 
-  as_tibble() %>%
-  select(-c(gene_id)) %>%
-  group_by(timepoint, gene_name) %>%
-  reframe(count = n(),
-          tot_fpkm_time = tot_fpkm_time,
-          sum_fpkm = sum(fpkm),
-          perc_fpkm = (sum_fpkm / tot_fpkm_time) * 100) %>% 
-  unique()
-
-stringtie_abun %>% 
-  filter(!gene_name == "unknown") %>%
-  mutate(timepoint = factor(timepoint,
-                            levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>% 
-  ggplot(aes(gene_name, perc_fpkm, fill = timepoint)) +
-  geom_col(position = position_dodge(0.7), width = 0.4) +
-  scale_fill_jama() +
-  theme_classic()
-
-
-## plotting values from python script: pile_reads_to_orfs.py
-
-
-# load in stringtie abundance tables
-py_files <- list.files("results/hisat2/bulk", pattern = "subsetTHEV_\\d{1,2}hrs.bam_pileup.csv",
-                    full.names = T) %>% 
-  setNames(c("12h.p.i", "24h.p.i","4h.p.i", "72h.p.i"))
-
-orf_read_pileups <- map_dfr(py_files, read_csv,
[…]

### 2023-08-31 supplementary_thev_trxptome.Rmd
Rerun project after deleting stringtie abund files

@@
 ```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
 library(knitr)

### 2023-09-01 manuscript_thev_transcriptome.Rmd
Fixed tables in manuscript with flextables

@@
 library(scales)
-library(kableExtra)
+library(flextable)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(tab.cap.pre = "", tab.cap.sep = "")
 
@@
 Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.
+\newpage
 
 ```{r}
-tab1 %>%
-kbl(format = "latex", booktabs = T) %>%
-  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
-  row_spec(0, font_size = 15) %>%
-  column_spec(1, bold = T)
+#| tab.id: NULL
+#| tab.cap.pre: ""
+#| tab.cap.sep: ""
+
+set_flextable_defaults(font.size = 8)
+t1 <- flextable(tab1) %>% theme_zebra() %>%
+  set_table_properties(layout = "fixed", width = 0.95,
+                       opts_pdf = list(caption_repeat = F)) %>%
+  font(part = "all", fontname = "Avenir") %>%
+  width(., j = "Metric", 1.5) %>%
+  set_caption("Overview of sequencing results",
+              style = "Table Caption")
+bold(t1, j = "Metric", bold = T)
 
 ```
+\newpage
 
@@
 
+\newpage
 ![](results/r/figures/thev_spliced_map.png)
@@
 
-**Table 2A**
+\newpage
 
 ```{r}
-sig_12_juncs%>%
-  kbl(format = "latex", booktabs = T) %>%
-  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
-  row_spec(0, font_size = 15)
+#| tab.id: NULL
+#| tab.cap.pre: ""
+#| tab.cap.sep: ""
+set_flextable_defaults(font.size = 8)
+flextable(sig_12_juncs) %>% theme_zebra() %>%
+  set_table_properties(layout = "fixed", width = 1,
+                       opts_pdf = list(caption_repeat = F)) %>%
+  font(part = "all", fontname = "Avenir") %>%
+  set_caption("Table 2a: Most abundant splice junctions at 12h.p.i",
+              style = "Table Caption")
 ```
-
-**Table 2B**
+\newpage
 
 ```{r}
-sig_24_juncs %>%
-  kbl(format = "latex", booktabs = T) %>%
-  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
-  row_spec(0, font_size = 15)
+#| tab.id: NULL
+set_flextable_defaults(font.size = 8)
+flextable(sig_24_juncs) %>% theme_zebra() %>%
+  set_table_properties(layout = "fixed", width = 1,
+                       opts_pdf = list(caption_repeat = F)) %>%
+  font(part = "all", fontname = "Avenir") %>%
+  set_caption("Table 2b: Most abundant splice junctions at 24h.p.i",
+              style = "Table Caption")
 ```
-
-**Table 2C**
+\newpage
 
 ```{r}
-sig_72_juncs %>%
-  kbl(format = "latex") %>%
-  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>%
-  row_spec(0, font_size = 15)
+#| tab.id: NULL
+set_flextable_defaults(font.size = 8)
+flextable(sig_72_juncs) %>% theme_zebra() %>%
+  set_table_properties(layout = "fixed", width = 1,
+                       opts_pdf = list(caption_repeat = F)) %>%
+  font(part = "all", fontname = "Avenir") %>%
+  set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
+              style = "Table Caption")
 ```
+\newpage
 
@@
 
+\newpage
 ![](results/r/figures/junc_abundances.png)

### 2023-09-01 supplementary_thev_trxptome.Rmd
Fixed tables in manuscript with flextables

--- 2023-08-23 supplementary_thev_trxptome.Rmd
@@
 library(gt)
-
+library(kableExtra)
 source("scripts/r/bam_file_analysis.R")

### 2023-09-01 scripts/r/bam_file_analysis.R

@@ -184,18 +184,18 @@ join_stats <- left_join(all_covs, bulk_sum_stats, by = c("timepoint", "organism"
 # ------------------
 # For Table 1
 tab1 <- tibble(Metric = c("Total reads",
-                          "Mapped\n(Host)",
-                          "Mapped\n(THEV)",
-                          "Mean Per Base\nCoverage/Depth",
-                          "Total unique \nsplice junctions",
-                          "Junction coverage\nTotal (at least 1 read)",
-                          "Junction coverage\nMean reads",
-                          "Junction coverage\n(at least 10 reads)",
-                          "Junction coverage\n(at least 100 reads)",
-                          "Junction coverage\n(at least 1000 reads)"),
+                          "Mapped \n (Host)",
+                          "Mapped \n (THEV)",
+                          "Mean Per Base \n Coverage/Depth",
+                          "Total unique \n splice junctions",
+                          "Junction coverage \n Total (at least 1 read)",
+                          "Junction coverage \n Mean reads",
+                          "Junction coverage \n (at least 10 reads)",
+                          "Junction coverage \n (at least 100 reads)",
+                          "Junction coverage \n (at least 1000 reads)"),
               "4h.p.i" = c(all_covs$total_reads[1],
-                           glue("{all_covs$total_mapped[1]}\n({all_covs$perc_mapped[1]}%)"),
-                           glue("{all_covs$total_mapped[5]}\n({all_covs$perc_mapped[5]}%)"),
+                           glue("{all_covs$total_mapped[1]} \n ({all_covs$perc_mapped[1]}%)"),
+                           glue("{all_covs$total_mapped[5]} \n ({all_covs$perc_mapped[5]}%)"),
                            as.numeric(join_stats$mean_depth[5]),
                            join_stats$total_unq_juncs[5],
                            join_stats$total_reads_tp[5],
@@ -204,8 +204,8 @@ tab1 <- tibble(Metric = c("Total reads",
                            join_stats$reads100[5],
                            join_stats$reads1000[5]),
               "12h.p.i" = c(all_covs$total_reads[2],
-                            glue("{all_covs$total_mapped[2]}\n({all_covs$perc_mapped[2]}%)"),
-                            glue("{all_covs$total_mapped[6]}\n({all_covs$perc_mapped[6]}%)"),
[…]

### 2023-09-01 manuscript_thev_transcriptome.Rmd
Fixed table sizes in pdf

@@
 set_flextable_defaults(font.size = 8)
-t1 <- flextable(tab1) %>% theme_zebra() %>%
-  set_table_properties(layout = "fixed", width = 0.95,
+flextable(tab1) %>% theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed", width = 0.95,
                        opts_pdf = list(caption_repeat = F)) %>%
-  font(part = "all", fontname = "Avenir") %>%
-  width(., j = "Metric", 1.5) %>%
-  set_caption("Overview of sequencing results",
-              style = "Table Caption")
-bold(t1, j = "Metric", bold = T)
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::width(., j = ~ Metric, width = 1.5) %>%
+  flextable::set_caption("Overview of sequencing results",
+              style = "Table Caption") %>%
+  flextable::bold(part = "body", j = ~ Metric)
 
@@
 flextable(sig_12_juncs) %>% theme_zebra() %>%
-  set_table_properties(layout = "fixed", width = 1,
+  flextable::set_table_properties(layout = "fixed", width = 1,
                        opts_pdf = list(caption_repeat = F)) %>%
-  font(part = "all", fontname = "Avenir") %>%
-  set_caption("Table 2a: Most abundant splice junctions at 12h.p.i",
-              style = "Table Caption")
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::set_caption("Table 2a: Most abundant splice junctions at 12h.p.i",
+              style = "Table Caption") %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::width(., width = 0.7) %>%
+  flextable::width(., j = ~ Reads_Percentage, width = 1)
 ```
@@
 flextable(sig_24_juncs) %>% theme_zebra() %>%
-  set_table_properties(layout = "fixed", width = 1,
+  flextable::set_table_properties(layout = "fixed", width = 1,
                        opts_pdf = list(caption_repeat = F)) %>%
-  font(part = "all", fontname = "Avenir") %>%
-  set_caption("Table 2b: Most abundant splice junctions at 24h.p.i",
-              style = "Table Caption")
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::set_caption("Table 2b: Most abundant splice junctions at 24h.p.i",
+              style = "Table Caption") %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::width(., width = 0.7) %>%
+  flextable::width(., j = ~ Reads_Percentage, width = 1)
 ```
@@
 flextable(sig_72_juncs) %>% theme_zebra() %>%
-  set_table_properties(layout = "fixed", width = 1,
+  flextable::set_table_properties(layout = "fixed", width = 1,
                        opts_pdf = list(caption_repeat = F)) %>%
-  font(part = "all", fontname = "Avenir") %>%
-  set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
-              style = "Table Caption")
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
+              style = "Table Caption") %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::width(., width = 0.7) %>%
+  flextable::width(., j = ~ Reads_Percentage, width = 1)
 ```

### 2023-09-04 manuscript_thev_transcriptome.Rmd
make abundance plots ready as one figure

@@
 
-**Changes in THEV splice junction profile over time**   
+**Changes in THEV splicing profile over time**   
 AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU).
@@
 To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes, was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time.
-This revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
+Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
 Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly overexpressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
 Secondly, we estimated relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point.
-Very few unique splice junctions and reads were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
 At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were predominantly early region (E1, E2, and E3) junctions, albeit a significant proportion are MLP-derived (__Table 2a__).
@@
 At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions was not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
-Also see __Supplementary Tables 1a-c__; __Figure 5a__).
-When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 5b__).
+Also see __Supplementary Tables 1a-c__; __Figure 4c__).
+When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 4d__).
 Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
@@
 **Early Region 1 (E1) transcripts**.
-This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell.
+This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell but at low levels [@Zhao2014].
 The host transcription machinery is solely responsible for the transcription of this region.
@@
 ![](results/r/figures/region_fpkm_percent_abund.png)
-**Figure 4 Overview of change in expression of THEV transcripts over time.** 
-**a)** 
-**b)**
+**Figure 4 Changes in splicing and expression profile of THEV over time.** 
+**a)** Expression levels of transcripts over time.
+**b)** Expression levels of transcripts by region over time.
 
@@
 ![](results/r/figures/junc_abundances.png)
-**Figure 5.
-a) Relative abundances of splice junctions over time as a proxy of estimating activity levels of THEV promoters**.
-## Description here ##########.
-**b) Relative abundances of junctions in final transcriptome**.
-##Description here #######.
+**c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in final transcriptome.

### 2023-09-04 scripts/r/bam_file_analysis.R

@@ -271,7 +271,6 @@ find_sig_juncs <- function(tp){
     left_join(meta_dt, est, by = join_by(timepoint, start, end)) %>%
     filter(perc >= 1) %>%
     arrange(desc(perc)) %>%
-    distinct(start, end, .keep_all = T) %>%
     mutate(tot_tp_j_rds = comma(tot_tp_j_rds),
            intron_len = comma(intron_len),
            counts_percent = glue("{tot_tp_j_rds} ({perc}%)")) %>%

### 2023-09-04 scripts/r/splice_site_analyses.R

@@ -61,36 +61,6 @@ unq_trxptome_juncs <- rbind(get_junc_pair("j1_ss", "j1_ts"), get_junc_pair("j2_s
 # load in counted splice sites from regtools output to quantify 
 # the splices sites of any specified region 
 # -----------------
-# single_jun_files <- list.files("results/hisat2", full.names = T,
-#                                pattern = "\\w+\\.bed") %>%
-#   setNames(c("t12s1","t12s3", "t24s1", "t24s2", "t24s3","t4s1",
-#              "t4s2", "t4s3", "t72s1", "t72s2", "t72s3"))
-# 
-# single_junc_stats <- map_dfr(single_jun_files, read_tsv,
-#                              col_names = F,
-#                              show_col_types = F,
-#                              col_types = c("ciiciciicicc"),
-#                              .id = "timepoint") %>%
-#   set_colnames(c("timepoint", "chrom", "start", "end", "junc_name",
-#                  "read_count", "strand", "thickStart", "thickEnd",
-#                  "color", "exons", "exon_sizes", "exon_starts")) %>%
-#   arrange(start, end) %>%
-#   mutate(timepoint = case_when(timepoint %in% glue("t4s{c(1,2,3)}") ~ "4hpi",
-#                                timepoint %in% glue("t12s{c(1,3)}") ~ "12hpi",
-#                                timepoint %in% glue("t24s{c(1,2,3)}") ~ "24hpi",
-#                                timepoint %in% glue("t72s{c(1,2,3)}") ~ "72hpi",
-#                                TRUE ~ timepoint)) %>% 
-#   separate(exon_sizes, c("exon1size", "exon2size"), sep = ",", convert = T) %>%
-#   mutate(junc_ss = start + exon1size,
-#          junc_ts = (end - exon2size) + 1) %>%
-  # select(timepoint, strand, junc_ss, junc_ts, read_count) %>%
-  # group_by(timepoint, junc_ss, junc_ts) %>%
-  # reframe(count_accumul_juncs = n(),
-  #         tot_rds_j_time = sum(read_count))
-
-
-# -----------------
-
 
 bulk_jun_files <- list.files("results/hisat2/bulk", full.names = T,
                              pattern = "annot_\\d+hrsSS\\.txt") %>% 
@@ -100,29 +70,52 @@ bulk_jun_files <- list.files("results/hisat2/bulk", full.names = T,
[…]

### 2023-09-05 manuscript_thev_transcriptome.Rmd
reorganize scripts to make reg-by-reg data  tables

@@
 source("scripts/r/thev_splicing_fullMap.R")
+source("scripts/r/abundance_analyses.R")
 
@@
 After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
-We discovered four novel transcripts in this region with varying protein-coding potential (PCP).
+Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered four novel transcripts in this region (__Figure 5__).
+The abundance of the transcripts and splice junctions varied over time.
+The most abundant was #### at #### and
 
@@
 Early Region 2A (E2A) transcripts.
+some with multiple protein-coding potential (PCP)
 
@@
 **c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in final transcriptome.
+
+```{r region-by-region_e1_figure}
+set_flextable_defaults(font.size = 8)
+flextable(reg_e1_brkdown) %>% theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Site", region = "Region",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               coding_potential = "Protein Coding Potential",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i") %>%
+  flextable::width(., width = 0.6) %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))
+```

### 2023-09-05 scripts/r/abundance_analyses.R

@@ -1,0 +1,433 @@
+#!/usr/bin/env Rscript
+
+library(magrittr)
+library(scales)
+library(plyr)
+library(rtracklayer)
+library(glue)
+library(ballgown)
+library(devtools)
+library(genefilter)
+library(tidyverse)
+
+# load in data from from full transcriptome to access the splice sites
+all_trxptome_ss <- import("results/gffcompare/updated_alltimes.combined.gtf") %>%
+  as_tibble() %>%
+  select(chr = seqnames, gene_id, transcript_id, gene_name, strand, type,
+         start, end, orf_size = width, exon_number) %>%
+  filter(type != "transcript") %>%
+  mutate(type = glue("{type}_{exon_number}")) %>%
+  group_by(transcript_id, strand, region = gene_name) %>%
+  reframe(start = list(start),
+          end = list(end)) %>%
+  unnest_wider(c(start, end), names_sep = "_") %>%
+  arrange(region) %>%
+  mutate(j1_ss = end_1, j1_ts = start_2,
+         j2_ss = end_2, j2_ts = start_3,
+         j3_ss = end_3, j3_ts = start_4,
+         j4_ss = end_4, j4_ts = start_5,
+         j5_ss = end_5, j5_ts = start_6,
+         j6_ss = end_6, j6_ts = start_7
+  ) %>% 
+  select(-ends_with("_1"), -starts_with("start"), -starts_with("end")) %>%
+  mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1)))
+
+# extract junction pairs (start and end) to make long format
+get_junc_pair <- function(j_ss, j_ts){
+  return(data.frame(transcript_id = all_trxptome_ss$transcript_id,
+                    trxpt_id = all_trxptome_ss$trxpt_id,
+                    strand = all_trxptome_ss$strand,
+                    region = all_trxptome_ss$region,
+                    junc_ss = all_trxptome_ss %>% select(all_of(j_ss)),
+                    junc_ts = all_trxptome_ss %>% select(all_of(j_ts))
+                    ) %>%
+           set_colnames(c("transcript_name", "trxpt_id", "strand", "region",
+                                  "junc_ss", "junc_ts")) %>%
+           as_tibble()
+  )
+}
+
+# Unique splice junctions in the finalized transcriptome
[…]

### 2023-09-05 scripts/r/ballgown.R

@@ -1,213 +1,6 @@
 #!/usr/bin/env Rscript
 
-library(ballgown)
-library(devtools)
-library(genefilter)
-library(ggsci)
-library(tidyverse)
 
-# make experimental data dataframe
-exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
-                      "abund_12hrsS1", "12h.p.i", "Rep1",
-                      "abund_12hrsS3", "12h.p.i", "Rep3",
-                      "abund_24hrsS1", "24h.p.i", "Rep1",
-                      "abund_24hrsS2", "24h.p.i", "Rep2",
-                      "abund_24hrsS3", "24h.p.i", "Rep3",
-                      "abund_4hrsS1", "4h.p.i", "Rep1",
-                      "abund_4hrsS2", "4h.p.i", "Rep2",
-                      "abund_72hrsS1", "72h.p.i", "Rep1",
-                      "abund_72hrsS2", "72h.p.i", "Rep2",
-                      "abund_72hrsS3", "72h.p.i", "Rep3") %>% data.frame()
-
-# load in expression level files for making ballgown object
-bam_files <- list.files("results/hisat2",
-                        pattern = "^thev_subset_\\d+hrsS\\d\\.bam$",
-                        full.names = T) %>%
-  .[c(1:7, 9:11)]
-  
-raw_data <- ballgown(dataDir = "results/ballgown",
-                        samplePattern = "abund_",
-                        pData = exp_info,
-                       bamfiles = bam_files)
-
-
-# extract transcript expression level data
-t_exp_levels <- texpr(raw_data, meas = "all") %>%
-  as_tibble() %>%
-  pivot_longer(cols = starts_with("FPKM"),
-               names_to = "samples",
-               values_to = "fpkm") %>%
-  mutate(timepoint = case_when(str_detect(samples, "_4hrs") ~ "4h.p.i",
-                               str_detect(samples, "_12hrs") ~ "12h.p.i",
-                               str_detect(samples, "_24hrs") ~ "24h.p.i",
-                               str_detect(samples, "_72hrs") ~ "72h.p.i",
-                               TRUE ~ NA_character_),
-         timepoint = factor(timepoint,
-                            levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>%
-  select(c("timepoint", "t_name", region = "gene_name", "strand", "start", "end", "fpkm")) %>%
[…]

### 2023-09-05 scripts/r/plot_abundances.R

@@ -1,0 +1,252 @@
+#!/usr/bin/env Rscript
+
+library(magrittr)
+library(scales)
+library(tidyverse)
+library(plyr)
+library(rtracklayer)
+library(glue)
+library(ggsci)
+library(patchwork)
+
+## load in analyzed data
+source("scripts/r/abundance_analyses.R")
+
+
+## visualize ---------------------------
+plot_time_genexpression <- function(count_ss){
+  up_lim = max(count_ss$reg_junc_percent) %>% plyr::round_any(., 10, f = ceiling)
+  count_ss %>%
+    filter(timepoint != "4hpi") %>%
+    ggplot(aes(timepoint, reg_junc_percent, group = region, color = region)) +
+    geom_line(linewidth = 3) +
+    geom_point(size = 5) +
+    scale_colour_jco() +
+    scale_y_continuous(expand = c(0.01, 0.01),
+                       breaks = c(seq(0, up_lim, 10)),
+                       labels = scales::label_percent(scale = 1)) +
+    scale_x_discrete(expand = c(0.005, 0.01)) +
+    coord_cartesian(clip = "off") +
+    theme_classic() +
+    theme(plot.margin = margin(rep(30, 4)),
+          panel.grid.major.y = element_line(linewidth = 0.4, color = "grey",
+                                            linetype = "dashed"),
+          axis.title.y = element_text(size = 16, face = "bold", margin = margin(r = 15)),
+          axis.text.x = element_text(size = 16, face = "bold"),
+          axis.text.y = element_text(size = 14, face = "bold"),
+          legend.justification = c(0, 0),
+          legend.position = c(0.05, 0.9),
+          legend.key.width = unit(2, "cm"),
+          legend.title = element_blank(),
+          legend.text = element_text(size = 14, face = "bold", colour = "black"),
+          legend.text.align = 0) +
+    guides(color = guide_legend(label.position = "top",
+                                label.hjust = 0.5,
+                                label.vjust = 1,
+                                direction = "horizontal",
+                                nrow = 1,
+                                ))
+}
+
+
+# plot and save abundances of juncs found in final trxptome
+trxptome_juncs <- plot_time_genexpression(bulk_count_trxptome_ss) +
+  labs(x = element_blank(),
[…]

### 2023-09-05 scripts/r/splice_site_analyses.R

@@ -1,338 +1,0 @@
-#!/usr/bin/env Rscript
-
-library(magrittr)
-library(scales)
-library(tidyverse)
-library(plyr)
-library(rtracklayer)
-library(glue)
-library(ggsci)
-library(patchwork)
-
-# load in data from from full transcriptome to access the splice sites
-all_trxptome_ss <- import("results/gffcompare/updated_alltimes.combined.gtf") %>%
-  as_tibble() %>%
-  select(chr = seqnames, gene_id, transcript_id, gene_name, strand, type,
-         start, end, orf_size = width, exon_number) %>%
-  filter(type != "transcript") %>%
-  mutate(type = glue("{type}_{exon_number}")) %>%
-  group_by(transcript_id, strand, region = gene_name) %>%
-  reframe(start = list(start),
-          end = list(end)) %>%
-  unnest_wider(c(start, end), names_sep = "_") %>%
-  arrange(region) %>%
-  mutate(j1_ss = end_1, j1_ts = start_2,
-         j2_ss = end_2, j2_ts = start_3,
-         j3_ss = end_3, j3_ts = start_4,
-         j4_ss = end_4, j4_ts = start_5,
-         j5_ss = end_5, j5_ts = start_6,
-         j6_ss = end_6, j6_ts = start_7
-  ) %>% 
-  select(-ends_with("_1"), -starts_with("start"), -starts_with("end"))
-
-
-# extract junction pairs (start and end) to make long format
-get_junc_pair <- function(j_ss, j_ts){
-  return(data.frame(transcript_id = all_trxptome_ss$transcript_id,
-             strand = all_trxptome_ss$strand,
-             region = all_trxptome_ss$region,
-             junc_ss = all_trxptome_ss %>% select(all_of(j_ss)),
-             junc_ts = all_trxptome_ss %>% select(all_of(j_ts))
-             ) %>%
-           set_colnames(c("transcript_id", "strand", "region",
-                                  "junc_ss", "junc_ts")) %>%
-           as_tibble()
-  )
-}
-
-# Unique splice junctions in the finalized transcriptome
-unq_trxptome_juncs <- rbind(get_junc_pair("j1_ss", "j1_ts"), get_junc_pair("j2_ss", "j2_ts"),
-                                  get_junc_pair("j3_ss", "j3_ts"), get_junc_pair("j4_ss", "j4_ts"),
[…]

### 2023-09-05 scripts/r/ballgown.R
fixed E4 trxpt position

@@ -1,9 +1,0 @@
-#!/usr/bin/env Rscript
-
-
-
-
-
-
-
- 

### 2023-09-05 manuscript_thev_transcriptome.Rmd
fixed E4 transcript positioning in plot

--- 2023-09-04 manuscript_thev_transcriptome.Rmd
@@
 **c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in final transcriptome.
+
+```{r region-by-region_e1_figure}
+set_flextable_defaults(font.size = 7)
+flextable(reg_e1_brkdown) %>% theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Site", region = "Region",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               coding_potential = "Protein Coding Potential",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i") %>%
+  flextable::width(., width = 0.5) %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))  %>%
+  flextable::width(., j = ~ coding_potential, width = 1)
+```

### 2023-09-05 scripts/r/thev_splicing_fullMap.R

@@ -90,7 +90,7 @@ plot_full_trxptome <- function(combined_gtf){
   # add y-axis positions to negative strand transcripts
   
   ypos_e4 <- combined_gtf %>% filter(region == "E4")
-  ypos_e4$ypos <- rep(c(23, 24), length.out = nrow(ypos_e4))
+  ypos_e4$ypos <- rep(c(22, 23), length.out = nrow(ypos_e4))
   
   ypos_e2 <- combined_gtf %>% filter(region == "E2")
   ypos_e2$ypos <- rep(c(23:18), length.out = nrow(ypos_e2))

### 2023-10-06 manuscript_thev_transcriptome.Rmd
Write manuscript results section For E1, E4, IM, and partially E2 regions Make table of transcripts with validation gels in supplementary PCR section.

--- 2023-09-04 manuscript_thev_transcriptome.Rmd
@@
 library(flextable)
+library(english)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 source("scripts/r/thev_splicing_fullMap.R")
+source("scripts/r/abundance_analyses.R")
+source("scripts/r/reg_by_reg_plots.R")
 
@@
 **Early Region 1 (E1) transcripts**.
-This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell but at low levels [@Zhao2014].
-The host transcription machinery is solely responsible for the transcription of this region.
+This region in MAdVs is the first transcribed after successful entry of the viral DNA into the host cell nucleus, albeit at low levels [@Zhao2014].
+The host transcription machinery solely mediates the transcription of this region.
 After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
-We discovered four novel transcripts in this region with varying protein-coding potential (PCP).
+Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (__Figure 5__).
+Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the Hyd protein as the 3'-most coding sequence (CDS) if the first start codon (SSC) is skipped.
+The 5'-most CDS of TRXPT_1 is multi-exonic, producing a 17.9 kilodalton (kDa) protein of 160 residues [amino acids (aa)].
+The CDS begins in the first exon, starting at position 211, spans the second exon, and terminates in the third exon at position 2312.
+From the 5'-most SSC, TRXPT_2 encodes the largest protein in this region ——  a 64.3 kDa, 580 aa protein with the same SSC as TRXPT_1 (position 211).
+This CDS spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 to 1964 (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of the Hyd STC.
+However, it has an SSC 102 bp upstream and in-frame with ORF1's predicted SSC.
+The N-terminus of TRXPT_2 CDS therefore, shares substantial protein sequence similarity with ORF1 but Hyd and TRXPT_2 are not in-frame; hence no protein sequence similarity.
+TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
+From our analysis, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2; however, given that studies in MAdVs show that E1 mRNAs share a common 5' and 3' positions, only differing from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are truncated, and the TSS just like the transcription termination site (TTS) are identical for all E1 transcripts.
+Regardless of the TSS considered for TRXPT_3, the coding potential remains unaffected.
+Its 5'-most CDS, beginning at 1965 and sharing the same STC as TRXPT_1 and TRXPT_2, produces a 13.1 kDa, 115 residue protein.
+This CDS (ORF4) was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003], but our data suggests it is a bona fide ORF.
+The coding potential of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its coding potential is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
+However, if we assume that TRXPT_4 shares the same TSS as TRXPT_1, then the 5'-most CDS is a distinct multi-exonic 15.9 kDa, 143 aa protein with the same SSC as TRXPT_1 and TRXPT_2 but with a unique STC.
+All splice junctions of the transcripts in this region (except the junction for TRXPT_4) have been validated by cloning and Sanger sequencing of cDNA (__Figure 5b__; __supplementary PCR methods__).
+Finally, during our validation of TRXPT_2, ORF1 was present on the agarose gel and Sanger sequencing results as a bona fide transcript (__supplementary PCR methods__).
+This is corroborated by 3' Rapid Amplification of cDNA Ends (3'RACE) experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing.
+The 5'-most CDS of this transcript would encode ORF1.
+Given that the SSC of the predicted ORF1 is in-frame but downstream of TRXPT_2 SSC, it suggests that the predicted ORF1 CDS is truncated; it shares the same SSC as TRXPT_2, but has a unique STC, albeit it has the same TTS.
 
-~~and also validated the predicted ORF (sialidase; ORF1)~~.
+**Early Region 2 (E2) and Intermediate Region (IM) transcripts**.
+The E2 TU expressed on the reverse strand, is subdivided into E2A and E2B and encodes three classical AdV proteins: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [####].
+Unlike MAdV where two promoters (E2-early and E2-late) were discovered [###], we discovered only a single promoter from which both E2A and E2B transcription is initiated.
+However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs; the E2B transcripts sharing the TTS of the IVa2 transcript of the IM region [####] (__Figure 6__).
+~~Analysis of the coding potential of the transcripts; include the variant of DBP from 3'RACE data~~.
 
-Early Region 2A (E2A) transcripts.
+The IM region is a single-transcript TU, encoding a single classical protein, IVa2.
+The promoter expressing this single transcript (TRXPT_5) is embedded in E2B region and shares a TTS with E2B transcripts [@Donovan2020; @Zhao2014].
+TRXPT_5 is a two-exon transcript located on the reverse strand spliced at 3447-3615.
+The first exon is an untranslated region (UTR), except the last 2 nucleotides, which connect with the first nucleotide of second exon to form the 5'-most SSC.
+This first SSC is 4 codons upstream and in-frame of the predicted IVa2 SSC.
+Regardless of the SSC considered, the encoded protein (IVa2) is largely unaffected.
+Except for the four extra residues at the N-terminus (considering the 5'-most SSC), the entire protein sequence is identical.
 
-Early Region 2B (E2B) transcripts.
+The splice junction of ~~TRXPT_5 add trxpts from E2~~ were confirmed by cloning and Sanger sequencing of cDNA (__supplementary PCR methods__).
 
-Early Region 3 (E3) transcripts.
+**Early Region 3 (E3) transcripts**.
 
-Early Region 4 (E4) transcripts.
+**Early Region 4 (E4) transcripts**.
+This transcription unit (TU) is the found at the tail-end (3'-end) of the genome, on the reverse strand.
+Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the same strand as ORF8 nor transcribed from a promoter in the E4 region, only ORF8 can legitimately be classified as a transcript in this TU.
+This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the reverse strand (__Figure 8__).
+The transcript (TRXPT_28) spans 25192-26247 and is spliced at 25701-26055; hence, a two-exon transcript.
+The second exon fully matches the predicted ORF8 with 12 extra base pairs at the 3'-end; however, the encoded protein is an exact match.
+There is a SSC in the first exon at position 26246 (second nucleotide of the transcript).
+The encoded protein from this SSC is in-frame with the SSC of ORF8 in the second exon; hence, the C-terminus of this longer protein (26.4 kDa, 229 aa) would be the identical to the predicted ORF8 protein.
+The splice junction of TRXPT_28 was validated by cloning and Sanger sequencing of cDNA (__supplementary PCR methods__).
 
-Intermediate Region (IM) transcripts.
-
-Major Late Promoter Region (MLP) transcripts.
+**Major Late Promoter Region (MLP) transcripts**.
 
@@
 ## DISCUSSION/CONCLUSIONS
+In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene.
+However, later studies predicted and preferred Hyd instead of ORF4; hence, the current prediction map.
+However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
 
+TRXPT_2 and ORF1 are isoforms
 \newpage
@@
 **c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in final transcriptome.
+
+```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e1_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Site",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5)) %>%
+  footnote(., i = 2, j = 11, value = as_paragraph(c("Not validated for TRXPT_4")),
+           ref_symbols = c("*"), part = "body")
+
+brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(2, 0.05, 2)) +
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 22, face = "bold"))
+
+```
+
+**Figure 5: E1 region transcripts.
+a)** The splice map of the E1 transcription unit.
+Exons are depicted as boxes connected by introns (dotted lines).
+Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and the previously annotated ORF4 is colored black.
+Each transcript or ORF is labelled with its name to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+
+```{r region-by-region_e2ANDim_figure, fig.height=16, fig.width=18, warning=FALSE}
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e2_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Site",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 2, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
+                                                                  width = 1.5)) %>%
+  footnote(., i = 9, j = 12, value = as_paragraph(c("Truncated transcript")),
+           ref_symbols = c("*"), part = "body")
+
+brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.05, 2))
+
+```
+
+**Figure 6: E2 and IM region transcripts.
+a)** The splice map of the E1 and IM transcription units.
+Exons are depicted as boxes connected by introns (dotted lines).
+Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
+Each transcript or ORF is labelled with its name to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+
+```{r region-by-region_e4_figure, fig.height=5, fig.width=7, warning=FALSE}
+reg_e4_brkdown <- reg_e4_brkdown %>%
+  mutate(splice_site = "GT-AG",
+         `4hpi` = as.numeric(`4hpi`), `12hpi` = as.numeric(`12hpi`),
+         `24hpi` = as.numeric(`24hpi`), `72hpi` = as.numeric(`72hpi`)) %>%
+  select(-c(coding_potential, region)) %>%
+  group_by(trxpt_id, start, end, splice_site, intron_len, strand, status) %>%
+  reframe("4hpi" = sum(`4hpi`),
+          "12hpi" = sum(`12hpi`),
+          "24hpi" = sum(`24hpi`),
+          "72hpi" = sum(`72hpi`)) %>%
+  select(trxpt_id, start, end, splice_site, intron_len, strand, "4hpi", "12hpi",
+         "24hpi", "72hpi", status)
+
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e4_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Site",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))
+
+brkdwn_e4_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.01, 1)) +
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 18, face = "bold"))
+
+```
+
+**Figure 8:  E4 region transcripts.
+a)** The splice map of the E4 transcription unit.
+Exons are depicted as boxes connected by introns (dotted lines).
+The transcript from RNA-seq data is colored red and the predicted ORF, grey.
+The transcript and ORF are labelled with their names to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junction are indicated.
+
+```{r region-by-region_im_figure, fig.height=5, fig.width=10, warning=FALSE, include=FALSE}
+reg_im_brkdown <- reg_im_brkdown %>%
+  mutate(trxpt_id = "TRXPT_5")
+
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_im_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Site",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))
+
+brkdwn_im_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.01, 1)) +
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 18, face = "bold"))
+
+```
+
+<!-- **Figure 9 IM region transcripts. a)** The splice map of the IM transcription unit. **b)** The sequence reads covering the splice junction are indicated. -->

### 2023-10-06 supplementary_thev_trxptome.Rmd
Write manuscript results section For E1, E4, IM, and partially E2 regions Make table of transcripts with validation gels in supplementary PCR section.

--- 2023-08-23 supplementary_thev_trxptome.Rmd
@@
 ```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
 library(knitr)
 library(tidyverse)
-library(gt)
-
+library(flextable)
 source("scripts/r/bam_file_analysis.R")
+source("scripts/r/reg_by_reg_plots.R")
 ```
@@
 ```{r Sup Table 1A}
-gt(tp_reg_expr_12)
+flextable(tp_reg_expr_12) %>% theme_zebra()
 ```
@@
 ```{r Sup Table 1B}
-gt(tp_reg_expr_24)
+flextable(tp_reg_expr_24) %>% theme_zebra()
 ```
@@
 ```{r Sup Table 1C}
-gt(tp_reg_expr_72)
+flextable(tp_reg_expr_72) %>% theme_zebra()
 ```
+
+\newpage
+## Supplementary PCR Methods
+```{r Supplementary PCR Methods}
+set_flextable_defaults(font.size = 4)
+
+flextable(supp_pcr_meth_tab) %>%
+  theme_zebra() %>%
+  flextable::fontsize(j = c("forwardP", "reverseP"), size = 3) %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::width(., width = 0.3) %>% 
+  colformat_image(j = "gel_image", i = c(1, 3:6), na_str = "-",
+                  width = 1, height = 1) %>%
+  flextable::width(j = ~forwardP, width = 1) %>%
+  flextable::width(j = ~reverseP, width = 1) %>%
+  flextable::width(j = ~valid_status, width = 0.4) %>%
+  flextable::width(j = ~gel_image, width = 1) %>% 
+  footnote(., i = c(1:6), j = 12, value = as_paragraph(c("Primer binds exon 1")),
+           ref_symbols = c("a"), part = "body") %>%
+  footnote(., i = c(1:6), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
+           ref_symbols = c("b"), part = "body")
+```

### 2023-10-06 scripts/r/abundance_analyses.R

@@ -10,7 +10,131 @@ library(devtools)
 library(genefilter)
 library(tidyverse)
 
+
+# ====================================================================
+# TRANSCRIPT ABUNDANCE ANALYSIS WITH BALLGOWN
+# ====================================================================
+
+# make experimental data dataframe
+exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
+                    "abund_12hrsS1", "12h.p.i", "Rep1",
+                    "abund_12hrsS3", "12h.p.i", "Rep3",
+                    "abund_24hrsS1", "24h.p.i", "Rep1",
+                    "abund_24hrsS2", "24h.p.i", "Rep2",
+                    "abund_24hrsS3", "24h.p.i", "Rep3",
+                    "abund_4hrsS1", "4h.p.i", "Rep1",
+                    "abund_4hrsS2", "4h.p.i", "Rep2",
+                    "abund_72hrsS1", "72h.p.i", "Rep1",
+                    "abund_72hrsS2", "72h.p.i", "Rep2",
+                    "abund_72hrsS3", "72h.p.i", "Rep3") %>% data.frame()
+
+# load in expression level files for making ballgown object
+bam_files <- list.files("results/hisat2",
+                        pattern = "^thev_subset_\\d+hrsS\\d\\.bam$",
+                        full.names = T) %>%
+  .[c(1:7, 9:11)]
+
+raw_data <- ballgown(dataDir = "results/ballgown",
+                     samplePattern = "abund_",
+                     pData = exp_info,
+                     bamfiles = bam_files)
+
+
+# extract transcript expression level data
+t_exp_levels <- texpr(raw_data, meas = "all") %>%
+  as_tibble() %>%
+  mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1))) %>% 
+  pivot_longer(cols = starts_with("FPKM"),
+               names_to = "samples",
+               values_to = "fpkm") %>%
+  mutate(timepoint = case_when(str_detect(samples, "_4hrs") ~ "4h.p.i",
+                               str_detect(samples, "_12hrs") ~ "12h.p.i",
+                               str_detect(samples, "_24hrs") ~ "24h.p.i",
+                               str_detect(samples, "_72hrs") ~ "72h.p.i",
+                               TRUE ~ NA_character_),
+         timepoint = factor(timepoint,
[…]

### 2023-10-06 scripts/r/reg_by_reg_plots.R

@@ -70,7 +70,9 @@ t_exp_levels <- texpr(raw_data, meas = "all") %>%
   select(trxpt_id, t_name, num_exons)
 
 comp_spliced_gtf <- left_join(spliced_gtf, t_exp_levels,
-                              by = "trxpt_id")
+                              by = "trxpt_id") %>%
+  mutate(sstcodon = c(rep(211, 3), 1965, rep(NA, 22), 26246, 3616),
+         stpcodon = c(2312, 1953, rep(2312, 2), rep(NA, 22), 25204, 2334))
 
 
 # load in data and prepare predicted ORFs only
@@ -105,8 +107,10 @@ predicted_orfs <- predicted_orfs %>%
                             gene_name == "IVa2" ~ "IM",
                             gene_name == "UXP" ~ "LONE",
                             TRUE ~ "MLP")) %>%
-  arrange(strand, region)
-
+  arrange(strand, region) %>%
+  rbind(tibble( gene_name = "ORF4", transcript_id = "gp04", strand = "+",
+                start_1 = 1965, start_2 = NA, start_3 = NA, end_1 = 2312,
+                end_2 = NA, end_3 = NA, region = "E1")) 
 
 combined_gtf <- plyr::rbind.fill(comp_spliced_gtf, predicted_orfs) %>% 
   arrange(strand, region) %>% as_tibble() %>%
@@ -114,7 +118,8 @@ combined_gtf <- plyr::rbind.fill(comp_spliced_gtf, predicted_orfs) %>%
 
 
 
-plot_full_trxptome <- function(combined_gtf, trxptome_part){
+plot_full_trxptome <- function(combined_gtf, trxptome_part, trxpt_part2=NULL){
+  regs <- c(trxptome_part, trxpt_part2)
   
   # =======================================================
   # TRANSCRIPT X AND Y POSITIONS FOR FULL TRANSCRIPTOME MAP
@@ -142,7 +147,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part){
   ypos_e2$ypos <- rep(c(24:19), length.out = nrow(ypos_e2))
   
   ypos_im <- combined_gtf %>% filter(region == "IM")
-  ypos_im$ypos <- rep(c(19, 20), length.out = nrow(ypos_im))
+  ypos_im$ypos <- rep(c(21, 21.5), length.out = nrow(ypos_im))
   
[…]

### 2023-11-09 manuscript_thev_transcriptome.Rmd
validated mlp juncs:D,F,G,H

@@
 **Major Late Promoter Region (MLP) transcripts**.
-
+\newpage
+## DISCUSSION/CONCLUSIONS
+In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene.
+However, later studies predicted and preferred Hyd instead of ORF4; hence, the current prediction map.
+However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
 \newpage
@@
 
+### Validation of Novel Splice Junctions 
+All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
+However, these predicted splice junctions have not been experimentally validated hitherto, and we identified additional novel exons, giving a more complete picture of the transcripts.
+~~The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in Table###1~~.
+We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit paired with their respective universal primers (~~supplementary, PCR methods~~).
+Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
+After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method and Sanger sequenced to validate these splice junctions at the sequence level.
+
+### 3' Rapid Amplification of cDNA Ends (3'RACE)
+
 ### Computational Analysis of RNA Sequencing Data: Mapping and Transcript characterization
@@
 A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
-
-### Validation of Novel Splice Junctions 
-All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
-However, these predicted splice junctions have not been experimentally validated hitherto, and we identified additional novel splice junctions beside the predicted junctions, giving a more complete picture of the transcripts.
-
-The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in ~~Table###1~~.
-We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit with their respective universal primers (~~supplementary, PCR methods~~).
-Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
-After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method and Sanger sequenced to validate these splice junctions at the sequence level.
-
-### 3' Rapid Amplification of cDNA Ends (3'RACE)
-
 \newpage
-
-## DISCUSSION/CONCLUSIONS
-In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene.
-However, later studies predicted and preferred Hyd instead of ORF4; hence, the current prediction map.
-However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
 
@@
 ## ACKNOWLEDGMENTS  
-LC Sciences
-`Eton Bioscience, Inc, San Diego, CA`
+`LC Sciences` - RNA sequencing was done here
+`Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here
 \newpage

### 2023-11-15 manuscript_thev_transcriptome.Rmd
made publication-worthy figures and removed uneeded figs

@@
 To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes, was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time.
-Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
+Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
+This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
 Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly overexpressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
@@
 However, the MLP-derived junctions were unsurprisingly the most preponderant overall at this time point, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__).
-At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions was not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
+At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
 Also see __Supplementary Tables 1a-c__; __Figure 4c__).
@@
 Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
-This revealed that, with the exception of one junction (which was a T-G donor-acceptor pair), all splice donor-acceptor pairs in the final transcriptome were the canonical T-A pair.
+We found that most splice donor-acceptor sequences were unsurprisingly the canonical GU-AG nucleotides.
 
@@
 \newpage
+
 ## DISCUSSION/CONCLUSIONS   
@@
 However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
+For fig2a: There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection.
+Unexpectedly, the pileup of reads seems consistently skewed over similar regions of the genome.
+We could speculate that the temporal gene expression regulation of THEV is different from MAdVs or this could simply mean that the infection was not well synchronized.
+However, the relative proportions over these similar regions shows some variation over time.
+For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death
 \newpage
@@
 ### CODE AVAILABILITY    
-All the code/scripts written for analysis of the data is available on github (linkXXXXXX)
+All the code/scripts written for analysis of the data is available on github (linkXXXXX)
 \newpage
@@
 
-```{r}
-#| tab.id: NULL
-#| tab.cap.pre: ""
-#| tab.cap.sep: ""
-
-set_flextable_defaults(font.size = 8)
-flextable(tab1) %>% theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed", width = 0.95,
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::font(part = "all", fontname = "Avenir") %>%
-  flextable::width(., j = ~ Metric, width = 1.5) %>%
-  flextable::set_caption("Overview of sequencing results",
-              style = "Table Caption") %>%
-  flextable::bold(part = "body", j = ~ Metric)
-
-```
-\newpage
-
-![](results/r/figures/overlay_alltimes.png)
-![](results/r/figures/thev_growth_curve.png)
-**Figure 2.
+![](results/r/figures/fig_2.png)
+**Figure 2: Increasing levels of THEV over time.
 a) _Per base coverage of sequence reads mapping to THEV genome by time point_**.
-The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point show remarkable difference in terms of quantities.
-There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection.
-Unexpectedly, the pileup of reads seems consistently skewed over similar regions of the genome.
-We could speculate that the temporal gene expression regulation of THEV is different from MAdVs or this could simply mean that the infection was not well synchronized.
-However, the relative proportions over these similar regions shows some variation over time.
+The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
 **b) _One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
@@
 There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured.
-The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i, probably due to high cell death.
+The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i.
 GCN: genome copy number.
@@
 Transcripts are color coded as explained in **a**.
+\newpage
 
+![](results/r/figures/figure_4a_d.png)
+**Figure 4: Changes in splicing and expression profile of THEV over time.** 
+**a)** Expression levels of transcripts over time.**b)** Expression levels of transcripts by region over time.**c)** Relative abundances of all splice junctions over time.
+**d)** Relative abundances of junctions in transcriptome.
+\newpage
+
+```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e1_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               splice_site = "Splice Donor-Acceptor",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5)) %>%
+  footnote(., i = 2, j = 10, value = as_paragraph(c("Not validated for TRXPT_4")),
+           ref_symbols = c("*"), part = "body")
+
+brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(2, 0.05, 2)) +
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 22, face = "bold"))
+```
+
+**Figure 5: E1 region transcripts.
+a)** The splice map of the E1 transcription unit.
+Exons are depicted as boxes connected by introns (dotted lines).
+Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and the previously annotated ORF4 is colored black.
+Each transcript or ORF is labelled with its name to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+
+```{r region-by-region_e2andim_figure, fig.height=16, fig.width=18, warning=FALSE}
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e2_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Donor-Acceptor",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 2, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
+                                                                  width = 1.5)) %>%
+  footnote(., i = 6, j = 12, value = as_paragraph(c("Truncated transcript")),
+           ref_symbols = c("*"), part = "body")
+
+brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.05, 1.5))
+```
+
+**Figure 6: E2 and IM region transcripts.
+a)** The splice map of the E1 and IM transcription units.
+Exons are depicted as boxes connected by introns (dotted lines).
+Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
+Each transcript or ORF is labelled with its name to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+
+```{r region-by-region_e4_figure, fig.height=5, fig.width=7, warning=FALSE}
+reg_e4_brkdown <- reg_e4_brkdown %>%
+  mutate(splice_site = "GT-AG",
+         `4hpi` = as.numeric(`4hpi`), `12hpi` = as.numeric(`12hpi`),
+         `24hpi` = as.numeric(`24hpi`), `72hpi` = as.numeric(`72hpi`)) %>%
+  select(-c(coding_potential, region)) %>%
+  group_by(trxpt_id, start, end, splice_site, intron_len, strand, status) %>%
+  reframe("4hpi" = sum(`4hpi`),
+          "12hpi" = sum(`12hpi`),
+          "24hpi" = sum(`24hpi`),
+          "72hpi" = sum(`72hpi`)) %>%
+  select(trxpt_id, start, end, splice_site, intron_len, strand, "4hpi", "12hpi",
+         "24hpi", "72hpi", status)
+
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e4_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Donor-Acceptor",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))
+
+brkdwn_e4_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.01, 1)) +
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 18, face = "bold"))
+```
+
+**Figure 8:  E4 region transcripts.
+a)** The splice map of the E4 transcription unit.
+Exons are depicted as boxes connected by introns (dotted lines).
+The transcript from RNA-seq data is colored red and the predicted ORF, grey.
+The transcript and ORF are labelled with their names to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junction are indicated.
+
+```{r region-by-region_im_figure, fig.height=5, fig.width=10, warning=FALSE, include=FALSE}
+reg_im_brkdown <- reg_im_brkdown %>%
+  mutate(trxpt_id = "TRXPT_5")
+
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_im_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Donor-Acceptor",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))
+
+brkdwn_im_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.01, 1)) +
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 18, face = "bold"))
+
+```
+
+<!-- **Figure 9 IM region transcripts. a)** The splice map of the IM transcription unit. **b)** The sequence reads covering the splice junction are indicated. -->
+
+```{r region-by-region_mlp_figure, fig.height=16, fig.width=18, warning=FALSE}
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_mlp_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site",
+                             "intron_len","strand", "4hpi", "12hpi",
+                             "24hpi", "72hpi", "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Donor-Acceptor",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                  width = 1.5)) %>%
+  flextable::width(width = 0.3) %>%
+  flextable::width(j = 1, width = 1.5)
+
+brkdwn_mlp_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.02, 1.2))
+```
+
+**Figure 9: MLP region transcripts. a)**
+\newpage
+
+```{r}
+#| tab.id: NULL
+#| tab.cap.pre: ""
+#| tab.cap.sep: ""
+
+set_flextable_defaults(font.size = 8)
+flextable(tab1) %>% theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed", width = 0.95,
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::font(part = "all", fontname = "Avenir") %>%
+  flextable::width(., j = ~ Metric, width = 1.5) %>%
+  flextable::set_caption("Table 1: Overview of sequencing results",
+              style = "Table Caption") %>%
+  flextable::bold(part = "body", j = ~ Metric)
+
+```
 \newpage
@@
 ```
-\newpage
-
-![](results/r/figures/trxpt_fpkm_percent_abund.png)
-
-![](results/r/figures/region_fpkm_percent_abund.png)
-**Figure 4 Changes in splicing and expression profile of THEV over time.** 
-**a)** Expression levels of transcripts over time.
-**b)** Expression levels of transcripts by region over time.
-
-\newpage
-![](results/r/figures/junc_abundances.png)
-**c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in final transcriptome.
-
-```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e1_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Site",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5)) %>%
-  footnote(., i = 2, j = 11, value = as_paragraph(c("Not validated for TRXPT_4")),
-           ref_symbols = c("*"), part = "body")
-
-brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(2, 0.05, 2)) +
-  plot_annotation(tag_levels = "A") &
-  theme(plot.tag = element_text(size = 22, face = "bold"))
-
-```
-
-**Figure 5: E1 region transcripts.
-a)** The splice map of the E1 transcription unit.
-Exons are depicted as boxes connected by introns (dotted lines).
-Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and the previously annotated ORF4 is colored black.
-Each transcript or ORF is labelled with its name to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
-
-```{r region-by-region_e2ANDim_figure, fig.height=16, fig.width=18, warning=FALSE}
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e2_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Site",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 2, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
-                                                                  width = 1.5)) %>%
-  footnote(., i = 9, j = 12, value = as_paragraph(c("Truncated transcript")),
-           ref_symbols = c("*"), part = "body")
-
-brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.05, 2))
-
-```
-
-**Figure 6: E2 and IM region transcripts.
-a)** The splice map of the E1 and IM transcription units.
-Exons are depicted as boxes connected by introns (dotted lines).
-Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
-Each transcript or ORF is labelled with its name to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
-
-```{r region-by-region_e4_figure, fig.height=5, fig.width=7, warning=FALSE}
-reg_e4_brkdown <- reg_e4_brkdown %>%
-  mutate(splice_site = "GT-AG",
-         `4hpi` = as.numeric(`4hpi`), `12hpi` = as.numeric(`12hpi`),
-         `24hpi` = as.numeric(`24hpi`), `72hpi` = as.numeric(`72hpi`)) %>%
-  select(-c(coding_potential, region)) %>%
-  group_by(trxpt_id, start, end, splice_site, intron_len, strand, status) %>%
-  reframe("4hpi" = sum(`4hpi`),
-          "12hpi" = sum(`12hpi`),
-          "24hpi" = sum(`24hpi`),
-          "72hpi" = sum(`72hpi`)) %>%
-  select(trxpt_id, start, end, splice_site, intron_len, strand, "4hpi", "12hpi",
-         "24hpi", "72hpi", status)
-
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e4_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Site",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5))
-
-brkdwn_e4_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.01, 1)) +
-  plot_annotation(tag_levels = "A") &
-  theme(plot.tag = element_text(size = 18, face = "bold"))
-
-```
-
-**Figure 8:  E4 region transcripts.
-a)** The splice map of the E4 transcription unit.
-Exons are depicted as boxes connected by introns (dotted lines).
-The transcript from RNA-seq data is colored red and the predicted ORF, grey.
-The transcript and ORF are labelled with their names to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junction are indicated.
-
-```{r region-by-region_im_figure, fig.height=5, fig.width=10, warning=FALSE, include=FALSE}
-reg_im_brkdown <- reg_im_brkdown %>%
-  mutate(trxpt_id = "TRXPT_5")
-
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_im_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Site",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5))
-
-brkdwn_im_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.01, 1)) +
-  plot_annotation(tag_levels = "A") &
-  theme(plot.tag = element_text(size = 18, face = "bold"))
-
-```
-
-<!-- **Figure 9 IM region transcripts. a)** The splice map of the IM transcription unit. **b)** The sequence reads covering the splice junction are indicated. -->

### 2023-11-15 scripts/r/abundance_analyses.R

@@ -426,7 +426,8 @@ reg_e1_brkdown <- reg_brkdown_tab("E1") %>%
 
 # E2 region table analysis for discussion
 reg_e2_brkdown <- reg_brkdown_tab("E2") %>%
-  mutate(status = c(rep("Validated", 8), "Unvalidated"))
+  distinct(start, end, intron_len, .keep_all = T) %>% 
+  mutate(status = c(rep("Validated", 5), "Unvalidated"))
 
 # E3 region table analysis for discussion
 reg_e3_brkdown <- reg_brkdown_tab("E3")
@@ -441,7 +442,9 @@ reg_im_brkdown <- reg_brkdown_tab("IM") %>%
   mutate(status = "Validated")
 
 # MLP region table analysis for discussion
-reg_mlp_brkdown <- reg_brkdown_tab("MLP")
+reg_mlp_brkdown <- reg_brkdown_tab("MLP") %>%
+  distinct(start, end, intron_len, .keep_all = T) %>% 
+  mutate(status = rep("Validated", 15))
 
 
 

### 2023-11-15 scripts/r/plot_abundances.R

@@ -31,14 +31,14 @@ plot_time_genexpression <- function(count_ss){
     theme(plot.margin = margin(rep(30, 4)),
           panel.grid.major.y = element_line(linewidth = 0.4, color = "grey",
                                             linetype = "dashed"),
-          axis.title.y = element_text(size = 16, face = "bold", margin = margin(r = 15)),
-          axis.text.x = element_text(size = 16, face = "bold"),
-          axis.text.y = element_text(size = 14, face = "bold"),
+          axis.title.y = element_text(size = 28, face = "bold", margin = margin(r = 15)),
+          axis.text.x = element_text(size = 28, face = "bold"),
+          axis.text.y = element_text(size = 18, face = "bold"),
           legend.justification = c(0, 0),
           legend.position = c(0.05, 0.9),
           legend.key.width = unit(2, "cm"),
           legend.title = element_blank(),
-          legend.text = element_text(size = 14, face = "bold", colour = "black"),
+          legend.text = element_text(size = 15, face = "bold", colour = "black"),
           legend.text.align = 0) +
     guides(color = guide_legend(label.position = "top",
                                 label.hjust = 0.5,
@@ -59,11 +59,11 @@ all_juncs <- plot_time_genexpression(plot_all_junc_abunds) +
   labs(x = element_blank(),
        y = "Relative Abundances of All Junctions")
 
-patch_expr <- (all_juncs | trxptome_juncs)
+# patch_expr <- (all_juncs | trxptome_juncs)
 
-ggsave("junc_abundances.png",
-       plot = patch_expr, path = "results/r/figures",
-       width = 20, height = 12, dpi = 500)
+# ggsave("junc_abundances.png",
+#        plot = patch_expr, path = "results/r/figures",
+#        width = 20, height = 12, dpi = 500)
 
 
 # -------------------
@@ -72,16 +72,16 @@ ggsave("junc_abundances.png",
 # acceptors and donors in trxptome
 bulk_trxptome_ss_seq <- count_trxptome_ss(unq_bulk_juncs) %>%
   distinct(junc_ss, junc_ts, .keep_all = T) %>%
-  dplyr::group_by(exact_ss) %>%
+  dplyr::group_by(splice_site) %>%
   reframe(freq = n()) %>% 
   mutate(sum_junc_count = sum(freq),
          percent_abund = (freq / sum_junc_count) * 100)
 
[…]

### 2023-11-15 scripts/r/thev_cov_depth.R

@@ -9,14 +9,6 @@ library(ggtext)
 library(grDevices)
 library(tidyverse)
 
-source("scripts/r/thev_genomic_map.R")
-
-### remove older files before generating new files
-path <- "results/r/figures"
-files <- list.files(path, pattern = ".+(.pdf|.png|.jpg|.jpeg)", 
-                    full.names = TRUE, recursive = TRUE)
-unlink(files, recursive = FALSE, force = FALSE)
-
 # load in depth files
 
 ### find all the depth files
@@ -48,70 +40,69 @@ all_depths <- map_dfr(all_depth_files, read_tsv,
   
 # -------------------
 ## split the table into individual time-points and plot iteratively with map()
-each_plot <- all_depths %>% 
-  split(.$timepoint) %>% 
-  map(~ggplot(., aes(position, depth)) +
-        geom_col(color = glue("{.$color}")) +
-        labs(title = glue("{.$titles}"),
-             x = element_blank(),
-             y = "Mapping Depth") +
-        scale_y_continuous(expand = c(0, 0)) +
-        scale_x_continuous(expand = c(0, 0),
-                           breaks = seq(1000, 26000, 2000),
-                           labels = glue("{seq(1,26,2)}kb")) +
-        theme_classic() +
-        theme(plot.title = element_text(size = 18,
-                                        face = "bold",
-                                        hjust = 0.5,
-                                        margin = margin(t = 10)),
-              panel.grid.major.y = element_line(linewidth = 0.6,
-                                                linetype = "dashed"),
-              axis.title.y = element_text(size = 14,
-                                          face = "bold",
-                                          margin = margin(r = 10, l = 10)),
-              axis.text.y = element_text(size = 10, color = "black"),
-              axis.text.x = element_text(size = 8.5, color = "black", face = "bold")
-            ))
-
-# save plot for each time-point
-
-# ggsave("depth_4hrs.png",
-#        plot = each_plot$`4hpi`, path = "results/r/figures",
-#        width = 10, height = 5)
+# each_plot <- all_depths %>% 
+#   split(.$timepoint) %>% 
+#   map(~ggplot(., aes(position, depth)) +
+#         geom_col(color = glue("{.$color}")) +
+#         labs(title = glue("{.$titles}"),
+#              x = element_blank(),
[…]

### 2023-11-15 scripts/r/thev_genomic_map.R

@@ -13,11 +13,9 @@ make_genomic_map <- function(bedfile){
                           col_types = "ciiciciicicc") %>% 
     set_colnames(c("chr", "start", "end", "gene_name", "score", "strand", "thickStart",
                    "thickEnd", "color", "blockCount", "blockSizes", "blockStarts")) %>% 
-    mutate(exon1Size = str_replace(blockSizes, pattern = "(\\d+),\\d+", replacement = "\\1"),
-           exon1Size = as.numeric(exon1Size),
-           exon2Size = str_replace(blockSizes, pattern = "\\d+,(\\d+)", replacement = "\\1"),
-           exon2Size  = as.numeric(exon2Size),
-           exon2Size = ifelse(exon2Size == exon1Size, NA_real_, exon2Size),
+    mutate(exon1Size = as.numeric(str_replace(blockSizes, pattern = "(\\d+),\\d+", replacement = "\\1")),
+           exon2Size = as.numeric(str_replace(blockSizes, pattern = "\\d+,(\\d+)", replacement = "\\1"))) %>%
+    mutate(exon2Size = ifelse(exon2Size == exon1Size, NA_real_, exon2Size),
            exon1start = thickStart,
            exon1end = ifelse(blockCount > 1, (start + exon1Size), thickEnd),
            exon2start = thickEnd - exon2Size,
@@ -27,7 +25,7 @@ make_genomic_map <- function(bedfile){
                                   "33K_spliced" ~ "33K",
                                   "pVIII gene" ~ "pVIII",
                                   .default = gene_name),
-           ypos = c(rep(c(0.5, 1, 1.5),7), 0.5 , 1)) 
+           ypos = c(rep(c(0.5, 1, 1.5),7), 0.5 , 1))
   
   spliced <- thev_genome %>% filter(blockCount > 1)
   
@@ -66,3 +64,5 @@ make_genomic_map <- function(bedfile){
           axis.ticks.y = element_blank()
           )
 }
+
+make_genomic_map("raw_files/annotations/THEVannotated_genesOnly.bed")

### 2023-11-15 scripts/r/thev_growthcurve.R

@@ -6,6 +6,8 @@ library(glue)
 library(lubridate)
 library(tidyverse)
 
+source("scripts/r/thev_cov_depth.R")
+
 exp2 <- "raw_files/wetlab_data/thev_growthcurve04_2023.xls"
 replicate_data <- read_excel(exp2,
                           sheet = "Results",
@@ -36,8 +38,7 @@ plot_prepped <- replicate_data %>%
   reframe(mean_conc = mean(conc), 
             mean_conc_per_mL = (mean_conc * 10 * 1000),
             replicates = n(),
-            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000,
-            .groups = "drop") %>% 
+            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000) %>% 
   mutate(treatment = str_replace(inf_hrs, "([a-zA-Z]{3})_\\d{1,2}", "\\1"))
 
 #================= visualize data just data from exp 2 ========================
@@ -112,15 +113,16 @@ rep1_data <- read_excel(exp1,
                 task = "Task", conc = "Quantity") %>% 
   select(well, task, sample_name, conc) %>% 
   drop_na(sample_name) %>% 
-  filter(!str_detect(sample_name, ".*DNA.*")) %>% 
-  mutate(sample_name = ifelse(well == "B3", "Inf1-D0", sample_name),
-         sample_name = ifelse(well == "B4", "Inf2-D0", sample_name),
-         sample_name = str_replace(sample_name,
+  filter(!str_detect(sample_name, ".*DNA.*")) %>%
+  mutate(sample_name = case_when(well == "B3" ~ "Inf1-D0",
+                                 well == "B4" ~ "Inf2-D0",
+                                 TRUE ~ sample_name)) %>%
+  mutate(sample_name = str_replace(sample_name,
                                    "([a-zA-Z]+)\\d?-D(\\d)",
                                    "\\1_\\2")) %>% 
   separate_wider_delim(sample_name,
                        names = c("condition", "day"),
-                       delim = "_") %>% 
+                       delim = "_") %>%
   mutate(inf_day = paste0(condition, "_", day),
          day = as.numeric(day),
          hrs_pi = day * 24,
@@ -152,7 +154,7 @@ growth_curve <- full_prepped %>%
                      breaks = full_prepped$hrs_pi,
[…]

### 2023-12-01 manuscript_thev_transcriptome.Rmd
validated tplE3 and E3-trxptA juncs

@@
 ### RNA extraction and Sequencing   
-Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` as per manufacturer's instructions.
+Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` per manufacturer's instructions.
 An agarose gel electrophoresis was performed to check RNA integrity.
@@
 All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
-However, these predicted splice junctions have not been experimentally validated hitherto, and we identified additional novel exons, giving a more complete picture of the transcripts.
+However, these predicted splice junctions had not been experimentally validated hitherto, and we identified additional novel exons, giving the complete picture of these transcripts.
 ~~The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in Table###1~~.
@@
 Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
-After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method and Sanger sequenced to validate these splice junctions at the sequence level.
+After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
 
 ### 3' Rapid Amplification of cDNA Ends (3'RACE)  
+We performed a rapid amplification of sequences from the 3′ ends of mRNAs (3'-RACE) experiment with total RNA extracted from independently infected MDTC-RP19 cells following the protocol described by Green _et al_ [@Green2019] with modifications.
+Briefly,
 

### 2023-12-15 manuscript_thev_transcriptome.Rmd
Corrected the scripts responsible for overestimating the read counts in tables 2a-c.
changed unicode character in ref to "'" to render pdf.

@@
 Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having coverage as high as `r max_junread72` reads.
-The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes an active infection, and correlates with our qPCR assay quantifying the total number of viral genome copies over time (__Figure 2b__).
+The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes an active infection, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (__Figure 2b__).
 Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
-In the final consolidated transcriptome of THEV, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` transcripts all of which are novel.
+In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` transcripts all of which are novel, ~~and using 3' Rapid Amplification of cDNA Ends (3'RACE) and other methods, we further identified #### unique splice variants~~.
 Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (__Figure 3__).
@@
 **Changes in THEV splicing profile over time**   
-AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU).
-Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs.
-To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes, was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time.
+AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU) or region.
+Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs [@Donovan2020; @Zhao2014].
+To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes [@Ballgown] was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time.
 Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
 This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
-Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly overexpressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
+Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly expressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
 Secondly, we estimated relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point.
@@
 Junctions from the E2 region were the most abundant at this time point, constituting `r round(most_sig_12, 1)`% of all junctions.
-The two most abundant junctions at 12 h.p.i were maintained at 24 h.p.i also as the most significantly expressed.
+The levels of the two most abundant junctions at 12 h.p.i were maintained also 24 h.p.i as the most significantly expressed.
 However, the MLP-derived junctions were unsurprisingly the most preponderant overall at this time point, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__).
@@
 Also see __Supplementary Tables 1a-c__; __Figure 4c__).
-When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 4d__).
+When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (__Figure 4d__).
 Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
@@
 Finally, during our validation of TRXPT_2, ORF1 was present on the agarose gel and Sanger sequencing results as a bona fide transcript (__supplementary PCR methods__).
-This is corroborated by 3' Rapid Amplification of cDNA Ends (3'RACE) experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing.
+This is corroborated by 3'RACE experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing.
 The 5'-most CDS of this transcript would encode ORF1.
@@
 ### 3' Rapid Amplification of cDNA Ends (3'RACE)  
-We performed a rapid amplification of sequences from the 3′ ends of mRNAs (3'-RACE) experiment with total RNA extracted from independently infected MDTC-RP19 cells following the protocol described by Green _et al_ [@Green2019] with modifications.
+We performed a rapid amplification of sequences from the 3' ends of mRNAs (3'-RACE) experiment with total RNA extracted from independently infected MDTC-RP19 cells following the protocol described by Green _et al_ [@Green2019] with modifications.
 Briefly,
@@
 A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
-\newpage
 
@@
 The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
-**b) _One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
-After infecting cells at an MOI of 100 GCN/cell, triplicates of harvested infected cells were quantified with an in-house qPCR assay measuring the total copies of THEV genome.
+**b) _Growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
+Virus titers were a qPCR assay.
 There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured.

### 2023-12-15 scripts/r/abundance_analyses.R

@@ -304,11 +304,11 @@ plot_all_junc_abunds <- bulk_junc_stats %>%
   group_by(timepoint, region) %>%
   reframe(accum_tally_j = n(),
           total_rd_j_tp_reg = sum(read_count)) %>%
-  drop_na(region) %>% 
+  drop_na(region) %>%
   split(.$timepoint) %>%
   map(mutate, tot_reads_time = sum(total_rd_j_tp_reg)) %>% 
   do.call("rbind", .) %>%
-  mutate(region = factor(region, levels = c("E1", "E2", "E3", "E4", "IM", "MLP"))) %>%
+  mutate(region = factor(region, levels=c("E1", "E2", "E3", "E4", "IM", "MLP"))) %>%
   group_by(timepoint, region, .drop = F) %>% 
   reframe(total_rd_j_tp_reg = total_rd_j_tp_reg,
           tot_reads_time = tot_reads_time,

### 2023-12-15 scripts/r/bam_file_analysis.R

@@ -247,28 +247,50 @@ tab1 <- tibble(Metric = c("Total reads",
                         ifelse(Total > 1000 & Total < 1000000, comma(Total),
                                Total)))
 
-
+# ---------------------
 # ---------------------
 # For Table 2A-C
-find_sig_juncs <- function(tp){
-  total_tp_juncs <- bulk_junc_stats %>% filter(timepoint == tp) %>% pull(read_count) %>% sum()
+# ---------------------
+# ----------------------
+find_sig_juncs <- function(tp, rg){
+  tp <- "12hpi"
+  regs <- c("E1","E2", "E3", "E4", "IM", "MLP")
   
-  meta_dt <-  bulk_junc_stats %>%
+  total_tp_juncs <- bulk_junc_stats %>%
+    filter(timepoint == tp) %>% pull(read_count) %>% sum()
+  
+  meta_dt <- bulk_junc_stats %>%
     filter(timepoint == tp) %>%
     select(timepoint, strand, start, end, splice_site,
            exact_ss, region) %>%
-    distinct(start, end, .keep_all = T)
+    distinct(region, start, end, .keep_all = T) %>%
+    drop_na()
   
-  est <- bulk_junc_stats %>%
-  filter(timepoint == tp) %>%
-  group_by(timepoint, start, end) %>%
-  reframe(tot_tp_j_rds = sum(read_count)
-          ) %>%
-  mutate(perc = round((tot_tp_j_rds/ total_tp_juncs) * 100, 1),
-         intron_len = end - start) 
+  # function to compute values for each region
+  est_percent <- function(rg){
+    est <- bulk_junc_stats %>%
+      filter(timepoint == tp, region == rg) %>%
+      group_by(region, start, end) %>%
+      reframe(tot_tp_j_rds = sum(read_count)) %>%
+      mutate(perc = round((tot_tp_j_rds/ total_tp_juncs) * 100, 1),
+             intron_len = end - start) 
+    return(est)
+  }
+  
+  # Initialize an empty list to store the dataframes
+  temp_list <- list()
+  
+  # Call the function iteratively and store the results
+  for(i in 1:length(regs)){
+    df <- est_percent(regs[i])
+    temp_list[[i]] <- df
+  }
+  # Combine all the dataframes into one final result
+  all_ests <- base::do.call(rbind, temp_list)
   
[…]

### 2023-12-15 scripts/r/plot_abundances.R

@@ -52,7 +52,7 @@ plot_time_genexpression <- function(count_ss){
 # plot and save abundances of juncs found in final trxptome
 trxptome_juncs <- plot_time_genexpression(bulk_count_trxptome_ss) +
   labs(x = element_blank(),
-       y = "Relative Abundances of Junctions in Final Transcriptome")
+       y = "Relative Abundances of Junctions in Transcriptome")
 
 
 all_juncs <- plot_time_genexpression(plot_all_junc_abunds) +

### 2023-12-19 manuscript_thev_transcriptome.Rmd
wrote some E2 reg results and added gels designed primers for E2 trxpt_15 and pol

@@
 
-most_sig_12 <- bulk_junc_stats %>% filter(timepoint == "12hpi", region == "E2") %>% pull(read_count) %>% sum()/as.numeric(tab1$`12h.p.i`[6])*100
+most_sig_12 <- bulk_junc_stats %>% filter(timepoint == "12hpi", region == "MLP") %>% pull(read_count) %>% sum()/as.numeric(tab1$`12h.p.i`[6])*100
 
@@
 Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs [@Donovan2020; @Zhao2014].
-To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes [@Ballgown] was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time.
+To evaluate the activity of each promoter over time, Firstly, `Ballgown`, a program for statistical analysis of assembled transcriptomes [@Ballgown] was used to estimate and normalize expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
 Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
-This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__).
-Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly expressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
-Secondly, we estimated relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point.
-At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were predominantly early region (E1, E2, and E3) junctions, albeit a significant proportion are MLP-derived (__Table 2a__).
-Junctions from the E2 region were the most abundant at this time point, constituting `r round(most_sig_12, 1)`% of all junctions.
-The levels of the two most abundant junctions at 12 h.p.i were maintained also 24 h.p.i as the most significantly expressed.
-However, the MLP-derived junctions were unsurprisingly the most preponderant overall at this time point, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__).
+```{r temporal transcript expression levels}
+abn_each_12 <- t_expr_each %>% filter(trxpt_id == "E2: TRXPT_21", timepoint == "12h.p.i") %>% pull(fpkm_trxpt_percent)
+```
+Individually, TRXPT_21 (DBP) - from the E2 region - was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
+Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
+The later time points were dominated by the MLP region; transcripts TRXPT_10 and TRXPT_14 were most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (__Figure 4a__).
+When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
+Secondly, we estimated relative abundances of all splice junctions for each time point using the raw reads.
+We counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads counted at the given time point.
+At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLP was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junctions reads.
+(__Table 2a__).
+The levels of the top most abundant junctions at 12 h.p.i were maintained also 24 h.p.i as the most significantly expressed.
+However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__).
 At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
@@
 TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-From our analysis, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2; however, given that studies in MAdVs show that E1 mRNAs share a common 5' and 3' positions, only differing from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are truncated, and the TSS just like the transcription termination site (TTS) are identical for all E1 transcripts.
+From our analysis, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2; however, given that studies in MAdVs show that E1 mRNAs share a common 5' and 3' positions, only differing from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and the TSS just like the transcription termination site (TTS) are identical for all E1 transcripts.
 Regardless of the TSS considered for TRXPT_3, the coding potential remains unaffected.
 Its 5'-most CDS, beginning at 1965 and sharing the same STC as TRXPT_1 and TRXPT_2, produces a 13.1 kDa, 115 residue protein.
-This CDS (ORF4) was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003], but our data suggests it is a bona fide ORF.
+This CDS (ORF4) was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggests it is a bona fide ORF.
 The coding potential of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its coding potential is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
@@
 Finally, during our validation of TRXPT_2, ORF1 was present on the agarose gel and Sanger sequencing results as a bona fide transcript (__supplementary PCR methods__).
-This is corroborated by 3'RACE experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing.
+This is corroborated by 3'-RACE experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing with a poly-A tail at the TTS of transcripts in this region.
 The 5'-most CDS of this transcript would encode ORF1.
-Given that the SSC of the predicted ORF1 is in-frame but downstream of TRXPT_2 SSC, it suggests that the predicted ORF1 CDS is truncated; it shares the same SSC as TRXPT_2, but has a unique STC, albeit it has the same TTS.
+Given that the SSC of the predicted ORF1 is in-frame but downstream of TRXPT_2 SSC, it suggests that the predicted ORF1 CDS is incomplete; it shares the same SSC and TSS, and TTS as TRXPT_2, but has a unique STC.
 
 **Early Region 2 (E2) and Intermediate Region (IM) transcripts**.
-The E2 TU expressed on the reverse strand, is subdivided into E2A and E2B and encodes three classical AdV proteins: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [####].
-Unlike MAdV where two promoters (E2-early and E2-late) were discovered [###], we discovered only a single promoter from which both E2A and E2B transcription is initiated.
-However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs; the E2B transcripts sharing the TTS of the IVa2 transcript of the IM region [####] (__Figure 6__).
-~~Analysis of the coding potential of the transcripts; include the variant of DBP from 3'RACE data~~.
+The E2 TU expressed on the reverse strand, is subdivided into E2A and E2B and encodes three classical AdV proteins: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [@Donovan2020; @Zhao2014].
+Unlike MAdV where two promoters (E2-early and E2-late) were discovered [@Donovan2020], we discovered only a single promoter from which both E2A and E2B transcription is initiated.
+However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (__Figure 6__).
+The E2A ORF, DBP is one of three ORFs predicted to be spliced from two exons, with the CDS spanning both exons.
+The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern exactly but with an additional non-coding exon at the 5'-end (E2-5'UTR); hence, a three-exon transcript.
+The encoded protein (DBP; 380 residues, 43.3 kDa) is identical.
+This transcript was also corroborated in a 3'-RACE experiment.
+Additionally, from the 3'-RACE, a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript was found.
+This transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP because the first SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron, and does not yield any viable product.
+The SSC 173 bp downstream of TRXPT_21's SSC yields a 346 residue, 39.3 kDa product, which is in-frame of DBP but wholly contained in the second exon starting at 18,013 bp and terminating just like DBP at 16,973 bp.
+TRXPT_21 and TRXPT_21B share a common TSS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine-rich sequence where the polyadenylation occurs.
+Hence, we suggest that the two transcripts also share the same TTS at 16,934 bp (__Figure 6__).
 
@@
 The encoded protein from this SSC is in-frame with the SSC of ORF8 in the second exon; hence, the C-terminus of this longer protein (26.4 kDa, 229 aa) would be the identical to the predicted ORF8 protein.
-The splice junction of TRXPT_28 was validated by cloning and Sanger sequencing of cDNA (__supplementary PCR methods__).
+~~The splice junction of TRXPT_28 was validated by cloning and Sanger sequencing of cDNA (__supplementary PCR methods__).~~
 
@@
 For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death
+TRXPT_2 and ORF1 are isoforms
+Presumeably, if the junction reads were normalized, MLP would not be predominant at 12hpi.
 \newpage
@@
 A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
-The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al*[@Mahsoub2017] with modifications.
+The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub _et al_ [@Mahsoub2017] with modifications.
 Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-seq.
 The infection was repeated but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
+Still one more independent infection was done at time points ranging from 12 to 168-h.p.i for qPCR quantification of virus titers.
 
@@
 However, these predicted splice junctions had not been experimentally validated hitherto, and we identified additional novel exons, giving the complete picture of these transcripts.
-~~The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in Table###1~~.
-We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit paired with their respective universal primers (~~supplementary, PCR methods~~).
+The novel splice junctions in this work discovered in the assembled transcripts using the `StringTie` transcript assembler which we validated by PCR and Sanger Sequencing are shown in supplementary PCR methods Table 1.
+Briefly, we designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit (TU) paired with their respective universal primers for the TU (~~supplementary PCR methods).
 Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
-After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
+After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System, these primers were used in a targeted PCR amplification, the products analyzed with agarose gel electrophoresis to confirm expected band sizes, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
 
-### 3' Rapid Amplification of cDNA Ends (3'RACE)  
-We performed a rapid amplification of sequences from the 3' ends of mRNAs (3'-RACE) experiment with total RNA extracted from independently infected MDTC-RP19 cells following the protocol described by Green _et al_ [@Green2019] with modifications.
-Briefly,
+### 3' Rapid Amplification of cDNA Ends (3'-RACE)  
+We performed a rapid amplification of sequences from the 3' ends of mRNAs (3'-RACE) experiment using a portion of the extracted total RNA of infected MDTC-RP19 cells used for the RNA-seq experiment as explained above.
+We followed the protocol described by Green _et al_ [@Green2019] with modifications.
+Briefly, 1ug of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter–primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
+A gene-specific sense primer with a 5'-end KpnI restriction site paired with an anti-sense adapter-primer with a 5'-end BamHI site were used to amplify target sections of the cDNA using Invitrogen's Platinum™ Taq DNA polymerase High Fidelity, following manufacturer's instructions.
+The PCR amplicons were restriction digested, cloned, and Sanger sequenced.
 
@@
 Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) and *Meleagris gallopavo* (https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings without relying on known splice sites.
-The generated `BAM` files from each infection time-point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI containing the predicted ORFs of THEV as a guide.
+The generated `BAM` files from each infection time-point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI cont m.
+aining the predicted ORFs of THEV as a guide.
 A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
-
-TRXPT_2 and ORF1 are isoforms
 \newpage
@@
 ### CODE AVAILABILITY    
-All the code/scripts written for analysis of the data is available on github (linkXXXXX)
+All the code/scripts written for analysis of the data are available on github (https://github.com/Abraham-Quaye/thev_transcriptome)
 \newpage
@@
 **Figure 1.
-_Genomic map of THEV avirulent strain_**.
+_Genomic map of THEV avirulent strain annotated ORFs_**.
 The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
@@
 The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
-**b) _Growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
-Virus titers were a qPCR assay.
+**b) _Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
+Virus titers were a quantified with a qPCR assay.
 There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured.
@@
                 col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+                             "strand", "4hpi", "12hpi", "24hpi", "72hpi",
+                             "status", "coding_potential")) %>%
   theme_zebra() %>%
@@
                                splice_site = "Splice Donor-Acceptor",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+                               "72hpi" = "72h.p.i", "status" = "Junction Status",
+                               coding_potential = "Coding Potential") %>%
   flextable::align(align = "center", part = "all") %>%
   add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                 colwidths = c(1, 4, 1, 4, 2)) %>%
+  flextable::vline(j = c(1, 5, 6, 10, 11), border = fp_border_default(color = "grey",
                                                                   width = 1.5)) %>%
-  footnote(., i = 2, j = 10, value = as_paragraph(c("Not validated for TRXPT_4")),
+  footnote(., i = 1, j = 11, value = as_paragraph(c("Not validated for TRXPT_4")),
            ref_symbols = c("*"), part = "body")
@@
 Exons are depicted as boxes connected by introns (dotted lines).
-Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and the previously annotated ORF4 is colored black.
+Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and the full ORF1 transcript and previously annotated ORF4 are colored black.
 Each transcript or ORF is labelled with its name to the right.
@@
                 col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
+                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi",
+                             "status")) %>%
   theme_zebra() %>%
@@
                                                                   width = 1.5)) %>%
-  footnote(., i = 6, j = 12, value = as_paragraph(c("Truncated transcript")),
+  footnote(., i = 6, j = 12, value = as_paragraph(c("Incomplete transcript")),
            ref_symbols = c("*"), part = "body")
@@
 
-```{r region-by-region_e4_figure, fig.height=5, fig.width=7, warning=FALSE}
+```{r region-by-region_e4_figure, fig.height=5, fig.width=8, warning=FALSE}
 reg_e4_brkdown <- reg_e4_brkdown %>%
@@
          `24hpi` = as.numeric(`24hpi`), `72hpi` = as.numeric(`72hpi`)) %>%
-  select(-c(coding_potential, region)) %>%
+  # select(-c(coding_potential, region)) %>%
   group_by(trxpt_id, start, end, splice_site, intron_len, strand, status) %>%

### 2023-12-19 supplementary_thev_trxptome.Rmd
wrote some E2 reg results and added gels designed primers for E2 trxpt_15 and pol

--- 2023-08-31 supplementary_thev_trxptome.Rmd
@@
 library(tidyverse)
-library(gt)
-
+library(flextable)
 source("scripts/r/bam_file_analysis.R")
+source("scripts/r/reg_by_reg_plots.R")
 ```
@@
 ```{r Sup Table 1C}
-gt(tp_reg_expr_72)
+flextable(tp_reg_expr_72) %>% theme_zebra()
 ```
+
+\newpage
+## Supplementary PCR Methods
+```{r Supplementary PCR Methods}
+set_flextable_defaults(font.size = 3.5)
+
+flextable(supp_pcr_meth_tab) %>%
+  theme_zebra() %>%
+  flextable::fontsize(j = c("forwardP", "reverseP"), size = 3) %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::width(., width = 0.35) %>% 
+  colformat_image(j = "gel_image", i = c(1, 3:7, 9, 10), na_str = "-",
+                  width = 1, height = 1) %>%
+  flextable::width(j = ~forwardP, width = 1) %>%
+  flextable::width(j = ~reverseP, width = 1) %>%
+  # flextable::width(j = ~valid_status, width = 0.35) %>%
+  flextable::width(j = ~gel_image, width = 1) %>% 
+  footnote(., i = c(1:6, 7, 9, 10), j = 12, value = as_paragraph(c("Primer binds exon 1")),
+           ref_symbols = c("a"), part = "body") %>%
+  footnote(., i = c(1:6, 7, 9, 10), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
+           ref_symbols = c("b"), part = "body")
+```

### 2023-12-19 scripts/r/abundance_analyses.R

@@ -304,7 +304,7 @@ plot_all_junc_abunds <- bulk_junc_stats %>%
   group_by(timepoint, region) %>%
   reframe(accum_tally_j = n(),
           total_rd_j_tp_reg = sum(read_count)) %>%
-  drop_na(region) %>%
+  # drop_na(region) %>%
   split(.$timepoint) %>%
   map(mutate, tot_reads_time = sum(total_rd_j_tp_reg)) %>% 
   do.call("rbind", .) %>%
@@ -320,7 +320,8 @@ plot_all_junc_abunds <- bulk_junc_stats %>%
           reg_junc_percent = round((tot_rds_tp_reg / mean_tot_rds_time) * 100, 2)) %>%
   replace_na(replace = list(mean_tot_rds_time = 0,
                             reg_junc_percent = 0)) %>%
-  mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi")))
+  mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>%
+  drop_na()
 
 
 

### 2023-12-19 scripts/r/bam_file_analysis.R

@@ -253,7 +253,6 @@ tab1 <- tibble(Metric = c("Total reads",
 # ---------------------
 # ----------------------
 find_sig_juncs <- function(tp, rg){
-  tp <- "12hpi"
   regs <- c("E1","E2", "E3", "E4", "IM", "MLP")
   
   total_tp_juncs <- bulk_junc_stats %>%

### 2023-12-19 scripts/r/plot_abundances.R

@@ -154,7 +154,7 @@ all_ss_seq <- bulk_junc_stats %>%
 # PLOT TRANSCRIPT ABUNDANCES FROM BALLGOWN
 # ====================================================================
 
-# plot
+# plot transcript expression levels per individual
 trxpt_fpkms <- t_expr_each %>%
   filter(timepoint != "4h.p.i") %>%
   ggplot(aes(trxpt_id, fpkm_trxpt_percent, group = timepoint, fill = timepoint)) +
@@ -184,7 +184,7 @@ trxpt_fpkms <- t_expr_each %>%
 #        width = 18, height = 12, dpi = 500)
 
 
-# plot transcript expression levels
+# plot transcript expression levels per region
 reg_fpkms <- t_exp_lev_byregion %>%
   filter(timepoint != "4h.p.i") %>%
   ggplot(aes(timepoint, fpkm_reg_percent, group = region, color = region)) +

### 2023-12-19 scripts/r/reg_by_reg_plots.R

@@ -71,8 +71,8 @@ t_exp_levels <- texpr(raw_data, meas = "all") %>%
 
 comp_spliced_gtf <- left_join(spliced_gtf, t_exp_levels,
                               by = "trxpt_id") %>%
-  mutate(sstcodon = c(rep(211, 3), 1965, rep(NA, 22), 26246, 3616),
-         stpcodon = c(2312, 1953, rep(2312, 2), rep(NA, 22), 25204, 2334))
+  mutate(sstcodon = c(rep(211, 3), 1965, rep(NA, 18), 18186, rep(NA, 3), 26246, 3616),
+         stpcodon = c(2312, 1953, rep(2312, 2), rep(NA, 18), 16973, rep(NA, 3), 25204, 2334))
 
 
 # load in data and prepare predicted ORFs only
@@ -108,13 +108,30 @@ predicted_orfs <- predicted_orfs %>%
                             gene_name == "UXP" ~ "LONE",
                             TRUE ~ "MLP")) %>%
   arrange(strand, region) %>%
+  # manually added transcripts not from StringTie
   rbind(tibble( gene_name = "ORF4", transcript_id = "gp04", strand = "+",
                 start_1 = 1965, start_2 = NA, start_3 = NA, end_1 = 2312,
-                end_2 = NA, end_3 = NA, region = "E1")) 
+                end_2 = NA, end_3 = NA, region = "E1")) %>%
+  # Full ORF1 transcript
+  rbind(tibble( gene_name = "Full ORF1", transcript_id = "fORF1", strand = "+",
+                start_1 = 54, start_2 = 54, start_3 = 54, end_1 = 2325,
+                end_2 = 2325, end_3 = 2325, region = "E1")) %>%
+  #TRXPT_21B (DBP isoform2)
+  rbind(tibble( gene_name = "TRXPT_21B", transcript_id = "DBP_iso2", strand = "-",
+                start_1 = 16934, start_2 = 16934, start_3 = 18684, end_1 = 18751,
+                end_2 = 18189, end_3 = 18751, region = "E2"))
 
 combined_gtf <- plyr::rbind.fill(comp_spliced_gtf, predicted_orfs) %>% 
   arrange(strand, region) %>% as_tibble() %>%
-  mutate(trxpt_id = ifelse(is.na(trxpt_id), gene_name, trxpt_id))
+  mutate(trxpt_id = ifelse(is.na(trxpt_id), gene_name, trxpt_id),
[…]

### 2023-12-20 manuscript_thev_transcriptome.Rmd
made fig 3 as one plot and removed uneeded plots

@@
 ---
+
 \vspace{5mm}
@@
 \vspace{10mm}
+
 Abraham Quaye^1\*^, Bret Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
@@
 
-^\*^Department of Microbiology and Molecular Biology, Brigham Young University       
-^1^First-author      
+^\*^Department of Microbiology and Molecular Biology, Brigham Young University\
+^1^First-author\
 ${^\dagger}$ Corresponding Author
@@
 \vspace{5mm}
-**Corresponding Author Information**     
-[brian_poole@byu.edu](mailto:brian_poole@byu.edu)       
-Department of Microbiology and Molecular Biology,       
-4007 Life Sciences Building (LSB),    
-Brigham Young University,   
-Provo, Utah  
+
+**Corresponding Author Information**\
+[brian_poole\@byu.edu](mailto:brian_poole@byu.edu)\
+Department of Microbiology and Molecular Biology,\
+4007 Life Sciences Building (LSB),\
+Brigham Young University,\
+Provo, Utah\
 \newpage
@@
 ```
+
 ## ABSTRACT
-**Background:** Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by _immunosuppression (IS)_ and bloody diarrhea.
-This disease is caused by _Turkey Hemorrhagic Enteritis Virus (THEV)_ of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
+
+**Background:** Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by *immunosuppression (IS)* and bloody diarrhea.
+This disease is caused by *Turkey Hemorrhagic Enteritis Virus (THEV)* of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
 The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
-_Our objective is to understand the genetic basis by which VAS induces IS_.
-The _transcriptome of THEV_ was studied to set the stage for further experimentation with specific viral genes that may mediate IS.
+*Our objective is to understand the genetic basis by which VAS induces IS*.
+The *transcriptome of THEV* was studied to set the stage for further experimentation with specific viral genes that may mediate IS.\
 **Methods:** After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
@@
 An in-house script was used to consolidate transcripts from all time-points, generating the final transcriptome.
-PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.
+PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.\
 **Results and Conclusions:** A total of `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
@@
 In keeping with all adenoviruses, all transcripts were spliced with either with 5'- or 3'-multi exon UTRs hitherto unknown.
-*~~Thirteen~~* novel exons were identified which were validated by PCR and Sanger sequencing.
-The splicing patterns strongly suggest that there are *~~three~~* main promoters (E1, E3, and major late promoters) driving expression of most of the genes with *~~two~~* possible minor promoters driving single genes (ORF7 and ORF8).
+~~*Thirteen*~~ novel exons were identified which were validated by PCR and Sanger sequencing.
+The splicing patterns strongly suggest that there are ~~*three*~~ main promoters (E1, E3, and major late promoters) driving expression of most of the genes with ~~*two*~~ possible minor promoters driving single genes (ORF7 and ORF8).
 This RNA-sequencing experiment is the first study of THEV gene expression to date.
@@
 ## INTRODUCTION
+
 Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all vertebrates.
@@
 Currently, there are three recognized members of the genus SiAdV: frog adenovirus 1, raptor adenovirus 1, and turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009].
-Members of SiAdV have the smallest genome size (~26 kb) and gene content (~23 genes) of all known AdVs, and many “genus-specific” putative genes of unknown functions have been annotated (see __Figure 1__)[@Harrach2008; @Kovács2011; @Davison2003].
+Members of SiAdV have the smallest genome size (\~26 kb) and gene content (\~23 genes) of all known AdVs, and many "genus-specific" putative genes of unknown functions have been annotated (see **Figure 1**)[@Harrach2008; @Kovács2011; @Davison2003].
 
@@
 Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
-Thus, the MLTU produces a complex repertoire of mRNA with diverse 5'-UTRs spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5).
+Thus, the MLTU produces a complex repertoire of mRNA with diverse 5' untranslated regions (UTRs) spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5).
 Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
@@
 ## RESULTS
-**Overview of sequencing data and analysis pipeline outputs**     
+
+**Overview of sequencing data and analysis pipeline outputs**\
 A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
@@
 A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
-The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (__Table 1__, __Figure 2a__).
+The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (**Table 1**, **Figure 2a**).
 From the mapped reads, we identified an overall total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
@@
 Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having coverage as high as `r max_junread72` reads.
-The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes an active infection, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (__Figure 2b__).
+The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes an active infection, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2b**).
 Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
-In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` transcripts all of which are novel, ~~and using 3' Rapid Amplification of cDNA Ends (3'RACE) and other methods, we further identified #### unique splice variants~~.
-Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (__Figure 3__).
-The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (http://www.ncbi.nlm.nih.gov/geo) under **accession no.
+In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` transcripts all of which are novel, ~~and using 3' Rapid Amplification of cDNA Ends (3'RACE) and other methods, we further identified \#### unique splice variants~~.
+Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (**Figure 3**).
+The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under **accession no.
 XXXXXX**.
 
-**Changes in THEV splicing profile over time**   
+**Changes in THEV splicing profile over time**\
 AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU) or region.
@@
 Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
+
 ```{r temporal transcript expression levels}
@@
 ```
+
 Individually, TRXPT_21 (DBP) - from the E2 region - was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
 Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
-The later time points were dominated by the MLP region; transcripts TRXPT_10 and TRXPT_14 were most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (__Figure 4a__).
-When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).
+The later time points were dominated by the MLP region; transcripts TRXPT_10 and TRXPT_14 were most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (**Figure 4a**).
+When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 h.p.i, after which the MLP region assumes predominance (**Figure 4b**).
 Secondly, we estimated relative abundances of all splice junctions for each time point using the raw reads.
@@
 At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLP was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junctions reads.
-(__Table 2a__).
+(**Table 2a**).
 The levels of the top most abundant junctions at 12 h.p.i were maintained also 24 h.p.i as the most significantly expressed.
-However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__).
-At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__.
-Also see __Supplementary Tables 1a-c__; __Figure 4c__).
-When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (__Figure 4d__).
+However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b**).
+At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (**Table 2c**.
+Also see **Supplementary Tables 1a-c**; **Figure 4c**).
+When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (**Figure 4d**).\
 Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
@@
 After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
-Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (__Figure 5__).
-Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the Hyd protein as the 3'-most coding sequence (CDS) if the first start codon (SSC) is skipped.
+Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (**Figure 5**).
+Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered.
 The 5'-most CDS of TRXPT_1 is multi-exonic, producing a 17.9 kilodalton (kDa) protein of 160 residues [amino acids (aa)].
 The CDS begins in the first exon, starting at position 211, spans the second exon, and terminates in the third exon at position 2312.
-From the 5'-most SSC, TRXPT_2 encodes the largest protein in this region ——  a 64.3 kDa, 580 aa protein with the same SSC as TRXPT_1 (position 211).
+From the 5'-most start codon (SSC), TRXPT_2 encodes the largest protein in this region - a 64.3 kDa, 580 aa protein with the same SSC as TRXPT_1 (position 211).
 This CDS spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 to 1964 (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of the Hyd STC.
@@
 TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-From our analysis, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2; however, given that studies in MAdVs show that E1 mRNAs share a common 5' and 3' positions, only differing from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and the TSS just like the transcription termination site (TTS) are identical for all E1 transcripts.
+From our RNA-seq data, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2; however, given that studies in MAdVs show that E1 mRNAs share a common 5' and 3' positions, only differing from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and the TSS (at position 54bp) just like the transcription termination site (TTS; at position 2325bp) are identical for all E1 transcripts.
 Regardless of the TSS considered for TRXPT_3, the coding potential remains unaffected.
@@
 However, if we assume that TRXPT_4 shares the same TSS as TRXPT_1, then the 5'-most CDS is a distinct multi-exonic 15.9 kDa, 143 aa protein with the same SSC as TRXPT_1 and TRXPT_2 but with a unique STC.
-All splice junctions of the transcripts in this region (except the junction for TRXPT_4) have been validated by cloning and Sanger sequencing of cDNA (__Figure 5b__; __supplementary PCR methods__).
-Finally, during our validation of TRXPT_2, ORF1 was present on the agarose gel and Sanger sequencing results as a bona fide transcript (__supplementary PCR methods__).
-This is corroborated by 3'-RACE experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing with a poly-A tail at the TTS of transcripts in this region.
+All splice junctions of the transcripts in this region (except the junction for TRXPT_4) have been validated by cloning and Sanger sequencing of cDNA (**Figure 5b**; **supplementary PCR methods**).
+Finally, during our validation of TRXPT_2, ORF1 was present on the agarose gel and Sanger sequencing results as a bona fide transcript (**supplementary PCR methods**).
+This is corroborated by 3'-RACE experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing with a poly-A tail immediately after the TTS of transcripts in this region.
 The 5'-most CDS of this transcript would encode ORF1.
@@
 Unlike MAdV where two promoters (E2-early and E2-late) were discovered [@Donovan2020], we discovered only a single promoter from which both E2A and E2B transcription is initiated.
-However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (__Figure 6__).
-The E2A ORF, DBP is one of three ORFs predicted to be spliced from two exons, with the CDS spanning both exons.
-The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern exactly but with an additional non-coding exon at the 5'-end (E2-5'UTR); hence, a three-exon transcript.
-The encoded protein (DBP; 380 residues, 43.3 kDa) is identical.
-This transcript was also corroborated in a 3'-RACE experiment.
+However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 6**).
+The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from two exons, with the CDS spanning both exons.
+The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern exactly but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp, making a three-exon transcript.
+The encoded protein (DBP; 380 residues, 43.3 kDa) remains identical.
+This transcript (TRXPT_21) was also corroborated in a 3'-RACE experiment.
 Additionally, from the 3'-RACE, a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript was found.
@@
 The SSC 173 bp downstream of TRXPT_21's SSC yields a 346 residue, 39.3 kDa product, which is in-frame of DBP but wholly contained in the second exon starting at 18,013 bp and terminating just like DBP at 16,973 bp.
-TRXPT_21 and TRXPT_21B share a common TSS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine-rich sequence where the polyadenylation occurs.
-Hence, we suggest that the two transcripts also share the same TTS at 16,934 bp (__Figure 6__).
+TRXPT_21 and TRXPT_21B share a common TSS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence where the polyadenylation occurs.
+This suggests that the bona fide E2A TTS is at 16,934 bp (**Figure 6**).
+
+The E2B region transcripts share the TSS of E2A - begins with E2-5'UTR - but extend thousands of base pairs downstream to reach the TTS at 2334bp, which is immediately followed by an A-T rich sequence where polyadenylation probably occurs.
+Interestingly, the TTS of the E1 TU on the sense strand is in the immediate vicinity of this A-T rich sequence (position 2323-2339bp), and the A-T rich sequence is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B transcripts.
+The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four (**Figure 6**).
+TRXPT_7 has the coding potential for IVa2 and both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like all other AdVs.
+The predicted splice junction is corroborated by our data; however, the transcript is marked longer than the predicted ORF.
+There are two novel exons, the third exon is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size, although the SSC and STC encoding pTP are unaffected.
+The first two exons are 5'-UTRs - the SSC here is immediately followed by STCs - hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC is utilized.
+The encoded product is identical to the predicted pTP ORF (597 residues; 70.5 kDa).
+However, if we consider secondary SSC usage, the encoded product is identical to the predicted Ad-pol ORF (1112 residues; 129.2 kDa), with SSC at 6768bp and STC at 3430bp.
+
+~~finish trxpt_7 and then discuss trxpt_6~~.
 
@@
 TRXPT_5 is a two-exon transcript located on the reverse strand spliced at 3447-3615.
-The first exon is an untranslated region (UTR), except the last 2 nucleotides, which connect with the first nucleotide of second exon to form the 5'-most SSC.
+The first exon is an UTR, except the last 2 nucleotides, which connect with the first nucleotide of second exon to form the 5'-most SSC.
 This first SSC is 4 codons upstream and in-frame of the predicted IVa2 SSC.
@@
 
-The splice junction of ~~TRXPT_5 add trxpts from E2~~ were confirmed by cloning and Sanger sequencing of cDNA (__supplementary PCR methods__).
+The splice junction of ~~TRXPT_5 add trxpts from E2~~ were confirmed by cloning and Sanger sequencing of cDNA (**supplementary PCR methods**).
 
@@
 Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the same strand as ORF8 nor transcribed from a promoter in the E4 region, only ORF8 can legitimately be classified as a transcript in this TU.
-This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the reverse strand (__Figure 8__).
+This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the reverse strand (**Figure 8**).
 The transcript (TRXPT_28) spans 25192-26247 and is spliced at 25701-26055; hence, a two-exon transcript.
@@
 The encoded protein from this SSC is in-frame with the SSC of ORF8 in the second exon; hence, the C-terminus of this longer protein (26.4 kDa, 229 aa) would be the identical to the predicted ORF8 protein.
-~~The splice junction of TRXPT_28 was validated by cloning and Sanger sequencing of cDNA (__supplementary PCR methods__).~~
+~~The splice junction of TRXPT_28 was validated by cloning and Sanger sequencing of cDNA (**supplementary PCR methods**).~~
 
-**Major Late Promoter Region (MLP) transcripts**.
-\newpage
+**Major Late Promoter Region (MLP) transcripts**. \newpage
 
 ## DISCUSSION/CONCLUSIONS
+
 In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene.
@@
 However, the relative proportions over these similar regions shows some variation over time.
-For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death
-TRXPT_2 and ORF1 are isoforms
-Presumeably, if the junction reads were normalized, MLP would not be predominant at 12hpi.
+For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death TRXPT_2 and ORF1 are isoforms Presumably, if the junction reads were normalized, MLP would not be predominant at 12hpi.
 \newpage
@@
 ## MATERIALS AND METHODS
+
 ### Cell culture and THEV Infection
+
 The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium with 10% fetal bovine serum (FBS), 20% chicken serum (ChS), 5% tryptose phosphate broth (TPB), and 1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin), at 41^o^C in a humidified atmosphere with 5% CO~2~.
@@
 A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
-The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub _et al_ [@Mahsoub2017] with modifications.
+The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al* [@Mahsoub2017] with modifications.
 Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-seq.
@@
 ### RNA extraction and Sequencing
+
 Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` per manufacturer's instructions.
 An agarose gel electrophoresis was performed to check RNA integrity.
-The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2.
+The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was \>2 and \<2.2.
 Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
@@
 ### Validation of Novel Splice Junctions
+
 All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
@@
 The novel splice junctions in this work discovered in the assembled transcripts using the `StringTie` transcript assembler which we validated by PCR and Sanger Sequencing are shown in supplementary PCR methods Table 1.
-Briefly, we designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit (TU) paired with their respective universal primers for the TU (~~supplementary PCR methods).
+Briefly, we designed primers that crossed a range of novel exon--exon boundaries for each specific transcript in a transcription unit (TU) paired with their respective universal primers for the TU (\~\~supplementary PCR methods).
 Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
@@
 ### 3' Rapid Amplification of cDNA Ends (3'-RACE)
+
 We performed a rapid amplification of sequences from the 3' ends of mRNAs (3'-RACE) experiment using a portion of the extracted total RNA of infected MDTC-RP19 cells used for the RNA-seq experiment as explained above.
-We followed the protocol described by Green _et al_ [@Green2019] with modifications.
-Briefly, 1ug of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter–primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
+We followed the protocol described by Green *et al* [@Green2019] with modifications.
+Briefly, 1ug of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter--primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
 A gene-specific sense primer with a 5'-end KpnI restriction site paired with an anti-sense adapter-primer with a 5'-end BamHI site were used to amplify target sections of the cDNA using Invitrogen's Platinum™ Taq DNA polymerase High Fidelity, following manufacturer's instructions.
@@
 ### Computational Analysis of RNA Sequencing Data: Mapping and Transcript characterization
-Analysis of our sequence reads were analyzed following a well established protocol described by Pertea _et al_ [@Pertea2016], using `SNAKEMAKE 7.24.0` to drive the pipeline.
+
+Analysis of our sequence reads were analyzed following a well established protocol described by Pertea *et al* [@Pertea2016], using `SNAKEMAKE 7.24.0` to drive the pipeline.
 Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/) and *Meleagris gallopavo* (https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings without relying on known splice sites.
+Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings without relying on known splice sites.
 The generated `BAM` files from each infection time-point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI cont m.
@@
 ### CODE AVAILABILITY
-All the code/scripts written for analysis of the data are available on github (https://github.com/Abraham-Quaye/thev_transcriptome)
-\newpage
+
+All the code/scripts written for analysis of the data are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>) \newpage
 
 ## ACKNOWLEDGMENTS
-`LC Sciences` - RNA sequencing was done here
-`Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here
-\newpage
+
+`LC Sciences` - RNA sequencing was done here `Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here \newpage
 
 ## REFERENCES
+
+```{=tex}
 \setlength{\parindent}{-0.25in}
 \setlength{\leftskip}{0.25in}
+```
 \noindent
-<div id="refs"></div>
+
+::: {#refs}
+:::
+
+```{=tex}
 \setlength{\parindent}{0in}
@@
 \newpage
+```
+## TABLES AND FIGURES
 
-## TABLES AND FIGURES     
 ![](results/r/figures/thev_orf_map.png)
+
 **Figure 1.
-_Genomic map of THEV avirulent strain annotated ORFs_**.
+*Genomic map of THEV avirulent strain annotated ORFs***.
 The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
@@
 ![](results/r/figures/fig_2.png)
+
 **Figure 2: Increasing levels of THEV over time.
-a) _Per base coverage of sequence reads mapping to THEV genome by time point_**.
+a) *Per base coverage of sequence reads mapping to THEV genome by time point***.
 The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
-**b) _Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**.
+**b) *Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line***.
 Virus titers were a quantified with a qPCR assay.
@@
 \newpage
-![](results/r/figures/thev_spliced_map.png)
-![](results/r/figures/thev_patched_timepoints_spliced_map.png)
+
+![](results/r/figures/figure3.png)
+
 **Figure 3.
-a) __Full transcriptome of THEV__**.
+a) Composite transcriptome of THEV from RNA-seq**.
 THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map).
@@
 Predicted ORFs are also indicated here, colored light grey.
-**b) __THEV transcripts identified at given time points__**.
+**b) THEV transcripts identified at given time points**.
 Transcripts are color coded as explained in **a**.
@@
 
-![](results/r/figures/figure_4a_d.png)
-**Figure 4: Changes in splicing and expression profile of THEV over time.** 
-**a)** Expression levels of transcripts over time.**b)** Expression levels of transcripts by region over time.**c)** Relative abundances of all splice junctions over time.
+![](results/r/figures/figure_4a_d.png) **Figure 4: Changes in splicing and expression profile of THEV over time.** **a)** Expression levels of transcripts over time.**b)** Expression levels of transcripts by region over time.**c)** Relative abundances of all splice junctions over time.
 **d)** Relative abundances of junctions in transcriptome.
@@
 
-**Figure 9: MLP region transcripts. a)**
-\newpage
+**Figure 9: MLP region transcripts. a)** \newpage
 
@@
 ```
+
 \newpage

### 2023-12-20 scripts/r/plot_thev_timepoint_splicing.R

@@ -7,20 +7,20 @@ library(rtracklayer)
 library(patchwork)
 library(ggtext)
 
+# load full transcriptome plot
+source("scripts/r/thev_splicing_fullMap.R")
 # table of transcript ids for different genome regions here for transcription unit assignment
 
 trxpt_ids_repo <- tribble(~region, ~`4hpi`, ~`12hpi`, ~`24hpi`, ~`72hpi`,
-                     "e1", NA, c("12S1.1.2", "12S1.1.1"), c("24S1.1.1", "24S2.1.1",
-                                                            "24S2.1.2", "24S3.1.2",
-                                                            "24S3.1.1", "24S1.1.2"), c("72S1.1.1", "72S2.1.1", "72S2.1.2", "72S3.1.1"),
-                     "e2", c("4S1.4.1",
-                             "4S2.3.1"), NA, c("24S2.2.2", "24S3.2.2", "24S3.2.1",
-                                               "24S1.2.1", "24S1.2.2", "24S2.2.1",
-                                               "24S1.2.4", "24S3.2.5", "24S2.2.4"), c("72S1.12.1", "72S2.8.1", "72S3.10.1", "72S3.3.2"),
-                     "e3", c("4S1.5.1"), c("12S3.6.2",
-                                           "12S1.4.7",
-                                           "12S1.4.8"), c("24S3.11.1", "24S1.11.1", "24S2.11.1",
-                                                          "24S1.11.2", "24S3.11.2", "24S2.11.2"), c("72S1.13.4", "72S3.11.3", "72S1.13.1", "72S3.11.2", "72S1.13.2"),
+                     "e1", NA, c("12S1.1.2", "12S1.1.1"),
+                     c("24S1.1.1", "24S2.1.1","24S2.1.2", "24S3.1.2", "24S3.1.1", "24S1.1.2"),
+                     c("72S1.1.1", "72S2.1.1", "72S2.1.2", "72S3.1.1"),
+                     "e2", c("4S1.4.1","4S2.3.1"), NA,
+                     c("24S2.2.2", "24S3.2.2", "24S3.2.1","24S1.2.1", "24S1.2.2", "24S2.2.1",
+                      "24S1.2.4", "24S3.2.5", "24S2.2.4"), c("72S1.12.1", "72S2.8.1", "72S3.10.1", "72S3.3.2"),
+                     "e3", c("4S1.5.1"), c("12S3.6.2","12S1.4.7", "12S1.4.8"), 
[…]

### 2023-12-20 scripts/r/reg_by_reg_plots.R

@@ -71,8 +71,8 @@ t_exp_levels <- texpr(raw_data, meas = "all") %>%
 
 comp_spliced_gtf <- left_join(spliced_gtf, t_exp_levels,
                               by = "trxpt_id") %>%
-  mutate(sstcodon = c(rep(211, 3), 1965, rep(NA, 18), 18186, rep(NA, 3), 26246, 3616),
-         stpcodon = c(2312, 1953, rep(2312, 2), rep(NA, 18), 16973, rep(NA, 3), 25204, 2334))
+  mutate(sstcodon = c(rep(211, 3), 1965, rep(NA, 18), 18186, NA, 10995, NA, 26246, 3616),
+         stpcodon = c(2312, 1953, rep(2312, 2), rep(NA, 18), 16973, NA, 6765, NA, 25204, 2334))
 
 
 # load in data and prepare predicted ORFs only
@@ -302,9 +302,11 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part, trxpt_part2=NULL){
   # Loop through the remaining exons (start and end columns) and 
   # add a geom_segment layer for each pair
   for (i in seq_along(start_cols)[-1]) {
-    splice_map <- splice_map +
-      geom_segment(aes_string(x = start_cols[i], xend = end_cols[i], y = "ypos", yend = "ypos"),
-                   color = combined_gtf$color, linewidth = 7)
+    if(!base::is.na(start_cols[i])){
+      splice_map <- splice_map +
+        geom_segment(aes_string(x = start_cols[i], xend = end_cols[i], y = "ypos", yend = "ypos"),
+                     color = combined_gtf$color, linewidth = 7)
+    }
   }
   
   # Add labels for full plot -----------------

### 2023-12-20 scripts/r/thev_splicing_fullMap.R

@@ -270,7 +270,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part){
     scale_y_continuous(expand = c(0.01,0.01),
                        limits = y_lims) +
     theme(plot.margin = margin(rep(15, 4)),
-          plot.background = element_rect(fill = "#ffffff", color = c("grey")),
+          plot.background = element_rect(fill = "#ffffff"),
           panel.background = element_rect(fill = "#ffffff"),
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
@@ -339,9 +339,9 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part){
 }  
 
 ## Save final figure of full transcriptome
-ggsave(plot = plot_full_trxptome(combined_gtf, "all"),
-       filename = "results/r/figures/thev_spliced_map.png",
-       dpi = 500, width = 12, height = 8)
+# ggsave(plot = plot_full_trxptome(combined_gtf, "all"),
+#        filename = "results/r/figures/thev_spliced_map.png",
+#        dpi = 500, width = 12, height = 8)
 
 
 

### 2024-01-06 manuscript_thev_transcriptome.Rmd
added E3 region plotand gels with SSC and STC

@@
 An in-house script was used to consolidate transcripts from all time-points, generating the final transcriptome.
-PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.\
-**Results and Conclusions:** A total of `r total_mapped` million reads mapped to THEV genome providing good coverage/depth, leaving no regions unmapped.
-All predicted genes in the genome were represented.
-In keeping with all adenoviruses, all transcripts were spliced with either with 5'- or 3'-multi exon UTRs hitherto unknown.
-~~*Thirteen*~~ novel exons were identified which were validated by PCR and Sanger sequencing.
-The splicing patterns strongly suggest that there are ~~*three*~~ main promoters (E1, E3, and major late promoters) driving expression of most of the genes with ~~*two*~~ possible minor promoters driving single genes (ORF7 and ORF8).
-This RNA-sequencing experiment is the first study of THEV gene expression to date.
-In keeping with other Adenoviruses, almost all THEV genes are spliced, and several genes are expressed as one transcription unit under a single promoter.
-This insight into THEV's transcriptome may allow the engineering of the VAS to provide immune protection with less or no associated IS.
+PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.
 \newpage
@@
 
-Virulent strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
+Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
 In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967].
@@
 However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU), which generates five families of late mRNAs (L1-L5).
+MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU or major late promoter [MLP]), which generates five families of late mRNAs (L1-L5).
 An additional gene (UXP or U exon) is located on the reverse strand.
@@
 Then the intermediate early genes, IVa2 and pIX are expressed followed by the late genes [@Zhao2014; @Donovan2020; @Guimet2016].
-MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs; all but pIX mRNA undergo at least one splicing event.
+MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs.
+All but the pIX mRNA undergo at least one splicing event.
 The MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
@@
 Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
-Almost all AdV mRNAs are generated by the excision of one or more introns and most of these introns are located in the 5' or 3' UTRs of pre-mRNA.
-Thus the viral introns scarcely interrupt the open reading frames (ORFs) [@Davison2003; @Zhao2014].
+During translation of AdV mRNA, recent studies strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020].
 
@@
 The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (**Table 1**, **Figure 2a**).
-From the mapped reads, we identified an overall total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
+From the mapped reads, we identified a total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
 For example all the `r tot_jun_4` unique junctions at 4 h.p.i had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads/junction.
@@
 
-**Early Region 1 (E1) transcripts**.
+**Early Region 1 (E1) transcripts**    
 This region in MAdVs is the first transcribed after successful entry of the viral DNA into the host cell nucleus, albeit at low levels [@Zhao2014].
@@
 Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered.
-The 5'-most CDS of TRXPT_1 is multi-exonic, producing a 17.9 kilodalton (kDa) protein of 160 residues [amino acids (aa)].
+The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a 17.9 kilodalton (kDa) protein of 160 residues [amino acids (aa)].
 The CDS begins in the first exon, starting at position 211, spans the second exon, and terminates in the third exon at position 2312.
@@
 However, it has an SSC 102 bp upstream and in-frame with ORF1's predicted SSC.
-The N-terminus of TRXPT_2 CDS therefore, shares substantial protein sequence similarity with ORF1 but Hyd and TRXPT_2 are not in-frame; hence no protein sequence similarity.
+TRXPT_2 CDS therefore, shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SSC of Hyd is not in-frame.
 TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-From our RNA-seq data, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2; however, given that studies in MAdVs show that E1 mRNAs share a common 5' and 3' positions, only differing from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and the TSS (at position 54bp) just like the transcription termination site (TTS; at position 2325bp) are identical for all E1 transcripts.
-Regardless of the TSS considered for TRXPT_3, the coding potential remains unaffected.
+From our RNA-seq data, all E1 transcripts share the same transcription termination site (TTS; at position 2325bp); however, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (at position 54bp).
+Given that studies in MAdVs show that E1 mRNAs share not only a common TTS but also the TSS, and only differ from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and their actual TSS just like the TTS are identical for all E1 transcripts.
+Regardless of the TSS considered for TRXPT_3, the coding potential (CP) remains unaffected.
 Its 5'-most CDS, beginning at 1965 and sharing the same STC as TRXPT_1 and TRXPT_2, produces a 13.1 kDa, 115 residue protein.
 This CDS (ORF4) was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggests it is a bona fide ORF.
-The coding potential of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its coding potential is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
+The CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
 However, if we assume that TRXPT_4 shares the same TSS as TRXPT_1, then the 5'-most CDS is a distinct multi-exonic 15.9 kDa, 143 aa protein with the same SSC as TRXPT_1 and TRXPT_2 but with a unique STC.
@@
 The 5'-most CDS of this transcript would encode ORF1.
-Given that the SSC of the predicted ORF1 is in-frame but downstream of TRXPT_2 SSC, it suggests that the predicted ORF1 CDS is incomplete; it shares the same SSC and TSS, and TTS as TRXPT_2, but has a unique STC.
+However, the SSC of the predicted ORF1 is in-frame but downstream of TRXPT_2 SSC, suggesting that the predicted ORF1 CDS is a truncated ORF; it shares the same TSS, SSC, and TTS as TRXPT_2, but has a unique STC.
 
-**Early Region 2 (E2) and Intermediate Region (IM) transcripts**.
-The E2 TU expressed on the reverse strand, is subdivided into E2A and E2B and encodes three classical AdV proteins: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [@Donovan2020; @Zhao2014].
+**Early Region 2 (E2) and Intermediate Region (IM) transcripts**     
+The E2 TU expressed on the anti-sense strand, is subdivided into E2A and E2B and encodes three classical AdV proteins essential for genome replication: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [@Donovan2020; @Zhao2014].
 Unlike MAdV where two promoters (E2-early and E2-late) were discovered [@Donovan2020], we discovered only a single promoter from which both E2A and E2B transcription is initiated.
 However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 6**).
-The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from two exons, with the CDS spanning both exons.
-The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern exactly but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp, making a three-exon transcript.
-The encoded protein (DBP; 380 residues, 43.3 kDa) remains identical.
+
+The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from two exons.
+The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern exactly but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
+Thus a three-exon transcript with an identical encoded protein (DBP; 380 residues, 43.3 kDa).
 This transcript (TRXPT_21) was also corroborated in a 3'-RACE experiment.
@@
 This transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP because the first SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron, and does not yield any viable product.
-The SSC 173 bp downstream of TRXPT_21's SSC yields a 346 residue, 39.3 kDa product, which is in-frame of DBP but wholly contained in the second exon starting at 18,013 bp and terminating just like DBP at 16,973 bp.
-TRXPT_21 and TRXPT_21B share a common TSS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence where the polyadenylation occurs.
-This suggests that the bona fide E2A TTS is at 16,934 bp (**Figure 6**).
+Utilizing the SSC 173 bp downstream of TRXPT_21's SSC yields a 346 residue, 39.3 kDa product, which is in-frame of DBP but entirely contained in the second exon.
+TRXPT_21 and TRXPT_21B share a common TSS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 6**).
 
-The E2B region transcripts share the TSS of E2A - begins with E2-5'UTR - but extend thousands of base pairs downstream to reach the TTS at 2334bp, which is immediately followed by an A-T rich sequence where polyadenylation probably occurs.
-Interestingly, the TTS of the E1 TU on the sense strand is in the immediate vicinity of this A-T rich sequence (position 2323-2339bp), and the A-T rich sequence is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B transcripts.
+The E2B region transcripts share the TSS of E2A - begins with E2-5'UTR - but extend thousands of base pairs downstream to reach the TTS at 2334bp in the IM region, which is immediately followed by an A-T rich sequence (position 2323-2339bp) where polyadenylation probably occurs.
+Interestingly, the TTS of the E1 region on the sense strand is in the immediate vicinity of this A-T rich sequence, and the A-T rich sequence is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
 The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four (**Figure 6**).
-TRXPT_7 has the coding potential for IVa2 and both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like all other AdVs.
-The predicted splice junction is corroborated by our data; however, the transcript is marked longer than the predicted ORF.
-There are two novel exons, the third exon is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size, although the SSC and STC encoding pTP are unaffected.
-The first two exons are 5'-UTRs - the SSC here is immediately followed by STCs - hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC is utilized.
+TRXPT_7 has the CP for IVa2 and both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
+The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel 5' exons, the third exon (containing the SSC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
+The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC is utilized.
 The encoded product is identical to the predicted pTP ORF (597 residues; 70.5 kDa).
-However, if we consider secondary SSC usage, the encoded product is identical to the predicted Ad-pol ORF (1112 residues; 129.2 kDa), with SSC at 6768bp and STC at 3430bp.
-
+If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol ORF (1112 residues; 129.2 kDa).
 ~~finish trxpt_7 and then discuss trxpt_6~~.
@@
 
-The splice junction of ~~TRXPT_5 add trxpts from E2~~ were confirmed by cloning and Sanger sequencing of cDNA (**supplementary PCR methods**).
+**Early Region 3 (E3) transcripts**.   
+The E3 region is wholly contained in the MLTU and encodes proteins involved in modulating and evading the host immune defenses.
+In MAdVs, this region contains seven ORFs expressed from several transcripts which share the same TSS (from the E3 promoter) but have different TTSs [@Guimet2016; @Donovan2020; @Zhao2014].
+However, some E3 transcripts use the MLP as their TSS.
+Due to sharing the same TSS, in MAdVs, secSSC usage is heavily relied on for gene expression in this region except for 12.5K and transcripts using the MLP as TSS, as utilizing only the first SSC cannot produce all the other transcripts in this TU [@Donovan2020].
 
-**Early Region 3 (E3) transcripts**.
+In THEV, only one ORF (E3) was predicted in this region.
+However, we identified six transcripts here (`r paste0("TRXPT_", 22:27, collapse = ", ")`), all of which are novel (**Figure 7**).
+We identified two distinct TSSs - one similar to the classic MAdV E3 TSS (position 18,230bp) and the other about 500 bp downstream at 18,727bp.
+The E3 transcripts collectively have the CP for several THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU; however, some CDSs are nonidentical due to unpredicted splicing.
+For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered it to be a four-exon ORF expressed from TRXPT_24.
+The first two exons were not predicted but the last two, match the predicted exons precisely and the CDS is in-frame.
+However, the first 20bp of the predicted 33K (including the SSC) is spliced as as part of the second intron of TRXPT_24.
+Thus, the bona fide 33K is a 19.8 kDa, 171 residue protein spanning four exons.
+TRXPT_24 can also encode the ORFs, pVIII and E3 if we consider downstream SSC usage.
+TRXPT_22 and TRXPT_23 share the TSS of TRXPT_24 (E3 promoter; 18,230bp) but have distinct TTSs.
+Considering the first SSCs, they both encode novel 73 residue proteins that is over 80% similar but differ at the C-termini.
+Considering downstream SSC usage, both transcripts can encode pVIII and E3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+TRXPT_25 is the largest transcript in the TU.
+It also utilizes the classic E3 TSS but has distinct TTS.
+It is a two exon transcript, encoding a novel protein (t100K; 543 residues), which is a shorter isoform of the predicted 100K ORF.
+Considering secSSC usage on this transcript yields the predicted ORF, 22K.
+It also has the CP for pVIII and E3 in that order.
+Furthermore, during the validation of TRXPT_25's splice junction using primers that span the junction (18350-18717bp), we noticed a DNA band that corresponds to the full unspliced sequence (**supplementary PCR methods Table 1**).
+As TRXPT_25 only falls short of encoding the complete 100K protein due to its splice junction, this band (which we cloned and validated by Sanger sequencing) suggests that the predicted 100K is indeed expressed.
+This transcript (TRXPT_25B) although not seen in our RNA-seq data, likely shares the same TSS and TTS as TRXPT_25.
+Lastly, TRXPT_26 and TRXPT_27 share the same TSS, unique from the other transcripts in this region but have distinct TTSs.
+TRXPT_26 is a three-exon transcript but the first two are UTRs - only the terminal exon encodes proteins.
+It encodes pVIII as the 5'-most ORF and has the CP for E3 and Fiber in that order.
+TRXPT_27 on the other hand, is only a two-exon transcript but similarly, only the terminal exon contains the CDSs.
+It encodes Fiber as the 5'-most ORF and ORF7 downstream with secSSC usage.
+TRXPT_13, which seems to be an E3 transcript that uses the MLP as TSS is discussed under the MLTU transcripts.
 
@@
 
-**Major Late Promoter Region (MLP) transcripts**. \newpage
+**Major Late Transcription Unit (MLTU) or MLP Region transcripts**. \newpage
 
@@
 However, the relative proportions over these similar regions shows some variation over time.
-For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death TRXPT_2 and ORF1 are isoforms Presumably, if the junction reads were normalized, MLP would not be predominant at 12hpi.
+For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death TRXPT_2 and ORF1 are isoforms Presumably, if the junction reads were normalized, MLTU would not be predominant at 12hpi.
+The TTSs were all in the context of A-T rich sequences; which presumably serve as polyA signals.
+All splice junctions were confirmed by cloning and Sanger sequencing of cDNA (**supplementary PCR methods**).
 \newpage
@@
 The organization of TUs in the THEV genome is unsurprisingly similar to MAdVs; however, the MAdV genome shows significantly more transcripts.
-The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark grey, E4 - green, MLP - blue.
+The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark grey, E4 - green, MLTU - blue.
 Predicted ORFs are also indicated here, colored light grey.
@@
 **Figure 6: E2 and IM region transcripts.
-a)** The splice map of the E1 and IM transcription units.
+a)** The splice map of the E2 and IM transcription units.
+Exons are depicted as boxes connected by introns (dotted lines).
+Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
+Each transcript or ORF is labelled with its name to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+
+```{r region-by-region_e3, fig.height=16, fig.width=18, warning=FALSE}
+set_flextable_defaults(font.size = 7)
+ft <- flextable(reg_e3_brkdown,
+                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
+                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi",
+                             "status")) %>%
+  theme_zebra() %>%
+  flextable::set_table_properties(layout = "fixed",
+                       opts_pdf = list(caption_repeat = F)) %>%
+  flextable::set_header_labels(start = "Start", end = "End",
+                               splice_site = "Splice Donor-Acceptor",
+                               strand = "Strand", trxpt_id = "Transcript ID",
+                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+  flextable::align(align = "center", part = "all") %>%
+  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                 colwidths = c(1, 4, 2, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
+                                                                  width = 1.5))
+
+brkdwn_e3_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
+  plot_layout(heights = c(1, 0.05, 1))
+```
+**Figure 7: E3 transcripts.
+a)** The splice map of the E3 transcription unit.
 Exons are depicted as boxes connected by introns (dotted lines).
@@
 
-**Figure 9: MLP region transcripts. a)** \newpage
+**Figure 9: MLTU transcripts. a)** \newpage
 

### 2024-01-06 supplementary_thev_trxptome.Rmd
added E3 region plotand gels with SSC and STC

@@
   flextable::width(., width = 0.35) %>% 
-  colformat_image(j = "gel_image", i = c(1, 3:7, 9, 10), na_str = "-",
+  colformat_image(j = "gel_image", i = c(1:3, 6:16), na_str = "-",
                   width = 1, height = 1) %>%
@@
   flextable::width(j = ~gel_image, width = 1) %>% 
-  footnote(., i = c(1:6, 7, 9, 10), j = 12, value = as_paragraph(c("Primer binds exon 1")),
+  footnote(., i = c(1:4, 6:16), j = 12, value = as_paragraph(c("Primer binds exon 1")),
            ref_symbols = c("a"), part = "body") %>%
-  footnote(., i = c(1:6, 7, 9, 10), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
+  footnote(., i = c(1:4, 6:16), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
            ref_symbols = c("b"), part = "body")

### 2024-01-06 scripts/r/abundance_analyses.R

@@ -431,7 +431,9 @@ reg_e2_brkdown <- reg_brkdown_tab("E2") %>%
   mutate(status = c(rep("Validated", 5), "Unvalidated"))
 
 # E3 region table analysis for discussion
-reg_e3_brkdown <- reg_brkdown_tab("E3")
+reg_e3_brkdown <- reg_brkdown_tab("E3") %>%
+  mutate(status = "Validated")
+
 
 # E4 region table analysis for discussion
 reg_e4_brkdown <- reg_brkdown_tab("E4") %>%

### 2024-01-06 scripts/r/plot_abundances.R

@@ -233,29 +233,29 @@ ggsave(plot = patch_fig4, "results/r/figures/figure_4a_d.png",
 # ------------------------------
 # distribution of fpkm levels in samples
 
-fpkm_dist <- t_exp_levels %>%
-  mutate(fpkm = log2(fpkm + 1),
-         timepoint = factor(timepoint,
-                            levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>%
-  ggplot(aes(timepoint, fpkm, fill = timepoint)) +
-  geom_boxplot() +
-  geom_jitter(show.legend = F, width = 0.25, size = 3, alpha = 0.6) +
-  scale_y_continuous(expand = c(0.01, 0.01)) +
-  scale_fill_igv() +
-  labs(title = "Distribution of Transcript FPKM Values Across Four Timepoints",
-       x = "Time-Point",
-       y = "log2(FPKM + 1)",
-       fill = element_blank()) +
-  theme_classic() +
-  theme(plot.margin = margin(rep(20, 4)),
-        plot.title = element_text(size = 18, colour = "#000000", face = "bold",
-                                  hjust = 0.5),
-        axis.title = element_text(size = 16, face = "bold"),
-        axis.text = element_text(size = 14, color = "#000000"),
-        legend.justification = c(0, 0),
-        legend.position = c(0.92, 0.85),
-        legend.key.size = unit(1, "cm"),
-        legend.text = element_text(size = 14, face = "bold"))
-
-ggsave(plot = fpkm_dist, "results/r/figures/fpkm_dist_by_time.png",
-       width = 14, height = 10, dpi = 500)
+# fpkm_dist <- t_exp_levels %>%
+#   mutate(fpkm = log2(fpkm + 1),
+#          timepoint = factor(timepoint,
+#                             levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>%
+#   ggplot(aes(timepoint, fpkm, fill = timepoint)) +
+#   geom_boxplot() +
+#   geom_jitter(show.legend = F, width = 0.25, size = 3, alpha = 0.6) +
+#   scale_y_continuous(expand = c(0.01, 0.01)) +
+#   scale_fill_igv() +
+#   labs(title = "Distribution of Transcript FPKM Values Across Four Timepoints",
+#        x = "Time-Point",
+#        y = "log2(FPKM + 1)",
+#        fill = element_blank()) +
+#   theme_classic() +
[…]

### 2024-01-06 scripts/r/reg_by_reg_plots.R

@@ -38,6 +38,7 @@ spliced_gtf <- spliced_gtf %>%
   mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1)),
          transcript_id = factor(transcript_id, levels = trxpt_order)) %>%
   arrange(transcript_id)
+
 # trxpt id and names info
 
 exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
@@ -71,8 +72,14 @@ t_exp_levels <- texpr(raw_data, meas = "all") %>%
 
 comp_spliced_gtf <- left_join(spliced_gtf, t_exp_levels,
                               by = "trxpt_id") %>%
-  mutate(sstcodon = c(rep(211, 3), 1965, rep(NA, 18), 18186, NA, 10995, NA, 26246, 3616),
-         stpcodon = c(2312, 1953, rep(2312, 2), rep(NA, 18), 16973, NA, 6765, NA, 25204, 2334))
+  mutate(sstcodon = c(rep(211, 3), 1965, 
+                      rep(18230, 4), 20769, 22519,
+                      rep(NA, 12), 18186, NA, 10995, NA, 26246, 3616),
+         stpcodon = c(2312, 1953, rep(2312, 2), 
+                      20262, 20699, 20457, 20227, 21371, 23883,
+                      rep(NA, 12), 16973, NA, 6765, NA, 25204, 2334),
+         secSSC = c(rep(NA, 4), rep(20769, 3), 20142, 21247, 24512, rep(NA, 18)),
+         secSTC = c(rep(NA, 4), rep(21371, 3), 20411, 22116, 25168, rep(NA, 18)))
 
 
 # load in data and prepare predicted ORFs only
@@ -119,7 +126,11 @@ predicted_orfs <- predicted_orfs %>%
   #TRXPT_21B (DBP isoform2)
   rbind(tibble( gene_name = "TRXPT_21B", transcript_id = "DBP_iso2", strand = "-",
                 start_1 = 16934, start_2 = 16934, start_3 = 18684, end_1 = 18751,
-                end_2 = 18189, end_3 = 18751, region = "E2"))
+                end_2 = 18189, end_3 = 18751, region = "E2")) %>%
+  #TRXPT_21B (DBP isoform2)
+  rbind(tibble( gene_name = "TRXPT_25B", transcript_id = "100K", strand = "+",
[…]

### 2024-01-06 scripts/r/thev_splicing_fullMap.R

@@ -210,7 +210,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part){
                     )
   
   mlp_lab <- tribble(~x, ~xend, ~y, ~labb, ~ylabb,
-                     filter(combined_gtf, transcript_id == "TCONS_00000006") %>% pull(start_1), filter(combined_gtf, transcript_id == "TCONS_00000022") %>% pull(end_1), 44.5, "MLP", 46.5)
+                     filter(combined_gtf, transcript_id == "TCONS_00000006") %>% pull(start_1), filter(combined_gtf, transcript_id == "TCONS_00000022") %>% pull(end_1), 44.5, "MLTU", 46.5)
   
   
   # ========================================================

### 2024-01-17 manuscript_thev_transcriptome.Rmd
added more text to manuscript

@@
 ---
-title: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus
+title: Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus
 output:
@@
 
-Abraham Quaye^1\*^, Bret Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
+Abraham Quaye^1\*^, Brett Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
 
@@
 Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all vertebrates.
-Their double-stranded linear DNA genomes range between 26 and 45kb in size, producing a broad repertoire of transcripts via a highly complex alternative splicing pattern [@Davison2003; @Harrach2008].
+Their double-stranded linear DNA genomes range between 26 and 45kb in size, producing a broad repertoire of transcripts via highly complex alternative splicing patterns [@Davison2003; @Harrach2008].
 The AdV genome is one of the most optimally economized; both the forward and reverse DNA strands harbor protein-coding genes, making it highly gene-dense.
@@
 
-Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants and the THEV-V cause different clinical diseases in these birds [@Harrach2008; @Beach2006].
+Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants, with the THEV-V causing different clinical diseases in these birds [@Harrach2008; @Beach2006].
 In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967].
 HE is the most economically significant disease caused by any strain of THEV [@Beach2006].
-While the current vaccine strain (a THEV-A isolated from a pheasant, Virginia Avirulent Strain [VAS]) have proven effective at preventing HE in young turkey poults, it still retains the immunosuppressive ability.
+While the current vaccine strain (a THEV-A isolated from a pheasant, Virginia Avirulent Strain [VAS]) has proven effective at preventing HE in young turkey poults, it still retains the immunosuppressive ability.
 Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
@@
 However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
-A well-characterized transcriptome of THEV is required to enable the next leap forward in THEV research - experimentation with specific viral genes that may mediate IS.
+A well-characterized transcriptome of THEV is required to enable experimentation with specific viral genes that may mediate IS.
 
 Myriads of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
-However, a large preponderance of studies focus on MAdVs - specifically human AdVs - thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU or major late promoter [MLP]), which generates five families of late mRNAs (L1-L5).
+However, a large preponderance of studies focus on MAdVs --- specifically human AdVs.
+Thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
+MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU or major late promoter [MLP] region), which generates five families of late mRNAs (L1-L5) based on the polyadenylation site.
 An additional gene (UXP or U exon) is located on the reverse strand.
@@
 Then the intermediate early genes, IVa2 and pIX are expressed followed by the late genes [@Zhao2014; @Donovan2020; @Guimet2016].
+Noteworthily, the MLP shows basal transcriptional activity during early infection (before DNA replication), with a comparable efficiency to other early viral promoters, but reaches its maximal activity during late infection (after DNA replication).
+However, during early infection the repertoire of late transcripts from the MLP is restricted until late infection [@Guimet2016].
 MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs.
@@
 Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
-Thus, the MLTU produces a complex repertoire of mRNA with diverse 5' untranslated regions (UTRs) spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5).
-Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing of the genes encoded in the unit[@Zhao2014; @Donovan2020; @Guimet2016].
+Thus, the MLTU produces a complex repertoire of mRNA with diverse 5' untranslated regions (UTRs) spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5) based on polyadenylation site.
+Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing in the unit [@Zhao2014; @Donovan2020; @Guimet2016].
 During translation of AdV mRNA, recent studies strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020].
@@
 It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014].
-In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time, the transcriptome of THEV (VAS vaccine strain) during different phases of the infection, yielding the first THEV splicing map.
+In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time the transcriptome of THEV (VAS vaccine strain) during different phases of the infection, yielding the first THEV splicing map.
 Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
-The generated data from our paired-end sequencing experiment should thus be reliable.
 \newpage
@@
 Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*M.gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
+Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*M.
+gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
 A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
@@
 Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having coverage as high as `r max_junread72` reads.
-The substantial increases in splice junctions and mapping reads to the THEV genome over time denotes an active infection, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2b**).
-Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time-point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
-In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` transcripts all of which are novel, ~~and using 3' Rapid Amplification of cDNA Ends (3'RACE) and other methods, we further identified \#### unique splice variants~~.
+The substantial increases in splice junction and mapping reads to the THEV genome over time denotes an active infection, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2b**).
+
+Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
+In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` novel transcripts.
+~~and using 3' Rapid Amplification of cDNA Ends (3'RACE) and other methods, we further identified #### unique splice variants~~.
 Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (**Figure 3**).
+
+We validated the splice junctions in all transcripts by PCR amplification of viral cDNA, cloning, and Sanger sequencing (**Supplementary PCR methods**).
 The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under **accession no.
@@
 **Changes in THEV splicing profile over time**\
-AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU) or region.
-Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs [@Donovan2020; @Zhao2014].
-To evaluate the activity of each promoter over time, Firstly, `Ballgown`, a program for statistical analysis of assembled transcriptomes [@Ballgown] was used to estimate and normalize expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
+AdV gene expression occurs under exquisite temporal control with each promoter typically producing one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts.
+To evaluate the activity of each promoter over time, `StringTie` and `Ballgown` (a program for statistical analysis of assembled transcriptomes) [@Ballgown] were used to estimate and normalize expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
 Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
@@
 
-Individually, TRXPT_21 (DBP) - from the E2 region - was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
+Individually, TRXPT_21 (DBP) --- from the E2 region --- was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
 Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
-The later time points were dominated by the MLP region; transcripts TRXPT_10 and TRXPT_14 were most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (**Figure 4a**).
+The later time points were dominated by the MLP region --- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (**Figure 4a**).
 When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 h.p.i, after which the MLP region assumes predominance (**Figure 4b**).
-Secondly, we estimated relative abundances of all splice junctions for each time point using the raw reads.
-We counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads counted at the given time point.
-At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLP was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junctions reads.
-(**Table 2a**).
-The levels of the top most abundant junctions at 12 h.p.i were maintained also 24 h.p.i as the most significantly expressed.
+Secondly, we estimated relative abundances of all splice junctions at each time point using the raw reads.
+We counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads at the given time point.
+At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a**).
+The top most abundant junctions at 12 h.p.i remained the most significantly expressed at 24 h.p.i also.
 However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b**).
-At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (**Table 2c**.
+At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall --- accounting for `r round(most_sig_72, 1)`% of all junctions reads --- but also contained the most significantly expressed individual junctions (**Table 2c**.
 Also see **Supplementary Tables 1a-c**; **Figure 4c**).
-When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (**Figure 4d**).\
-Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
+When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (**Figure 4d**).
+We also analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
 We found that most splice donor-acceptor sequences were unsurprisingly the canonical GU-AG nucleotides.
@@
 Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (**Figure 5**).
-Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered.
-The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a 17.9 kilodalton (kDa) protein of 160 residues [amino acids (aa)].
-The CDS begins in the first exon, starting at position 211, spans the second exon, and terminates in the third exon at position 2312.
-From the 5'-most start codon (SSC), TRXPT_2 encodes the largest protein in this region - a 64.3 kDa, 580 aa protein with the same SSC as TRXPT_1 (position 211).
-This CDS spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 to 1964 (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of the Hyd STC.
+Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered as reported for other AdVs [@Donovan2020; @Zhao2014].
+The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a novel 17.9 kilodalton (kDa), 160 residue [amino acids (aa)] protein.
+From its 5'-most start codon (SSC), TRXPT_2 encodes the largest protein in this region --- a 64.3 kDa, 580 aa protein with the same SSC as TRXPT_1 (position 211bp).
+This CDS spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 to 1964bp (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of the Hyd's STC.
 However, it has an SSC 102 bp upstream and in-frame with ORF1's predicted SSC.
-TRXPT_2 CDS therefore, shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SSC of Hyd is not in-frame.
+Thus, the CDS of TRXPT_2 shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SSC of Hyd is not in-frame.
+Without its splice site removing the ORF1 STC, TRXPT_2 would encode a longer variant of ORF1, starting from an upstream SSC.
 TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-From our RNA-seq data, all E1 transcripts share the same transcription termination site (TTS; at position 2325bp); however, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (at position 54bp).
-Given that studies in MAdVs show that E1 mRNAs share not only a common TTS but also the TSS, and only differ from each other regarding the introns [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and their actual TSS just like the TTS are identical for all E1 transcripts.
+Our RNA-seq data shows that all E1 transcripts share the same transcription termination site (TTS; at position 2325bp); however, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (at position 54bp).
+Given that studies in MAdVs show that E1 mRNAs share not only a common TTS but also the TSS, and only differ from each other regarding the internal splicing [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and their actual TSS just like the TTS are identical for all E1 transcripts.
 Regardless of the TSS considered for TRXPT_3, the coding potential (CP) remains unaffected.
-Its 5'-most CDS, beginning at 1965 and sharing the same STC as TRXPT_1 and TRXPT_2, produces a 13.1 kDa, 115 residue protein.
-This CDS (ORF4) was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggests it is a bona fide ORF.
-The CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
-However, if we assume that TRXPT_4 shares the same TSS as TRXPT_1, then the 5'-most CDS is a distinct multi-exonic 15.9 kDa, 143 aa protein with the same SSC as TRXPT_1 and TRXPT_2 but with a unique STC.
-All splice junctions of the transcripts in this region (except the junction for TRXPT_4) have been validated by cloning and Sanger sequencing of cDNA (**Figure 5b**; **supplementary PCR methods**).
-Finally, during our validation of TRXPT_2, ORF1 was present on the agarose gel and Sanger sequencing results as a bona fide transcript (**supplementary PCR methods**).
-This is corroborated by 3'-RACE experiment, which shows transcripts spanning the entire ORF1 and Hyd ORFs without any splicing with a poly-A tail immediately after the TTS of transcripts in this region.
-The 5'-most CDS of this transcript would encode ORF1.
-However, the SSC of the predicted ORF1 is in-frame but downstream of TRXPT_2 SSC, suggesting that the predicted ORF1 CDS is a truncated ORF; it shares the same TSS, SSC, and TTS as TRXPT_2, but has a unique STC.
+Its 5'-most CDS, beginning at 1965bp and sharing the same STC as TRXPT_1 and TRXPT_2, produces a 13.1 kDa, 115 residue protein (ORF4).
+ORF4 was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggests it is a bona fide ORF.
+Unlike TRXPT_3, the CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
+However, if we assume that TRXPT_4 shares the same TSS as TRXPT_1, then the 5'-most CDS is a distinct, novel, multi-exonic 15.9 kDa, 143 aa protein with the same SSC as TRXPT_1 and TRXPT_2 but with a unique STC.
+The splice junctions of the transcripts in this region (except the junction for TRXPT_4) were validated by cloning of viral cDNA and Sanger sequencing (**Figure 5**; **Supplementary PCR methods**).
+During the validation of TRXPT_2, ORF1 was present on the agarose gel (an unspliced band size) and Sanger sequencing results as a bona fide transcript (**Supplementary PCR methods**).
+This was corroborated by our 3'RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without any splicing, with a poly-A tail immediately after the TTS of transcripts in this region.
+The 5'-most CDS of this transcript (TRXPT_2B) would encode ORF1.
+However, TRXPT_2B has an upstream and in-frame SSC to the predicted SSC of ORF1, suggesting that the predicted ORF1 CDS is truncated; it shares the same TSS, SSC, and TTS as TRXPT_2, but has a unique STC.
 
@@
 The E2 TU expressed on the anti-sense strand, is subdivided into E2A and E2B and encodes three classical AdV proteins essential for genome replication: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [@Donovan2020; @Zhao2014].
-Unlike MAdV where two promoters (E2-early and E2-late) were discovered [@Donovan2020], we discovered only a single promoter from which both E2A and E2B transcription is initiated.
+Unlike MAdV where two promoters (E2-early and E2-late) are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751bp) from which both E2A and E2B transcription is initiated.
 However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 6**).
@@
 The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from two exons.
-The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern exactly but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
-Thus a three-exon transcript with an identical encoded protein (DBP; 380 residues, 43.3 kDa).
+The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern precisely but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
+Thus, TRXPT_21 is a three-exon transcript encoding DBP (380 residues, 43.3 kDa) precisely as predicted.
 This transcript (TRXPT_21) was also corroborated in a 3'-RACE experiment.
@@
 Utilizing the SSC 173 bp downstream of TRXPT_21's SSC yields a 346 residue, 39.3 kDa product, which is in-frame of DBP but entirely contained in the second exon.
-TRXPT_21 and TRXPT_21B share a common TSS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 6**).
+TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 6**).
 
-The E2B region transcripts share the TSS of E2A - begins with E2-5'UTR - but extend thousands of base pairs downstream to reach the TTS at 2334bp in the IM region, which is immediately followed by an A-T rich sequence (position 2323-2339bp) where polyadenylation probably occurs.
-Interestingly, the TTS of the E1 region on the sense strand is in the immediate vicinity of this A-T rich sequence, and the A-T rich sequence is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
-The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four (**Figure 6**).
+The E2B region transcripts also start with the E2-5'UTR but extend thousands of base pairs downstream to reach the TTS at 2334bp in the IM region, which is immediately followed by an A-T rich sequence (position 2323-2339bp) where polyadenylation probably occurs.
+Interestingly, the TTS of the E1 region (position 2,325bp) on the sense strand is also in the immediate vicinity of this A-T rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
+The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 6**).
 TRXPT_7 has the CP for IVa2 and both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
-The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel 5' exons, the third exon (containing the SSC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
-The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC is utilized.
+The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel non-coding 5' exons, the third exon (containing the SSC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
+The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC of pTP is utilized.
 The encoded product is identical to the predicted pTP ORF (597 residues; 70.5 kDa).
-If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol ORF (1112 residues; 129.2 kDa).
-~~finish trxpt_7 and then discuss trxpt_6~~.
+If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol (polymerase) ORF (1112 residues; 129.2 kDa).
+TRXPT_6 differs from TRXPT_7 by containing an extra splice site at 3447-3515bp.
+However, the CP remains similar to that of TRXPT_7 except the Ad-pol encoded from the secSSC is a truncated isoform with a new STC resulting from the splice site.
+We also found a novel short transcript (TRXPT_15) entirely nested within the terminal exon of TRXPT_7 but with a unique splice site.
+This transcript is an incomplete construction from the mapped reads as it contains an incomplete CDS.
+However, we validated the this splice junction to be genuine (**Supplementary PCR methods**).
 
@@
 The promoter expressing this single transcript (TRXPT_5) is embedded in E2B region and shares a TTS with E2B transcripts [@Donovan2020; @Zhao2014].
-TRXPT_5 is a two-exon transcript located on the reverse strand spliced at 3447-3615.
+TRXPT_5 is a two-exon transcript spliced at 3447-3615bp exactly as the last intron of TRXPT_6.
 The first exon is an UTR, except the last 2 nucleotides, which connect with the first nucleotide of second exon to form the 5'-most SSC.
@@
 Regardless of the SSC considered, the encoded protein (IVa2) is largely unaffected.
-Except for the four extra residues at the N-terminus (considering the 5'-most SSC), the entire protein sequence is identical.
+Except for the four extra residues at the N-terminus (considering the 5'-most SSC), the entire protein sequence is identical to IVa2.
 
@@
 In MAdVs, this region contains seven ORFs expressed from several transcripts which share the same TSS (from the E3 promoter) but have different TTSs [@Guimet2016; @Donovan2020; @Zhao2014].
-However, some E3 transcripts use the MLP as their TSS.
-Due to sharing the same TSS, in MAdVs, secSSC usage is heavily relied on for gene expression in this region except for 12.5K and transcripts using the MLP as TSS, as utilizing only the first SSC cannot produce all the other transcripts in this TU [@Donovan2020].
+However, some E3 transcripts use the TSS of the MLP.
+Due to sharing the same TSS, in MAdVs, secSSC usage is heavily relied on for gene expression in this region except for 12.5K and transcripts using the MLP's TSS, as utilizing only the first SSC cannot produce all the other transcripts in this TU [@Donovan2020].
 
 In THEV, only one ORF (E3) was predicted in this region.
-However, we identified six transcripts here (`r paste0("TRXPT_", 22:27, collapse = ", ")`), all of which are novel (**Figure 7**).
-We identified two distinct TSSs - one similar to the classic MAdV E3 TSS (position 18,230bp) and the other about 500 bp downstream at 18,727bp.
-The E3 transcripts collectively have the CP for several THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU; however, some CDSs are nonidentical due to unpredicted splicing.
-For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered it to be a four-exon ORF expressed from TRXPT_24.
-The first two exons were not predicted but the last two, match the predicted exons precisely and the CDS is in-frame.
-However, the first 20bp of the predicted 33K (including the SSC) is spliced as as part of the second intron of TRXPT_24.
-Thus, the bona fide 33K is a 19.8 kDa, 171 residue protein spanning four exons.
-TRXPT_24 can also encode the ORFs, pVIII and E3 if we consider downstream SSC usage.
-TRXPT_22 and TRXPT_23 share the TSS of TRXPT_24 (E3 promoter; 18,230bp) but have distinct TTSs.
-Considering the first SSCs, they both encode novel 73 residue proteins that is over 80% similar but differ at the C-termini.
-Considering downstream SSC usage, both transcripts can encode pVIII and E3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+However, we identified six novel transcripts here (`r paste0("TRXPT_", 22:27, collapse = ", ")`) (**Figure 7**).
+We identified two distinct TSSs --- one similar to the classic MAdV E3 TSS (position 18,230bp) and the other about 500 bp downstream at 18,727bp.
+The E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU; however, some CDSs are nonidentical due to unpredicted splicing or the use of an upstream, in-frame SSC.
+For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered it to be a significantly longer four-exon ORF expressed from TRXPT_24.
+The first two exons of L33K were not predicted but the last two match the predicted exons and the CDS is in-frame.
+However, the first 20bp of the predicted 33K (including the SSC at 20,142bp) is spliced out as as part of the second intron of TRXPT_24.
+Thus, the bona fide 33K is a 19.8 kDa, 171 residue protein (L33K) spanning four exons instead of the predicted 120 aa protein.
+TRXPT_24 also has the CP for the ORFs, pVIII and E3 (a longer variant starting from and upstream, in-frame SSC) if we consider downstream SSC usage.
+Also, 22K (89 residues) is a single-exon ORF predicted to use the same SSC as 33K (20,142bp).
+However, just like 33K, all the transcripts in this region exclude the predicted SSC as part of their introns; hence 22K as predicted is not identical to any expressed ORF.
+TRXPT_29 has its SSC upstream of 22K's predicted SSC but is spliced to overlap a portion of 22K's CDS.
+However, the overlapping sequence is short and not in-frame of 22K.
+The 5'-most product of TRXPT_29 is a novel 73 residue protein (8.3aK) entirely different from 22K.
+TRXPT_23 being spliced identically as TRXPT_29 also encodes this novel 73 aa protein (8.3aK) from its first SSC.
+Similarly, TRXPT_22 also encodes a 73 aa novel protein (8.3bK) from its first SSC that shares over 80% similarity with 8.3aK, but it differs from 8.3aK at the C-terminus.
+Considering downstream SSC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and E3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair and they were differentiated from each other by cloning and Sanger sequencing.
+
+In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed another splice  variant undetected in our RNA-seq transcriptome.
+This was a three-exon transcript (TRXPT_30) with its first and last exons spliced identically as TRXPT_23, but which also has the second exon of TRXPT_24 (**Figure 7**).
+The first CDS on TRXPT_30 spans all three exons, with the STC in the terminal (third) exon, producing a novel 140 residue, 15.7kDa protein (L22K).
+Interestingly, the last 81 C-terminus residues are identical to 22K (89 residues); only the first 7 residues are lacking due to splicing.
+Hence, we may consider L22K as a long variant of the predicted 22K ORF.
+Albeit the TSS and TTS of TRXPT_30 was not seen, we presume that they are similar to TRXPT_23, in which case it would also have the downstream CP of TRXPT_23.
 TRXPT_25 is the largest transcript in the TU.
@@
 It also has the CP for pVIII and E3 in that order.
-Furthermore, during the validation of TRXPT_25's splice junction using primers that span the junction (18350-18717bp), we noticed a DNA band that corresponds to the full unspliced sequence (**supplementary PCR methods Table 1**).
-As TRXPT_25 only falls short of encoding the complete 100K protein due to its splice junction, this band (which we cloned and validated by Sanger sequencing) suggests that the predicted 100K is indeed expressed.
+Furthermore, during the validation of TRXPT_25's splice junction using primers that span its junction (18350-18717bp), we noticed a DNA band that corresponds to the full unspliced sequence (**Supplementary PCR methods**).
+As TRXPT_25 only falls short of encoding the complete predicted 100K protein due to its splice junction, this band (which we cloned and validated by Sanger sequencing) suggests that the predicted 100K is indeed expressed.
 This transcript (TRXPT_25B) although not seen in our RNA-seq data, likely shares the same TSS and TTS as TRXPT_25.
-Lastly, TRXPT_26 and TRXPT_27 share the same TSS, unique from the other transcripts in this region but have distinct TTSs.
-TRXPT_26 is a three-exon transcript but the first two are UTRs - only the terminal exon encodes proteins.
+Lastly, TRXPT_26 and TRXPT_27 share the same TSS, unique from the other transcripts in this region but with distinct TTSs.
+TRXPT_26 is a three-exon transcript but the first two are UTRs.
 It encodes pVIII as the 5'-most ORF and has the CP for E3 and Fiber in that order.
-TRXPT_27 on the other hand, is only a two-exon transcript but similarly, only the terminal exon contains the CDSs.
-It encodes Fiber as the 5'-most ORF and ORF7 downstream with secSSC usage.
-TRXPT_13, which seems to be an E3 transcript that uses the MLP as TSS is discussed under the MLTU transcripts.
+TRXPT_27 on the other hand, is only a two-exon transcript but similar to TRXPT_26, only the terminal exon contains the CDSs.
+It encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSSC usage.
+TRXPT_13, which seems to be an E3 transcript that uses the MLP TSS is discussed under the MLTU transcripts.
 
 **Early Region 4 (E4) transcripts**.
-This transcription unit (TU) is the found at the tail-end (3'-end) of the genome, on the reverse strand.
+This transcription unit (TU) is the found at the tail-end (3'-end) of the genome on the anti-sense strand.
 Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the same strand as ORF8 nor transcribed from a promoter in the E4 region, only ORF8 can legitimately be classified as a transcript in this TU.
-This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the reverse strand (**Figure 8**).
+This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the anti-sense strand (**Figure 8**).
 The transcript (TRXPT_28) spans 25192-26247 and is spliced at 25701-26055; hence, a two-exon transcript.
@@
 There is a SSC in the first exon at position 26246 (second nucleotide of the transcript).
-The encoded protein from this SSC is in-frame with the SSC of ORF8 in the second exon; hence, the C-terminus of this longer protein (26.4 kDa, 229 aa) would be the identical to the predicted ORF8 protein.
-~~The splice junction of TRXPT_28 was validated by cloning and Sanger sequencing of cDNA (**supplementary PCR methods**).~~
+The encoded protein from this SSC is in-frame with the predicted SSC of ORF8 in the second exon; hence, the bulk of this longer protein (26.4 kDa, 229 aa) is identical to the predicted ORF8 protein.
 
-**Major Late Transcription Unit (MLTU) or MLP Region transcripts**. \newpage
+**Major Late Transcription Unit (MLTU) or MLP Region transcripts**   
+The MLTU transcripts dominate the late phase (i.e, after DNA replication) of the AdV infectious cycle.
+The MLP produces all late mRNAs by alternative splicing and alternative polyadenylation of a primary transcript, which are grouped into five transcript classes (L1-L5).
+These late proteins primarily act as capsid proteins, promote virion assembly, and direct genome packaging [@Guimet2016; @Donovan2020; @Zhao2014].
+Similar to other AdVs, most of THEV's coding capacity falls within this TU.
+Specifically, about 13 out of the 23 predicted ORFs were assigned to this TU, some of which we have found to belong to the E3 TU instead.
+Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU.
+We identified the untranslated TPL at the 5' end of most transcripts in this region as expected.
+However, for three transcripts (`r paste0("TRXPT_", c(16:18), collapse = ", ")`), a different leader sequence (sTPL) is used: the first TPL exon is substituted for a unique first exon, found between the first and second TPL exons.
+Also, TRXPT_20 seems to include only the third TPL exon (**Figure 9**).
+
+We identified five TTSs (10,549bp, 12,709bp, 16,870bp, 17,891bp, 20,865bp) in this TU, corresponding to the five late mRNA classes (L1-L5), respectively, as found in all AdVs.
+L1 mRNAs include TRXPT_8, which comprises the TPL (non-coding) and the CDS-containing terminal exon.
+This transcript encodes the 52K ORF exactly as predicted with the SSC beginning from the first nucleotide of the terminal exon.
+L2 mRNAs include TRXPT_16, TRXPT_17, and TRXPT_18, all of which consist of the sTPL (also non-coding) followed by their respective terminal exons.
+TRXPT_16 encodes pIIIa exactly as predicted as the 5'-most ORF, and also has the CP for the ORFs, III and pVII in that order.
+TRXPT_17 encodes the ORF, III (penton), and TRXPT_18 encodes the ORF pVII exactly as predicted.
+The L3 mRNAs include TRXPT_14 and TRXPT_20, of which TRXPT_14 utilizes the full TPL whereas TRXPT_20 uses only the third TPL exon (ex3TPL).
+Both transcripts have the CP for the ORF, hexon (II) but hexon is the only ORF encoded on TRXPT_14, whereas the 5'-most ORF on TRXPT_20 is pX (pre-Mu) followed by pVI and hexon in that order.
+L4 mRNAs include TRXPT_9, TRXPT_10, TRXPT_11, and TRXPT_13 all of which begin with the TPL followed by three (TRXPT_9, TRXPT_10, and TRXPT_13) or four (TRXPT_11) coding exons.
+These are the largest transcripts found in the transcriptome, each one possessing the CP for several similar late proteins.
+Normally, MLTU transcripts encoding particular ORFs splice the TPL onto a splice site just upstream of the ORF to be expressed [@Donovan2020].
+While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as the L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSSC utility and ribosome shunting found in other AdVs for their translation [@Donovan2020; @Yueh1996].
+TRXPT_9 and TRXPT_10 are very similar but not identical.
+The last exon of TRXPT_9 seems to be truncated and probably shares the same TTS as the other L4 mRNAs.
+They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (Lprot) --- uses an in-frame, upstream SSC than predicted, and 14K (a novel unpredicted 120 aa protein).
+TRXTP_10 (and TRXPT_9 with the L4 TTS) also has the CP for pVIII and E3.
+TRXPT_11 is a seven-exon mRNA with hexon as it's 5'-most ORF but it also has the CP for Lprot, 14K, L33K, and also pVIII and E3 in that order.
+TRXPT_13 seems to be an E3 ORF utilizing the MLP TSS.
+It encodes pVIII and E3 in that order similar to TRXPT_22 but lacks TRXPT_22's novel first ORF.
+
+Lastly, the L5 class includes only TRXPT_12 which contains the TPL and a coding terminal exon.
+Its 5'-most ORF is fiber (IV) but it also has the CP for the THEV specific gene, ORF7.
+TRXPT_12's CP is identical TRXPT_27 of the the E3 TU albeit they differ in their 5'-UTRs.
+\newpage
 
@@
 
-In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene.
-However, later studies predicted and preferred Hyd instead of ORF4; hence, the current prediction map.
-However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
 For fig2a: There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection.
@@
 The TTSs were all in the context of A-T rich sequences; which presumably serve as polyA signals.
-All splice junctions were confirmed by cloning and Sanger sequencing of cDNA (**supplementary PCR methods**).
+All splice junctions were confirmed by cloning and Sanger sequencing of cDNA (**Supplementary PCR methods**).
+We did not find the x,y,z or i-leaders for MLP transcripts probably because THEV doesn't use it due to its smaller size
+The E3 ORF has an upstream, in-frame SSC.
 \newpage
@@
 However, these predicted splice junctions had not been experimentally validated hitherto, and we identified additional novel exons, giving the complete picture of these transcripts.
-The novel splice junctions in this work discovered in the assembled transcripts using the `StringTie` transcript assembler which we validated by PCR and Sanger Sequencing are shown in supplementary PCR methods Table 1.
-Briefly, we designed primers that crossed a range of novel exon--exon boundaries for each specific transcript in a transcription unit (TU) paired with their respective universal primers for the TU (\~\~supplementary PCR methods).
+The novel splice junctions in this work discovered in the assembled transcripts using the `StringTie` transcript assembler which we validated by PCR and Sanger Sequencing are shown in **Supplementary PCR methods**.
+Briefly, we designed primers that crossed a range of novel exon-exon boundaries for each specific transcript in a transcription unit (TU) paired with their respective universal primers for the TU.
 Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
@@
 We followed the protocol described by Green *et al* [@Green2019] with modifications.
-Briefly, 1ug of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter--primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
+Briefly, 1ug of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter-primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
 A gene-specific sense primer with a 5'-end KpnI restriction site paired with an anti-sense adapter-primer with a 5'-end BamHI site were used to amplify target sections of the cDNA using Invitrogen's Platinum™ Taq DNA polymerase High Fidelity, following manufacturer's instructions.
@@
 
-Analysis of our sequence reads were analyzed following a well established protocol described by Pertea *et al* [@Pertea2016], using `SNAKEMAKE 7.24.0` to drive the pipeline.
+Our sequence reads were analyzed following a well established protocol described by Pertea *et al* [@Pertea2016], using `Snakemake - version 7.24.0` [@Snakemake2021], a popular workflow management system to drive the pipeline.
 Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped to the complete sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings without relying on known splice sites.
-The generated `BAM` files from each infection time-point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `gff3` file from NCBI cont m.
-aining the predicted ORFs of THEV as a guide.
-A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the final transcriptome of THEV.
+Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings.
+The generated alignment (`BAM`) files from each infection time point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `GTF` file derived from a `gff3` file obtained from NCBI, which contains the predicted ORFs of THEV as a guide.
+A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the transcriptome of THEV.
+See **Supplementary Computational Analysis** for the details of transcript expression level estimations and splice junction read counts.
 \newpage
@@
 ### CODE AVAILABILITY
-
-All the code/scripts written for analysis of the data are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>) \newpage
+All the code/scripts written for analysis of the data are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>) 
+\newpage
 
@@
 
-`LC Sciences` - RNA sequencing was done here `Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here \newpage
+`LC Sciences` - RNA sequencing was done here   
+`Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here 
+\newpage
 
@@
 ## TABLES AND FIGURES
-
-![](results/r/figures/thev_orf_map.png)
-
-**Figure 1.
+![](results/r/figures/thev_orf_map.png) **Figure 1.
 *Genomic map of THEV avirulent strain annotated ORFs***.
@@
 Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.
-\newpage
 
 ![](results/r/figures/fig_2.png) 
-
 **Figure 2: Increasing levels of THEV over time.
@@
 Virus titers were a quantified with a qPCR assay.
-There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured.
+There is no discernible increase in virus titer up 12 h.p.i, after which a steady increase in virus titer is measured.
 The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i.
 GCN: genome copy number.
-
-\newpage
-
 ![](results/r/figures/figure3.png) 
-
 **Figure 3.
-a) Composite transcriptome of THEV from RNA-seq**.
+a) Transcriptome of THEV from RNA-seq**.
 THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map).
@@
 Transcripts are color coded as explained in **a**.
-\newpage
-
-![](results/r/figures/figure_4a_d.png) **Figure 4: Changes in splicing and expression profile of THEV over time.** **a)** Expression levels of transcripts over time.**b)** Expression levels of transcripts by region over time.**c)** Relative abundances of all splice junctions over time.
-**d)** Relative abundances of junctions in transcriptome.
-\newpage
+![](results/r/figures/figure_4a_d.png) 
+**Figure 4: Changes in splicing and expression profile of THEV over time.** **a)** _Normalized (FPKM) expression levels of transcripts over time_.
+The expression levels (FPKM) of individual transcripts as a percentage of the total expression of all transcripts at each time point are indicated.
+Only transcripts from our RNA-seq data are included here.
+**b)** _Normalized (FPKM) expression levels of transcripts by region over time_.
+The expression levels of each region/TU as a percentage of the total expression of all transcripts at each time point are indicated.
+Region expression levels were calculated by summing up the FPKMs of all transcripts categorized in that region.
+**c)** _Relative abundances of all splice junctions grouped by region/TU over time_.
+After assigning all `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique junctions to a TU and the total junction reads counted at each time point for each region, the total junction reads for each TU plotted as percentage of all junction reads at each time point is indicated.
+Note that the junction read counts are not normalized.
+**d)** _Relative abundances of junctions in transcriptome grouped by region/TU over time_.
+This is identical to **(c)**, except that only the junctions found in the full transcriptome obtained from the RNA-seq data were included.
 
@@
                              "strand", "4hpi", "12hpi", "24hpi", "72hpi",
-                             "status", "coding_potential")) %>%
+                             "status")) %>%
   theme_zebra() %>%
@@
                                splice_site = "Splice Donor-Acceptor",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status",
-                               coding_potential = "Coding Potential") %>%
+                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
   flextable::align(align = "center", part = "all") %>%
   add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 2)) %>%
-  flextable::vline(j = c(1, 5, 6, 10, 11), border = fp_border_default(color = "grey",
+                 colwidths = c(1, 4, 1, 4, 1)) %>%
+  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                   width = 1.5)) %>%
@@
 brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(2, 0.05, 2)) +
-  plot_annotation(tag_levels = "A") &
-  theme(plot.tag = element_text(size = 22, face = "bold"))
+  plot_layout(heights = c(2, 0.05, 2)) 
+#+
+  # plot_annotation(tag_levels = "A") &
+  # theme(plot.tag = element_text(size = 22, face = "bold"))
 ```
-
-**Figure 5: E1 region transcripts.
-a)** The splice map of the E1 transcription unit.
-Exons are depicted as boxes connected by introns (dotted lines).
-Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and the full ORF1 transcript and previously annotated ORF4 are colored black.
+**Figure 5: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
+Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and transcripts or ORFs discovered by other means are colored black.
 Each transcript or ORF is labelled with its name to the right.
 The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
-
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
 ```{r region-by-region_e2andim_figure, fig.height=16, fig.width=18, warning=FALSE}
@@
   flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
-                                                                  width = 1.5)) %>%
-  footnote(., i = 6, j = 12, value = as_paragraph(c("Incomplete transcript")),
-           ref_symbols = c("*"), part = "body")
+                                                                  width = 1.5))
 
@@
 ```
-
-**Figure 6: E2 and IM region transcripts.
-a)** The splice map of the E2 and IM transcription units.
+**Figure 6: The splice map of the E2 and IM TUs**.
 Exons are depicted as boxes connected by introns (dotted lines).
 Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
+TRXPT_21B discovered by 3'RACE is colored black.
 Each transcript or ORF is labelled with its name to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+The SSC and STC of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
 
@@
 brkdwn_e3_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.05, 1))
+  plot_layout(heights = c(1.5, 0.05, 1))
 ```
-**Figure 7: E3 transcripts.
-a)** The splice map of the E3 transcription unit.
-Exons are depicted as boxes connected by introns (dotted lines).
+**Figure 7: The splice map of the E3 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
+Transcripts discovered by other means are colored black.
 Each transcript or ORF is labelled with its name to the right.
 The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junctions are indicated with information about their validation status using cloning and Sanger sequencing.
+Similarly, the secondary SSC (secSSC) and secondary STC (secSTC) are shown.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
 
@@
 ```
-
-**Figure 8: E4 region transcripts.
-a)** The splice map of the E4 transcription unit.
-Exons are depicted as boxes connected by introns (dotted lines).
+**Figure 8: The splice map of the E4 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 The transcript from RNA-seq data is colored red and the predicted ORF, grey.
@@
 The start codon (SSC) and stop codon (STC) of the 5'-most CDS is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference **b)** The sequence reads covering the splice junction are indicated.
-
-```{r region-by-region_im_figure, fig.height=5, fig.width=10, warning=FALSE, include=FALSE}
-reg_im_brkdown <- reg_im_brkdown %>%
-  mutate(trxpt_id = "TRXPT_5")
-
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_im_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Donor-Acceptor",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5))
-
-brkdwn_im_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.01, 1)) +
-  plot_annotation(tag_levels = "A") &
-  theme(plot.tag = element_text(size = 18, face = "bold"))
-
-```
-
-<!-- **Figure 9 IM region transcripts. a)** The splice map of the IM transcription unit. **b)** The sequence reads covering the splice junction are indicated. -->
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
+The table shows sequence reads covering the splice junction with its validation status using cloning and Sanger sequencing.
 
@@
 brkdwn_mlp_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.02, 1.2))
+  plot_layout(heights = c(2.5, 0.02, 1.2))
 ```
-
-**Figure 9: MLTU transcripts. a)** \newpage
+**Figure 9: The splice map of the MLTU.** Exons are depicted as boxes connected by introns (dotted lines).
+The transcripts from our RNA-seq data are colored red and the predicted ORFs, grey.
+The transcripts and ORFs are labelled with their names to the right.
+The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+Similarly, the secondary SSC (secSSC) and secondary STC (secSTC) are shown.
+The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
+\newpage
 
@@
 flextable(tab1) %>% theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed", width = 0.95,
-                       opts_pdf = list(caption_repeat = F)) %>%
   flextable::font(part = "all", fontname = "Avenir") %>%
@@
               style = "Table Caption") %>%
-  flextable::bold(part = "body", j = ~ Metric)
+  flextable::bold(part = "body", j = ~ Metric) %>%
+  flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = F),
+                       opts_word = list(split = F,
+                                        keep_with_next = T))
 
@@
 set_flextable_defaults(font.size = 8)
-flextable(sig_12_juncs) %>% theme_zebra() %>%
+top_juncs_tp <- function(tab, title){
+  tab %>% 
+    select(-c(`Splice \n Acceptor-Donor`, Reads)) %>% 
+    dplyr::rename("Reads (Percentage)" = Reads_Percentage) %>% 
+    flextable() %>%
+    theme_zebra() %>%
     flextable::set_table_properties(layout = "fixed", width = 1,
@@
     flextable::font(part = "all", fontname = "Avenir") %>%
-  flextable::set_caption("Table 2a: Most abundant splice junctions at 12h.p.i",
+    flextable::set_caption(title,
                 style = "Table Caption") %>%
@@
     flextable::width(., width = 0.7) %>%
-  flextable::width(., j = ~ Reads_Percentage, width = 1)
+    flextable::width(., j = ~ `Reads (Percentage)`, width = 1.2) %>%
+    flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = F),
+                       opts_word = list(split = F,
+                                        keep_with_next = T))
+}
+title12 <- "Table 2a: Most abundant splice junctions at 12h.p.i"
+top_juncs_tp(sig_12_juncs, title12)
 ```
@@
 set_flextable_defaults(font.size = 8)
-flextable(sig_24_juncs) %>% theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed", width = 1,
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::font(part = "all", fontname = "Avenir") %>%
-  flextable::set_caption("Table 2b: Most abundant splice junctions at 24h.p.i",
-              style = "Table Caption") %>%
-  flextable::align(align = "center", part = "all") %>%
-  flextable::width(., width = 0.7) %>%
-  flextable::width(., j = ~ Reads_Percentage, width = 1)
+title24 <- "Table 2b: Most abundant splice junctions at 24h.p.i"
+top_juncs_tp(sig_24_juncs, title24)
 ```
@@
 set_flextable_defaults(font.size = 8)
-flextable(sig_72_juncs) %>% theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed", width = 1,
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::font(part = "all", fontname = "Avenir") %>%
-  flextable::set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
-              style = "Table Caption") %>%
-  flextable::align(align = "center", part = "all") %>%
-  flextable::width(., width = 0.7) %>%
-  flextable::width(., j = ~ Reads_Percentage, width = 1)
+title72 <- "Table 2c: Most abundant splice junctions at 72h.p.i"
+top_juncs_tp(sig_72_juncs, title72)
 ```

### 2024-01-17 supplementary_thev_trxptome.Rmd
added more text to manuscript

@@
 title: "Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus"
-output: pdf_document
+output:
+  word_document: default
+  pdf_document: default
 geometry: margin=1in
@@
   - \linenumbers
+  - \usepackage{textcomp}
 editor_options:
@@
 ```{r Sup Table 1A}
-flextable(tp_reg_expr_12) %>% theme_zebra()
+set_flextable_defaults(font.size = 8)
+make_reg_stats_table <- function(tp_table){
+  return(tp_table %>%
+    select(-junc_freq) %>% 
+    flextable() %>% 
+    theme_zebra() %>% 
+    set_header_labels(timepoint = "Time", region = "Region", strand = "Strand",
+                      sum_reads_reg = "Total Reads", perc_reg = "Percentage") %>% 
+    flextable::width(width = 0.8) %>% 
+    flextable::align(align = "center", part = "all") %>%
+    flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = FALSE),
+                       opts_word = list(split = F))
+  )
+}
+make_reg_stats_table(tp_reg_expr_12) %>%
+  set_caption("Table 1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")
+
 ```
@@
 ```{r Sup Table 1B}
-flextable(tp_reg_expr_24) %>% theme_zebra()
+set_flextable_defaults(font.size = 8)
+make_reg_stats_table(tp_reg_expr_24) %>%
+  set_caption("Table 1b: Most Transcriptionally Active Regions of THEV at 24h.p.i")
 ```
@@
 ```{r Sup Table 1C}
-flextable(tp_reg_expr_72) %>% theme_zebra()
+set_flextable_defaults(font.size = 8)
+make_reg_stats_table(tp_reg_expr_72) %>%
+  set_caption("Table 1c: Most Transcriptionally Active Regions of THEV at 72h.p.i")
 ```
@@
 
-flextable(supp_pcr_meth_tab) %>%
+supp_pcr_meth_tab %>% 
+  select(-valid_status) %>% 
+flextable() %>%
   theme_zebra() %>%
-  flextable::fontsize(j = c("forwardP", "reverseP"), size = 3) %>%
+  set_header_labels(trxpt_id = "Transcript ID", region = "Region", num_exons = "Number of Exons",
+                    full_trxpt = "Full Transcript", exon1 = "Exon 1", exon2 = "Exon 2",
+                    exon3 = "Exon 3", exon4 = "Exon 4", exon5 = "Exon 5", exon6 = "Exon 6",
+                    exon7 = "Exon 7", forwardP = "Forward Primer", reverseP = "Reverse Primer",
+                    gel_image = "Agarose Gel") %>% 
+  flextable::fontsize(j = c("full_trxpt", "exon1", "exon2", "exon3",
+                            "exon4", "exon5", "exon6", "exon7",
+                            "forwardP", "reverseP"), size = 3) %>%
   flextable::align(align = "center", part = "all") %>%
   flextable::width(., width = 0.35) %>% 
-  colformat_image(j = "gel_image", i = c(1:3, 6:16), na_str = "-",
-                  width = 1, height = 1) %>%
-  flextable::width(j = ~forwardP, width = 1) %>%
-  flextable::width(j = ~reverseP, width = 1) %>%
-  # flextable::width(j = ~valid_status, width = 0.35) %>%
-  flextable::width(j = ~gel_image, width = 1) %>% 
-  footnote(., i = c(1:4, 6:16), j = 12, value = as_paragraph(c("Primer binds exon 1")),
-           ref_symbols = c("a"), part = "body") %>%
-  footnote(., i = c(1:4, 6:16), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
-           ref_symbols = c("b"), part = "body")
+  colformat_image(j = "gel_image", i = c(1:3, 5:25, 27:29),
+                  width = 1.1, height = 1) %>%
+  flextable::width(j = ~forwardP, width = 1.1) %>%
+  flextable::width(j = ~reverseP, width = 1.1) %>%
+  flextable::width(j = ~gel_image, width = 1.15) %>%
+  # flextable::height(height = 0, part = "header") %>% 
+  footnote(., i = c(1:17, 18:29), j = 12, value = as_paragraph(c("Primer binds inside first exon")),
+           ref_symbols = c("a"), part = "body", inline = T) %>%
+  footnote(., i = c(1:7, 9:17, 20:28), j = 13, value = as_paragraph(c("Primer binds inside terminal exon")), ref_symbols = c("b"), part = "body", inline  = T) %>% 
+  # transcripts too long to validate with one primer pair
+  footnote(., i = c(8,18,19,29), j = 13, value = as_paragraph(c("Primer binds inside fourth exon")),
+           ref_symbols = c("c"), part = "body", inline = T) %>% 
+  footnote(., i = c(8), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_6 due to identical splicing")), ref_symbols = c("I"), part = "body", inline = T) %>%
+  footnote(., i = c(9), j = 14, value = as_paragraph(c("Agarose gel identical to last 3 exons of TRXPT_10 due to identical splicing")), ref_symbols = c("II"), part = "body", inline = T) %>%
+  footnote(., i = c(11), j = 14, value = as_paragraph(c("Agarose gel identical to last 4 exons of TRXPT_11 due to identical splicing")), ref_symbols = c("III"), part = "body", inline = T) %>% 
+  footnote(., i = c(15), j = 14, value = as_paragraph(c("Agarose gel dentical to TRXPT_23 due to identical splicing")), ref_symbols = c("IV"), part = "body", inline = T) %>% 
+  footnote(., i = c(18), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_9 due to identical splicing")), ref_symbols = c("V"), part = "body", inline = T) %>% 
+  footnote(., i = c(19), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_14 due to identical splicing")), ref_symbols = c("VI"), part = "body", inline = T) %>%
+  flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = F),
+                       opts_word = list(split = F)) %>%
+  set_caption("Table 1: Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
 ```
+
+In the table above, the restriction sites in the primer tails are shown in lowercase letters.
+All the primer melting temperatures (TMs) are 58-60\textdegree C using a hot start Taq DNA polymerase.
+The PCR reaction mix was done per manufacturer's instructions.
+The PCR cycling conditions were as follows: Initial denaturation -- 95$^{\circ}$C for 1 minute; cyclical denaturation -- 95$^{\circ}$C for 30 seconds, annealing -- variable temperature (at least 53$^{\circ}$C) for 30 seconds, primer extension -- 68$^{\circ}$C for variable time, and final elongation -- 68$^{\circ}$C for 5 minutes.
+We used 35 cycles of amplification.
+
+## Supplementary Computational Analysis   
+Our trimmed RNA-seq reads were mapped to the genome of _M.
+gallopavo_ (with THEV's genome as one of its chromosomes) using `Hisat2` to generate the alignment (BAM) files and `StringTie` used to assemble the transcriptome with a `GTF` file containing the predicted THEV ORFs as a guide.
+`StringTie` was also used to estimate the normalized expression levels (FPKM) of all the transcripts and `Ballgown` was used to perform statistical analysis and comparisons of the transcript expression levels, which instructive in understanding the temporal regulation THEV genes.
+We used `RegTools` to extract and analyze the splice junctions in the BAM files.
+The command `regtools junctions extract` provides a wealth of information about all the splice sites in the BAM file provided such as: the start and end positions, the strand, and number of reads supporting the splice junctions.
+The command `regtools junctions annotate` gives even more information such as: the splice site donor-acceptor sequences and transcripts/genes that overlap the junction.
+These information was the basis for estimating and comparing the splicing activity of different regions (TUs) of THEV over time.
+
+The entire analysis pipeline was managed with `Snakemake`, from which we generate the below diagram of the major steps of the analysis pipeline.  
+![](project_map.png)

### 2024-01-17 scripts/r/abundance_analyses.R

@@ -428,7 +428,7 @@ reg_e1_brkdown <- reg_brkdown_tab("E1") %>%
 # E2 region table analysis for discussion
 reg_e2_brkdown <- reg_brkdown_tab("E2") %>%
   distinct(start, end, intron_len, .keep_all = T) %>% 
-  mutate(status = c(rep("Validated", 5), "Unvalidated"))
+  mutate(status = c(rep("Validated", 6)))
 
 # E3 region table analysis for discussion
 reg_e3_brkdown <- reg_brkdown_tab("E3") %>%

### 2024-01-17 scripts/r/plot_abundances.R

@@ -107,48 +107,48 @@ ss <- bulk_trxptome_ss_seq %>%
         )
 
 # All acceptors and donors
-all_ss_seq <- bulk_junc_stats %>%
-  distinct(timepoint, start, end, .keep_all = T) %>%
-  mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>% 
-  group_by(timepoint, splice_site) %>%
-  reframe(tally = n(),
-          total_reads = sum(read_count)) %>%
-  split(.$timepoint) %>%
-  map(mutate, tot_tally_tp = sum(tally)) %>% 
-  do.call("rbind", .) %>%
-  mutate(percent_abund = (tally / tot_tally_tp) * 100) %>% 
-  ggplot(aes(splice_site, percent_abund, group = timepoint, color = timepoint)) +
-  geom_point(show.legend = F, size = 10) +
-  geom_segment(aes(x = splice_site, xend = splice_site,
-                   y = 0, yend = percent_abund),
-               linewidth = 2,
-               show.legend = F) +
-  geom_text(aes(label = glue("{round(percent_abund, 1)}%")),
-            nudge_y = 4.5,
-            size = 5, fontface = "bold", color = "#000000") +
-  facet_wrap(~ timepoint, scales = "free") +
-  labs(x = "Splice Site Donor-Acceptor",
-       y = "Frequency") +
-  scale_color_lancet() +
-  scale_y_continuous(expand = c(0.01,0.01),
-                     limits = c(0, 105),
-                     labels = scales::label_percent(scale = 1)) +
-  scale_x_discrete(expand = c(0.05, 0.05)) +
-  coord_cartesian(clip = "off") +
-  theme_classic() +
-  theme(plot.margin = margin(rep(30, 4)),
-        panel.grid.major.y = element_line(linewidth = 0.4, color = "grey",
-                                          linetype = "dashed"),
-        axis.title = element_text(size = 16, face = "bold", margin = margin(r = 15, t = 15)),
-        axis.text.x = element_text(size = 16, face = "bold"),
-        axis.text.y = element_text(size = 14, face = "bold"),
-        axis.line = element_line(color = "grey40"),
-        axis.ticks.length = unit(0, "pt"),
-        strip.background = element_rect(linewidth = 0.1, fill = "grey"),
-        strip.text.x = element_text(size = 12, face = "bold", margin = margin(0.2,0,0.2,0, "cm")),
[…]

### 2024-01-17 scripts/r/plot_thev_timepoint_splicing.R

@@ -80,10 +80,14 @@ graph_trxpts <- function(gtf){
   
   # add y-axis positions to postive strand E3 transcripts
   ypos_pos_e3 <- merged_gtf %>% filter(strand == "+" & region == "E3")
-  ypos_pos_e3$ypos <- case_when(catch_timepoint == "4hpi" ~ rep(ypos_vals, length.out = nrow(ypos_pos_e3)),
-                                catch_timepoint == "12hpi" ~ rep(c(27:32), length.out = nrow(ypos_pos_e3)),
-                                catch_timepoint == "24hpi" ~ rep(ypos_vals, length.out = nrow(ypos_pos_e3)),
-                                catch_timepoint == "72hpi" ~ rep(c(31:40), length.out = nrow(ypos_pos_e3))
+  ypos_pos_e3$ypos <- case_when(catch_timepoint == "4hpi" ~ rep(ypos_vals,
+                                                                length.out = nrow(ypos_pos_e3)),
+                                catch_timepoint == "12hpi" ~ rep(c(27:32),
+                                                                 length.out = nrow(ypos_pos_e3)),
+                                catch_timepoint == "24hpi" ~ rep(ypos_vals,
+                                                                 length.out = nrow(ypos_pos_e3)),
+                                catch_timepoint == "72hpi" ~ rep(c(31:40),
+                                                                 length.out = nrow(ypos_pos_e3))
                                 )
   
   # add y-axis positions to negative strand transcripts

### 2024-01-17 scripts/r/reg_by_reg_plots.R

@@ -37,7 +37,12 @@ spliced_gtf <- spliced_gtf %>%
   arrange(start_1, end_1) %>%
   mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1)),
          transcript_id = factor(transcript_id, levels = trxpt_order)) %>%
-  arrange(transcript_id)
+  arrange(transcript_id) %>%
+  rbind(tibble(transcript_id = "TCONS_00000029", strand = "+", start_1 = 18230, start_2 = 18230,
+               start_3 = 20162, start_4 = NA, start_5 = NA, start_6 = NA, start_7 = NA, start_8 = NA,
+               end_1 = 20732, end_2 = 18350, end_3 = 20732, end_4 = NA, end_5 = NA, end_6 = NA,
+               end_7 = NA, end_8 = NA, region = "E3", trxpt_id = "TRXPT_29"))
+
 
 # trxpt id and names info
 
@@ -68,18 +73,55 @@ raw_data <- ballgown(dataDir = "results/ballgown",
 t_exp_levels <- texpr(raw_data, meas = "all") %>%
   as_tibble() %>%
   mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1))) %>%
-  select(trxpt_id, t_name, num_exons)
+  select(trxpt_id, t_name, num_exons) %>%
+  rbind(tibble(trxpt_id = "TRXPT_29", t_name = "22K", num_exons = 2)) 
+
 
 comp_spliced_gtf <- left_join(spliced_gtf, t_exp_levels,
                               by = "trxpt_id") %>%
-  mutate(sstcodon = c(rep(211, 3), 1965, 
+  mutate(sstcodon = c(# E1
+                      rep(211, 3), 1965, 
+                      # E3
                       rep(18230, 4), 20769, 22519,
-                      rep(NA, 12), 18186, NA, 10995, NA, 26246, 3616),
-         stpcodon = c(2312, 1953, rep(2312, 2), 
+                      # MLP
+                      NA, 8570, 20769, 13610, 12712, 12347, 12347, 13610, 22519,
+                      9462, 11001, 12347,
+                      # E2
+                      18186, 10995, 10995, NA, 
+                      # E4
+                      26246, 
+                      # IM
+                      3616, 
+                      # trxpt_29
+                      18230),
+         stpcodon = c(# E1 
+                      2312, 1953, rep(2312, 2), 
+                      # E3
[…]

### 2024-01-17 scripts/r/thev_splicing_fullMap.R

@@ -35,7 +35,12 @@ spliced_gtf <- spliced_gtf %>%
   arrange(start_1, end_1) %>%
   mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1)),
          transcript_id = factor(transcript_id, levels = trxpt_order)) %>%
-  arrange(transcript_id)
+  arrange(transcript_id) %>%
+  rbind(tibble(transcript_id = "TCONS_00000029", strand = "+", start_1 = 18230, start_2 = 18230,
+               start_3 = 20162, start_4 = NA, start_5 = NA, start_6 = NA, start_7 = NA, start_8 = NA,
+               end_1 = 20732, end_2 = 18350, end_3 = 20732, end_4 = NA, end_5 = NA, end_6 = NA,
+               end_7 = NA, end_8 = NA, region = "E3", trxpt_id = "TRXPT_29"))
+
 # trxpt id and names info
 
 exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
@@ -65,7 +70,8 @@ raw_data <- ballgown(dataDir = "results/ballgown",
 t_exp_levels <- texpr(raw_data, meas = "all") %>%
   as_tibble() %>%
   mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1))) %>%
-  select(trxpt_id, t_name, num_exons)
+  select(trxpt_id, t_name, num_exons) %>%
+  rbind(tibble(trxpt_id = "TRXPT_29", t_name = "22K", num_exons = 2)) 
 
 comp_spliced_gtf <- left_join(spliced_gtf, t_exp_levels,
                               by = "trxpt_id")
@@ -152,7 +158,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part){
   
   # recreate full dataframe with y-axis positions
   combined_gtf <- rbind(ypos_pos_e1, ypos_pos_mlp, ypos_pos_e3,
-                        ypos_e4, ypos_e2, ypos_im, ypos_uxp) %>% 
+                        ypos_e4, ypos_e2, ypos_im, ypos_uxp) %>%
     mutate(color = case_when(region == "E1" ~ "#ff0000",
                              region == "E2" ~ "#000000",
                              region == "E3" ~ "grey50",
@@ -206,7 +212,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part){
                          16972, 18186, 17.5, "E2A", 17
                          )
[…]

### 2024-01-24 manuscript_thev_transcriptome.Rmd
added Sanger seq data for trxpt_31 which encodes AdPol, also added gel
added files to submit to GEO

updated plots to include new transcript

@@
 tot_jun_4 <- tab1$`4h.p.i`[5]
-tot_jun_72 <- tab1$`72h.p.i`[5]
+tot_jun_72 <- as.character(tab1$`72h.p.i`[5])
 mean_juncreads_4 <- tab1$`4h.p.i`[7]
@@
 
-most_sig_24 <- bulk_junc_stats %>% filter(timepoint == "24hpi", region == "MLP") %>% pull(read_count) %>% sum()/as.numeric(tab1$`24h.p.i`[6])*100
+most_sig_24 <- bulk_junc_stats %>% filter(timepoint == "24hpi", region == "MLP") %>% pull(read_count) %>% sum()/as.numeric(str_remove(tab1$`24h.p.i`[6], ","))*100
 
@@
 
-**Background:** Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by *immunosuppression (IS)* and bloody diarrhea.
-This disease is caused by *Turkey Hemorrhagic Enteritis Virus (THEV)* of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
+Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by immunosuppression (IS) and bloody diarrhea.
+This disease is caused by *Turkey Hemorrhagic Enteritis Virus* (THEV) of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
 The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
-*Our objective is to understand the genetic basis by which VAS induces IS*.
-The *transcriptome of THEV* was studied to set the stage for further experimentation with specific viral genes that may mediate IS.\
-**Methods:** After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
+We have performed the first RNA-sequencing experiment characterizing THEV’s transcriptome, yielding the most detailed insight into THEV gene expression, to set the stage for further experimentation with specific viral genes that may mediate IS.
+After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
 Total RNA was subsequently extracted, and poly-A-tailed mRNA sequencing done.
-After trimming the raw sequencing reads with the `FastQC`, reads were mapped to the THEV genome using `Hisat2` and transcripts assembled with `StringTie`.
-An in-house script was used to consolidate transcripts from all time-points, generating the final transcriptome.
-PCR, gel electrophoresis, and Sanger sequencing were used to validate all identified splice junctions.
+After trimming the raw sequencing reads with the `Trim-galore`, reads were mapped to the THEV genome using `Hisat2` and transcripts assembled with `StringTie`.
+We identified 29 transcripts from our RNA-seq data all of which consisted of novel exons albeit some exons matched the predicted ORFs.
+The three predicted splice junctions were also corroborated in our data.
+We performed PCR amplification of THEV cDNA, cloned the PCR products, and Sanger sequencing was used to validate all identified splice junctions.
+During validation, we identified 5 additional transcripts some of which were further validated by 3'RACE data.
+Thus, the transcriptome of THEV consists of 34 unique transcripts with the coding capacity for all predicted ORFs.
+However, we found 8 predicted ORFs to be incomplete as either an upstream, in-frame start codon was identified or additional coding exons were found, making the actual expressed versions of these ORFs longer.
+We also identified 7 novel unpredicted ORFs that could be encoded by some transcripts; albeit it is beyond the scope of this manuscript to investigate whether they are indeed expressed.
+In keeping with all Adenoviruses, our data shows that all THEV transcripts are spliced, and organized in transcription units under the control of their cognate promoter.
 \newpage
@@
 Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
-The induced IS also interferes with vaccination schemes for other infections of turkeys [@Beach2006; @Rautenschlein2000].
 To eliminate this immunossupressive side-effect of the vaccine, a thorough investigation of the culprit viral factors (genes) mediating this phenomenon is essential.
@@
 Myriads of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
-However, a large preponderance of studies focus on MAdVs --- specifically human AdVs.
+However, a large preponderance of studies focus on MAdVs -- specifically human AdVs.
 Thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
@@
 An additional gene (UXP or U exon) is located on the reverse strand.
-The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins.
+The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins that act as capsid proteins, promote virion assembly, and direct genome packaging.
 The immediate early gene E1A is expressed first, followed by the the delayed early genes, E1B, E2, E3 and E4.
@@
 All but the pIX mRNA undergo at least one splicing event.
-The MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
+For instance, the MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
 There is also an alternate 5' three non-coding exons present in varying amounts on a subset of MLTU mRNAs (known as the x-, y- and z-leaders).
@@
 Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing in the unit [@Zhao2014; @Donovan2020; @Guimet2016].
+The promoters are activated at different phases of the infection by proteins from previously activated TUs.
+Paradoxically, the early-to-late phase transition during infection requires the L4 genes, 22K and 33K, which should only be available after the transition.
+However, a promoter in the L4 region (L4P) that directs the expression of these two proteins independent of the MLP was found, resolving the paradox [@Morris2010; @Guimet2016; @Donovan2020].
 During translation of AdV mRNA, recent studies strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020].
@@
 
-**Overview of sequencing data and analysis pipeline outputs**\
+**Overview of sequencing data and analysis pipeline outputs**  
 A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
 Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*M.
-gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
+Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*Meleagris gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
 A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
@@
 In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` novel transcripts.
-~~and using 3' Rapid Amplification of cDNA Ends (3'RACE) and other methods, we further identified #### unique splice variants~~.
 Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (**Figure 3**).
@@
 We validated the splice junctions in all transcripts by PCR amplification of viral cDNA, cloning, and Sanger sequencing (**Supplementary PCR methods**).
+During validation, we identified 5 additional transcripts some of which were further validated by 3' Rapid Amplification of cDNA Ends (3'RACE) data.
 The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under **accession no.
@@
 AdV gene expression occurs under exquisite temporal control with each promoter typically producing one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts.
-To evaluate the activity of each promoter over time, `StringTie` and `Ballgown` (a program for statistical analysis of assembled transcriptomes) [@Ballgown] were used to estimate and normalize expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
+To evaluate the activity of each promoter over time, `StringTie` and `Ballgown` (a program for statistical analysis of assembled transcriptomes) [@Ballgown] were used to estimate the normalized expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
 Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
@@
 
-Individually, TRXPT_21 (DBP) --- from the E2 region --- was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
+Individually, TRXPT_21 (DBP) -- from the E2 region -- was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
 Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
-The later time points were dominated by the MLP region --- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (**Figure 4a**).
+The later time points were dominated by the MLP region transcripts -- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (**Figure 4a**).
 When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 h.p.i, after which the MLP region assumes predominance (**Figure 4b**).
 Secondly, we estimated relative abundances of all splice junctions at each time point using the raw reads.
-We counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads at the given time point.
-At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a**).
+For individual junctions, we counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads at the given time point.
+At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table 1a**).
 The top most abundant junctions at 12 h.p.i remained the most significantly expressed at 24 h.p.i also.
-However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b**).
-At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall --- accounting for `r round(most_sig_72, 1)`% of all junctions reads --- but also contained the most significantly expressed individual junctions (**Table 2c**.
-Also see **Supplementary Tables 1a-c**; **Figure 4c**).
+However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table 1b**).
+At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall -- accounting for `r round(most_sig_72, 1)`% of all junction reads, -- but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table 1c** and **Figure 4c**).
 When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (**Figure 4d**).
+
 We also analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
@@
 After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
+
 Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (**Figure 5**).
-Most of the encoded proteins of the novel transcripts are distinct from the predicted ORFs, although they all have the potential to encode the predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered as reported for other AdVs [@Donovan2020; @Zhao2014].
-The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a novel 17.9 kilodalton (kDa), 160 residue [amino acids (aa)] protein.
-From its 5'-most start codon (SSC), TRXPT_2 encodes the largest protein in this region --- a 64.3 kDa, 580 aa protein with the same SSC as TRXPT_1 (position 211bp).
-This CDS spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 to 1964bp (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of the Hyd's STC.
+Most of the ORFs of the novel transcripts are distinct from the predicted ORFs, but they all have the coding potential (CP) for the predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered as reported for other AdVs [@Donovan2020; @Zhao2014].
+The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a novel 17.9 kilodalton (kDa), 160 residue [amino acids (aa)] protein (ORF9).
+From its 5'-most start codon (SSC), TRXPT_2 encodes the largest protein in this region -- a 64.3 kDa, 580 aa protein (ORF10) with the same SSC as ORF9 (position 211bp).
+ORF10 spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655bp to 1964bp (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of Hyd's STC.
 However, it has an SSC 102 bp upstream and in-frame with ORF1's predicted SSC.
-Thus, the CDS of TRXPT_2 shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SSC of Hyd is not in-frame.
+Thus, ORF10 shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SSC of Hyd is not in-frame.
 Without its splice site removing the ORF1 STC, TRXPT_2 would encode a longer variant of ORF1, starting from an upstream SSC.
 TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-Our RNA-seq data shows that all E1 transcripts share the same transcription termination site (TTS; at position 2325bp); however, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (at position 54bp).
+Our RNA-seq data shows that all E1 transcripts share the same transcription termination site (TTS; at position 2325bp).
+However, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (E1 TSS; position: 54bp).
 Given that studies in MAdVs show that E1 mRNAs share not only a common TTS but also the TSS, and only differ from each other regarding the internal splicing [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and their actual TSS just like the TTS are identical for all E1 transcripts.
 Regardless of the TSS considered for TRXPT_3, the coding potential (CP) remains unaffected.
-Its 5'-most CDS, beginning at 1965bp and sharing the same STC as TRXPT_1 and TRXPT_2, produces a 13.1 kDa, 115 residue protein (ORF4).
+Its 5'-most CDS, beginning at 1965bp and sharing the same STC as ORF9, produces a 13.1 kDa, 115 residue protein (ORF4).
 ORF4 was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggests it is a bona fide ORF.
-Unlike TRXPT_3, the CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS if the first SSC is skipped).
-However, if we assume that TRXPT_4 shares the same TSS as TRXPT_1, then the 5'-most CDS is a distinct, novel, multi-exonic 15.9 kDa, 143 aa protein with the same SSC as TRXPT_1 and TRXPT_2 but with a unique STC.
-The splice junctions of the transcripts in this region (except the junction for TRXPT_4) were validated by cloning of viral cDNA and Sanger sequencing (**Figure 5**; **Supplementary PCR methods**).
+Unlike TRXPT_3, the CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS using the secondary SSC).
+However, if we assume that TRXPT_4 uses the E1 TSS, then the 5'-most CDS is a distinct, novel, multi-exonic 15.9 kDa, 143 aa protein (ORF11) with the same SSC as ORF9 and ORF10 but with a unique STC.
+The splice junctions of all transcripts in this region (except the junction for TRXPT_4) were validated by cloning of viral cDNA and Sanger sequencing (**Supplementary PCR methods**).
+
 During the validation of TRXPT_2, ORF1 was present on the agarose gel (an unspliced band size) and Sanger sequencing results as a bona fide transcript (**Supplementary PCR methods**).
-This was corroborated by our 3'RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without any splicing, with a poly-A tail immediately after the TTS of transcripts in this region.
+This was corroborated by our 3'RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without any splicing, with a poly-A tail immediately after the E1 TTS.
 The 5'-most CDS of this transcript (TRXPT_2B) would encode ORF1.
-However, TRXPT_2B has an upstream and in-frame SSC to the predicted SSC of ORF1, suggesting that the predicted ORF1 CDS is truncated; it shares the same TSS, SSC, and TTS as TRXPT_2, but has a unique STC.
+However, TRXPT_2B has an upstream and in-frame SSC to the predicted SSC of ORF1, suggesting that the predicted ORF1 CDS is truncated -- the actual ORF1 (eORF1) that is expressed shares the same SSC as ORF10, but has a unique STC.
 
 **Early Region 2 (E2) and Intermediate Region (IM) transcripts**     
-The E2 TU expressed on the anti-sense strand, is subdivided into E2A and E2B and encodes three classical AdV proteins essential for genome replication: pTP and Ad-pol (E2B proteins), and DBP (E2A protein) [@Donovan2020; @Zhao2014].
+The E2 TU expressed on the anti-sense strand is subdivided into E2A and E2B and encodes three classical AdV proteins --  pTP and Ad-pol (E2B proteins), and DBP (E2A protein) -- essential for genome replication [@Donovan2020; @Zhao2014].
 Unlike MAdV where two promoters (E2-early and E2-late) are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751bp) from which both E2A and E2B transcription is initiated.
@@
 The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from two exons.
-The corresponding transcript (TRXPT_21) found in our data matches this predicted splicing pattern precisely but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
+The corresponding transcript (TRXPT_21) found in our data matches this predicted splice junction precisely but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
 Thus, TRXPT_21 is a three-exon transcript encoding DBP (380 residues, 43.3 kDa) precisely as predicted.
-This transcript (TRXPT_21) was also corroborated in a 3'-RACE experiment.
-Additionally, from the 3'-RACE, a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript was found.
-This transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP because the first SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron, and does not yield any viable product.
-Utilizing the SSC 173 bp downstream of TRXPT_21's SSC yields a 346 residue, 39.3 kDa product, which is in-frame of DBP but entirely contained in the second exon.
+This transcript (TRXPT_21) was also corroborated in a 3'RACE experiment.
+Additionally, from the 3'RACE, a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript was found.
+This transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP (tDBP) because the SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron.
+The SSC 173 bp downstream of DBP's SSC yields tDBP (a 346 residue, 39.3 kDa product), which is in-frame of DBP but entirely contained in the second exon.
 TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 6**).
@@
 The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 6**).
-TRXPT_7 has the CP for IVa2 and both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
+TRXPT_7 has the CP for both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
 The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel non-coding 5' exons, the third exon (containing the SSC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
 The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC of pTP is utilized.
-The encoded product is identical to the predicted pTP ORF (597 residues; 70.5 kDa).
+The encoded product is identical to the predicted pTP protein (597 residues; 70.5 kDa).
 If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol (polymerase) ORF (1112 residues; 129.2 kDa).
@@
 However, the CP remains similar to that of TRXPT_7 except the Ad-pol encoded from the secSSC is a truncated isoform with a new STC resulting from the splice site.
-We also found a novel short transcript (TRXPT_15) entirely nested within the terminal exon of TRXPT_7 but with a unique splice site.
-This transcript is an incomplete construction from the mapped reads as it contains an incomplete CDS.
-However, we validated the this splice junction to be genuine (**Supplementary PCR methods**).
+
+While both TRXPT_6 and TRXPT_7 have the CP for Ad-pol with secSSC usage, in all AdVs studied, the two proteins (pTP and Ad-pol) are encoded by separate mRNAs with identical first three 5' exons and TTS, but the splice junction to the terminal exons are different.
+We checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing) and discovered a unique splice junction (10,981-7062bp) not found in our RNA-seq data.
+If initiated from the E2 TSS and terminated at the E2 TTS, this transcript(TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 6**).
+
+Our RNA-seq data also showed a novel short transcript (TRXPT_15) entirely nested within the terminal exon of TRXPT_7 but with a unique splice site.
+This transcript is an incomplete construction from the mapped reads as it contains a truncated CDS.
+However, we validated this splice junction to be genuine (**Supplementary PCR methods**).
 
@@
 The promoter expressing this single transcript (TRXPT_5) is embedded in E2B region and shares a TTS with E2B transcripts [@Donovan2020; @Zhao2014].
-TRXPT_5 is a two-exon transcript spliced at 3447-3615bp exactly as the last intron of TRXPT_6.
-The first exon is an UTR, except the last 2 nucleotides, which connect with the first nucleotide of second exon to form the 5'-most SSC.
+TRXPT_5 is a two-exon transcript spliced exactly as the last splice junction of TRXPT_6.
+The first exon is a UTR, except the last 2 nucleotides, which connect with the first nucleotide of the second exon to form the 5'-most SSC.
 This first SSC is 4 codons upstream and in-frame of the predicted IVa2 SSC.
-Regardless of the SSC considered, the encoded protein (IVa2) is largely unaffected.
-Except for the four extra residues at the N-terminus (considering the 5'-most SSC), the entire protein sequence is identical to IVa2.
+Except for the four extra N-terminus residues, the entire protein sequence is identical to the predicted IVa2.
 
@@
 In THEV, only one ORF (E3) was predicted in this region.
-However, we identified six novel transcripts here (`r paste0("TRXPT_", 22:27, collapse = ", ")`) (**Figure 7**).
-We identified two distinct TSSs --- one similar to the classic MAdV E3 TSS (position 18,230bp) and the other about 500 bp downstream at 18,727bp.
-The E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU; however, some CDSs are nonidentical due to unpredicted splicing or the use of an upstream, in-frame SSC.
-For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered it to be a significantly longer four-exon ORF expressed from TRXPT_24.
-The first two exons of L33K were not predicted but the last two match the predicted exons and the CDS is in-frame.
-However, the first 20bp of the predicted 33K (including the SSC at 20,142bp) is spliced out as as part of the second intron of TRXPT_24.
-Thus, the bona fide 33K is a 19.8 kDa, 171 residue protein (L33K) spanning four exons instead of the predicted 120 aa protein.
-TRXPT_24 also has the CP for the ORFs, pVIII and E3 (a longer variant starting from and upstream, in-frame SSC) if we consider downstream SSC usage.
-Also, 22K (89 residues) is a single-exon ORF predicted to use the same SSC as 33K (20,142bp).
-However, just like 33K, all the transcripts in this region exclude the predicted SSC as part of their introns; hence 22K as predicted is not identical to any expressed ORF.
-TRXPT_29 has its SSC upstream of 22K's predicted SSC but is spliced to overlap a portion of 22K's CDS.
-However, the overlapping sequence is short and not in-frame of 22K.
-The 5'-most product of TRXPT_29 is a novel 73 residue protein (8.3aK) entirely different from 22K.
-TRXPT_23 being spliced identically as TRXPT_29 also encodes this novel 73 aa protein (8.3aK) from its first SSC.
-Similarly, TRXPT_22 also encodes a 73 aa novel protein (8.3bK) from its first SSC that shares over 80% similarity with 8.3aK, but it differs from 8.3aK at the C-terminus.
-Considering downstream SSC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and E3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
-As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair and they were differentiated from each other by cloning and Sanger sequencing.
+However, as the E3 TU is nested in the MLTU, transcripts from the L4P (100K, 22K, 33K, and pVIII) not only overlap the E3 region transcripts entirely as seen in our RNA-seq results, but also have their TSS and TTS in practically the same locations (**Figure 7**).
+Therefore, we have categorized these two groups together as E3 transcripts.
+
+We identified seven novel transcripts here (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs -- one corresponding to the TSS of the L4P (position 18,230bp) and the other at 18,727bp corresponding the E3 promoter (E3P).
+These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU.
+But some CDSs are nonidentical due to unpredicted splicing or the use of an in-frame upstream SSC.
+For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered a significantly longer four-exon ORF (e33K) on TRXPT_24 that contains it almost entirely.
+The first two exons of e33K were not predicted but the last two match the predicted exons and the CDS is in-frame, but the first 20bp of the predicted 33K (including the SSC at 20,142bp) is spliced out as part of the second intron of TRXPT_24.
+Thus, the bona fide 33K (e33K) is a 19.8 kDa, 171 residue protein spanning four exons instead of the predicted 120 aa protein.
+TRXPT_24 also has the CP for the ORFs, pVIII and a longer variant of E3 (eE3; starting from an in-frame upstream SSC) if we consider downstream SSC usage.
+TRXPT_29 is the shortest transcript in this TU.
+It is a two-exon transcript, both exons comprising the CDS.
+The product of TRXPT_29 is a novel 73 residue protein (8.3KI) sharing the SSC of e33K but with a unique STC.
+TRXPT_23 being spliced identically as TRXPT_29 also encodes 8.3KI from its first SSC.
+Similarly, TRXPT_22 also encodes a 73 aa novel protein (8.3KII) from its first SSC that shares over 80% similarity with 8.3KI, but it differs from 8.3KI at the C-terminus.
+Considering downstream SSC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and eE3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair and they were differentiated from each other by cloning and Sanger sequencing (**Supplementary PCR methods**).
 
@@
 This was a three-exon transcript (TRXPT_30) with its first and last exons spliced identically as TRXPT_23, but which also has the second exon of TRXPT_24 (**Figure 7**).
-The first CDS on TRXPT_30 spans all three exons, with the STC in the terminal (third) exon, producing a novel 140 residue, 15.7kDa protein (L22K).
-Interestingly, the last 81 C-terminus residues are identical to 22K (89 residues); only the first 7 residues are lacking due to splicing.
-Hence, we may consider L22K as a long variant of the predicted 22K ORF.
+The first CDS on TRXPT_30 spans all three exons, producing a novel 140 residue, 15.7kDa protein (e22K).
+Interestingly, the last 81 C-terminus residues of e22K are identical to 22K (89 residues), which is a single-exon ORF predicted to use the same SSC as 33K (20,142bp).
+Just as seen for 33K, all the transcripts in this region exclude the first 20bp of 22K (including the SSC) as part of their introns; therefore, the first 7 residues of 22K are lacking in e22K due to splicing.
+Hence, we may consider e22K as a long variant of the predicted 22K ORF.
 Albeit the TSS and TTS of TRXPT_30 was not seen, we presume that they are similar to TRXPT_23, in which case it would also have the downstream CP of TRXPT_23.
 TRXPT_25 is the largest transcript in the TU.
-It also utilizes the classic E3 TSS but has distinct TTS.
-It is a two exon transcript, encoding a novel protein (t100K; 543 residues), which is a shorter isoform of the predicted 100K ORF.
-Considering secSSC usage on this transcript yields the predicted ORF, 22K.
-It also has the CP for pVIII and E3 in that order.
+It also utilizes the L4P TSS but has a distinct TTS.
+It is a two-exon transcript, encoding a novel protein (t100K; 543 residues), which is a shorter isoform of the predicted 100K ORF.
+Considering secSSC usage on this transcript yields the predicted 22K ORF precisely.
+It also has the CP for pVIII and eE3 in that order.
 Furthermore, during the validation of TRXPT_25's splice junction using primers that span its junction (18350-18717bp), we noticed a DNA band that corresponds to the full unspliced sequence (**Supplementary PCR methods**).
 As TRXPT_25 only falls short of encoding the complete predicted 100K protein due to its splice junction, this band (which we cloned and validated by Sanger sequencing) suggests that the predicted 100K is indeed expressed.
-This transcript (TRXPT_25B) although not seen in our RNA-seq data, likely shares the same TSS and TTS as TRXPT_25.
-Lastly, TRXPT_26 and TRXPT_27 share the same TSS, unique from the other transcripts in this region but with distinct TTSs.
+This transcript (TRXPT_25B) although not seen in full, likely shares the same TSS and TTS as TRXPT_25.
+Lastly, TRXPT_26 and TRXPT_27 both originate from the E3 TSS but have distinct TTSs.
 TRXPT_26 is a three-exon transcript but the first two are UTRs.
-It encodes pVIII as the 5'-most ORF and has the CP for E3 and Fiber in that order.
+It encodes pVIII as the 5'-most ORF and has the CP for eE3 and Fiber in that order.
 TRXPT_27 on the other hand, is only a two-exon transcript but similar to TRXPT_26, only the terminal exon contains the CDSs.
 It encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSSC usage.
-TRXPT_13, which seems to be an E3 transcript that uses the MLP TSS is discussed under the MLTU transcripts.
+TRXPT_13, which is an L4 transcript that uses the MLP TSS is discussed under the MLTU transcripts.
 
-**Early Region 4 (E4) transcripts**.
-This transcription unit (TU) is the found at the tail-end (3'-end) of the genome on the anti-sense strand.
+**Early Region 4 (E4) transcripts**   
+This TU is found at the tail-end (3'-end) of the genome  and expressed from the anti-sense strand.
 Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the same strand as ORF8 nor transcribed from a promoter in the E4 region, only ORF8 can legitimately be classified as a transcript in this TU.
 This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the anti-sense strand (**Figure 8**).
-The transcript (TRXPT_28) spans 25192-26247 and is spliced at 25701-26055; hence, a two-exon transcript.
-The second exon fully matches the predicted ORF8 with 12 extra base pairs at the 3'-end; however, the encoded protein is an exact match.
-There is a SSC in the first exon at position 26246 (second nucleotide of the transcript).
-The encoded protein from this SSC is in-frame with the predicted SSC of ORF8 in the second exon; hence, the bulk of this longer protein (26.4 kDa, 229 aa) is identical to the predicted ORF8 protein.
+The transcript (TRXPT_28) spans 25192-26247bp and is spliced at 25701-26055bp, making a two-exon transcript.
+The second exon fully matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
+However, there is a SSC in the first exon at position 26246bp (192bp upstream of the predicted SSC).
+The encoded protein from this SSC is in-frame with the predicted SSC found in the second exon; hence, we consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of the predicted ORF8, the genuinely expressed ORF with an identical C-terminus to the predicted ORF8 protein.
 
@@
 The MLTU transcripts dominate the late phase (i.e, after DNA replication) of the AdV infectious cycle.
-The MLP produces all late mRNAs by alternative splicing and alternative polyadenylation of a primary transcript, which are grouped into five transcript classes (L1-L5).
-These late proteins primarily act as capsid proteins, promote virion assembly, and direct genome packaging [@Guimet2016; @Donovan2020; @Zhao2014].
-Similar to other AdVs, most of THEV's coding capacity falls within this TU.
-Specifically, about 13 out of the 23 predicted ORFs were assigned to this TU, some of which we have found to belong to the E3 TU instead.
-Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU.
-We identified the untranslated TPL at the 5' end of most transcripts in this region as expected.
-However, for three transcripts (`r paste0("TRXPT_", c(16:18), collapse = ", ")`), a different leader sequence (sTPL) is used: the first TPL exon is substituted for a unique first exon, found between the first and second TPL exons.
+The MLP produces all late mRNAs by alternative splicing and alternative polyadenylation of a primary transcript, grouped into five transcript classes (L1-L5).
+Most of THEV's coding capacity falls within this TU.
+Specifically, about 13 out of the 23 predicted ORFs were assigned to this TU, some of which we have categorized under the E3 TU instead.
+Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU, the majority of which have the 5' untranslated TPL leader sequence as seen in all AdVs.
+For three transcripts (`r paste0("TRXPT_", c(16:18), collapse = ", ")`), a different leader sequence (sTPL) is used, which differs from the TPL in only one regard: the first TPL exon is substituted for a different first exon, found between the first and second TPL exons.
 Also, TRXPT_20 seems to include only the third TPL exon (**Figure 9**).
@@
 TRXPT_17 encodes the ORF, III (penton), and TRXPT_18 encodes the ORF pVII exactly as predicted.
-The L3 mRNAs include TRXPT_14 and TRXPT_20, of which TRXPT_14 utilizes the full TPL whereas TRXPT_20 uses only the third TPL exon (ex3TPL).
+The L3 mRNAs include TRXPT_14 and TRXPT_20, of which TRXPT_14 utilizes the full TPL whereas TRXPT_20 uses only the third TPL exon (TPL3).
 Both transcripts have the CP for the ORF, hexon (II) but hexon is the only ORF encoded on TRXPT_14, whereas the 5'-most ORF on TRXPT_20 is pX (pre-Mu) followed by pVI and hexon in that order.
@@
 Normally, MLTU transcripts encoding particular ORFs splice the TPL onto a splice site just upstream of the ORF to be expressed [@Donovan2020].
-While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as the L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSSC utility and ribosome shunting found in other AdVs for their translation [@Donovan2020; @Yueh1996].
+While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as these L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSSC utility and ribosome shunting found in other AdVs for their translation [@Donovan2020; @Yueh1996].
 TRXPT_9 and TRXPT_10 are very similar but not identical.
 The last exon of TRXPT_9 seems to be truncated and probably shares the same TTS as the other L4 mRNAs.
-They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (Lprot) --- uses an in-frame, upstream SSC than predicted, and 14K (a novel unpredicted 120 aa protein).
-TRXTP_10 (and TRXPT_9 with the L4 TTS) also has the CP for pVIII and E3.
-TRXPT_11 is a seven-exon mRNA with hexon as it's 5'-most ORF but it also has the CP for Lprot, 14K, L33K, and also pVIII and E3 in that order.
-TRXPT_13 seems to be an E3 ORF utilizing the MLP TSS.
-It encodes pVIII and E3 in that order similar to TRXPT_22 but lacks TRXPT_22's novel first ORF.
+They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) -- uses an upstream in-frame SSC than predicted, and ORF12 (a novel unpredicted 120 aa protein).
+TRXTP_10 (and TRXPT_9 with the L4 TTS) also has the CP for pVIII and eE3.
+Conversely, TRXPT_11 is a seven-exon mRNA with hexon as it's 5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also pVIII and eE3 in that order.
+TRXPT_13 seems to be an E3 ORF utilizing the MLP TSS as it encodes classical L4P genes such as pVIII and eE3 in that order similar to TRXPT_22 (E3 TU) but lacks TRXPT_22's novel first ORF (8.3KII).
 
@@
 Its 5'-most ORF is fiber (IV) but it also has the CP for the THEV specific gene, ORF7.
-TRXPT_12's CP is identical TRXPT_27 of the the E3 TU albeit they differ in their 5'-UTRs.
+TRXPT_12's CP is identical to TRXPT_27 of the the E3 TU but they differ in their 5'-UTRs.
 \newpage
@@
 ## DISCUSSION/CONCLUSIONS
+expression level changes over time: The pattern seen is similar to other AdVs.
+the MLTU is significantly expressed relative to other TUs because at 12h.p.i, the infectious cycle is well underway.
+And the MLP is expressed sub optimally even before full activation of all late genes
 
@@
 The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al* [@Mahsoub2017] with modifications.
-Cells were infected at a multiplicity of infection (MOI) of 100 GCN/cell and samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for RNA-seq.
+Cells were infected in triplicates at a multiplicity of infection (MOI) of 100 GCN/cell, incubate at 41^o^C for 1 hour, and washed three times to get rid of free virion particles.
+Samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for total RNA extraction.
 The infection was repeated but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
@@
 ### Validation of Novel Splice Junctions
-
-All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work.
+All splice junctions identified in this work are novel except one predicted splice site each for pTP, DBP, and 33K, which were corroborated in our work.
 However, these predicted splice junctions had not been experimentally validated hitherto, and we identified additional novel exons, giving the complete picture of these transcripts.
-The novel splice junctions in this work discovered in the assembled transcripts using the `StringTie` transcript assembler which we validated by PCR and Sanger Sequencing are shown in **Supplementary PCR methods**.
-Briefly, we designed primers that crossed a range of novel exon-exon boundaries for each specific transcript in a transcription unit (TU) paired with their respective universal primers for the TU.
-Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site.
-After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System, these primers were used in a targeted PCR amplification, the products analyzed with agarose gel electrophoresis to confirm expected band sizes, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
+The novel splice junctions discovered in this work using the StringTie transcript assembler were validated by PCR, cloning, and Sanger Sequencing (**Supplementary PCR methods**).
+Briefly, we designed primers that span a range of novel exon-exon boundaries for each specific transcript in a transcription unit (TU).
+We designed a universal forward or reverse primers for each respective TU and paired them with primers binding specific positions in each transcript.
+Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site in the primer tails.
+After first-strand cDNA synthesis of total RNA extracted from THEV infected MDTC-RP19 cells with SuperScript™ IV First-Strand Synthesis System, these primers were used in a targeted PCR amplification, the products analyzed with agarose gel electrophoresis to confirm expected band sizes, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
 
@@
 Our sequence reads were analyzed following a well established protocol described by Pertea *et al* [@Pertea2016], using `Snakemake - version 7.24.0` [@Snakemake2021], a popular workflow management system to drive the pipeline.
-Briefly, sequencing reads were trimmed with the `FastQC - version 0.11.9` [@FastQC] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent turkey hemorrhagic enteritis virus strain Virginia (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings.
-The generated alignment (`BAM`) files from each infection time point were filtered for reads mapping to the THEV genome and fed into `StringTie - version 2.2.1` [@Pertea2016] using a `GTF` file derived from a `gff3` file obtained from NCBI, which contains the predicted ORFs of THEV as a guide.
-A custom script was used to consolidate all transcripts from all time-points without redundancy, generating the transcriptome of THEV.
+Briefly, sequencing reads were trimmed with the `Trim-galore - version 0.6.6` [@TrimGalore] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
+Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent turkey hemorrhagic enteritis virus (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings.
+The generated alignment (`BAM`) files from each infection time point were filtered for reads mapping to the THEV genome using `Samtools - version 1.16.1` and fed into `StringTie - version 2.2.1` [@Pertea2016] to assemble the transcripts, using a `GTF` annotation file derived from a `GFF3` annotation file obtained from NCBI, which contains the predicted ORFs of THEV as a guide.
+`GFFCOMPARE - version 0.12.6` was used to merge all transcripts from all time points without redundancy and using a custom `R` script, adenovirus transcripts units (regions) were assigned to each transcript, generating the transcriptome of THEV.
+`StringTie` set to expression estimation mode was used to calculate FPKM scores for all transcripts after which `Ballgown - version 2.33.0` in `R` was used to perform the statistical analysis on the transcript expression levels.
+`Samtools` was also used to count the total sequencing reads for all replicates at each time point and `Regtools - version 1.0.0` was used to count all junctions, the reads supporting them, and extract all other information related to the junction.
 See **Supplementary Computational Analysis** for the details of transcript expression level estimations and splice junction read counts.
@@
 
-## SCRIPTS AND SUPPLEMENTARY MATERIALS
+## SUPPLEMENTARY MATERIALS
 
@@
 ### CODE AVAILABILITY
-All the code/scripts written for analysis of the data are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>) 
+All the code/scripts in the entire analysis pipeline are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>) 
 \newpage
@@
 `Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here 
+BYU computing systems
 \newpage
@@
 ## TABLES AND FIGURES
-![](results/r/figures/thev_orf_map.png) **Figure 1.
+![](results/r/figures/thev_orf_map.png)   
+**Figure 1.
 *Genomic map of THEV avirulent strain annotated ORFs***.
@@
 GCN: genome copy number.
+
 ![](results/r/figures/figure3.png)   
@@
 **b) THEV transcripts identified at given time points**.
-Transcripts are color coded as explained in **a**.
+Transcripts are color coded as explained in **(a)**.
+
 ![](results/r/figures/figure_4a_d.png)    
@@
 set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e2_brkdown,
+ft <- reg_e2_brkdown %>%
+  mutate(splice_site = ifelse(splice_site == "CT-AC, GT-AG",
+                              "GT-AG", splice_site)) %>% 
+  flextable(.,
             col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
@@
 brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.05, 1.5))
+  plot_layout(heights = c(1.2, 0.05, 1.5))
 ```

### 2024-01-24 supplementary_thev_trxptome.Rmd
added Sanger seq data for trxpt_31 which encodes AdPol, also added gel
added files to submit to GEO

updated plots to include new transcript

--- 2024-01-06 supplementary_thev_trxptome.Rmd
@@
 
-flextable(supp_pcr_meth_tab) %>%
+supp_pcr_meth_tab %>% 
+  select(-valid_status) %>% 
+flextable() %>%
   theme_zebra() %>%
-  flextable::fontsize(j = c("forwardP", "reverseP"), size = 3) %>%
+  set_header_labels(trxpt_id = "Transcript ID", region = "Region", num_exons = "Number of Exons",
+                    full_trxpt = "Full Transcript", exon1 = "Exon 1", exon2 = "Exon 2",
+                    exon3 = "Exon 3", exon4 = "Exon 4", exon5 = "Exon 5", exon6 = "Exon 6",
+                    exon7 = "Exon 7", forwardP = "Forward Primer", reverseP = "Reverse Primer",
+                    gel_image = "Agarose Gel") %>% 
+  flextable::fontsize(j = c("full_trxpt", "exon1", "exon2", "exon3",
+                            "exon4", "exon5", "exon6", "exon7",
+                            "forwardP", "reverseP"), size = 3) %>%
   flextable::align(align = "center", part = "all") %>%
   flextable::width(., width = 0.35) %>% 
-  colformat_image(j = "gel_image", i = c(1:3, 6:16), na_str = "-",
-                  width = 1, height = 1) %>%
-  flextable::width(j = ~forwardP, width = 1) %>%
-  flextable::width(j = ~reverseP, width = 1) %>%
-  # flextable::width(j = ~valid_status, width = 0.35) %>%
-  flextable::width(j = ~gel_image, width = 1) %>% 
-  footnote(., i = c(1:4, 6:16), j = 12, value = as_paragraph(c("Primer binds exon 1")),
-           ref_symbols = c("a"), part = "body") %>%
-  footnote(., i = c(1:4, 6:16), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
-           ref_symbols = c("b"), part = "body")
+  colformat_image(j = "gel_image", i = c(1:3, 5:26, 28:30),
+                  width = 1.1, height = 1) %>%
+  flextable::width(j = ~forwardP, width = 1.1) %>%
+  flextable::width(j = ~reverseP, width = 1.1) %>%
+  flextable::width(j = ~gel_image, width = 1.15) %>%
+  # flextable::height(height = 0, part = "header") %>% 
+  footnote(., i = c(1:26, 28:30), j = 12, value = as_paragraph(c("Primer binds inside first exon")),
+           ref_symbols = c("a"), part = "body", inline = T) %>%
+  footnote(., i = c(1:7, 9:18, 21:26, 28, 29), j = 13, value = as_paragraph(c("Primer binds inside terminal exon")), ref_symbols = c("b"), part = "body", inline  = T) %>% 
+  # transcripts too long to validate with one primer pair
+  footnote(., i = c(8,19, 20, 30), j = 13, value = as_paragraph(c("Primer binds inside fourth exon")),
+           ref_symbols = c("c"), part = "body", inline = T) %>% 
+  footnote(., i = c(8), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_7 due to identical splicing")), ref_symbols = c("I"), part = "body", inline = T) %>%
+  footnote(., i = c(10), j = 14, value = as_paragraph(c("Agarose gel identical to last 3 exons of TRXPT_10 due to identical splicing")), ref_symbols = c("II"), part = "body", inline = T) %>%
+  footnote(., i = c(12), j = 14, value = as_paragraph(c("Agarose gel identical to last 4 exons of TRXPT_11 due to identical splicing")), ref_symbols = c("III"), part = "body", inline = T) %>% 
+  footnote(., i = c(16), j = 14, value = as_paragraph(c("Agarose gel dentical to TRXPT_23 due to identical splicing")), ref_symbols = c("IV"), part = "body", inline = T) %>% 
+  footnote(., i = c(19), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_9 due to identical splicing")), ref_symbols = c("V"), part = "body", inline = T) %>% 
+  footnote(., i = c(20), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_14 due to identical splicing")), ref_symbols = c("VI"), part = "body", inline = T) %>%
+  flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = F),
+                       opts_word = list(split = F)) %>%
+  set_caption("Table 1: Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
 ```
+
+In the table above, the restriction sites in the primer tails are shown in lowercase letters.
+All the primer melting temperatures (TMs) are 58-60^o^C using a hot start Taq DNA polymerase.
+The PCR reaction mix was done per manufacturer's instructions.
+The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (at least 53^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes.
+We used 35 cycles of amplification.
+
+## Supplementary Computational Analysis   
+`Snakemake v7.24.0` was used to manage our entire workflow.
+A graph of the main steps in our pipeline generated with `Snakemake` is shown below.
+Our trimmed RNA-seq reads were mapped to the genome of _M.
+gallopavo_ (with THEV's genome as one of its chromosomes) using `Hisat2`, to generate the alignment (BAM) files and `StringTie` used to assemble the transcriptome with a `GTF` annotation file containing the predicted THEV ORFs as a guide.
+The `GTF` annotation file was derived from a `GFF3` annotation file obtained from NCBI using `Agat - version 1.0.0`, a program for converting between many different file formats used in bioinformatics.
+However, the NCBI `GFF3` annotation file itself was first modified to remove all unimportant features, leaving only the ORFs.
+
+`StringTie` was also used to estimate the normalized expression levels (FPKM) of all the transcripts and `Ballgown` in `R` was used to perform statistical analysis and comparisons of the transcript expression levels, which instructive in understanding the temporal regulation THEV gene expression.
+
+In these steps above, each sample (replicate of each time point) was processed independently and merged only in the final transcriptome assembly or during analysis with `Ballgown`.
+In the subsequent steps described below, all samples for each time point were processed together.
+
+We used `RegTools` to extract and analyze the splice junctions in the BAM files.
+The command `regtools junctions extract` provides a wealth of information about all the splice sites in the BAM file provided such as: the start and end positions, the strand, and number of reads supporting the splice junctions.
+The command `regtools junctions annotate` gives even more information such as: the splice site donor-acceptor sequences and transcripts/genes that overlap the junction.
+These information was the basis for estimating and comparing the splicing activity of different regions (TUs) of THEV over time.
+Also, `Samtools` was also used to count the total sequencing reads for all replicates at each time point.
+![](project_map.png)

### 2024-01-24 scripts/r/abundance_analyses.R

@@ -26,7 +26,8 @@ exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
                     "abund_4hrsS2", "4h.p.i", "Rep2",
                     "abund_72hrsS1", "72h.p.i", "Rep1",
                     "abund_72hrsS2", "72h.p.i", "Rep2",
-                    "abund_72hrsS3", "72h.p.i", "Rep3") %>% data.frame()
+                    "abund_72hrsS3", "72h.p.i", "Rep3") %>%
+  data.frame()
 
 # load in expression level files for making ballgown object
 bam_files <- list.files("results/hisat2",
@@ -41,9 +42,18 @@ raw_data <- ballgown(dataDir = "results/ballgown",
 
 
 # extract transcript expression level data
-t_exp_levels <- texpr(raw_data, meas = "all") %>%
+t_exp_raw <- texpr(raw_data, meas = "all") %>%
   as_tibble() %>%
-  mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1))) %>% 
+  mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1)))
+
+# geo_submit_exp <- t_exp_raw %>%
+#   select(chr, trxpt_id, region = "gene_name", strand, start, end, num_exons, length,
+#          starts_with("FPKM"))
+
+# write.table(geo_submit_exp, "thev_trxpt_fpkm.txt", sep = "\t",
+#             quote = F, col.names = T)
+
+t_exp_levels <- t_exp_raw %>%
   pivot_longer(cols = starts_with("FPKM"),
                names_to = "samples",
                values_to = "fpkm") %>%
@@ -53,7 +63,7 @@ t_exp_levels <- texpr(raw_data, meas = "all") %>%
                                str_detect(samples, "_72hrs") ~ "72h.p.i",
                                TRUE ~ NA_character_),
          timepoint = factor(timepoint,
-                            levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>%
+                            levels = c("4h.p.i", "12h.p.i", "24h.p.i", "72h.p.i"))) %>% 
   select(c("timepoint", "t_name", trxpt_id, region = "gene_name", "strand", "start", "end", "fpkm")) %>%
   split(.$timepoint) %>%
   map(mutate, tot_fpkm_tp = sum(fpkm)) %>% 

### 2024-01-24 scripts/r/bam_file_analysis.R

@@ -72,11 +72,18 @@ bulk_junc_stats <- map_dfr(bulk_jun_files, read_tsv,
 extract_unq_juncs <- function(df){
   unqs <- df %>%
   group_by(start, end) %>%
-  reframe(Frequency = n(),
+  reframe(Timepoint = list(timepoint),
+          Frequency = n(),
           Total_Reads = sum(read_count),
           region = list(region),
           strand = list(strand))
 
+  # cleanup timepoint column of duplicated and NA values
+  unqs$Timepoint <- map(unqs$Timepoint, ~unique(na.omit(.x)))
+  
+  # convert timepoint column back to string vector
+  unqs$Timepoint <- map_chr(unqs$Timepoint, ~paste(.x, collapse = ","))
+  
   # cleanup region column of duplicated and NA values
   unqs$region <- map(unqs$region, ~unique(na.omit(.x)))
 
@@ -96,7 +103,12 @@ extract_unq_juncs <- function(df){
   return(unqs)
 }
 
-total_unq_jncs_submit <- extract_unq_juncs(bulk_junc_stats)
+total_unq_jncs_submit <- extract_unq_juncs(bulk_junc_stats) %>%
+  mutate(Name = paste0("JUNC_", 1:nrow(.))) %>%
+  select(Name, Timepoint, start, end, Strand, Frequency, Total_Reads)
+
+# write.table(total_unq_jncs_submit, "thev_unq_juncs_geo.txt", sep = "\t",
+#             quote = F, col.names = T)
   
 # --------------------
 # function to extract unique junctions for each timepoint

### 2024-01-24 scripts/r/reg_by_reg_plots.R

@@ -38,10 +38,16 @@ spliced_gtf <- spliced_gtf %>%
   mutate(trxpt_id = paste0("TRXPT_", seq(1, 28, 1)),
          transcript_id = factor(transcript_id, levels = trxpt_order)) %>%
   arrange(transcript_id) %>%
+  # Manually add transcript 29 from initial stringtie results before gffcompare merge
   rbind(tibble(transcript_id = "TCONS_00000029", strand = "+", start_1 = 18230, start_2 = 18230,
                start_3 = 20162, start_4 = NA, start_5 = NA, start_6 = NA, start_7 = NA, start_8 = NA,
                end_1 = 20732, end_2 = 18350, end_3 = 20732, end_4 = NA, end_5 = NA, end_6 = NA,
-               end_7 = NA, end_8 = NA, region = "E3", trxpt_id = "TRXPT_29"))
+               end_7 = NA, end_8 = NA, region = "E3", trxpt_id = "TRXPT_29")) %>%
+  # Manually add transcript 31 from junction validation discovery
+  rbind(tibble(transcript_id = "TCONS_00000031", strand = "-", start_1 = 2334, start_2 = 2334,
+               start_3 = 10981, start_4 = 18159, start_5 = 18684, start_6 = NA, start_7 = NA, start_8 = NA,
+               end_1 = 18751, end_2 = 7062, end_3 = 11079, end_4 = 18189, end_5 = 18751, end_6 = NA,
+               end_7 = NA, end_8 = NA, region = "E2", trxpt_id = "TRXPT_31"))
 
 
 # trxpt id and names info
@@ -56,7 +62,8 @@ exp_info <- tribble(~sample_name, ~timepoint, ~ replicate,
                     "abund_4hrsS2", "4h.p.i", "Rep2",
                     "abund_72hrsS1", "72h.p.i", "Rep1",
                     "abund_72hrsS2", "72h.p.i", "Rep2",
-                    "abund_72hrsS3", "72h.p.i", "Rep3") %>% data.frame()
+                    "abund_72hrsS3", "72h.p.i", "Rep3") %>%
+  data.frame()
 
 # load in expression level files for making ballgown object
 bam_files <- list.files("results/hisat2",
@@ -74,7 +81,10 @@ t_exp_levels <- texpr(raw_data, meas = "all") %>%
   as_tibble() %>%
[…]

### 2024-01-30 manuscript_thev_transcriptome.Rmd
added plot for SSites; added to discussion

@@
 However, a promoter in the L4 region (L4P) that directs the expression of these two proteins independent of the MLP was found, resolving the paradox [@Morris2010; @Guimet2016; @Donovan2020].
-During translation of AdV mRNA, recent studies strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020].
+During translation of AdV mRNA, recent studies strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020; @Westergren2021].
 
 High throughput sequencing methods have facilitated the discovery of many novel transcribed regions and splicing isoforms.
-It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014].
+It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014; Westergren2021].
 In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time the transcriptome of THEV (VAS vaccine strain) during different phases of the infection, yielding the first THEV splicing map.
@@
 **Overview of sequencing data and analysis pipeline outputs**  
-A previous study by Zeinab *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
+A previous study by Aboezz *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
 Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
@@
 During validation, we identified 5 additional transcripts some of which were further validated by 3' Rapid Amplification of cDNA Ends (3'RACE) data.
-The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under **accession no.
-XXXXXX**.
+The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
 
@@
 We also analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
-We found that most splice donor-acceptor sequences were unsurprisingly the canonical GU-AG nucleotides.
+We found that most splice donor-acceptor sequences were unsurprisingly the canonical GT-AG nucleotides.
+However, the splice acceptor-donor pairing became less specific over time, such that all combinations of nucleotide pairs were eventually detected (**Figure 5**)
 
@@
 
-Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (**Figure 5**).
+Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (**Figure 6**).
 Most of the ORFs of the novel transcripts are distinct from the predicted ORFs, but they all have the coding potential (CP) for the predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered as reported for other AdVs [@Donovan2020; @Zhao2014].
@@
 Unlike MAdV where two promoters (E2-early and E2-late) are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751bp) from which both E2A and E2B transcription is initiated.
-However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 6**).
+However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 7**).
 
@@
 The SSC 173 bp downstream of DBP's SSC yields tDBP (a 346 residue, 39.3 kDa product), which is in-frame of DBP but entirely contained in the second exon.
-TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 6**).
+TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 7**).
 
@@
 Interestingly, the TTS of the E1 region (position 2,325bp) on the sense strand is also in the immediate vicinity of this A-T rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
-The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 6**).
+The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 7**).
 TRXPT_7 has the CP for both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
@@
 We checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing) and discovered a unique splice junction (10,981-7062bp) not found in our RNA-seq data.
-If initiated from the E2 TSS and terminated at the E2 TTS, this transcript(TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 6**).
+If initiated from the E2 TSS and terminated at the E2 TTS, this transcript(TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 7**).
 
@@
 In THEV, only one ORF (E3) was predicted in this region.
-However, as the E3 TU is nested in the MLTU, transcripts from the L4P (100K, 22K, 33K, and pVIII) not only overlap the E3 region transcripts entirely as seen in our RNA-seq results, but also have their TSS and TTS in practically the same locations (**Figure 7**).
+However, as the E3 TU is nested in the MLTU, transcripts from the L4P (100K, 22K, 33K, and pVIII) not only overlap the E3 region transcripts entirely as seen in our RNA-seq results, but also have their TSS and TTS in practically the same locations (**Figure 8**).
 Therefore, we have categorized these two groups together as E3 transcripts.
@@
 These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU.
-But some CDSs are nonidentical due to unpredicted splicing or the use of an in-frame upstream SSC.
+But some CDSs are nonidentical due to unknown splice sites or the use of an in-frame upstream SSC.
 For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered a significantly longer four-exon ORF (e33K) on TRXPT_24 that contains it almost entirely.
@@
 In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed another splice  variant undetected in our RNA-seq transcriptome.
-This was a three-exon transcript (TRXPT_30) with its first and last exons spliced identically as TRXPT_23, but which also has the second exon of TRXPT_24 (**Figure 7**).
+This was a three-exon transcript (TRXPT_30) with its first and last exons spliced identically as TRXPT_23, but which also has the second exon of TRXPT_24 (**Figure 8**).
 The first CDS on TRXPT_30 spans all three exons, producing a novel 140 residue, 15.7kDa protein (e22K).
@@
 Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the same strand as ORF8 nor transcribed from a promoter in the E4 region, only ORF8 can legitimately be classified as a transcript in this TU.
-This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the anti-sense strand (**Figure 8**).
+This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the anti-sense strand (**Figure 9**).
 The transcript (TRXPT_28) spans 25192-26247bp and is spliced at 25701-26055bp, making a two-exon transcript.
@@
 For three transcripts (`r paste0("TRXPT_", c(16:18), collapse = ", ")`), a different leader sequence (sTPL) is used, which differs from the TPL in only one regard: the first TPL exon is substituted for a different first exon, found between the first and second TPL exons.
-Also, TRXPT_20 seems to include only the third TPL exon (**Figure 9**).
+Also, TRXPT_20 seems to include only the third TPL exon (**Figure 10**).
 
@@
 They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) -- uses an upstream in-frame SSC than predicted, and ORF12 (a novel unpredicted 120 aa protein).
-TRXTP_10 (and TRXPT_9 with the L4 TTS) also has the CP for pVIII and eE3.
+TRXTP_10 (and TRXPT_9 with the L4 TTS) additionally has the CP for pVIII and eE3.
 Conversely, TRXPT_11 is a seven-exon mRNA with hexon as it's 5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also pVIII and eE3 in that order.
@@
 ## DISCUSSION/CONCLUSIONS
-expression level changes over time: The pattern seen is similar to other AdVs.
-the MLTU is significantly expressed relative to other TUs because at 12h.p.i, the infectious cycle is well underway.
-And the MLP is expressed sub optimally even before full activation of all late genes
+While the advent of next-generation sequencing has rendered easier the study of large and complex eukaryotic transcriptomes, the study of the smaller and compact viral transcriptomes remains unintuitively challenging, as several transcripts may have significant overlaps due to genome economization.
+Characterizing AdV transcriptomes is even more difficult due to the wide array of mRNAs produced via very complex alternative splicing combined with alternative polyadenylation, all initiated from relatively few promoters.
+This makes AdV transcriptomes some of the most intricate for a virus.
+The challenge is further compounded by the fact that the standard software programs used in the RNA-seq analysis pipelines are not designed primarily for such compact, gene-dense, and complex transcriptomes as AdVs.
+Furthermore, there is no prior transcriptomic studies for THEV.
+Our approach to properly handle this complex data was to use standard RNA-seq analysis programs coupled with some custom analysis and validating all splice junctions with independent methods.
+Our work provides the first insights into the splicing patterns of THEV, which is expectedly similar to other MAdVs but with key differences.
+Our work shows 34 transcripts in the THEV transcriptome grouped into five TUs, of which the E3 TU shows great complexity of alternative splicing.
 
-For fig2a: There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection.
-Unexpectedly, the pileup of reads seems consistently skewed over similar regions of the genome.
-We could speculate that the temporal gene expression regulation of THEV is different from MAdVs or this could simply mean that the infection was not well synchronized.
-However, the relative proportions over these similar regions shows some variation over time.
-For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death TRXPT_2 and ORF1 are isoforms Presumably, if the junction reads were normalized, MLTU would not be predominant at 12hpi.
-The TTSs were all in the context of A-T rich sequences; which presumably serve as polyA signals.
+An unexpected observation is that the pileup of mapped reads to THEV seems consistently skewed over similar regions of the genome at all time points.
+As AdVs gene expression is temporally regulated, we expected to see unambiguous differences in the pileup of reads over different regions of the genome at different time points, indicating the different stages of infection.
+While this could simply mean that the infection was not well synchronized, we speculate that the temporal gene expression regulation of THEV is different from MAdVs.
+This is supported by a previous study stating the same conclusion with its finding that almost all THEV transcripts were detectable by at 4h.p.i, and by 8h.p.i, mRNA for all predicted ORFs were present [@Aboezz2019].
+Despite the overall pileup similarity, a close inspection shows that the relative proportions of reads over some regions show some variation over time.
+The breakdown of transcripts detected at different time points in **Figure 3b** seems to support this different temporal regulation of THEV.
+Specifically, the MLP of THEV is active significantly earlier in infection -- as early as 4h.p.i (**Figure 3b** and **Table 2a**), -- whereas the late phase shift in MAdVs occurs after 24h.p.i.
+This also lends credence to our speculation.
+However, generally speaking, the overall temporal gene expression regulation known in MAdVs -- early regions showing their peak expression at earlier time points followed by predominance of the MLTU at later time points -- also holds true for THEV.
+Further studies would be necessary to establish the precise temporal regulation of THEV transcription.
+
+The use of short read deep sequencing to reconstruct full AdV mRNA structures provides excellent results, especially for mapping the splice sites.
+However, due to the substantial overlapping nature of AdV mRNAs coupled with the fragmentation step in the library preparation protocol, mapping the precise TSS and TTS of the assembled transcripts is difficult.
+Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA, since the short reads alone do not provide enough data for the transcript assembler (`StringTie`) to distinguish them.
+In our results, we see transcripts in the same TU initiated or terminated in the same approximate area (10-70bp and 1-300bp apart for TSS and TTS, respectively) but not precisely at the same position.
+We consider the most upstream TSS or most downstream TTS for the transcripts involved but we present them unchanged in all the figures shown.
+Also, by comparison to the more well-studies MAdV transcriptomes, we think that a few long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are probably a result of fusing some L4P-derived E3 transcripts to the terminal exons of the bona fide MLTU transcripts by StringTie, making them significantly longer.
+These mRNAs do not only have unusually many exons for an AdV, but their last three or four exons are also identical to the L4P-derived mRNAs.
+Future studies using long read sequencing technologies are necessary to provide conclusive data for precisely mapping the TSS and TTS, as well as teasing apart the bona fide structures of the long MLTU transcripts.
+Furthermore, it is not unreasonable to presume that several splice variants were undiscovered in our work as evidenced firstly by finding unique transcripts using 3'RACE and during our splice junction validation steps.
+And secondly, recent studies [@Donovan2020; @Zhao2014; @Westergren2021] are still discovering novel mRNA variants for even the best studied MAdVs decades later.
+Another observation made is that all the TTSs in THEV's transcriptome are in close proximity to A-T rich sequences which we presume to be polyadenylation signal sequences (PASS).
+Interestingly, some of these PASSs are located in the immediate vicinity of two closely-located TTSs expressed on opposite strands.
+Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS between them, as do the E4 and TRXPT_12 and TRXPT_27.
+
+An interesting finding of our analysis is that while most of the predicted ORFs are encoded by the spliced transcripts precisely, we found a few that seem to be truncated predictions, as either an upstream in-frame SSC (eORF1, eE3, and eProt) or unknown upstream exons spliced onto them (eIVa2, e33K, and eORF8) were found.
+Other ORFs were identified that were either shorter (tDBP, t100K) or longer (e22K) isoforms of some predicted ORF but we found evidence to support the predicted ORF itself, making them all possibly translated variants.
+We also found several novel unpredicted ORFs.
+Taken together, we surmise that further studies will likely yield even more unpredicted novel ORFs or variants of predicted ORFs.
+
+Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most AUG normally being used as the translation reading frame.
+However, depending on the sequence context in some organisms, the initiating codon may even be altered to a non-AUG start codon.
+AdV mRNAs, which mostly span more than one ORF, are known to be functionally polycistronic by employing non-standard mechanisms of translation, namely, secSSC usage and ribosome shunting.
+Albeit there is no reliable method of predicting how efficiently any given AUG will be used, AdVs use secondary AUGs as initiation codons for most E1b proteins and for some E3 proteins.
+In fact, recent studies show that secSSC usage is found transcriptome-wide.
+This is thought to occur because translation initiation at the first SSC is inefficient, allowing downstream SSCs to be employed for initiation [@Donovan2020].
+The ribosomal shunting or jumping mechanism is utilized for MLTU transcripts that have the TPL.
+This mechanism allows the ribosome to translocate to a downstream initiating codon under the direction of the shunting elements in the TPL, even if a start codon in a good Kozak sequence context is bypassed.
+Thus, predicting the protein(s) that are expressed from an mRNA becomes highly uncertain as any one of the SSC may be selected [@Guimet2016; @Westergren2021].
+Almost all the THEV transcripts in our data have the CP for several ORFs, some spanning as many as six ORFs but the majority spanning at least two ORFs.
+Therefore, we believe our data supports the usage of these special ribosome initiation mechanisms as a several predicted and novel ORFs found on mRNA in our data have no conceivable mechanism of being translated if only the typical ribosome scanning mechanism is employed.
+
+It is well established that AdV alternative splicing undergoes a regulated temporal shift in splice site usage.
+This was thought to be limited to certain TUs; however, recent studies suggest that AdVs routinely produce different combinations of splice acceptor–donor pairs and that this is observed in all TUs [@Westergren2021; @Akusjarvi2008; @Donovan2020; @Guimet2016].
+The mechanistic details of this phenomenon has been best studied for the E1A and L1 units.
+The studies show that AdVs (specifically, late phase AdV-infected nuclear extract) modulate the activities of the splicing factor U2AF and the cellular SR family of splicing factors (reviewed in reference [@Akusjarvi2008]) and encode several mostly late phase proteins (E4-ORF3, E4-ORF6, E4-ORF4, L4-33K, and L4-22K) that influence the RNA splice site used.
+This phenomenon seems to occur in the THEV transcriptome also, as the stringency of splice sites used decreases significantly from the onset of the late phase (see **Figure 5**).
+It is unlikely that all repertoire of mRNA produced via this mechanism will actually be translated.
+However, it has been speculated that the plasticity in alternative RNA splicing enables the AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions.
+And also that the capacity to produce novel exon combinations will offer the virus an evolutionary advantage to change the gene expression repertoire and protein production in a changing environment [@Donovan2020; @Westergren2021].
+
 All splice junctions were confirmed by cloning and Sanger sequencing of cDNA (**Supplementary PCR methods**).
@@
 ### DATA AVAILABILITY
+The raw sequence data (FastQ), transcript expression counts, and total unique junctions have been deposited at the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
+
+Data is available on request by contacting the designated corresponding author
 
@@
 `Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here 
-BYU computing systems
+`BYU high performance computing systems` - Memory intensive analysis were run here.
 \newpage
@@
 **Figure 1.
-*Genomic map of THEV avirulent strain annotated ORFs***.
+*Predicted ORF map of THEV avirulent strain***.
 The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
@@
 
+![](results/r/figures/figure_5a_d.png)
+**Figure 5: Changes in splice donor-acceptor nucleotides over time.** The splice donor-acceptor nucleotides of THEV just like other AdVs is mostly the canonical GT-AG.
+At early time points (4h.p.i and 12h.p.i [**(a)** and **(b)**]) the junction nucleotides used appear to be well scrutinized or restricted, utilizing mostly the canonical splice nucleotides.
+However, as the infection progresses to the late stages (24h.p.i and 72h.p.i [**(c)** and **(d)**]), the selectivity of specific splice acceptor-donor pairs seems to degenerate significantly, such that all combinations of nucleotides are utilized.
+
 ```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
@@
 ```
-**Figure 5: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
+**Figure 6: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
 Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and transcripts or ORFs discovered by other means are colored black.
@@
 ```
-**Figure 6: The splice map of the E2 and IM TUs**.
+**Figure 7: The splice map of the E2 and IM TUs**.
 Exons are depicted as boxes connected by introns (dotted lines).
@@
 ```
-**Figure 7: The splice map of the E3 TU.** Exons are depicted as boxes connected by introns (dotted lines).
+**Figure 8: The splice map of the E3 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
@@
 ```
-**Figure 8: The splice map of the E4 TU.** Exons are depicted as boxes connected by introns (dotted lines).
+**Figure 9: The splice map of the E4 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 The transcript from RNA-seq data is colored red and the predicted ORF, grey.
@@
 ```
-**Figure 9: The splice map of the MLTU.** Exons are depicted as boxes connected by introns (dotted lines).
+**Figure 10: The splice map of the MLTU.** Exons are depicted as boxes connected by introns (dotted lines).
 The transcripts from our RNA-seq data are colored red and the predicted ORFs, grey.

### 2024-01-30 scripts/r/bam_file_analysis.R

@@ -22,24 +22,6 @@ library(scales)
 #   distinct(start, end, .keep_all = T) %>%
 #   # convert from 0-base indexing of .bed format to 1-base indexing
 #   mutate(start = start + 1)
-# 
-# 
-# single_sum_stats <- single_junc_stats %>%
-#   mutate(timepoint = case_when(timepoint %in% c("t72s1", "t72s2", "t72s3") ~ "72hpi",
-#                                timepoint %in% c("t24s1", "t24s2", "t24s3") ~ "24hpi",
-#                                timepoint %in% c("t12s1", "t12s3") ~ "12hpi",
-#                                timepoint %in% c("t4s1", "t4s2", "t4s3") ~ "4hpi",
-#                                .default = timepoint)) %>%
-#   group_by(timepoint) %>%
-#   summarize(total_junctions = n(),
-#             reads10  = sum(read_count > 10),
-#             reads100  = sum(read_count > 100),
-#             reads1000  = sum(read_count > 1000),
-#             total_reads_supporting = sum(read_count),
-#             mean_read_supporting = total_reads_supporting/total_junctions,
-#             organism = "thev") %>%
-#   mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>%
-#   arrange(total_junctions)
 
 # ============================BULK=============================================
 # =============================================================================

### 2024-01-30 scripts/r/plot_abundances.R

@@ -77,78 +77,136 @@ bulk_trxptome_ss_seq <- count_trxptome_ss(unq_bulk_juncs) %>%
   mutate(sum_junc_count = sum(freq),
          percent_abund = (freq / sum_junc_count) * 100)
 
-# plot trxptome acceptors and donor frequencies
-ss <- bulk_trxptome_ss_seq %>%
-  ggplot(aes(splice_site, percent_abund, color = splice_site)) +
-  geom_point(show.legend = F, size = 10) +
-  geom_segment(aes(x = splice_site, xend = splice_site,
-                   y = 0, yend = percent_abund),
-               linewidth = 2,
-               show.legend = F) +
-  geom_text(aes(label = glue("{round(percent_abund, 1)}%")),
-             nudge_y = 3.5,
-            size = 10, fontface = "bold", color = "#000000") +
-  labs(x = "Splice Site Donor-Acceptor",
-       y = "Frequency") +
-  scale_color_lancet() +
-  scale_y_continuous(expand = c(0.01,0.01),
-                     labels = scales::label_percent(scale = 1)) +
-  scale_x_discrete(expand = c(0.13, 0.13)) +
-  coord_cartesian(clip = "off") +
-  theme_classic() +
-  theme(plot.margin = margin(rep(30, 4)),
-        panel.grid.major.y = element_line(linewidth = 0.4, color = "grey",
-                                          linetype = "dashed"),
-        axis.title = element_text(size = 16, face = "bold", margin = margin(r = 15, t = 25)),
-        axis.text.x = element_text(size = 16, face = "bold"),
-        axis.text.y = element_text(size = 14, face = "bold"),
-        axis.line = element_line(color = "grey40"),
-        axis.ticks.length = unit(0, "pt")
-        )
-
-# All acceptors and donors
-# all_ss_seq <- bulk_junc_stats %>%
-#   distinct(timepoint, start, end, .keep_all = T) %>%
-#   mutate(timepoint = factor(timepoint, levels = c("4hpi", "12hpi", "24hpi", "72hpi"))) %>% 
-#   group_by(timepoint, splice_site) %>%
-#   reframe(tally = n(),
-#           total_reads = sum(read_count)) %>%
-#   split(.$timepoint) %>%
-#   map(mutate, tot_tally_tp = sum(tally)) %>% 
-#   do.call("rbind", .) %>%
[…]

### 2024-01-31 manuscript_thev_transcriptome.Rmd
finished discussion; improved supp tables

@@
 Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
-In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)` novel transcripts.
+In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)-1` novel transcripts.
 Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (**Figure 3**).
@@
 
-Individually, TRXPT_21 (DBP) -- from the E2 region -- was the most significantly expressed at 12 h.p.i, comprising about `r abn_each_12`% of the total transcripts.
+Considering individual mRNAs, TRXPT_21 -- from the E2 region -- was the most significantly expressed at 12 h.p.i, constituting about `r abn_each_12`% of the total expression of all transcripts.
 Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
@@
 After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
+In MAdVs, this region is subdivided into E1a and E2b units but the transcripts found in our data categorized under this region do not appear to so divided.
 
@@
 Additionally, from the 3'RACE, a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript was found.
-This transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP (tDBP) because the SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron.
+This new transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP (tDBP) because the SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron.
 The SSC 173 bp downstream of DBP's SSC yields tDBP (a 346 residue, 39.3 kDa product), which is in-frame of DBP but entirely contained in the second exon.
-TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine-thymine (A-T) rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 7**).
+TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine/thymine (A/T)-rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 7**).
 
-The E2B region transcripts also start with the E2-5'UTR but extend thousands of base pairs downstream to reach the TTS at 2334bp in the IM region, which is immediately followed by an A-T rich sequence (position 2323-2339bp) where polyadenylation probably occurs.
-Interestingly, the TTS of the E1 region (position 2,325bp) on the sense strand is also in the immediate vicinity of this A-T rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
+The E2B region transcripts also start with the E2-5'UTR but extend thousands of base pairs downstream to reach the TTS at 2334bp in the IM region, which is immediately followed by an A/T rich sequence (position 2323-2339bp) where polyadenylation probably occurs.
+Interestingly, the TTS of the E1 region (position 2,325bp) on the sense strand is also in the immediate vicinity of this A/T rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
 The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 7**).
@@
 The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel non-coding 5' exons, the third exon (containing the SSC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
-The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; hence, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC of pTP is utilized.
+The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; thus, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC of pTP is utilized.
 The encoded product is identical to the predicted pTP protein (597 residues; 70.5 kDa).
-If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol (polymerase) ORF (1112 residues; 129.2 kDa).
+If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol (polymerase) protein (1112 residues; 129.2 kDa).
 TRXPT_6 differs from TRXPT_7 by containing an extra splice site at 3447-3515bp.
@@
 
-We identified seven novel transcripts here (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs -- one corresponding to the TSS of the L4P (position 18,230bp) and the other at 18,727bp corresponding the E3 promoter (E3P).
-These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, E3, Fiber (IV), and ORF7 belonging to the MLTU.
-But some CDSs are nonidentical due to unknown splice sites or the use of an in-frame upstream SSC.
+We identified seven novel transcripts here (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs -- we consider the first TSS (position 18,230bp) as corresponding to the L4P and the other at 18,727bp as corresponding to the E3 promoter (E3P).
+These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, and E3, as well as Fiber (IV) and ORF7 belonging to the MLTU.
+But some of these CDSs are different than predicted due to either unknown exons or the presence of an in-frame upstream SSC.
 For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered a significantly longer four-exon ORF (e33K) on TRXPT_24 that contains it almost entirely.
-The first two exons of e33K were not predicted but the last two match the predicted exons and the CDS is in-frame, but the first 20bp of the predicted 33K (including the SSC at 20,142bp) is spliced out as part of the second intron of TRXPT_24.
+The first two exons of e33K were not predicted but the last two match the predicted exons and the CDS is in-frame, albeit the first 20bp of the predicted 33K (including the SSC at 20,142bp) is spliced out as part of the second intron of TRXPT_24.
 Thus, the bona fide 33K (e33K) is a 19.8 kDa, 171 residue protein spanning four exons instead of the predicted 120 aa protein.
-TRXPT_24 also has the CP for the ORFs, pVIII and a longer variant of E3 (eE3; starting from an in-frame upstream SSC) if we consider downstream SSC usage.
+TRXPT_24 also has the CP for pVIII and E3 if we consider downstream SSC usage.
+However, the predicted E3 has an upstream in-frame SSC; thus this longer version of E3 (eE3) is the genuinely expressed ORF.
 TRXPT_29 is the shortest transcript in this TU.
@@
 Considering downstream SSC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and eE3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+
 As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair and they were differentiated from each other by cloning and Sanger sequencing (**Supplementary PCR methods**).
-
 In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed another splice  variant undetected in our RNA-seq transcriptome.
 This was a three-exon transcript (TRXPT_30) with its first and last exons spliced identically as TRXPT_23, but which also has the second exon of TRXPT_24 (**Figure 8**).
-The first CDS on TRXPT_30 spans all three exons, producing a novel 140 residue, 15.7kDa protein (e22K).
-Interestingly, the last 81 C-terminus residues of e22K are identical to 22K (89 residues), which is a single-exon ORF predicted to use the same SSC as 33K (20,142bp).
+The first CDS on TRXPT_30 spans all three exons, producing a novel 140 residue, 15.7kDa protein.
+Interestingly, the last 81 C-terminus residues of this new protein (e22K) are identical to 22K (89 residues), which is a single-exon ORF predicted to use the same SSC as 33K (20,142bp).
 Just as seen for 33K, all the transcripts in this region exclude the first 20bp of 22K (including the SSC) as part of their introns; therefore, the first 7 residues of 22K are lacking in e22K due to splicing.
-Hence, we may consider e22K as a long variant of the predicted 22K ORF.
+Hence, we consider e22K as a long variant of the predicted 22K ORF.
 Albeit the TSS and TTS of TRXPT_30 was not seen, we presume that they are similar to TRXPT_23, in which case it would also have the downstream CP of TRXPT_23.
+
 TRXPT_25 is the largest transcript in the TU.
@@
 Specifically, about 13 out of the 23 predicted ORFs were assigned to this TU, some of which we have categorized under the E3 TU instead.
-Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU, the majority of which have the 5' untranslated TPL leader sequence as seen in all AdVs.
+Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU, the majority of which have the 5' untranslated TPL sequence as seen in all AdVs.
 For three transcripts (`r paste0("TRXPT_", c(16:18), collapse = ", ")`), a different leader sequence (sTPL) is used, which differs from the TPL in only one regard: the first TPL exon is substituted for a different first exon, found between the first and second TPL exons.
@@
 
-We identified five TTSs (10,549bp, 12,709bp, 16,870bp, 17,891bp, 20,865bp) in this TU, corresponding to the five late mRNA classes (L1-L5), respectively, as found in all AdVs.
+We identified five TTSs (10,549bp, 12,709bp, 16,870bp, 17,891bp, 20,865bp) in this TU, which we consider as corresponding to the five late mRNA classes (L1-L5), respectively, as found in all AdVs.
 L1 mRNAs include TRXPT_8, which comprises the TPL (non-coding) and the CDS-containing terminal exon.
@@
 As AdVs gene expression is temporally regulated, we expected to see unambiguous differences in the pileup of reads over different regions of the genome at different time points, indicating the different stages of infection.
-While this could simply mean that the infection was not well synchronized, we speculate that the temporal gene expression regulation of THEV is different from MAdVs.
-This is supported by a previous study stating the same conclusion with its finding that almost all THEV transcripts were detectable by at 4h.p.i, and by 8h.p.i, mRNA for all predicted ORFs were present [@Aboezz2019].
-Despite the overall pileup similarity, a close inspection shows that the relative proportions of reads over some regions show some variation over time.
+While this could simply mean that the infection was not well synchronized, we speculate that the temporal gene expression regulation of THEV is probably different from MAdVs.
+This is supported by a previous study stating the same conclusion with its finding that almost all THEV transcripts were detectable by at 4h.p.i, and by 8h.p.i, mRNA for all predicted ORFs (including the late genes) were present [@Aboezz2019].
+Conversely, despite the overall pileup similarity, a close inspection shows that the relative proportions of reads over some regions show some variation over time.
 The breakdown of transcripts detected at different time points in **Figure 3b** seems to support this different temporal regulation of THEV.
-Specifically, the MLP of THEV is active significantly earlier in infection -- as early as 4h.p.i (**Figure 3b** and **Table 2a**), -- whereas the late phase shift in MAdVs occurs after 24h.p.i.
+Specifically, the MLP of THEV is active significantly earlier in infection -- as early as 4h.p.i and more pronounced at 12h.p.i (**Figure 3b** and **Table 2a**), -- whereas the late phase shift in MAdVs occurs after 24h.p.i.
 This also lends credence to our speculation.
@@
 However, due to the substantial overlapping nature of AdV mRNAs coupled with the fragmentation step in the library preparation protocol, mapping the precise TSS and TTS of the assembled transcripts is difficult.
-Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA, since the short reads alone do not provide enough data for the transcript assembler (`StringTie`) to distinguish them.
+Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA, since the short reads alone do not provide enough context for the transcript assembler (`StringTie`) to distinguish them.
 In our results, we see transcripts in the same TU initiated or terminated in the same approximate area (10-70bp and 1-300bp apart for TSS and TTS, respectively) but not precisely at the same position.
 We consider the most upstream TSS or most downstream TTS for the transcripts involved but we present them unchanged in all the figures shown.
-Also, by comparison to the more well-studies MAdV transcriptomes, we think that a few long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are probably a result of fusing some L4P-derived E3 transcripts to the terminal exons of the bona fide MLTU transcripts by StringTie, making them significantly longer.
+Also, by comparison to the more well-studies MAdV transcriptomes, we think that a few long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are probably a result of fusing some L4P-derived transcripts to the terminal exons of the bona fide MLTU transcripts by StringTie, making them significantly longer.
 These mRNAs do not only have unusually many exons for an AdV, but their last three or four exons are also identical to the L4P-derived mRNAs.
@@
 And secondly, recent studies [@Donovan2020; @Zhao2014; @Westergren2021] are still discovering novel mRNA variants for even the best studied MAdVs decades later.
-Another observation made is that all the TTSs in THEV's transcriptome are in close proximity to A-T rich sequences which we presume to be polyadenylation signal sequences (PASS).
+Another observation made is that all the TTSs in THEV's transcriptome are in close proximity to A/T-rich sequences which we presume to be polyadenylation signal sequences (PASS).
 Interestingly, some of these PASSs are located in the immediate vicinity of two closely-located TTSs expressed on opposite strands.
-Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS between them, as do the E4 and TRXPT_12 and TRXPT_27.
+Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS between them, as do the E4 (anti-sense strand) and the sense strand TRXPT_12 and TRXPT_27.
 
-An interesting finding of our analysis is that while most of the predicted ORFs are encoded by the spliced transcripts precisely, we found a few that seem to be truncated predictions, as either an upstream in-frame SSC (eORF1, eE3, and eProt) or unknown upstream exons spliced onto them (eIVa2, e33K, and eORF8) were found.
-Other ORFs were identified that were either shorter (tDBP, t100K) or longer (e22K) isoforms of some predicted ORF but we found evidence to support the predicted ORF itself, making them all possibly translated variants.
+An interesting finding of our analysis is that while most of the predicted ORFs are precisely encoded by the spliced transcripts, we found a few that seem to be truncated predictions, as either an upstream in-frame SSC (eORF1, eE3, and eProt) or unknown upstream exons spliced onto them (eIVa2, e33K, and eORF8) were found.
+Other ORFs were identified that were either shorter (tDBP, t100K) or longer (e22K) isoforms of some predicted ORF but we found evidence to support the predicted ORF itself, making them all possible genuinely translated variants.
 We also found several novel unpredicted ORFs.
@@
 Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most AUG normally being used as the translation reading frame.
-However, depending on the sequence context in some organisms, the initiating codon may even be altered to a non-AUG start codon.
-AdV mRNAs, which mostly span more than one ORF, are known to be functionally polycistronic by employing non-standard mechanisms of translation, namely, secSSC usage and ribosome shunting.
+However, depending on the sequence context, in some organisms, the initiating codon may even be a non-AUG start codon.
+AdV mRNAs, which mostly span more than one ORF, are known to be functionally polycistronic, employing non-standard mechanisms of translation initiation, namely, secSSC usage and ribosome shunting [@Westergren2021; @Guimet2016].
 Albeit there is no reliable method of predicting how efficiently any given AUG will be used, AdVs use secondary AUGs as initiation codons for most E1b proteins and for some E3 proteins.
@@
 This mechanism allows the ribosome to translocate to a downstream initiating codon under the direction of the shunting elements in the TPL, even if a start codon in a good Kozak sequence context is bypassed.
-Thus, predicting the protein(s) that are expressed from an mRNA becomes highly uncertain as any one of the SSC may be selected [@Guimet2016; @Westergren2021].
+Thus, predicting the protein(s) that are expressed from an AdV mRNA becomes highly uncertain as any one of the SSC may be selected [@Guimet2016; @Westergren2021].
 Almost all the THEV transcripts in our data have the CP for several ORFs, some spanning as many as six ORFs but the majority spanning at least two ORFs.
 Therefore, we believe our data supports the usage of these special ribosome initiation mechanisms as a several predicted and novel ORFs found on mRNA in our data have no conceivable mechanism of being translated if only the typical ribosome scanning mechanism is employed.
+Interestingly, several distinct transcripts have identical CPs.
+This is not unique to THEV but is observed in human AdVs in a recent study [@Donovan2020].
+They proposed that this may permit protein production to be fine-tuned through alteration in the balance between different mRNA groups expressing that ORF.
 
@@
 The studies show that AdVs (specifically, late phase AdV-infected nuclear extract) modulate the activities of the splicing factor U2AF and the cellular SR family of splicing factors (reviewed in reference [@Akusjarvi2008]) and encode several mostly late phase proteins (E4-ORF3, E4-ORF6, E4-ORF4, L4-33K, and L4-22K) that influence the RNA splice site used.
-This phenomenon seems to occur in the THEV transcriptome also, as the stringency of splice sites used decreases significantly from the onset of the late phase (see **Figure 5**).
+This phenomenon seems to occur in the THEV transcriptome also, as the stringency of splice acceptor-donor pairs selected decreased measurably from the onset of the late phase (see **Figure 5**).
+In fact, recent studies of some human AdVs show that virtually unlimited number of combinatorial alternative splicing events resulting in menagerie of novel transcripts are produced in an AdV lytic infection [@Donovan2020; @Westergren2021].
 It is unlikely that all repertoire of mRNA produced via this mechanism will actually be translated.
@@
 
-All splice junctions were confirmed by cloning and Sanger sequencing of cDNA (**Supplementary PCR methods**).
-We did not find the x,y,z or i-leaders for MLP transcripts probably because THEV doesn't use it due to its smaller size
-The E3 ORF has an upstream, in-frame SSC.
+Summarizing all the main points above, we see that the THEV transcriptome bares remarkable overall similarity to the better studied MAdVs.
+The transcriptome organization into five TUs, the overall regulation of early and late genes, and the production of a broad repertoire of transcripts via virtually unlimited alternative splicing.
+However, the THEV transcriptome appears to be less sophisticated (i.e, encode less genes) than MAdVs primarily because the MAdV genomes are close to twice a long as that of THEV's, which rationally should encode less genes.
+The lack of subdivision of the E1 region into E1a and E1b is one of the most obvious examples.
+Also, the MAdV E4 region encodes several proteins unlike in THEV where only one transcript coding for only one protein was found.
+The most conspicuous example is found in examining the complexity of the MLTU leader sequences.
+While the majority of THEV's MLTU transcripts begin with the TPL (267bp long) just like MAdVs and also utilizes a variant leader sequence (sTPL), it is well established that a significantly more diverse 5'UTRs are employed for MAdV MLTU transcripts, including the TPL (used for majority of transcripts), the so called x, y, and z leaders, and the i-leader.
+Granted, the MAdV MLTU transcripts infrequently incorporate the the non-TPL leaders, their absence in our data could mean that the 5'UTR diversity of THEV's MLTU mRNA are indeed more limited due to its smaller genome size.
+It is also possible that later studies could uncover more variety not seen our results.
 \newpage

### 2024-01-31 supplementary_thev_trxptome.Rmd
finished discussion; improved supp tables

@@
     select(-junc_freq) %>% 
+    mutate(region = ifelse(is.na(region), "Unassigned", region)) %>% 
     flextable() %>% 
@@
 The PCR reaction mix was done per manufacturer's instructions.
-The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (at least 53^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes.
+The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (53^o^C-56^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes.
 We used 35 cycles of amplification.

### 2024-01-31 scripts/r/bam_file_analysis.R

@@ -5,24 +5,6 @@ library(glue)
 library(tidyverse)
 library(scales)
 
-# -------------
-# single_jun_files <- list.files("results/hisat2", full.names = T,
-#                                pattern = "\\w+\\.bed") %>%
-#   setNames(c("t12s1","t12s3", "t24s1", "t24s2", "t24s3","t4s1",
-#              "t4s2", "t4s3", "t72s1", "t72s2", "t72s3"))
-# # 
-# single_junc_stats <- map_dfr(single_jun_files, read_tsv,
-#                              col_names = F,
-#                              show_col_types = F,
-#                              .id = "timepoint") %>%
-#   set_colnames(c("timepoint", "chrom", "start", "end", "junc_name",
-#                  "read_count", "strand", "thickStart", "thickEnd",
-#                  "color", "exons", "exon_sizes", "exon_starts")) %>%
-#   arrange(start, end) %>%
-#   distinct(start, end, .keep_all = T) %>%
-#   # convert from 0-base indexing of .bed format to 1-base indexing
-#   mutate(start = start + 1)
-
 # ============================BULK=============================================
 # =============================================================================
 bulk_jun_files <- list.files("results/hisat2/bulk", full.names = T,
@@ -285,7 +267,7 @@ find_sig_juncs <- function(tp, rg){
     # add back the metadata
     left_join(meta_dt, all_ests, by = join_by(region, start, end)) %>%
     filter(perc >= 1) %>%
-    arrange(desc(perc)) %>%
+    arrange(dplyr::desc(perc)) %>%
     mutate(tot_tp_j_rds = comma(tot_tp_j_rds),
            intron_len = comma(intron_len),
            counts_percent = glue("{tot_tp_j_rds} ({perc}%)")) %>%
@@ -337,11 +319,3 @@ tp_reg_expr_12 <- tp_reg_expr_abund("12hpi")
 tp_reg_expr_24 <- tp_reg_expr_abund("24hpi")
 
 tp_reg_expr_72 <- tp_reg_expr_abund("72hpi")
-
-
-
-
-
-
-
-

### 2024-01-31 manuscript_thev_transcriptome.Rmd
added styling to word output

@@
 output:
-  word_document: default
+  word_document:
+    reference_docx: style_word_output.docx
   pdf_document: default
@@
 library(english)
+library(rticles)
 opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 
-Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by immunosuppression (IS) and bloody diarrhea.
-This disease is caused by *Turkey Hemorrhagic Enteritis Virus* (THEV) of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
-The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
-We have performed the first RNA-sequencing experiment characterizing THEV’s transcriptome, yielding the most detailed insight into THEV gene expression, to set the stage for further experimentation with specific viral genes that may mediate IS.
-After infecting a turkey B-cell line (MDTC-RP19) with the VAS vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
-Total RNA was subsequently extracted, and poly-A-tailed mRNA sequencing done.
-After trimming the raw sequencing reads with the `Trim-galore`, reads were mapped to the THEV genome using `Hisat2` and transcripts assembled with `StringTie`.
-We identified 29 transcripts from our RNA-seq data all of which consisted of novel exons albeit some exons matched the predicted ORFs.
-The three predicted splice junctions were also corroborated in our data.
-We performed PCR amplification of THEV cDNA, cloned the PCR products, and Sanger sequencing was used to validate all identified splice junctions.
+We have performed an RNA-sequencing experiment characterizing the transcriptome of turkey hemorrhagic enteritis virus (THEV) for the first time, yielding the only insight into THEV's gene expression patterns.
+Previously, THEV's genome had been predicted to encode 23 open reading frames (ORFs).
+In this work we identified 29 transcripts from our RNA-seq data all of which consisted of novel exons albeit some exons matched the predicted ORFs.
+The three predicted splice junctions were also corroborated by our data.
+We performed PCR amplification of THEV cDNA and cloned the PCR products, and Sanger sequencing was used to validate all identified splice junctions.
 During validation, we identified 5 additional transcripts some of which were further validated by 3'RACE data.
 Thus, the transcriptome of THEV consists of 34 unique transcripts with the coding capacity for all predicted ORFs.
-However, we found 8 predicted ORFs to be incomplete as either an upstream, in-frame start codon was identified or additional coding exons were found, making the actual expressed versions of these ORFs longer.
-We also identified 7 novel unpredicted ORFs that could be encoded by some transcripts; albeit it is beyond the scope of this manuscript to investigate whether they are indeed expressed.
-In keeping with all Adenoviruses, our data shows that all THEV transcripts are spliced, and organized in transcription units under the control of their cognate promoter.
+However, we found 6 predicted ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated predictions as either an in-frame upstream start codon was identified or additional coding exons were found.
+We also identified 3 predicted ORFs with longer or shorter isoforms, and 7 novel unpredicted ORFs that could be encoded by some transcripts; albeit it is beyond the scope of this manuscript to investigate whether they get translated.
+Similar to other adenoviruses, THEV also produce multiple distinctly spliced transcripts that code for the same protein across its genome.
+Also, our data shows that all THEV transcripts are spliced, and organized in five transcription units under the control of their cognate promoter.
+However, our data suggests that THEV's temporal regulation may be different from other adenoviruses.
+Over 2,300 unique splice junctions were found across the genome, mostly at low levels.
+This low-level use of broad alternative splicing patterns is thought to enable the virus to maximize its coding potential in an evolving environment.
 \newpage
@@
 An additional gene (UXP or U exon) is located on the reverse strand.
-The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins that act as capsid proteins, promote virion assembly, and direct genome packaging.
+The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication, or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins that act as capsid proteins, promote virion assembly, and direct genome packaging.
 The immediate early gene E1A is expressed first, followed by the the delayed early genes, E1B, E2, E3 and E4.
@@
 A previous study by Aboezz *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
-Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection(h.p.i) to ensure an amply wide time window to sample all transcripts.
+Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection (h.p.i) to ensure an amply wide time window to sample all transcripts.
 Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*Meleagris gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
@@
 From the mapped reads, we identified a total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
-For example all the `r tot_jun_4` unique junctions at 4 h.p.i had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads/junction.
+For example, all the `r tot_jun_4` unique junctions at 4 h.p.i had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads/junction.
 Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having coverage as high as `r max_junread72` reads.
-The substantial increases in splice junction and mapping reads to the THEV genome over time denotes an active infection, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2b**).
+The substantial increases in splice junction and mapping reads to the THEV genome over time denotes an active infection and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2b**).
 
@@
 At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table 1a**).
-The top most abundant junctions at 12 h.p.i remained the most significantly expressed at 24 h.p.i also.
+The topmost abundant junctions at 12 h.p.i remained the most significantly expressed at 24 h.p.i also.
 However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table 1b**).
@@
 After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
-In MAdVs, this region is subdivided into E1a and E2b units but the transcripts found in our data categorized under this region do not appear to so divided.
+In MAdVs, this region is subdivided into E1a and E2b units, but the transcripts found in our data categorized under this region do not appear to so divided.
 
@@
 We checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing) and discovered a unique splice junction (10,981-7062bp) not found in our RNA-seq data.
-If initiated from the E2 TSS and terminated at the E2 TTS, this transcript(TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 7**).
+If initiated from the E2 TSS and terminated at the E2 TTS, this transcript (TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 7**).
 
@@
 TRXPT_24 also has the CP for pVIII and E3 if we consider downstream SSC usage.
-However, the predicted E3 has an upstream in-frame SSC; thus this longer version of E3 (eE3) is the genuinely expressed ORF.
+However, the predicted E3 has an upstream in-frame SSC; thus, this longer version of E3 (eE3) is the genuinely expressed ORF.
 TRXPT_29 is the shortest transcript in this TU.
@@
 
-As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair and they were differentiated from each other by cloning and Sanger sequencing (**Supplementary PCR methods**).
+As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair, and they were differentiated from each other by cloning and Sanger sequencing (**Supplementary PCR methods**).
 In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed another splice  variant undetected in our RNA-seq transcriptome.
@@
 The second exon fully matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
-However, there is a SSC in the first exon at position 26246bp (192bp upstream of the predicted SSC).
+However, there is an SSC in the first exon at position 26246bp (192bp upstream of the predicted SSC).
 The encoded protein from this SSC is in-frame with the predicted SSC found in the second exon; hence, we consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of the predicted ORF8, the genuinely expressed ORF with an identical C-terminus to the predicted ORF8 protein.
@@
 However, due to the substantial overlapping nature of AdV mRNAs coupled with the fragmentation step in the library preparation protocol, mapping the precise TSS and TTS of the assembled transcripts is difficult.
-Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA, since the short reads alone do not provide enough context for the transcript assembler (`StringTie`) to distinguish them.
+Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA since the short reads alone do not provide enough context for the transcript assembler (`StringTie`) to distinguish them.
 In our results, we see transcripts in the same TU initiated or terminated in the same approximate area (10-70bp and 1-300bp apart for TSS and TTS, respectively) but not precisely at the same position.
@@
 Another observation made is that all the TTSs in THEV's transcriptome are in close proximity to A/T-rich sequences which we presume to be polyadenylation signal sequences (PASS).
-Interestingly, some of these PASSs are located in the immediate vicinity of two closely-located TTSs expressed on opposite strands.
+Interestingly, some of these PASSs are located in the immediate vicinity of two closely located TTSs expressed on opposite strands.
 Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS between them, as do the E4 (anti-sense strand) and the sense strand TRXPT_12 and TRXPT_27.
@@
 The most conspicuous example is found in examining the complexity of the MLTU leader sequences.
-While the majority of THEV's MLTU transcripts begin with the TPL (267bp long) just like MAdVs and also utilizes a variant leader sequence (sTPL), it is well established that a significantly more diverse 5'UTRs are employed for MAdV MLTU transcripts, including the TPL (used for majority of transcripts), the so called x, y, and z leaders, and the i-leader.
+While the majority of THEV's MLTU transcripts begin with the TPL (267bp long) just like MAdVs and also utilizes a variant leader sequence (sTPL), it is well established that a significantly more diverse 5'UTRs are employed for MAdV MLTU transcripts, including the TPL (used for majority of transcripts), the so-called x, y, and z leaders, and the i-leader.
 Granted, the MAdV MLTU transcripts infrequently incorporate the the non-TPL leaders, their absence in our data could mean that the 5'UTR diversity of THEV's MLTU mRNA are indeed more limited due to its smaller genome size.
@@
 A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
-The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number(GCN)/mL, similar to Mahshoub *et al* [@Mahsoub2017] with modifications.
+The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number (GCN)/mL, similar to Mahshoub *et al* [@Mahsoub2017] with modifications.
 Cells were infected in triplicates at a multiplicity of infection (MOI) of 100 GCN/cell, incubate at 41^o^C for 1 hour, and washed three times to get rid of free virion particles.
@@
 
-Our sequence reads were analyzed following a well established protocol described by Pertea *et al* [@Pertea2016], using `Snakemake - version 7.24.0` [@Snakemake2021], a popular workflow management system to drive the pipeline.
+Our sequence reads were analyzed following a well-established protocol described by Pertea *et al* [@Pertea2016], using `Snakemake - version 7.24.0` [@Snakemake2021], a popular workflow management system to drive the pipeline.
 Briefly, sequencing reads were trimmed with the `Trim-galore - version 0.6.6` [@TrimGalore] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
@@
 ## SUPPLEMENTARY MATERIALS    
+File attached separately
 
@@
 
-Data is available on request by contacting the designated corresponding author
+Data is also available on request by contacting the designated corresponding author
 
-### CODE AVAILABILITY
+## CODE AVAILABILITY
 All the code/scripts in the entire analysis pipeline are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>) 
@@
 `Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here 
-`BYU high performance computing systems` - Memory intensive analysis were run here.
+`BYU high performance computing systems` - Memory-intensive analysis were run here.
 \newpage

### 2024-01-31 README.Rmd
Continue writing manuscript; write scripts to insert stats
made standalone fig6-10

@@
 
-total_mapped <- round(sum(cov_all$numreads)/1e6)
+total_mapped <- round(sum(cov_all$numreads) / 1e6, 2)
 ```
@@
 
-**Hemorrhagic enteritis (HE)** is a disease affecting 6-12-week-old turkeys characterized by bloody diarrhea, **immunosuppression (IS)**, and up to 60% mortality.
-This disease is caused by **_Turkey Hemorrhagic Enteritis Virus (THEV)_** of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
+Hemorrhagic enteritis (HE) is a disease affecting 6-12-week-old turkeys characterized by immunosuppression, bloody diarrhea, and up to 80% mortality.
+This disease is caused by *Turkey Hemorrhagic Enteritis Virus* (THEV) of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
 The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
-**_Our objective is to understand the genetic basis by which VAS brings about IS_**.
-However, the **transcriptome of THEV** has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical as the viral splicing and gene expression patterns are unknown.
-To identify such viral factors, a well-characterized transcriptome of THEV is required to set the stage for experimentation with specific viral genes that may mediate IS.
+Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts leading to substantial economic losses.
+To mitigate this side effect, it is imperative that the viral genes mediating this immunosuppression be well characterized.
+However, the transcriptome of THEV has not been studied, making the investigation of specific viral genes for possible roles in causing this immunosuppression impractical.
+As the viral splicing and gene expression patterns are unknown, the most pressing need was for a well-characterized transcriptome of THEV to set the stage for experimentation with specific viral genes that may mediate the immunosuppression.
 

### 2024-01-31 manuscript_thev_transcriptome.Rmd
made standalone fig6-10

@@
 output:
-  word_document:
+  officedown::rdocx_document:
     reference_docx: style_word_output.docx
@@
 For individual junctions, we counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads at the given time point.
-At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table 1a**).
+At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table S1a**).
 The topmost abundant junctions at 12 h.p.i remained the most significantly expressed at 24 h.p.i also.
-However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table 1b**).
-At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall -- accounting for `r round(most_sig_72, 1)`% of all junction reads, -- but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table 1c** and **Figure 4c**).
+However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table S1b**).
+At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall -- accounting for `r round(most_sig_72, 1)`% of all junction reads, -- but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table S1c** and **Figure 4c**).
 When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (**Figure 4d**).
@@
 See **Supplementary Computational Analysis** for the details of transcript expression level estimations and splice junction read counts.
-\newpage
-
-## SUPPLEMENTARY MATERIALS    
-File attached separately
 
 ### DATA AVAILABILITY
+
 The raw sequence data (FastQ), transcript expression counts, and total unique junctions have been deposited at the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
@@
 ```
+\newpage
 ## TABLES AND FIGURES
@@
 
-```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e1_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi",
-                             "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               splice_site = "Splice Donor-Acceptor",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5)) %>%
-  footnote(., i = 1, j = 11, value = as_paragraph(c("Not validated for TRXPT_4")),
-           ref_symbols = c("*"), part = "body")
-
-brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(2, 0.05, 2)) 
-#+
-  # plot_annotation(tag_levels = "A") &
-  # theme(plot.tag = element_text(size = 22, face = "bold"))
-```
+![](results/r/figures/figure_6.png)
 **Figure 6: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
@@
 The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
-```{r region-by-region_e2andim_figure, fig.height=16, fig.width=18, warning=FALSE}
-set_flextable_defaults(font.size = 7)
-ft <- reg_e2_brkdown %>%
-  mutate(splice_site = ifelse(splice_site == "CT-AC, GT-AG",
-                              "GT-AG", splice_site)) %>% 
-  flextable(.,
-            col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi",
-                             "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Donor-Acceptor",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 2, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
-                                                                  width = 1.5))
 
-brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1.2, 0.05, 1.5))
-```
+![](results/r/figures/figure_7.png)
 **Figure 7: The splice map of the E2 and IM TUs**.
@@
 
-```{r region-by-region_e3, fig.height=16, fig.width=18, warning=FALSE}
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e3_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi",
-                             "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Donor-Acceptor",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 2, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
-                                                                  width = 1.5))
-
-brkdwn_e3_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1.5, 0.05, 1))
-```
+![](results/r/figures/figure_8.png)
 **Figure 8: The splice map of the E3 TU.** Exons are depicted as boxes connected by introns (dotted lines).
@@
 
-```{r region-by-region_e4_figure, fig.height=5, fig.width=8, warning=FALSE}
-reg_e4_brkdown <- reg_e4_brkdown %>%
-  mutate(splice_site = "GT-AG",
-         `4hpi` = as.numeric(`4hpi`), `12hpi` = as.numeric(`12hpi`),
-         `24hpi` = as.numeric(`24hpi`), `72hpi` = as.numeric(`72hpi`)) %>%
-  # select(-c(coding_potential, region)) %>%
-  group_by(trxpt_id, start, end, splice_site, intron_len, strand, status) %>%
-  reframe("4hpi" = sum(`4hpi`),
-          "12hpi" = sum(`12hpi`),
-          "24hpi" = sum(`24hpi`),
-          "72hpi" = sum(`72hpi`)) %>%
-  select(trxpt_id, start, end, splice_site, intron_len, strand, "4hpi", "12hpi",
-         "24hpi", "72hpi", status)
-
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_e4_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
-                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Donor-Acceptor",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5))
-
-brkdwn_e4_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(1, 0.01, 1)) +
-  plot_annotation(tag_levels = "A") &
-  theme(plot.tag = element_text(size = 18, face = "bold"))
-```
+![](results/r/figures/figure_9.png)
 **Figure 9: The splice map of the E4 TU.** Exons are depicted as boxes connected by introns (dotted lines).
@@
 
-```{r region-by-region_mlp_figure, fig.height=16, fig.width=18, warning=FALSE}
-set_flextable_defaults(font.size = 7)
-ft <- flextable(reg_mlp_brkdown,
-                col_keys = c("trxpt_id", "start", "end", "splice_site",
-                             "intron_len","strand", "4hpi", "12hpi",
-                             "24hpi", "72hpi", "status")) %>%
-  theme_zebra() %>%
-  flextable::set_table_properties(layout = "fixed",
-                       opts_pdf = list(caption_repeat = F)) %>%
-  flextable::set_header_labels(start = "Start", end = "End",
-                               splice_site = "Splice Donor-Acceptor",
-                               strand = "Strand", trxpt_id = "Transcript ID",
-                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
-                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
-  flextable::align(align = "center", part = "all") %>%
-  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                 colwidths = c(1, 4, 1, 4, 1)) %>%
-  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                  width = 1.5)) %>%
-  flextable::width(width = 0.3) %>%
-  flextable::width(j = 1, width = 1.5)
-
-brkdwn_mlp_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
-  plot_layout(heights = c(2.5, 0.02, 1.2))
-```
+![](results/r/figures/figure_10.png)
 **Figure 10: The splice map of the MLTU.** Exons are depicted as boxes connected by introns (dotted lines).
@@
 ```
+\newpage
+## SUPPLEMENTARY MATERIALS
+
+**Supplementary Table S1A**
+
+```{r Sup Table S1A}
+set_flextable_defaults(font.size = 8)
+make_reg_stats_table <- function(tp_table){
+  return(tp_table %>%
+    select(-junc_freq) %>% 
+    mutate(region = ifelse(is.na(region), "Unassigned", region)) %>% 
+    flextable() %>% 
+    theme_zebra() %>% 
+    set_header_labels(timepoint = "Time", region = "Region", strand = "Strand",
+                      sum_reads_reg = "Total Reads", perc_reg = "Percentage") %>% 
+    flextable::width(width = 0.8) %>% 
+    flextable::align(align = "center", part = "all") %>%
+    flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = FALSE),
+                       opts_word = list(split = F))
+  )
+}
+make_reg_stats_table(tp_reg_expr_12) %>%
+  set_caption("Table S1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")
+
+```
+
+**Supplementary Table S1B**
+
+```{r Sup Table S1B}
+set_flextable_defaults(font.size = 8)
+make_reg_stats_table(tp_reg_expr_24) %>%
+  set_caption("Table S1b: Most Transcriptionally Active Regions of THEV at 24h.p.i")
+```
+
+**Supplementary Table S1C**
+
+```{r Sup Table S1C}
+set_flextable_defaults(font.size = 8)
+make_reg_stats_table(tp_reg_expr_72) %>%
+  set_caption("Table S1c: Most Transcriptionally Active Regions of THEV at 72h.p.i")
+```
+
+\newpage
+**Supplementary PCR Methods**
+```{r Supplementary PCR Methods}
+set_flextable_defaults(font.size = 3.5)
+
+supp_pcr_meth_tab %>% 
+  select(-valid_status) %>% 
+flextable() %>%
+  theme_zebra() %>%
+  set_header_labels(trxpt_id = "Transcript ID", region = "Region", num_exons = "Number of Exons",
+                    full_trxpt = "Full Transcript", exon1 = "Exon 1", exon2 = "Exon 2",
+                    exon3 = "Exon 3", exon4 = "Exon 4", exon5 = "Exon 5", exon6 = "Exon 6",
+                    exon7 = "Exon 7", forwardP = "Forward Primer", reverseP = "Reverse Primer",
+                    gel_image = "Agarose Gel") %>% 
+  flextable::fontsize(j = c("full_trxpt", "exon1", "exon2", "exon3",
+                            "exon4", "exon5", "exon6", "exon7",
+                            "forwardP", "reverseP"), size = 3) %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::width(., width = 0.35) %>% 
+  colformat_image(j = "gel_image", i = c(1:3, 5:26, 28:30),
+                  width = 1.1, height = 1) %>%
+  flextable::width(j = ~forwardP, width = 1.1) %>%
+  flextable::width(j = ~reverseP, width = 1.1) %>%
+  flextable::width(j = ~gel_image, width = 1.15) %>%
+  # flextable::height(height = 0, part = "header") %>% 
+  footnote(., i = c(1:26, 28:30), j = 12, value = as_paragraph(c("Primer binds inside first exon")),
+           ref_symbols = c("a"), part = "body", inline = T) %>%
+  footnote(., i = c(1:7, 9:18, 21:26, 28, 29), j = 13, value = as_paragraph(c("Primer binds inside terminal exon")), ref_symbols = c("b"), part = "body", inline  = T) %>% 
+  # transcripts too long to validate with one primer pair
+  footnote(., i = c(8,19, 20, 30), j = 13, value = as_paragraph(c("Primer binds inside fourth exon")),
+           ref_symbols = c("c"), part = "body", inline = T) %>% 
+  footnote(., i = c(8), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_7 due to identical splicing")), ref_symbols = c("I"), part = "body", inline = T) %>%
+  footnote(., i = c(10), j = 14, value = as_paragraph(c("Agarose gel identical to last 3 exons of TRXPT_10 due to identical splicing")), ref_symbols = c("II"), part = "body", inline = T) %>%
+  footnote(., i = c(12), j = 14, value = as_paragraph(c("Agarose gel identical to last 4 exons of TRXPT_11 due to identical splicing")), ref_symbols = c("III"), part = "body", inline = T) %>% 
+  footnote(., i = c(16), j = 14, value = as_paragraph(c("Agarose gel dentical to TRXPT_23 due to identical splicing")), ref_symbols = c("IV"), part = "body", inline = T) %>% 
+  footnote(., i = c(19), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_9 due to identical splicing")), ref_symbols = c("V"), part = "body", inline = T) %>% 
+  footnote(., i = c(20), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_14 due to identical splicing")), ref_symbols = c("VI"), part = "body", inline = T) %>%
+  flextable::set_table_properties(layout = "fixed", align = "left",
+                       opts_pdf = list(caption_repeat = F),
+                       opts_word = list(split = F)) %>%
+  set_caption("Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
+```
+
+In the table above, the restriction sites in the primer tails are shown in lowercase letters.
+All the primer melting temperatures (TMs) are 58-60^o^C using a hot start Taq DNA polymerase.
+The PCR reaction mix was done per manufacturer's instructions.
+The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (53^o^C-56^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes.
+We used 35 cycles of amplification.
+
+**Supplementary Computational Analysis**    
+`Snakemake v7.24.0` was used to manage our entire workflow.
+A graph of the main steps in our pipeline generated with `Snakemake` is shown below.
+Our trimmed RNA-seq reads were mapped to the genome of _M.
+gallopavo_ (with THEV's genome as one of its chromosomes) using `Hisat2`, to generate the alignment (BAM) files and `StringTie` used to assemble the transcriptome with a `GTF` annotation file containing the predicted THEV ORFs as a guide.
+The `GTF` annotation file was derived from a `GFF3` annotation file obtained from NCBI using `Agat - version 1.0.0`, a program for converting between many different file formats used in bioinformatics.
+However, the NCBI `GFF3` annotation file itself was first modified to remove all unimportant features, leaving only the ORFs.
+
+`StringTie` was also used to estimate the normalized expression levels (FPKM) of all the transcripts and `Ballgown` in `R` was used to perform statistical analysis and comparisons of the transcript expression levels, which instructive in understanding the temporal regulation THEV gene expression.
+
+In these steps above, each sample (replicate of each time point) was processed independently and merged only in the final transcriptome assembly or during analysis with `Ballgown`.
+In the subsequent steps described below, all samples for each time point were processed together.
+
+We used `RegTools` to extract and analyze the splice junctions in the BAM files.
+The command `regtools junctions extract` provides a wealth of information about all the splice sites in the BAM file provided such as: the start and end positions, the strand, and number of reads supporting the splice junctions.
+The command `regtools junctions annotate` gives even more information such as: the splice site donor-acceptor sequences and transcripts/genes that overlap the junction.
+These information was the basis for estimating and comparing the splicing activity of different regions (TUs) of THEV over time.
+Also, `Samtools` was also used to count the total sequencing reads for all replicates at each time point.
+
+![](project_map.png)

### 2024-01-31 supplementary_thev_trxptome.Rmd
made standalone fig6-10

@@
 output: 
-  word_document: default
+  officedown::rdocx_document:
+    reference_docx: style_word_output.docx
   pdf_document: default
@@
 
-## Supplementary Table 1A
+## Supplementary Table S1A
 
-```{r Sup Table 1A}
+```{r Sup Table S1A}
 set_flextable_defaults(font.size = 8)
@@
 make_reg_stats_table(tp_reg_expr_12) %>%
-  set_caption("Table 1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")
+  set_caption("Table S1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")
 
@@
 
-## Supplementary Table 1B
+## Supplementary Table S1B
 
-```{r Sup Table 1B}
+```{r Sup Table S1B}
 set_flextable_defaults(font.size = 8)
 make_reg_stats_table(tp_reg_expr_24) %>%
-  set_caption("Table 1b: Most Transcriptionally Active Regions of THEV at 24h.p.i")
+  set_caption("Table S1b: Most Transcriptionally Active Regions of THEV at 24h.p.i")
 ```
 
-## Supplementary Table 1C
+## Supplementary Table S1C
 
-```{r Sup Table 1C}
+```{r Sup Table S1C}
 set_flextable_defaults(font.size = 8)
 make_reg_stats_table(tp_reg_expr_72) %>%
-  set_caption("Table 1c: Most Transcriptionally Active Regions of THEV at 72h.p.i")
+  set_caption("Table S1c: Most Transcriptionally Active Regions of THEV at 72h.p.i")
 ```
@@
                        opts_word = list(split = F)) %>%
-  set_caption("Table 1: Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
+  set_caption("Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
 ```

### 2024-01-31 scripts/r/plot_fig6_10.R

@@ -1,0 +1,96 @@
+#!/usr/bin/env Rscript
+
+library(flextable)
+source("scripts/r/abundance_analyses.R")
+source("scripts/r/reg_by_reg_plots.R")
+
+# plot the transcript breakdown for each TU
+
+# function to plot figures
+plot_figs <- function(trxpt_table, trxpt_plot){
+  
+  set_flextable_defaults(font.size = 7)
+  
+  # prepare junction table
+  junc_tab <- trxpt_table %>% 
+    mutate(splice_site = ifelse(splice_site == "CT-AC, GT-AG",
+                                "GT-AG", splice_site)) %>% 
+    flextable(.,
+            col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
+                         "strand", "4hpi", "12hpi", "24hpi", "72hpi",
+                         "status")) %>%
+    theme_zebra() %>%
+    flextable::set_table_properties(layout = "fixed",
+                                    opts_pdf = list(caption_repeat = F)) %>%
+    flextable::set_header_labels(start = "Start", end = "End",
+                                 strand = "Strand", trxpt_id = "Transcript ID",
+                                 intron_len = "Intron Length", "4hpi" = "4h.p.i",
+                                 "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
+                                 splice_site = "Splice Donor-Acceptor",
+                                 "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
+    flextable::align(align = "center", part = "all") %>%
+    add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
+                   colwidths = c(1, 4, 1, 4, 1)) %>%
+    flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
+                                                                    width = 1.5)) 
+  
+  if ("TRXPT_1, TRXPT_4" %in% pull(trxpt_table, trxpt_id)){
+    junc_tab <- junc_tab %>%
+    footnote(., i = 1, j = 11, value = as_paragraph(c("Not validated for TRXPT_4")),
[…]

### 2024-01-31 scripts/r/plot_thev_timepoint_splicing.R

@@ -221,7 +221,7 @@ total_plots <- total_plots + plot_annotation(tag_levels = list(c("A", "", "B"), 
 
 ggsave(plot = total_plots,
        filename = "results/r/figures/figure3.png",
-       dpi = 500, width = 12, height = 20)
+       dpi = 500, width = 14, height = 20)
 
 # ggsave(plot = all_tp_plots,
 #        filename = "results/r/figures/thev_patched_timepoints_spliced_map.png",

### 2024-01-31 scripts/r/reg_by_reg_plots.R

@@ -466,31 +466,31 @@ brkdown_reg_plots <- function(reg, reg2=NULL){
                 label.size = NA, label.padding = unit(0, "pt"), fill = NA) +
   # start codon positions
   geom_richtext(aes(x = sstcodon, y = ypos, label = glue("|")),
-                size = 5, label.size = NA, label.padding = unit(0, "pt"),
+                size = 6, label.size = NA, label.padding = unit(0, "pt"),
                 fill = NA, nudge_y = offset_y/2) +
   geom_richtext(aes(x = sstcodon, y = ypos, label = glue("<sup>SSC ({sstcodon})</sup>")),
-                size = 3.5, label.size = NA, label.padding = unit(0, "pt"),
+                size = 4.5, label.size = NA, label.padding = unit(0, "pt"),
                 fill = NA, nudge_y = offset_y, hjust = ljust) +
   # stop codon positions
   geom_richtext(aes(x = stpcodon, y = ypos, label = glue("|")),
-                size = 5, label.size = NA, label.padding = unit(0, "pt"),
+                size = 6, label.size = NA, label.padding = unit(0, "pt"),
                 fill = NA, nudge_y = offset_y/2) +
     geom_richtext(aes(x = stpcodon, y = ypos, label = glue("<sup>STC ({stpcodon})</sup>")),
-                  size = 3.5, label.size = NA, label.padding = unit(0, "pt"),
+                  size = 4.5, label.size = NA, label.padding = unit(0, "pt"),
                   fill = NA, nudge_y = offset_y, hjust = rjust) +
     # secondary start codon positions
     geom_richtext(aes(x = secSSC, y = ypos, label = glue("|")),
-                  size = 5, label.size = NA, label.padding = unit(0, "pt"),
+                  size = 6, label.size = NA, label.padding = unit(0, "pt"),
                   fill = NA, nudge_y = -offset_y) +
     geom_richtext(aes(x = secSSC, y = ypos, label = glue("<sup>secSSC ({secSSC})</sup>")),
-                  size = 3.5, label.size = NA, label.padding = unit(0, "pt"),
+                  size = 4.5, label.size = NA, label.padding = unit(0, "pt"),
                   fill = NA, nudge_y = -offset_y*1.5, hjust = ljust) +
     # secondary stop codon positions
     geom_richtext(aes(x = secSTC, y = ypos, label = glue("|")),
[…]

### 2024-02-25 scripts/r/plot_fig6_10.R
scripts; changed splice site labels from T ot U

@@ -13,8 +13,9 @@ plot_figs <- function(trxpt_table, trxpt_plot){
   
   # prepare junction table
   junc_tab <- trxpt_table %>% 
-    mutate(splice_site = ifelse(splice_site == "CT-AC, GT-AG",
-                                "GT-AG", splice_site)) %>% 
+    # change thymines to uracils to match RNA
+    mutate(splice_site = dplyr::case_when(splice_site %in% c("CT-AC, GT-AG", "GT-AG") ~ "GU-AG",
+                                          splice_site == "GT-GC" ~ "GU-GC")) %>% 
     flextable(.,
             col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
                          "strand", "4hpi", "12hpi", "24hpi", "72hpi",
@@ -32,7 +33,8 @@ plot_figs <- function(trxpt_table, trxpt_plot){
     add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                    colwidths = c(1, 4, 1, 4, 1)) %>%
     flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                    width = 1.5)) 
+                                                                    width = 1.5)) %>%
+    flextable::font(part = "all", fontname = "Arial")
   
   if ("TRXPT_1, TRXPT_4" %in% pull(trxpt_table, trxpt_id)){
     junc_tab <- junc_tab %>%
@@ -41,7 +43,7 @@ plot_figs <- function(trxpt_table, trxpt_plot){
   }
   
   # combine with trxpt plot
-  trxpt_plot / plot_spacer()/ gen_grob(junc_tab, fit = "auto", scaling = "full")
+  return(trxpt_plot / plot_spacer()/ gen_grob(junc_tab, fit = "auto", scaling = "full"))
 }
 
 # Figure 6
@@ -80,17 +82,16 @@ fig9 <- plot_figs(reg_e4_brkdown, brkdwn_e4_trxtps) +
 fig10 <- plot_figs(reg_mlp_brkdown, brkdwn_mlp_trxtps) +
   plot_layout(heights = c(2.5, 0.02, 1.2))
 
-figures <- list(fig6, fig7, fig8, fig9, fig10)
+figures <- list(fig6, fig7, fig8, fig10)
+fig_str <- list("fig6", "fig7", "fig8", "fig10")
 
 for(p in seq_along(figures)){
[…]

### 2024-02-25 scripts/r/reg_by_reg_plots.R

@@ -6,7 +6,6 @@ library(glue)
 library(rtracklayer)
 library(patchwork)
 library(ggtext)
-library(ggbrace)
 library(plyr)
 library(tidyverse)
 library(ballgown)
@@ -468,7 +467,7 @@ brkdown_reg_plots <- function(reg, reg2=NULL){
   geom_richtext(aes(x = sstcodon, y = ypos, label = glue("|")),
                 size = 6, label.size = NA, label.padding = unit(0, "pt"),
                 fill = NA, nudge_y = offset_y/2) +
-  geom_richtext(aes(x = sstcodon, y = ypos, label = glue("<sup>SSC ({sstcodon})</sup>")),
+  geom_richtext(aes(x = sstcodon, y = ypos, label = glue("<sup>SC ({sstcodon})</sup>")),
                 size = 4.5, label.size = NA, label.padding = unit(0, "pt"),
                 fill = NA, nudge_y = offset_y, hjust = ljust) +
   # stop codon positions
@@ -482,7 +481,7 @@ brkdown_reg_plots <- function(reg, reg2=NULL){
     geom_richtext(aes(x = secSSC, y = ypos, label = glue("|")),
                   size = 6, label.size = NA, label.padding = unit(0, "pt"),
                   fill = NA, nudge_y = -offset_y) +
-    geom_richtext(aes(x = secSSC, y = ypos, label = glue("<sup>secSSC ({secSSC})</sup>")),
+    geom_richtext(aes(x = secSSC, y = ypos, label = glue("<sup>secSC ({secSSC})</sup>")),
                   size = 4.5, label.size = NA, label.padding = unit(0, "pt"),
                   fill = NA, nudge_y = -offset_y*1.5, hjust = ljust) +
     # secondary stop codon positions
@@ -503,7 +502,7 @@ brkdwn_e3_trxtps <- brkdown_reg_plots("E3")
 
 brkdwn_e4_trxtps <- brkdown_reg_plots("E4")
 
-brkdwn_im_trxtps <- brkdown_reg_plots("IM")
+# brkdwn_im_trxtps <- brkdown_reg_plots("IM")
 
 brkdwn_mlp_trxtps <- brkdown_reg_plots("MLP")
 

### 2024-02-25 scripts/r/thev_cov_depth.R

@@ -109,7 +109,6 @@ ggsave("patch_alltimes.png",
 
 comp_all <- all_depths %>%
   select(timepoint, position, depth) %>% 
-  mutate(depth = ifelse(depth < 1, 1, depth)) %>% 
   ggplot(aes(position, sqrt(depth), group = timepoint, fill = timepoint, color = timepoint)) +
   geom_area(key_glyph = "crossbar") +
   scale_fill_igv(guide = guide_legend(keywidth = unit(1, "cm"))) +

### 2024-02-25 manuscript_thev_transcriptome.Rmd
modified acknowledgment section
implemented prof edits to manuscript to submit

@@
 ---
-title: Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus
+title: Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line
 output:
@@
   - \usepackage{float}
+  - \usepackage{placeins}
   - \usepackage{colortbl}
@@
   - \usepackage{xcolor}
+  - \usepackage{caption}
+  - \usepackage[labelformat=empty]{caption}
 bibliography: transcriptome_refs.bib
@@
 ---
+\captionsetup[table]{labelformat=empty}
 
@@
 
-Abraham Quaye^1\*^, Brett Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
+Abraham Quaye^1\*^, Brett E. Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
 
@@
 knitr::opts_chunk$set(tab.cap.pre = "", tab.cap.sep = "")
-
-inline_hook <- function(x) {
-  if(is.numeric(x)){
-    formatted <- format(x, big.mark = ",")
-  }else{formatted <- x}
-  paste0("**", formatted, "**")
-}
-knit_hooks$set(inline = inline_hook)
 ```
@@
 
-We have performed an RNA-sequencing experiment characterizing the transcriptome of turkey hemorrhagic enteritis virus (THEV) for the first time, yielding the only insight into THEV's gene expression patterns.
-Previously, THEV's genome had been predicted to encode 23 open reading frames (ORFs).
-In this work we identified 29 transcripts from our RNA-seq data all of which consisted of novel exons albeit some exons matched the predicted ORFs.
-The three predicted splice junctions were also corroborated by our data.
-We performed PCR amplification of THEV cDNA and cloned the PCR products, and Sanger sequencing was used to validate all identified splice junctions.
-During validation, we identified 5 additional transcripts some of which were further validated by 3'RACE data.
-Thus, the transcriptome of THEV consists of 34 unique transcripts with the coding capacity for all predicted ORFs.
-However, we found 6 predicted ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated predictions as either an in-frame upstream start codon was identified or additional coding exons were found.
-We also identified 3 predicted ORFs with longer or shorter isoforms, and 7 novel unpredicted ORFs that could be encoded by some transcripts; albeit it is beyond the scope of this manuscript to investigate whether they get translated.
-Similar to other adenoviruses, THEV also produce multiple distinctly spliced transcripts that code for the same protein across its genome.
-Also, our data shows that all THEV transcripts are spliced, and organized in five transcription units under the control of their cognate promoter.
-However, our data suggests that THEV's temporal regulation may be different from other adenoviruses.
-Over 2,300 unique splice junctions were found across the genome, mostly at low levels.
-This low-level use of broad alternative splicing patterns is thought to enable the virus to maximize its coding potential in an evolving environment.
+Characterizing the splice map of turkey hemorrhagic enteritis virus (THEV) is an essential step that would allow studies of individual genes mediating its immunosuppressive functions.
+We used an RNA-sequencing experiment to characterize the transcriptome of THEV for the first time, providing key insight into the THEV gene expression and mRNA structures.
+Researchers previously annotated THEV's genome as encoding 23 open reading frames (ORFs).
+In this work we identified 29 spliced transcripts all of which consisted of novel exons although some exons matched some previously annotated ORFs.
+The three annotated splice junctions were also corroborated by our data.
+We performed PCR amplification of THEV cDNA, cloned the PCR products, and used Sanger sequencing to validate all identified splice junctions.
+During validation we identified five additional unique transcripts, a subset of which were further validated by 3' rapid amplification of cDNA ends (3' RACE) experiments.
+Thus, we report that the genome of THEV contains 34 unique transcripts with the coding capacity for all annotated ORFs.
+However, we found six of the previously annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated ORFs on the basis of the identification of an in-frame upstream start codon or the detection of additional coding exons.
+We also identified three of the annotated ORFs with longer or shorter isoforms, and seven novel unpredicted ORFs that could potentially be translated; although it is beyond the scope of this manuscript to investigate whether they are translated.
+Similar to other adenoviruses (AdVs), THEV also produces multiple distinctly spliced transcripts that code for the same proteins across its genome.
+Our data show that all THEV transcripts are spliced and organized into five transcription units under the control of their cognate promoters like other AdVs.
+However, our data suggest that the temporal regulation of THEV may be different from other AdVs.
 \newpage
@@
 
-Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all vertebrates.
+Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses, causing infection in virtually all types of vertebrates studied to date.
 Their double-stranded linear DNA genomes range between 26 and 45kb in size, producing a broad repertoire of transcripts via highly complex alternative splicing patterns [@Davison2003; @Harrach2008].
@@
 All other genes are termed "genus-specific".
-"Genus-specific" genes tend to be located at the termini of the genome while "genus-common" genes are usually central [@Davison2003].
-This pattern is observed in *Adenoviridae*, *Poxviridae*, and *Herpesviridae* [@Davison2003; @Upton2003; @McGeoch1999].
-The family *Adenoviridae* consists of five genera: *Mastadenovirus* (MAdV), *Aviadenovirus*, *Atadenovirus*, *Ichtadenovirus*, and *Siadenovirus* (SiAdV) [@Harrach2011; @Guimet2016].
-Currently, there are three recognized members of the genus SiAdV: frog adenovirus 1, raptor adenovirus 1, and turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009].
-Members of SiAdV have the smallest genome size (\~26 kb) and gene content (\~23 genes) of all known AdVs, and many "genus-specific" putative genes of unknown functions have been annotated (see **Figure 1**)[@Harrach2008; @Kovács2011; @Davison2003].
+The genus-specific genes tend to be located at the termini of the genome while genus-common genes are usually towards the center of the genome [@Davison2003].
+This pattern is also observed in *Poxviridae* and *Herpesviridae*, which also have linear DNA genomes [@Davison2003; @Upton2003; @McGeoch1999].
+The family *Adenoviridae* consists of five genera: *Mastadenovirus* (MAdV), *Aviadenovirus*, *Atadenovirus*, *Ichtadenovirus*, and *Siadenovirus* (SiAdV) to which turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) belongs [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009; @Guimet2016].
+Members of SiAdV have the smallest genome size (\~26 kb) and gene content of all known AdVs (see **Figure 1**) [@Harrach2008; @Kovács2011; @Davison2003].
 
-Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV are serologically indistinguishable, infecting turkeys, chickens, and pheasants, with the THEV-V causing different clinical diseases in these birds [@Harrach2008; @Beach2006].
-In turkeys, the THEV-V cause hemorrhagic enteritis (HE), a debilitating acute disease affecting predominantly 6-12-week-old turkeys characterized by immunosuppression (IS), weight loss, intestinal lesions leading to bloody diarrhea, splenomegaly, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967].
-HE is the most economically significant disease caused by any strain of THEV [@Beach2006].
-While the current vaccine strain (a THEV-A isolated from a pheasant, Virginia Avirulent Strain [VAS]) has proven effective at preventing HE in young turkey poults, it still retains the immunosuppressive ability.
-Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
-To eliminate this immunossupressive side-effect of the vaccine, a thorough investigation of the culprit viral factors (genes) mediating this phenomenon is essential.
-However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making the investigation of specific viral genes for possible roles in causing IS impractical.
-A well-characterized transcriptome of THEV is required to enable experimentation with specific viral genes that may mediate IS.
+Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV both infect turkeys, with THEV-V causing hemorrhagic enteritis (HE), a debilitating acute disease predominantly affecting turkey poults characterized by immunosuppression (IS), intestinal lesions leading to bloody diarrhea, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967; @Harrach2008].
+While the current vaccine strain (a THEV-A strain isolated from a pheasant; Virginia Avirulent Strain [VAS]) has proven effective at preventing HE in turkey poults, it still retains its immunosuppressive ability.
+Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated birds leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
+To eliminate the immunossupressive effect of the vaccine strain, a thorough investigation of the culprit viral genes mediating this phenomenon is essential.
+However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making an investigation of specific IS-related viral genes impractical.
 
-Myriads of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
+A myriad of studies have elucidated the AdV transcriptome in fine detail [@Donovan2020; @Zhao2014].
 However, a large preponderance of studies focus on MAdVs -- specifically human AdVs.
 Thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV genes are transcribed in a temporal manner; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late unit (MLTU or major late promoter [MLP] region), which generates five families of late mRNAs (L1-L5) based on the polyadenylation site.
+MAdV transcription is temporally regulated; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late transcription unit (MLTU or major late promoter [MLP] region), which generates five families of late mRNAs (L1-L5) based on the polyadenylation site.
 An additional gene (UXP or U exon) is located on the reverse strand.
-The early genes encode non-structural proteins such as enzymes or host cell modulating proteins, primarily involved in DNA replication, or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins that act as capsid proteins, promote virion assembly, and direct genome packaging.
-The immediate early gene E1A is expressed first, followed by the the delayed early genes, E1B, E2, E3 and E4.
+The early genes encode non-structural proteins such as enzymes or host-cell modulating proteins, primarily involved in DNA replication, or providing the necessary intracellular niche for optimal replication while late genes encode structural proteins that act as capsid proteins, promote virion assembly, or direct genome packaging.
+The immediate early genes E1A are expressed first, followed by the delayed early genes, E1B, E2, E3 and E4.
 Then the intermediate early genes, IVa2 and pIX are expressed followed by the late genes [@Zhao2014; @Donovan2020; @Guimet2016].
-Noteworthily, the MLP shows basal transcriptional activity during early infection (before DNA replication), with a comparable efficiency to other early viral promoters, but reaches its maximal activity during late infection (after DNA replication).
-However, during early infection the repertoire of late transcripts from the MLP is restricted until late infection [@Guimet2016].
+It is noteworthy that the MLP shows basal transcriptional activity during early infection (before DNA replication), with a comparable efficiency to other early viral promoters, but it reaches its maximal activity during late infection (after DNA replication).
+However, during early infection only a subset of the MLP-derived transcripts are expressed [@Guimet2016].
 MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs.
 All but the pIX mRNA undergo at least one splicing event.
-For instance, the MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader, TPL) [@Donovan2020; @Zhao2014].
-There is also an alternate 5' three non-coding exons present in varying amounts on a subset of MLTU mRNAs (known as the x-, y- and z-leaders).
+For instance, the MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader; TPL) [@Donovan2020; @Zhao2014].
+There is also an alternate three-exon 5' non-coding leader sequence present in varying amounts on a subset of MLTU mRNAs (known as the x-, y-, and z-leaders).
 Lastly, there is the i-leader exon, which is infrequently included between the second and third TPL exons, and codes for the i-leader protein [@Falvey1983].
 Thus, the MLTU produces a complex repertoire of mRNA with diverse 5' untranslated regions (UTRs) spliced onto different 3' coding exons which are grouped into five different 3'-end classes (L1-L5) based on polyadenylation site.
-Each transcription unit (TU) contains its own promoter driving the expression of all the array of mRNA transcripts produced via alternative splicing in the unit [@Zhao2014; @Donovan2020; @Guimet2016].
+Each transcription unit (TU) contains its own promoter driving the expression of the array of mRNA transcripts produced via alternative splicing in the unit [@Zhao2014; @Donovan2020; @Guimet2016].
 The promoters are activated at different phases of the infection by proteins from previously activated TUs.
-Paradoxically, the early-to-late phase transition during infection requires the L4 genes, 22K and 33K, which should only be available after the transition.
+Paradoxically, the early-to-late phase transition during infection requires the L4 gene products, 22K and 33K, which should only be available after the transition.
 However, a promoter in the L4 region (L4P) that directs the expression of these two proteins independent of the MLP was found, resolving the paradox [@Morris2010; @Guimet2016; @Donovan2020].
-During translation of AdV mRNA, recent studies strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020; @Westergren2021].
+During translation of AdV mRNA, recent studies using long-read direct RNA sequencing strongly suggest the potential usage of secondary start codons; adding to what was already a highly complex system for gene expression [@Donovan2020; @Westergren2021].
 
 High throughput sequencing methods have facilitated the discovery of many novel transcribed regions and splicing isoforms.
-It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014; Westergren2021].
-In this paper, a paired-end deep sequencing experiment was performed to characterize for the first time the transcriptome of THEV (VAS vaccine strain) during different phases of the infection, yielding the first THEV splicing map.
+It is also a very powerful tool to study alternative splicing under different conditions at an unparalleled depth [@Djebali2012; @Zhao2014; @Westergren2021].
+In this paper, we use a paired-end deep sequencing experiment to characterize, for the first time, the transcriptome and splicing of THEV (VAS vaccine strain) during different phases of the infection.
 Our paired-end sequencing allowed for reading `r seq_len` bp long high quality (mean Phred Score of 36) sequences from each end of cDNA fragments, which were mapped to the genome of THEV.
@@
 **Overview of sequencing data and analysis pipeline outputs**  
-A previous study by Aboezz *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours [@Aboezz2019].
-Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hours post-infection (h.p.i) to ensure an amply wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len`bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*Meleagris gallopavo*) genomes using the `Hisat2` [@Pertea2016] alignment program.
+A previous study by Aboezz *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours, with a full replication cycle of about 18-hours post infection (hpi) [@Aboezz2019].
+Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hpi  to ensure a wide time window to sample all transcripts.
+Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len` bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*Meleagris gallopavo*) genomes using the Hisat2 [@Pertea2016] reference-based aligner.
 A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
-The mapped reads to the virus genome increased substantially from `r cov_4hr` reads at 4 h.p.i to `r cov_72hr` million reads at 72 h.p.i (**Table 1**, **Figure 2a**).
+The mapped reads to the virus genome increased substantially from a mere `r cov_4hr` reads at 4 hpi to `r cov_72hr` million reads at 72 hpi (**Table 1**, **Figure 2A**).
 From the mapped reads, we identified a total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
-For example, all the `r tot_jun_4` unique junctions at 4 h.p.i had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads/junction.
-Conversely, the `r tot_jun_72` unique junctions at 72 h.p.i averaged `r mean_juncreads_72` reads/junction, some junctions having coverage as high as `r max_junread72` reads.
-The substantial increases in splice junction and mapping reads to the THEV genome over time denotes an active infection and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2b**).
+For example, all the `r tot_jun_4` unique junctions at 4 hpi had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads per junction.
+Conversely, the `r tot_jun_72` unique junctions at 72 hpi averaged `r mean_juncreads_72` reads per junction, some junctions having coverage as high as `r max_junread72` reads.
+The substantial increases in splice junction and mapping reads to the THEV genome over time denotes an active infection and a successful viral replication, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2B**).
 
-Using `StringTie` [@Pertea2016], an assembler of RNA-seq alignments into potential transcripts, the mapped reads for each time point were assembled into transcripts using the genomic location of the predicted THEV ORFs as a guide.
-In the consolidated transcriptome, a composite of all unredundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)-1` novel transcripts.
-Although some exons in some transcripts match the predicted ORFs exactly, most of our identified exons are longer, spanning multiple predicted ORFs (**Figure 3**).
+Using StringTie [@Pertea2016], we assembled the data into potential transcripts using the genomic location of the prior predicted THEV ORFs as a guide.
+In the consolidated transcriptome, a composite of all non-redundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)-1` novel transcripts.
+We found that a subset of exons in the viral transcripts match the predicted ORFs exactly, with the majority of the exons being longer and spanning multiple predicted ORFs (**Figure 3**).
 
-We validated the splice junctions in all transcripts by PCR amplification of viral cDNA, cloning, and Sanger sequencing (**Supplementary PCR methods**).
-During validation, we identified 5 additional transcripts some of which were further validated by 3' Rapid Amplification of cDNA Ends (3'RACE) data.
-The complete list of unique splice junctions mapped to THEV's genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
+We then validated the splice junctions in all transcripts by PCR amplification of viral cDNA, cloning, and Sanger sequencing (**Supplementary PCR methods**).
+During validation, we identified five additional transcripts, some of which were further validated by 3' Rapid Amplification of cDNA Ends (3' RACE) data.
+The complete list of unique splice junctions mapped to the THEV genome has been submitted to the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
 
 **Changes in THEV splicing profile over time**\
-AdV gene expression occurs under exquisite temporal control with each promoter typically producing one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts.
-To evaluate the activity of each promoter over time, `StringTie` and `Ballgown` (a program for statistical analysis of assembled transcriptomes) [@Ballgown] were used to estimate the normalized expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
-Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.
+AdV gene expression occurs under exquisite temporal control with each promoter typically producing one or few pre-mRNAs that undergo alternative splicing to yield a repertoire of mature mRNAs.
+To evaluate the activity of each promoter over time, StringTie and Ballgown (a program for statistical analysis of assembled transcriptomes) [@Ballgown] were used to estimate the normalized expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
+Very few unique splice junctions, reads, and transcripts were counted at 4 hpi; hence, this time point was excluded in this analysis.
 
@@
 
-Considering individual mRNAs, TRXPT_21 -- from the E2 region -- was the most significantly expressed at 12 h.p.i, constituting about `r abn_each_12`% of the total expression of all transcripts.
+Considering individual mRNAs, TRXPT_21 -- from the E2 region -- was the most significantly expressed at 12 hpi, constituting `r abn_each_12`% of the total expression of all transcripts.
 Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
-The later time points were dominated by the MLP region transcripts -- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 h.p.i, respectively, as expected (**Figure 4a**).
-When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 h.p.i, after which the MLP region assumes predominance (**Figure 4b**).
+The later time points were dominated by the MLP region transcripts -- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 hpi, respectively, as expected (**Figure 4A**).
+When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 hpi, after which the MLP region assumes predominance (**Figure 4B**).
 Secondly, we estimated relative abundances of all splice junctions at each time point using the raw reads.
-For individual junctions, we counted as significantly expressed only junctions with coverage of at least 1% of the total splice junction reads at the given time point.
-At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table S1a**).
-The topmost abundant junctions at 12 h.p.i remained the most significantly expressed at 24 h.p.i also.
+Only junctions with a read coverage of at least 1% of the total splice junction reads at the given time point were considered significant and included in **Tables 2a-2c**.
+At 12 hpi, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table S1a**).
+The most abundant junctions at 12 hpi remained the most significantly expressed at 24 hpi also.
 However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table S1b**).
-At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall -- accounting for `r round(most_sig_72, 1)`% of all junction reads, -- but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table S1c** and **Figure 4c**).
-When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was generally similar to the pattern seen with all the junctions included (**Figure 4d**).
+At 72 hpi, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall -- accounting for `r round(most_sig_72, 1)`% of all junction reads, -- but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table S1c** and **Figure 4C**).
+When we limited this analysis to only junctions in the final transcriptome, we observed the relative abundances of the junctions for each region over time to be similar to the pattern seen with all the junctions included (**Figure 4D**).
 
 We also analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
-We found that most splice donor-acceptor sequences were unsurprisingly the canonical GT-AG nucleotides.
-However, the splice acceptor-donor pairing became less specific over time, such that all combinations of nucleotide pairs were eventually detected (**Figure 5**)
+We found that most splice donor-acceptor sequences were unsurprisingly the canonical GU-AG nucleotides.
+However, the splice acceptor-donor pairing became less specific over time, such that all combinations of nucleotide pairs were eventually detected (**Figure 5**).
 
@@
 The host transcription machinery solely mediates the transcription of this region.
-After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016].
-In MAdVs, this region is subdivided into E1a and E2b units, but the transcripts found in our data categorized under this region do not appear to so divided.
+After their translation, the E1 proteins in concert with a myriad of host transcription factors activate other viral promoters [@Guimet2016].
+In MAdVs, this region is subdivided into E1a and E2b units, but the transcripts found in our data categorized under this region do not appear to be subdivided.
 
-Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r nrow(reg_e1_brkdown)` unique splice junctions (**Figure 6**).
+Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r english(nrow(reg_e1_brkdown))` unique splice junctions (**Figure 6**).
 Most of the ORFs of the novel transcripts are distinct from the predicted ORFs, but they all have the coding potential (CP) for the predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered as reported for other AdVs [@Donovan2020; @Zhao2014].
 The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a novel 17.9 kilodalton (kDa), 160 residue [amino acids (aa)] protein (ORF9).
-From its 5'-most start codon (SSC), TRXPT_2 encodes the largest protein in this region -- a 64.3 kDa, 580 aa protein (ORF10) with the same SSC as ORF9 (position 211bp).
-ORF10 spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655bp to 1964bp (ORF1's C-terminus, including the stop codon), and it's stop codon (STC; position 2312) is 13 bp short of Hyd's STC.
-However, it has an SSC 102 bp upstream and in-frame with ORF1's predicted SSC.
-Thus, ORF10 shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SSC of Hyd is not in-frame.
-Without its splice site removing the ORF1 STC, TRXPT_2 would encode a longer variant of ORF1, starting from an upstream SSC.
+From its 5'-most start codon (SC), TRXPT_2 encodes the largest protein in this region -- a 64.3 kDa, 580 aa protein (ORF10) with the same SC as ORF9 (position 211 bp).
+ORF10 spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 bp to 1964 bp (ORF1's C-terminus, including the stop codon), and its stop codon (STC; position 2312) is 13 bp short of the Hyd STC.
+However, it has an SC 102 bp upstream and in-frame with ORF1's predicted SC.
+Thus, ORF10 shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SC of Hyd is not in-frame.
+Without its splice site removing the ORF1 STC, TRXPT_2 would encode a longer variant of ORF1, starting from an upstream SC.
 TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-Our RNA-seq data shows that all E1 transcripts share the same transcription termination site (TTS; at position 2325bp).
-However, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (E1 TSS; position: 54bp).
+Our RNA-seq data show that all E1 transcripts share the same transcription termination site (TTS; at position 2325 bp).
+However, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (E1 TSS; position: 54 bp).
 Given that studies in MAdVs show that E1 mRNAs share not only a common TTS but also the TSS, and only differ from each other regarding the internal splicing [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and their actual TSS just like the TTS are identical for all E1 transcripts.
-Regardless of the TSS considered for TRXPT_3, the coding potential (CP) remains unaffected.
-Its 5'-most CDS, beginning at 1965bp and sharing the same STC as ORF9, produces a 13.1 kDa, 115 residue protein (ORF4).
-ORF4 was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggests it is a bona fide ORF.
-Unlike TRXPT_3, the CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is the same as TRXPT_3 (ORF4 as the first CDS and Hyd as second CDS using the secondary SSC).
-However, if we assume that TRXPT_4 uses the E1 TSS, then the 5'-most CDS is a distinct, novel, multi-exonic 15.9 kDa, 143 aa protein (ORF11) with the same SSC as ORF9 and ORF10 but with a unique STC.
+Regardless of the TSS considered for TRXPT_3, the CP remains unaffected.
+Its 5'-most CDS, beginning at 1965 bp and sharing the same STC as ORF9, produces a 13.1 kDa, 115 residue protein (ORF4).
+ORF4 was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggest it is a genuinely expressed ORF.
+Unlike TRXPT_3, the CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is identical to TRXPT_3.
+However, if we assume that TRXPT_4 uses the E1 TSS, then the 5'-most CDS is a distinct, novel, multi-exonic 15.9 kDa, 143 aa protein (ORF11) with the same SC as ORF9 and ORF10 but with a unique STC.
+
 The splice junctions of all transcripts in this region (except the junction for TRXPT_4) were validated by cloning of viral cDNA and Sanger sequencing (**Supplementary PCR methods**).
-
-During the validation of TRXPT_2, ORF1 was present on the agarose gel (an unspliced band size) and Sanger sequencing results as a bona fide transcript (**Supplementary PCR methods**).
-This was corroborated by our 3'RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without any splicing, with a poly-A tail immediately after the E1 TTS.
+During the validation of TRXPT_2, we found ORF1 to be present on the agarose gel (an unspliced band size) and Sanger sequencing results showed it to be a transcribed mRNA (**Supplementary PCR methods**).
+This was corroborated by our 3' RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without any splicing, with a poly-A tail immediately after the E1 TTS.
 The 5'-most CDS of this transcript (TRXPT_2B) would encode ORF1.
-However, TRXPT_2B has an upstream and in-frame SSC to the predicted SSC of ORF1, suggesting that the predicted ORF1 CDS is truncated -- the actual ORF1 (eORF1) that is expressed shares the same SSC as ORF10, but has a unique STC.
+However, TRXPT_2B has an upstream and in-frame SC to the predicted SC of ORF1, suggesting that the predicted ORF1 CDS is truncated -- the actual ORF1 (eORF1) that is expressed shares the same SC as ORF10, but has a unique STC.
 
@@
 The E2 TU expressed on the anti-sense strand is subdivided into E2A and E2B and encodes three classical AdV proteins --  pTP and Ad-pol (E2B proteins), and DBP (E2A protein) -- essential for genome replication [@Donovan2020; @Zhao2014].
-Unlike MAdV where two promoters (E2-early and E2-late) are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751bp) from which both E2A and E2B transcription is initiated.
+Unlike MAdV where two promoters (E2-early and E2-late) are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751 bp) from which both E2A and E2B transcription is initiated.
 However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 7**).
@@
 Thus, TRXPT_21 is a three-exon transcript encoding DBP (380 residues, 43.3 kDa) precisely as predicted.
-This transcript (TRXPT_21) was also corroborated in a 3'RACE experiment.
-Additionally, from the 3'RACE, a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript was found.
-This new transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP (tDBP) because the SSC utilized by TRXPT_21, is followed shortly by STCs in the retained intron.
-The SSC 173 bp downstream of DBP's SSC yields tDBP (a 346 residue, 39.3 kDa product), which is in-frame of DBP but entirely contained in the second exon.
-TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine/thymine (A/T)-rich sequence before the poly-A tail sequence occur, suggesting this position (16,934bp) as the bona fide E2A TTS (**Figure 7**).
+This transcript (TRXPT_21) was also corroborated in a 3' RACE experiment.
+Additionally, from the 3' RACE data, we found a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript.
+This new transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP (tDBP) because the SC utilized by TRXPT_21, is followed shortly by STCs in the retained intron.
+The SC 173 bp downstream of the DBP SC yields tDBP (a 346 residue, 39.3 kDa product), which is in-frame of DBP but entirely contained in the second exon.
+TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine/thymine (A/T)-rich sequence before the poly-A tail sequence occurs, suggesting this position (16,934 bp) as the true E2A TTS (**Figure 7**).
 
-The E2B region transcripts also start with the E2-5'UTR but extend thousands of base pairs downstream to reach the TTS at 2334bp in the IM region, which is immediately followed by an A/T rich sequence (position 2323-2339bp) where polyadenylation probably occurs.
-Interestingly, the TTS of the E1 region (position 2,325bp) on the sense strand is also in the immediate vicinity of this A/T rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
-The E2B transcripts, TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 7**).
+The E2B region transcripts also start with the E2-5'UTR but extend thousands of base pairs downstream to reach the TTS at 2334 bp in the IM region, which is immediately followed by an A/T-rich sequence (position 2323-2339 bp) where polyadenylation probably occurs.
+Interestingly, the TTS of the E1 region (position 2,325 bp) on the sense strand is also in the immediate vicinity of this A/T-rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
+The E2B transcripts TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 7**).
 TRXPT_7 has the CP for both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
-The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel non-coding 5' exons, the third exon (containing the SSC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
-The first two exons are 5'-UTRs because the SSC here is immediately followed by STCs; thus, the 5'-most SSC (position 10,995bp) of the third exon which matches the predicted SSC of pTP is utilized.
+The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel non-coding 5' exons, the third exon (containing the SC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
+The first two exons are 5'-UTRs because the SC here is immediately followed by STCs; thus, the 5'-most SC (position 10,995 bp) of the third exon which matches the predicted SC of pTP is utilized.
 The encoded product is identical to the predicted pTP protein (597 residues; 70.5 kDa).
-If secondary SSC (secSSC) usage is considered, with SSC at 6768bp and STC at 3430bp, the encoded product is identical to the predicted Ad-pol (polymerase) protein (1112 residues; 129.2 kDa).
-TRXPT_6 differs from TRXPT_7 by containing an extra splice site at 3447-3515bp.
-However, the CP remains similar to that of TRXPT_7 except the Ad-pol encoded from the secSSC is a truncated isoform with a new STC resulting from the splice site.
+If secondary SC (secSC) usage is considered, with SC at 6768 bp and STC at 3430 bp, the encoded product is identical to the predicted Ad-pol (polymerase) protein (1112 residues; 129.2 kDa).
+TRXPT_6 differs from TRXPT_7 by containing an extra splice site at 3447-3515 bp.
+However, the CP remains similar to that of TRXPT_7 except the Ad-pol encoded from the secSC is a truncated isoform with a new STC resulting from the splice site.
 
-While both TRXPT_6 and TRXPT_7 have the CP for Ad-pol with secSSC usage, in all AdVs studied, the two proteins (pTP and Ad-pol) are encoded by separate mRNAs with identical first three 5' exons and TTS, but the splice junction to the terminal exons are different.
-We checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing) and discovered a unique splice junction (10,981-7062bp) not found in our RNA-seq data.
+While both TRXPT_6 and TRXPT_7 have the CP for Ad-pol with secSC usage, in all AdVs studied, the two proteins (pTP and Ad-pol) are encoded by separate mRNAs with identical first three 5' exons and TTS, but the splice junction to the terminal exons are different.
+We checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing) and discovered a unique splice junction (10,981-7062 bp) not found in our RNA-seq data.
 If initiated from the E2 TSS and terminated at the E2 TTS, this transcript (TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 7**).
@@
 TRXPT_5 is a two-exon transcript spliced exactly as the last splice junction of TRXPT_6.
-The first exon is a UTR, except the last 2 nucleotides, which connect with the first nucleotide of the second exon to form the 5'-most SSC.
-This first SSC is 4 codons upstream and in-frame of the predicted IVa2 SSC.
+The first exon is a UTR, except the last 2 nucleotides, which connect with the first nucleotide of the second exon to form the 5'-most SC.
+This first SC is 4 codons upstream and in-frame of the predicted IVa2 SC.
 Except for the four extra N-terminus residues, the entire protein sequence is identical to the predicted IVa2.
@@
 However, some E3 transcripts use the TSS of the MLP.
-Due to sharing the same TSS, in MAdVs, secSSC usage is heavily relied on for gene expression in this region except for 12.5K and transcripts using the MLP's TSS, as utilizing only the first SSC cannot produce all the other transcripts in this TU [@Donovan2020].
+Due to sharing the same TSS, in MAdVs, secSC usage is heavily relied on for gene expression in this region except for 12.5K and transcripts using the MLP TSS, as utilizing only the first SC cannot produce all the other transcripts in this TU [@Donovan2020].
 
@@
 
-We identified seven novel transcripts here (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs -- we consider the first TSS (position 18,230bp) as corresponding to the L4P and the other at 18,727bp as corresponding to the E3 promoter (E3P).
+We identified seven novel transcripts here (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs -- we consider the first TSS (position 18,230 bp) as corresponding to the L4P and the other at 18,727 bp as corresponding to the E3 promoter (E3P).
 These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, and E3, as well as Fiber (IV) and ORF7 belonging to the MLTU.
-But some of these CDSs are different than predicted due to either unknown exons or the presence of an in-frame upstream SSC.
+But some of these CDSs are different than predicted due to either unknown exons or the presence of an in-frame upstream SC.
 For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered a significantly longer four-exon ORF (e33K) on TRXPT_24 that contains it almost entirely.
-The first two exons of e33K were not predicted but the last two match the predicted exons and the CDS is in-frame, albeit the first 20bp of the predicted 33K (including the SSC at 20,142bp) is spliced out as part of the second intron of TRXPT_24.
+The first two exons of e33K were not predicted but the last two match the predicted exons and the CDS is in-frame, albeit the first 20 bp of the predicted 33K (including the SC at 20,142 bp) is spliced out as part of the second intron of TRXPT_24.
 Thus, the bona fide 33K (e33K) is a 19.8 kDa, 171 residue protein spanning four exons instead of the predicted 120 aa protein.
-TRXPT_24 also has the CP for pVIII and E3 if we consider downstream SSC usage.
-However, the predicted E3 has an upstream in-frame SSC; thus, this longer version of E3 (eE3) is the genuinely expressed ORF.
+TRXPT_24 also has the CP for pVIII and E3 if we consider downstream SC usage.
+However, the predicted E3 has an upstream in-frame SC; thus, this longer version of E3 (eE3) is likely the genuinely expressed ORF.
 TRXPT_29 is the shortest transcript in this TU.
 It is a two-exon transcript, both exons comprising the CDS.
-The product of TRXPT_29 is a novel 73 residue protein (8.3KI) sharing the SSC of e33K but with a unique STC.
-TRXPT_23 being spliced identically as TRXPT_29 also encodes 8.3KI from its first SSC.
-Similarly, TRXPT_22 also encodes a 73 aa novel protein (8.3KII) from its first SSC that shares over 80% similarity with 8.3KI, but it differs from 8.3KI at the C-terminus.
-Considering downstream SSC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and eE3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+The product of TRXPT_29 is a novel 73 residue protein (8.3KI) sharing the SC of e33K but with a unique STC.
+TRXPT_23 being spliced identically as TRXPT_29 also encodes 8.3KI from its first SC.
+Similarly, TRXPT_22 also encodes a 73 aa novel protein (8.3KII) from its first SC that shares over 80% similarity with 8.3KI, but it differs from 8.3KI at the C-terminus.
+Considering downstream SC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and eE3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
 
@@
 The first CDS on TRXPT_30 spans all three exons, producing a novel 140 residue, 15.7kDa protein.
-Interestingly, the last 81 C-terminus residues of this new protein (e22K) are identical to 22K (89 residues), which is a single-exon ORF predicted to use the same SSC as 33K (20,142bp).
-Just as seen for 33K, all the transcripts in this region exclude the first 20bp of 22K (including the SSC) as part of their introns; therefore, the first 7 residues of 22K are lacking in e22K due to splicing.
+Interestingly, the last 81 C-terminus residues of this new protein (e22K) are identical to 22K (89 residues), which is a single-exon ORF predicted to use the same SC as 33K (20,142 bp).
+Just as seen for 33K, all the transcripts in this region exclude the first 20 bp of 22K (including the SC) as part of their introns; therefore, the first 7 residues of 22K are lacking in e22K due to splicing.
 Hence, we consider e22K as a long variant of the predicted 22K ORF.
@@
 It is a two-exon transcript, encoding a novel protein (t100K; 543 residues), which is a shorter isoform of the predicted 100K ORF.
-Considering secSSC usage on this transcript yields the predicted 22K ORF precisely.
+Considering secSC usage on this transcript yields the predicted 22K ORF precisely as predicted.
 It also has the CP for pVIII and eE3 in that order.
-Furthermore, during the validation of TRXPT_25's splice junction using primers that span its junction (18350-18717bp), we noticed a DNA band that corresponds to the full unspliced sequence (**Supplementary PCR methods**).
+Furthermore, during the validation of the TRXPT_25 splice junction using primers that span its junction (18,350-18,717 bp), we noticed a DNA band that corresponds to the full unspliced sequence (**Supplementary PCR methods**).
 As TRXPT_25 only falls short of encoding the complete predicted 100K protein due to its splice junction, this band (which we cloned and validated by Sanger sequencing) suggests that the predicted 100K is indeed expressed.
 This transcript (TRXPT_25B) although not seen in full, likely shares the same TSS and TTS as TRXPT_25.
-Lastly, TRXPT_26 and TRXPT_27 both originate from the E3 TSS but have distinct TTSs.
+Lastly, TRXPT_26 and TRXPT_27 both originate from the E3P but have distinct TTSs.
 TRXPT_26 is a three-exon transcript but the first two are UTRs.
 It encodes pVIII as the 5'-most ORF and has the CP for eE3 and Fiber in that order.
-TRXPT_27 on the other hand, is only a two-exon transcript but similar to TRXPT_26, only the terminal exon contains the CDSs.
-It encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSSC usage.
+TRXPT_27 on the other hand, is only a two-exon transcript that is similar to TRXPT_26, only the terminal exon contains the CDSs.
+It encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSC usage.
 TRXPT_13, which is an L4 transcript that uses the MLP TSS is discussed under the MLTU transcripts.
@@
 This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the anti-sense strand (**Figure 9**).
-The transcript (TRXPT_28) spans 25192-26247bp and is spliced at 25701-26055bp, making a two-exon transcript.
+The transcript (TRXPT_28) spans 25192-26247 bp and is spliced at 25701-26055 bp, making a two-exon transcript.
 The second exon fully matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
-However, there is an SSC in the first exon at position 26246bp (192bp upstream of the predicted SSC).
-The encoded protein from this SSC is in-frame with the predicted SSC found in the second exon; hence, we consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of the predicted ORF8, the genuinely expressed ORF with an identical C-terminus to the predicted ORF8 protein.
+However, there is an SC in the first exon at position 26246 bp (192 bp upstream of the predicted SC).
+The encoded protein from this SC is in-frame with the predicted SC found in the second exon; hence, we consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of the predicted ORF8, as the genuinely expressed ORF with an identical C-terminus to the predicted ORF8 protein.
 
@@
 The MLP produces all late mRNAs by alternative splicing and alternative polyadenylation of a primary transcript, grouped into five transcript classes (L1-L5).
-Most of THEV's coding capacity falls within this TU.
+Most of the coding capacity of THEV falls within this TU.
 Specifically, about 13 out of the 23 predicted ORFs were assigned to this TU, some of which we have categorized under the E3 TU instead.
@@
 
-We identified five TTSs (10,549bp, 12,709bp, 16,870bp, 17,891bp, 20,865bp) in this TU, which we consider as corresponding to the five late mRNA classes (L1-L5), respectively, as found in all AdVs.
+We identified five TTSs (10,549 bp, 12,709 bp, 16,870 bp, 17,891 bp, 20,865 bp) in this TU, which we consider as corresponding to the five late mRNA classes (L1-L5), respectively, as found in all AdVs.
 L1 mRNAs include TRXPT_8, which comprises the TPL (non-coding) and the CDS-containing terminal exon.
-This transcript encodes the 52K ORF exactly as predicted with the SSC beginning from the first nucleotide of the terminal exon.
+This transcript encodes the 52K ORF exactly as predicted with the SC beginning from the first nucleotide of the terminal exon.
 L2 mRNAs include TRXPT_16, TRXPT_17, and TRXPT_18, all of which consist of the sTPL (also non-coding) followed by their respective terminal exons.
@@
 Normally, MLTU transcripts encoding particular ORFs splice the TPL onto a splice site just upstream of the ORF to be expressed [@Donovan2020].
-While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as these L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSSC utility and ribosome shunting found in other AdVs for their translation [@Donovan2020; @Yueh1996].
+While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as these L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSC utility and ribosome shunting found in other AdVs for their translation [@Donovan2020; @Yueh1996].
 TRXPT_9 and TRXPT_10 are very similar but not identical.
 The last exon of TRXPT_9 seems to be truncated and probably shares the same TTS as the other L4 mRNAs.
-They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) -- uses an upstream in-frame SSC than predicted, and ORF12 (a novel unpredicted 120 aa protein).
+They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) -- uses an upstream in-frame SC than predicted, and ORF12 (a novel unpredicted 120 aa protein).
 TRXTP_10 (and TRXPT_9 with the L4 TTS) additionally has the CP for pVIII and eE3.
-Conversely, TRXPT_11 is a seven-exon mRNA with hexon as it's 5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also pVIII and eE3 in that order.
-TRXPT_13 seems to be an E3 ORF utilizing the MLP TSS as it encodes classical L4P genes such as pVIII and eE3 in that order similar to TRXPT_22 (E3 TU) but lacks TRXPT_22's novel first ORF (8.3KII).
+Conversely, TRXPT_11 is a seven-exon mRNA with hexon as its 5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also pVIII and eE3 in that order.
+TRXPT_13 seems to be an E3 ORF utilizing the MLP TSS as it encodes classical L4P genes such as pVIII and eE3 in that order similar to TRXPT_22 (E3 TU) but it lacks the novel first ORF (8.3KII) of TRXPT_22.
 
@@
 Its 5'-most ORF is fiber (IV) but it also has the CP for the THEV specific gene, ORF7.
-TRXPT_12's CP is identical to TRXPT_27 of the the E3 TU but they differ in their 5'-UTRs.
+TRXPT_12's CP is identical to TRXPT_27 of the E3 TU but they differ in their 5'-UTRs.
 \newpage
@@
 The challenge is further compounded by the fact that the standard software programs used in the RNA-seq analysis pipelines are not designed primarily for such compact, gene-dense, and complex transcriptomes as AdVs.
-Furthermore, there is no prior transcriptomic studies for THEV.
-Our approach to properly handle this complex data was to use standard RNA-seq analysis programs coupled with some custom analysis and validating all splice junctions with independent methods.
+Furthermore, in our case, there is no prior transcriptomic studies for THEV.
+Our approach to properly handle this complex data was to use standard RNA-seq analysis programs coupled with some custom analyses and experimentally validating all splice junctions with independent methods.
 Our work provides the first insights into the splicing patterns of THEV, which is expectedly similar to other MAdVs but with key differences.
@@
 An unexpected observation is that the pileup of mapped reads to THEV seems consistently skewed over similar regions of the genome at all time points.
-As AdVs gene expression is temporally regulated, we expected to see unambiguous differences in the pileup of reads over different regions of the genome at different time points, indicating the different stages of infection.
+As the gene expression of AdVs is temporally regulated, we expected to see unambiguous differences in the pileup of reads over different regions of the genome at different time points, indicating the different stages of infection.
 While this could simply mean that the infection was not well synchronized, we speculate that the temporal gene expression regulation of THEV is probably different from MAdVs.
@@
 However, due to the substantial overlapping nature of AdV mRNAs coupled with the fragmentation step in the library preparation protocol, mapping the precise TSS and TTS of the assembled transcripts is difficult.
-Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA since the short reads alone do not provide enough context for the transcript assembler (`StringTie`) to distinguish them.
-In our results, we see transcripts in the same TU initiated or terminated in the same approximate area (10-70bp and 1-300bp apart for TSS and TTS, respectively) but not precisely at the same position.
+Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA since the short reads alone do not provide enough context for the transcript assembler (StringTie) to distinguish them.
+In our results, we see transcripts in the same TU initiated or terminated in the same approximate area (10-70 bp and 1-300 bp apart for TSS and TTS, respectively) but not precisely at the same position.
 We consider the most upstream TSS or most downstream TTS for the transcripts involved but we present them unchanged in all the figures shown.
-Also, by comparison to the more well-studies MAdV transcriptomes, we think that a few long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are probably a result of fusing some L4P-derived transcripts to the terminal exons of the bona fide MLTU transcripts by StringTie, making them significantly longer.
+Also, by comparison to the more well-studied MAdV transcriptomes, we believe that a few long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are probably a result of fusing some L4P-derived transcripts to the terminal exons of the bona fide MLTU transcripts by StringTie, making them significantly longer.
 These mRNAs do not only have unusually many exons for an AdV, but their last three or four exons are also identical to the L4P-derived mRNAs.
 Future studies using long read sequencing technologies are necessary to provide conclusive data for precisely mapping the TSS and TTS, as well as teasing apart the bona fide structures of the long MLTU transcripts.
-Furthermore, it is not unreasonable to presume that several splice variants were undiscovered in our work as evidenced firstly by finding unique transcripts using 3'RACE and during our splice junction validation steps.
+Furthermore, it is not unreasonable to presume that several splice variants were undiscovered in our work as evidenced firstly by finding unique transcripts using 3' RACE and during our splice junction validation steps.
 And secondly, recent studies [@Donovan2020; @Zhao2014; @Westergren2021] are still discovering novel mRNA variants for even the best studied MAdVs decades later.
@@
 
-An interesting finding of our analysis is that while most of the predicted ORFs are precisely encoded by the spliced transcripts, we found a few that seem to be truncated predictions, as either an upstream in-frame SSC (eORF1, eE3, and eProt) or unknown upstream exons spliced onto them (eIVa2, e33K, and eORF8) were found.
+An interesting finding of our analysis is that while most of the predicted ORFs are precisely encoded by the spliced transcripts, we found a few that seem to be truncated predictions, as either an upstream in-frame SC (eORF1, eE3, and eProt) or unknown upstream exons spliced onto them (eIVa2, e33K, and eORF8) were found.
 Other ORFs were identified that were either shorter (tDBP, t100K) or longer (e22K) isoforms of some predicted ORF but we found evidence to support the predicted ORF itself, making them all possible genuinely translated variants.
@@
 
-Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most AUG normally being used as the translation reading frame.
+Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most AUG normally being used to determine the translation reading frame.
 However, depending on the sequence context, in some organisms, the initiating codon may even be a non-AUG start codon.
-AdV mRNAs, which mostly span more than one ORF, are known to be functionally polycistronic, employing non-standard mechanisms of translation initiation, namely, secSSC usage and ribosome shunting [@Westergren2021; @Guimet2016].
-Albeit there is no reliable method of predicting how efficiently any given AUG will be used, AdVs use secondary AUGs as initiation codons for most E1b proteins and for some E3 proteins.
-In fact, recent studies show that secSSC usage is found transcriptome-wide.
-This is thought to occur because translation initiation at the first SSC is inefficient, allowing downstream SSCs to be employed for initiation [@Donovan2020].
+AdV mRNAs, which mostly span more than one ORF, are known to be functionally polycistronic, employing non-standard mechanisms of translation initiation, namely, secSC usage and ribosome shunting [@Westergren2021; @Guimet2016].
+While there is no reliable method of predicting how efficiently any given AUG will be used, AdVs use secondary AUGs as initiation codons for most E1b proteins and for some E3 proteins.
+In fact, recent studies show that secSC usage is found transcriptome-wide.
+This is thought to occur because translation initiation at the first SC is inefficient, allowing downstream SCs to be employed for initiation [@Donovan2020].
 The ribosomal shunting or jumping mechanism is utilized for MLTU transcripts that have the TPL.
 This mechanism allows the ribosome to translocate to a downstream initiating codon under the direction of the shunting elements in the TPL, even if a start codon in a good Kozak sequence context is bypassed.
-Thus, predicting the protein(s) that are expressed from an AdV mRNA becomes highly uncertain as any one of the SSC may be selected [@Guimet2016; @Westergren2021].
+Thus, predicting the protein(s) that are expressed from an AdV mRNA becomes highly uncertain as any one of the SC may be selected [@Guimet2016; @Westergren2021].
 Almost all the THEV transcripts in our data have the CP for several ORFs, some spanning as many as six ORFs but the majority spanning at least two ORFs.
-Therefore, we believe our data supports the usage of these special ribosome initiation mechanisms as a several predicted and novel ORFs found on mRNA in our data have no conceivable mechanism of being translated if only the typical ribosome scanning mechanism is employed.
+Therefore, we believe our data support the usage of these special ribosome initiation mechanisms as several predicted and novel ORFs found on mRNA in our data have no conceivable mechanism of being translated if only the typical ribosome scanning mechanism is employed.
 Interestingly, several distinct transcripts have identical CPs.
@@
 This was thought to be limited to certain TUs; however, recent studies suggest that AdVs routinely produce different combinations of splice acceptor–donor pairs and that this is observed in all TUs [@Westergren2021; @Akusjarvi2008; @Donovan2020; @Guimet2016].
-The mechanistic details of this phenomenon has been best studied for the E1A and L1 units.
+The mechanistic details of this phenomenon have been best studied for the E1A and L1 units.
 The studies show that AdVs (specifically, late phase AdV-infected nuclear extract) modulate the activities of the splicing factor U2AF and the cellular SR family of splicing factors (reviewed in reference [@Akusjarvi2008]) and encode several mostly late phase proteins (E4-ORF3, E4-ORF6, E4-ORF4, L4-33K, and L4-22K) that influence the RNA splice site used.
-This phenomenon seems to occur in the THEV transcriptome also, as the stringency of splice acceptor-donor pairs selected decreased measurably from the onset of the late phase (see **Figure 5**).
-In fact, recent studies of some human AdVs show that virtually unlimited number of combinatorial alternative splicing events resulting in menagerie of novel transcripts are produced in an AdV lytic infection [@Donovan2020; @Westergren2021].
-It is unlikely that all repertoire of mRNA produced via this mechanism will actually be translated.
-However, it has been speculated that the plasticity in alternative RNA splicing enables the AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions.
-And also that the capacity to produce novel exon combinations will offer the virus an evolutionary advantage to change the gene expression repertoire and protein production in a changing environment [@Donovan2020; @Westergren2021].
+This phenomenon seems to occur in the THEV transcriptome also, as the stringency of splice acceptor-donor pairs selected decreases measurably from the onset of the late phase (see **Figure 5**).
+In fact, recent studies of some human AdVs show that a virtually unlimited number of combinatorial alternative splicing events occur in an AdV lytic infection, resulting in menagerie of novel transcripts [@Donovan2020; @Westergren2021].
+It is unlikely that the entire repertoire of mRNA produced via this mechanism will actually be translated.
+However, it has been speculated that the plasticity in alternative RNA splicing enables AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions.
+The capacity to produce novel exon combinations offers the virus an evolutionary advantage to adjust the repertoire of mRNA transcription and protein production in the changing environment of the viral replication cycle [@Donovan2020; @Westergren2021].
 
-Summarizing all the main points above, we see that the THEV transcriptome bares remarkable overall similarity to the better studied MAdVs.
-The transcriptome organization into five TUs, the overall regulation of early and late genes, and the production of a broad repertoire of transcripts via virtually unlimited alternative splicing.
-However, the THEV transcriptome appears to be less sophisticated (i.e, encode less genes) than MAdVs primarily because the MAdV genomes are close to twice a long as that of THEV's, which rationally should encode less genes.
+Summarizing all the main points above, we see that the THEV transcriptome bears remarkable overall similarity to the better studied MAdVs.
+The transcriptome is organized into five TUs, the temporal regulation is divided into early and late genes, and a broad repertoire of transcripts are produced via virtually unlimited alternative splicing.
+However, the THEV transcriptome appears to be less sophisticated (i.e, it encodes fewer genes) than MAdVs primarily because the MAdV genomes are close to twice as long as that of THEV, which rationally should encode less genes.
 The lack of subdivision of the E1 region into E1a and E1b is one of the most obvious examples.
-Also, the MAdV E4 region encodes several proteins unlike in THEV where only one transcript coding for only one protein was found.
+Also, the MAdV E4 region encodes several proteins unlike in THEV where only one transcript coding for one protein was found.
 The most conspicuous example is found in examining the complexity of the MLTU leader sequences.
-While the majority of THEV's MLTU transcripts begin with the TPL (267bp long) just like MAdVs and also utilizes a variant leader sequence (sTPL), it is well established that a significantly more diverse 5'UTRs are employed for MAdV MLTU transcripts, including the TPL (used for majority of transcripts), the so-called x, y, and z leaders, and the i-leader.
-Granted, the MAdV MLTU transcripts infrequently incorporate the the non-TPL leaders, their absence in our data could mean that the 5'UTR diversity of THEV's MLTU mRNA are indeed more limited due to its smaller genome size.
-It is also possible that later studies could uncover more variety not seen our results.
+While the majority of the THEV MLTU transcripts begin with the TPL (267 bp long) just like MAdVs, and also utilize a variant leader sequence (sTPL), it is well-established that significantly more diverse 5'UTRs are employed for MAdV MLTU transcripts.
+Namely, the TPL (used for majority of transcripts), the so-called x, y, and z leaders, and the i-leader are 5' leaders utilized by MAdV MLTU mRNAs.
+Granted, the MAdV MLTU transcripts infrequently incorporate the non-TPL leaders, their absence in our data could mean that the 5'UTR diversity of THEV's MLTU mRNA are indeed more limited due to its smaller genome size.
+It is also possible that later studies could uncover more variety not seen in our results.
+Specifically, using long read sequencing technologies would be a excellent approach to discovering and fine-tuning the transcriptome characterized in this work.
+Also, it is likely that future studies repeating this work in other cell lines will yield some interesting insights.
 \newpage
@@
 
-The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium with 10% fetal bovine serum (FBS), 20% chicken serum (ChS), 5% tryptose phosphate broth (TPB), and 1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin), at 41^o^C in a humidified atmosphere with 5% CO~2~.
-Infected cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and 1% antibiotics solution (100 U/mL Penicillin and 100ug/mL Streptomycin).
-A commercially available HE vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
+The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium with 10% fetal bovine serum (FBS), 20% chicken serum (ChS), 5% tryptose phosphate broth (TPB), and 1% antibiotic solution (100 U/mL Penicillin and 100$\mu g$/mL Streptomycin), at 41^o^C in a humidified atmosphere with 5% CO~2~.
+Infected cells were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media (SRLM) with 2.5% FBS, 5% ChS, 1.2% TPB, and 1% antibiotic solution.
+A commercially available THEV vaccine was purchased from Hygieia Biological Labs as a source of THEV-A (VAS strain).
 The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number (GCN)/mL, similar to Mahshoub *et al* [@Mahsoub2017] with modifications.
-Cells were infected in triplicates at a multiplicity of infection (MOI) of 100 GCN/cell, incubate at 41^o^C for 1 hour, and washed three times to get rid of free virion particles.
-Samples in triplicates were harvested at 4-, 12-, 24-, and 72-h.p.i for total RNA extraction.
-The infection was repeated but samples in triplicates were harvested at 12-, 24-, 36-, 48-, and 72-h.p.i for PCR validation of novel splice sites.
-Still one more independent infection was done at time points ranging from 12 to 168-h.p.i for qPCR quantification of virus titers.
+Cells were infected in triplicate at a multiplicity of infection (MOI) of 100 GCN/cell, incubated at 41^o^C for 1 hour, and washed three times with phosphate buffered saline (PBS) to get rid of free virus particles.
+Triplicate samples were harvested at 4-, 12-, 24-, and 72-hpi for total RNA extraction.
+The infection was repeated but samples in triplicate were harvested at 12-, 24-, 36-, 48-, and 72-hpi for PCR validation of novel splice sites.
+Still one more independent infection was done at time points ranging from 12 to 168-hpi for qPCR quantification of virus titers.
 
@@
 
-Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` per manufacturer's instructions.
+Total RNA was extracted from infected cells using the Thermofisher RNAqueous™-4PCR Total RNA Isolation Kit (which includes a DNase I digestion step)  per manufacturer's instructions.
 An agarose gel electrophoresis was performed to check RNA integrity.
-The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was \>2 and \<2.2.
-Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`.
-Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.
+The RNA quantity and purity was initially assessed using nanodrop, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was \>2 and \<2.2.
+Extracted total RNA samples were sent to LC Sciences, Houston TX for poly-A-tailed mRNA sequencing where RNA integrity was checked with Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip and poly(A) RNA-seq library was prepared following Illumina's TruSeq-stranded-mRNA sample preparation protocol.
+Paired-end sequencing to generate 150 bp reads was performed on the Illumina NovaSeq 6000 sequencing system.
 
@@
 The novel splice junctions discovered in this work using the StringTie transcript assembler were validated by PCR, cloning, and Sanger Sequencing (**Supplementary PCR methods**).
-Briefly, we designed primers that span a range of novel exon-exon boundaries for each specific transcript in a transcription unit (TU).
-We designed a universal forward or reverse primers for each respective TU and paired them with primers binding specific positions in each transcript.
-Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site in the primer tails.
-After first-strand cDNA synthesis of total RNA extracted from THEV infected MDTC-RP19 cells with SuperScript™ IV First-Strand Synthesis System, these primers were used in a targeted PCR amplification, the products analyzed with agarose gel electrophoresis to confirm expected band sizes, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
+Briefly, primers spanning a range of novel exon-exon boundaries for each specific transcript in a transcription unit (TU) were designed.
+Universal forward or reverse primers for each respective TU were designed and paired with primers binding specific positions in each transcript.
+Each forward primer contained a KpnI restriction site and each reverse primer, an XbaI site in the primer 5' ends.
+After first-strand cDNA synthesis of total RNA obtained from THEV infected MDTC-RP19 cells was done using SuperScript™ IV First-Strand Synthesis System, the primers were used in a targeted PCR amplification, the products analyzed with agarose gel electrophoresis to confirm expected band sizes, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.
+The total RNA was extracted as described above, including the DNase I digestion step.
+We included infected total RNA controls with no reverse transcriptase (no RT) during the cDNA synthesis step and the parent RNA were digested using RNase H after cDNA synthesis was complete to ensured that the bands obtained from the targeted PCR amplifications did not originate from the viral genomic DNA.
+As seen in the agarose gel images in **Supplementary PCR methods**, DNA bands were not found in the "no RT" controls, indicating that the DNA bands seen are of cDNA origin.
 
-### 3' Rapid Amplification of cDNA Ends (3'-RACE)
+### 3' Rapid Amplification of cDNA Ends (3' RACE)
 
-We performed a rapid amplification of sequences from the 3' ends of mRNAs (3'-RACE) experiment using a portion of the extracted total RNA of infected MDTC-RP19 cells used for the RNA-seq experiment as explained above.
+A rapid amplification of sequences from the 3' ends of mRNAs (3' RACE) experiment was performed using a portion of the extracted total RNA of infected MDTC-RP19 cells used for the RNA-seq experiment as explained above.
 We followed the protocol described by Green *et al* [@Green2019] with modifications.
-Briefly, 1ug of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter-primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
+Briefly, 1$\mu g$ of total RNA was reverse transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System following the manufacturing instructions using an adapter-primer with a 3'-end poly(T) and a 5'-end BamHI restriction site.
 A gene-specific sense primer with a 5'-end KpnI restriction site paired with an anti-sense adapter-primer with a 5'-end BamHI site were used to amplify target sections of the cDNA using Invitrogen's Platinum™ Taq DNA polymerase High Fidelity, following manufacturer's instructions.
@@
 
-Our sequence reads were analyzed following a well-established protocol described by Pertea *et al* [@Pertea2016], using `Snakemake - version 7.24.0` [@Snakemake2021], a popular workflow management system to drive the pipeline.
-Briefly, sequencing reads were trimmed with the `Trim-galore - version 0.6.6` [@TrimGalore] program to achieve an overall `Mean Sequence Quality (Phred Score)` of 36.
-Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent turkey hemorrhagic enteritis virus (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using `Hisat2 - version 2.2.1` [@Pertea2016] with default settings.
-The generated alignment (`BAM`) files from each infection time point were filtered for reads mapping to the THEV genome using `Samtools - version 1.16.1` and fed into `StringTie - version 2.2.1` [@Pertea2016] to assemble the transcripts, using a `GTF` annotation file derived from a `GFF3` annotation file obtained from NCBI, which contains the predicted ORFs of THEV as a guide.
-`GFFCOMPARE - version 0.12.6` was used to merge all transcripts from all time points without redundancy and using a custom `R` script, adenovirus transcripts units (regions) were assigned to each transcript, generating the transcriptome of THEV.
-`StringTie` set to expression estimation mode was used to calculate FPKM scores for all transcripts after which `Ballgown - version 2.33.0` in `R` was used to perform the statistical analysis on the transcript expression levels.
-`Samtools` was also used to count the total sequencing reads for all replicates at each time point and `Regtools - version 1.0.0` was used to count all junctions, the reads supporting them, and extract all other information related to the junction.
+Sequencing reads were analyzed following a well-established protocol described by Pertea *et al* [@Pertea2016], using Snakemake - version 7.24.0 [@Snakemake2021], a popular workflow management system to drive the pipeline.
+Briefly, sequencing reads were trimmed with the Trim-galore - version 0.6.6 [@TrimGalore] program to achieve an overall Mean Sequence Quality (Phred Score) of 36.
+Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent turkey hemorrhagic enteritis virus (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using Hisat2 - version 2.2.1 [@Pertea2016] with default settings.
+The generated binary alignment (BAM) files from each infection time point were filtered for reads mapping to the THEV genome using Samtools - version 1.16.1 and fed into StringTie - version 2.2.1 [@Pertea2016] to assemble the transcripts, using a gene transfer format (GTF) annotation file derived from a gene feature format 3 (GFF3) annotation file obtained from NCBI, which contains the predicted ORFs of THEV as a guide.
+GFFCOMPARE - version 0.12.6 was used to merge all transcripts from all time points without redundancy and using a custom R script, adenovirus transcripts units (regions) were assigned to each transcript, generating the transcriptome of THEV.
+StringTie was set to expression estimation mode to calculate FPKM scores for all transcripts after which Ballgown - version 2.33.0 in R was used to perform the statistical analysis on the transcript expression levels.
+Samtools was also used to count the total sequencing reads for all replicates at each time point and Regtools - version 1.0.0 was used to count all junctions, the reads supporting them, and extract all other information related to the junction.
 See **Supplementary Computational Analysis** for the details of transcript expression level estimations and splice junction read counts.
@@
 
-The raw sequence data (FastQ), transcript expression counts, and total unique junctions have been deposited at the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
+The raw sequencing read data (FastQ), transcript expression counts, and total unique junctions have been deposited at the National Center for Biotechnology Information Gene Expression Omnibus (<http://www.ncbi.nlm.nih.gov/geo>) under accession number GSE254416.
 
-Data is also available on request by contacting the designated corresponding author
+Data is also available on request by contacting the designated corresponding author.
 
@@
 All the code/scripts in the entire analysis pipeline are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>)
-\newpage
 
@@
 
-`LC Sciences` - RNA sequencing was done here   
-`Eton Bioscience, Inc, San Diego, CA` - All Sanger sequencing validations was done here 
-`BYU high performance computing systems` - Memory-intensive analysis were run here.
+We thank the Office of Research Computing at Brigham Young University for granting us access to the high performance computing systems to perform the memory-intensive steps in the analysis pipeline of this work.
 \newpage
@@
 ## REFERENCES
-
 ```{=tex}
@@
 ## TABLES AND FIGURES
-![](results/r/figures/thev_orf_map.png)   
-**Figure 1.
-*Predicted ORF map of THEV avirulent strain***.
-The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
-Blocks represent viral genes.
-Blocks above the DNA line are transcribed rightward, those below are transcribed leftward.
-pTP, DBP and 33K predicted to be spliced are shown as having tails.
+![**Figure 1.
+Predicted ORF map of THEV avirulent strain.** The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
+Colored blocks represent viral genes.
+Blocks above the DNA line are transcribed on the sense DNA strand and those below, on the anti-sense strand.
+pTP, DBP and 33K are predicted to be spliced and are shown as two exons connected with dashed lines.
 Shaded regions indicate regions containing "genus-specific" genes (colored red).
 Genes colored in blue are "genus-common".
-Gene colored in light green is conserved in all but Atadenoviruses.
-The UXP (light blue) is an incomplete gene present in almost all AdVs.
-Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.
+The gene colored in light green is conserved in all but Atadenoviruses.
+Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.](results/r/figures/thev_orf_map.png)
 
-![](results/r/figures/fig_2.png)   
-**Figure 2: Increasing levels of THEV over time.
-a) *Per base coverage of sequence reads mapping to THEV genome by time point***.
-The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
-**b) *Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line***.
-Virus titers were a quantified with a qPCR assay.
-There is no discernible increase in virus titer up 12 h.p.i, after which a steady increase in virus titer is measured.
-The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i.
-GCN: genome copy number.
+![**Figure 2: Increasing levels of THEV over time.
+A) Per base coverage of sequence reads mapping to THEV genome by time point.** The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
+**B) Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line.** Virus titers in the freeze-thawed supernatant from infected cells were a quantified with a qPCR assay.
+There is no discernible increase in virus titer up 12 hpi, after which a steady increase in virus titer is measured.
+The virus titer expands exponentially beginning from 48 hpi, increasing by orders of magnitude before reaching a plateau at 120 hpi.
+GCN: genome copy number.](results/r/figures/fig_2.png)
 
-![](results/r/figures/figure3.png)   
-**Figure 3.
-a) Transcriptome of THEV from RNA-seq**.
-THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map).
+![**Figure 3.
+A) Transcriptome of THEV from RNA-seq.** THEV transcripts assembled from all time points by StringTie are unified forming this final transcriptome (splicing map).
 Transcripts belonging to the same transcription unit (TU) are located in close proximity on the genome and are color coded and labeled in this figure as such.
@@
 Predicted ORFs are also indicated here, colored light grey.
-**b) THEV transcripts identified at given time points**.
-Transcripts are color coded as explained in **(a)**.
+**B) THEV transcripts identified at given time points.** Transcripts are color coded as explained in **(A)**.
+](results/r/figures/figure3.png)
 
-![](results/r/figures/figure_4a_d.png)    
-**Figure 4: Changes in splicing and expression profile of THEV over time.** **a)** _Normalized (FPKM) expression levels of transcripts over time_.
-The expression levels (FPKM) of individual transcripts as a percentage of the total expression of all transcripts at each time point are indicated.
+![**Figure 4: Changes in splicing and expression profile of THEV over time.** **A) Normalized (FPKM) expression levels of transcripts over time.** The expression levels (FPKM) of individual transcripts as a percentage of the total expression of all transcripts at each time point are indicated.
 Only transcripts from our RNA-seq data are included here.
-**b)** _Normalized (FPKM) expression levels of transcripts by region over time_.
-The expression levels of each region/TU as a percentage of the total expression of all transcripts at each time point are indicated.
+**B) Normalized (FPKM) expression levels of transcripts by region over time.** The expression levels of each region/TU as a percentage of the total expression of all transcripts at each time point are indicated.
 Region expression levels were calculated by summing up the FPKMs of all transcripts categorized in that region.
-**c)** _Relative abundances of all splice junctions grouped by region/TU over time_.
-After assigning all `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique junctions to a TU and the total junction reads counted at each time point for each region, the total junction reads for each TU plotted as percentage of all junction reads at each time point is indicated.
+**C) Relative abundances of all splice junctions grouped by region/TU over time.** After assigning all `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique junctions to a TU and the total junction reads counted at each time point for each region, the total junction reads for each TU were plotted as percentages of all junction reads at each time point.
 Note that the junction read counts are not normalized.
-**d)** _Relative abundances of junctions in transcriptome grouped by region/TU over time_.
-This is identical to **(c)**, except that only the junctions found in the full transcriptome obtained from the RNA-seq data were included.
+**D) Relative abundances of junctions in transcriptome grouped by region/TU over time.** This is identical to **(C)**, except that only the junctions found in the full transcriptome obtained from the RNA-seq data were included.](results/r/figures/figure_4a_d.png)
 
-![](results/r/figures/figure_5a_d.png)
-**Figure 5: Changes in splice donor-acceptor nucleotides over time.** The splice donor-acceptor nucleotides of THEV just like other AdVs is mostly the canonical GT-AG.
-At early time points (4h.p.i and 12h.p.i [**(a)** and **(b)**]) the junction nucleotides used appear to be well scrutinized or restricted, utilizing mostly the canonical splice nucleotides.
-However, as the infection progresses to the late stages (24h.p.i and 72h.p.i [**(c)** and **(d)**]), the selectivity of specific splice acceptor-donor pairs seems to degenerate significantly, such that all combinations of nucleotides are utilized.
+![**Figure 5: Changes in splice donor-acceptor nucleotides over time.** The splice donor-acceptor nucleotides of THEV just like other AdVs is mostly the canonical GU-AG.
+At early time points (4h.p.i and 12h.p.i **(A)** and **(B)**, respectively) the junction nucleotides used appear to be well scrutinized or restricted, utilizing mostly the canonical splice nucleotides.
+However, as the infection progresses to the late stages (24h.p.i and 72h.p.i **(C)** and **(D)**, respectively), the selectivity of specific splice acceptor-donor pairs seems to degenerate significantly, such that all combinations of nucleotides are utilized.](results/r/figures/figure_5a_d.png)
 
-![](results/r/figures/figure_6.png)
-**Figure 6: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
+![**Figure 6: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
 Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and transcripts or ORFs discovered by other means are colored black.
 Each transcript or ORF is labelled with its name to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The start codon (SC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_6.png)
 
-![](results/r/figures/figure_7.png)
-**Figure 7: The splice map of the E2 and IM TUs**.
-Exons are depicted as boxes connected by introns (dotted lines).
+![**Figure 7: The splice map of the E2 and IM TUs.** Exons are depicted as boxes connected by introns (dotted lines).
 Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
@@
 Each transcript or ORF is labelled with its name to the right.
-The SSC and STC of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The SC and STC of the 5'-most CDS of each transcript are indicated with the nucleotide position in brackets.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_7.png)
 
-![](results/r/figures/figure_8.png)
-**Figure 8: The splice map of the E3 TU.** Exons are depicted as boxes connected by introns (dotted lines).
+![**Figure 8: The splice map of the E3 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 Red transcripts are generated from RNA-seq data and predicted ORFs are colored grey.
@@
 Each transcript or ORF is labelled with its name to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-Similarly, the secondary SSC (secSSC) and secondary STC (secSTC) are shown.
+The start codon (SC) and stop codon (STC) of the 5'-most CDS of each transcript are indicated with the nucleotide position in brackets.
+Similarly, the secondary SC (secSC) and secondary STC (secSTC) are shown.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_8.png)
 
-![](results/r/figures/figure_9.png)
-**Figure 9: The splice map of the E4 TU.** Exons are depicted as boxes connected by introns (dotted lines).
+![**Figure 9: The splice map of the E4 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 The transcript from RNA-seq data is colored red and the predicted ORF, grey.
 The transcript and ORF are labelled with their names to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS is indicated with the nucleotide position in brackets.
+The start codon (SC) and stop codon (STC) of the 5'-most CDS are indicated with the nucleotide position in brackets.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junction with its validation status using cloning and Sanger sequencing.
+The table shows sequence reads covering the splice junction with its validation status using cloning and Sanger sequencing.](results/r/figures/figure_9.png)
 
-![](results/r/figures/figure_10.png)
-**Figure 10: The splice map of the MLTU.** Exons are depicted as boxes connected by introns (dotted lines).
+\newpage
+
+![**Figure 10: The splice map of the MLTU.** Exons are depicted as boxes connected by introns (dotted lines).
 The transcripts from our RNA-seq data are colored red and the predicted ORFs, grey.
 The transcripts and ORFs are labelled with their names to the right.
-The start codon (SSC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
-Similarly, the secondary SSC (secSSC) and secondary STC (secSTC) are shown.
+The start codon (SC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+Similarly, the secondary SC (secSC) and secondary STC (secSTC) are shown.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_10.png)
+
 \newpage
 
+\FloatBarrier
 ```{r}
@@
 
-set_flextable_defaults(font.size = 8)
+set_flextable_defaults(font.size = 8, table.layout = "fixed", float = "none")
 flextable(tab1) %>% theme_zebra() %>%
@@
   flextable::set_caption("Table 1: Overview of sequencing results",
-              style = "Table Caption") %>%
+              style = "Table Caption",
+              align_with_table = F) %>%
   flextable::bold(part = "body", j = ~ Metric) %>%
@@
 ```
+\FloatBarrier
 
@@
     dplyr::rename("Reads (Percentage)" = Reads_Percentage) %>%
+    mutate(Splice_Site = case_when(Splice_Site == "GT-AG" ~ "GU-AG",
+                                   Splice_Site == "CT-AC" ~ "CU-AC",
+                                   TRUE ~ Splice_Site)) %>% 
     flextable() %>%
     theme_zebra() %>%
-    flextable::set_table_properties(layout = "fixed", width = 1,
-                         opts_pdf = list(caption_repeat = F)) %>%
     flextable::font(part = "all", fontname = "Avenir") %>%
     flextable::set_caption(title,
-                style = "Table Caption") %>%
+                style = "Table Caption",
+                align_with_table = F) %>%
     flextable::align(align = "center", part = "all") %>%
@@
 All the primer melting temperatures (TMs) are 58-60^o^C using a hot start Taq DNA polymerase.
-The PCR reaction mix was done per manufacturer's instructions.
+The PCR reaction mix was made per manufacturer's instructions.
 The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (53^o^C-56^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes.
@@
 **Supplementary Computational Analysis**    
-`Snakemake v7.24.0` was used to manage our entire workflow.
-A graph of the main steps in our pipeline generated with `Snakemake` is shown below.
+Snakemake v7.24.0 was used to manage our entire workflow.
+A graph of the main steps in our pipeline generated with Snakemake is shown below.
 Our trimmed RNA-seq reads were mapped to the genome of _M.
-gallopavo_ (with THEV's genome as one of its chromosomes) using `Hisat2`, to generate the alignment (BAM) files and `StringTie` used to assemble the transcriptome with a `GTF` annotation file containing the predicted THEV ORFs as a guide.
-The `GTF` annotation file was derived from a `GFF3` annotation file obtained from NCBI using `Agat - version 1.0.0`, a program for converting between many different file formats used in bioinformatics.
-However, the NCBI `GFF3` annotation file itself was first modified to remove all unimportant features, leaving only the ORFs.
+gallopavo_ (with the THEV genome as one of its chromosomes) using Hisat2, to generate the alignment (BAM) files and StringTie used to assemble the transcriptome with a GTF annotation file containing the predicted THEV ORFs as a guide.
+The GTF annotation file was derived from a GFF3 annotation file obtained from NCBI using Agat - version 1.0.0, a program for converting between many different file formats used in bioinformatics.
+However, the NCBI GFF3 annotation file itself was first modified to remove all unimportant features, leaving only the ORFs.
 
-`StringTie` was also used to estimate the normalized expression levels (FPKM) of all the transcripts and `Ballgown` in `R` was used to perform statistical analysis and comparisons of the transcript expression levels, which instructive in understanding the temporal regulation THEV gene expression.
+StringTie was also used to estimate the normalized expression levels (FPKM) of all the transcripts and Ballgown in R was used to perform statistical analysis and comparisons of the transcript expression levels, which was instructive in understanding the temporal regulation THEV gene expression.
 
-In these steps above, each sample (replicate of each time point) was processed independently and merged only in the final transcriptome assembly or during analysis with `Ballgown`.
+In these steps above, each sample (replicate of each time point) was processed independently and merged only in the final transcriptome assembly or during analysis with Ballgown.
 In the subsequent steps described below, all samples for each time point were processed together.
 
-We used `RegTools` to extract and analyze the splice junctions in the BAM files.
-The command `regtools junctions extract` provides a wealth of information about all the splice sites in the BAM file provided such as: the start and end positions, the strand, and number of reads supporting the splice junctions.
-The command `regtools junctions annotate` gives even more information such as: the splice site donor-acceptor sequences and transcripts/genes that overlap the junction.
-These information was the basis for estimating and comparing the splicing activity of different regions (TUs) of THEV over time.
-Also, `Samtools` was also used to count the total sequencing reads for all replicates at each time point.
+We used RegTools to extract and analyze the splice junctions in the BAM files.
+The command "regtools junctions extract" provides a wealth of information about all the splice sites in the BAM file provided such as: the start and end positions, the strand, and number of reads supporting the splice junctions.
+The command "regtools junctions annotate" gives even more information such as: the splice site donor-acceptor sequences and transcripts/genes that overlap the junction.
+This information was the basis for estimating and comparing the splicing activity of different regions (TUs) of THEV over time.
+Also, Samtools was also used to count the total sequencing reads for all replicates at each time point.
 
-![](project_map.png)
+![A flowchart of the major steps in the computationalanalysis pipeline (_generated with Snakemake_)](project_map.png)

### 2024-02-25 importance_of_study.Rmd
wrote importance of study and keywords

---
title: "Importance of the Study"
output:
  officedown::rdocx_document:
    reference_docx: style_word_output.docx
  pdf_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
---
## Key words
Alternative splicing, Turkey hemorrhagic enteritis virus, Adenovirus, Transcriptome, RNA sequencing.

\vspace{15mm}
Hemorrhagic enteritis (HE) is a disease of turkey poults characterized by immunosuppression (IS), bloody diarrhea, and up to 80% mortality. This disease is caused by *Turkey Hemorrhagic Enteritis Virus* (THEV) of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated. The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties. Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts. To establish the genetic basis by which VAS brings about IS leading to its mitigation, it is imperative that the viral gene(s) mediating the IS be well-characterized. As the viral splicing and gene expression patterns are unknown, the most pressing need was for a well-characterized transcriptome of THEV. Also, the detailed characterization of an non-human adenovirus splice map, which is scantily studied, provides valuable insights into the differences of various adenovirus splicing patterns.

### 2024-02-25 importance_of_study.Rmd
edited imporatance of study

@@
 As the viral splicing and gene expression patterns are unknown, the most pressing need was for a well-characterized transcriptome of THEV.
-Also, the detailed characterization of an non-human adenovirus splice map, which is scantily studied, provides valuable insights into the differences of various adenovirus splicing patterns.
+Also, the detailed characterization of a non-human adenovirus splice map, which is scantily studied, provides valuable insights into the differences of various adenovirus splicing patterns.

### 2024-03-21 manuscript_thev_transcriptome.Rmd
minor change in manuscript -- add a space conjoined words
Modified Rmd yaml to retain tex file for easy tracking of chages across versions

@@
     reference_docx: style_word_output.docx
-  pdf_document: default
+  pdf_document:
+    keep_tex: true
 geometry: margin=1in
@@
 
-![A flowchart of the major steps in the computationalanalysis pipeline (_generated with Snakemake_)](project_map.png)
+![A flowchart of the major steps in the computational analysis pipeline (_generated with Snakemake_)](project_map.png)

### 2024-03-21 manuscript_thev_transcriptome.tex
Modified Rmd yaml to retain tex file for easy tracking of chages across versions

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{placeins}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage[labelformat=empty]{caption}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis
Virus in a Turkey B-cell Line}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\captionsetup[table]{labelformat=empty}

\vspace{5mm}

\textbf{Running Title:} Novel Insights into Turkey Hemorrhagic Enteritis
Virus Transcriptome

\vspace{10mm}

Abraham Quaye\textsuperscript{1*}, Brett E. Pickett\textsuperscript{*},
Joel S. Griffitts\textsuperscript{*}, Bradford K.
Berges\textsuperscript{*}, Brian D.
Poole\({^\dagger}\)\textsuperscript{*}

\vspace{5mm}

\textsuperscript{*}Department of Microbiology and Molecular Biology,
Brigham Young University\\
\textsuperscript{1}First-author\\
\({^\dagger}\) Corresponding Author

\vspace{5mm}

\textbf{Corresponding Author Information}\\
\href{mailto:brian_poole@byu.edu}{\nolinkurl{brian\_poole@byu.edu}}\\
Department of Microbiology and Molecular Biology,\\
4007 Life Sciences Building (LSB),\\
Brigham Young University,\\
Provo, Utah\\
\newpage

\subsection{ABSTRACT}\label{abstract}

Characterizing the splice map of turkey hemorrhagic enteritis virus
(THEV) is an essential step that would allow studies of individual genes
mediating its immunosuppressive functions. We used an RNA-sequencing
experiment to characterize the transcriptome of THEV for the first time,
providing key insight into the THEV gene expression and mRNA structures.
Researchers previously annotated THEV's genome as encoding 23 open
reading frames (ORFs). In this work we identified 29 spliced transcripts
all of which consisted of novel exons although some exons matched some
previously annotated ORFs. The three annotated splice junctions were
also corroborated by our data. We performed PCR amplification of THEV
cDNA, cloned the PCR products, and used Sanger sequencing to validate
all identified splice junctions. During validation we identified five
additional unique transcripts, a subset of which were further validated
by 3' rapid amplification of cDNA ends (3' RACE) experiments. Thus, we
report that the genome of THEV contains 34 unique transcripts with the
coding capacity for all annotated ORFs. However, we found six of the
previously annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to
be truncated ORFs on the basis of the identification of an in-frame
upstream start codon or the detection of additional coding exons. We
also identified three of the annotated ORFs with longer or shorter
isoforms, and seven novel unpredicted ORFs that could potentially be
translated; although it is beyond the scope of this manuscript to
investigate whether they are translated. Similar to other adenoviruses
(AdVs), THEV also produces multiple distinctly spliced transcripts that
code for the same proteins across its genome. Our data show that all
THEV transcripts are spliced and organized into five transcription units
under the control of their cognate promoters like other AdVs. However,
our data suggest that the temporal regulation of THEV may be different
from other AdVs. \newpage

\subsection{INTRODUCTION}\label{introduction}

Adenoviruses (AdVs) are non-enveloped icosahedral-shaped DNA viruses,
causing infection in virtually all types of vertebrates studied to date.
Their double-stranded linear DNA genomes range between 26 and 45kb in
size, producing a broad repertoire of transcripts via highly complex
alternative splicing patterns (1, 2). The AdV genome is one of the most
optimally economized; both the forward and reverse DNA strands harbor
protein-coding genes, making it highly gene-dense. There are 16 genes
termed ``genus-common'' that are homologous in all AdVs; these are
thought to be inherited from a common ancestor. All other genes are
termed ``genus-specific''. The genus-specific genes tend to be located
at the termini of the genome while genus-common genes are usually
towards the center of the genome (1). This pattern is also observed in
\emph{Poxviridae} and \emph{Herpesviridae}, which also have linear DNA
genomes (1, 3, 4). The family \emph{Adenoviridae} consists of five
genera: \emph{Mastadenovirus} (MAdV), \emph{Aviadenovirus},
\emph{Atadenovirus}, \emph{Ichtadenovirus}, and \emph{Siadenovirus}
(SiAdV) to which turkey adenovirus 3 also called turkey hemorrhagic
enteritis virus (THEV) belongs (5--10). Members of SiAdV have the
smallest genome size (\textasciitilde26 kb) and gene content of all
known AdVs (see \textbf{Figure 1}) (1, 2, 6).

Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV
both infect turkeys, with THEV-V causing hemorrhagic enteritis (HE), a
debilitating acute disease predominantly affecting turkey poults
characterized by immunosuppression (IS), intestinal lesions leading to
bloody diarrhea, and up to 80\% mortality (2, 11--13). While the current
vaccine strain (a THEV-A strain isolated from a pheasant; Virginia
Avirulent Strain {[}VAS{]}) has proven effective at preventing HE in
turkey poults, it still retains its immunosuppressive ability. Thus,
vaccinated birds are rendered more susceptible to opportunistic
infections and death than unvaccinated birds leading to substantial
economic losses (11, 14--16). To eliminate the immunossupressive effect
of the vaccine strain, a thorough investigation of the culprit viral
genes mediating this phenomenon is essential. However, the transcriptome
(splicing and gene expression patterns) of THEV has not been
characterized, making an investigation of specific IS-related viral
genes impractical.

A myriad of studies have elucidated the AdV transcriptome in fine detail
(17, 18). However, a large preponderance of studies focus on MAdVs --
specifically human AdVs. Thus, most of the current knowledge regarding
AdV gene expression and replication is based on MAdV studies, which is
generalized for all other AdVs (10, 19). MAdV transcription is
temporally regulated; therefore, genes are categorized into five early
transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM)
units (pIX and IVa2), and one major late transcription unit (MLTU or
major late promoter {[}MLP{]} region), which generates five families of
late mRNAs (L1-L5) based on the polyadenylation site. An additional gene
(UXP or U exon) is located on the reverse strand. The early genes encode
non-structural proteins such as enzymes or host-cell modulating
proteins, primarily involved in DNA replication, or providing the
necessary intracellular niche for optimal replication while late genes
encode structural proteins that act as capsid proteins, promote virion
assembly, or direct genome packaging. The immediate early genes E1A are
expressed first, followed by the delayed early genes, E1B, E2, E3 and
E4. Then the intermediate early genes, IVa2 and pIX are expressed
followed by the late genes (10, 17, 18). It is noteworthy that the MLP
shows basal transcriptional activity during early infection (before DNA
replication), with a comparable efficiency to other early viral
promoters, but it reaches its maximal activity during late infection
(after DNA replication). However, during early infection only a subset
of the MLP-derived transcripts are expressed (10). MAdV makes an
extensive use of alternative RNA splicing to produce a very complex
array of mRNAs. All but the pIX mRNA undergo at least one splicing
event. For instance, the MLTU produces over 20 distinct splice variants
all of which contain three non-coding exons at the 5'-end (collectively
known as the tripartite leader; TPL) (17, 18). There is also an
alternate three-exon 5' non-coding leader sequence present in varying
amounts on a subset of MLTU mRNAs (known as the x-, y-, and z-leaders).
Lastly, there is the i-leader exon, which is infrequently included
between the second and third TPL exons, and codes for the i-leader
protein (20). Thus, the MLTU produces a complex repertoire of mRNA with
diverse 5' untranslated regions (UTRs) spliced onto different 3' coding
exons which are grouped into five different 3'-end classes (L1-L5) based
on polyadenylation site. Each transcription unit (TU) contains its own
promoter driving the expression of the array of mRNA transcripts
produced via alternative splicing in the unit (10, 17, 18). The
promoters are activated at different phases of the infection by proteins
from previously activated TUs. Paradoxically, the early-to-late phase
transition during infection requires the L4 gene products, 22K and 33K,
which should only be available after the transition. However, a promoter
in the L4 region (L4P) that directs the expression of these two proteins
independent of the MLP was found, resolving the paradox (10, 17, 21).
During translation of AdV mRNA, recent studies using long-read direct
RNA sequencing strongly suggest the potential usage of secondary start
codons; adding to what was already a highly complex system for gene
expression (17, 22).

High throughput sequencing methods have facilitated the discovery of
many novel transcribed regions and splicing isoforms. It is also a very
powerful tool to study alternative splicing under different conditions
at an unparalleled depth (18, 22, 23). In this paper, we use a
paired-end deep sequencing experiment to characterize, for the first
time, the transcriptome and splicing of THEV (VAS vaccine strain) during
different phases of the infection. Our paired-end sequencing allowed for
reading 149 bp long high quality (mean Phred Score of 36) sequences from
each end of cDNA fragments, which were mapped to the genome of THEV.
\newpage

\subsection{RESULTS}\label{results}

\textbf{Overview of sequencing data and analysis pipeline outputs}\\
A previous study by Aboezz \emph{et al} showed that almost all THEV
transcripts were detectable beginning at 4 hours, with a full
replication cycle of about 18-hours post infection (hpi) (24).
Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and
72-hpi to ensure a wide time window to sample all transcripts. Our
paired-end RNA sequencing (RNA-seq) experiment yielded an average of
107.1 million total reads of 149 bp in length per time-point, which were
simultaneously mapped to both the virus (THEV) and host (\emph{Meleagris
gallopavo}) genomes using the Hisat2 (25) reference-based aligner. A
total of 18.1 million reads from all time-points mapped to the virus
genome; this provided good coverage/depth, leaving no regions unmapped.
The mapped reads to the virus genome increased substantially from a mere
432 reads at 4 hpi to 16.9 million reads at 72 hpi (\textbf{Table 1},
\textbf{Figure 2A}). From the mapped reads, we identified a total of
2,457 unique THEV splice junctions from all time-points, with splice
junctions from the later time-points being supported by significantly
more sequence reads than earlier time-points. For example, all the 13
unique junctions at 4 hpi had less than 10 reads supporting each one,
averaging a mere 2.8 reads per junction. Conversely, the 2374 unique
junctions at 72 hpi averaged 898.4 reads per junction, some junctions
having coverage as high as 322,677 reads. The substantial increases in
splice junction and mapping reads to the THEV genome over time denotes
an active infection and a successful viral replication, and correlates
with our quantitative PCR (qPCR) assay quantifying the total number of
viral genome copies over time (\textbf{Figure 2B}).

Using StringTie (25), we assembled the data into potential transcripts
using the genomic location of the prior predicted THEV ORFs as a guide.
In the consolidated transcriptome, a composite of all non-redundant
transcripts from all time points, we counted a total of 29 novel
transcripts. We found that a subset of exons in the viral transcripts
match the predicted ORFs exactly, with the majority of the exons being
longer and spanning multiple predicted ORFs (\textbf{Figure 3}).

We then validated the splice junctions in all transcripts by PCR
amplification of viral cDNA, cloning, and Sanger sequencing
(\textbf{Supplementary PCR methods}). During validation, we identified
five additional transcripts, some of which were further validated by 3'
Rapid Amplification of cDNA Ends (3' RACE) data. The complete list of
unique splice junctions mapped to the THEV genome has been submitted to
the National Center for Biotechnology Information Gene Expression
Omnibus (\url{http://www.ncbi.nlm.nih.gov/geo}) under accession number
GSE254416.

\textbf{Changes in THEV splicing profile over time}\\
AdV gene expression occurs under exquisite temporal control with each
promoter typically producing one or few pre-mRNAs that undergo
alternative splicing to yield a repertoire of mature mRNAs. To evaluate
the activity of each promoter over time, StringTie and Ballgown (a
program for statistical analysis of assembled transcriptomes) (26) were
used to estimate the normalized expression levels of all transcripts for
each time point in Fragments Per Kilobase of transcript per Million
mapped reads (FPKM) units. Very few unique splice junctions, reads, and
transcripts were counted at 4 hpi; hence, this time point was excluded
in this analysis.

Considering individual mRNAs, TRXPT\_21 -- from the E2 region -- was the
most significantly expressed at 12 hpi, constituting 33.58\% of the
total expression of all transcripts. Transcripts in the E3 and E4
regions also contributed significant proportions, and noticeably, some
MLP region transcripts. The later time points were dominated by the MLP
region transcripts -- TRXPT\_10 and TRXPT\_14 were the most abundantly
expressed at 24 and 72 hpi, respectively, as expected (\textbf{Figure
4A}). When we performed analysis of the FPKM values of transcripts per
region we found a similar pattern: the E2 region was the most abundantly
expressed at 12 hpi, after which the MLP region assumes predominance
(\textbf{Figure 4B}). Secondly, we estimated relative abundances of all
splice junctions at each time point using the raw reads. Only junctions
with a read coverage of at least 1\% of the total splice junction reads
at the given time point were considered significant and included in
\textbf{Tables 2a-2c}. At 12 hpi, 18 junctions meet the 1\% threshold,
and were comprised of predominantly early region (E1, E2, E3, and E4)
junctions, albeit the MLTU was the single most preponderant region
overall, constituting 38.8\% of all the junction reads (\textbf{Table
2a} and \textbf{Supplementary Table S1a}). The most abundant junctions
at 12 hpi remained the most significantly expressed at 24 hpi also.
However, here, the MLP-derived junctions were unsurprisingly even more
preponderant overall, accounting for 45.7\% of all the junction reads
counted (\textbf{Table 2b} and \textbf{Supplementary Table S1b}). At 72
hpi, the trend of increased activity of the MLP continued as expected;
at this time, the MLP region junctions were not only the most abundant
overall -- accounting for 67.3\% of all junction reads, -- but also
contained the most significantly expressed individual junctions
(\textbf{Table 2c}, \textbf{Supplementary Table S1c} and \textbf{Figure
4C}). When we limited this analysis to only junctions in the final
transcriptome, we observed the relative abundances of the junctions for
each region over time to be similar to the pattern seen with all the
junctions included (\textbf{Figure 4D}).

We also analyzed splice donor and acceptor site nucleotide usage over
time to investigate any peculiarities that THEV may show, generally or
over the course of the infection. We found that most splice
donor-acceptor sequences were unsurprisingly the canonical GU-AG
nucleotides. However, the splice acceptor-donor pairing became less
specific over time, such that all combinations of nucleotide pairs were
eventually detected (\textbf{Figure 5}).

\textbf{Early Region 1 (E1) transcripts}\\
This region in MAdVs is the first transcribed after successful entry of
the viral DNA into the host cell nucleus, albeit at low levels (18). The
host transcription machinery solely mediates the transcription of this
region. After their translation, the E1 proteins in concert with a
myriad of host transcription factors activate other viral promoters
(10). In MAdVs, this region is subdivided into E1a and E2b units, but
the transcripts found in our data categorized under this region do not
appear to be subdivided.

Only two ORFs (ORF1 {[}sialidase{]} and Hyd) are predicted in this
region; however, we discovered four novel transcripts in this region,
which collectively contain 3 unique splice junctions (\textbf{Figure
6}). Most of the ORFs of the novel transcripts are distinct from the
predicted ORFs, but they all have the coding potential (CP) for the
predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary
start codon usage is considered as reported for other AdVs (17, 18). The
5'-most CDS of TRXPT\_1 is multi-exonic, encoding a novel 17.9
kilodalton (kDa), 160 residue {[}amino acids (aa){]} protein (ORF9).
From its 5'-most start codon (SC), TRXPT\_2 encodes the largest protein
in this region -- a 64.3 kDa, 580 aa protein (ORF10) with the same SC as
ORF9 (position 211 bp). ORF10 spans almost the entire predicted ORF1 and
Hyd, coming short in two regards: it is spliced from 1655 bp to 1964 bp
(ORF1's C-terminus, including the stop codon), and its stop codon (STC;
position 2312) is 13 bp short of the Hyd STC. However, it has an SC 102
bp upstream and in-frame with ORF1's predicted SC. Thus, ORF10 shares
substantial protein sequence similarity with ORF1 but not with Hyd, as
the SC of Hyd is not in-frame. Without its splice site removing the ORF1
STC, TRXPT\_2 would encode a longer variant of ORF1, starting from an
upstream SC. TRXPT\_3 is almost identical to TRXPT\_1, except for the
lack of TRXPT\_1's second exon. Our RNA-seq data show that all E1
transcripts share the same transcription termination site (TTS; at
position 2325 bp). However, TRXPT\_3 and TRXPT\_4 seem to have
transcription start sites (TSS) downstream of the TSS of TRXPT\_1 and
TRXPT\_2 (E1 TSS; position: 54 bp). Given that studies in MAdVs show
that E1 mRNAs share not only a common TTS but also the TSS, and only
differ from each other regarding the internal splicing (18), it is
likely that TRXPT\_3 and TRXPT\_4 are incomplete, and their actual TSS
just like the TTS are identical for all E1 transcripts. Regardless of
the TSS considered for TRXPT\_3, the CP remains unaffected. Its 5'-most
CDS, beginning at 1965 bp and sharing the same STC as ORF9, produces a
13.1 kDa, 115 residue protein (ORF4). ORF4 was predicted in an earlier
study (27) but was excluded in later studies (1, 12); however, our data
suggest it is a genuinely expressed ORF. Unlike TRXPT\_3, the CP of
TRXPT\_4 is affected by the TSS considered; if we consider its
unmodified TSS, then its CP is identical to TRXPT\_3. However, if we
assume that TRXPT\_4 uses the E1 TSS, then the 5'-most CDS is a
distinct, novel, multi-exonic 15.9 kDa, 143 aa protein (ORF11) with the
same SC as ORF9 and ORF10 but with a unique STC.

The splice junctions of all transcripts in this region (except the
junction for TRXPT\_4) were validated by cloning of viral cDNA and
Sanger sequencing (\textbf{Supplementary PCR methods}). During the
validation of TRXPT\_2, we found ORF1 to be present on the agarose gel
(an unspliced band size) and Sanger sequencing results showed it to be a
transcribed mRNA (\textbf{Supplementary PCR methods}). This was
corroborated by our 3' RACE experiment, which showed a transcript
(TRXPT\_2B) spanning the entire ORF1 and Hyd ORFs without any splicing,
with a poly-A tail immediately after the E1 TTS. The 5'-most CDS of this
transcript (TRXPT\_2B) would encode ORF1. However, TRXPT\_2B has an
upstream and in-frame SC to the predicted SC of ORF1, suggesting that
the predicted ORF1 CDS is truncated -- the actual ORF1 (eORF1) that is
expressed shares the same SC as ORF10, but has a unique STC.

\textbf{Early Region 2 (E2) and Intermediate Region (IM) transcripts}\\
The E2 TU expressed on the anti-sense strand is subdivided into E2A and
E2B and encodes three classical AdV proteins -- pTP and Ad-pol (E2B
proteins), and DBP (E2A protein) -- essential for genome replication
(17, 18). Unlike MAdV where two promoters (E2-early and E2-late) are
known (17), we discovered only a single TSS (E2 TSS; 18,751 bp) from
which both E2A and E2B transcription is initiated. However, similar to
MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B
transcripts share the TTS of the IVa2 transcript of the IM region (17,
18) (\textbf{Figure 7}).

The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from
two exons. The corresponding transcript (TRXPT\_21) found in our data
matches this predicted splice junction precisely but with a non-coding
additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
Thus, TRXPT\_21 is a three-exon transcript encoding DBP (380 residues,
43.3 kDa) precisely as predicted. This transcript (TRXPT\_21) was also
corroborated in a 3' RACE experiment. Additionally, from the 3' RACE
data, we found a splice variant of TRXPT\_21 which retains the second
intron leading to a 2-exon transcript. This new transcript (TRXPT\_21B),
albeit longer due to retaining the second intron and possessing a short
3' UTR, encodes a truncated isoform of DBP (tDBP) because the SC
utilized by TRXPT\_21, is followed shortly by STCs in the retained
intron. The SC 173 bp downstream of the DBP SC yields tDBP (a 346
residue, 39.3 kDa product), which is in-frame of DBP but entirely
contained in the second exon. TRXPT\_21 and TRXPT\_21B share a common
TTS but TRXPT\_21B as seen in our 3'-RACE data, extends 39 bp into an
adenine/thymine (A/T)-rich sequence before the poly-A tail sequence
occurs, suggesting this position (16,934 bp) as the true E2A TTS
(\textbf{Figure 7}).

The E2B region transcripts also start with the E2-5'UTR but extend
thousands of base pairs downstream to reach the TTS at 2334 bp in the IM
region, which is immediately followed by an A/T-rich sequence (position
2323-2339 bp) where polyadenylation probably occurs. Interestingly, the
TTS of the E1 region (position 2,325 bp) on the sense strand is also in
the immediate vicinity of this A/T-rich sequence, which is almost
palindromic; hence it likely serves as the polyadenylation signal for
both E1 and E2B/IM transcripts. The E2B transcripts TRXPT\_6 and
TRXPT\_7 are almost identical except for an extra splice junction at the
3'-end of TRXPT\_6, making TRXPT\_6 a five-exon transcript and TRXPT\_7,
four exons (\textbf{Figure 7}). TRXPT\_7 has the CP for both classical
proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF
is predicted to be spliced from two exons just like in all other AdVs.
The predicted splice junction of pTP is corroborated by our data;
however, the full transcript is markedly longer than the predicted ORF:
there are two novel non-coding 5' exons, the third exon (containing the
SC of pTP) is significantly longer than predicted, and the last exon
containing the bulk of the CDS is more than triple the predicted size of
pTP. The first two exons are 5'-UTRs because the SC here is immediately
followed by STCs; thus, the 5'-most SC (position 10,995 bp) of the third
exon which matches the predicted SC of pTP is utilized. The encoded
product is identical to the predicted pTP protein (597 residues; 70.5
kDa). If secondary SC (secSC) usage is considered, with SC at 6768 bp
and STC at 3430 bp, the encoded product is identical to the predicted
Ad-pol (polymerase) protein (1112 residues; 129.2 kDa). TRXPT\_6 differs
from TRXPT\_7 by containing an extra splice site at 3447-3515 bp.
However, the CP remains similar to that of TRXPT\_7 except the Ad-pol
encoded from the secSC is a truncated isoform with a new STC resulting
from the splice site.

While both TRXPT\_6 and TRXPT\_7 have the CP for Ad-pol with secSC
usage, in all AdVs studied, the two proteins (pTP and Ad-pol) are
encoded by separate mRNAs with identical first three 5' exons and TTS,
but the splice junction to the terminal exons are different. We checked
for a longer splice junction between the third and fourth (terminal)
exons of TRXPT\_7 with our junction validation method (targeted PCR,
cloning, and Sanger sequencing) and discovered a unique splice junction
(10,981-7062 bp) not found in our RNA-seq data. If initiated from the E2
TSS and terminated at the E2 TTS, this transcript (TRXPT\_31) would
encode Ad-pol exactly as predicted as its 5'-most CDS (\textbf{Figure
7}).

Our RNA-seq data also showed a novel short transcript (TRXPT\_15)
entirely nested within the terminal exon of TRXPT\_7 but with a unique
splice site. This transcript is an incomplete construction from the
mapped reads as it contains a truncated CDS. However, we validated this
splice junction to be genuine (\textbf{Supplementary PCR methods}).

The IM region is a single-transcript TU, encoding a single classical
protein, IVa2. The promoter expressing this single transcript (TRXPT\_5)
is embedded in E2B region and shares a TTS with E2B transcripts (17,
18). TRXPT\_5 is a two-exon transcript spliced exactly as the last
splice junction of TRXPT\_6. The first exon is a UTR, except the last 2
nucleotides, which connect with the first nucleotide of the second exon
to form the 5'-most SC. This first SC is 4 codons upstream and in-frame
of the predicted IVa2 SC. Except for the four extra N-terminus residues,
the entire protein sequence is identical to the predicted IVa2.

\textbf{Early Region 3 (E3) transcripts}.\\
The E3 region is wholly contained in the MLTU and encodes proteins
involved in modulating and evading the host immune defenses. In MAdVs,
this region contains seven ORFs expressed from several transcripts which
share the same TSS (from the E3 promoter) but have different TTSs (10,
17, 18). However, some E3 transcripts use the TSS of the MLP. Due to
sharing the same TSS, in MAdVs, secSC usage is heavily relied on for
gene expression in this region except for 12.5K and transcripts using
the MLP TSS, as utilizing only the first SC cannot produce all the other
transcripts in this TU (17).

In THEV, only one ORF (E3) was predicted in this region. However, as the
E3 TU is nested in the MLTU, transcripts from the L4P (100K, 22K, 33K,
and pVIII) not only overlap the E3 region transcripts entirely as seen
in our RNA-seq results, but also have their TSS and TTS in practically
the same locations (\textbf{Figure 8}). Therefore, we have categorized
these two groups together as E3 transcripts.

We identified seven novel transcripts here (TRXPT\_22, TRXPT\_23,
TRXPT\_24, TRXPT\_25, TRXPT\_26, TRXPT\_27, TRXPT\_29) from our RNA-seq
data, all originating from two distinct TSSs -- we consider the first
TSS (position 18,230 bp) as corresponding to the L4P and the other at
18,727 bp as corresponding to the E3 promoter (E3P). These E3
transcripts collectively have the CP for several predicted THEV ORFs:
100K, 22K, 33K, pVIII, and E3, as well as Fiber (IV) and ORF7 belonging
to the MLTU. But some of these CDSs are different than predicted due to
either unknown exons or the presence of an in-frame upstream SC. For
instance, 33K is one of the few THEV ORFs predicted to be spliced from
two exons; however, we discovered a significantly longer four-exon ORF
(e33K) on TRXPT\_24 that contains it almost entirely. The first two
exons of e33K were not predicted but the last two match the predicted
exons and the CDS is in-frame, albeit the first 20 bp of the predicted
33K (including the SC at 20,142 bp) is spliced out as part of the second
intron of TRXPT\_24. Thus, the bona fide 33K (e33K) is a 19.8 kDa, 171
residue protein spanning four exons instead of the predicted 120 aa
protein. TRXPT\_24 also has the CP for pVIII and E3 if we consider
downstream SC usage. However, the predicted E3 has an upstream in-frame
SC; thus, this longer version of E3 (eE3) is likely the genuinely
expressed ORF. TRXPT\_29 is the shortest transcript in this TU. It is a
two-exon transcript, both exons comprising the CDS. The product of
TRXPT\_29 is a novel 73 residue protein (8.3KI) sharing the SC of e33K
but with a unique STC. TRXPT\_23 being spliced identically as TRXPT\_29
also encodes 8.3KI from its first SC. Similarly, TRXPT\_22 also encodes
a 73 aa novel protein (8.3KII) from its first SC that shares over 80\%
similarity with 8.3KI, but it differs from 8.3KI at the C-terminus.
Considering downstream SC usage, both TRXPT\_22 and TRXPT\_23 can encode
pVIII and eE3 in that order, but TRXPT\_23 being longer, has the CP for
the Fiber ORF also.

As the splice junctions of TRXPT\_22, TRXPT\_23, TRXPT\_24, and
TRXPT\_29 essentially share the same genomic space, their validation was
done with a single primer pair, and they were differentiated from each
other by cloning and Sanger sequencing (\textbf{Supplementary PCR
methods}). In addition to corroborating the splice junctions for the
aforementioned transcripts, the Sanger sequencing results also showed
another splice variant undetected in our RNA-seq transcriptome. This was
a three-exon transcript (TRXPT\_30) with its first and last exons
spliced identically as TRXPT\_23, but which also has the second exon of
TRXPT\_24 (\textbf{Figure 8}). The first CDS on TRXPT\_30 spans all
three exons, producing a novel 140 residue, 15.7kDa protein.
Interestingly, the last 81 C-terminus residues of this new protein
(e22K) are identical to 22K (89 residues), which is a single-exon ORF
predicted to use the same SC as 33K (20,142 bp). Just as seen for 33K,
all the transcripts in this region exclude the first 20 bp of 22K
(including the SC) as part of their introns; therefore, the first 7
residues of 22K are lacking in e22K due to splicing. Hence, we consider
e22K as a long variant of the predicted 22K ORF. Albeit the TSS and TTS
of TRXPT\_30 was not seen, we presume that they are similar to
TRXPT\_23, in which case it would also have the downstream CP of
TRXPT\_23.

TRXPT\_25 is the largest transcript in the TU. It also utilizes the L4P
TSS but has a distinct TTS. It is a two-exon transcript, encoding a
novel protein (t100K; 543 residues), which is a shorter isoform of the
predicted 100K ORF. Considering secSC usage on this transcript yields
the predicted 22K ORF precisely as predicted. It also has the CP for
pVIII and eE3 in that order. Furthermore, during the validation of the
TRXPT\_25 splice junction using primers that span its junction
(18,350-18,717 bp), we noticed a DNA band that corresponds to the full
unspliced sequence (\textbf{Supplementary PCR methods}). As TRXPT\_25
only falls short of encoding the complete predicted 100K protein due to
its splice junction, this band (which we cloned and validated by Sanger
sequencing) suggests that the predicted 100K is indeed expressed. This
transcript (TRXPT\_25B) although not seen in full, likely shares the
same TSS and TTS as TRXPT\_25. Lastly, TRXPT\_26 and TRXPT\_27 both
originate from the E3P but have distinct TTSs. TRXPT\_26 is a three-exon
transcript but the first two are UTRs. It encodes pVIII as the 5'-most
ORF and has the CP for eE3 and Fiber in that order. TRXPT\_27 on the
other hand, is only a two-exon transcript that is similar to TRXPT\_26,
only the terminal exon contains the CDSs. It encodes Fiber as the
5'-most ORF, and ORF7 downstream with secSC usage. TRXPT\_13, which is
an L4 transcript that uses the MLP TSS is discussed under the MLTU
transcripts.

\textbf{Early Region 4 (E4) transcripts}\\
This TU is found at the tail-end (3'-end) of the genome and expressed
from the anti-sense strand. Based on nucleotide position, ORF7 and ORF8
were predicted in this region (1); however, as ORF7 is neither on the
same strand as ORF8 nor transcribed from a promoter in the E4 region,
only ORF8 can legitimately be classified as a transcript in this TU.
This is corroborated by our RNA-seq data, as only one transcript was
identified in this region on the anti-sense strand (\textbf{Figure 9}).
The transcript (TRXPT\_28) spans 25192-26247 bp and is spliced at
25701-26055 bp, making a two-exon transcript. The second exon fully
matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
However, there is an SC in the first exon at position 26246 bp (192 bp
upstream of the predicted SC). The encoded protein from this SC is
in-frame with the predicted SC found in the second exon; hence, we
consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of
the predicted ORF8, as the genuinely expressed ORF with an identical
C-terminus to the predicted ORF8 protein.

\textbf{Major Late Transcription Unit (MLTU) or MLP Region
transcripts}\\
The MLTU transcripts dominate the late phase (i.e, after DNA
replication) of the AdV infectious cycle. The MLP produces all late
mRNAs by alternative splicing and alternative polyadenylation of a
primary transcript, grouped into five transcript classes (L1-L5). Most
of the coding capacity of THEV falls within this TU. Specifically, about
13 out of the 23 predicted ORFs were assigned to this TU, some of which
we have categorized under the E3 TU instead. Our RNA-seq data revealed
12 transcripts (TRXPT\_8, TRXPT\_9, TRXPT\_10, TRXPT\_11, TRXPT\_12,
TRXPT\_13, TRXPT\_14, TRXPT\_16, TRXPT\_17, TRXPT\_18, TRXPT\_19,
TRXPT\_20) in this TU, the majority of which have the 5' untranslated
TPL sequence as seen in all AdVs. For three transcripts (TRXPT\_16,
TRXPT\_17, TRXPT\_18), a different leader sequence (sTPL) is used, which
differs from the TPL in only one regard: the first TPL exon is
substituted for a different first exon, found between the first and
second TPL exons. Also, TRXPT\_20 seems to include only the third TPL
exon (\textbf{Figure 10}).

We identified five TTSs (10,549 bp, 12,709 bp, 16,870 bp, 17,891 bp,
20,865 bp) in this TU, which we consider as corresponding to the five
late mRNA classes (L1-L5), respectively, as found in all AdVs. L1 mRNAs
include TRXPT\_8, which comprises the TPL (non-coding) and the
CDS-containing terminal exon. This transcript encodes the 52K ORF
exactly as predicted with the SC beginning from the first nucleotide of
the terminal exon. L2 mRNAs include TRXPT\_16, TRXPT\_17, and TRXPT\_18,
all of which consist of the sTPL (also non-coding) followed by their
respective terminal exons. TRXPT\_16 encodes pIIIa exactly as predicted
as the 5'-most ORF, and also has the CP for the ORFs, III and pVII in
that order. TRXPT\_17 encodes the ORF, III (penton), and TRXPT\_18
encodes the ORF pVII exactly as predicted. The L3 mRNAs include
TRXPT\_14 and TRXPT\_20, of which TRXPT\_14 utilizes the full TPL
whereas TRXPT\_20 uses only the third TPL exon (TPL3). Both transcripts
have the CP for the ORF, hexon (II) but hexon is the only ORF encoded on
TRXPT\_14, whereas the 5'-most ORF on TRXPT\_20 is pX (pre-Mu) followed
by pVI and hexon in that order. L4 mRNAs include TRXPT\_9, TRXPT\_10,
TRXPT\_11, and TRXPT\_13 all of which begin with the TPL followed by
three (TRXPT\_9, TRXPT\_10, and TRXPT\_13) or four (TRXPT\_11) coding
exons. These are the largest transcripts found in the transcriptome,
each one possessing the CP for several similar late proteins. Normally,
MLTU transcripts encoding particular ORFs splice the TPL onto a splice
site just upstream of the ORF to be expressed (17). While this holds
true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do
not have such close proximity splicing but are contained in larger
transcripts such as these L4 mRNAs, strongly suggesting the use of
non-standard ribosomal initiation mechanisms such as secSC utility and
ribosome shunting found in other AdVs for their translation (17, 28).
TRXPT\_9 and TRXPT\_10 are very similar but not identical. The last exon
of TRXPT\_9 seems to be truncated and probably shares the same TTS as
the other L4 mRNAs. They are both 6-exon transcripts encoding pVII as
the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a
longer variant of protease (eProt) -- uses an upstream in-frame SC than
predicted, and ORF12 (a novel unpredicted 120 aa protein). TRXTP\_10
(and TRXPT\_9 with the L4 TTS) additionally has the CP for pVIII and
eE3. Conversely, TRXPT\_11 is a seven-exon mRNA with hexon as its
5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also
pVIII and eE3 in that order. TRXPT\_13 seems to be an E3 ORF utilizing
the MLP TSS as it encodes classical L4P genes such as pVIII and eE3 in
that order similar to TRXPT\_22 (E3 TU) but it lacks the novel first ORF
(8.3KII) of TRXPT\_22.

Lastly, the L5 class includes only TRXPT\_12 which contains the TPL and
a coding terminal exon. Its 5'-most ORF is fiber (IV) but it also has
the CP for the THEV specific gene, ORF7. TRXPT\_12's CP is identical to
TRXPT\_27 of the E3 TU but they differ in their 5'-UTRs. \newpage

\subsection{DISCUSSION/CONCLUSIONS}\label{discussionconclusions}

While the advent of next-generation sequencing has rendered easier the
study of large and complex eukaryotic transcriptomes, the study of the
smaller and compact viral transcriptomes remains unintuitively
challenging, as several transcripts may have significant overlaps due to
genome economization. Characterizing AdV transcriptomes is even more
difficult due to the wide array of mRNAs produced via very complex
alternative splicing combined with alternative polyadenylation, all
initiated from relatively few promoters. This makes AdV transcriptomes
some of the most intricate for a virus. The challenge is further
compounded by the fact that the standard software programs used in the
RNA-seq analysis pipelines are not designed primarily for such compact,
gene-dense, and complex transcriptomes as AdVs. Furthermore, in our
case, there is no prior transcriptomic studies for THEV. Our approach to
properly handle this complex data was to use standard RNA-seq analysis
programs coupled with some custom analyses and experimentally validating
all splice junctions with independent methods. Our work provides the
first insights into the splicing patterns of THEV, which is expectedly
similar to other MAdVs but with key differences. Our work shows 34
transcripts in the THEV transcriptome grouped into five TUs, of which
the E3 TU shows great complexity of alternative splicing.

An unexpected observation is that the pileup of mapped reads to THEV
seems consistently skewed over similar regions of the genome at all time
points. As the gene expression of AdVs is temporally regulated, we
expected to see unambiguous differences in the pileup of reads over
different regions of the genome at different time points, indicating the
different stages of infection. While this could simply mean that the
infection was not well synchronized, we speculate that the temporal gene
expression regulation of THEV is probably different from MAdVs. This is
supported by a previous study stating the same conclusion with its
finding that almost all THEV transcripts were detectable by at 4h.p.i,
and by 8h.p.i, mRNA for all predicted ORFs (including the late genes)
were present (24). Conversely, despite the overall pileup similarity, a
close inspection shows that the relative proportions of reads over some
regions show some variation over time. The breakdown of transcripts
detected at different time points in \textbf{Figure 3b} seems to support
this different temporal regulation of THEV. Specifically, the MLP of
THEV is active significantly earlier in infection -- as early as 4h.p.i
and more pronounced at 12h.p.i (\textbf{Figure 3b} and \textbf{Table
2a}), -- whereas the late phase shift in MAdVs occurs after 24h.p.i.
This also lends credence to our speculation. However, generally
speaking, the overall temporal gene expression regulation known in MAdVs
-- early regions showing their peak expression at earlier time points
followed by predominance of the MLTU at later time points -- also holds
true for THEV. Further studies would be necessary to establish the
precise temporal regulation of THEV transcription.

The use of short read deep sequencing to reconstruct full AdV mRNA
structures provides excellent results, especially for mapping the splice
sites. However, due to the substantial overlapping nature of AdV mRNAs
coupled with the fragmentation step in the library preparation protocol,
mapping the precise TSS and TTS of the assembled transcripts is
difficult. Also, similar transcripts with substantial overlaps may be
assembled as one longer mRNA since the short reads alone do not provide
enough context for the transcript assembler (StringTie) to distinguish
them. In our results, we see transcripts in the same TU initiated or
terminated in the same approximate area (10-70 bp and 1-300 bp apart for
TSS and TTS, respectively) but not precisely at the same position. We
consider the most upstream TSS or most downstream TTS for the
transcripts involved but we present them unchanged in all the figures
shown. Also, by comparison to the more well-studied MAdV transcriptomes,
we believe that a few long transcripts in the MLTU (TRXPT\_9, TRXPT\_10,
and TRXPT\_11) are probably a result of fusing some L4P-derived
transcripts to the terminal exons of the bona fide MLTU transcripts by
StringTie, making them significantly longer. These mRNAs do not only
have unusually many exons for an AdV, but their last three or four exons
are also identical to the L4P-derived mRNAs. Future studies using long
read sequencing technologies are necessary to provide conclusive data
for precisely mapping the TSS and TTS, as well as teasing apart the bona
fide structures of the long MLTU transcripts. Furthermore, it is not
unreasonable to presume that several splice variants were undiscovered
in our work as evidenced firstly by finding unique transcripts using 3'
RACE and during our splice junction validation steps. And secondly,
recent studies (17, 18, 22) are still discovering novel mRNA variants
for even the best studied MAdVs decades later. Another observation made
is that all the TTSs in THEV's transcriptome are in close proximity to
A/T-rich sequences which we presume to be polyadenylation signal
sequences (PASS). Interestingly, some of these PASSs are located in the
immediate vicinity of two closely located TTSs expressed on opposite
strands. Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS
between them, as do the E4 (anti-sense strand) and the sense strand
TRXPT\_12 and TRXPT\_27.

An interesting finding of our analysis is that while most of the
predicted ORFs are precisely encoded by the spliced transcripts, we
found a few that seem to be truncated predictions, as either an upstream
in-frame SC (eORF1, eE3, and eProt) or unknown upstream exons spliced
onto them (eIVa2, e33K, and eORF8) were found. Other ORFs were
identified that were either shorter (tDBP, t100K) or longer (e22K)
isoforms of some predicted ORF but we found evidence to support the
predicted ORF itself, making them all possible genuinely translated
variants. We also found several novel unpredicted ORFs. Taken together,
we surmise that further studies will likely yield even more unpredicted
novel ORFs or variants of predicted ORFs.

Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most
AUG normally being used to determine the translation reading frame.
However, depending on the sequence context, in some organisms, the
initiating codon may even be a non-AUG start codon. AdV mRNAs, which
mostly span more than one ORF, are known to be functionally
polycistronic, employing non-standard mechanisms of translation
initiation, namely, secSC usage and ribosome shunting (10, 22). While
there is no reliable method of predicting how efficiently any given AUG
will be used, AdVs use secondary AUGs as initiation codons for most E1b
proteins and for some E3 proteins. In fact, recent studies show that
secSC usage is found transcriptome-wide. This is thought to occur
because translation initiation at the first SC is inefficient, allowing
downstream SCs to be employed for initiation (17). The ribosomal
shunting or jumping mechanism is utilized for MLTU transcripts that have
the TPL. This mechanism allows the ribosome to translocate to a
downstream initiating codon under the direction of the shunting elements
in the TPL, even if a start codon in a good Kozak sequence context is
bypassed. Thus, predicting the protein(s) that are expressed from an AdV
mRNA becomes highly uncertain as any one of the SC may be selected (10,
22). Almost all the THEV transcripts in our data have the CP for several
ORFs, some spanning as many as six ORFs but the majority spanning at
least two ORFs. Therefore, we believe our data support the usage of
these special ribosome initiation mechanisms as several predicted and
novel ORFs found on mRNA in our data have no conceivable mechanism of
being translated if only the typical ribosome scanning mechanism is
employed. Interestingly, several distinct transcripts have identical
CPs. This is not unique to THEV but is observed in human AdVs in a
recent study (17). They proposed that this may permit protein production
to be fine-tuned through alteration in the balance between different
mRNA groups expressing that ORF.

It is well established that AdV alternative splicing undergoes a
regulated temporal shift in splice site usage. This was thought to be
limited to certain TUs; however, recent studies suggest that AdVs
routinely produce different combinations of splice acceptor--donor pairs
and that this is observed in all TUs (10, 17, 22, 29). The mechanistic
details of this phenomenon have been best studied for the E1A and L1
units. The studies show that AdVs (specifically, late phase AdV-infected
nuclear extract) modulate the activities of the splicing factor U2AF and
the cellular SR family of splicing factors (reviewed in reference (29))
and encode several mostly late phase proteins (E4-ORF3, E4-ORF6,
E4-ORF4, L4-33K, and L4-22K) that influence the RNA splice site used.
This phenomenon seems to occur in the THEV transcriptome also, as the
stringency of splice acceptor-donor pairs selected decreases measurably
from the onset of the late phase (see \textbf{Figure 5}). In fact,
recent studies of some human AdVs show that a virtually unlimited number
of combinatorial alternative splicing events occur in an AdV lytic
infection, resulting in menagerie of novel transcripts (17, 22). It is
unlikely that the entire repertoire of mRNA produced via this mechanism
will actually be translated. However, it has been speculated that the
plasticity in alternative RNA splicing enables AdVs to fine-tune protein
synthesis by providing different alternatively spliced variants encoding
the same protein under changing conditions. The capacity to produce
novel exon combinations offers the virus an evolutionary advantage to
adjust the repertoire of mRNA transcription and protein production in
the changing environment of the viral replication cycle (17, 22).

Summarizing all the main points above, we see that the THEV
transcriptome bears remarkable overall similarity to the better studied
MAdVs. The transcriptome is organized into five TUs, the temporal
regulation is divided into early and late genes, and a broad repertoire
of transcripts are produced via virtually unlimited alternative
splicing. However, the THEV transcriptome appears to be less
sophisticated (i.e, it encodes fewer genes) than MAdVs primarily because
the MAdV genomes are close to twice as long as that of THEV, which
rationally should encode less genes. The lack of subdivision of the E1
region into E1a and E1b is one of the most obvious examples. Also, the
MAdV E4 region encodes several proteins unlike in THEV where only one
transcript coding for one protein was found. The most conspicuous
example is found in examining the complexity of the MLTU leader
sequences. While the majority of the THEV MLTU transcripts begin with
the TPL (267 bp long) just like MAdVs, and also utilize a variant leader
sequence (sTPL), it is well-established that significantly more diverse
5'UTRs are employed for MAdV MLTU transcripts. Namely, the TPL (used for
majority of transcripts), the so-called x, y, and z leaders, and the
i-leader are 5' leaders utilized by MAdV MLTU mRNAs. Granted, the MAdV
MLTU transcripts infrequently incorporate the non-TPL leaders, their
absence in our data could mean that the 5'UTR diversity of THEV's MLTU
mRNA are indeed more limited due to its smaller genome size. It is also
possible that later studies could uncover more variety not seen in our
results. Specifically, using long read sequencing technologies would be
a excellent approach to discovering and fine-tuning the transcriptome
characterized in this work. Also, it is likely that future studies
repeating this work in other cell lines will yield some interesting
insights. \newpage

\subsection{MATERIALS AND METHODS}\label{materials-and-methods}

\subsubsection{Cell culture and THEV
Infection}\label{cell-culture-and-thev-infection}

The Turkey B-cell line (MDTC-RP19, ATCC CRL-8135) was grown as
suspension cultures in 1:1 complete Leibovitz's L-15/McCoy's 5A medium
with 10\% fetal bovine serum (FBS), 20\% chicken serum (ChS), 5\%
tryptose phosphate broth (TPB), and 1\% antibiotic solution (100 U/mL
Penicillin and 100\(\mu g\)/mL Streptomycin), at 41\textsuperscript{o}C
in a humidified atmosphere with 5\% CO\textsubscript{2}. Infected cells
were maintained in 1:1 serum-reduced Leibovitz's L15/McCoy's 5A media
(SRLM) with 2.5\% FBS, 5\% ChS, 1.2\% TPB, and 1\% antibiotic solution.
A commercially available THEV vaccine was purchased from Hygieia
Biological Labs as a source of THEV-A (VAS strain). The stock virus was
titrated using an in-house qPCR assay with titer expressed as genome
copy number (GCN)/mL, similar to Mahshoub \emph{et al} (30) with
modifications. Cells were infected in triplicate at a multiplicity of
infection (MOI) of 100 GCN/cell, incubated at 41\textsuperscript{o}C for
1 hour, and washed three times with phosphate buffered saline (PBS) to
get rid of free virus particles. Triplicate samples were harvested at
4-, 12-, 24-, and 72-hpi for total RNA extraction. The infection was
repeated but samples in triplicate were harvested at 12-, 24-, 36-, 48-,
and 72-hpi for PCR validation of novel splice sites. Still one more
independent infection was done at time points ranging from 12 to 168-hpi
for qPCR quantification of virus titers.

\subsubsection{RNA extraction and
Sequencing}\label{rna-extraction-and-sequencing}

Total RNA was extracted from infected cells using the Thermofisher
RNAqueous™-4PCR Total RNA Isolation Kit (which includes a DNase I
digestion step) per manufacturer's instructions. An agarose gel
electrophoresis was performed to check RNA integrity. The RNA quantity
and purity was initially assessed using nanodrop, and RNA was used only
if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was
\textgreater2 and \textless2.2. Extracted total RNA samples were sent to
LC Sciences, Houston TX for poly-A-tailed mRNA sequencing where RNA
integrity was checked with Agilent Technologies 2100 Bioanalyzer High
Sensitivity DNA Chip and poly(A) RNA-seq library was prepared following
Illumina's TruSeq-stranded-mRNA sample preparation protocol. Paired-end
sequencing to generate 150 bp reads was performed on the Illumina
NovaSeq 6000 sequencing system.

\subsubsection{Validation of Novel Splice
Junctions}\label{validation-of-novel-splice-junctions}

All splice junctions identified in this work are novel except one
predicted splice site each for pTP, DBP, and 33K, which were
corroborated in our work. However, these predicted splice junctions had
not been experimentally validated hitherto, and we identified additional
novel exons, giving the complete picture of these transcripts. The novel
splice junctions discovered in this work using the StringTie transcript
assembler were validated by PCR, cloning, and Sanger Sequencing
(\textbf{Supplementary PCR methods}). Briefly, primers spanning a range
of novel exon-exon boundaries for each specific transcript in a
transcription unit (TU) were designed. Universal forward or reverse
primers for each respective TU were designed and paired with primers
binding specific positions in each transcript. Each forward primer
contained a KpnI restriction site and each reverse primer, an XbaI site
in the primer 5' ends. After first-strand cDNA synthesis of total RNA
obtained from THEV infected MDTC-RP19 cells was done using SuperScript™
IV First-Strand Synthesis System, the primers were used in a targeted
PCR amplification, the products analyzed with agarose gel
electrophoresis to confirm expected band sizes, cloned by traditional
restriction enzyme method, and Sanger sequenced to validate these splice
junctions at the sequence level. The total RNA was extracted as
described above, including the DNase I digestion step. We included
infected total RNA controls with no reverse transcriptase (no RT) during
the cDNA synthesis step and the parent RNA were digested using RNase H
after cDNA synthesis was complete to ensured that the bands obtained
from the targeted PCR amplifications did not originate from the viral
genomic DNA. As seen in the agarose gel images in \textbf{Supplementary
PCR methods}, DNA bands were not found in the ``no RT'' controls,
indicating that the DNA bands seen are of cDNA origin.

\subsubsection{3' Rapid Amplification of cDNA Ends (3'
RACE)}\label{rapid-amplification-of-cdna-ends-3-race}

A rapid amplification of sequences from the 3' ends of mRNAs (3' RACE)
experiment was performed using a portion of the extracted total RNA of
infected MDTC-RP19 cells used for the RNA-seq experiment as explained
above. We followed the protocol described by Green \emph{et al} (31)
with modifications. Briefly, 1\(\mu g\) of total RNA was reverse
transcribed to cDNA using SuperScript™ IV First-Strand Synthesis System
following the manufacturing instructions using an adapter-primer with a
3'-end poly(T) and a 5'-end BamHI restriction site. A gene-specific
sense primer with a 5'-end KpnI restriction site paired with an
anti-sense adapter-primer with a 5'-end BamHI site were used to amplify
target sections of the cDNA using Invitrogen's Platinum™ Taq DNA
polymerase High Fidelity, following manufacturer's instructions. The PCR
amplicons were restriction digested, cloned, and Sanger sequenced.

\subsubsection{Computational Analysis of RNA Sequencing Data: Mapping
and Transcript
characterization}\label{computational-analysis-of-rna-sequencing-data-mapping-and-transcript-characterization}

Sequencing reads were analyzed following a well-established protocol
described by Pertea \emph{et al} (25), using Snakemake - version 7.24.0
(32), a popular workflow management system to drive the pipeline.
Briefly, sequencing reads were trimmed with the Trim-galore - version
0.6.6 (33) program to achieve an overall Mean Sequence Quality (Phred
Score) of 36. Trimmed reads were mapped simultaneously to the complete
genomic sequence of avirulent turkey hemorrhagic enteritis virus
(\url{https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/}) and
\emph{Meleagris gallopavo}
(\url{https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo})
using Hisat2 - version 2.2.1 (25) with default settings. The generated
binary alignment (BAM) files from each infection time point were
filtered for reads mapping to the THEV genome using Samtools - version
1.16.1 and fed into StringTie - version 2.2.1 (25) to assemble the
transcripts, using a gene transfer format (GTF) annotation file derived
from a gene feature format 3 (GFF3) annotation file obtained from NCBI,
which contains the predicted ORFs of THEV as a guide. GFFCOMPARE -
version 0.12.6 was used to merge all transcripts from all time points
without redundancy and using a custom R script, adenovirus transcripts
units (regions) were assigned to each transcript, generating the
transcriptome of THEV. StringTie was set to expression estimation mode
to calculate FPKM scores for all transcripts after which Ballgown -
version 2.33.0 in R was used to perform the statistical analysis on the
transcript expression levels. Samtools was also used to count the total
sequencing reads for all replicates at each time point and Regtools -
version 1.0.0 was used to count all junctions, the reads supporting
them, and extract all other information related to the junction. See
\textbf{Supplementary Computational Analysis} for the details of
transcript expression level estimations and splice junction read counts.

\subsubsection{DATA AVAILABILITY}\label{data-availability}

The raw sequencing read data (FastQ), transcript expression counts, and
total unique junctions have been deposited at the National Center for
Biotechnology Information Gene Expression Omnibus
(\url{http://www.ncbi.nlm.nih.gov/geo}) under accession number
GSE254416.

Data is also available on request by contacting the designated
corresponding author.

\subsection{CODE AVAILABILITY}\label{code-availability}

All the code/scripts in the entire analysis pipeline are available on
github (\url{https://github.com/Abraham-Quaye/thev_transcriptome})

\subsection{ACKNOWLEDGMENTS}\label{acknowledgments}

We thank the Office of Research Computing at Brigham Young University
for granting us access to the high performance computing systems to
perform the memory-intensive steps in the analysis pipeline of this
work. \newpage

\subsection{REFERENCES}\label{references}

\setlength{\parindent}{-0.25in}
\setlength{\leftskip}{0.25in}

\noindent

\phantomsection\label{refs}
\begin{CSLReferences}{0}{1}
\bibitem[\citeproctext]{ref-Davison2003}
\CSLLeftMargin{1. }%
\CSLRightInline{Davison A, Benko M, Harrach B. 2003.
\href{https://doi.org/10.1099/vir.0.19497-0}{Genetic content and
evolution of adenoviruses}. The Journal of general virology
84:2895--908.}

\bibitem[\citeproctext]{ref-Harrach2008}
\CSLLeftMargin{2. }%
\CSLRightInline{Harrach B. 2008.
\href{https://doi.org/10.1016/B978-012374410-4.00680-4}{Adenoviruses:
General features}, p. 1--9. \emph{In} Mahy, BWJ, Van Regenmortel, MHV
(eds.), Encyclopedia of virology (third edition). Book Section. Academic
Press, Oxford.}

\bibitem[\citeproctext]{ref-Upton2003}
\CSLLeftMargin{3. }%
\CSLRightInline{Upton C, Slack S, Hunter AL, Ehlers A, Roper RL. 2003.
\href{https://doi.org/10.1128/jvi.77.13.7590-7600.2003}{Poxvirus
orthologous clusters: Toward defining the minimum essential poxvirus
genome}. Journal of virology 77:7590--7600.}

\bibitem[\citeproctext]{ref-McGeoch1999}
\CSLLeftMargin{4. }%
\CSLRightInline{McGeoch D, Davison AJ. 1999.
\href{https://doi.org/10.1016/B978-012220360-2/50018-0}{Chapter 17 - the
molecular evolutionary history of the herpesviruses}, p. 441--465.
\emph{In} Domingo, E, Webster, R, Holland, J (eds.), Origin and
evolution of viruses. Book Section. Academic Press, London.}

\bibitem[\citeproctext]{ref-Harrach2011}
\CSLLeftMargin{5. }%
\CSLRightInline{Harrach B, Benko M, Both GW, Brown M, Davison AJ,
Echavarría M, Hess M, Jones M, Kajon A, Lehmkuhl HD, Mautner V, Mittal
S, Wadell G. 2011. Family adenoviridae. Virus Taxonomy: 9th Report of
the International Committee on Taxonomy of Viruses 125--141.}

\bibitem[\citeproctext]{ref-Kovuxe1cs2011}
\CSLLeftMargin{6. }%
\CSLRightInline{Kovács ER, Benkő M. 2011.
\href{https://doi.org/10.1016/j.meegid.2011.03.021}{Complete sequence of
raptor adenovirus 1 confirms the characteristic genome organization of
siadenoviruses}. Infection, Genetics and Evolution 11:1058--1065.}

\bibitem[\citeproctext]{ref-Davison2000}
\CSLLeftMargin{7. }%
\CSLRightInline{Davison AJ, Wright KM, Harrach B. 2000.
\href{https://doi.org/10.1099/0022-1317-81-10-2431}{DNA sequence of frog
adenovirus}. J Gen Virol 81:2431--2439.}

\bibitem[\citeproctext]{ref-Kovuxe1cs2010}
\CSLLeftMargin{8. }%
\CSLRightInline{Kovács ER, Jánoska M, Dán Á, Harrach B, Benkő M. 2010.
\href{https://doi.org/10.1016/j.jviromet.2009.10.007}{Recognition and
partial genome characterization by non-specific DNA amplification and
PCR of a new siadenovirus species in a sample originating from parus
major, a great tit}. Journal of Virological Methods 163:262--268.}

\bibitem[\citeproctext]{ref-Katoh2009}
\CSLLeftMargin{9. }%
\CSLRightInline{Katoh H, Ohya K, Kubo M, Murata K, Yanai T, Fukushi H.
2009. \href{https://doi.org/10.1016/j.virusres.2009.04.012}{A novel
budgerigar-adenovirus belonging to group II avian adenovirus of
siadenovirus}. Virus Research 144:294--297.}

\bibitem[\citeproctext]{ref-Guimet2016}
\CSLLeftMargin{10. }%
\CSLRightInline{Guimet D, Hearing P. 2016.
\href{https://doi.org/10.1016/B978-0-12-800276-6.00003-6}{3 - adenovirus
replication}, p. 59--84. \emph{In} Curiel, DT (ed.), Adenoviral vectors
for gene therapy (second edition). Book Section. Academic Press, San
Diego.}

\bibitem[\citeproctext]{ref-Beach2006}
\CSLLeftMargin{11. }%
\CSLRightInline{Beach NM. 2006.
\href{http://scholar.lib.vt.edu/theses/available/etd-08142006-145339/}{Characterization
of avirulent turkey hemorrhagic enteritis virus: A study of the
molecular basis for variation in virulence and the occurrence of
persistent infection}. Thesis.}

\bibitem[\citeproctext]{ref-Beach2009a}
\CSLLeftMargin{12. }%
\CSLRightInline{Beach NM, Duncan RB, Larsen CT, Meng XJ, Sriranganathan
N, Pierson FW. 2009.
\href{https://doi.org/10.1099/vir.0.010090-0}{Comparison of 12 turkey
hemorrhagic enteritis virus isolates allows prediction of genetic
factors affecting virulence}. J Gen Virol 90:1978--85.}

\bibitem[\citeproctext]{ref-Gross1967}
\CSLLeftMargin{13. }%
\CSLRightInline{Gross WB, Moore WE. 1967. Hemorrhagic enteritis of
turkeys. Avian Dis 11:296--307.}

\bibitem[\citeproctext]{ref-Rautenschlein2000}
\CSLLeftMargin{14. }%
\CSLRightInline{Rautenschlein S, Sharma JM. 2000.
\href{https://doi.org/10.1016/s0145-305x(99)00075-0}{Immunopathogenesis
of haemorrhagic enteritis virus (HEV) in turkeys}. Dev Comp Immunol
24:237--46.}

\bibitem[\citeproctext]{ref-Larsen1985}
\CSLLeftMargin{15. }%
\CSLRightInline{Larsen CT, Domermuth CH, Sponenberg DP, Gross WB. 1985.
Colibacillosis of turkeys exacerbated by hemorrhagic enteritis virus.
Laboratory studies. Avian Dis 29:729--32.}

\bibitem[\citeproctext]{ref-Dhama2017}
\CSLLeftMargin{16. }%
\CSLRightInline{Dhama K, Gowthaman V, Karthik K, Tiwari R, Sachan S,
Kumar MA, Palanivelu M, Malik YS, Singh RK, Munir M. 2017.
\href{https://doi.org/10.1080/01652176.2016.1277281}{Haemorrhagic
enteritis of turkeys -- current knowledge}. Veterinary Quarterly
37:31--42.}

\bibitem[\citeproctext]{ref-Donovan2020}
\CSLLeftMargin{17. }%
\CSLRightInline{Donovan-Banfield I, Turnell AS, Hiscox JA, Leppard KN,
Matthews DA. 2020. \href{https://doi.org/10.1038/s42003-020-0849-9}{Deep
splicing plasticity of the human adenovirus type 5 transcriptome drives
virus evolution}. Communications Biology 3:124.}

\bibitem[\citeproctext]{ref-Zhao2014}
\CSLLeftMargin{18. }%
\CSLRightInline{Zhao H, Chen M, Pettersson U. 2014.
\href{https://doi.org/10.1016/j.virol.2014.04.006}{A new look at
adenovirus splicing}. Virology 456-457:329--341.}

\bibitem[\citeproctext]{ref-Wolfrum2013}
\CSLLeftMargin{19. }%
\CSLRightInline{Wolfrum N, Greber UF. 2013.
\href{https://doi.org/10.1111/cmi.12053}{Adenovirus signalling in
entry}. Cell Microbiol 15:53--62.}

\bibitem[\citeproctext]{ref-Falvey1983}
\CSLLeftMargin{20. }%
\CSLRightInline{Falvey E, Ziff E. 1983.
\href{https://doi.org/10.1128/jvi.45.1.185-191.1983}{Sequence
arrangement and protein coding capacity of the adenovirus type 2 "i"
leader}. Journal of Virology 45:185--191.}

\bibitem[\citeproctext]{ref-Morris2010}
\CSLLeftMargin{21. }%
\CSLRightInline{Morris SJ, Scott GE, Leppard KN. 2010.
\href{https://doi.org/10.1128/jvi.00107-10}{Adenovirus late-phase
infection is controlled by a novel L4 promoter}. Journal of Virology
84:7096--7104.}

\bibitem[\citeproctext]{ref-Westergren2021}
\CSLLeftMargin{22. }%
\CSLRightInline{Westergren Jakobsson A, Segerman B, Wallerman O,
Bergström Lind S, Zhao H, Rubin C-J, Pettersson U, Akusjärvi G. 2021.
\href{https://doi.org/10.1128/jvi.01869-20}{The human adenovirus 2
transcriptome: An amazing complexity of alternatively spliced mRNAs}.
Journal of Virology 95.}

\bibitem[\citeproctext]{ref-Djebali2012}
\CSLLeftMargin{23. }%
\CSLRightInline{Djebali S, Davis CA, Merkel A, Dobin A, Lassmann T,
Mortazavi A, Tanzer A, Lagarde J, Lin W, Schlesinger F, Xue C, Marinov
GK, Khatun J, Williams BA, Zaleski C, Rozowsky J, Röder M, Kokocinski F,
Abdelhamid RF, Alioto T, Antoshechkin I, Baer MT, Bar NS, Batut P, Bell
K, Bell I, Chakrabortty S, Chen X, Chrast J, Curado J, Derrien T,
Drenkow J, Dumais E, Dumais J, Duttagupta R, Falconnet E, Fastuca M,
Fejes-Toth K, Ferreira P, Foissac S, Fullwood MJ, Gao H, Gonzalez D,
Gordon A, Gunawardena H, Howald C, Jha S, Johnson R, Kapranov P, King B,
Kingswood C, Luo OJ, Park E, Persaud K, Preall JB, Ribeca P, Risk B,
Robyr D, Sammeth M, Schaffer L, See L-H, Shahab A, Skancke J, Suzuki AM,
Takahashi H, Tilgner H, Trout D, Walters N, Wang H, Wrobel J, Yu Y, Ruan
X, Hayashizaki Y, Harrow J, Gerstein M, Hubbard T, Reymond A,
Antonarakis SE, Hannon G, Giddings MC, Ruan Y, Wold B, Carninci P, Guigó
R, Gingeras TR. 2012.
\href{https://doi.org/10.1038/nature11233}{Landscape of transcription in
human cells}. Nature 489:101--108.}

\bibitem[\citeproctext]{ref-Aboezz2019}
\CSLLeftMargin{24. }%
\CSLRightInline{Aboezz Z, Mahsoub H, El-Bagoury G, Pierson F. 2019.
\href{https://www.sciencedirect.com/science/article/abs/pii/S016817021830529X?via\%3Dihub}{In
vitro growth kinetics and gene expression analysis of the turkey
adenovirus 3, a siadenovirus}. Virus Research 263:47--54.}

\bibitem[\citeproctext]{ref-Pertea2016}
\CSLLeftMargin{25. }%
\CSLRightInline{Pertea M, Kim D, Pertea GM, Leek JT, Salzberg SL. 2016.
\href{https://doi.org/10.1038/nprot.2016.095}{Transcript-level
expression analysis of RNA-seq experiments with HISAT, StringTie and
ballgown}. Nature Protocols 11:1650--1667.}

\bibitem[\citeproctext]{ref-Ballgown}
\CSLLeftMargin{26. }%
\CSLRightInline{Jack Fu {[}Aut{]}, Alyssa C. Frazee {[}Aut, Cre{]},
LeonardoCollado-Torres {[}Aut{]}, Andrew E. Jaffe {[}Aut{]}, Jeffrey T.
Leek{[}Aut, Ths{]}. 2017.
\href{https://doi.org/10.18129/B9.BIOC.BALLGOWN}{Ballgown}.
Bioconductor.}

\bibitem[\citeproctext]{ref-Pitcovski1998}
\CSLLeftMargin{27. }%
\CSLRightInline{Pitcovski J, Mualem M, Rei-Koren Z, Krispel S, Shmueli
E, Peretz Y, Gutter B, Gallili GE, Michael A, Goldberg D. 1998.
\href{https://doi.org/10.1006/viro.1998.9336}{The complete {DNA}
sequence and genome organization of the avian adenovirus, hemorrhagic
enteritis virus}. Virology 249:307--315.}

\bibitem[\citeproctext]{ref-Yueh1996}
\CSLLeftMargin{28. }%
\CSLRightInline{Yueh A, Schneider RJ. 1996.
\href{https://doi.org/10.1101/gad.10.12.1557}{Selective translation
initiation by ribosome jumping in adenovirus-infected and heat-shocked
cells.} Genes \&amp; Development 10:1557--1567.}

\bibitem[\citeproctext]{ref-Akusjarvi2008}
\CSLLeftMargin{29. }%
\CSLRightInline{Akusjarvi G. 2008.
\href{https://doi.org/10.2741/3059}{Temporal regulation of adenovirus
major late alternative RNA splicing}. Frontiers in Bioscience
Volume:5006.}

\bibitem[\citeproctext]{ref-Mahsoub2017}
\CSLLeftMargin{30. }%
\CSLRightInline{Mahsoub HM, Evans NP, Beach NM, Yuan L, Zimmerman K,
Pierson FW. 2017.
\href{https://doi.org/10.1016/j.jviromet.2016.11.002}{Real-time
{PCR}-based infectivity assay for the titration of turkey hemorrhagic
enteritis virus, an adenovirus, in live vaccines}. Journal of
Virological Methods 239:42--49.}

\bibitem[\citeproctext]{ref-Green2019}
\CSLLeftMargin{31. }%
\CSLRightInline{Green MR, Sambrook J. 2019.
\href{https://doi.org/10.1101/pdb.prot095216}{Rapid amplification of
sequences from the 3' ends of mRNAs: 3'-RACE}. Cold Spring Harbor
Protocols 2019:pdb.prot095216.}

\bibitem[\citeproctext]{ref-Snakemake2021}
\CSLLeftMargin{32. }%
\CSLRightInline{Mölder F, Jablonski KP, Letcher B, Hall MB,
Tomkins-Tinch CH, Sochat V, Forster J, Lee S, Twardziok SO, Kanitz A,
Wilm A, Holtgrewe M, Rahmann S, Nahnsen S, Köster J. 2021.
\href{https://doi.org/10.12688/f1000research.29032.2}{Sustainable data
analysis with snakemake}. F1000Research 10:33.}

\bibitem[\citeproctext]{ref-TrimGalore}
\CSLLeftMargin{33. }%
\CSLRightInline{Krueger F, James F, Ewels P, Afyounian E, Weinstein M,
Schuster-Boeckler B, Hulselmans G, Sclamons. 2023.
\href{https://doi.org/10.5281/ZENODO.7598955}{FelixKrueger/TrimGalore:
v0.6.10 - add default decompression path}. Zenodo.}

\end{CSLReferences}

\setlength{\parindent}{0in}
\setlength{\leftskip}{0in}
\newpage

\newpage

\subsection{TABLES AND FIGURES}\label{tables-and-figures}

\begin{figure}
\centering
\includegraphics{results/r/figures/thev_orf_map.png}
\caption{\textbf{Figure 1. Predicted ORF map of THEV avirulent strain.}
The central horizontal line represents the double-stranded DNA marked at
5kb intervals as white line breaks. Colored blocks represent viral
genes. Blocks above the DNA line are transcribed on the sense DNA strand
and those below, on the anti-sense strand. pTP, DBP and 33K are
predicted to be spliced and are shown as two exons connected with dashed
lines. Shaded regions indicate regions containing ``genus-specific''
genes (colored red). Genes colored in blue are ``genus-common''. The
gene colored in light green is conserved in all but Atadenoviruses.
Regions comprising the different transcription units are labelled at the
bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise
the MLTU.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/fig_2.png}
\caption{\textbf{Figure 2: Increasing levels of THEV over time. A) Per
base coverage of sequence reads mapping to THEV genome by time point.}
The pileup of mRNA reads mapping to THEV genome at the base-pair level
for each indicated time point. \textbf{B) Growth curve of THEV (VAS
vaccine strain) in MDTC-RP19 cell line.} Virus titers in the
freeze-thawed supernatant from infected cells were a quantified with a
qPCR assay. There is no discernible increase in virus titer up 12 hpi,
after which a steady increase in virus titer is measured. The virus
titer expands exponentially beginning from 48 hpi, increasing by orders
of magnitude before reaching a plateau at 120 hpi. GCN: genome copy
number.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure3.png}
\caption{\textbf{Figure 3. A) Transcriptome of THEV from RNA-seq.} THEV
transcripts assembled from all time points by StringTie are unified
forming this final transcriptome (splicing map). Transcripts belonging
to the same transcription unit (TU) are located in close proximity on
the genome and are color coded and labeled in this figure as such. The
organization of TUs in the THEV genome is unsurprisingly similar to
MAdVs; however, the MAdV genome shows significantly more transcripts.
The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark
grey, E4 - green, MLTU - blue. Predicted ORFs are also indicated here,
colored light grey. \textbf{B) THEV transcripts identified at given time
points.} Transcripts are color coded as explained in \textbf{(A)}.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_4a_d.png}
\caption{\textbf{Figure 4: Changes in splicing and expression profile of
THEV over time.} \textbf{A) Normalized (FPKM) expression levels of
transcripts over time.} The expression levels (FPKM) of individual
transcripts as a percentage of the total expression of all transcripts
at each time point are indicated. Only transcripts from our RNA-seq data
are included here. \textbf{B) Normalized (FPKM) expression levels of
transcripts by region over time.} The expression levels of each
region/TU as a percentage of the total expression of all transcripts at
each time point are indicated. Region expression levels were calculated
by summing up the FPKMs of all transcripts categorized in that region.
\textbf{C) Relative abundances of all splice junctions grouped by
region/TU over time.} After assigning all 2,457 unique junctions to a TU
and the total junction reads counted at each time point for each region,
the total junction reads for each TU were plotted as percentages of all
junction reads at each time point. Note that the junction read counts
are not normalized. \textbf{D) Relative abundances of junctions in
transcriptome grouped by region/TU over time.} This is identical to
\textbf{(C)}, except that only the junctions found in the full
transcriptome obtained from the RNA-seq data were included.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_5a_d.png}
\caption{\textbf{Figure 5: Changes in splice donor-acceptor nucleotides
over time.} The splice donor-acceptor nucleotides of THEV just like
other AdVs is mostly the canonical GU-AG. At early time points (4h.p.i
and 12h.p.i \textbf{(A)} and \textbf{(B)}, respectively) the junction
nucleotides used appear to be well scrutinized or restricted, utilizing
mostly the canonical splice nucleotides. However, as the infection
progresses to the late stages (24h.p.i and 72h.p.i \textbf{(C)} and
\textbf{(D)}, respectively), the selectivity of specific splice
acceptor-donor pairs seems to degenerate significantly, such that all
combinations of nucleotides are utilized.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_6.png}
\caption{\textbf{Figure 6: The splice map of the E1 transcription unit
(TU).} Exons are depicted as boxes connected by introns (dotted lines).
Transcripts from RNA-seq data are colored red, predicted ORFs are
colored grey, and transcripts or ORFs discovered by other means are
colored black. Each transcript or ORF is labelled with its name to the
right. The start codon (SC) and stop codon (STC) of the 5'-most CDS of
each transcript is indicated with the nucleotide position in brackets.
The region of the virus is depicted at the bottom as a black line with
labels of the nucleotide positions for reference. The table shows
sequence reads covering the splice junctions with information about
their validation status using cloning and Sanger sequencing.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_7.png}
\caption{\textbf{Figure 7: The splice map of the E2 and IM TUs.} Exons
are depicted as boxes connected by introns (dotted lines). Red
transcripts are generated from RNA-seq data and predicted ORFs are
colored grey. TRXPT\_21B discovered by 3'RACE is colored black. Each
transcript or ORF is labelled with its name to the right. The SC and STC
of the 5'-most CDS of each transcript are indicated with the nucleotide
position in brackets. The region of the virus is depicted at the bottom
as a black line with labels of the nucleotide positions for reference.
The table shows sequence reads covering the splice junctions with
information about their validation status using cloning and Sanger
sequencing.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_8.png}
\caption{\textbf{Figure 8: The splice map of the E3 TU.} Exons are
depicted as boxes connected by introns (dotted lines). Red transcripts
are generated from RNA-seq data and predicted ORFs are colored grey.
Transcripts discovered by other means are colored black. Each transcript
or ORF is labelled with its name to the right. The start codon (SC) and
stop codon (STC) of the 5'-most CDS of each transcript are indicated
with the nucleotide position in brackets. Similarly, the secondary SC
(secSC) and secondary STC (secSTC) are shown. The region of the virus is
depicted at the bottom as a black line with labels of the nucleotide
positions for reference. The table shows sequence reads covering the
splice junctions with information about their validation status using
cloning and Sanger sequencing.}
\end{figure}

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_9.png}
\caption{\textbf{Figure 9: The splice map of the E4 TU.} Exons are
depicted as boxes connected by introns (dotted lines). The transcript
from RNA-seq data is colored red and the predicted ORF, grey. The
transcript and ORF are labelled with their names to the right. The start
codon (SC) and stop codon (STC) of the 5'-most CDS are indicated with
the nucleotide position in brackets. The region of the virus is depicted
at the bottom as a black line with labels of the nucleotide positions
for reference. The table shows sequence reads covering the splice
junction with its validation status using cloning and Sanger
sequencing.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{results/r/figures/figure_10.png}
\caption{\textbf{Figure 10: The splice map of the MLTU.} Exons are
depicted as boxes connected by introns (dotted lines). The transcripts
from our RNA-seq data are colored red and the predicted ORFs, grey. The
transcripts and ORFs are labelled with their names to the right. The
start codon (SC) and stop codon (STC) of the 5'-most CDS of each
transcript is indicated with the nucleotide position in brackets.
Similarly, the secondary SC (secSC) and secondary STC (secSTC) are
shown. The region of the virus is depicted at the bottom as a black line
with labels of the nucleotide positions for reference. The table shows
sequence reads covering the splice junctions with information about
their validation status using cloning and Sanger sequencing.}
\end{figure}

\newpage

\FloatBarrier

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{1.50in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{Table\ 1:\ Overview\ of\ sequencing\ results}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Metric}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{4h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{12h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{24h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{72h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Metric}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{4h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{12h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{24h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{72h.p.i}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.17e+08}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7.63e+07}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.20e+08}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.15e+08}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4.28e+08}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Mapped\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ (Host)}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.04e+08\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(89.06\%)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6.79e+07\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(89.0393\%)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.06e+08\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(88.2719\%)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{8.38e+07\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(72.9802\%)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3.62e+08}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Mapped\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ (THEV)}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4.32e+02\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(\ 0.0004\%)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6.70e+03\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(\ 0.0088\%)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.18e+06\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(\ 0.9841\%)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.69e+07\ }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{(14.6904\%)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.81e+07}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Mean\ Per\ Base\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ Coverage/Depth}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2.42}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{37.71}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\ 6,666.96}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\ 95,041.7}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{101,749}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ unique\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ splice\ junctions}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{37}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{236}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2374}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,457}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Junction\ coverage\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ Total\ (at\ least\ 1\ read)}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{37}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{605}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{115075}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2132806}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2.25e+06}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Junction\ coverage\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ Mean\ reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2.8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{16.4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{487.6}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{898.4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{351.3}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Junction\ coverage\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ (at\ least\ 10\ reads)}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{132}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1791}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,936}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Junction\ coverage\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ (at\ least\ 100\ reads)}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{53}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{805}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{859}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Junction\ coverage\ }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{\ (at\ least\ 1000\ reads)}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{168}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{186}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\FloatBarrier

\newpage

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{1.20in}}

\caption{Table\ 2a:\ Most\ abundant\ splice\ junctions\ at\ 12h.p.i}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{103\ (17\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{CU-AC}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{97\ (16\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{58\ (9.6\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,701}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26,055}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{354\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{37\ (6.1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{33\ (5.5\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{32\ (5.3\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22\ (3.6\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21\ (3.5\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21\ (3.5\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18\ (3\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18\ (3\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14\ (2.3\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,682}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,931\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10\ (1.7\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,312\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{9\ (1.5\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{9\ (1.5\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,163}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{76\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{8\ (1.3\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7\ (1.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6\ (1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\newpage

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{1.20in}}

\caption{Table\ 2b:\ Most\ abundant\ splice\ junctions\ at\ 24h.p.i}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,825\ (16.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{CU-AC}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{17,670\ (15.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,319\ (10.7\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,583\ (9.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,128\ (6.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6,619\ (5.8\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,207\ (4.5\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,930\ (3.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,870\ (3.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,553\ (2.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,446\ (2.1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,642\ (1.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,395\ (1.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,910\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,391\ (1.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,124\ (1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,128}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,377\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,124\ (1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,894}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{671\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,208\ (1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\newpage

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{1.20in}}

\caption{Table\ 2c:\ Most\ abundant\ splice\ junctions\ at\ 72h.p.i}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{322,677\ (15.1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{179,607\ (8.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{161,336\ (7.6\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{CU-AC}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{146,425\ (6.9\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{93,238\ (4.4\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{81,420\ (3.8\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{77,616\ (3.6\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{45,062\ (2.1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38,491\ (1.8\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38,841\ (1.8\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{35,490\ (1.7\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,312\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,041\ (1.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26,338\ (1.2\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,904}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,097\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,946\ (1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,891\ (1\%)}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\newpage

\subsection{SUPPLEMENTARY MATERIALS}\label{supplementary-materials}

\textbf{Supplementary Table S1A}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}}

\caption{Table\ S1a:\ Most\ Transcriptionally\ Active\ Regions\ of\ THEV\ at\ 12h.p.i}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Time}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ Reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Percentage}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Time}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ Reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Percentage}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{235}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38.8\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{161}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26.6\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{104}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{17.2\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{40}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6.6\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{Unassigned}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-,+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{40}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6.6\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3.3\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{IM}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0.8\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\textbf{Supplementary Table S1B}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}}

\caption{Table\ S1b:\ Most\ Transcriptionally\ Active\ Regions\ of\ THEV\ at\ 24h.p.i}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Time}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ Reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Percentage}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Time}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ Reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Percentage}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{52,589}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{45.7\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{29,208}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25.4\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{27,833}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24.2\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,724}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2.4\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{Unassigned}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-,+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,313}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.1\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{IM}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{744}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0.6\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{664}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0.6\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\textbf{Supplementary Table S1C}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}}

\caption{Table\ S1c:\ Most\ Transcriptionally\ Active\ Regions\ of\ THEV\ at\ 72h.p.i}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Time}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ Reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Percentage}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Time}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Total\ Reads}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Percentage}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,436,199}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{67.3\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304,191}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14.3\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{271,310}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12.7\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{74,135}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3.5\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{Unassigned}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-,+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{28,921}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1.4\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{IM}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,482}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0.7\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,568}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0.2\%}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\newpage

\textbf{Supplementary PCR Methods}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{1.10in}|p{1.10in}|p{1.15in}}

\caption{Agarose\ Gels\ Showing\ PCR\ Amplification\ of\ THEV\ cDNA\ With\ Gene-Specific\ Primers}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Transcript\ ID}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Number\ of\ Exons}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Full\ Transcript}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 1}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 2}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 3}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 4}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 5}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 6}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 7}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Forward\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Reverse\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Agarose\ Gel}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Transcript\ ID}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Number\ of\ Exons}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Full\ Transcript}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 1}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 2}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 3}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 4}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 5}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 6}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 7}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Forward\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Reverse\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Agarose\ Gel}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\endhead

\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{FFFFFF}

\endfoot

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-1655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTTCTGTTTGAATTGTGGGCGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-1.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-1655}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGCCTGTTGGAATTGTTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-2.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{225-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{225-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCATTTCCCGTACACGGTGTTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-3.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{271-2303}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{271-304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-2303}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCATCACAACTGACCTTGTCGTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Not\ Validated}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_15}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6206-6878}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6206-6551}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6843-6878}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCCTTTAAAATCAAGCCTATTGGTCTTGTAAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGTGTCATTGTCTACGCTGTTGTAGTAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-4.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_21}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{16973-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{16973-18087}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGTTGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGAACCCAGATATTGGCTCCAAGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-5.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-7062}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTAGTGGCAGTGTTCGAAGATTCC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGCAGGTATGAATTGCGGAGTAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-6.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3447}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{3615-8543}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGTTGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGAATAGATAAGCGTAGCCAATCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-7.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{5}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-8543}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGTTGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGAATAGATAAGCGTAGCCAATCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-8.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_22}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-22491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-9.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_23}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-23884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-23884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-10.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_24}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18234-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18234-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-11.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_25}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18237-23702}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18237-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-23702}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGGTAGCACATACTGTATTGCCTGAAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-12.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_26}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-23884}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-23884}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCCGAAGTCTCAGCAACAGATTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-13.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_27}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-18768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{22492-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCCGAAGTCTCAGCAACAGATTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaTGCAATGCTAATCCTCCTGCTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-14.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_29}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-20732}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20732}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-15.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_28}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{25192-26247}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{25192-25701}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{26055-26247}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGACACGTGTTCGTTAGAGAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCAGTGCAATCCGACGCTCTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-16.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{IM}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3678}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3447}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{3615-3678}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTCTGGTGAGATCTTCCAAACAGAAAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGCAACCTGTAGGTCCGATTAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-17.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_10}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-22116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTACTCTACGTCTCTTAGCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-18.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_11}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{13610-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCTTCAGTATTAGCAGCTGCACAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-19.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_12}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{22492-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaTTTCCAGCTGAAGCCTGGAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-20.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_13}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4279-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4279-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-21.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_14}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4304-16870}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4304-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{13610-16870}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCTTCAGTATTAGCAGCTGCACAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-22.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_16}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{9430-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTCCAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCTGTCCAACAACCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-23.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_17}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{11001-12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTCCAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTCCCCATCTAGACCTTTCATCTAACTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-24.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_18}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTCCAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGTTCTCCGTCTTCTACGTCGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-25.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_19}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7401-7836}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7401-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7836}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{N/A}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_20}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7765-16856}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7765-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12466-16856}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGATTTGAAGCCAATTATCCTTCAACG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCTGCAGGCACAACAGGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-26.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-10549}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{8570-10549}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTATCATCTGGCAATTCCGGTATG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-27.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_9}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-20484}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-20484}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTACTCTACGTCTCTTAGCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-28.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

In the table above, the restriction sites in the primer tails are shown
in lowercase letters. All the primer melting temperatures (TMs) are
58-60\textsuperscript{o}C using a hot start Taq DNA polymerase. The PCR
reaction mix was made per manufacturer's instructions. The PCR cycling
conditions were as follows: Initial denaturation --
95\textsuperscript{o}C for 1 minute; cyclical denaturation --
95\textsuperscript{o}C for 30 seconds, annealing -- variable temperature
(53\textsuperscript{o}C-56\textsuperscript{o}C) for 30 seconds, primer
extension -- 68\textsuperscript{o}C for variable time, and final
elongation -- 68\textsuperscript{o}C for 5 minutes. We used 35 cycles of
amplification.

\textbf{Supplementary Computational Analysis}\\
Snakemake v7.24.0 was used to manage our entire workflow. A graph of the
main steps in our pipeline generated with Snakemake is shown below. Our
trimmed RNA-seq reads were mapped to the genome of \emph{M. gallopavo}
(with the THEV genome as one of its chromosomes) using Hisat2, to
generate the alignment (BAM) files and StringTie used to assemble the
transcriptome with a GTF annotation file containing the predicted THEV
ORFs as a guide. The GTF annotation file was derived from a GFF3
annotation file obtained from NCBI using Agat - version 1.0.0, a program
for converting between many different file formats used in
bioinformatics. However, the NCBI GFF3 annotation file itself was first
modified to remove all unimportant features, leaving only the ORFs.

StringTie was also used to estimate the normalized expression levels
(FPKM) of all the transcripts and Ballgown in R was used to perform
statistical analysis and comparisons of the transcript expression
levels, which was instructive in understanding the temporal regulation
THEV gene expression.

In these steps above, each sample (replicate of each time point) was
processed independently and merged only in the final transcriptome
assembly or during analysis with Ballgown. In the subsequent steps
described below, all samples for each time point were processed
together.

We used RegTools to extract and analyze the splice junctions in the BAM
files. The command ``regtools junctions extract'' provides a wealth of
information about all the splice sites in the BAM file provided such as:
the start and end positions, the strand, and number of reads supporting
the splice junctions. The command ``regtools junctions annotate'' gives
even more information such as: the splice site donor-acceptor sequences
and transcripts/genes that overlap the junction. This information was
the basis for estimating and comparing the splicing activity of
different regions (TUs) of THEV over time. Also, Samtools was also used
to count the total sequencing reads for all replicates at each time
point.

\begin{figure}
\centering
\includegraphics{project_map.png}
\caption{A flowchart of the major steps in the computational analysis
pipeline (\emph{generated with Snakemake})}
\end{figure}

\end{document}

### 2024-03-21 manuscript_thev_transcriptome.tex
rerun entire workflow after rebuilding environment

@@
 
-\setlength{\tabcolsep}{0pt}
+\setlength{\tabcolsep}{2pt}
 
@@
 
-\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\
+\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\
 
@@
 
-\endfoot
+\endlastfoot
 

### 2024-03-21 manuscript_thev_transcriptome.Rmd
Put linebreaks in primer sequences of supp table to fit on pdf

@@
                   width = 1.1, height = 1) %>%
-  flextable::width(j = ~forwardP, width = 1.1) %>%
-  flextable::width(j = ~reverseP, width = 1.1) %>%
+  flextable::width(j = ~forwardP, width = 0.6) %>%
+  flextable::width(j = ~reverseP, width = 0.6) %>%
   flextable::width(j = ~gel_image, width = 1.15) %>%

### 2024-03-21 manuscript_thev_transcriptome.tex
Put linebreaks in primer sequences of supp table to fit on pdf

@@
 
-\begin{longtable}[l]{|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{1.10in}|p{1.10in}|p{1.15in}}
+\begin{longtable}[l]{|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.60in}|p{0.60in}|p{1.15in}}
 
@@
 
-\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Transcript\ ID}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Number\ of\ Exons}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Full\ Transcript}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 1}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 2}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 3}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 4}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 5}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 6}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 7}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Forward\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Reverse\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Agarose\ Gel}}}} \\
+\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Transcript\ ID}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Number\ of\ Exons}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Full\ Transcript}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 1}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 2}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 3}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 4}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 5}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 6}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 7}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Forward\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Reverse\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Agarose\ Gel}}}} \\
 
@@
 
-\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\
+\multicolumn{14}{>{\raggedright}m{\dimexpr 6.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\
 
@@
 
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-1655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTTCTGTTTGAATTGTGGGCGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-1.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-1655}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGCCTGTTGGAATTGTTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-2.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{225-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{225-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCATTTCCCGTACACGGTGTTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-3.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{271-2303}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{271-304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-2303}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCATCACAACTGACCTTGTCGTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Not\ Validated}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_15}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6206-6878}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6206-6551}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6843-6878}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCCTTTAAAATCAAGCCTATTGGTCTTGTAAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGTGTCATTGTCTACGCTGTTGTAGTAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-4.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_21}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{16973-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{16973-18087}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGTTGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGAACCCAGATATTGGCTCCAAGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-5.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-7062}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTAGTGGCAGTGTTCGAAGATTCC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGCAGGTATGAATTGCGGAGTAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-6.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3447}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{3615-8543}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGTTGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGAATAGATAAGCGTAGCCAATCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-7.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{5}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-8543}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGTTGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGAATAGATAAGCGTAGCCAATCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-8.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_22}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-22491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-9.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_23}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-23884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-23884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-10.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_24}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18234-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18234-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-11.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_25}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18237-23702}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18237-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-23702}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGGTAGCACATACTGTATTGCCTGAAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-12.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_26}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-23884}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-23884}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCCGAAGTCTCAGCAACAGATTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-13.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_27}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-18768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{22492-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCCGAAGTCTCAGCAACAGATTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaTGCAATGCTAATCCTCCTGCTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-14.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_29}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-20732}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20732}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-15.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_28}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{25192-26247}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{25192-25701}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{26055-26247}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGACACGTGTTCGTTAGAGAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCAGTGCAATCCGACGCTCTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-16.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{IM}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3678}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3447}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{3615-3678}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTCTGGTGAGATCTTCCAAACAGAAAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGCAACCTGTAGGTCCGATTAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-17.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_10}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-22116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTACTCTACGTCTCTTAGCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-18.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_11}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{13610-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCTTCAGTATTAGCAGCTGCACAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-19.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_12}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{22492-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaTTTCCAGCTGAAGCCTGGAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-20.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_13}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4279-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4279-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-21.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_14}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4304-16870}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4304-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{13610-16870}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCTTCAGTATTAGCAGCTGCACAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-22.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_16}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{9430-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTCCAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCTGTCCAACAACCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-23.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_17}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{11001-12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTCCAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTCCCCATCTAGACCTTTCATCTAACTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-24.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_18}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTCCAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGTTCTCCGTCTTCTACGTCGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-25.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_19}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7401-7836}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7401-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7836}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{N/A}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_20}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7765-16856}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7765-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12466-16856}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGATTTGAAGCCAATTATCCTTCAACG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCTGCAGGCACAACAGGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-26.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-10549}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{8570-10549}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTATCATCTGGCAATTCCGGTATG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-27.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_9}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-20484}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-20484}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATCCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTACTCTACGTCTCTTAGCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-28.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-1655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTTCTGT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TTGAATTGTGGGCGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-1.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-1655}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGCCT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTTGGAATTGTTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-2.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{225-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{225-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCATTTCCC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTACACGGTGTTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-3.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{271-2303}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{271-304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-2303}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTCATCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAACTGACCTTGTCGTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Not\ Validated}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_15}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6206-6878}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6206-6551}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6843-6878}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCCTTTAAA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{ATCAAGCCTATTGGTCTTGTAAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGTGTCATT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTCTACGCTGTTGTAGTAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-4.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_21}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{16973-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{16973-18087}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGAACCC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGATATTGGCTCCAAGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-5.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-7062}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTAGTGGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGTGTTCGAAGATTCC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGCAGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TATGAATTGCGGAGTAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-6.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3447}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{3615-8543}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGAATA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GATAAGCGTAGCCAATCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-7.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{5}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-8543}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{10981-11079}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18159-18189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18684-18751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TGCTGAGACTTCGGACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCATTGAATA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GATAAGCGTAGCCAATCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-8.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_22}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-22491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-9.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_23}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-23884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-23884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-10.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_24}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18234-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18234-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGCTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-11.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_25}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18237-23702}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18237-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-23702}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GGAGGTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGGTAGCACA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TACTGTATTGCCTGAAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-12.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_26}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-23884}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-23884}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CGAAGTCTCAGCAACAGATTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-13.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_27}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18727-18768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{22492-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CGAAGTCTCAGCAACAGATTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaTGCAAT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GCTAATCCTCCTGCTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-14.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_29}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-20732}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18230-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20732}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtacCTGAGGAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTCGTAGACTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-15.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_28}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{25192-26247}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{25192-25701}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{26055-26247}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGACAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTGTTCGTTAGAGAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAATCCGACGCTCTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-16.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{IM}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3678}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{2334-3447}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{3615-3678}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTCTGGTGAGA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TCTTCCAAACAGAAAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGCAA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCTGTAGGTCCGATTAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-17.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_10}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-22116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-18350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTACTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TACGTCTCTTAGCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-18.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_11}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{13610-18350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCTTCAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TATTAGCAGCTGCACAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-19.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_12}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{22492-25168}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaTTTCC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGCTGAAGCCTGGAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-20.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_13}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4279-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4279-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{18717-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-22116}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCAAG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTTGGTCAGGTGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-21.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_14}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4304-16870}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4304-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{13610-16870}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCATC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCTTCAGT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{ATTAGCAGCTGCACAACC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-22.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_16}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{9430-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGCCT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTCCAACAACCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-23.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_17}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{11001-12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTCCCCATCTAGAC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTTTCATCTAACTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-24.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_18}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{6934-6969}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGGATCTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CAGATTCTGGTCTGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaGTTCTC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CGTCTTCTACGTCGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-25.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_19}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7401-7836}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7401-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7836}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{N/A}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_20}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7765-16856}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7765-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12466-16856}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGATTTGA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{AGCCAATTATCCTTCAACG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCTGCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GGCACAACAGGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-26.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-10549}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{8570-10549}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCAT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTATC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{ATCTGGCAATTCCGGTATG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-27.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_9}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-20484}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{4226-4360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7454-7531}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{7754-7807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{12238-18768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20162-20223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{20419-20484}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGCTCATCAT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCAGTTCTAAATTTCTCTCTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCCTACT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CTACGTCTCTTAGCAGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{c}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-28.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
 

### 2024-03-21 scripts/r/reg_by_reg_plots.R

@@ -542,60 +542,60 @@ wetlab_val <- tibble(trxpt_id = c(# E1
                                   paste0("TRXPT_", c(10:14, 16:20, 8:9))
                                   ),
                      forwardP = c(# E1
-                                  "CCCggtaccTTCTGTTTGAATTGTGGGCGG",
-                                  "CCCggtaccGAGGCCTGTTGGAATTGTTGC",
-                                  "CCCggtacCATTTCCCGTACACGGTGTTG",
-                                  "CCCggtaccGTCATCACAACTGACCTTGTCGTC",
+                                  "CCCggtaccTTCTGT\nTTGAATTGTGGGCGG",
+                                  "CCCggtaccGAGGCCT\nGTTGGAATTGTTGC",
+                                  "CCCggtacCATTTCCC\nGTACACGGTGTTG",
+                                  "CCCggtaccGTCATCA\nCAACTGACCTTGTCGTC",
                                   # E2
-                                  rep("CCCggtacCTGTTGCTGAGACTTCGGACC", 3), # E2 universal R,
-                                  "CCCggtacCCTTTAAAATCAAGCCTATTGGTCTTGTAAC",
-                                  "CCCggtacCTAGTGGCAGTGTTCGAAGATTCC",
+                                  rep("CCCggtacCTGT\nTGCTGAGACTTCGGACC", 3), # E2 universal R,
+                                  "CCCggtacCCTTTAAA\nATCAAGCCTATTGGTCTTGTAAC",
+                                  "CCCggtacCTAGTGGC\nAGTGTTCGAAGATTCC",
                                   #E3
-                                  rep("CCCggtacCTGAGGAGGTCGTAGACTCTGC", 4), #E3_univiersal F
-                                  rep("CCCggtaccGTCCGAAGTCTCAGCAACAGATTC", 2),
-                                  "CCCggtacCTGAGGAGGTCGTAGACTCTGC",
+                                  rep("CCCggtacCTGA\nGGAGGTCGTAGACTCTGC", 4), #E3_univiersal F
+                                  rep("CCCggtaccGTC\nCGAAGTCTCAGCAACAGATTC", 2),
+                                  "CCCggtacCTGAGGAG\nGTCGTAGACTCTGC",
                                   # E4
-                                  "CCCggtaccGGACACGTGTTCGTTAGAGAACC",
+                                  "CCCggtaccGGACAC\nGTGTTCGTTAGAGAACC",
[…]

### 2024-05-06 importance_of_study.Rmd
first round changes after jvi review

@@
 \vspace{15mm}
-Hemorrhagic enteritis (HE) is a disease of turkey poults characterized by immunosuppression (IS), bloody diarrhea, and up to 80% mortality.
-This disease is caused by *Turkey Hemorrhagic Enteritis Virus* (THEV) of which avirulent strains (THEV-A) that do not cause HE but retain the immunosuppressive ability have been isolated.
-The THEV-A Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
+Hemorrhagic enteritis (HE) is a disease of turkey poults characterized by immunosuppression, bloody diarrhea, and up to 80% mortality.
+This disease is caused by *Turkey Hemorrhagic Enteritis Virus* (THEV) of which avirulent strains that do not cause HE but retain the immunosuppressive ability have been isolated.
+The Virginia Avirulent Strain (VAS) is still used as a live vaccine despite its immunosuppressive properties.
 Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated cohorts.
-To establish the genetic basis by which VAS brings about IS leading to its mitigation, it is imperative that the viral gene(s) mediating the IS be well-characterized.
+To establish the genetic basis by which VAS brings about immunosuppression leading to its mitigation, it is imperative that the viral gene(s) mediating the immunosuppression be well-characterized.
 As the viral splicing and gene expression patterns are unknown, the most pressing need was for a well-characterized transcriptome of THEV.
-Also, the detailed characterization of a non-human adenovirus splice map, which is scantily studied, provides valuable insights into the differences of various adenovirus splicing patterns.
+Also, the detailed characterization of a non-human adenovirus splice map, which are scantily studied, provides valuable insights into the differences of various adenovirus splicing patterns.

### 2024-05-06 manuscript_thev_transcriptome.Rmd
first round changes after jvi review

@@
   chunck_output_type: console
+  markdown: 
+    wrap: sentence
 ---
+
 \captionsetup[table]{labelformat=empty}
@@
 We used an RNA-sequencing experiment to characterize the transcriptome of THEV for the first time, providing key insight into the THEV gene expression and mRNA structures.
-Researchers previously annotated THEV's genome as encoding 23 open reading frames (ORFs).
+Researchers previously annotated the genome of THEV as encoding 23 open reading frames (ORFs).
 In this work we identified 29 spliced transcripts all of which consisted of novel exons although some exons matched some previously annotated ORFs.
@@
 During validation we identified five additional unique transcripts, a subset of which were further validated by 3' rapid amplification of cDNA ends (3' RACE) experiments.
-Thus, we report that the genome of THEV contains 34 unique transcripts with the coding capacity for all annotated ORFs.
+Thus, we report that the genome of THEV contains 34 transcripts with the coding capacity for all annotated ORFs.
 However, we found six of the previously annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated ORFs on the basis of the identification of an in-frame upstream start codon or the detection of additional coding exons.
-We also identified three of the annotated ORFs with longer or shorter isoforms, and seven novel unpredicted ORFs that could potentially be translated; although it is beyond the scope of this manuscript to investigate whether they are translated.
+We also identified three of the annotated ORFs with longer or shorter isoforms, and seven novel unannotated ORFs that could potentially be translated; although it is beyond the scope of this manuscript to investigate whether they are translated.
 Similar to other adenoviruses (AdVs), THEV also produces multiple distinctly spliced transcripts that code for the same proteins across its genome.
 Our data show that all THEV transcripts are spliced and organized into five transcription units under the control of their cognate promoters like other AdVs.
-However, our data suggest that the temporal regulation of THEV may be different from other AdVs.
 \newpage
@@
 The AdV genome is one of the most optimally economized; both the forward and reverse DNA strands harbor protein-coding genes, making it highly gene-dense.
-There are 16 genes termed "genus-common" that are homologous in all AdVs; these are thought to be inherited from a common ancestor.
+There are 16 genes termed "genus-common" that are homologous in all AdVs, presumably inherited from a common ancestor.
 All other genes are termed "genus-specific".
@@
 
-Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV both infect turkeys, with THEV-V causing hemorrhagic enteritis (HE), a debilitating acute disease predominantly affecting turkey poults characterized by immunosuppression (IS), intestinal lesions leading to bloody diarrhea, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967; @Harrach2008].
-While the current vaccine strain (a THEV-A strain isolated from a pheasant; Virginia Avirulent Strain [VAS]) has proven effective at preventing HE in turkey poults, it still retains its immunosuppressive ability.
+Virulent THEV strains (THEV-V) and avirulent strains (THEV-A) of THEV both infect turkeys, with THEV-V causing hemorrhagic enteritis (HE), a debilitating acute disease predominantly affecting turkey poults characterized by immunosuppression, intestinal lesions leading to bloody diarrhea, and up to 80% mortality [@Beach2006; @Beach2009a; @Gross1967; @Harrach2008].
+While the current vaccine strain (a THEV-A called Virginia Avirulent Strain [VAS]) has proven effective at preventing HE in turkey poults, it still retains its immunosuppressive ability.
 Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated birds leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
-To eliminate the immunossupressive effect of the vaccine strain, a thorough investigation of the culprit viral genes mediating this phenomenon is essential.
-However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making an investigation of specific IS-related viral genes impractical.
+To eliminate the immunosupressive effect of the vaccine strain, a thorough investigation of the culprit viral genes mediating this phenomenon is essential.
+However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making an investigation of specific immunosuppressive viral genes impractical.
 
@@
 However, a large preponderance of studies focus on MAdVs -- specifically human AdVs.
-Thus, most of the current knowledge regarding AdV gene expression and replication is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
-MAdV transcription is temporally regulated; therefore, genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late transcription unit (MLTU or major late promoter [MLP] region), which generates five families of late mRNAs (L1-L5) based on the polyadenylation site.
+Thus, most of the current AdV gene expression and replication knowledge is based on MAdV studies, which is generalized for all other AdVs [@Guimet2016; @Wolfrum2013].
+MAdV transcription is temporally regulated; their genes are categorized into five early transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and one major late transcription unit (MLTU or major late promoter [MLP] region), which generates five families of late mRNAs (L1-L5) based on the polyadenylation site.
 An additional gene (UXP or U exon) is located on the reverse strand.
@@
 All but the pIX mRNA undergo at least one splicing event.
-For instance, the MLTU produces over 20 distinct splice variants all of which contain three non-coding exons at the 5'-end (collectively known as the tripartite leader; TPL) [@Donovan2020; @Zhao2014].
+For instance, the MLTU produces over 20 distinct splice variants all containing three non-coding exons at the 5'-end (collectively known as the tripartite leader; TPL) [@Donovan2020; @Zhao2014].
 There is also an alternate three-exon 5' non-coding leader sequence present in varying amounts on a subset of MLTU mRNAs (known as the x-, y-, and z-leaders).
@@
 **Overview of sequencing data and analysis pipeline outputs**   
-A previous study by Aboezz *et al* showed that almost all THEV transcripts were detectable beginning at 4 hours, with a full replication cycle of about 18-hours post infection (hpi) [@Aboezz2019].
-Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and 72-hpi  to ensure a wide time window to sample all transcripts.
-Our paired-end RNA sequencing (RNA-seq) experiment yielded an average of `r avg_tot_count` million total reads of `r seq_len` bp in length per time-point, which were simultaneously mapped to both the virus (THEV) and host (*Meleagris gallopavo*) genomes using the Hisat2 [@Pertea2016] reference-based aligner.
-A total of `r total_mapped` million reads from all time-points mapped to the virus genome; this provided good coverage/depth, leaving no regions unmapped.
-The mapped reads to the virus genome increased substantially from a mere `r cov_4hr` reads at 4 hpi to `r cov_72hr` million reads at 72 hpi (**Table 1**, **Figure 2A**).
-From the mapped reads, we identified a total of `r total_unq_jncs_submit %>% nrow() %>% comma(.)` unique THEV splice junctions from all time-points, with splice junctions from the later time-points being supported by significantly more sequence reads than earlier time-points.
-For example, all the `r tot_jun_4` unique junctions at 4 hpi had less than 10 reads supporting each one, averaging a mere `r mean_juncreads_4` reads per junction.
-Conversely, the `r tot_jun_72` unique junctions at 72 hpi averaged `r mean_juncreads_72` reads per junction, some junctions having coverage as high as `r max_junread72` reads.
-The substantial increases in splice junction and mapping reads to the THEV genome over time denotes an active infection and a successful viral replication, and correlates with our quantitative PCR (qPCR) assay quantifying the total number of viral genome copies over time (**Figure 2B**).
+A prior study by Aboezz *et al*.
+demonstrated that nearly all THEV transcripts became detectable starting at 4 hours post-infection (hpi), with one replication cycle concluding around 18 hpi [@Aboezz2019].
+Consequently, we harvested infected MDTC-RP19 cells (MOI of 100 genome copy numbers/cell) at 4-, 12-, 24-, and 72-hpi to capture all transcripts within a broad time window.
+Our paired-end RNA sequencing (RNA-seq) experiment generated an average of `r avg_tot_count` million total reads of `r seq_len` bp length per time-point.
+These reads were concurrently mapped to both the virus (THEV) and host (*Meleagris gallopavo*) genomes using the Hisat2 [@Pertea2016] reference-based aligner.
+A total of `r total_mapped` million reads from all time-points mapped to the virus genome, providing comprehensive coverage and leaving no regions unmapped.
+The mapped reads to the virus genome increased significantly from a scant `r cov_4hr` reads at 4 hpi to `r cov_72hr` million reads at 72 hpi (**Table 1**, **Figure 2A**).
+From these mapped reads, we identified `r comma(nrow(total_unq_jncs_submit))` unique THEV splice junctions across all time-points, with later time-points exhibiting significantly more sequence reads supporting the splice junctions than earlier time-points.
+For instance, all `r tot_jun_4` unique junctions at 4 hpi had fewer than 10 supporting reads each, averaging only `r mean_juncreads_4` reads per junction.
+In contrast, the `r tot_jun_72` unique junctions at 72 hpi averaged `r mean_juncreads_72` reads per junction, with some junctions reaching as high as `r max_junread72` reads.
+The marked increase in splice junction and mapping reads to the THEV genome over time indicates an active infection and successful viral replication, which is corroborated by our quantitative PCR (qPCR) assay that quantified the total number of viral genome copies over time (**Figure 2B**).
 
-Using StringTie [@Pertea2016], we assembled the data into potential transcripts using the genomic location of the prior predicted THEV ORFs as a guide.
-In the consolidated transcriptome, a composite of all non-redundant transcripts from all time points, we counted a total of `r nrow(spliced_gtf)-1` novel transcripts.
-We found that a subset of exons in the viral transcripts match the predicted ORFs exactly, with the majority of the exons being longer and spanning multiple predicted ORFs (**Figure 3**).
+Using StringTie [@Pertea2016], we assembled the data into potential transcripts, guided by the genomic locations of the previously predicted THEV ORFs.
+In the consolidated transcriptome, a composite of all non-redundant transcripts across all time points, we identified a total of `r nrow(spliced_gtf)-1` novel transcripts.
+We found that a subset of exons in the viral transcripts match some predicted ORFs exactly, with the majority of the exons being longer and spanning multiple predicted ORFs (**Figure 3**).
 
@@
 
-**Changes in THEV splicing profile over time**\
-AdV gene expression occurs under exquisite temporal control with each promoter typically producing one or few pre-mRNAs that undergo alternative splicing to yield a repertoire of mature mRNAs.
-To evaluate the activity of each promoter over time, StringTie and Ballgown (a program for statistical analysis of assembled transcriptomes) [@Ballgown] were used to estimate the normalized expression levels of all transcripts for each time point in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
-Very few unique splice junctions, reads, and transcripts were counted at 4 hpi; hence, this time point was excluded in this analysis.
+**Changes in THEV splicing profile over time**  
+AdV gene expression is subject to meticulous temporal regulation, with each promoter typically generating one or a few pre-mRNAs.
+These pre-mRNAs undergo alternative splicing to produce a diverse array of mature mRNAs.
+To assess the temporal activity of each promoter, we utilized StringTie and Ballgown (a tool for statistical analysis of assembled transcriptomes) [@Ballgown].
+These tools estimated the normalized expression levels of all transcripts at each time point, measured in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units.
+At 4 hpi, we counted very few unique splice junctions, reads, and transcripts; hence, this time-point was excluded from this analysis.
 
@@
 
-Considering individual mRNAs, TRXPT_21 -- from the E2 region -- was the most significantly expressed at 12 hpi, constituting `r abn_each_12`% of the total expression of all transcripts.
-Transcripts in the E3 and E4 regions also contributed significant proportions, and noticeably, some MLP region transcripts.
-The later time points were dominated by the MLP region transcripts -- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 hpi, respectively, as expected (**Figure 4A**).
-When we performed analysis of the FPKM values of transcripts per region we found a similar pattern: the E2 region was the most abundantly expressed at 12 hpi, after which the MLP region assumes predominance (**Figure 4B**).
-Secondly, we estimated relative abundances of all splice junctions at each time point using the raw reads.
+Examining individual mRNAs, TRXPT_21 – from the E2 region – was the most significantly expressed at 12 hpi, constituting `r abn_each_12`% of the total expression of all transcripts.
+Transcripts in the E3 and E4 regions also contributed substantial proportions, along with some MLP region transcripts.
+The later time points were dominated by the MLP region transcripts –- TRXPT_10 and TRXPT_14 were the most abundantly expressed at 24 and 72 hpi, respectively (**Figure 4A**).
+Our analysis of the FPKM values of transcripts per region/TU revealed a similar pattern: the E2 region was the most abundantly expressed at 12 hpi, after which the MLP region assumed dominance (**Figure 4B**).
+
+Next, we estimated the relative abundances of all splice junctions at each time point using the raw reads.
 Only junctions with a read coverage of at least 1% of the total splice junction reads at the given time point were considered significant and included in **Tables 2a-2c**.
-At 12 hpi, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were comprised of predominantly early region (E1, E2, E3, and E4) junctions, albeit the MLTU was the single most preponderant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table S1a**).
-The most abundant junctions at 12 hpi remained the most significantly expressed at 24 hpi also.
-However, here, the MLP-derived junctions were unsurprisingly even more preponderant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table S1b**).
-At 72 hpi, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall -- accounting for `r round(most_sig_72, 1)`% of all junction reads, -- but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table S1c** and **Figure 4C**).
+At 12 hpi, `r nrow(sig_12_juncs)` junctions met the 1% threshold, predominantly from early regions (E1, E2, E3, and E4), although the MLTU was the single most predominant region overall, constituting `r round(most_sig_12, 1)`% of all the junction reads (**Table 2a** and **Supplementary Table S1a**).
+The most abundant junctions at 12 hpi remained the most significantly expressed at 24 hpi.
+However, here, the MLP-derived junctions unsurprisingly became even more predominant overall, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (**Table 2b** and **Supplementary Table S1b**).
+At 72 hpi, the trend of increased activity of the MLP continued as expected; at this time, the MLP region junctions were not only the most abundant overall –- accounting for `r round(most_sig_72, 1)`% of all junction reads, -– but also contained the most significantly expressed individual junctions (**Table 2c**, **Supplementary Table S1c** and **Figure 4C**).
 When we limited this analysis to only junctions in the final transcriptome, we observed the relative abundances of the junctions for each region over time to be similar to the pattern seen with all the junctions included (**Figure 4D**).
 
-We also analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection.
-We found that most splice donor-acceptor sequences were unsurprisingly the canonical GU-AG nucleotides.
+Finally, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may exhibit, generally or over the course of the infection.
+We found that most splice donor-acceptor sequences were, unsurprisingly, the canonical GU-AG nucleotides.
 However, the splice acceptor-donor pairing became less specific over time, such that all combinations of nucleotide pairs were eventually detected (**Figure 5**).
@@
 **Early Region 1 (E1) transcripts**   
-This region in MAdVs is the first transcribed after successful entry of the viral DNA into the host cell nucleus, albeit at low levels [@Zhao2014].
-The host transcription machinery solely mediates the transcription of this region.
-After their translation, the E1 proteins in concert with a myriad of host transcription factors activate other viral promoters [@Guimet2016].
-In MAdVs, this region is subdivided into E1a and E2b units, but the transcripts found in our data categorized under this region do not appear to be subdivided.
+In MAdVs, E1 is the first region transcribed post-viral DNA entry into the host cell nucleus, mediated solely by host transcription machinery [@Zhao2014].
+Translated E1 proteins subsequently activate other viral promoters in conjunction with host transcription factors [@Guimet2016].
+Despite subdivision into E1a and E1b units in MAdVs, our THEV data does not reflect this.
+This region is predicted to encode only two ORFs: ORF1 (sialidase) and Hyd (a hydrophobic product with unknown function) in THEV.
 
-Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, which collectively contain `r english(nrow(reg_e1_brkdown))` unique splice junctions (**Figure 6**).
-Most of the ORFs of the novel transcripts are distinct from the predicted ORFs, but they all have the coding potential (CP) for the predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary start codon usage is considered as reported for other AdVs [@Donovan2020; @Zhao2014].
-The 5'-most CDS of TRXPT_1 is multi-exonic, encoding a novel 17.9 kilodalton (kDa), 160 residue [amino acids (aa)] protein (ORF9).
-From its 5'-most start codon (SC), TRXPT_2 encodes the largest protein in this region -- a 64.3 kDa, 580 aa protein (ORF10) with the same SC as ORF9 (position 211 bp).
-ORF10 spans almost the entire predicted ORF1 and Hyd, coming short in two regards: it is spliced from 1655 bp to 1964 bp (ORF1's C-terminus, including the stop codon), and its stop codon (STC; position 2312) is 13 bp short of the Hyd STC.
-However, it has an SC 102 bp upstream and in-frame with ORF1's predicted SC.
-Thus, ORF10 shares substantial protein sequence similarity with ORF1 but not with Hyd, as the SC of Hyd is not in-frame.
-Without its splice site removing the ORF1 STC, TRXPT_2 would encode a longer variant of ORF1, starting from an upstream SC.
-TRXPT_3 is almost identical to TRXPT_1, except for the lack of TRXPT_1's second exon.
-Our RNA-seq data show that all E1 transcripts share the same transcription termination site (TTS; at position 2325 bp).
-However, TRXPT_3 and TRXPT_4 seem to have transcription start sites (TSS) downstream of the TSS of TRXPT_1 and TRXPT_2 (E1 TSS; position: 54 bp).
-Given that studies in MAdVs show that E1 mRNAs share not only a common TTS but also the TSS, and only differ from each other regarding the internal splicing [@Zhao2014], it is likely that TRXPT_3 and TRXPT_4 are incomplete, and their actual TSS just like the TTS are identical for all E1 transcripts.
-Regardless of the TSS considered for TRXPT_3, the CP remains unaffected.
-Its 5'-most CDS, beginning at 1965 bp and sharing the same STC as ORF9, produces a 13.1 kDa, 115 residue protein (ORF4).
-ORF4 was predicted in an earlier study [@Pitcovski1998] but was excluded in later studies [@Beach2009a; @Davison2003]; however, our data suggest it is a genuinely expressed ORF.
-Unlike TRXPT_3, the CP of TRXPT_4 is affected by the TSS considered; if we consider its unmodified TSS, then its CP is identical to TRXPT_3.
-However, if we assume that TRXPT_4 uses the E1 TSS, then the 5'-most CDS is a distinct, novel, multi-exonic 15.9 kDa, 143 aa protein (ORF11) with the same SC as ORF9 and ORF10 but with a unique STC.
+We identified `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` novel transcripts in this region, containing `r english(nrow(reg_e1_brkdown))` unique splice junctions (**Figure 6**), and encoding `r as.character(english(nrow(filter(spliced_gtf, region == "E1"))))` distinct novel ORFs in addition to Hyd.
+All transcripts have coding potential (CP) for the Hyd protein as the 3’-most coding sequence if secondary start codon usage is considered [@Donovan2020; @Zhao2014].
+Also, all the transcripts have a common transcription termination site (TTS; at position 2325 bp), but TRXPT_1 and TRXPT_2 have an upstream transcription start sites (TSS) to TRXPT_3 and TRXPT_4.
+Given that E1 mRNAs in MAdVs share a common TTS and TSS, differing only in the internal splicing [@Zhao2014], we consider the upstream TSS (position 54 bp) as the actual TSS for all E1 region transcripts.
+We also identified the canonical polyadenylation signal (PAS; AAUAAA) in the immediate context of the TTS at position 2323 bp (location of the "U" in the PAS sequence); see **Supplementary Table S2**.
 
-The splice junctions of all transcripts in this region (except the junction for TRXPT_4) were validated by cloning of viral cDNA and Sanger sequencing (**Supplementary PCR methods**).
-During the validation of TRXPT_2, we found ORF1 to be present on the agarose gel (an unspliced band size) and Sanger sequencing results showed it to be a transcribed mRNA (**Supplementary PCR methods**).
-This was corroborated by our 3' RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without any splicing, with a poly-A tail immediately after the E1 TTS.
-The 5'-most CDS of this transcript (TRXPT_2B) would encode ORF1.
-However, TRXPT_2B has an upstream and in-frame SC to the predicted SC of ORF1, suggesting that the predicted ORF1 CDS is truncated -- the actual ORF1 (eORF1) that is expressed shares the same SC as ORF10, but has a unique STC.
+From the 5'-most start codon (SC), TRXPT_1 encodes a multi-exonic novel 17.9 kDa, 160 residue protein (ORF9).
+TRXPT_2 encodes a two-exon 66.4 kDa, 597 residue novel protein (ORF10), spanning almost the entire predicted ORF1 and Hyd.
+The intron of TRXPT_2 excludes the C-terminus of ORF1 (including its stop codon) from ORF10 but the SC of ORF10 is 102 bp upstream and in-frame with the predicted SC of ORF1.
+TRXPT_3, similar to TRXPT_1 but lacking the second exon, encodes a 13.1 kDa, 115 residue protein (ORF4), previously predicted [@Pitcovski1998] but excluded in later annotations [@Beach2009a; @Davison2003].
+Our data suggest it is genuinely expressed.
+Lastly, TRXPT_4 encodes a distinct novel 15.9 kDa, 143 residue protein (ORF11).
+
+The splice junctions of all transcripts in this region, except for TRXPT_4, were validated by cloning of viral cDNA and Sanger sequencing (see **Supplementary PCR methods**).
+During TRXPT_2 validation, ORF1 was found on the agarose gel (an unspliced band size) and Sanger sequencing results showed it to be a transcribed mRNA (**Supplementary PCR methods**).
+This was corroborated by our 3' RACE experiment, which showed a transcript (TRXPT_2B) spanning the entire ORF1 and Hyd ORFs without splicing, with a poly-A tail immediately after the E1 TTS.
+The 5'-most coding sequence (CDS) of this transcript (TRXPT_2B) encodes ORF1.
+However, TRXPT_2B has an upstream and in-frame SC to the predicted SC of ORF1, suggesting that the predicted ORF1 CDS is truncated -- the expressed ORF1 (eORF1) shares the same SC as ORF10, but has a unique stop codon (STC).
+See **Supplementary Table S3** for all transcripts and their encoded proteins.
 
 **Early Region 2 (E2) and Intermediate Region (IM) transcripts**   
-The E2 TU expressed on the anti-sense strand is subdivided into E2A and E2B and encodes three classical AdV proteins --  pTP and Ad-pol (E2B proteins), and DBP (E2A protein) -- essential for genome replication [@Donovan2020; @Zhao2014].
-Unlike MAdV where two promoters (E2-early and E2-late) are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751 bp) from which both E2A and E2B transcription is initiated.
-However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B transcripts share the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 7**).
+The E2 TU expressed on the anti-sense strand, is subdivided into E2A and E2B and encodes three classical AdV proteins -- pTP and Ad-pol (E2B proteins), and DBP (E2A protein) -- essential for genome replication [@Donovan2020; @Zhao2014].
+Unlike MAdV where two promoters are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751 bp) for both E2A and E2B transcripts in THEV.
+However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, with E2B transcripts sharing the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 7**).
 
-The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from two exons.
-The corresponding transcript (TRXPT_21) found in our data matches this predicted splice junction precisely but with a non-coding additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
-Thus, TRXPT_21 is a three-exon transcript encoding DBP (380 residues, 43.3 kDa) precisely as predicted.
-This transcript (TRXPT_21) was also corroborated in a 3' RACE experiment.
-Additionally, from the 3' RACE data, we found a splice variant of TRXPT_21 which retains the second intron leading to a 2-exon transcript.
-This new transcript (TRXPT_21B), albeit longer due to retaining the second intron and possessing a short 3' UTR, encodes a truncated isoform of DBP (tDBP) because the SC utilized by TRXPT_21, is followed shortly by STCs in the retained intron.
-The SC 173 bp downstream of the DBP SC yields tDBP (a 346 residue, 39.3 kDa product), which is in-frame of DBP but entirely contained in the second exon.
-TRXPT_21 and TRXPT_21B share a common TTS but TRXPT_21B as seen in our 3'-RACE data, extends 39 bp into an adenine/thymine (A/T)-rich sequence before the poly-A tail sequence occurs, suggesting this position (16,934 bp) as the true E2A TTS (**Figure 7**).
+The E2A ORF, DBP, is one of three THEV ORFs predicted to be spliced from two exons.
+The corresponding transcript (TRXPT_21) in our data matches the predicted splice junction but includes an additional non-coding exon at the 5'-end (E2-5'UTR).
+Thus, TRXPT_21 is a three-exon transcript encoding DBP (380 residues, 43.3 kDa) precisely.
+TRXPT_21 was also corroborated in a 3' RACE experiment.
+Additionally, from the 3' RACE data, we found a splice variant of TRXPT_21 which retains the second intron, leading to a 2-exon transcript (TRXPT_21B).
+Although longer, TRXPT_21B encodes a truncated isoform of DBP (tDBP; a 346 residue, 39.3 kDa product) using a downstream in-frame SC but the same STC as DBP.
+Both TRXPT_21 and TRXPT_21B share a common TTS, seen in our 3' RACE data, located 39 bp downstream of the CDS in an adenine/thymine (A/T)-rich sequence followed by the poly-A tail sequence, suggesting this position (16,934 bp) as the true E2A TTS.
+There are two canonical PASs (AAUAAA; 16,964 and 16950 bp) immediately after the CDS any of which can serve as the PAS without affecting the encoded proteins (**Supplementary Table S2**).
 
-The E2B region transcripts also start with the E2-5'UTR but extend thousands of base pairs downstream to reach the TTS at 2334 bp in the IM region, which is immediately followed by an A/T-rich sequence (position 2323-2339 bp) where polyadenylation probably occurs.
-Interestingly, the TTS of the E1 region (position 2,325 bp) on the sense strand is also in the immediate vicinity of this A/T-rich sequence, which is almost palindromic; hence it likely serves as the polyadenylation signal for both E1 and E2B/IM transcripts.
-The E2B transcripts TRXPT_6 and TRXPT_7 are almost identical except for an extra splice junction at the 3'-end of TRXPT_6, making TRXPT_6 a five-exon transcript and TRXPT_7, four exons (**Figure 7**).
-TRXPT_7 has the CP for both classical proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF is predicted to be spliced from two exons just like in all other AdVs.
-The predicted splice junction of pTP is corroborated by our data; however, the full transcript is markedly longer than the predicted ORF: there are two novel non-coding 5' exons, the third exon (containing the SC of pTP) is significantly longer than predicted, and the last exon containing the bulk of the CDS is more than triple the predicted size of pTP.
-The first two exons are 5'-UTRs because the SC here is immediately followed by STCs; thus, the 5'-most SC (position 10,995 bp) of the third exon which matches the predicted SC of pTP is utilized.
-The encoded product is identical to the predicted pTP protein (597 residues; 70.5 kDa).
-If secondary SC (secSC) usage is considered, with SC at 6768 bp and STC at 3430 bp, the encoded product is identical to the predicted Ad-pol (polymerase) protein (1112 residues; 129.2 kDa).
-TRXPT_6 differs from TRXPT_7 by containing an extra splice site at 3447-3515 bp.
-However, the CP remains similar to that of TRXPT_7 except the Ad-pol encoded from the secSC is a truncated isoform with a new STC resulting from the splice site.
+The E2B region transcripts also start with the E2-5'UTR but extend downstream to reach the TTS at 2334 bp in the IM region, which is in the immediate context of a canonical PAS (position 2333 bp) where polyadenylation likely occurs.
+The E2B transcripts, TRXPT_6 and TRXPT_7, are almost identical except for an extra splice junction at the 3'-end of TRXPT_6 (**Figure 7**).
+TRXPT_7 has the CP for both classical proteins (pTP and Ad-pol) encoded in this region, with the pTP ORF predicted to be spliced from two exons.
+The predicted splice junction of pTP is corroborated by our data but the full transcript is markedly longer than the predicted ORF, although, the encoded product (pTP) remains unchanged.
+Ad-pol (polymerase) is encoded downstream of pTP with secondary SC (secSC) usage.
+The CP of TRXPT_6 slightly differs from TRXPT_7 because a new STC resulting from the extra splice site forms a minimal truncation of the Ad-pol encoded from its secSC.
 
-While both TRXPT_6 and TRXPT_7 have the CP for Ad-pol with secSC usage, in all AdVs studied, the two proteins (pTP and Ad-pol) are encoded by separate mRNAs with identical first three 5' exons and TTS, but the splice junction to the terminal exons are different.
-We checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing) and discovered a unique splice junction (10,981-7062 bp) not found in our RNA-seq data.
-If initiated from the E2 TSS and terminated at the E2 TTS, this transcript (TRXPT_31) would encode Ad-pol exactly as predicted as its 5'-most CDS (**Figure 7**).
+While both TRXPT_6 and TRXPT_7 have the CP for Ad-pol with secSC usage, in all AdVs studied, the two proteins (pTP and Ad-pol) are encoded by separate mRNAs with identical first three 5' exons and TTS, but different splice junctions to the terminal coding exons.
+Hence, we checked for a longer splice junction between the third and fourth (terminal) exons of TRXPT_7 with our junction validation method (targeted PCR, cloning, and Sanger sequencing).
+We discovered a unique splice junction (10,981-7062 bp) not present in our RNA-seq data.
+If initiated from the E2 TSS and terminated at the E2B TTS, this transcript (TRXPT_31) would encode Ad-pol in its 5'-most CDS (**Figure 7**).
 
@@
 The IM region is a single-transcript TU, encoding a single classical protein, IVa2.
-The promoter expressing this single transcript (TRXPT_5) is embedded in E2B region and shares a TTS with E2B transcripts [@Donovan2020; @Zhao2014].
-TRXPT_5 is a two-exon transcript spliced exactly as the last splice junction of TRXPT_6.
-The first exon is a UTR, except the last 2 nucleotides, which connect with the first nucleotide of the second exon to form the 5'-most SC.
-This first SC is 4 codons upstream and in-frame of the predicted IVa2 SC.
-Except for the four extra N-terminus residues, the entire protein sequence is identical to the predicted IVa2.
+The promoter expressing this single transcript (TRXPT_5) is embedded in the E2B region and shares a TTS with E2B transcripts [@Donovan2020; @Zhao2014].
+TRXPT_5 is a two-exon transcript with a non-coding first exon, except the last 2 nucleotides, which connect with the first nucleotide of the second exon to form the 5'-most SC.
+This new SC is four codons upstream and in-frame of the predicted IVa2 SC.
+Beside the four additional N-terminus residues, the protein sequence is unchanged.
 
-**Early Region 3 (E3) transcripts**.   
-The E3 region is wholly contained in the MLTU and encodes proteins involved in modulating and evading the host immune defenses.
-In MAdVs, this region contains seven ORFs expressed from several transcripts which share the same TSS (from the E3 promoter) but have different TTSs [@Guimet2016; @Donovan2020; @Zhao2014].
+**Early Region 3 (E3) transcripts**   
+The E3 region, nested within the MLTU, encodes proteins that modulate and evade host immune defenses.
+In MAdVs, this region contains seven ORFs expressed from multiple transcripts sharing the same TSS (from the E3 promoter) but having different TTSs [@Guimet2016; @Donovan2020; @Zhao2014].
 However, some E3 transcripts use the TSS of the MLP.
-Due to sharing the same TSS, in MAdVs, secSC usage is heavily relied on for gene expression in this region except for 12.5K and transcripts using the MLP TSS, as utilizing only the first SC cannot produce all the other transcripts in this TU [@Donovan2020].
+Due to sharing the same TSS, in MAdVs, secSC usage is heavily relied on for gene expression in this region as utilizing only the first SC cannot produce the downstream transcripts in this TU.
+The 12.5K ORF and transcripts using the MLP TSS are exceptions [@Donovan2020].
 
 In THEV, only one ORF (E3) was predicted in this region.
-However, as the E3 TU is nested in the MLTU, transcripts from the L4P (100K, 22K, 33K, and pVIII) not only overlap the E3 region transcripts entirely as seen in our RNA-seq results, but also have their TSS and TTS in practically the same locations (**Figure 8**).
+However, as the E3 TU is nested in the MLTU, transcripts from the L4 promoter (100K, 22K, 33K, and pVIII) overlap the E3 region transcripts entirely and share similar TSS and TTS locations (**Figure 8**).
 Therefore, we have categorized these two groups together as E3 transcripts.
 
-We identified seven novel transcripts here (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs -- we consider the first TSS (position 18,230 bp) as corresponding to the L4P and the other at 18,727 bp as corresponding to the E3 promoter (E3P).
-These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, and E3, as well as Fiber (IV) and ORF7 belonging to the MLTU.
-But some of these CDSs are different than predicted due to either unknown exons or the presence of an in-frame upstream SC.
-For instance, 33K is one of the few THEV ORFs predicted to be spliced from two exons; however, we discovered a significantly longer four-exon ORF (e33K) on TRXPT_24 that contains it almost entirely.
-The first two exons of e33K were not predicted but the last two match the predicted exons and the CDS is in-frame, albeit the first 20 bp of the predicted 33K (including the SC at 20,142 bp) is spliced out as part of the second intron of TRXPT_24.
-Thus, the bona fide 33K (e33K) is a 19.8 kDa, 171 residue protein spanning four exons instead of the predicted 120 aa protein.
+We identified seven novel transcripts (`r paste0("TRXPT_", c(22:27, 29), collapse = ", ")`) from our RNA-seq data, all originating from two distinct TSSs.
+We consider the first TSS (position 18,230 bp) as corresponding to the L4 promoter (L4P) and the other at 18,727 bp as corresponding to the E3 promoter (E3P).
+We also identified the canonical or other known PASs [@Beaudoing2000] near the TTS of the transcripts (see **Supplementary Table S2**).
+These E3 transcripts collectively have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, and E3, as well as Fiber (IV) and ORF7 of the MLTU (see **Supplementary Table S3**).
+However, some of these CDSs differ from the predictions due to either unknown exons or the presence of an in-frame upstream SC.
+For instance, we discovered that 33K, predicted to be spliced from two exons, is actually a significantly longer four-exon ORF (e33K; 19.8 kDa, 171 residues) encoded on TRXPT_24.
+Its first two exons were unknown but the last two match the predicted exons and the CDS is in-frame, albeit the first 20 bp of the predicted 33K (including the SC) is spliced out as part of the second intron of TRXPT_24.
 TRXPT_24 also has the CP for pVIII and E3 if we consider downstream SC usage.
-However, the predicted E3 has an upstream in-frame SC; thus, this longer version of E3 (eE3) is likely the genuinely expressed ORF.
-TRXPT_29 is the shortest transcript in this TU.
-It is a two-exon transcript, both exons comprising the CDS.
-The product of TRXPT_29 is a novel 73 residue protein (8.3KI) sharing the SC of e33K but with a unique STC.
-TRXPT_23 being spliced identically as TRXPT_29 also encodes 8.3KI from its first SC.
-Similarly, TRXPT_22 also encodes a 73 aa novel protein (8.3KII) from its first SC that shares over 80% similarity with 8.3KI, but it differs from 8.3KI at the C-terminus.
-Considering downstream SC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and eE3 in that order, but TRXPT_23 being longer, has the CP for the Fiber ORF also.
+However, we found an upstream in-frame SC for the predicted E3; thus, this longer version of E3 (eE3) is likely the genuinely expressed ORF.
+TRXPT_29, the shortest transcript in this TU, encodes a novel 73 residue protein (8.3KI) across its two exons using the SC of e33K with a unique STC.
+TRXPT_23, spliced identically as TRXPT_29, also encodes 8.3KI from its first SC.
+Similarly, TRXPT_22 encodes a 73 residue novel protein (8.3KII) from its first SC that shares over 80% similarity with 8.3KI, but they differ at the C-terminus.
+Considering downstream SC usage, both TRXPT_22 and TRXPT_23 can encode pVIII and eE3 in that order, but TRXPT_23 being longer, also has the CP for the Fiber ORF.
 
-As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 essentially share the same genomic space, their validation was done with a single primer pair, and they were differentiated from each other by cloning and Sanger sequencing (**Supplementary PCR methods**).
-In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed another splice  variant undetected in our RNA-seq transcriptome.
-This was a three-exon transcript (TRXPT_30) with its first and last exons spliced identically as TRXPT_23, but which also has the second exon of TRXPT_24 (**Figure 8**).
-The first CDS on TRXPT_30 spans all three exons, producing a novel 140 residue, 15.7kDa protein.
-Interestingly, the last 81 C-terminus residues of this new protein (e22K) are identical to 22K (89 residues), which is a single-exon ORF predicted to use the same SC as 33K (20,142 bp).
-Just as seen for 33K, all the transcripts in this region exclude the first 20 bp of 22K (including the SC) as part of their introns; therefore, the first 7 residues of 22K are lacking in e22K due to splicing.
-Hence, we consider e22K as a long variant of the predicted 22K ORF.
-Albeit the TSS and TTS of TRXPT_30 was not seen, we presume that they are similar to TRXPT_23, in which case it would also have the downstream CP of TRXPT_23.
+As the splice junctions of TRXPT_22, TRXPT_23, TRXPT_24, and TRXPT_29 share the same genomic space, their validation was done with a single primer pair, and they were differentiated from each other by cloning the cDNA and Sanger sequencing (**Supplementary PCR methods**).
+In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed a distinct splice variant undetected in our RNA-seq transcriptome.
+This was a three-exon transcript (TRXPT_30) with identical first and last exons as TRXPT_23, but also contained the second exon of TRXPT_24 (**Figure 8**).
+TRXPT_30 encodes a novel 140 residue, 15.7kDa protein (e22K), spanning all three exons.
+Interestingly, the last 81 C-terminus residues of e22K are identical to 22K (89 residues), a single-exon ORF predicted to use the same SC as 33K.
+Just as seen for 33K, the first 20 bp of 22K is intronic, excluding the first 7 residues of 22K from e22K.
+We consider e22K as a long variant of the predicted 22K ORF.
+Assuming TRXPT_30 shares the same TSS and TTS as TRXPT_23, it would also have the downstream CP of TRXPT_23.
 
-TRXPT_25 is the largest transcript in the TU.
-It also utilizes the L4P TSS but has a distinct TTS.
-It is a two-exon transcript, encoding a novel protein (t100K; 543 residues), which is a shorter isoform of the predicted 100K ORF.
-Considering secSC usage on this transcript yields the predicted 22K ORF precisely as predicted.
-It also has the CP for pVIII and eE3 in that order.
-Furthermore, during the validation of the TRXPT_25 splice junction using primers that span its junction (18,350-18,717 bp), we noticed a DNA band that corresponds to the full unspliced sequence (**Supplementary PCR methods**).
+TRXPT_25, the largest transcript in the TU, is a two-exon transcript, encoding a novel protein (t100K; 543 residues), which is a shorter isoform of the predicted 100K ORF.
+secSC usage on this transcript yields the predicted 22K ORF.
+It also has the CP for pVIII and eE3 downstream.
+Furthermore, during the validation of the TRXPT_25 splice junction using primers that span its junction (18,350-18,717 bp), we noticed a DNA band corresponding to the full unspliced sequence (**Supplementary PCR methods**).
 As TRXPT_25 only falls short of encoding the complete predicted 100K protein due to its splice junction, this band (which we cloned and validated by Sanger sequencing) suggests that the predicted 100K is indeed expressed.
-This transcript (TRXPT_25B) although not seen in full, likely shares the same TSS and TTS as TRXPT_25.
-Lastly, TRXPT_26 and TRXPT_27 both originate from the E3P but have distinct TTSs.
-TRXPT_26 is a three-exon transcript but the first two are UTRs.
-It encodes pVIII as the 5'-most ORF and has the CP for eE3 and Fiber in that order.
-TRXPT_27 on the other hand, is only a two-exon transcript that is similar to TRXPT_26, only the terminal exon contains the CDSs.
-It encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSC usage.
-TRXPT_13, which is an L4 transcript that uses the MLP TSS is discussed under the MLTU transcripts.
+We assume that this transcript (TRXPT_25B) shares the same TSS and TTS as TRXPT_25.
+
+Lastly, TRXPT_26 and TRXPT_27, both originate from the E3P but have distinct TTSs.
+TRXPT_26 encodes pVIII as the 5'-most ORF and has the CP for eE3 and Fiber in that order.
+TRXPT_27, a two-exon transcript, encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSC usage.
+TRXPT_13 is an L4P transcript that uses the MLP TSS; it is discussed under the MLTU transcripts.
 
 **Early Region 4 (E4) transcripts** 
-This TU is found at the tail-end (3'-end) of the genome  and expressed from the anti-sense strand.
-Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the same strand as ORF8 nor transcribed from a promoter in the E4 region, only ORF8 can legitimately be classified as a transcript in this TU.
-This is corroborated by our RNA-seq data, as only one transcript was identified in this region on the anti-sense strand (**Figure 9**).
-The transcript (TRXPT_28) spans 25192-26247 bp and is spliced at 25701-26055 bp, making a two-exon transcript.
+This TU is found at the 3'-end of the genome and expressed on the anti-sense strand.
+Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the anti-sense strand nor transcribed from a promoter in the E4 region; hence, we only classify ORF8 in this TU.
+This is corroborated by our RNA-seq data, showing only one transcript in this region on the anti-sense strand (**Figure 9**).
+The transcript (TRXPT_28) spans 25192-26247 bp and is spliced at 25701-26055 bp, forming a two-exon transcript.
 The second exon fully matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
-However, there is an SC in the first exon at position 26246 bp (192 bp upstream of the predicted SC).
-The encoded protein from this SC is in-frame with the predicted SC found in the second exon; hence, we consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of the predicted ORF8, as the genuinely expressed ORF with an identical C-terminus to the predicted ORF8 protein.
+However, we identified a SC 192 bp upstream of the predicted SC in the first exon from which an in-frame protein is encoded.
+We consider this longer isoform (eORF8 -- 26.4 kDa, 229 residues) as the genuinely expressed ORF.
+We also identified a canonical PAS 11 bp upstream of TTS (**Supplementary Table S2**).
 
 **Major Late Transcription Unit (MLTU) or MLP Region transcripts**   
-The MLTU transcripts dominate the late phase (i.e, after DNA replication) of the AdV infectious cycle.
-The MLP produces all late mRNAs by alternative splicing and alternative polyadenylation of a primary transcript, grouped into five transcript classes (L1-L5).
-Most of the coding capacity of THEV falls within this TU.
-Specifically, about 13 out of the 23 predicted ORFs were assigned to this TU, some of which we have categorized under the E3 TU instead.
-Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU, the majority of which have the 5' untranslated TPL sequence as seen in all AdVs.
-For three transcripts (`r paste0("TRXPT_", c(16:18), collapse = ", ")`), a different leader sequence (sTPL) is used, which differs from the TPL in only one regard: the first TPL exon is substituted for a different first exon, found between the first and second TPL exons.
-Also, TRXPT_20 seems to include only the third TPL exon (**Figure 10**).
+The MLTU transcripts, dominant in the late phase of the AdV infectious cycle, are produced by alternative polyadenylation and splicing of a primary transcript and grouped into five transcript classes (L1-L5).
+About 13 out of the 23 predicted ORFs in THEV fall within this TU, some of which we have categorized under the E3 TU instead.
+Our RNA-seq data revealed 12 transcripts (`r paste0("TRXPT_", c(8:14, 16:20), collapse = ", ")`) in this TU, most of which have the 5' TPL sequence as in all AdVs.
+However, three transcripts (`r paste0("TRXPT_", c(16:18),collapse = ", ")`) use a different leader sequence (sTPL), where a different first exon is used instead of the first TPL exon, and TRXPT_20 uses only the third TPL exon (TPL3); see **Figure 10**.
 
-We identified five TTSs (10,549 bp, 12,709 bp, 16,870 bp, 17,891 bp, 20,865 bp) in this TU, which we consider as corresponding to the five late mRNA classes (L1-L5), respectively, as found in all AdVs.
-L1 mRNAs include TRXPT_8, which comprises the TPL (non-coding) and the CDS-containing terminal exon.
-This transcript encodes the 52K ORF exactly as predicted with the SC beginning from the first nucleotide of the terminal exon.
-L2 mRNAs include TRXPT_16, TRXPT_17, and TRXPT_18, all of which consist of the sTPL (also non-coding) followed by their respective terminal exons.
-TRXPT_16 encodes pIIIa exactly as predicted as the 5'-most ORF, and also has the CP for the ORFs, III and pVII in that order.
-TRXPT_17 encodes the ORF, III (penton), and TRXPT_18 encodes the ORF pVII exactly as predicted.
-The L3 mRNAs include TRXPT_14 and TRXPT_20, of which TRXPT_14 utilizes the full TPL whereas TRXPT_20 uses only the third TPL exon (TPL3).
-Both transcripts have the CP for the ORF, hexon (II) but hexon is the only ORF encoded on TRXPT_14, whereas the 5'-most ORF on TRXPT_20 is pX (pre-Mu) followed by pVI and hexon in that order.
-L4 mRNAs include TRXPT_9, TRXPT_10, TRXPT_11, and TRXPT_13 all of which begin with the TPL followed by three (TRXPT_9, TRXPT_10, and TRXPT_13) or four (TRXPT_11) coding exons.
-These are the largest transcripts found in the transcriptome, each one possessing the CP for several similar late proteins.
-Normally, MLTU transcripts encoding particular ORFs splice the TPL onto a splice site just upstream of the ORF to be expressed [@Donovan2020].
-While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as these L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSC utility and ribosome shunting found in other AdVs for their translation [@Donovan2020; @Yueh1996].
+We identified five TTSs (10,549, 12,709, 16,870, 22,116, 25,168 bp) in this TU, which we consider as corresponding to the five late mRNA classes (L1-L5), respectively.
+L1 mRNAs include TRXPT_8, encoding the 52K ORF as predicted.
+L2 mRNAs include TRXPT_16, TRXPT_17, and TRXPT_18, all containing the sTPL with their respective coding exons.
+They encode pIIIa, III (penton), and pVII, respectively.
+The L3 mRNAs, TRXPT_14 and TRXPT_20, both encode the hexon (II) ORF but hexon is the only ORF encoded on TRXPT_14, whereas TRXPT_20 encodes pX (pre-Mu), pVI, and hexon in that order.
+L4 mRNAs, TRXPT_9, TRXPT_10, TRXPT_11, and TRXPT_13 are the largest transcripts in the transcriptome and encode several similar late proteins.
 TRXPT_9 and TRXPT_10 are very similar but not identical.
-The last exon of TRXPT_9 seems to be truncated and probably shares the same TTS as the other L4 mRNAs.
-They are both 6-exon transcripts encoding pVII as the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) -- uses an upstream in-frame SC than predicted, and ORF12 (a novel unpredicted 120 aa protein).
-TRXTP_10 (and TRXPT_9 with the L4 TTS) additionally has the CP for pVIII and eE3.
-Conversely, TRXPT_11 is a seven-exon mRNA with hexon as its 5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also pVIII and eE3 in that order.
-TRXPT_13 seems to be an E3 ORF utilizing the MLP TSS as it encodes classical L4P genes such as pVIII and eE3 in that order similar to TRXPT_22 (E3 TU) but it lacks the novel first ORF (8.3KII) of TRXPT_22.
-
-Lastly, the L5 class includes only TRXPT_12 which contains the TPL and a coding terminal exon.
-Its 5'-most ORF is fiber (IV) but it also has the CP for the THEV specific gene, ORF7.
-TRXPT_12's CP is identical to TRXPT_27 of the E3 TU but they differ in their 5'-UTRs.
+The last exon of TRXPT_9 seems to be truncated and likely shares the same TTS as TRXPT_10.
+They both encode pVII as the 5'-most ORF and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) from an upstream in-frame SC, and ORF12 (a novel 120 residue protein).
+Additionally they have the CP for pVIII and eE3.
+TRXPT_11 encodes hexon as its 5'-most ORF and also has the CP for eProt, ORF12, e33K, pVIII and eE3.
+Typically, MLTU transcripts splice the TPL onto a splice site just upstream of the ORF to be expressed [@Donovan2020].
+While this holds true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do not have such close proximity splicing but are contained in larger transcripts such as these L4 mRNAs, strongly suggesting the use of non-standard ribosomal initiation mechanisms such as secSC usage or ribosome shunting described in other AdVs for their translation [@Donovan2020; @Yueh1996].
+TRXPT_13, an E3 ORF utilizing the MLP TSS, encodes the classical L4P genes, pVIII and eE3.
+Lastly, the L5 class transcript, TRXPT_12, encodes Fiber as its 5'-most ORF but also has the CP for ORF7.
+Interestingly, the CP of TRXPT_12 and TRXPT_27 of the E3 TU are identical but are initiated from different TSSs.
 \newpage
@@
 ## DISCUSSION/CONCLUSIONS
-While the advent of next-generation sequencing has rendered easier the study of large and complex eukaryotic transcriptomes, the study of the smaller and compact viral transcriptomes remains unintuitively challenging, as several transcripts may have significant overlaps due to genome economization.
-Characterizing AdV transcriptomes is even more difficult due to the wide array of mRNAs produced via very complex alternative splicing combined with alternative polyadenylation, all initiated from relatively few promoters.
-This makes AdV transcriptomes some of the most intricate for a virus.
-The challenge is further compounded by the fact that the standard software programs used in the RNA-seq analysis pipelines are not designed primarily for such compact, gene-dense, and complex transcriptomes as AdVs.
-Furthermore, in our case, there is no prior transcriptomic studies for THEV.
-Our approach to properly handle this complex data was to use standard RNA-seq analysis programs coupled with some custom analyses and experimentally validating all splice junctions with independent methods.
-Our work provides the first insights into the splicing patterns of THEV, which is expectedly similar to other MAdVs but with key differences.
-Our work shows 34 transcripts in the THEV transcriptome grouped into five TUs, of which the E3 TU shows great complexity of alternative splicing.
 
+While the advent of next-generation sequencing has rendered easier the study of large and complex eukaryotic transcriptomes, studying the smaller, compact viral transcriptomes remains unintuitively challenging, as the transcripts typically have significant overlaps due to genome economization.
+AdV transcriptomes escalate the difficulty due to the wide array of mRNAs produced via very complex alternative splicing and polyadenylation, all initiated from relatively few promoters.
+Standard RNA-seq analysis programs, not primarily designed for such compact, gene-dense, and complex transcriptomes, further compound this challenge.
+Furthermore, in our case, no prior transcriptomic studies for THEV exist.
+Our approach combines standard RNA-seq analysis programs with custom analyses and experimentally validating all splice junctions with independent methods.
+The transcript map for THEV produced from our analysis is strikingly similar to that of the MAdVs.
+
+Our work provides the first insights into THEV splicing, revealing 34 transcripts grouped into five transcription units (TUs).
+The general temporal gene expression regulation observed in MAdVs, with early regions peaking at earlier time points followed by MLTU predominance at later time points, seems to also apply to THEV.
 An unexpected observation is that the pileup of mapped reads to THEV seems consistently skewed over similar regions of the genome at all time points.
-As the gene expression of AdVs is temporally regulated, we expected to see unambiguous differences in the pileup of reads over different regions of the genome at different time points, indicating the different stages of infection.
-While this could simply mean that the infection was not well synchronized, we speculate that the temporal gene expression regulation of THEV is probably different from MAdVs.
-This is supported by a previous study stating the same conclusion with its finding that almost all THEV transcripts were detectable by at 4h.p.i, and by 8h.p.i, mRNA for all predicted ORFs (including the late genes) were present [@Aboezz2019].
-Conversely, despite the overall pileup similarity, a close inspection shows that the relative proportions of reads over some regions show some variation over time.
-The breakdown of transcripts detected at different time points in **Figure 3b** seems to support this different temporal regulation of THEV.
-Specifically, the MLP of THEV is active significantly earlier in infection -- as early as 4h.p.i and more pronounced at 12h.p.i (**Figure 3b** and **Table 2a**), -- whereas the late phase shift in MAdVs occurs after 24h.p.i.
-This also lends credence to our speculation.
-However, generally speaking, the overall temporal gene expression regulation known in MAdVs -- early regions showing their peak expression at earlier time points followed by predominance of the MLTU at later time points -- also holds true for THEV.
-Further studies would be necessary to establish the precise temporal regulation of THEV transcription.
+Given the temporal regulation of AdVs gene expression, we anticipated distinct differences in read pileups over the genome at different time points, indicating the different stages of infection.
+This probably due to the infection not being well-synchronized, leading to transcripts overlapping the time points.
+Further research is required to determine the precise temporal regulation of THEV.
 
-The use of short read deep sequencing to reconstruct full AdV mRNA structures provides excellent results, especially for mapping the splice sites.
-However, due to the substantial overlapping nature of AdV mRNAs coupled with the fragmentation step in the library preparation protocol, mapping the precise TSS and TTS of the assembled transcripts is difficult.
-Also, similar transcripts with substantial overlaps may be assembled as one longer mRNA since the short reads alone do not provide enough context for the transcript assembler (StringTie) to distinguish them.
-In our results, we see transcripts in the same TU initiated or terminated in the same approximate area (10-70 bp and 1-300 bp apart for TSS and TTS, respectively) but not precisely at the same position.
-We consider the most upstream TSS or most downstream TTS for the transcripts involved but we present them unchanged in all the figures shown.
-Also, by comparison to the more well-studied MAdV transcriptomes, we believe that a few long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are probably a result of fusing some L4P-derived transcripts to the terminal exons of the bona fide MLTU transcripts by StringTie, making them significantly longer.
-These mRNAs do not only have unusually many exons for an AdV, but their last three or four exons are also identical to the L4P-derived mRNAs.
-Future studies using long read sequencing technologies are necessary to provide conclusive data for precisely mapping the TSS and TTS, as well as teasing apart the bona fide structures of the long MLTU transcripts.
-Furthermore, it is not unreasonable to presume that several splice variants were undiscovered in our work as evidenced firstly by finding unique transcripts using 3' RACE and during our splice junction validation steps.
+Short read deep sequencing effectively reconstructs full AdV mRNA structures, particularly mapping splice sites [@Zhao2014].
+However, the substantial overlapping nature of AdV mRNAs and fragmentation during library preparation make it challenging to map the exact TSS, TTS, and PASs of assembled transcripts.
+Also, transcripts with significant overlaps may be assembled as a single, longer mRNA, since the short reads alone do not provide enough context for the transcript assembler (StringTie) to distinguish them.
+Our results show transcripts in the same TU initiating or terminating in similar areas, but not at the exact same position.
+We consider the most upstream TSS or most downstream TTS for for the transcripts involved but we present them unchanged in all the figures shown (see **Supplementary Table S2**).
+Also, comparing our results to the better-studied MAdV transcriptomes, we believe some long transcripts in the MLTU (TRXPT_9, TRXPT_10, and TRXPT_11) are likely due to fusing some E3 transcripts to the terminal exons of the MLTU transcripts by StringTie, making them significantly longer.
+These mRNAs have unusually many exons and their last few exons are identical to some E3 mRNAs.
+Future studies using long read sequencing technologies will provide more precise mapping of the TSS and TTS and clarify the structures of the long MLTU transcripts.
+
+While most predicted ORFs are encoded by the spliced transcripts, we found some that seem to be truncated predictions, as either an upstream in-frame SC or unknown upstream exons were found.
+Other ORFs were identified that were either shorter or longer isoforms of some predicted ORF.
+We also found several novel unpredicted ORFs (**Supplementary Table S3**).
+On this basis, we anticipate that further studies will likely reveal more unpredicted novel ORFs or new variants of predicted ORFs.
+Furthermore, it is not unreasonable to presume that several splice variants will likely be found as evidenced firstly by finding unique transcripts using 3' RACE and during our splice junction validation steps.
 And secondly, recent studies [@Donovan2020; @Zhao2014; @Westergren2021] are still discovering novel mRNA variants for even the best studied MAdVs decades later.
-Another observation made is that all the TTSs in THEV's transcriptome are in close proximity to A/T-rich sequences which we presume to be polyadenylation signal sequences (PASS).
-Interestingly, some of these PASSs are located in the immediate vicinity of two closely located TTSs expressed on opposite strands.
-Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS between them, as do the E4 (anti-sense strand) and the sense strand TRXPT_12 and TRXPT_27.
 
-An interesting finding of our analysis is that while most of the predicted ORFs are precisely encoded by the spliced transcripts, we found a few that seem to be truncated predictions, as either an upstream in-frame SC (eORF1, eE3, and eProt) or unknown upstream exons spliced onto them (eIVa2, e33K, and eORF8) were found.
-Other ORFs were identified that were either shorter (tDBP, t100K) or longer (e22K) isoforms of some predicted ORF but we found evidence to support the predicted ORF itself, making them all possible genuinely translated variants.
-We also found several novel unpredicted ORFs.
-Taken together, we surmise that further studies will likely yield even more unpredicted novel ORFs or variants of predicted ORFs.
-
-Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most AUG normally being used to determine the translation reading frame.
-However, depending on the sequence context, in some organisms, the initiating codon may even be a non-AUG start codon.
-AdV mRNAs, which mostly span more than one ORF, are known to be functionally polycistronic, employing non-standard mechanisms of translation initiation, namely, secSC usage and ribosome shunting [@Westergren2021; @Guimet2016].
-While there is no reliable method of predicting how efficiently any given AUG will be used, AdVs use secondary AUGs as initiation codons for most E1b proteins and for some E3 proteins.
+Eukaryotic mRNAs are typically functionally monocistronic, with the 5’-most AUG determining the translation reading frame.
+However, AdV mRNAs, which span more than one ORF, are functionally polycistronic, employing non-standard mechanisms of translation initiation such as secSC usage and ribosome shunting [@Westergren2021; @Guimet2016].
+AdVs use secondary AUGs as initiation codons for most E1b proteins and some E3 proteins.
 In fact, recent studies show that secSC usage is found transcriptome-wide.
-This is thought to occur because translation initiation at the first SC is inefficient, allowing downstream SCs to be employed for initiation [@Donovan2020].
-The ribosomal shunting or jumping mechanism is utilized for MLTU transcripts that have the TPL.
-This mechanism allows the ribosome to translocate to a downstream initiating codon under the direction of the shunting elements in the TPL, even if a start codon in a good Kozak sequence context is bypassed.
-Thus, predicting the protein(s) that are expressed from an AdV mRNA becomes highly uncertain as any one of the SC may be selected [@Guimet2016; @Westergren2021].
-Almost all the THEV transcripts in our data have the CP for several ORFs, some spanning as many as six ORFs but the majority spanning at least two ORFs.
-Therefore, we believe our data support the usage of these special ribosome initiation mechanisms as several predicted and novel ORFs found on mRNA in our data have no conceivable mechanism of being translated if only the typical ribosome scanning mechanism is employed.
-Interestingly, several distinct transcripts have identical CPs.
-This is not unique to THEV but is observed in human AdVs in a recent study [@Donovan2020].
+This is thought to occur because translation initiation at the first SC is inefficient, allowing downstream SCs to be employed [@Donovan2020].
+Ribosomal shunting or jumping mechanism is utilized for MLTU transcripts that have the TPL.
+This mechanism allows the ribosome to translocate to a downstream AUG, under the direction of the shunting elements in the TPL, even if a start codon in a good Kozak sequence context is bypassed.
+Thus, predicting the protein(s) expressed from an AdV mRNA is uncertain as any one of the AUGs may be selected [@Guimet2016; @Westergren2021].
+Almost all the THEV transcripts in our data have the CP for several ORFs, some spanning as many as six ORFs.
+This supports the usage of these special ribosome initiation mechanisms as several predicted and novel ORFs found on mRNA in our data could not be translated using only the typical ribosome scanning mechanism.
+Interestingly, several distinct THEV mRNAs have identical CPs.
+This is also observed in human AdVs in a recent study [@Donovan2020].
 They proposed that this may permit protein production to be fine-tuned through alteration in the balance between different mRNA groups expressing that ORF.
 
-It is well established that AdV alternative splicing undergoes a regulated temporal shift in splice site usage.
-This was thought to be limited to certain TUs; however, recent studies suggest that AdVs routinely produce different combinations of splice acceptor–donor pairs and that this is observed in all TUs [@Westergren2021; @Akusjarvi2008; @Donovan2020; @Guimet2016].
-The mechanistic details of this phenomenon have been best studied for the E1A and L1 units.
-The studies show that AdVs (specifically, late phase AdV-infected nuclear extract) modulate the activities of the splicing factor U2AF and the cellular SR family of splicing factors (reviewed in reference [@Akusjarvi2008]) and encode several mostly late phase proteins (E4-ORF3, E4-ORF6, E4-ORF4, L4-33K, and L4-22K) that influence the RNA splice site used.
-This phenomenon seems to occur in the THEV transcriptome also, as the stringency of splice acceptor-donor pairs selected decreases measurably from the onset of the late phase (see **Figure 5**).
-In fact, recent studies of some human AdVs show that a virtually unlimited number of combinatorial alternative splicing events occur in an AdV lytic infection, resulting in menagerie of novel transcripts [@Donovan2020; @Westergren2021].
+AdV alternative splicing undergoes a regulated temporal shift in splice site usage, previously thought to be limited to certain TUs.
+However, recent studies suggest that AdVs routinely produce different combinations of splice acceptor–donor pairs across all TUs [@Westergren2021; @Akusjarvi2008; @Donovan2020; @Guimet2016].
+The details of this phenomenon have been best studied for the E1A and L1 units.
+AdVs modulate the activities of the splicing factor U2AF and the cellular SR family of splicing factors (reviewed here [@Akusjarvi2008]), and encode several proteins that influence the RNA splice site used.
+This phenomenon appears to occur in the THEV transcriptome, as the stringency of splice acceptor-donor pairs selected decreases from the onset of the late phase (**Figure 5**).
+Recent studies show that a virtually unlimited number of combinatorial alternative splicing events occur in an AdV lytic infection, resulting in a variety of novel transcripts [@Donovan2020; @Westergren2021].
 It is unlikely that the entire repertoire of mRNA produced via this mechanism will actually be translated.
-However, it has been speculated that the plasticity in alternative RNA splicing enables AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions.
-The capacity to produce novel exon combinations offers the virus an evolutionary advantage to adjust the repertoire of mRNA transcription and protein production in the changing environment of the viral replication cycle [@Donovan2020; @Westergren2021].
+However, it has been speculated that the plasticity in alternative RNA splicing enables AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions, confering an evolutionary advantage [@Donovan2020; @Westergren2021].
 
-Summarizing all the main points above, we see that the THEV transcriptome bears remarkable overall similarity to the better studied MAdVs.
-The transcriptome is organized into five TUs, the temporal regulation is divided into early and late genes, and a broad repertoire of transcripts are produced via virtually unlimited alternative splicing.
-However, the THEV transcriptome appears to be less sophisticated (i.e, it encodes fewer genes) than MAdVs primarily because the MAdV genomes are close to twice as long as that of THEV, which rationally should encode less genes.
+In summary, the THEV transcriptome bears remarkable similarity to the better-studied MAdVs.
+The transcriptome is organized into five TUs, with temporal regulation divided into early and late genes, and a broad repertoire of transcripts are produced via virtually unlimited alternative splicing.
+However, the THEV transcriptome appears less sophisticated (i.e, it encodes fewer genes) than MAdVs, primarily because the MAdV genomes are close to twice as long as that of THEV.
 The lack of subdivision of the E1 region into E1a and E1b is one of the most obvious examples.
-Also, the MAdV E4 region encodes several proteins unlike in THEV where only one transcript coding for one protein was found.
-The most conspicuous example is found in examining the complexity of the MLTU leader sequences.
-While the majority of the THEV MLTU transcripts begin with the TPL (267 bp long) just like MAdVs, and also utilize a variant leader sequence (sTPL), it is well-established that significantly more diverse 5'UTRs are employed for MAdV MLTU transcripts.
-Namely, the TPL (used for majority of transcripts), the so-called x, y, and z leaders, and the i-leader are 5' leaders utilized by MAdV MLTU mRNAs.
-Granted, the MAdV MLTU transcripts infrequently incorporate the non-TPL leaders, their absence in our data could mean that the 5'UTR diversity of THEV's MLTU mRNA are indeed more limited due to its smaller genome size.
-It is also possible that later studies could uncover more variety not seen in our results.
-Specifically, using long read sequencing technologies would be a excellent approach to discovering and fine-tuning the transcriptome characterized in this work.
-Also, it is likely that future studies repeating this work in other cell lines will yield some interesting insights.
+Also, the MAdV E4 region encodes several proteins unlike in THEV where only one transcript encoding one protein was found.
+The complexity of the MLTU leader sequences is another example.
+While the majority of the THEV MLTU transcripts begin with the TPL just like MAdVs with a small subset using a variant leader sequence (sTPL), significantly more diverse 5'-UTRs are employed for MAdV MLTU transcripts.
+Namely, the TPL, the so-called x, y, and z leaders, and the i-leader are 5' leaders utilized by MAdV MLTU mRNAs.
+The absence of these non-TPL leaders in our data could mean that the 5'-UTR diversity of THEV's MLTU mRNAs is more limited due to its smaller genome size or future studies using long read sequencing technologies could uncover more variety not seen in our results.
 \newpage
@@
 ### Validation of Novel Splice Junctions
+
 All splice junctions identified in this work are novel except one predicted splice site each for pTP, DBP, and 33K, which were corroborated in our work.
@@
 ## CODE AVAILABILITY
+
 All the code/scripts in the entire analysis pipeline are available on github (<https://github.com/Abraham-Quaye/thev_transcriptome>)
@@
 ## REFERENCES
+
 ```{=tex}
@@
 \newpage
+
 ## TABLES AND FIGURES
+
 ![**Figure 1.
-Predicted ORF map of THEV avirulent strain.** The central horizontal line represents the double-stranded DNA marked at 5kb intervals as white line breaks.
+Predicted ORF map of THEV avirulent strain.** The central horizontal line represents the double-stranded DNA marked at 2kb intervals as white line breaks.
 Colored blocks represent viral genes.
@@
 A) Per base coverage of sequence reads mapping to THEV genome by time point.** The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point.
-**B) Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line.** Virus titers in the freeze-thawed supernatant from infected cells were a quantified with a qPCR assay.
+**B) Growth curve of THEV (VAS vaccine strain) in MDTC-RP19 cell line.** Virus quantities in the freeze-thawed supernatant from infected cells were a quantified with a qPCR assay.
 There is no discernible increase in virus titer up 12 hpi, after which a steady increase in virus titer is measured.
@@
 ![**Figure 3.
-A) Transcriptome of THEV from RNA-seq.** THEV transcripts assembled from all time points by StringTie are unified forming this final transcriptome (splicing map).
+A) Transcriptome of THEV from RNA-seq.** THEV transcripts assembled from all time points by StringTie are unified forming this transcriptome (splicing map).
 Transcripts belonging to the same transcription unit (TU) are located in close proximity on the genome and are color coded and labeled in this figure as such.
@@
 Predicted ORFs are also indicated here, colored light grey.
-**B) THEV transcripts identified at given time points.** Transcripts are color coded as explained in **(A)**.
-](results/r/figures/figure3.png)
+**B) THEV transcripts identified at given time points.** Transcripts are color coded as explained in **(A)**.](results/r/figures/figure3.png)
 
@@
 \FloatBarrier
+
 ```{r}
@@
 ```
+
 \FloatBarrier
@@
   tab %>% 
-    select(-c(`Splice \n Acceptor-Donor`, Reads)) %>% 
+    select(-c(`Splice \n Acceptor-Donor`, Reads, Splice_Site)) %>% 
     dplyr::rename("Reads (Percentage)" = Reads_Percentage) %>%
-    mutate(Splice_Site = case_when(Splice_Site == "GT-AG" ~ "GU-AG",
-                                   Splice_Site == "CT-AC" ~ "CU-AC",
-                                   TRUE ~ Splice_Site)) %>% 
     flextable() %>%
@@
 ```
+
 \newpage
+
 ## SUPPLEMENTARY MATERIALS
@@
 
+**Supplementary Table S2**
+
+```{r}
+tibble(region = c("E1", "E2", "E2/IM", rep("E3", 3), "E4", rep("MLTU", 5)),
+       sub_region = c("E1", "E2A", "E2B/IM", "E3A", "E3B", "E3C", "E4",
+                      "L1", "L2", "L3", "L4", "L5"),
+       trxpts = c(list(paste0("TRXPT_", 1:4, collapse = ", ")),
+                  list(paste0("TRXPT_", c(21, "21B"), collapse = ", ")),
+                  list(paste0("TRXPT_", c(5:7, 31), collapse = ", ")),
+                  list(paste0("TRXPT_", c(22, 24), collapse = ", ")),
+                  list(paste0("TRXPT_", c(23,25,"25B",26,30), collapse = ", ")),
+                  "TRXPT_27", "TRXPT_28", "TRXPT_8",
+                  list(paste0("TRXPT_", c(16:17), collapse = ", ")),
+                  list(paste0("TRXPT_", c(14,20), collapse = ", ")),
+                  list(paste0("TRXPT_", c(9:11, 13), collapse = ", ")),
+                  "TRXPT_12"),
+       tts = c(2325, 16934, 2334, 22491, 23884, 25168, 25192, 10549, 12709,
+               16870, 22116, 25168),
+       nearest_pas = c("2,323", "16,950", "2,333", "22,458 (AGUAAA)", "23,889",
+                       "25,166", "25,203", "10,537", "-", "16,903",
+                       "22,098 (AAGAAA)", "25,166")
+             ) %>%
+  dplyr::mutate(trxpts = as.character(trxpts)) %>%
+  flextable(.) %>%
+  flextable::theme_zebra() %>%
+  flextable::set_header_labels(region = "Region", sub_region = "Sub Region",
+                    trxpts = "Transcripts", tts = "TTS",
+                    nearest_pas = "Nearest ‘AAUAAA’ TTS signal (location refers to 'U' in the sequence)") %>%
+  flextable::width(width = 0.8) %>%
+  flextable::width(j = "trxpts", width = 2) %>%
+  flextable::width(j = "nearest_pas", width = 1.5) %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::font(fontname = "Arial", part = "all") %>%
+  set_caption("Table S2: Mapping Transcript TTS with Closest Polyadenylation Signal")
+
+```
+
+**Supplementary Table S3**
+```{r}
+set_flextable_defaults(font.size = 10)
+#annotate novel proteins with 1 and longer variants with 2 
+# fix label clip of fig 7
+tibble(trxpts = paste0("TRXPT_", c(1, 2, "2B", 3:21, "21B", 22:25, "25B", 26:31)),
+       primary_prod = c("ORF9", "ORF10", "eORF1", "ORF4", "ORF11", "IVa2",
+                        rep("pTP", 2), "52K", rep("pVII", 2), "Hexon (II)",
+                        "Fiber (IV)", "pVIII", "Hexon (II)", "-", "pIIIa",
+                        "Penton (III)", "pVII", "-", "pX", "DBP", "tDBP",
+                        "8.3KII", "8.3KI", "e33K", "t100K", "100K", "pVIII",
+                        "Fiber (IV)", "eORF8", "8.3KI", "e22K", "Ad-pol"
+                        ),
+       size_kda = c(17.9, 66.4, 64.3, 13.1, 15.9, 42.3, rep(70.5, 2), 33.8,
+                    rep(13.2, 2), 101.1, 49.0, 21.8, 101.1, "-", 57.6, 50.8,
+                    13.2, "-", 6.1, 43.3, 39.3, 8.6, 8.3, 19.8, 62.4, 76.5,
+                    21.8, 49.0, 26.4, 8.3, 15.7, 129.2
+                    ),
+       size_aa = c(160, 597, 580, 115, 143, 371, rep(597, 2), 300, rep(120, 2),
+                   906, 454, 200, 906, "-", 505, 448, 120, "-", 58, 380, 346,
+                   73, 73, 171, 543, 665, 200, 454, 229, 73, 140, 1112
+                   ),
+       start = c(211, 211, 1965, 211, 211, 3616, rep(10995, 2), 8570,
+                 rep(12347, 2), 13610, 22519, 20769, 13610, "-", 9462, 11001,
+                 12347, "-", 12712, 18186, 18013, rep(18230, 5), 20769, 22519,
+                 26246, rep(18230, 2), 6768
+                 ),
+       stop = c(rep(2312, 2), 1953, 2312, 1953, 2334, rep(6765, 2), 9472,
+                rep(12709, 2), 16330, 23883, 21371, 16330, "-", 10979, 12347,
+                12709, "-", 12888, rep(16973, 2), 20457, 20262, 20699, rep(20227, 2),
+                21371, 23883, 25204, 20262, 20411, 3430
+                ),
+       coding_pt = c(rep(list(c("Hyd", "ORF4")), 3), "Hyd", list(c("Hyd", "ORF4")),
+                     "-", rep("Ad-pol", 2), "-",
+                     rep(list(c("pX", "pVI", "hexon", "eProt", "ORF12", "pVIII", "eE3")), 2),
+                     list(c("eProt", "ORF12", "e33K", "pVIII", "eE3")), "ORF7",
+                     "eE3", "-", "-", list(c("Penton (III)", "pVII")), "-", "-",
+                     "-", list(c("pVI", "hexon")), "-", "-", list(c("pVIII", "eE3")),
+                     list(c("pVIII", "eE3", "Fiber")), list(c("pVIII", "E3")),
+                     rep(list(c("22K", "pVIII", "eE3")), 2), list(c("eE3", "Fiber")),
+                     "ORF7", "-", "-", list(c("pVIII", "eE3", "Fiber")), "-"
+                     )
+       ) %>%
+  mutate(coding_pt = as.character(coding_pt)) %>%
+  mutate(coding_pt = str_replace(coding_pt, '^c\\((.*)\\)$', '\\1')) %>%
+  mutate(coding_pt = str_replace_all(coding_pt, '"', "")) %>% 
+  flextable(.) %>%
+  flextable::theme_zebra() %>%
+  flextable::set_header_labels(trxpts = "mRNA", primary_prod = "Primary Product",
+                               size_kda = "Size\n(kDa)", 
+                               size_aa = "Number of\nResidues",
+                               start = "Start Codon\nPosition",
+                               stop = "Stop Codon\nPosition",
+                               coding_pt = "Downstream\nCoding Potential") %>% 
+  flextable::width(width = 0.8) %>%
+  flextable::width(j = "coding_pt", width = 2) %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::font(fontname = "Arial", part = "all") %>%
+  footnote(., i = c(1,2,5,24,25), j = 2,
+           value = as_paragraph(c("Novel product identified in this work")),
+           ref_symbols = c("new"), part = "body", inline = T) %>%
+  footnote(., i = c(3,26,31,33), j = 2,
+           value = as_paragraph(c("Longer isoform identified in this work")),
+           ref_symbols = c("L"), part = "body", inline = F) %>%
+  footnote(., i = c(23), j = 2,
+           value = as_paragraph(c("Shorter isoform identified in this work")),
+           ref_symbols = c("S"), part = "body", inline = F) %>%
+  set_caption("Table S3: The Encoded Proteins and Coding Potential of THEV Transcripts")
+```
+
 \newpage
+
 **Supplementary PCR Methods**
+
 ```{r Supplementary PCR Methods}
@@
 We used 35 cycles of amplification.
+The PCR products of THEV cDNA shown in the gels in the table above were cloned and Sanger sequenced to confirm the splice junctions.
+We included "No reverse transcriptase (No RT)" template controls to ensure the PCR products are of RNA origin.
 
-**Supplementary Computational Analysis**    
+**Supplementary Computational Analysis**\
 Snakemake v7.24.0 was used to manage our entire workflow.
 A graph of the main steps in our pipeline generated with Snakemake is shown below.
-Our trimmed RNA-seq reads were mapped to the genome of _M.
-gallopavo_ (with the THEV genome as one of its chromosomes) using Hisat2, to generate the alignment (BAM) files and StringTie used to assemble the transcriptome with a GTF annotation file containing the predicted THEV ORFs as a guide.
+Our trimmed RNA-seq reads were mapped to the genome of *M.
+gallopavo* (with the THEV genome as one of its chromosomes) using Hisat2, to generate the alignment (BAM) files and StringTie used to assemble the transcriptome with a GTF annotation file containing the predicted THEV ORFs as a guide.
 The GTF annotation file was derived from a GFF3 annotation file obtained from NCBI using Agat - version 1.0.0, a program for converting between many different file formats used in bioinformatics.
@@
 
-![A flowchart of the major steps in the computational analysis pipeline (_generated with Snakemake_)](project_map.png)
+![A flowchart of the major steps in the computational analysis pipeline (*generated with Snakemake*)](project_map.png)

### 2024-05-06 manuscript_thev_transcriptome.tex
first round changes after jvi review

@@
 providing key insight into the THEV gene expression and mRNA structures.
-Researchers previously annotated THEV's genome as encoding 23 open
+Researchers previously annotated the genome of THEV as encoding 23 open
 reading frames (ORFs). In this work we identified 29 spliced transcripts
@@
 by 3' rapid amplification of cDNA ends (3' RACE) experiments. Thus, we
-report that the genome of THEV contains 34 unique transcripts with the
-coding capacity for all annotated ORFs. However, we found six of the
-previously annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to
-be truncated ORFs on the basis of the identification of an in-frame
-upstream start codon or the detection of additional coding exons. We
-also identified three of the annotated ORFs with longer or shorter
-isoforms, and seven novel unpredicted ORFs that could potentially be
-translated; although it is beyond the scope of this manuscript to
-investigate whether they are translated. Similar to other adenoviruses
-(AdVs), THEV also produces multiple distinctly spliced transcripts that
-code for the same proteins across its genome. Our data show that all
-THEV transcripts are spliced and organized into five transcription units
-under the control of their cognate promoters like other AdVs. However,
-our data suggest that the temporal regulation of THEV may be different
-from other AdVs. \newpage
+report that the genome of THEV contains 34 transcripts with the coding
+capacity for all annotated ORFs. However, we found six of the previously
+annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated
+ORFs on the basis of the identification of an in-frame upstream start
+codon or the detection of additional coding exons. We also identified
+three of the annotated ORFs with longer or shorter isoforms, and seven
+novel unannotated ORFs that could potentially be translated; although it
+is beyond the scope of this manuscript to investigate whether they are
+translated. Similar to other adenoviruses (AdVs), THEV also produces
+multiple distinctly spliced transcripts that code for the same proteins
+across its genome. Our data show that all THEV transcripts are spliced
+and organized into five transcription units under the control of their
+cognate promoters like other AdVs. \newpage
 
@@
 protein-coding genes, making it highly gene-dense. There are 16 genes
-termed ``genus-common'' that are homologous in all AdVs; these are
-thought to be inherited from a common ancestor. All other genes are
-termed ``genus-specific''. The genus-specific genes tend to be located
-at the termini of the genome while genus-common genes are usually
-towards the center of the genome (1). This pattern is also observed in
+termed ``genus-common'' that are homologous in all AdVs, presumably
+inherited from a common ancestor. All other genes are termed
+``genus-specific''. The genus-specific genes tend to be located at the
+termini of the genome while genus-common genes are usually towards the
+center of the genome (1). This pattern is also observed in
 \emph{Poxviridae} and \emph{Herpesviridae}, which also have linear DNA
@@
 debilitating acute disease predominantly affecting turkey poults
-characterized by immunosuppression (IS), intestinal lesions leading to
-bloody diarrhea, and up to 80\% mortality (2, 11--13). While the current
-vaccine strain (a THEV-A strain isolated from a pheasant; Virginia
-Avirulent Strain {[}VAS{]}) has proven effective at preventing HE in
-turkey poults, it still retains its immunosuppressive ability. Thus,
-vaccinated birds are rendered more susceptible to opportunistic
-infections and death than unvaccinated birds leading to substantial
-economic losses (11, 14--16). To eliminate the immunossupressive effect
-of the vaccine strain, a thorough investigation of the culprit viral
-genes mediating this phenomenon is essential. However, the transcriptome
-(splicing and gene expression patterns) of THEV has not been
-characterized, making an investigation of specific IS-related viral
-genes impractical.
+characterized by immunosuppression, intestinal lesions leading to bloody
+diarrhea, and up to 80\% mortality (2, 11--13). While the current
+vaccine strain (a THEV-A called Virginia Avirulent Strain {[}VAS{]}) has
+proven effective at preventing HE in turkey poults, it still retains its
+immunosuppressive ability. Thus, vaccinated birds are rendered more
+susceptible to opportunistic infections and death than unvaccinated
+birds leading to substantial economic losses (11, 14--16). To eliminate
+the immunosupressive effect of the vaccine strain, a thorough
+investigation of the culprit viral genes mediating this phenomenon is
+essential. However, the transcriptome (splicing and gene expression
+patterns) of THEV has not been characterized, making an investigation of
+specific immunosuppressive viral genes impractical.
 
@@
 (17, 18). However, a large preponderance of studies focus on MAdVs --
-specifically human AdVs. Thus, most of the current knowledge regarding
-AdV gene expression and replication is based on MAdV studies, which is
-generalized for all other AdVs (10, 19). MAdV transcription is
-temporally regulated; therefore, genes are categorized into five early
-transcription units (E1A, E1B, E2, E3, and E4), two intermediate (IM)
-units (pIX and IVa2), and one major late transcription unit (MLTU or
-major late promoter {[}MLP{]} region), which generates five families of
-late mRNAs (L1-L5) based on the polyadenylation site. An additional gene
-(UXP or U exon) is located on the reverse strand. The early genes encode
-non-structural proteins such as enzymes or host-cell modulating
-proteins, primarily involved in DNA replication, or providing the
-necessary intracellular niche for optimal replication while late genes
-encode structural proteins that act as capsid proteins, promote virion
-assembly, or direct genome packaging. The immediate early genes E1A are
-expressed first, followed by the delayed early genes, E1B, E2, E3 and
-E4. Then the intermediate early genes, IVa2 and pIX are expressed
-followed by the late genes (10, 17, 18). It is noteworthy that the MLP
-shows basal transcriptional activity during early infection (before DNA
-replication), with a comparable efficiency to other early viral
-promoters, but it reaches its maximal activity during late infection
-(after DNA replication). However, during early infection only a subset
-of the MLP-derived transcripts are expressed (10). MAdV makes an
-extensive use of alternative RNA splicing to produce a very complex
-array of mRNAs. All but the pIX mRNA undergo at least one splicing
-event. For instance, the MLTU produces over 20 distinct splice variants
-all of which contain three non-coding exons at the 5'-end (collectively
-known as the tripartite leader; TPL) (17, 18). There is also an
-alternate three-exon 5' non-coding leader sequence present in varying
-amounts on a subset of MLTU mRNAs (known as the x-, y-, and z-leaders).
-Lastly, there is the i-leader exon, which is infrequently included
-between the second and third TPL exons, and codes for the i-leader
-protein (20). Thus, the MLTU produces a complex repertoire of mRNA with
-diverse 5' untranslated regions (UTRs) spliced onto different 3' coding
-exons which are grouped into five different 3'-end classes (L1-L5) based
-on polyadenylation site. Each transcription unit (TU) contains its own
-promoter driving the expression of the array of mRNA transcripts
-produced via alternative splicing in the unit (10, 17, 18). The
-promoters are activated at different phases of the infection by proteins
-from previously activated TUs. Paradoxically, the early-to-late phase
-transition during infection requires the L4 gene products, 22K and 33K,
-which should only be available after the transition. However, a promoter
-in the L4 region (L4P) that directs the expression of these two proteins
-independent of the MLP was found, resolving the paradox (10, 17, 21).
-During translation of AdV mRNA, recent studies using long-read direct
-RNA sequencing strongly suggest the potential usage of secondary start
-codons; adding to what was already a highly complex system for gene
-expression (17, 22).
+specifically human AdVs. Thus, most of the current AdV gene expression
+and replication knowledge is based on MAdV studies, which is generalized
+for all other AdVs (10, 19). MAdV transcription is temporally regulated;
+their genes are categorized into five early transcription units (E1A,
+E1B, E2, E3, and E4), two intermediate (IM) units (pIX and IVa2), and
+one major late transcription unit (MLTU or major late promoter {[}MLP{]}
+region), which generates five families of late mRNAs (L1-L5) based on
+the polyadenylation site. An additional gene (UXP or U exon) is located
+on the reverse strand. The early genes encode non-structural proteins
+such as enzymes or host-cell modulating proteins, primarily involved in
+DNA replication, or providing the necessary intracellular niche for
+optimal replication while late genes encode structural proteins that act
+as capsid proteins, promote virion assembly, or direct genome packaging.
+The immediate early genes E1A are expressed first, followed by the
+delayed early genes, E1B, E2, E3 and E4. Then the intermediate early
+genes, IVa2 and pIX are expressed followed by the late genes (10, 17,
+18). It is noteworthy that the MLP shows basal transcriptional activity
+during early infection (before DNA replication), with a comparable
+efficiency to other early viral promoters, but it reaches its maximal
+activity during late infection (after DNA replication). However, during
+early infection only a subset of the MLP-derived transcripts are
+expressed (10). MAdV makes an extensive use of alternative RNA splicing
+to produce a very complex array of mRNAs. All but the pIX mRNA undergo
+at least one splicing event. For instance, the MLTU produces over 20
+distinct splice variants all containing three non-coding exons at the
+5'-end (collectively known as the tripartite leader; TPL) (17, 18).
+There is also an alternate three-exon 5' non-coding leader sequence
+present in varying amounts on a subset of MLTU mRNAs (known as the x-,
+y-, and z-leaders). Lastly, there is the i-leader exon, which is
+infrequently included between the second and third TPL exons, and codes
+for the i-leader protein (20). Thus, the MLTU produces a complex
+repertoire of mRNA with diverse 5' untranslated regions (UTRs) spliced
+onto different 3' coding exons which are grouped into five different
+3'-end classes (L1-L5) based on polyadenylation site. Each transcription
+unit (TU) contains its own promoter driving the expression of the array
+of mRNA transcripts produced via alternative splicing in the unit (10,
+17, 18). The promoters are activated at different phases of the
+infection by proteins from previously activated TUs. Paradoxically, the
+early-to-late phase transition during infection requires the L4 gene
+products, 22K and 33K, which should only be available after the
+transition. However, a promoter in the L4 region (L4P) that directs the
+expression of these two proteins independent of the MLP was found,
+resolving the paradox (10, 17, 21). During translation of AdV mRNA,
+recent studies using long-read direct RNA sequencing strongly suggest
+the potential usage of secondary start codons; adding to what was
+already a highly complex system for gene expression (17, 22).
 
@@
 \textbf{Overview of sequencing data and analysis pipeline outputs}\\
-A previous study by Aboezz \emph{et al} showed that almost all THEV
-transcripts were detectable beginning at 4 hours, with a full
-replication cycle of about 18-hours post infection (hpi) (24).
-Therefore, infected MDTC-RP19 cells were harvested at 4-, 12-, 24-, and
-72-hpi to ensure a wide time window to sample all transcripts. Our
-paired-end RNA sequencing (RNA-seq) experiment yielded an average of
-107.1 million total reads of 149 bp in length per time-point, which were
-simultaneously mapped to both the virus (THEV) and host (\emph{Meleagris
-gallopavo}) genomes using the Hisat2 (25) reference-based aligner. A
-total of 18.1 million reads from all time-points mapped to the virus
-genome; this provided good coverage/depth, leaving no regions unmapped.
-The mapped reads to the virus genome increased substantially from a mere
-432 reads at 4 hpi to 16.9 million reads at 72 hpi (\textbf{Table 1},
-\textbf{Figure 2A}). From the mapped reads, we identified a total of
-2,457 unique THEV splice junctions from all time-points, with splice
-junctions from the later time-points being supported by significantly
-more sequence reads than earlier time-points. For example, all the 13
-unique junctions at 4 hpi had less than 10 reads supporting each one,
-averaging a mere 2.8 reads per junction. Conversely, the 2374 unique
-junctions at 72 hpi averaged 898.4 reads per junction, some junctions
-having coverage as high as 322,677 reads. The substantial increases in
-splice junction and mapping reads to the THEV genome over time denotes
-an active infection and a successful viral replication, and correlates
-with our quantitative PCR (qPCR) assay quantifying the total number of
-viral genome copies over time (\textbf{Figure 2B}).
-
-Using StringTie (25), we assembled the data into potential transcripts
-using the genomic location of the prior predicted THEV ORFs as a guide.
+A prior study by Aboezz \emph{et al}. demonstrated that nearly all THEV
+transcripts became detectable starting at 4 hours post-infection (hpi),
+with one replication cycle concluding around 18 hpi (24). Consequently,
+we harvested infected MDTC-RP19 cells (MOI of 100 genome copy
+numbers/cell) at 4-, 12-, 24-, and 72-hpi to capture all transcripts
+within a broad time window. Our paired-end RNA sequencing (RNA-seq)
+experiment generated an average of 107.1 million total reads of 149 bp
+length per time-point. These reads were concurrently mapped to both the
+virus (THEV) and host (\emph{Meleagris gallopavo}) genomes using the
+Hisat2 (25) reference-based aligner. A total of 18.1 million reads from
+all time-points mapped to the virus genome, providing comprehensive
+coverage and leaving no regions unmapped. The mapped reads to the virus
+genome increased significantly from a scant 432 reads at 4 hpi to 16.9
+million reads at 72 hpi (\textbf{Table 1}, \textbf{Figure 2A}). From
+these mapped reads, we identified 2,457 unique THEV splice junctions
+across all time-points, with later time-points exhibiting significantly
+more sequence reads supporting the splice junctions than earlier
+time-points. For instance, all 13 unique junctions at 4 hpi had fewer
+than 10 supporting reads each, averaging only 2.8 reads per junction. In
+contrast, the 2374 unique junctions at 72 hpi averaged 898.4 reads per
+junction, with some junctions reaching as high as 322,677 reads. The
+marked increase in splice junction and mapping reads to the THEV genome
+over time indicates an active infection and successful viral
+replication, which is corroborated by our quantitative PCR (qPCR) assay
+that quantified the total number of viral genome copies over time
+(\textbf{Figure 2B}).
+
+Using StringTie (25), we assembled the data into potential transcripts,
+guided by the genomic locations of the previously predicted THEV ORFs.
 In the consolidated transcriptome, a composite of all non-redundant
-transcripts from all time points, we counted a total of 29 novel
+transcripts across all time points, we identified a total of 29 novel
 transcripts. We found that a subset of exons in the viral transcripts
-match the predicted ORFs exactly, with the majority of the exons being
+match some predicted ORFs exactly, with the majority of the exons being
 longer and spanning multiple predicted ORFs (\textbf{Figure 3}).
@@
 \textbf{Changes in THEV splicing profile over time}\\
-AdV gene expression occurs under exquisite temporal control with each
-promoter typically producing one or few pre-mRNAs that undergo
-alternative splicing to yield a repertoire of mature mRNAs. To evaluate
-the activity of each promoter over time, StringTie and Ballgown (a
-program for statistical analysis of assembled transcriptomes) (26) were
-used to estimate the normalized expression levels of all transcripts for
-each time point in Fragments Per Kilobase of transcript per Million
-mapped reads (FPKM) units. Very few unique splice junctions, reads, and
-transcripts were counted at 4 hpi; hence, this time point was excluded
-in this analysis.
-
-Considering individual mRNAs, TRXPT\_21 -- from the E2 region -- was the
+AdV gene expression is subject to meticulous temporal regulation, with
+each promoter typically generating one or a few pre-mRNAs. These
+pre-mRNAs undergo alternative splicing to produce a diverse array of
+mature mRNAs. To assess the temporal activity of each promoter, we
+utilized StringTie and Ballgown (a tool for statistical analysis of
+assembled transcriptomes) (26). These tools estimated the normalized
+expression levels of all transcripts at each time point, measured in
+Fragments Per Kilobase of transcript per Million mapped reads (FPKM)
+units. At 4 hpi, we counted very few unique splice junctions, reads, and
+transcripts; hence, this time-point was excluded from this analysis.
+
+Examining individual mRNAs, TRXPT\_21 -- from the E2 region -- was the
 most significantly expressed at 12 hpi, constituting 33.58\% of the
 total expression of all transcripts. Transcripts in the E3 and E4
-regions also contributed significant proportions, and noticeably, some
-MLP region transcripts. The later time points were dominated by the MLP
-region transcripts -- TRXPT\_10 and TRXPT\_14 were the most abundantly
-expressed at 24 and 72 hpi, respectively, as expected (\textbf{Figure
-4A}). When we performed analysis of the FPKM values of transcripts per
-region we found a similar pattern: the E2 region was the most abundantly
-expressed at 12 hpi, after which the MLP region assumes predominance
-(\textbf{Figure 4B}). Secondly, we estimated relative abundances of all
-splice junctions at each time point using the raw reads. Only junctions
-with a read coverage of at least 1\% of the total splice junction reads
-at the given time point were considered significant and included in
-\textbf{Tables 2a-2c}. At 12 hpi, 18 junctions meet the 1\% threshold,
-and were comprised of predominantly early region (E1, E2, E3, and E4)
-junctions, albeit the MLTU was the single most preponderant region
-overall, constituting 38.8\% of all the junction reads (\textbf{Table
-2a} and \textbf{Supplementary Table S1a}). The most abundant junctions
-at 12 hpi remained the most significantly expressed at 24 hpi also.
-However, here, the MLP-derived junctions were unsurprisingly even more
-preponderant overall, accounting for 45.7\% of all the junction reads
-counted (\textbf{Table 2b} and \textbf{Supplementary Table S1b}). At 72
-hpi, the trend of increased activity of the MLP continued as expected;
-at this time, the MLP region junctions were not only the most abundant
-overall -- accounting for 67.3\% of all junction reads, -- but also
-contained the most significantly expressed individual junctions
-(\textbf{Table 2c}, \textbf{Supplementary Table S1c} and \textbf{Figure
-4C}). When we limited this analysis to only junctions in the final
-transcriptome, we observed the relative abundances of the junctions for
-each region over time to be similar to the pattern seen with all the
-junctions included (\textbf{Figure 4D}).
-
-We also analyzed splice donor and acceptor site nucleotide usage over
-time to investigate any peculiarities that THEV may show, generally or
-over the course of the infection. We found that most splice
-donor-acceptor sequences were unsurprisingly the canonical GU-AG
+regions also contributed substantial proportions, along with some MLP
+region transcripts. The later time points were dominated by the MLP
+region transcripts --- TRXPT\_10 and TRXPT\_14 were the most abundantly
+expressed at 24 and 72 hpi, respectively (\textbf{Figure 4A}). Our
+analysis of the FPKM values of transcripts per region/TU revealed a
+similar pattern: the E2 region was the most abundantly expressed at 12
+hpi, after which the MLP region assumed dominance (\textbf{Figure 4B}).
+
+Next, we estimated the relative abundances of all splice junctions at
+each time point using the raw reads. Only junctions with a read coverage
+of at least 1\% of the total splice junction reads at the given time
+point were considered significant and included in \textbf{Tables 2a-2c}.
+At 12 hpi, 18 junctions met the 1\% threshold, predominantly from early
+regions (E1, E2, E3, and E4), although the MLTU was the single most
+predominant region overall, constituting 38.8\% of all the junction
+reads (\textbf{Table 2a} and \textbf{Supplementary Table S1a}). The most
+abundant junctions at 12 hpi remained the most significantly expressed
+at 24 hpi. However, here, the MLP-derived junctions unsurprisingly
+became even more predominant overall, accounting for 45.7\% of all the
+junction reads counted (\textbf{Table 2b} and \textbf{Supplementary
+Table S1b}). At 72 hpi, the trend of increased activity of the MLP
+continued as expected; at this time, the MLP region junctions were not
+only the most abundant overall --- accounting for 67.3\% of all junction
+reads, -\/-- but also contained the most significantly expressed
+individual junctions (\textbf{Table 2c}, \textbf{Supplementary Table
+S1c} and \textbf{Figure 4C}). When we limited this analysis to only
+junctions in the final transcriptome, we observed the relative
+abundances of the junctions for each region over time to be similar to
+the pattern seen with all the junctions included (\textbf{Figure 4D}).
+
+Finally, we analyzed splice donor and acceptor site nucleotide usage
+over time to investigate any peculiarities that THEV may exhibit,
+generally or over the course of the infection. We found that most splice
+donor-acceptor sequences were, unsurprisingly, the canonical GU-AG
 nucleotides. However, the splice acceptor-donor pairing became less
@@
 \textbf{Early Region 1 (E1) transcripts}\\
-This region in MAdVs is the first transcribed after successful entry of
-the viral DNA into the host cell nucleus, albeit at low levels (18). The
-host transcription machinery solely mediates the transcription of this
-region. After their translation, the E1 proteins in concert with a
-myriad of host transcription factors activate other viral promoters
-(10). In MAdVs, this region is subdivided into E1a and E2b units, but
-the transcripts found in our data categorized under this region do not
-appear to be subdivided.
-
-Only two ORFs (ORF1 {[}sialidase{]} and Hyd) are predicted in this
-region; however, we discovered four novel transcripts in this region,
-which collectively contain 3 unique splice junctions (\textbf{Figure
-6}). Most of the ORFs of the novel transcripts are distinct from the
-predicted ORFs, but they all have the coding potential (CP) for the
-predicted Hyd protein as the 3'-most coding sequence (CDS) if secondary
-start codon usage is considered as reported for other AdVs (17, 18). The
-5'-most CDS of TRXPT\_1 is multi-exonic, encoding a novel 17.9
-kilodalton (kDa), 160 residue {[}amino acids (aa){]} protein (ORF9).
-From its 5'-most start codon (SC), TRXPT\_2 encodes the largest protein
-in this region -- a 64.3 kDa, 580 aa protein (ORF10) with the same SC as
-ORF9 (position 211 bp). ORF10 spans almost the entire predicted ORF1 and
-Hyd, coming short in two regards: it is spliced from 1655 bp to 1964 bp
-(ORF1's C-terminus, including the stop codon), and its stop codon (STC;
-position 2312) is 13 bp short of the Hyd STC. However, it has an SC 102
-bp upstream and in-frame with ORF1's predicted SC. Thus, ORF10 shares
-substantial protein sequence similarity with ORF1 but not with Hyd, as
-the SC of Hyd is not in-frame. Without its splice site removing the ORF1
-STC, TRXPT\_2 would encode a longer variant of ORF1, starting from an
-upstream SC. TRXPT\_3 is almost identical to TRXPT\_1, except for the
-lack of TRXPT\_1's second exon. Our RNA-seq data show that all E1
-transcripts share the same transcription termination site (TTS; at
-position 2325 bp). However, TRXPT\_3 and TRXPT\_4 seem to have
-transcription start sites (TSS) downstream of the TSS of TRXPT\_1 and
-TRXPT\_2 (E1 TSS; position: 54 bp). Given that studies in MAdVs show
-that E1 mRNAs share not only a common TTS but also the TSS, and only
-differ from each other regarding the internal splicing (18), it is
-likely that TRXPT\_3 and TRXPT\_4 are incomplete, and their actual TSS
-just like the TTS are identical for all E1 transcripts. Regardless of
-the TSS considered for TRXPT\_3, the CP remains unaffected. Its 5'-most
-CDS, beginning at 1965 bp and sharing the same STC as ORF9, produces a
-13.1 kDa, 115 residue protein (ORF4). ORF4 was predicted in an earlier
-study (27) but was excluded in later studies (1, 12); however, our data
-suggest it is a genuinely expressed ORF. Unlike TRXPT\_3, the CP of
-TRXPT\_4 is affected by the TSS considered; if we consider its
-unmodified TSS, then its CP is identical to TRXPT\_3. However, if we
-assume that TRXPT\_4 uses the E1 TSS, then the 5'-most CDS is a
-distinct, novel, multi-exonic 15.9 kDa, 143 aa protein (ORF11) with the
-same SC as ORF9 and ORF10 but with a unique STC.
-
-The splice junctions of all transcripts in this region (except the
-junction for TRXPT\_4) were validated by cloning of viral cDNA and
-Sanger sequencing (\textbf{Supplementary PCR methods}). During the
-validation of TRXPT\_2, we found ORF1 to be present on the agarose gel
-(an unspliced band size) and Sanger sequencing results showed it to be a
-transcribed mRNA (\textbf{Supplementary PCR methods}). This was
-corroborated by our 3' RACE experiment, which showed a transcript
-(TRXPT\_2B) spanning the entire ORF1 and Hyd ORFs without any splicing,
-with a poly-A tail immediately after the E1 TTS. The 5'-most CDS of this
-transcript (TRXPT\_2B) would encode ORF1. However, TRXPT\_2B has an
-upstream and in-frame SC to the predicted SC of ORF1, suggesting that
-the predicted ORF1 CDS is truncated -- the actual ORF1 (eORF1) that is
-expressed shares the same SC as ORF10, but has a unique STC.
+In MAdVs, E1 is the first region transcribed post-viral DNA entry into
+the host cell nucleus, mediated solely by host transcription machinery
+(18). Translated E1 proteins subsequently activate other viral promoters
+in conjunction with host transcription factors (10). Despite subdivision
+into E1a and E1b units in MAdVs, our THEV data does not reflect this.
+This region is predicted to encode only two ORFs: ORF1 (sialidase) and
+Hyd (a hydrophobic product with unknown function) in THEV.
+
+We identified four novel transcripts in this region, containing 3 unique
+splice junctions (\textbf{Figure 6}), and encoding four distinct novel
+ORFs in addition to Hyd. All transcripts have coding potential (CP) for
+the Hyd protein as the 3'-most coding sequence if secondary start codon
+usage is considered (17, 18). Also, all the transcripts have a common
+transcription termination site (TTS; at position 2325 bp), but TRXPT\_1
+and TRXPT\_2 have an upstream transcription start sites (TSS) to
+TRXPT\_3 and TRXPT\_4. Given that E1 mRNAs in MAdVs share a common TTS
+and TSS, differing only in the internal splicing (18), we consider the
+upstream TSS (position 54 bp) as the actual TSS for all E1 region
+transcripts. We also identified the canonical polyadenylation signal
+(PAS; AAUAAA) in the immediate context of the TTS at position 2323 bp
+(location of the ``U'' in the PAS sequence); see \textbf{Supplementary
+Table S2}.
+
+From the 5'-most start codon (SC), TRXPT\_1 encodes a multi-exonic novel
+17.9 kDa, 160 residue protein (ORF9). TRXPT\_2 encodes a two-exon 66.4
+kDa, 597 residue novel protein (ORF10), spanning almost the entire
+predicted ORF1 and Hyd. The intron of TRXPT\_2 excludes the C-terminus
+of ORF1 (including its stop codon) from ORF10 but the SC of ORF10 is 102
+bp upstream and in-frame with the predicted SC of ORF1. TRXPT\_3,
+similar to TRXPT\_1 but lacking the second exon, encodes a 13.1 kDa, 115
+residue protein (ORF4), previously predicted (27) but excluded in later
+annotations (1, 12). Our data suggest it is genuinely expressed. Lastly,
+TRXPT\_4 encodes a distinct novel 15.9 kDa, 143 residue protein (ORF11).
+
+The splice junctions of all transcripts in this region, except for
+TRXPT\_4, were validated by cloning of viral cDNA and Sanger sequencing
+(see \textbf{Supplementary PCR methods}). During TRXPT\_2 validation,
+ORF1 was found on the agarose gel (an unspliced band size) and Sanger
+sequencing results showed it to be a transcribed mRNA
+(\textbf{Supplementary PCR methods}). This was corroborated by our 3'
+RACE experiment, which showed a transcript (TRXPT\_2B) spanning the
+entire ORF1 and Hyd ORFs without splicing, with a poly-A tail
+immediately after the E1 TTS. The 5'-most coding sequence (CDS) of this
+transcript (TRXPT\_2B) encodes ORF1. However, TRXPT\_2B has an upstream
+and in-frame SC to the predicted SC of ORF1, suggesting that the
+predicted ORF1 CDS is truncated -- the expressed ORF1 (eORF1) shares the
+same SC as ORF10, but has a unique stop codon (STC). See
+\textbf{Supplementary Table S3} for all transcripts and their encoded
+proteins.
 
 \textbf{Early Region 2 (E2) and Intermediate Region (IM) transcripts}\\
-The E2 TU expressed on the anti-sense strand is subdivided into E2A and
+The E2 TU expressed on the anti-sense strand, is subdivided into E2A and
 E2B and encodes three classical AdV proteins -- pTP and Ad-pol (E2B
 proteins), and DBP (E2A protein) -- essential for genome replication
-(17, 18). Unlike MAdV where two promoters (E2-early and E2-late) are
-known (17), we discovered only a single TSS (E2 TSS; 18,751 bp) from
-which both E2A and E2B transcription is initiated. However, similar to
-MAdVs, E2A and E2B transcripts have distinct TTSs, and the E2B
-transcripts share the TTS of the IVa2 transcript of the IM region (17,
-18) (\textbf{Figure 7}).
-
-The E2A ORF, DBP is one of three THEV ORFs predicted to be spliced from
-two exons. The corresponding transcript (TRXPT\_21) found in our data
-matches this predicted splice junction precisely but with a non-coding
-additional exon at the 5'-end (E2-5'UTR) at position 18,684-18,751 bp.
-Thus, TRXPT\_21 is a three-exon transcript encoding DBP (380 residues,
-43.3 kDa) precisely as predicted. This transcript (TRXPT\_21) was also
+(17, 18). Unlike MAdV where two promoters are known (17), we discovered
+only a single TSS (E2 TSS; 18,751 bp) for both E2A and E2B transcripts
+in THEV. However, similar to MAdVs, E2A and E2B transcripts have
+distinct TTSs, with E2B transcripts sharing the TTS of the IVa2
+transcript of the IM region (17, 18) (\textbf{Figure 7}).
+
+The E2A ORF, DBP, is one of three THEV ORFs predicted to be spliced from
+two exons. The corresponding transcript (TRXPT\_21) in our data matches
+the predicted splice junction but includes an additional non-coding exon
+at the 5'-end (E2-5'UTR). Thus, TRXPT\_21 is a three-exon transcript
+encoding DBP (380 residues, 43.3 kDa) precisely. TRXPT\_21 was also
 corroborated in a 3' RACE experiment. Additionally, from the 3' RACE
 data, we found a splice variant of TRXPT\_21 which retains the second
-intron leading to a 2-exon transcript. This new transcript (TRXPT\_21B),
-albeit longer due to retaining the second intron and possessing a short
-3' UTR, encodes a truncated isoform of DBP (tDBP) because the SC
-utilized by TRXPT\_21, is followed shortly by STCs in the retained
-intron. The SC 173 bp downstream of the DBP SC yields tDBP (a 346
-residue, 39.3 kDa product), which is in-frame of DBP but entirely
-contained in the second exon. TRXPT\_21 and TRXPT\_21B share a common
-TTS but TRXPT\_21B as seen in our 3'-RACE data, extends 39 bp into an
-adenine/thymine (A/T)-rich sequence before the poly-A tail sequence
-occurs, suggesting this position (16,934 bp) as the true E2A TTS
-(\textbf{Figure 7}).
+intron, leading to a 2-exon transcript (TRXPT\_21B). Although longer,
+TRXPT\_21B encodes a truncated isoform of DBP (tDBP; a 346 residue, 39.3
+kDa product) using a downstream in-frame SC but the same STC as DBP.
+Both TRXPT\_21 and TRXPT\_21B share a common TTS, seen in our 3' RACE
+data, located 39 bp downstream of the CDS in an adenine/thymine
+(A/T)-rich sequence followed by the poly-A tail sequence, suggesting
+this position (16,934 bp) as the true E2A TTS. There are two canonical
+PASs (AAUAAA; 16,964 and 16950 bp) immediately after the CDS any of
+which can serve as the PAS without affecting the encoded proteins
+(\textbf{Supplementary Table S2}).
 
 The E2B region transcripts also start with the E2-5'UTR but extend
-thousands of base pairs downstream to reach the TTS at 2334 bp in the IM
-region, which is immediately followed by an A/T-rich sequence (position
-2323-2339 bp) where polyadenylation probably occurs. Interestingly, the
-TTS of the E1 region (position 2,325 bp) on the sense strand is also in
-the immediate vicinity of this A/T-rich sequence, which is almost
-palindromic; hence it likely serves as the polyadenylation signal for
-both E1 and E2B/IM transcripts. The E2B transcripts TRXPT\_6 and
-TRXPT\_7 are almost identical except for an extra splice junction at the
-3'-end of TRXPT\_6, making TRXPT\_6 a five-exon transcript and TRXPT\_7,
-four exons (\textbf{Figure 7}). TRXPT\_7 has the CP for both classical
-proteins (pTP and Ad-pol) encoded in this region, of which the pTP ORF
-is predicted to be spliced from two exons just like in all other AdVs.
-The predicted splice junction of pTP is corroborated by our data;
-however, the full transcript is markedly longer than the predicted ORF:
-there are two novel non-coding 5' exons, the third exon (containing the
-SC of pTP) is significantly longer than predicted, and the last exon
-containing the bulk of the CDS is more than triple the predicted size of
-pTP. The first two exons are 5'-UTRs because the SC here is immediately
-followed by STCs; thus, the 5'-most SC (position 10,995 bp) of the third
-exon which matches the predicted SC of pTP is utilized. The encoded
-product is identical to the predicted pTP protein (597 residues; 70.5
-kDa). If secondary SC (secSC) usage is considered, with SC at 6768 bp
-and STC at 3430 bp, the encoded product is identical to the predicted
-Ad-pol (polymerase) protein (1112 residues; 129.2 kDa). TRXPT\_6 differs
-from TRXPT\_7 by containing an extra splice site at 3447-3515 bp.
-However, the CP remains similar to that of TRXPT\_7 except the Ad-pol
-encoded from the secSC is a truncated isoform with a new STC resulting
-from the splice site.
+downstream to reach the TTS at 2334 bp in the IM region, which is in the
+immediate context of a canonical PAS (position 2333 bp) where
+polyadenylation likely occurs. The E2B transcripts, TRXPT\_6 and
+TRXPT\_7, are almost identical except for an extra splice junction at
+the 3'-end of TRXPT\_6 (\textbf{Figure 7}). TRXPT\_7 has the CP for both
+classical proteins (pTP and Ad-pol) encoded in this region, with the pTP
+ORF predicted to be spliced from two exons. The predicted splice
+junction of pTP is corroborated by our data but the full transcript is
+markedly longer than the predicted ORF, although, the encoded product
+(pTP) remains unchanged. Ad-pol (polymerase) is encoded downstream of
+pTP with secondary SC (secSC) usage. The CP of TRXPT\_6 slightly differs
+from TRXPT\_7 because a new STC resulting from the extra splice site
+forms a minimal truncation of the Ad-pol encoded from its secSC.
 
@@
 encoded by separate mRNAs with identical first three 5' exons and TTS,
-but the splice junction to the terminal exons are different. We checked
-for a longer splice junction between the third and fourth (terminal)
-exons of TRXPT\_7 with our junction validation method (targeted PCR,
-cloning, and Sanger sequencing) and discovered a unique splice junction
-(10,981-7062 bp) not found in our RNA-seq data. If initiated from the E2
-TSS and terminated at the E2 TTS, this transcript (TRXPT\_31) would
-encode Ad-pol exactly as predicted as its 5'-most CDS (\textbf{Figure
-7}).
+but different splice junctions to the terminal coding exons. Hence, we
+checked for a longer splice junction between the third and fourth
+(terminal) exons of TRXPT\_7 with our junction validation method
+(targeted PCR, cloning, and Sanger sequencing). We discovered a unique
+splice junction (10,981-7062 bp) not present in our RNA-seq data. If
+initiated from the E2 TSS and terminated at the E2B TTS, this transcript
+(TRXPT\_31) would encode Ad-pol in its 5'-most CDS (\textbf{Figure 7}).
 
@@
 protein, IVa2. The promoter expressing this single transcript (TRXPT\_5)
-is embedded in E2B region and shares a TTS with E2B transcripts (17,
-18). TRXPT\_5 is a two-exon transcript spliced exactly as the last
-splice junction of TRXPT\_6. The first exon is a UTR, except the last 2
-nucleotides, which connect with the first nucleotide of the second exon
-to form the 5'-most SC. This first SC is 4 codons upstream and in-frame
-of the predicted IVa2 SC. Except for the four extra N-terminus residues,
-the entire protein sequence is identical to the predicted IVa2.
-
-\textbf{Early Region 3 (E3) transcripts}.\\
-The E3 region is wholly contained in the MLTU and encodes proteins
-involved in modulating and evading the host immune defenses. In MAdVs,
-this region contains seven ORFs expressed from several transcripts which
-share the same TSS (from the E3 promoter) but have different TTSs (10,
-17, 18). However, some E3 transcripts use the TSS of the MLP. Due to
-sharing the same TSS, in MAdVs, secSC usage is heavily relied on for
-gene expression in this region except for 12.5K and transcripts using
-the MLP TSS, as utilizing only the first SC cannot produce all the other
-transcripts in this TU (17).
+is embedded in the E2B region and shares a TTS with E2B transcripts (17,
+18). TRXPT\_5 is a two-exon transcript with a non-coding first exon,
+except the last 2 nucleotides, which connect with the first nucleotide
+of the second exon to form the 5'-most SC. This new SC is four codons
+upstream and in-frame of the predicted IVa2 SC. Beside the four
+additional N-terminus residues, the protein sequence is unchanged.
+
+\textbf{Early Region 3 (E3) transcripts}\\
+The E3 region, nested within the MLTU, encodes proteins that modulate
+and evade host immune defenses. In MAdVs, this region contains seven
+ORFs expressed from multiple transcripts sharing the same TSS (from the
+E3 promoter) but having different TTSs (10, 17, 18). However, some E3
+transcripts use the TSS of the MLP. Due to sharing the same TSS, in
+MAdVs, secSC usage is heavily relied on for gene expression in this
+region as utilizing only the first SC cannot produce the downstream
+transcripts in this TU. The 12.5K ORF and transcripts using the MLP TSS
+are exceptions (17).
 
 In THEV, only one ORF (E3) was predicted in this region. However, as the
-E3 TU is nested in the MLTU, transcripts from the L4P (100K, 22K, 33K,
-and pVIII) not only overlap the E3 region transcripts entirely as seen
-in our RNA-seq results, but also have their TSS and TTS in practically
-the same locations (\textbf{Figure 8}). Therefore, we have categorized
-these two groups together as E3 transcripts.
-
-We identified seven novel transcripts here (TRXPT\_22, TRXPT\_23,
-TRXPT\_24, TRXPT\_25, TRXPT\_26, TRXPT\_27, TRXPT\_29) from our RNA-seq
-data, all originating from two distinct TSSs -- we consider the first
-TSS (position 18,230 bp) as corresponding to the L4P and the other at
-18,727 bp as corresponding to the E3 promoter (E3P). These E3
-transcripts collectively have the CP for several predicted THEV ORFs:
-100K, 22K, 33K, pVIII, and E3, as well as Fiber (IV) and ORF7 belonging
-to the MLTU. But some of these CDSs are different than predicted due to
-either unknown exons or the presence of an in-frame upstream SC. For
-instance, 33K is one of the few THEV ORFs predicted to be spliced from
-two exons; however, we discovered a significantly longer four-exon ORF
-(e33K) on TRXPT\_24 that contains it almost entirely. The first two
-exons of e33K were not predicted but the last two match the predicted
-exons and the CDS is in-frame, albeit the first 20 bp of the predicted
-33K (including the SC at 20,142 bp) is spliced out as part of the second
-intron of TRXPT\_24. Thus, the bona fide 33K (e33K) is a 19.8 kDa, 171
-residue protein spanning four exons instead of the predicted 120 aa
-protein. TRXPT\_24 also has the CP for pVIII and E3 if we consider
-downstream SC usage. However, the predicted E3 has an upstream in-frame
-SC; thus, this longer version of E3 (eE3) is likely the genuinely
-expressed ORF. TRXPT\_29 is the shortest transcript in this TU. It is a
-two-exon transcript, both exons comprising the CDS. The product of
-TRXPT\_29 is a novel 73 residue protein (8.3KI) sharing the SC of e33K
-but with a unique STC. TRXPT\_23 being spliced identically as TRXPT\_29
-also encodes 8.3KI from its first SC. Similarly, TRXPT\_22 also encodes
-a 73 aa novel protein (8.3KII) from its first SC that shares over 80\%
-similarity with 8.3KI, but it differs from 8.3KI at the C-terminus.
-Considering downstream SC usage, both TRXPT\_22 and TRXPT\_23 can encode
-pVIII and eE3 in that order, but TRXPT\_23 being longer, has the CP for
-the Fiber ORF also.
+E3 TU is nested in the MLTU, transcripts from the L4 promoter (100K,
+22K, 33K, and pVIII) overlap the E3 region transcripts entirely and
+share similar TSS and TTS locations (\textbf{Figure 8}). Therefore, we
+have categorized these two groups together as E3 transcripts.
+
+We identified seven novel transcripts (TRXPT\_22, TRXPT\_23, TRXPT\_24,
+TRXPT\_25, TRXPT\_26, TRXPT\_27, TRXPT\_29) from our RNA-seq data, all
+originating from two distinct TSSs. We consider the first TSS (position
+18,230 bp) as corresponding to the L4 promoter (L4P) and the other at
+18,727 bp as corresponding to the E3 promoter (E3P). We also identified
+the canonical or other known PASs (28) near the TTS of the transcripts
+(see \textbf{Supplementary Table S2}). These E3 transcripts collectively
+have the CP for several predicted THEV ORFs: 100K, 22K, 33K, pVIII, and
+E3, as well as Fiber (IV) and ORF7 of the MLTU (see
+\textbf{Supplementary Table S3}). However, some of these CDSs differ
+from the predictions due to either unknown exons or the presence of an
+in-frame upstream SC. For instance, we discovered that 33K, predicted to
+be spliced from two exons, is actually a significantly longer four-exon
+ORF (e33K; 19.8 kDa, 171 residues) encoded on TRXPT\_24. Its first two
+exons were unknown but the last two match the predicted exons and the
+CDS is in-frame, albeit the first 20 bp of the predicted 33K (including
+the SC) is spliced out as part of the second intron of TRXPT\_24.
+TRXPT\_24 also has the CP for pVIII and E3 if we consider downstream SC
+usage. However, we found an upstream in-frame SC for the predicted E3;
+thus, this longer version of E3 (eE3) is likely the genuinely expressed
+ORF. TRXPT\_29, the shortest transcript in this TU, encodes a novel 73
+residue protein (8.3KI) across its two exons using the SC of e33K with a
+unique STC. TRXPT\_23, spliced identically as TRXPT\_29, also encodes
+8.3KI from its first SC. Similarly, TRXPT\_22 encodes a 73 residue novel
+protein (8.3KII) from its first SC that shares over 80\% similarity with
+8.3KI, but they differ at the C-terminus. Considering downstream SC
+usage, both TRXPT\_22 and TRXPT\_23 can encode pVIII and eE3 in that
+order, but TRXPT\_23 being longer, also has the CP for the Fiber ORF.
 
 As the splice junctions of TRXPT\_22, TRXPT\_23, TRXPT\_24, and
-TRXPT\_29 essentially share the same genomic space, their validation was
-done with a single primer pair, and they were differentiated from each
-other by cloning and Sanger sequencing (\textbf{Supplementary PCR
+TRXPT\_29 share the same genomic space, their validation was done with a
+single primer pair, and they were differentiated from each other by
+cloning the cDNA and Sanger sequencing (\textbf{Supplementary PCR
 methods}). In addition to corroborating the splice junctions for the
-aforementioned transcripts, the Sanger sequencing results also showed
-another splice variant undetected in our RNA-seq transcriptome. This was
-a three-exon transcript (TRXPT\_30) with its first and last exons
-spliced identically as TRXPT\_23, but which also has the second exon of
-TRXPT\_24 (\textbf{Figure 8}). The first CDS on TRXPT\_30 spans all
-three exons, producing a novel 140 residue, 15.7kDa protein.
-Interestingly, the last 81 C-terminus residues of this new protein
-(e22K) are identical to 22K (89 residues), which is a single-exon ORF
-predicted to use the same SC as 33K (20,142 bp). Just as seen for 33K,
-all the transcripts in this region exclude the first 20 bp of 22K
-(including the SC) as part of their introns; therefore, the first 7
-residues of 22K are lacking in e22K due to splicing. Hence, we consider
-e22K as a long variant of the predicted 22K ORF. Albeit the TSS and TTS
-of TRXPT\_30 was not seen, we presume that they are similar to
-TRXPT\_23, in which case it would also have the downstream CP of
-TRXPT\_23.
-
-TRXPT\_25 is the largest transcript in the TU. It also utilizes the L4P
-TSS but has a distinct TTS. It is a two-exon transcript, encoding a
-novel protein (t100K; 543 residues), which is a shorter isoform of the
-predicted 100K ORF. Considering secSC usage on this transcript yields
-the predicted 22K ORF precisely as predicted. It also has the CP for
-pVIII and eE3 in that order. Furthermore, during the validation of the
-TRXPT\_25 splice junction using primers that span its junction
-(18,350-18,717 bp), we noticed a DNA band that corresponds to the full
-unspliced sequence (\textbf{Supplementary PCR methods}). As TRXPT\_25
-only falls short of encoding the complete predicted 100K protein due to
-its splice junction, this band (which we cloned and validated by Sanger
-sequencing) suggests that the predicted 100K is indeed expressed. This
-transcript (TRXPT\_25B) although not seen in full, likely shares the
-same TSS and TTS as TRXPT\_25. Lastly, TRXPT\_26 and TRXPT\_27 both
-originate from the E3P but have distinct TTSs. TRXPT\_26 is a three-exon
-transcript but the first two are UTRs. It encodes pVIII as the 5'-most
-ORF and has the CP for eE3 and Fiber in that order. TRXPT\_27 on the
-other hand, is only a two-exon transcript that is similar to TRXPT\_26,
-only the terminal exon contains the CDSs. It encodes Fiber as the
-5'-most ORF, and ORF7 downstream with secSC usage. TRXPT\_13, which is
-an L4 transcript that uses the MLP TSS is discussed under the MLTU
-transcripts.
-
-\textbf{Early Region 4 (E4) transcripts}\\
-This TU is found at the tail-end (3'-end) of the genome and expressed
-from the anti-sense strand. Based on nucleotide position, ORF7 and ORF8
-were predicted in this region (1); however, as ORF7 is neither on the
-same strand as ORF8 nor transcribed from a promoter in the E4 region,
-only ORF8 can legitimately be classified as a transcript in this TU.
-This is corroborated by our RNA-seq data, as only one transcript was
-identified in this region on the anti-sense strand (\textbf{Figure 9}).
+aforementioned transcripts, the Sanger sequencing results also showed a
+distinct splice variant undetected in our RNA-seq transcriptome. This
+was a three-exon transcript (TRXPT\_30) with identical first and last
+exons as TRXPT\_23, but also contained the second exon of TRXPT\_24
+(\textbf{Figure 8}). TRXPT\_30 encodes a novel 140 residue, 15.7kDa
+protein (e22K), spanning all three exons. Interestingly, the last 81
+C-terminus residues of e22K are identical to 22K (89 residues), a
+single-exon ORF predicted to use the same SC as 33K. Just as seen for
+33K, the first 20 bp of 22K is intronic, excluding the first 7 residues
+of 22K from e22K. We consider e22K as a long variant of the predicted
+22K ORF. Assuming TRXPT\_30 shares the same TSS and TTS as TRXPT\_23, it
+would also have the downstream CP of TRXPT\_23.
+
+TRXPT\_25, the largest transcript in the TU, is a two-exon transcript,
+encoding a novel protein (t100K; 543 residues), which is a shorter
+isoform of the predicted 100K ORF. secSC usage on this transcript yields
+the predicted 22K ORF. It also has the CP for pVIII and eE3 downstream.
+Furthermore, during the validation of the TRXPT\_25 splice junction
+using primers that span its junction (18,350-18,717 bp), we noticed a
+DNA band corresponding to the full unspliced sequence
+(\textbf{Supplementary PCR methods}). As TRXPT\_25 only falls short of
+encoding the complete predicted 100K protein due to its splice junction,
+this band (which we cloned and validated by Sanger sequencing) suggests
+that the predicted 100K is indeed expressed. We assume that this
+transcript (TRXPT\_25B) shares the same TSS and TTS as TRXPT\_25.
+
+Lastly, TRXPT\_26 and TRXPT\_27, both originate from the E3P but have
+distinct TTSs. TRXPT\_26 encodes pVIII as the 5'-most ORF and has the CP
+for eE3 and Fiber in that order. TRXPT\_27, a two-exon transcript,
+encodes Fiber as the 5'-most ORF, and ORF7 downstream with secSC usage.
+TRXPT\_13 is an L4P transcript that uses the MLP TSS; it is discussed
+under the MLTU transcripts.
+
+\textbf{Early Region 4 (E4) transcripts} This TU is found at the 3'-end
+of the genome and expressed on the anti-sense strand. Based on
+nucleotide position, ORF7 and ORF8 were predicted in this region (1);
+however, as ORF7 is neither on the anti-sense strand nor transcribed
+from a promoter in the E4 region; hence, we only classify ORF8 in this
+TU. This is corroborated by our RNA-seq data, showing only one
+transcript in this region on the anti-sense strand (\textbf{Figure 9}).
 The transcript (TRXPT\_28) spans 25192-26247 bp and is spliced at
-25701-26055 bp, making a two-exon transcript. The second exon fully
+25701-26055 bp, forming a two-exon transcript. The second exon fully
 matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
-However, there is an SC in the first exon at position 26246 bp (192 bp
-upstream of the predicted SC). The encoded protein from this SC is
-in-frame with the predicted SC found in the second exon; hence, we
-consider this protein (eORF8 -- 26.4 kDa, 229 aa), a longer isoform of
-the predicted ORF8, as the genuinely expressed ORF with an identical
-C-terminus to the predicted ORF8 protein.
+However, we identified a SC 192 bp upstream of the predicted SC in the
+first exon from which an in-frame protein is encoded. We consider this
+longer isoform (eORF8 -- 26.4 kDa, 229 residues) as the genuinely
+expressed ORF. We also identified a canonical PAS 11 bp upstream of TTS
+(\textbf{Supplementary Table S2}).
 
@@
 transcripts}\\
-The MLTU transcripts dominate the late phase (i.e, after DNA
-replication) of the AdV infectious cycle. The MLP produces all late
-mRNAs by alternative splicing and alternative polyadenylation of a
-primary transcript, grouped into five transcript classes (L1-L5). Most
-of the coding capacity of THEV falls within this TU. Specifically, about
-13 out of the 23 predicted ORFs were assigned to this TU, some of which
-we have categorized under the E3 TU instead. Our RNA-seq data revealed
-12 transcripts (TRXPT\_8, TRXPT\_9, TRXPT\_10, TRXPT\_11, TRXPT\_12,
-TRXPT\_13, TRXPT\_14, TRXPT\_16, TRXPT\_17, TRXPT\_18, TRXPT\_19,
-TRXPT\_20) in this TU, the majority of which have the 5' untranslated
-TPL sequence as seen in all AdVs. For three transcripts (TRXPT\_16,
-TRXPT\_17, TRXPT\_18), a different leader sequence (sTPL) is used, which
-differs from the TPL in only one regard: the first TPL exon is
-substituted for a different first exon, found between the first and
-second TPL exons. Also, TRXPT\_20 seems to include only the third TPL
-exon (\textbf{Figure 10}).
-
-We identified five TTSs (10,549 bp, 12,709 bp, 16,870 bp, 17,891 bp,
-20,865 bp) in this TU, which we consider as corresponding to the five
-late mRNA classes (L1-L5), respectively, as found in all AdVs. L1 mRNAs
-include TRXPT\_8, which comprises the TPL (non-coding) and the
-CDS-containing terminal exon. This transcript encodes the 52K ORF
-exactly as predicted with the SC beginning from the first nucleotide of
-the terminal exon. L2 mRNAs include TRXPT\_16, TRXPT\_17, and TRXPT\_18,
-all of which consist of the sTPL (also non-coding) followed by their
-respective terminal exons. TRXPT\_16 encodes pIIIa exactly as predicted
-as the 5'-most ORF, and also has the CP for the ORFs, III and pVII in
-that order. TRXPT\_17 encodes the ORF, III (penton), and TRXPT\_18
-encodes the ORF pVII exactly as predicted. The L3 mRNAs include
-TRXPT\_14 and TRXPT\_20, of which TRXPT\_14 utilizes the full TPL
-whereas TRXPT\_20 uses only the third TPL exon (TPL3). Both transcripts
-have the CP for the ORF, hexon (II) but hexon is the only ORF encoded on
-TRXPT\_14, whereas the 5'-most ORF on TRXPT\_20 is pX (pre-Mu) followed
-by pVI and hexon in that order. L4 mRNAs include TRXPT\_9, TRXPT\_10,
-TRXPT\_11, and TRXPT\_13 all of which begin with the TPL followed by
-three (TRXPT\_9, TRXPT\_10, and TRXPT\_13) or four (TRXPT\_11) coding
-exons. These are the largest transcripts found in the transcriptome,
-each one possessing the CP for several similar late proteins. Normally,
-MLTU transcripts encoding particular ORFs splice the TPL onto a splice
-site just upstream of the ORF to be expressed (17). While this holds
-true for most MLTU ORFs, several late ORFs (pVI, protease, and ORF7) do
-not have such close proximity splicing but are contained in larger
-transcripts such as these L4 mRNAs, strongly suggesting the use of
-non-standard ribosomal initiation mechanisms such as secSC utility and
-ribosome shunting found in other AdVs for their translation (17, 28).
-TRXPT\_9 and TRXPT\_10 are very similar but not identical. The last exon
-of TRXPT\_9 seems to be truncated and probably shares the same TTS as
-the other L4 mRNAs. They are both 6-exon transcripts encoding pVII as
-the 5'-most ORF (fourth exon) and also have the CP for pX, pVI, hexon, a
-longer variant of protease (eProt) -- uses an upstream in-frame SC than
-predicted, and ORF12 (a novel unpredicted 120 aa protein). TRXTP\_10
-(and TRXPT\_9 with the L4 TTS) additionally has the CP for pVIII and
-eE3. Conversely, TRXPT\_11 is a seven-exon mRNA with hexon as its
-5'-most ORF but it also has the CP for eProt, ORF12, e33K, and also
-pVIII and eE3 in that order. TRXPT\_13 seems to be an E3 ORF utilizing
-the MLP TSS as it encodes classical L4P genes such as pVIII and eE3 in
-that order similar to TRXPT\_22 (E3 TU) but it lacks the novel first ORF
-(8.3KII) of TRXPT\_22.
-
-Lastly, the L5 class includes only TRXPT\_12 which contains the TPL and
-a coding terminal exon. Its 5'-most ORF is fiber (IV) but it also has
-the CP for the THEV specific gene, ORF7. TRXPT\_12's CP is identical to
-TRXPT\_27 of the E3 TU but they differ in their 5'-UTRs. \newpage
+The MLTU transcripts, dominant in the late phase of the AdV infectious
+cycle, are produced by alternative polyadenylation and splicing of a
+primary transcript and grouped into five transcript classes (L1-L5).
+About 13 out of the 23 predicted ORFs in THEV fall within this TU, some
+of which we have categorized under the E3 TU instead. Our RNA-seq data
+revealed 12 transcripts (TRXPT\_8, TRXPT\_9, TRXPT\_10, TRXPT\_11,
+TRXPT\_12, TRXPT\_13, TRXPT\_14, TRXPT\_16, TRXPT\_17, TRXPT\_18,
+TRXPT\_19, TRXPT\_20) in this TU, most of which have the 5' TPL sequence
+as in all AdVs. However, three transcripts (TRXPT\_16, TRXPT\_17,
+TRXPT\_18) use a different leader sequence (sTPL), where a different
+first exon is used instead of the first TPL exon, and TRXPT\_20 uses
+only the third TPL exon (TPL3); see \textbf{Figure 10}.
+
+We identified five TTSs (10,549, 12,709, 16,870, 22,116, 25,168 bp) in
+this TU, which we consider as corresponding to the five late mRNA
+classes (L1-L5), respectively. L1 mRNAs include TRXPT\_8, encoding the
+52K ORF as predicted. L2 mRNAs include TRXPT\_16, TRXPT\_17, and
+TRXPT\_18, all containing the sTPL with their respective coding exons.
+They encode pIIIa, III (penton), and pVII, respectively. The L3 mRNAs,
+TRXPT\_14 and TRXPT\_20, both encode the hexon (II) ORF but hexon is the
+only ORF encoded on TRXPT\_14, whereas TRXPT\_20 encodes pX (pre-Mu),
+pVI, and hexon in that order. L4 mRNAs, TRXPT\_9, TRXPT\_10, TRXPT\_11,
+and TRXPT\_13 are the largest transcripts in the transcriptome and
+encode several similar late proteins. TRXPT\_9 and TRXPT\_10 are very
+similar but not identical. The last exon of TRXPT\_9 seems to be
+truncated and likely shares the same TTS as TRXPT\_10. They both encode
+pVII as the 5'-most ORF and also have the CP for pX, pVI, hexon, a
+longer variant of protease (eProt) from an upstream in-frame SC, and
+ORF12 (a novel 120 residue protein). Additionally they have the CP for
+pVIII and eE3. TRXPT\_11 encodes hexon as its 5'-most ORF and also has
+the CP for eProt, ORF12, e33K, pVIII and eE3. Typically, MLTU
+transcripts splice the TPL onto a splice site just upstream of the ORF
+to be expressed (17). While this holds true for most MLTU ORFs, several
+late ORFs (pVI, protease, and ORF7) do not have such close proximity
+splicing but are contained in larger transcripts such as these L4 mRNAs,
+strongly suggesting the use of non-standard ribosomal initiation
+mechanisms such as secSC usage or ribosome shunting described in other
+AdVs for their translation (17, 29). TRXPT\_13, an E3 ORF utilizing the
+MLP TSS, encodes the classical L4P genes, pVIII and eE3. Lastly, the L5
+class transcript, TRXPT\_12, encodes Fiber as its 5'-most ORF but also
+has the CP for ORF7. Interestingly, the CP of TRXPT\_12 and TRXPT\_27 of
+the E3 TU are identical but are initiated from different TSSs. \newpage
 
@@
 While the advent of next-generation sequencing has rendered easier the
-study of large and complex eukaryotic transcriptomes, the study of the
-smaller and compact viral transcriptomes remains unintuitively
-challenging, as several transcripts may have significant overlaps due to
-genome economization. Characterizing AdV transcriptomes is even more
-difficult due to the wide array of mRNAs produced via very complex
-alternative splicing combined with alternative polyadenylation, all
-initiated from relatively few promoters. This makes AdV transcriptomes
-some of the most intricate for a virus. The challenge is further
-compounded by the fact that the standard software programs used in the
-RNA-seq analysis pipelines are not designed primarily for such compact,
-gene-dense, and complex transcriptomes as AdVs. Furthermore, in our
-case, there is no prior transcriptomic studies for THEV. Our approach to
-properly handle this complex data was to use standard RNA-seq analysis
-programs coupled with some custom analyses and experimentally validating
-all splice junctions with independent methods. Our work provides the
-first insights into the splicing patterns of THEV, which is expectedly
-similar to other MAdVs but with key differences. Our work shows 34
-transcripts in the THEV transcriptome grouped into five TUs, of which
-the E3 TU shows great complexity of alternative splicing.
-
-An unexpected observation is that the pileup of mapped reads to THEV
-seems consistently skewed over similar regions of the genome at all time
-points. As the gene expression of AdVs is temporally regulated, we
-expected to see unambiguous differences in the pileup of reads over
-different regions of the genome at different time points, indicating the
-different stages of infection. While this could simply mean that the
-infection was not well synchronized, we speculate that the temporal gene
-expression regulation of THEV is probably different from MAdVs. This is
-supported by a previous study stating the same conclusion with its
-finding that almost all THEV transcripts were detectable by at 4h.p.i,
-and by 8h.p.i, mRNA for all predicted ORFs (including the late genes)
-were present (24). Conversely, despite the overall pileup similarity, a
-close inspection shows that the relative proportions of reads over some
-regions show some variation over time. The breakdown of transcripts
-detected at different time points in \textbf{Figure 3b} seems to support
-this different temporal regulation of THEV. Specifically, the MLP of
-THEV is active significantly earlier in infection -- as early as 4h.p.i
-and more pronounced at 12h.p.i (\textbf{Figure 3b} and \textbf{Table
-2a}), -- whereas the late phase shift in MAdVs occurs after 24h.p.i.
-This also lends credence to our speculation. However, generally
-speaking, the overall temporal gene expression regulation known in MAdVs
--- early regions showing their peak expression at earlier time points
-followed by predominance of the MLTU at later time points -- also holds
-true for THEV. Further studies would be necessary to establish the
-precise temporal regulation of THEV transcription.
-
-The use of short read deep sequencing to reconstruct full AdV mRNA
-structures provides excellent results, especially for mapping the splice
-sites. However, due to the substantial overlapping nature of AdV mRNAs
-coupled with the fragmentation step in the library preparation protocol,
-mapping the precise TSS and TTS of the assembled transcripts is
-difficult. Also, similar transcripts with substantial overlaps may be
-assembled as one longer mRNA since the short reads alone do not provide
-enough context for the transcript assembler (StringTie) to distinguish
-them. In our results, we see transcripts in the same TU initiated or
-terminated in the same approximate area (10-70 bp and 1-300 bp apart for
-TSS and TTS, respectively) but not precisely at the same position. We
-consider the most upstream TSS or most downstream TTS for the
-transcripts involved but we present them unchanged in all the figures
-shown. Also, by comparison to the more well-studied MAdV transcriptomes,
-we believe that a few long transcripts in the MLTU (TRXPT\_9, TRXPT\_10,
-and TRXPT\_11) are probably a result of fusing some L4P-derived
-transcripts to the terminal exons of the bona fide MLTU transcripts by
-StringTie, making them significantly longer. These mRNAs do not only
-have unusually many exons for an AdV, but their last three or four exons
-are also identical to the L4P-derived mRNAs. Future studies using long
-read sequencing technologies are necessary to provide conclusive data
-for precisely mapping the TSS and TTS, as well as teasing apart the bona
-fide structures of the long MLTU transcripts. Furthermore, it is not
-unreasonable to presume that several splice variants were undiscovered
-in our work as evidenced firstly by finding unique transcripts using 3'
-RACE and during our splice junction validation steps. And secondly,
-recent studies (17, 18, 22) are still discovering novel mRNA variants
-for even the best studied MAdVs decades later. Another observation made
-is that all the TTSs in THEV's transcriptome are in close proximity to
-A/T-rich sequences which we presume to be polyadenylation signal
-sequences (PASS). Interestingly, some of these PASSs are located in the
-immediate vicinity of two closely located TTSs expressed on opposite
-strands. Namely, the E1 and E2B/IM TTSs have an almost palindromic PASS
-between them, as do the E4 (anti-sense strand) and the sense strand
-TRXPT\_12 and TRXPT\_27.
-
-An interesting finding of our analysis is that while most of the
-predicted ORFs are precisely encoded by the spliced transcripts, we
-found a few that seem to be truncated predictions, as either an upstream
-in-frame SC (eORF1, eE3, and eProt) or unknown upstream exons spliced
-onto them (eIVa2, e33K, and eORF8) were found. Other ORFs were
-identified that were either shorter (tDBP, t100K) or longer (e22K)
-isoforms of some predicted ORF but we found evidence to support the
-predicted ORF itself, making them all possible genuinely translated
-variants. We also found several novel unpredicted ORFs. Taken together,
-we surmise that further studies will likely yield even more unpredicted
-novel ORFs or variants of predicted ORFs.
-
-Eukaryotic mRNAs are typically functionally monocistronic, the 5'-most
-AUG normally being used to determine the translation reading frame.
-However, depending on the sequence context, in some organisms, the
-initiating codon may even be a non-AUG start codon. AdV mRNAs, which
-mostly span more than one ORF, are known to be functionally
-polycistronic, employing non-standard mechanisms of translation
-initiation, namely, secSC usage and ribosome shunting (10, 22). While
-there is no reliable method of predicting how efficiently any given AUG
-will be used, AdVs use secondary AUGs as initiation codons for most E1b
-proteins and for some E3 proteins. In fact, recent studies show that
-secSC usage is found transcriptome-wide. This is thought to occur
-because translation initiation at the first SC is inefficient, allowing
-downstream SCs to be employed for initiation (17). The ribosomal
+study of large and complex eukaryotic transcriptomes, studying the
+smaller, compact viral transcriptomes remains unintuitively challenging,
+as the transcripts typically have significant overlaps due to genome
+economization. AdV transcriptomes escalate the difficulty due to the
+wide array of mRNAs produced via very complex alternative splicing and
+polyadenylation, all initiated from relatively few promoters. Standard
+RNA-seq analysis programs, not primarily designed for such compact,
+gene-dense, and complex transcriptomes, further compound this challenge.
+Furthermore, in our case, no prior transcriptomic studies for THEV
+exist. Our approach combines standard RNA-seq analysis programs with
+custom analyses and experimentally validating all splice junctions with
+independent methods. The transcript map for THEV produced from our
+analysis is strikingly similar to that of the MAdVs.
+
+Our work provides the first insights into THEV splicing, revealing 34
+transcripts grouped into five transcription units (TUs). The general
+temporal gene expression regulation observed in MAdVs, with early
+regions peaking at earlier time points followed by MLTU predominance at
+later time points, seems to also apply to THEV. An unexpected
+observation is that the pileup of mapped reads to THEV seems
+consistently skewed over similar regions of the genome at all time
+points. Given the temporal regulation of AdVs gene expression, we
+anticipated distinct differences in read pileups over the genome at
+different time points, indicating the different stages of infection.
+This probably due to the infection not being well-synchronized, leading
+to transcripts overlapping the time points. Further research is required
+to determine the precise temporal regulation of THEV.
+
+Short read deep sequencing effectively reconstructs full AdV mRNA
+structures, particularly mapping splice sites (18). However, the
+substantial overlapping nature of AdV mRNAs and fragmentation during
+library preparation make it challenging to map the exact TSS, TTS, and
+PASs of assembled transcripts. Also, transcripts with significant
+overlaps may be assembled as a single, longer mRNA, since the short
+reads alone do not provide enough context for the transcript assembler
+(StringTie) to distinguish them. Our results show transcripts in the
+same TU initiating or terminating in similar areas, but not at the exact
+same position. We consider the most upstream TSS or most downstream TTS
+for for the transcripts involved but we present them unchanged in all
+the figures shown (see \textbf{Supplementary Table S2}). Also, comparing
+our results to the better-studied MAdV transcriptomes, we believe some
+long transcripts in the MLTU (TRXPT\_9, TRXPT\_10, and TRXPT\_11) are
+likely due to fusing some E3 transcripts to the terminal exons of the
+MLTU transcripts by StringTie, making them significantly longer. These
+mRNAs have unusually many exons and their last few exons are identical
+to some E3 mRNAs. Future studies using long read sequencing technologies
+will provide more precise mapping of the TSS and TTS and clarify the
+structures of the long MLTU transcripts.
+
+While most predicted ORFs are encoded by the spliced transcripts, we
+found some that seem to be truncated predictions, as either an upstream
+in-frame SC or unknown upstream exons were found. Other ORFs were
+identified that were either shorter or longer isoforms of some predicted
+ORF. We also found several novel unpredicted ORFs (\textbf{Supplementary
+Table S3}). On this basis, we anticipate that further studies will
+likely reveal more unpredicted novel ORFs or new variants of predicted
+ORFs. Furthermore, it is not unreasonable to presume that several splice
+variants will likely be found as evidenced firstly by finding unique
+transcripts using 3' RACE and during our splice junction validation
+steps. And secondly, recent studies (17, 18, 22) are still discovering
+novel mRNA variants for even the best studied MAdVs decades later.
+
+Eukaryotic mRNAs are typically functionally monocistronic, with the
+5'-most AUG determining the translation reading frame. However, AdV
+mRNAs, which span more than one ORF, are functionally polycistronic,
+employing non-standard mechanisms of translation initiation such as
+secSC usage and ribosome shunting (10, 22). AdVs use secondary AUGs as
+initiation codons for most E1b proteins and some E3 proteins. In fact,
+recent studies show that secSC usage is found transcriptome-wide. This
+is thought to occur because translation initiation at the first SC is
+inefficient, allowing downstream SCs to be employed (17). Ribosomal
 shunting or jumping mechanism is utilized for MLTU transcripts that have
 the TPL. This mechanism allows the ribosome to translocate to a
-downstream initiating codon under the direction of the shunting elements
-in the TPL, even if a start codon in a good Kozak sequence context is
-bypassed. Thus, predicting the protein(s) that are expressed from an AdV
-mRNA becomes highly uncertain as any one of the SC may be selected (10,
-22). Almost all the THEV transcripts in our data have the CP for several
-ORFs, some spanning as many as six ORFs but the majority spanning at
-least two ORFs. Therefore, we believe our data support the usage of
-these special ribosome initiation mechanisms as several predicted and
-novel ORFs found on mRNA in our data have no conceivable mechanism of
-being translated if only the typical ribosome scanning mechanism is
-employed. Interestingly, several distinct transcripts have identical
-CPs. This is not unique to THEV but is observed in human AdVs in a
-recent study (17). They proposed that this may permit protein production
-to be fine-tuned through alteration in the balance between different
-mRNA groups expressing that ORF.
-
-It is well established that AdV alternative splicing undergoes a
-regulated temporal shift in splice site usage. This was thought to be
-limited to certain TUs; however, recent studies suggest that AdVs
-routinely produce different combinations of splice acceptor--donor pairs
-and that this is observed in all TUs (10, 17, 22, 29). The mechanistic
-details of this phenomenon have been best studied for the E1A and L1
-units. The studies show that AdVs (specifically, late phase AdV-infected
-nuclear extract) modulate the activities of the splicing factor U2AF and
-the cellular SR family of splicing factors (reviewed in reference (29))
-and encode several mostly late phase proteins (E4-ORF3, E4-ORF6,
-E4-ORF4, L4-33K, and L4-22K) that influence the RNA splice site used.
-This phenomenon seems to occur in the THEV transcriptome also, as the
-stringency of splice acceptor-donor pairs selected decreases measurably
-from the onset of the late phase (see \textbf{Figure 5}). In fact,
-recent studies of some human AdVs show that a virtually unlimited number
-of combinatorial alternative splicing events occur in an AdV lytic
-infection, resulting in menagerie of novel transcripts (17, 22). It is
-unlikely that the entire repertoire of mRNA produced via this mechanism
-will actually be translated. However, it has been speculated that the
-plasticity in alternative RNA splicing enables AdVs to fine-tune protein
-synthesis by providing different alternatively spliced variants encoding
-the same protein under changing conditions. The capacity to produce
-novel exon combinations offers the virus an evolutionary advantage to
-adjust the repertoire of mRNA transcription and protein production in
-the changing environment of the viral replication cycle (17, 22).
-
-Summarizing all the main points above, we see that the THEV
-transcriptome bears remarkable overall similarity to the better studied
-MAdVs. The transcriptome is organized into five TUs, the temporal
-regulation is divided into early and late genes, and a broad repertoire
-of transcripts are produced via virtually unlimited alternative
-splicing. However, the THEV transcriptome appears to be less
-sophisticated (i.e, it encodes fewer genes) than MAdVs primarily because
-the MAdV genomes are close to twice as long as that of THEV, which
-rationally should encode less genes. The lack of subdivision of the E1
-region into E1a and E1b is one of the most obvious examples. Also, the
-MAdV E4 region encodes several proteins unlike in THEV where only one
-transcript coding for one protein was found. The most conspicuous
-example is found in examining the complexity of the MLTU leader
-sequences. While the majority of the THEV MLTU transcripts begin with
-the TPL (267 bp long) just like MAdVs, and also utilize a variant leader
-sequence (sTPL), it is well-established that significantly more diverse
-5'UTRs are employed for MAdV MLTU transcripts. Namely, the TPL (used for
-majority of transcripts), the so-called x, y, and z leaders, and the
-i-leader are 5' leaders utilized by MAdV MLTU mRNAs. Granted, the MAdV
-MLTU transcripts infrequently incorporate the non-TPL leaders, their
-absence in our data could mean that the 5'UTR diversity of THEV's MLTU
-mRNA are indeed more limited due to its smaller genome size. It is also
-possible that later studies could uncover more variety not seen in our
-results. Specifically, using long read sequencing technologies would be
-a excellent approach to discovering and fine-tuning the transcriptome
-characterized in this work. Also, it is likely that future studies
-repeating this work in other cell lines will yield some interesting
-insights. \newpage
+downstream AUG, under the direction of the shunting elements in the TPL,
+even if a start codon in a good Kozak sequence context is bypassed.
+Thus, predicting the protein(s) expressed from an AdV mRNA is uncertain
+as any one of the AUGs may be selected (10, 22). Almost all the THEV
+transcripts in our data have the CP for several ORFs, some spanning as
+many as six ORFs. This supports the usage of these special ribosome
+initiation mechanisms as several predicted and novel ORFs found on mRNA
+in our data could not be translated using only the typical ribosome
+scanning mechanism. Interestingly, several distinct THEV mRNAs have
+identical CPs. This is also observed in human AdVs in a recent study
+(17). They proposed that this may permit protein production to be
+fine-tuned through alteration in the balance between different mRNA
+groups expressing that ORF.
+
+AdV alternative splicing undergoes a regulated temporal shift in splice
+site usage, previously thought to be limited to certain TUs. However,
+recent studies suggest that AdVs routinely produce different
+combinations of splice acceptor--donor pairs across all TUs (10, 17, 22,
+30). The details of this phenomenon have been best studied for the E1A
+and L1 units. AdVs modulate the activities of the splicing factor U2AF
+and the cellular SR family of splicing factors (reviewed here (30)), and
+encode several proteins that influence the RNA splice site used. This
+phenomenon appears to occur in the THEV transcriptome, as the stringency
+of splice acceptor-donor pairs selected decreases from the onset of the
+late phase (\textbf{Figure 5}). Recent studies show that a virtually
+unlimited number of combinatorial alternative splicing events occur in
+an AdV lytic infection, resulting in a variety of novel transcripts (17,
+22). It is unlikely that the entire repertoire of mRNA produced via this
+mechanism will actually be translated. However, it has been speculated
+that the plasticity in alternative RNA splicing enables AdVs to
+fine-tune protein synthesis by providing different alternatively spliced
+variants encoding the same protein under changing conditions, confering
+an evolutionary advantage (17, 22).
+
+In summary, the THEV transcriptome bears remarkable similarity to the
+better-studied MAdVs. The transcriptome is organized into five TUs, with
+temporal regulation divided into early and late genes, and a broad
+repertoire of transcripts are produced via virtually unlimited
+alternative splicing. However, the THEV transcriptome appears less
+sophisticated (i.e, it encodes fewer genes) than MAdVs, primarily
+because the MAdV genomes are close to twice as long as that of THEV. The
+lack of subdivision of the E1 region into E1a and E1b is one of the most
+obvious examples. Also, the MAdV E4 region encodes several proteins
+unlike in THEV where only one transcript encoding one protein was found.
+The complexity of the MLTU leader sequences is another example. While
+the majority of the THEV MLTU transcripts begin with the TPL just like
+MAdVs with a small subset using a variant leader sequence (sTPL),
+significantly more diverse 5'-UTRs are employed for MAdV MLTU
+transcripts. Namely, the TPL, the so-called x, y, and z leaders, and the
+i-leader are 5' leaders utilized by MAdV MLTU mRNAs. The absence of
+these non-TPL leaders in our data could mean that the 5'-UTR diversity
+of THEV's MLTU mRNAs is more limited due to its smaller genome size or
+future studies using long read sequencing technologies could uncover
+more variety not seen in our results. \newpage
 
@@
 titrated using an in-house qPCR assay with titer expressed as genome
-copy number (GCN)/mL, similar to Mahshoub \emph{et al} (30) with
+copy number (GCN)/mL, similar to Mahshoub \emph{et al} (31) with
 modifications. Cells were infected in triplicate at a multiplicity of
@@
 infected MDTC-RP19 cells used for the RNA-seq experiment as explained
-above. We followed the protocol described by Green \emph{et al} (31)
+above. We followed the protocol described by Green \emph{et al} (32)
 with modifications. Briefly, 1\(\mu g\) of total RNA was reverse
@@
 described by Pertea \emph{et al} (25), using Snakemake - version 7.24.0
-(32), a popular workflow management system to drive the pipeline.
+(33), a popular workflow management system to drive the pipeline.
 Briefly, sequencing reads were trimmed with the Trim-galore - version
-0.6.6 (33) program to achieve an overall Mean Sequence Quality (Phred
+0.6.6 (34) program to achieve an overall Mean Sequence Quality (Phred
 Score) of 36. Trimmed reads were mapped simultaneously to the complete
@@
 
+\bibitem[\citeproctext]{ref-Beaudoing2000}
+\CSLLeftMargin{28. }%
+\CSLRightInline{Beaudoing E, Freier S, Wyatt JR, Claverie J-M, Gautheret
+D. 2000. \href{https://doi.org/10.1101/gr.10.7.1001}{Patterns of variant
+polyadenylation signal usage in human genes}. Genome Research
+10:1001--1010.}
+
 \bibitem[\citeproctext]{ref-Yueh1996}
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{29. }%
 \CSLRightInline{Yueh A, Schneider RJ. 1996.
@@
 \bibitem[\citeproctext]{ref-Akusjarvi2008}
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{Akusjarvi G. 2008.
@@
 \bibitem[\citeproctext]{ref-Mahsoub2017}
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{Mahsoub HM, Evans NP, Beach NM, Yuan L, Zimmerman K,
@@
 \bibitem[\citeproctext]{ref-Green2019}
-\CSLLeftMargin{31. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{Green MR, Sambrook J. 2019.
@@
 \bibitem[\citeproctext]{ref-Snakemake2021}
-\CSLLeftMargin{32. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{Mölder F, Jablonski KP, Letcher B, Hall MB,
@@
 \bibitem[\citeproctext]{ref-TrimGalore}
-\CSLLeftMargin{33. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{Krueger F, James F, Ewels P, Afyounian E, Weinstein M,
@@
 The central horizontal line represents the double-stranded DNA marked at
-5kb intervals as white line breaks. Colored blocks represent viral
+2kb intervals as white line breaks. Colored blocks represent viral
 genes. Blocks above the DNA line are transcribed on the sense DNA strand
@@
 for each indicated time point. \textbf{B) Growth curve of THEV (VAS
-vaccine strain) in MDTC-RP19 cell line.} Virus titers in the
+vaccine strain) in MDTC-RP19 cell line.} Virus quantities in the
 freeze-thawed supernatant from infected cells were a quantified with a
@@
 transcripts assembled from all time points by StringTie are unified
-forming this final transcriptome (splicing map). Transcripts belonging
-to the same transcription unit (TU) are located in close proximity on
-the genome and are color coded and labeled in this figure as such. The
+forming this transcriptome (splicing map). Transcripts belonging to the
+same transcription unit (TU) are located in close proximity on the
+genome and are color coded and labeled in this figure as such. The
 organization of TUs in the THEV genome is unsurprisingly similar to
@@
 
-\begin{longtable}[l]{|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{1.20in}}
+\begin{longtable}[l]{|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}|p{1.20in}}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}
-
-\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Splice\_Site}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}
+
+\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Timepoint}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Strand}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Start}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{End}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Intron\ Length}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Reads\ (Percentage)}}}} \\
 
@@
 
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{103\ (17\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{CU-AC}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{97\ (16\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{58\ (9.6\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,701}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26,055}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{354\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{37\ (6.1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{33\ (5.5\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{32\ (5.3\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22\ (3.6\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21\ (3.5\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21\ (3.5\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18\ (3\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18\ (3\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14\ (2.3\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,682}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,931\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10\ (1.7\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,312\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{9\ (1.5\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{9\ (1.5\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,163}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{76\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{8\ (1.3\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7\ (1.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6\ (1\%)}}} \\
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{103\ (17\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{97\ (16\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{58\ (9.6\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,701}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26,055}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{354\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{37\ (6.1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{33\ (5.5\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{32\ (5.3\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22\ (3.6\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21\ (3.5\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21\ (3.5\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18\ (3\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18\ (3\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14\ (2.3\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,682}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,931\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10\ (1.7\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,312\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{9\ (1.5\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{9\ (1.5\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,163}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{76\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{8\ (1.3\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7\ (1.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6\ (1\%)}}} \\
 
@@
 
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,825\ (16.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{CU-AC}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{17,670\ (15.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,319\ (10.7\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,583\ (9.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,128\ (6.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6,619\ (5.8\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,207\ (4.5\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,930\ (3.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,870\ (3.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,553\ (2.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,446\ (2.1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,642\ (1.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,395\ (1.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,910\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,391\ (1.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,124\ (1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,128}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,377\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,124\ (1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,894}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{671\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,208\ (1\%)}}} \\
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,825\ (16.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{17,670\ (15.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,319\ (10.7\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,583\ (9.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,128\ (6.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{6,619\ (5.8\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,207\ (4.5\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,930\ (3.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,870\ (3.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,553\ (2.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,446\ (2.1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,642\ (1.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,395\ (1.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,910\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,391\ (1.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,124\ (1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,128}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,377\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,124\ (1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{24hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,894}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{671\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,208\ (1\%)}}} \\
 
@@
 
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{322,677\ (15.1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{179,607\ (8.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{161,336\ (7.6\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{CU-AC}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{146,425\ (6.9\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{93,238\ (4.4\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{81,420\ (3.8\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{77,616\ (3.6\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{45,062\ (2.1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38,491\ (1.8\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38,841\ (1.8\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{35,490\ (1.7\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,312\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,041\ (1.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26,338\ (1.2\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,904}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,097\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,946\ (1\%)}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{GU-AG}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,891\ (1\%)}}} \\
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,531}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,754}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{223\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{322,677\ (15.1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,360}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,094\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{179,607\ (8.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,087}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,159}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{161,336\ (7.6\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,189}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,684}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{495\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{146,425\ (6.9\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,223}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,419}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{196\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{93,238\ (4.4\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{13,610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,803\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{81,420\ (3.8\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,238}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{4,431\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{77,616\ (3.6\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,394\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{45,062\ (2.1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,964}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{309\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38,491\ (1.8\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,162}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,812\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{38,841\ (1.8\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,350}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,717}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{367\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{35,490\ (1.7\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{304}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,312\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,041\ (1.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{18,751}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{20,668}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{1,917\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{26,338\ (1.2\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,904}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{5,097\ bp}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,946\ (1\%)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{+}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{7,807}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,492}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{14,685\ bp}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{21,891\ (1\%)}}} \\
 
@@
 \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{72hpi}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{3,568}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{0.2\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+\textbf{Supplementary Table S2}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.80in}|p{0.80in}|p{2.00in}|p{0.80in}|p{1.50in}}
+
+\caption{Table\ S2:\ Mapping\ Transcript\ TTS\ with\ Closest\ Polyadenylation\ Signal}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}
+
+\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Sub\ Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Transcripts}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{TTS}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Nearest\ ‘AAUAAA’\ TTS\ signal\ (location\ refers\ to\ 'U'\ in\ the\ sequence)}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\endfirsthead \caption[]{Table\ S2:\ Mapping\ Transcript\ TTS\ with\ Closest\ Polyadenylation\ Signal}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}
+
+\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Sub\ Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Transcripts}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{TTS}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{\textbf{Nearest\ ‘AAUAAA’\ TTS\ signal\ (location\ refers\ to\ 'U'\ in\ the\ sequence)}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\endhead
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_1,\ TRXPT\_2,\ TRXPT\_3,\ TRXPT\_4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,323}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_21,\ TRXPT\_21B}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{16,934}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{16,950}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2/IM}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E2B/IM}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_5,\ TRXPT\_6,\ TRXPT\_7,\ TRXPT\_31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,334}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{2,333}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_22,\ TRXPT\_24}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,491}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,458\ (AGUAAA)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3B}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_23,\ TRXPT\_25,\ TRXPT\_25B,\ TRXPT\_26,\ TRXPT\_30}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{23,884}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{23,889}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E3C}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_27}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,168}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,166}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{E4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_28}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,192}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,203}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLTU}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{L1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_8}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,549}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{10,537}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLTU}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{L2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_16,\ TRXPT\_17}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{12,709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLTU}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{L3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_14,\ TRXPT\_20}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{16,870}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{16,903}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLTU}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{L4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_9,\ TRXPT\_10,\ TRXPT\_11,\ TRXPT\_13}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,116}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{22,098\ (AAGAAA)}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{MLTU}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{L5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{TRXPT\_12}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,168}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{8}{8}\selectfont{25,166}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+\textbf{Supplementary Table S3}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}|p{0.80in}|p{2.00in}}
+
+\caption{Table\ S3:\ The\ Encoded\ Proteins\ and\ Coding\ Potential\ of\ THEV\ Transcripts}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}
+
+\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{mRNA}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Primary\ Product}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Size}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{(kDa)}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Number\ of}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Residues}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Start\ Codon}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Position}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Stop\ Codon}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Position}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Downstream}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Coding\ Potential}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\endfirsthead \caption[]{Table\ S3:\ The\ Encoded\ Proteins\ and\ Coding\ Potential\ of\ THEV\ Transcripts}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-}
+
+\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{mRNA}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Primary\ Product}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Size}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{(kDa)}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Number\ of}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Residues}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Start\ Codon}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Position}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Stop\ Codon}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Position}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Downstream}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{\linebreak }}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Coding\ Potential}}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\endhead
+
+\multicolumn{7}{>{\raggedright}m{\dimexpr 6.8in+12\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{new}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Novel\ product\ identified\ in\ this\ work}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{;\ }}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{FFFFFF}
+
+\multicolumn{7}{>{\raggedright}m{\dimexpr 6.8in+12\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{L}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Longer\ isoform\ identified\ in\ this\ work}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{FFFFFF}
+
+\multicolumn{7}{>{\raggedright}m{\dimexpr 6.8in+12\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{S}}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Shorter\ isoform\ identified\ in\ this\ work}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{FFFFFF}
+
+\endlastfoot
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF9}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{new}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{17.9}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{160}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{211}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2312}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hyd,\ ORF4}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF10}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{new}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{66.4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{597}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{211}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2312}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hyd,\ ORF4}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_2B}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{eORF1}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{L}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{64.3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{580}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1965}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1953}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hyd,\ ORF4}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF4}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{13.1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{115}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{211}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2312}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hyd}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF11}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{new}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{15.9}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{143}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{211}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1953}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hyd,\ ORF4}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{IVa2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{42.3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{371}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{3616}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2334}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_6}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pTP}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{70.5}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{597}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{10995}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{6765}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ad-pol}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_7}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pTP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{70.5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{597}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{10995}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{6765}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ad-pol}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{52K}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{33.8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{300}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8570}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{9472}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_9}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVII}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{13.2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{120}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12347}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12709}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pX,\ pVI,\ hexon,\ eProt,\ ORF12,\ pVIII,\ eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_10}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVII}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{13.2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{120}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12347}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pX,\ pVI,\ hexon,\ eProt,\ ORF12,\ pVIII,\ eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_11}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hexon\ (II)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{101.1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{906}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{13610}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{16330}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{eProt,\ ORF12,\ e33K,\ pVIII,\ eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_12}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Fiber\ (IV)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{49}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{454}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{22519}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{23883}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF7}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_13}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVIII}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{21.8}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{200}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20769}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{21371}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_14}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hexon\ (II)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{101.1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{906}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{13610}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{16330}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_15}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_16}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pIIIa}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{57.6}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{505}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{9462}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{10979}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Penton\ (III),\ pVII}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_17}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Penton\ (III)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{50.8}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{448}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{11001}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12347}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_18}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVII}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{13.2}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{120}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12347}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12709}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_19}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_20}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pX}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{6.1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{58}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12712}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{12888}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVI,\ hexon}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_21}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{DBP}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{43.3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{380}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18186}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{16973}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_21B}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{tDBP}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{S}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{39.3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{346}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18013}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{16973}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_22}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8.3KII}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{new}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8.6}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{73}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20457}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVIII,\ eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_23}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8.3KI}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{new}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8.3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{73}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20262}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVIII,\ eE3,\ Fiber}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_24}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{e33K}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{L}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{19.8}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{171}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20699}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVIII,\ E3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_25}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{t100K}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{62.4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{543}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20227}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{22K,\ pVIII,\ eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_25B}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{100K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{76.5}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{665}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20227}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{22K,\ pVIII,\ eE3}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_26}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVIII}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{21.8}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{200}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20769}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{21371}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{eE3,\ Fiber}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_27}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Fiber\ (IV)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{49}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{454}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{22519}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{23883}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF7}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_28}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{eORF8}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{L}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{26.4}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{229}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{26246}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{25204}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_29}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8.3KI}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{8.3}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{73}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20262}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_30}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{e22K}}\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textsuperscript{L}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{15.7}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{140}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{18230}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{20411}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{pVIII,\ eE3,\ Fiber}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TRXPT\_31}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ad-pol}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{129.2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1112}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{6768}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{3430}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-}}} \\
 
@@
 elongation -- 68\textsuperscript{o}C for 5 minutes. We used 35 cycles of
-amplification.
+amplification. The PCR products of THEV cDNA shown in the gels in the
+table above were cloned and Sanger sequenced to confirm the splice
+junctions. We included ``No reverse transcriptase (No RT)'' template
+controls to ensure the PCR products are of RNA origin.
 

### 2024-05-06 scripts/r/abund_analysis_tpm.R

@@ -1,45 +1,0 @@
-#!/usr/bin/env Rscript
-
-library(magrittr)
-library(scales)
-library(plyr)
-library(rtracklayer)
-library(glue)
-library(devtools)
-library(genefilter)
-library(tidyverse)
-
-
-# ====================================================================
-# TRANSCRIPT ABUNDANCE ANALYSIS
-# ====================================================================
-# load in abund files
-abund_metadata <- tibble(dir = c(list.dirs("results/abundances", full.names = T) %>% .[-1]),
-                     abund_file = map_chr(dir, function(dir) list.files(path = dir,
-                                             pattern = "^abund_\\d{1,2}hrsS\\d\\.gtf$",
-                                             full.names = T)),
-                     raw_tabs = map(abund_file, \(abund_file) as_tibble(import(abund_file))),
-                     time_labs = case_when(str_detect(dir, "_4hrs") ~ "4hpi",
-                                           str_detect(dir, "_12hrs") ~ "12hpi",
-                                           str_detect(dir, "_24hrs") ~ "24hpi",
-                                           str_detect(dir, "_72hrs") ~ "72hpi",
-                                           TRUE ~ NA_character_)
-                     )
-
-# join the dataframes as one
-abund_data <- abund_metadata$raw_tabs %>%
-  set_names(abund_metadata$time_labs) %>%
-  bind_rows(., .id = "timepoint") %>%
-  rename(fpkm = FPKM, tpm = TPM) %>%
-  filter(type == "transcript") %>%
-  mutate(tpm = as.numeric(tpm),
-         fpkm = as.numeric(fpkm)) %>%
-  group_by(timepoint, transcript_id, start, end) %>%
-  reframe(total_tmp = sum(tpm)) %>%
-  arrange(start)
-  
-
-abund_data %>%
-  ggplot(aes(transcript_id, total_tmp, fill = timepoint)) +
-  geom_col(position = "dodge") +
-  theme(axis.text.x = element_text(angle = 45))

### 2024-05-06 scripts/r/plot_abundances.R

@@ -31,14 +31,13 @@ plot_time_genexpression <- function(count_ss){
     theme(plot.margin = margin(rep(30, 4)),
           panel.grid.major.y = element_line(linewidth = 0.4, color = "grey",
                                             linetype = "dashed"),
-          axis.title.y = element_text(size = 28, face = "bold", margin = margin(r = 15)),
-          axis.text.x = element_text(size = 26, face = "bold"),
-          axis.text.y = element_text(size = 18, face = "bold"),
-          legend.justification = c(0, 0),
-          legend.position = c(0.05, 0.9),
-          legend.key.width = unit(2, "cm"),
+          axis.title.y = element_text(size = 28, face = "bold",
+                                      margin = margin(r = 15), colour = "#000000"),
+          axis.text = element_text(size = 30, face = "bold", colour = "#000000"),
+          legend.position = "top",
+          legend.key.width = unit(4, "cm"),
           legend.title = element_blank(),
-          legend.text = element_text(size = 20, face = "bold", colour = "black"),
+          legend.text = element_text(size = 28, face = "bold", colour = "black"),
           legend.text.align = 0) +
     guides(color = guide_legend(label.position = "top",
                                 label.hjust = 0.5,
@@ -193,15 +192,22 @@ trxpt_fpkms <- t_expr_each %>%
   theme(plot.margin = margin(t = 20, l = 20, r = 20, b = 5),
         panel.grid.major.y = element_line(linewidth = 0.2, color = "grey",
                                           linetype = "dashed"),
-        axis.title.y = element_text(size = 28, face = "bold", margin = margin(r = 15)),
-        axis.text.x = element_text(size = 16, face = "bold", angle = 45, hjust = 1),
+        axis.title.y = element_text(size = 30, face = "bold",
+                                    margin = margin(r = 15)),
+        axis.text.x = element_text(size = 28, face = "bold",
+                                   angle = 45, hjust = 1, colour = "#000000"),
         axis.text.y = element_text(size = 28, face = "bold", colour = "#000000"),
-        legend.justification = c(0, 0),
-        legend.position = c(0.02, 0.6),
+        # legend.justification = c(0, 0),
+        legend.direction = "horizontal",
+        legend.position = c(0.5, 0.9),
+        legend.text.position = "top",
         legend.key.size = unit(1.5, "cm"),
         legend.title = element_blank(),
-        legend.text = element_text(size = 18, face = "bold", colour = "black"),
[…]

### 2024-05-06 scripts/r/plot_fig6_10.R

@@ -12,12 +12,9 @@ plot_figs <- function(trxpt_table, trxpt_plot){
   set_flextable_defaults(font.size = 7)
   
   # prepare junction table
-  junc_tab <- trxpt_table %>% 
-    # change thymines to uracils to match RNA
-    mutate(splice_site = dplyr::case_when(splice_site %in% c("CT-AC, GT-AG", "GT-AG") ~ "GU-AG",
-                                          splice_site == "GT-GC" ~ "GU-GC")) %>% 
+  junc_tab <- trxpt_table %>%
     flextable(.,
-            col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
+            col_keys = c("trxpt_id", "start", "end", "intron_len",
                          "strand", "4hpi", "12hpi", "24hpi", "72hpi",
                          "status")) %>%
     theme_zebra() %>%
@@ -27,18 +24,17 @@ plot_figs <- function(trxpt_table, trxpt_plot){
                                  strand = "Strand", trxpt_id = "Transcript ID",
                                  intron_len = "Intron Length", "4hpi" = "4h.p.i",
                                  "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
-                                 splice_site = "Splice Donor-Acceptor",
                                  "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
     flextable::align(align = "center", part = "all") %>%
     add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
-                   colwidths = c(1, 4, 1, 4, 1)) %>%
-    flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
-                                                                    width = 1.5)) %>%
+                   colwidths = c(1, 3, 1, 4, 1)) %>%
+    flextable::vline(j = c(1, 4, 5, 9),
+                     border = fp_border_default(color = "grey", width = 1.5)) %>%
     flextable::font(part = "all", fontname = "Arial")
   
   if ("TRXPT_1, TRXPT_4" %in% pull(trxpt_table, trxpt_id)){
     junc_tab <- junc_tab %>%
[…]

### 2024-05-06 scripts/r/thev_cov_depth.R

@@ -69,7 +69,8 @@ comp_all <- ggplot() +
   scale_x_continuous(expand = c(0, 0),
                      breaks = seq(0, 26000, 1000),
                      labels = glue("{seq(0, 26, 1)}kb")) +
-  # scale_y_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 6)) +
   labs(title = "Mapping Depth of RNA-seq Reads Over THEV Genome",
        x = element_blank(),
        y = "Log<sub>10</sub>(Mapping Depth)",
@@ -87,15 +88,18 @@ comp_all <- ggplot() +
         plot.title = element_text(size = 28, 
                                   face = "bold", 
                                   hjust = 0.5,
-                                  margin = margin(t = 10)),
+                                  margin = margin(t = 10, b = 15)),
         axis.title.y = element_markdown(size = 22, face = "bold",
                                     margin = margin(l = 10)),
         legend.justification = c(0, 0),
-        legend.position = c(0, 0.92),
+        legend.position = "top",
+        legend.text.position = "top",
+        legend.key.width = unit(8, "in"),
+        legend.key.spacing = unit(2, "in"),
         legend.direction = "horizontal",
         legend.background = element_blank(),
-        legend.text = element_text(size = 14,
-                                   margin = margin(r = 10, l = 0, t = 0, b = 0),
+        legend.text = element_text(size = 22,
+                                   hjust = 0.5,
+                                   margin = margin(b = 0, t = 0),
                                    face = "bold"),
-        legend.key.height = unit(1, "cm"),
-        legend.text.align = 0)
+        legend.key.height = unit(1, "cm"))

### 2024-05-06 scripts/r/thev_growthcurve.R

@@ -79,27 +79,29 @@ group_by(condition, hrs_pi) %>%
   reframe(mean_conc = mean(conc), 
             mean_conc_per_mL = (mean_conc * 10 * 1000),
             replicates = n(),
-            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000)
+            stderr_conc_perML = (sd(conc)/sqrt(replicates)) * 10000) %>%
+  filter(condition == "Inf")
 
 growth_curve <- full_prepped %>% 
-  ggplot(aes(hrs_pi, mean_conc_per_mL, color = condition)) +
+  ggplot(aes(hrs_pi, mean_conc_per_mL)) +
   geom_errorbar(aes(ymax = mean_conc_per_mL + stderr_conc_perML,
                     ymin = mean_conc_per_mL - stderr_conc_perML),
                 width = 0.8, show.legend = F,
                 linewidth = 1, color = "#000000") +
   geom_point(size = 5) +
   geom_line(linewidth  = 1.5) +
-  scale_color_aaas(breaks = c("Inf", "Neg"),
-                   labels = c("Infected", "Mock-Infected")) +
+  # scale_color_aaas(breaks = c("Inf", "Neg"),
+  #                  labels = c("Infected", "Mock-Infected")) +
   scale_x_continuous(expand = c(0.01, 0.01),
                      breaks = full_prepped$hrs_pi,
-                     labels = c(paste0(full_prepped$hrs_pi, "hpi"))) +
-  scale_y_continuous(expand = c(0.02, 0.02)) +
+                     labels = c(full_prepped$hrs_pi)) +
+  scale_y_log10(expand = c(0.02, 0.02),
+                limits = c(5e7, 2e10),
+                breaks = c(5e7, 1e8, 1e9, 1e10),
+                labels = c(5e7, 1e8, 1e9, 1e10)) +
   labs(title = "THEV Growth Curve in RP-19 Turkey B-Cells",
-       x = element_blank(),
-       y = "Virus Titer (GCN/mL)",
-       size = element_blank()
-  ) +
+       x = "Hours post-infection",
+       y = "Virus Concentration (GCN/mL)") +
   theme(plot.background = element_rect(fill = "#ffffff"),
         plot.margin = margin(rep(5,4)),
         panel.background = element_rect(fill = "#ffffff"),
@@ -116,22 +118,9 @@ growth_curve <- full_prepped %>%
[…]

### 2024-05-06 scripts/r/thev_orf_map.R

@@ -8,30 +8,32 @@ library(tidyverse)
 ## position the plus strand genes above genome line and minus strand genes below
 make_genomic_map2 <- function(bedfile){
   genus_specific <- c("ORF1", "Hyd", "E3", "ORF7", "ORF8")
+  
   thev_genome2 <- read_tsv(bedfile,
                           col_names = FALSE,
                           col_types = "ciiciciicicc") %>% 
     set_colnames(c("chr", "start", "end", "gene_name", "score", "strand", "thickStart",
                    "thickEnd", "color", "blockCount", "blockSizes", "blockStarts")) %>% 
-    mutate(exon1Size = str_replace(blockSizes, pattern = "(\\d+),\\d+", replacement = "\\1"),
-           exon1Size = as.numeric(exon1Size),
-           exon2Size = str_replace(blockSizes, pattern = "\\d+,(\\d+)", replacement = "\\1"),
-           exon2Size  = as.numeric(exon2Size),
+    mutate(exon1Size = as.numeric(str_replace(blockSizes, pattern = "(\\d+),\\d+", replacement = "\\1")),
+           exon2Size = as.numeric(str_replace(blockSizes, pattern = "\\d+,(\\d+)", replacement = "\\1")),
            exon2Size = ifelse(exon2Size == exon1Size, NA_real_, exon2Size),
            exon1start = thickStart,
            exon1end = ifelse(blockCount > 1, (start + exon1Size), thickEnd),
            exon2start = thickEnd - exon2Size,
            exon2end = thickEnd,
-           color = "#6D58F5",
-           color = ifelse(gene_name %in% genus_specific, "red", color),
-           color = ifelse(gene_name == "U exon", "skyblue", color),
-           color = ifelse(gene_name == "22K", "green", color),
+           color = case_when(gene_name %in% genus_specific ~ "red",
+                             gene_name == "U exon" ~ "skyblue",
+                             gene_name == "22K" ~ "green",
+                             TRUE ~ "#6D58F5"),
            gene_name = case_match(gene_name,
                                   "33K_spliced" ~ "33K",
                                   "pVIII gene" ~ "pVIII",
                                   .default = gene_name),
-           ypos = ifelse(strand == "-", c(24, 24.5), c(25.5, 26)),
-           ypos = ifelse(gene_name == "22K", 26.5, ypos))
[…]

### 2024-05-09 importance_of_study.Rmd
second round of edits after jvi review

@@
 
-\vspace{15mm}
+## List of abbreviations  
+```{r echo=F, warning=F, message=F}
+library(tidyverse)
+library(flextable)
+tribble(~Abbreviation, ~Definition,
+               "AdV", "Adenovirus",
+               "MAdV", "Mastadenovirus",
+               "SiAdV", "Siadenovirus",
+               "THEV", "Turkey Hemorrhagic Enteritis Virus",
+              "HE", "Hemorrhagic Enteritis",
+              "UTR", "Untranslated Region",
+              "TU", "Transcription Unit",
+              "L4P", "L4 Promoter",
+              "MLP", "Major Late Promter",
+              "E3P", "E3 Promoter",
+              "hpi", "Hours Post-infection",
+              "qPCR", "Quantitative Polymerase Chain Reaction",
+              "FPKM", "Fragments Per Kilobase of transcript per Million mapped reads",
+              "CP", "Coding Potential",
+              "TSS", "Transcription Start Site",
+              "TTS", "Transcription Termination Site",
+              "SC", "Start Codon", 
+              "STC", "Stop Codon",
+              "secSC", "Secondary Start Codon",
+              "secSTC", "Secondary Stop Codon",
+              "ORF", "Open Reading Frame", 
+              "CDS", "Coding Sequence", 
+              "MLTU", "Major Late Transcription Unit",
+              "TPL", "Tripartite Leader",
+              "sTPL", "Short Tripartite Leader",
+              "TPL3", "Third exon of Tripartite Leader",
+              "GCN", "Genome Copy Number") %>%
+  flextable::flextable() %>%
+  flextable::theme_box() %>%
+  flextable::width(width = 1, j = 1) %>%
+  flextable::width(width = 2, j = 2) %>%
+  flextable::align(align = "center", part = "all")
+```
+
+\newpage
 Hemorrhagic enteritis (HE) is a disease of turkey poults characterized by immunosuppression, bloody diarrhea, and up to 80% mortality.

### 2024-05-09 manuscript_thev_transcriptome.Rmd
second round of edits after jvi review

@@
 ---
-title: Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line
+title: Characterizing the Splice Map of Turkey Hemorrhagic Enteritis Virus
 output:
@@
 
-**Running Title:** Novel Insights into Turkey Hemorrhagic Enteritis Virus Transcriptome
-
-\vspace{10mm}
-
-Abraham Quaye^1\*^, Brett E. Pickett^\*^, Joel S. Griffitts^\*^, Bradford K. Berges^\*^, Brian D. Poole${^\dagger}$^\*^
+Abraham Quaye${^\dagger}$^,a^, Brett E. Pickett^a^, Joel S. Griffitts^a^, Bradford K. Berges^a^, Brian D. Poole^a,\*^
 
@@
 
-^\*^Department of Microbiology and Molecular Biology, Brigham Young University\
-^1^First-author\
-${^\dagger}$ Corresponding Author
+^a^Department of Microbiology and Molecular Biology, Brigham Young University\
+${^\dagger}$First-author\
+^\*^Corresponding Author
 
@@
 Characterizing the splice map of turkey hemorrhagic enteritis virus (THEV) is an essential step that would allow studies of individual genes mediating its immunosuppressive functions.
-We used an RNA-sequencing experiment to characterize the transcriptome of THEV for the first time, providing key insight into the THEV gene expression and mRNA structures.
+We used RNA sequencing to characterize the transcriptome of THEV for the first time, providing key insights into the THEV gene expression and mRNA structures.
 Researchers previously annotated the genome of THEV as encoding 23 open reading frames (ORFs).
-In this work we identified 29 spliced transcripts all of which consisted of novel exons although some exons matched some previously annotated ORFs.
+In this work we identified 29 spliced transcripts all of which contained novel exons although some exons matched some previously annotated ORFs.
 The three annotated splice junctions were also corroborated by our data.
@@
 We also identified three of the annotated ORFs with longer or shorter isoforms, and seven novel unannotated ORFs that could potentially be translated; although it is beyond the scope of this manuscript to investigate whether they are translated.
-Similar to other adenoviruses (AdVs), THEV also produces multiple distinctly spliced transcripts that code for the same proteins across its genome.
+Similar to other adenoviruses (AdVs), THEV also produces multiple distinctly spliced transcripts that code for the same protein.
 Our data show that all THEV transcripts are spliced and organized into five transcription units under the control of their cognate promoters like other AdVs.
@@
 Each transcription unit (TU) contains its own promoter driving the expression of the array of mRNA transcripts produced via alternative splicing in the unit [@Zhao2014; @Donovan2020; @Guimet2016].
-The promoters are activated at different phases of the infection by proteins from previously activated TUs.
+The promoters are activated at different phases of infection by proteins from previously activated TUs.
 Paradoxically, the early-to-late phase transition during infection requires the L4 gene products, 22K and 33K, which should only be available after the transition.
@@
 Unlike MAdV where two promoters are known [@Donovan2020], we discovered only a single TSS (E2 TSS; 18,751 bp) for both E2A and E2B transcripts in THEV.
-However, similar to MAdVs, E2A and E2B transcripts have distinct TTSs, with E2B transcripts sharing the TTS of the IVa2 transcript of the IM region [@Donovan2020; @Zhao2014] (**Figure 7**).
+However, E2A and E2B transcripts have distinct TTSs, with E2B transcripts sharing the TTS of the IVa2 transcript of the IM region similar to MAdVs [@Donovan2020; @Zhao2014] (**Figure 7**).
 
@@
 TRXPT_7 has the CP for both classical proteins (pTP and Ad-pol) encoded in this region, with the pTP ORF predicted to be spliced from two exons.
-The predicted splice junction of pTP is corroborated by our data but the full transcript is markedly longer than the predicted ORF, although, the encoded product (pTP) remains unchanged.
-Ad-pol (polymerase) is encoded downstream of pTP with secondary SC (secSC) usage.
+The predicted splice junction of pTP is corroborated by our data but the full transcript is markedly longer than the predicted ORF, although the encoded product (pTP) remains unchanged.
+Ad-pol (polymerase) is encoded downstream of pTP with secondary start codon (secSC) usage.
 The CP of TRXPT_6 slightly differs from TRXPT_7 because a new STC resulting from the extra splice site forms a minimal truncation of the Ad-pol encoded from its secSC.
@@
 However, some E3 transcripts use the TSS of the MLP.
-Due to sharing the same TSS, in MAdVs, secSC usage is heavily relied on for gene expression in this region as utilizing only the first SC cannot produce the downstream transcripts in this TU.
+Due to sharing the same TSS, in MAdVs, secSC usage is heavily relied on for gene expression in this region as utilizing only the first SC cannot produce the downstream proteins in this TU.
 The 12.5K ORF and transcripts using the MLP TSS are exceptions [@Donovan2020].
@@
 In addition to corroborating the splice junctions for the aforementioned transcripts, the Sanger sequencing results also showed a distinct splice variant undetected in our RNA-seq transcriptome.
-This was a three-exon transcript (TRXPT_30) with identical first and last exons as TRXPT_23, but also contained the second exon of TRXPT_24 (**Figure 8**).
+This was a three-exon transcript (TRXPT_30) with identical first and last exons as TRXPT_23, which also contained the second exon of TRXPT_24 (**Figure 8**).
 TRXPT_30 encodes a novel 140 residue, 15.7kDa protein (e22K), spanning all three exons.
@@
 This TU is found at the 3'-end of the genome and expressed on the anti-sense strand.
-Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the anti-sense strand nor transcribed from a promoter in the E4 region; hence, we only classify ORF8 in this TU.
+Based on nucleotide position, ORF7 and ORF8 were predicted in this region [@Davison2003]; however, as ORF7 is neither on the anti-sense strand nor transcribed from a promoter in the E4 region, we only classify ORF8 in this TU.
 This is corroborated by our RNA-seq data, showing only one transcript in this region on the anti-sense strand (**Figure 9**).
@@
 They both encode pVII as the 5'-most ORF and also have the CP for pX, pVI, hexon, a longer variant of protease (eProt) from an upstream in-frame SC, and ORF12 (a novel 120 residue protein).
-Additionally they have the CP for pVIII and eE3.
+Additionally, they have the CP for pVIII and eE3.
 TRXPT_11 encodes hexon as its 5'-most ORF and also has the CP for eProt, ORF12, e33K, pVIII and eE3.
@@
 
-## DISCUSSION/CONCLUSIONS
+## DISCUSSION
 
@@
 Given the temporal regulation of AdVs gene expression, we anticipated distinct differences in read pileups over the genome at different time points, indicating the different stages of infection.
-This probably due to the infection not being well-synchronized, leading to transcripts overlapping the time points.
+This may be due to an unsynchronized infection, leading to transcripts overlapping the time points.
 Further research is required to determine the precise temporal regulation of THEV.
@@
 It is unlikely that the entire repertoire of mRNA produced via this mechanism will actually be translated.
-However, it has been speculated that the plasticity in alternative RNA splicing enables AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions, confering an evolutionary advantage [@Donovan2020; @Westergren2021].
+However, it has been speculated that the plasticity in alternative RNA splicing enables AdVs to fine-tune protein synthesis by providing different alternatively spliced variants encoding the same protein under changing conditions, conferring an evolutionary advantage [@Donovan2020; @Westergren2021].
 
@@
 
-## MATERIALS AND METHODS
+## METHODS
 

### 2024-05-09 manuscript_thev_transcriptome.tex
second round of edits after jvi review

@@
 \hypersetup{
-  pdftitle={Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line},
+  pdftitle={Characterizing the Splice Map of Turkey Hemorrhagic Enteritis Virus},
   hidelinks,
@@
 
-\title{Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis
-Virus in a Turkey B-cell Line}
+\title{Characterizing the Splice Map of Turkey Hemorrhagic Enteritis
+Virus}
 \author{}
@@
 
-\textbf{Running Title:} Novel Insights into Turkey Hemorrhagic Enteritis
-Virus Transcriptome
-
-\vspace{10mm}
-
-Abraham Quaye\textsuperscript{1*}, Brett E. Pickett\textsuperscript{*},
-Joel S. Griffitts\textsuperscript{*}, Bradford K.
-Berges\textsuperscript{*}, Brian D.
-Poole\({^\dagger}\)\textsuperscript{*}
+Abraham Quaye\({^\dagger}\)\textsuperscript{,a}, Brett E.
+Pickett\textsuperscript{a}, Joel S. Griffitts\textsuperscript{a},
+Bradford K. Berges\textsuperscript{a}, Brian D.
+Poole\textsuperscript{a,*}
 
@@
 
-\textsuperscript{*}Department of Microbiology and Molecular Biology,
+\textsuperscript{a}Department of Microbiology and Molecular Biology,
 Brigham Young University\\
-\textsuperscript{1}First-author\\
-\({^\dagger}\) Corresponding Author
+\({^\dagger}\)First-author\\
+\textsuperscript{*}Corresponding Author
 
@@
 (THEV) is an essential step that would allow studies of individual genes
-mediating its immunosuppressive functions. We used an RNA-sequencing
-experiment to characterize the transcriptome of THEV for the first time,
-providing key insight into the THEV gene expression and mRNA structures.
-Researchers previously annotated the genome of THEV as encoding 23 open
-reading frames (ORFs). In this work we identified 29 spliced transcripts
-all of which consisted of novel exons although some exons matched some
-previously annotated ORFs. The three annotated splice junctions were
-also corroborated by our data. We performed PCR amplification of THEV
-cDNA, cloned the PCR products, and used Sanger sequencing to validate
-all identified splice junctions. During validation we identified five
+mediating its immunosuppressive functions. We used RNA sequencing to
+characterize the transcriptome of THEV for the first time, providing key
+insights into the THEV gene expression and mRNA structures. Researchers
+previously annotated the genome of THEV as encoding 23 open reading
+frames (ORFs). In this work we identified 29 spliced transcripts all of
+which contained novel exons although some exons matched some previously
+annotated ORFs. The three annotated splice junctions were also
+corroborated by our data. We performed PCR amplification of THEV cDNA,
+cloned the PCR products, and used Sanger sequencing to validate all
+identified splice junctions. During validation we identified five
 additional unique transcripts, a subset of which were further validated
@@
 translated. Similar to other adenoviruses (AdVs), THEV also produces
-multiple distinctly spliced transcripts that code for the same proteins
-across its genome. Our data show that all THEV transcripts are spliced
-and organized into five transcription units under the control of their
-cognate promoters like other AdVs. \newpage
+multiple distinctly spliced transcripts that code for the same protein.
+Our data show that all THEV transcripts are spliced and organized into
+five transcription units under the control of their cognate promoters
+like other AdVs. \newpage
 
@@
 of mRNA transcripts produced via alternative splicing in the unit (10,
-17, 18). The promoters are activated at different phases of the
-infection by proteins from previously activated TUs. Paradoxically, the
-early-to-late phase transition during infection requires the L4 gene
-products, 22K and 33K, which should only be available after the
-transition. However, a promoter in the L4 region (L4P) that directs the
-expression of these two proteins independent of the MLP was found,
-resolving the paradox (10, 17, 21). During translation of AdV mRNA,
-recent studies using long-read direct RNA sequencing strongly suggest
-the potential usage of secondary start codons; adding to what was
-already a highly complex system for gene expression (17, 22).
+17, 18). The promoters are activated at different phases of infection by
+proteins from previously activated TUs. Paradoxically, the early-to-late
+phase transition during infection requires the L4 gene products, 22K and
+33K, which should only be available after the transition. However, a
+promoter in the L4 region (L4P) that directs the expression of these two
+proteins independent of the MLP was found, resolving the paradox (10,
+17, 21). During translation of AdV mRNA, recent studies using long-read
+direct RNA sequencing strongly suggest the potential usage of secondary
+start codons; adding to what was already a highly complex system for
+gene expression (17, 22).
 
@@
 only a single TSS (E2 TSS; 18,751 bp) for both E2A and E2B transcripts
-in THEV. However, similar to MAdVs, E2A and E2B transcripts have
-distinct TTSs, with E2B transcripts sharing the TTS of the IVa2
-transcript of the IM region (17, 18) (\textbf{Figure 7}).
+in THEV. However, E2A and E2B transcripts have distinct TTSs, with E2B
+transcripts sharing the TTS of the IVa2 transcript of the IM region
+similar to MAdVs (17, 18) (\textbf{Figure 7}).
 
@@
 junction of pTP is corroborated by our data but the full transcript is
-markedly longer than the predicted ORF, although, the encoded product
+markedly longer than the predicted ORF, although the encoded product
 (pTP) remains unchanged. Ad-pol (polymerase) is encoded downstream of
-pTP with secondary SC (secSC) usage. The CP of TRXPT\_6 slightly differs
-from TRXPT\_7 because a new STC resulting from the extra splice site
-forms a minimal truncation of the Ad-pol encoded from its secSC.
+pTP with secondary start codon (secSC) usage. The CP of TRXPT\_6
+slightly differs from TRXPT\_7 because a new STC resulting from the
+extra splice site forms a minimal truncation of the Ad-pol encoded from
+its secSC.
 
@@
 region as utilizing only the first SC cannot produce the downstream
-transcripts in this TU. The 12.5K ORF and transcripts using the MLP TSS
-are exceptions (17).
+proteins in this TU. The 12.5K ORF and transcripts using the MLP TSS are
+exceptions (17).
 
@@
 was a three-exon transcript (TRXPT\_30) with identical first and last
-exons as TRXPT\_23, but also contained the second exon of TRXPT\_24
+exons as TRXPT\_23, which also contained the second exon of TRXPT\_24
 (\textbf{Figure 8}). TRXPT\_30 encodes a novel 140 residue, 15.7kDa
@@
 however, as ORF7 is neither on the anti-sense strand nor transcribed
-from a promoter in the E4 region; hence, we only classify ORF8 in this
-TU. This is corroborated by our RNA-seq data, showing only one
-transcript in this region on the anti-sense strand (\textbf{Figure 9}).
-The transcript (TRXPT\_28) spans 25192-26247 bp and is spliced at
-25701-26055 bp, forming a two-exon transcript. The second exon fully
-matches the predicted ORF8 with 12 extra base pairs at the 3'-end.
-However, we identified a SC 192 bp upstream of the predicted SC in the
-first exon from which an in-frame protein is encoded. We consider this
-longer isoform (eORF8 -- 26.4 kDa, 229 residues) as the genuinely
-expressed ORF. We also identified a canonical PAS 11 bp upstream of TTS
+from a promoter in the E4 region, we only classify ORF8 in this TU. This
+is corroborated by our RNA-seq data, showing only one transcript in this
+region on the anti-sense strand (\textbf{Figure 9}). The transcript
+(TRXPT\_28) spans 25192-26247 bp and is spliced at 25701-26055 bp,
+forming a two-exon transcript. The second exon fully matches the
+predicted ORF8 with 12 extra base pairs at the 3'-end. However, we
+identified a SC 192 bp upstream of the predicted SC in the first exon
+from which an in-frame protein is encoded. We consider this longer
+isoform (eORF8 -- 26.4 kDa, 229 residues) as the genuinely expressed
+ORF. We also identified a canonical PAS 11 bp upstream of TTS
 (\textbf{Supplementary Table S2}).
@@
 longer variant of protease (eProt) from an upstream in-frame SC, and
-ORF12 (a novel 120 residue protein). Additionally they have the CP for
+ORF12 (a novel 120 residue protein). Additionally, they have the CP for
 pVIII and eE3. TRXPT\_11 encodes hexon as its 5'-most ORF and also has
@@
 
-\subsection{DISCUSSION/CONCLUSIONS}\label{discussionconclusions}
+\subsection{DISCUSSION}\label{discussion}
 
@@
 different time points, indicating the different stages of infection.
-This probably due to the infection not being well-synchronized, leading
-to transcripts overlapping the time points. Further research is required
-to determine the precise temporal regulation of THEV.
+This may be due to an unsynchronized infection, leading to transcripts
+overlapping the time points. Further research is required to determine
+the precise temporal regulation of THEV.
 
@@
 fine-tune protein synthesis by providing different alternatively spliced
-variants encoding the same protein under changing conditions, confering
+variants encoding the same protein under changing conditions, conferring
 an evolutionary advantage (17, 22).
@@
 
-\subsection{MATERIALS AND METHODS}\label{materials-and-methods}
+\subsection{METHODS}\label{methods}
 

### 2024-05-09 scripts/r/plot_fig6_10.R

@@ -9,8 +9,13 @@ source("scripts/r/reg_by_reg_plots.R")
 # function to plot figures
 plot_figs <- function(trxpt_table, trxpt_plot){
   
-  set_flextable_defaults(font.size = 7)
+  df_name <- deparse(substitute(trxpt_table))
+  t_fnt <- 12
+  t_width <- ifelse(df_name == "reg_mlp_brkdown", 0.1, 0.6)
+  t_id_width <- ifelse(df_name == "reg_mlp_brkdown", 2, 1.2)
   
+  set_flextable_defaults(font.size = t_fnt)
+
   # prepare junction table
   junc_tab <- trxpt_table %>%
     flextable(.,
@@ -30,8 +35,11 @@ plot_figs <- function(trxpt_table, trxpt_plot){
                    colwidths = c(1, 3, 1, 4, 1)) %>%
     flextable::vline(j = c(1, 4, 5, 9),
                      border = fp_border_default(color = "grey", width = 1.5)) %>%
-    flextable::font(part = "all", fontname = "Arial")
-  
+    flextable::font(part = "all", fontname = "Arial") %>%
+    flextable::width(width = t_width) %>%
+    flextable::width(width = t_id_width, j = "trxpt_id") %>%
+    flextable::fontsize(size = t_fnt, part = "all")
+
   if ("TRXPT_1, TRXPT_4" %in% pull(trxpt_table, trxpt_id)){
     junc_tab <- junc_tab %>%
     footnote(., i = 1, j = 10, value = as_paragraph(c("Not validated for TRXPT_4")),
@@ -39,7 +47,7 @@ plot_figs <- function(trxpt_table, trxpt_plot){
   }
   
   # combine with trxpt plot
-  return(trxpt_plot / plot_spacer()/ gen_grob(junc_tab, fit = "auto", scaling = "full"))
+  return(trxpt_plot / plot_spacer()/ gen_grob(junc_tab, fit = "auto", scaling = F))
 }
 
 # Figure 6
@@ -48,7 +56,7 @@ fig6 <- plot_figs(reg_e1_brkdown, brkdwn_e1_trxtps) +
 
 # Figure 7
 fig7 <- plot_figs(reg_e2_brkdown, brkdwn_e2_trxtps) +
-  plot_layout(heights = c(1.2, 0.05, 1.5))
+  plot_layout(heights = c(1, 0.05, 1))
 
 # Figure 8
[…]

### 2024-05-09 scripts/r/reg_by_reg_plots.R

@@ -325,7 +325,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part, trxpt_part2=NULL){
     if(trxptome_part == "E4"){
       x_axis_start <- x_axis_start - (x_axis_start * 0.01)
     }else if(trxptome_part == "E2"){
-      x_axis_start <- x_axis_start - (x_axis_start * 0.2)
+      x_axis_start <- x_axis_start - (x_axis_start * 0.25)
     }else{x_axis_start <- x_axis_start - (x_axis_start * 0.03)}
     x_axis_start <- plyr::round_any(x_axis_start, 100)
   } else{x_axis_start <- 0}
@@ -380,6 +380,7 @@ plot_full_trxptome <- function(combined_gtf, trxptome_part, trxpt_part2=NULL){
                        labels = paste0(seq(0,26, 2), "kb")) +
     scale_y_continuous(expand = c(0.01,0.01),
                        limits = y_lims) +
+    coord_cartesian(clip = "off") +
     theme(plot.margin = margin(rep(20, 4)),
           plot.background = element_rect(fill = "#ffffff", color = c("grey")),
           panel.background = element_rect(fill = "#ffffff"),

### 2024-05-12 manuscript_thev_transcriptome.Rmd
all edits made prior to committee second edits after jvi submission

@@
 ## ABSTRACT   
+**Background:** Hemorrhagic enteritis, caused by _Turkey Hemorrhagic Enteritis Virus (THEV)_, is a disease affecting turkey poults characterized by immunosuppression and bloody diarrhea.
+An avirulent THEV strain that retains the immunosuppressive ability is used as a live vaccine.
+Characterizing the splice map of THEV is an essential step that would allow studies of individual genes mediating its immunosuppressive functions.
+We used RNA sequencing to characterize the splice map of THEV for the first time, providing key insights into the THEV gene expression and mRNA structures.
+**Methods:** After infecting a turkey B-cell line with the vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
+Total RNA was extracted and poly-A-tailed mRNA sequenced.
+Reads were mapped to the THEV genome after trimming and transcripts assembled with StringTie.
+We performed PCR of THEV cDNA, cloned the PCR products, and used Sanger sequencing to validate all identified splice junctions.
+**Results:** Researchers previously annotated the THEV genome as encoding 23 open reading frames (ORFs).
+We identified 29 spliced transcripts from our RNA sequencing data, all containing novel exons although some exons matched some previously annotated ORFs.
+The three annotated splice junctions were also corroborated by our data.
+During validation we identified five additional unique transcripts, a subset of which were further validated by 3' rapid amplification of cDNA ends (3' RACE).
+Thus, we report that the genome of THEV contains 34 transcripts with the coding capacity for all annotated ORFs.
+However, we found six of the previously annotated ORFs to be truncated ORFs on the basis of the identification of an in-frame upstream start codon or the detection of additional coding exons.
+We also identified three of the annotated ORFs with longer or shorter isoforms, and seven novel unannotated ORFs that could potentially be translated; although it is beyond the scope of this manuscript to investigate whether they are translated.
+**Conclusions:** Similar to human adenoviruses, all THEV transcripts are spliced and organized into five transcription units under the control of their cognate promoters.
+The genes are expressed under temporal regulation and THEV also produces multiple distinctly spliced transcripts that code for the same protein.
 
-Characterizing the splice map of turkey hemorrhagic enteritis virus (THEV) is an essential step that would allow studies of individual genes mediating its immunosuppressive functions.
-We used RNA sequencing to characterize the transcriptome of THEV for the first time, providing key insights into the THEV gene expression and mRNA structures.
-Researchers previously annotated the genome of THEV as encoding 23 open reading frames (ORFs).
-In this work we identified 29 spliced transcripts all of which contained novel exons although some exons matched some previously annotated ORFs.
-The three annotated splice junctions were also corroborated by our data.
-We performed PCR amplification of THEV cDNA, cloned the PCR products, and used Sanger sequencing to validate all identified splice junctions.
-During validation we identified five additional unique transcripts, a subset of which were further validated by 3' rapid amplification of cDNA ends (3' RACE) experiments.
-Thus, we report that the genome of THEV contains 34 transcripts with the coding capacity for all annotated ORFs.
-However, we found six of the previously annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated ORFs on the basis of the identification of an in-frame upstream start codon or the detection of additional coding exons.
-We also identified three of the annotated ORFs with longer or shorter isoforms, and seven novel unannotated ORFs that could potentially be translated; although it is beyond the scope of this manuscript to investigate whether they are translated.
-Similar to other adenoviruses (AdVs), THEV also produces multiple distinctly spliced transcripts that code for the same protein.
-Our data show that all THEV transcripts are spliced and organized into five transcription units under the control of their cognate promoters like other AdVs.
+## KEY WORDS
+Alternative splicing, Turkey hemorrhagic enteritis virus, Adenovirus, Transcriptome, RNA sequencing.
 \newpage
 
-## INTRODUCTION
+## BACKGROUND
 
@@
 
-While the advent of next-generation sequencing has rendered easier the study of large and complex eukaryotic transcriptomes, studying the smaller, compact viral transcriptomes remains unintuitively challenging, as the transcripts typically have significant overlaps due to genome economization.
+While the advent of next-generation sequencing has rendered easier the study of large and complex eukaryotic transcriptomes, studying the smaller, compact viral transcriptomes is counterintuitively more challenging, as the transcripts typically have significant overlaps due to genome economization.
 AdV transcriptomes escalate the difficulty due to the wide array of mRNAs produced via very complex alternative splicing and polyadenylation, all initiated from relatively few promoters.
@@
 
-In summary, the THEV transcriptome bears remarkable similarity to the better-studied MAdVs.
+## CONCLUSIONS
+
+The THEV transcriptome bears remarkable similarity to the better-studied MAdVs.
 The transcriptome is organized into five TUs, with temporal regulation divided into early and late genes, and a broad repertoire of transcripts are produced via virtually unlimited alternative splicing.
@@
 Namely, the TPL, the so-called x, y, and z leaders, and the i-leader are 5' leaders utilized by MAdV MLTU mRNAs.
-The absence of these non-TPL leaders in our data could mean that the 5'-UTR diversity of THEV's MLTU mRNAs is more limited due to its smaller genome size or future studies using long read sequencing technologies could uncover more variety not seen in our results.
+The absence of these non-TPL leaders in our data could mean that the 5'-UTR diversity of THEV's MLTU mRNAs is more limited due to its smaller genome size or future studies could uncover more variety not seen in our results.
+Being the first transcriptomic characterization of THEV, this work should serve as useful resource to future THEV gene expression and transcriptomic studies, especially, mapping the mRNA splice sites.
 \newpage
@@
 See **Supplementary Computational Analysis** for the details of transcript expression level estimations and splice junction read counts.
+\newpage
 
-### DATA AVAILABILITY
+## LIST OF ABBREVIATIONS  
+```{r list_abbs}
+set_flextable_defaults(font.size = 10)
+tribble(~Abbreviation, ~Definition,
+               "AdV", "Adenovirus",
+               "MAdV", "Mastadenovirus",
+               "SiAdV", "Siadenovirus",
+               "THEV", "Turkey Hemorrhagic Enteritis Virus",
+              "HE", "Hemorrhagic Enteritis",
+              "UTR", "Untranslated Region",
+              "TU", "Transcription Unit",
+              "L4P", "L4 Promoter",
+              "MLP", "Major Late Promter",
+              "E3P", "E3 Promoter",
+              "hpi", "Hours Post-infection",
+              "qPCR", "Quantitative Polymerase Chain Reaction",
+              "FPKM", "Fragments Per Kilobase of transcript per Million mapped reads",
+              "CP", "Coding Potential",
+              "TSS", "Transcription Start Site",
+              "TTS", "Transcription Termination Site",
+              "SC", "Start Codon", 
+              "STC", "Stop Codon",
+              "secSC", "Secondary Start Codon",
+              "secSTC", "Secondary Stop Codon",
+              "ORF", "Open Reading Frame", 
+              "CDS", "Coding Sequence", 
+              "MLTU", "Major Late Transcription Unit",
+              "TPL", "Tripartite Leader",
+              "sTPL", "Short Tripartite Leader",
+              "TPL3", "Third exon of Tripartite Leader",
+              "GCN", "Genome Copy Number") %>%
+  flextable::flextable() %>%
+  flextable::theme_box() %>%
+  flextable::width(width = 1, j = 1) %>%
+  flextable::width(width = 2, j = 2) %>%
+  flextable::align(align = "center", part = "all")
+```
+
+## DATA AVAILABILITY
 
@@
 
-```{r}
+```{r table1}
 #| tab.id: NULL
@@
 **Supplementary Table S1A**
-
 ```{r Sup Table S1A}
@@
 **Supplementary Table S1B**
-
 ```{r Sup Table S1B}
@@
 **Supplementary Table S1C**
-
 ```{r Sup Table S1C}
@@
 **Supplementary Table S2**
-
 ```{r}

### 2024-05-12 manuscript_thev_transcriptome.tex
all edits made prior to committee second edits after jvi submission

@@
 
-Characterizing the splice map of turkey hemorrhagic enteritis virus
-(THEV) is an essential step that would allow studies of individual genes
-mediating its immunosuppressive functions. We used RNA sequencing to
-characterize the transcriptome of THEV for the first time, providing key
-insights into the THEV gene expression and mRNA structures. Researchers
-previously annotated the genome of THEV as encoding 23 open reading
-frames (ORFs). In this work we identified 29 spliced transcripts all of
-which contained novel exons although some exons matched some previously
-annotated ORFs. The three annotated splice junctions were also
-corroborated by our data. We performed PCR amplification of THEV cDNA,
+\textbf{Background:} Hemorrhagic enteritis, caused by \emph{Turkey
+Hemorrhagic Enteritis Virus (THEV)}, is a disease affecting turkey
+poults characterized by immunosuppression and bloody diarrhea. An
+avirulent THEV strain that retains the immunosuppressive ability is used
+as a live vaccine. Characterizing the splice map of THEV is an essential
+step that would allow studies of individual genes mediating its
+immunosuppressive functions. We used RNA sequencing to characterize the
+splice map of THEV for the first time, providing key insights into the
+THEV gene expression and mRNA structures.\\
+\textbf{Methods:} After infecting a turkey B-cell line with the vaccine
+strain, samples in triplicates were collected at 4-, 12-, 24-, and
+72-hours post-infection. Total RNA was extracted and poly-A-tailed mRNA
+sequenced. Reads were mapped to the THEV genome after trimming and
+transcripts assembled with StringTie. We performed PCR of THEV cDNA,
 cloned the PCR products, and used Sanger sequencing to validate all
-identified splice junctions. During validation we identified five
-additional unique transcripts, a subset of which were further validated
-by 3' rapid amplification of cDNA ends (3' RACE) experiments. Thus, we
-report that the genome of THEV contains 34 transcripts with the coding
-capacity for all annotated ORFs. However, we found six of the previously
-annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated
-ORFs on the basis of the identification of an in-frame upstream start
-codon or the detection of additional coding exons. We also identified
-three of the annotated ORFs with longer or shorter isoforms, and seven
-novel unannotated ORFs that could potentially be translated; although it
-is beyond the scope of this manuscript to investigate whether they are
-translated. Similar to other adenoviruses (AdVs), THEV also produces
-multiple distinctly spliced transcripts that code for the same protein.
-Our data show that all THEV transcripts are spliced and organized into
-five transcription units under the control of their cognate promoters
-like other AdVs. \newpage
-
-\subsection{INTRODUCTION}\label{introduction}
+identified splice junctions.\\
+\textbf{Results:} Researchers previously annotated the THEV genome as
+encoding 23 open reading frames (ORFs). We identified 29 spliced
+transcripts from our RNA sequencing data, all containing novel exons
+although some exons matched some previously annotated ORFs. The three
+annotated splice junctions were also corroborated by our data. During
+validation we identified five additional unique transcripts, a subset of
+which were further validated by 3' rapid amplification of cDNA ends (3'
+RACE). Thus, we report that the genome of THEV contains 34 transcripts
+with the coding capacity for all annotated ORFs. However, we found six
+of the previously annotated ORFs to be truncated ORFs on the basis of
+the identification of an in-frame upstream start codon or the detection
+of additional coding exons. We also identified three of the annotated
+ORFs with longer or shorter isoforms, and seven novel unannotated ORFs
+that could potentially be translated; although it is beyond the scope of
+this manuscript to investigate whether they are translated.\\
+\textbf{Conclusions:} Similar to human adenoviruses, all THEV
+transcripts are spliced and organized into five transcription units
+under the control of their cognate promoters. The genes are expressed
+under temporal regulation and THEV also produces multiple distinctly
+spliced transcripts that code for the same protein.
+
+\subsection{KEY WORDS}\label{key-words}
+
+Alternative splicing, Turkey hemorrhagic enteritis virus, Adenovirus,
+Transcriptome, RNA sequencing. \newpage
+
+\subsection{BACKGROUND}\label{background}
 
@@
 study of large and complex eukaryotic transcriptomes, studying the
-smaller, compact viral transcriptomes remains unintuitively challenging,
-as the transcripts typically have significant overlaps due to genome
-economization. AdV transcriptomes escalate the difficulty due to the
-wide array of mRNAs produced via very complex alternative splicing and
-polyadenylation, all initiated from relatively few promoters. Standard
-RNA-seq analysis programs, not primarily designed for such compact,
-gene-dense, and complex transcriptomes, further compound this challenge.
-Furthermore, in our case, no prior transcriptomic studies for THEV
-exist. Our approach combines standard RNA-seq analysis programs with
-custom analyses and experimentally validating all splice junctions with
-independent methods. The transcript map for THEV produced from our
-analysis is strikingly similar to that of the MAdVs.
+smaller, compact viral transcriptomes is counterintuitively more
+challenging, as the transcripts typically have significant overlaps due
+to genome economization. AdV transcriptomes escalate the difficulty due
+to the wide array of mRNAs produced via very complex alternative
+splicing and polyadenylation, all initiated from relatively few
+promoters. Standard RNA-seq analysis programs, not primarily designed
+for such compact, gene-dense, and complex transcriptomes, further
+compound this challenge. Furthermore, in our case, no prior
+transcriptomic studies for THEV exist. Our approach combines standard
+RNA-seq analysis programs with custom analyses and experimentally
+validating all splice junctions with independent methods. The transcript
+map for THEV produced from our analysis is strikingly similar to that of
+the MAdVs.
 
@@
 
-In summary, the THEV transcriptome bears remarkable similarity to the
-better-studied MAdVs. The transcriptome is organized into five TUs, with
-temporal regulation divided into early and late genes, and a broad
-repertoire of transcripts are produced via virtually unlimited
-alternative splicing. However, the THEV transcriptome appears less
-sophisticated (i.e, it encodes fewer genes) than MAdVs, primarily
-because the MAdV genomes are close to twice as long as that of THEV. The
-lack of subdivision of the E1 region into E1a and E1b is one of the most
-obvious examples. Also, the MAdV E4 region encodes several proteins
-unlike in THEV where only one transcript encoding one protein was found.
-The complexity of the MLTU leader sequences is another example. While
-the majority of the THEV MLTU transcripts begin with the TPL just like
-MAdVs with a small subset using a variant leader sequence (sTPL),
-significantly more diverse 5'-UTRs are employed for MAdV MLTU
-transcripts. Namely, the TPL, the so-called x, y, and z leaders, and the
-i-leader are 5' leaders utilized by MAdV MLTU mRNAs. The absence of
-these non-TPL leaders in our data could mean that the 5'-UTR diversity
-of THEV's MLTU mRNAs is more limited due to its smaller genome size or
-future studies using long read sequencing technologies could uncover
-more variety not seen in our results. \newpage
+\subsection{CONCLUSIONS}\label{conclusions}
+
+The THEV transcriptome bears remarkable similarity to the better-studied
+MAdVs. The transcriptome is organized into five TUs, with temporal
+regulation divided into early and late genes, and a broad repertoire of
+transcripts are produced via virtually unlimited alternative splicing.
+However, the THEV transcriptome appears less sophisticated (i.e, it
+encodes fewer genes) than MAdVs, primarily because the MAdV genomes are
+close to twice as long as that of THEV. The lack of subdivision of the
+E1 region into E1a and E1b is one of the most obvious examples. Also,
+the MAdV E4 region encodes several proteins unlike in THEV where only
+one transcript encoding one protein was found. The complexity of the
+MLTU leader sequences is another example. While the majority of the THEV
+MLTU transcripts begin with the TPL just like MAdVs with a small subset
+using a variant leader sequence (sTPL), significantly more diverse
+5'-UTRs are employed for MAdV MLTU transcripts. Namely, the TPL, the
+so-called x, y, and z leaders, and the i-leader are 5' leaders utilized
+by MAdV MLTU mRNAs. The absence of these non-TPL leaders in our data
+could mean that the 5'-UTR diversity of THEV's MLTU mRNAs is more
+limited due to its smaller genome size or future studies could uncover
+more variety not seen in our results. Being the first transcriptomic
+characterization of THEV, this work should serve as useful resource to
+future THEV gene expression and transcriptomic studies, especially,
+mapping the mRNA splice sites. \newpage
 
@@
 transcript expression level estimations and splice junction read counts.
-
-\subsubsection{DATA AVAILABILITY}\label{data-availability}
+\newpage
+
+\subsection{LIST OF ABBREVIATIONS}\label{list-of-abbreviations}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{1.00in}|p{2.00in}}
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Abbreviation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Definition}}}} \\
+
+\ascline{0.75pt}{666666}{1-2}\endfirsthead
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Abbreviation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Definition}}}} \\
+
+\ascline{0.75pt}{666666}{1-2}\endhead
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{AdV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Adenovirus}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MAdV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Mastadenovirus}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SiAdV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Siadenovirus}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{THEV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Turkey\ Hemorrhagic\ Enteritis\ Virus}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{HE}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hemorrhagic\ Enteritis}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{UTR}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Untranslated\ Region}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TU}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Transcription\ Unit}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{L4P}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{L4\ Promoter}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MLP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Major\ Late\ Promter}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{E3P}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{E3\ Promoter}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{hpi}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hours\ Post-infection}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{qPCR}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Quantitative\ Polymerase\ Chain\ Reaction}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{FPKM}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Fragments\ Per\ Kilobase\ of\ transcript\ per\ Million\ mapped\ reads}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{CP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coding\ Potential}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TSS}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Transcription\ Start\ Site}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TTS}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Transcription\ Termination\ Site}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Start\ Codon}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{STC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Stop\ Codon}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{secSC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Secondary\ Start\ Codon}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{secSTC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Secondary\ Stop\ Codon}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Open\ Reading\ Frame}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{CDS}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coding\ Sequence}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MLTU}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Major\ Late\ Transcription\ Unit}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TPL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Tripartite\ Leader}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{sTPL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Short\ Tripartite\ Leader}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TPL3}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Third\ exon\ of\ Tripartite\ Leader}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{GCN}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Genome\ Copy\ Number}}} \\
+
+\ascline{0.75pt}{666666}{1-2}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+\subsection{DATA AVAILABILITY}\label{data-availability}
 

### 2024-07-09 manuscript_thev_transcriptome.Rmd
addressed reviewer comments from virology journal

@@
 **Methods:** After infecting a turkey B-cell line with the vaccine strain, samples in triplicates were collected at 4-, 12-, 24-, and 72-hours post-infection.
-Total RNA was extracted and poly-A-tailed mRNA sequenced.
+Total RNA was extracted, and poly-A-tailed mRNA sequenced.
 Reads were mapped to the THEV genome after trimming and transcripts assembled with StringTie.
@@
 The genes are expressed under temporal regulation and THEV also produces multiple distinctly spliced transcripts that code for the same protein.
+Studies of the newly identified potential proteins should be urgently performed as these proteins may have roles in THEV-induced immunosuppression.
+Also, knowing the splicing of THEV genes should be invaluable to future research focusing of studying THEV genes, as this will allow accurate cloning of the mRNAs.
 
@@
 The family *Adenoviridae* consists of five genera: *Mastadenovirus* (MAdV), *Aviadenovirus*, *Atadenovirus*, *Ichtadenovirus*, and *Siadenovirus* (SiAdV) to which turkey adenovirus 3 also called turkey hemorrhagic enteritis virus (THEV) belongs [@Harrach2011; @Kovács2011; @Davison2000; @Kovács2010; @Katoh2009; @Guimet2016].
-Members of SiAdV have the smallest genome size (\~26 kb) and gene content of all known AdVs (see **Figure 1**) [@Harrach2008; @Kovács2011; @Davison2003].
+Members of SiAdV have the smallest genome size (\~26 kb) and gene content of all known AdVs, with five genus-specific genes of undefined functions (see **Figure 1**) [@Harrach2008; @Kovács2011; @Davison2003].
 
@@
 Thus, vaccinated birds are rendered more susceptible to opportunistic infections and death than unvaccinated birds leading to substantial economic losses [@Beach2006; @Rautenschlein2000; @Larsen1985; @Dhama2017].
-To eliminate the immunosupressive effect of the vaccine strain, a thorough investigation of the culprit viral genes mediating this phenomenon is essential.
+To eliminate the immunosuppressive effect of the vaccine strain, a thorough investigation of the culprit viral genes mediating this phenomenon is essential.
 However, the transcriptome (splicing and gene expression patterns) of THEV has not been characterized, making an investigation of specific immunosuppressive viral genes impractical.
@@
 However, during early infection only a subset of the MLP-derived transcripts are expressed [@Guimet2016].
-MAdV makes an extensive use of alternative RNA splicing to produce a very complex array of mRNAs.
+MAdVs make extensive use of alternative RNA splicing and polyadenylation to produce a very complex array of mRNAs.
 All but the pIX mRNA undergo at least one splicing event.
@@
 demonstrated that nearly all THEV transcripts became detectable starting at 4 hours post-infection (hpi), with one replication cycle concluding around 18 hpi [@Aboezz2019].
-Consequently, we harvested infected MDTC-RP19 cells (MOI of 100 genome copy numbers/cell) at 4-, 12-, 24-, and 72-hpi to capture all transcripts within a broad time window.
+Consequently, we harvested infected MDTC-RP19 cells (multiplicity of infection (MOI) of 100 genome copy numbers/cell) at 4-, 12-, 24-, and 72-hpi to capture all transcripts within a broad time window.
 Our paired-end RNA sequencing (RNA-seq) experiment generated an average of `r avg_tot_count` million total reads of `r seq_len` bp length per time-point.
@@
 The predicted splice junction of pTP is corroborated by our data but the full transcript is markedly longer than the predicted ORF, although the encoded product (pTP) remains unchanged.
-Ad-pol (polymerase) is encoded downstream of pTP with secondary start codon (secSC) usage.
+Ad-pol (polymerase) is encoded downstream of pTP with secondary SC (secSC) usage.
 The CP of TRXPT_6 slightly differs from TRXPT_7 because a new STC resulting from the extra splice site forms a minimal truncation of the Ad-pol encoded from its secSC.
@@
 
-**Major Late Transcription Unit (MLTU) or MLP Region transcripts**   
+**MLTU or MLP Region transcripts**   
 The MLTU transcripts, dominant in the late phase of the AdV infectious cycle, are produced by alternative polyadenylation and splicing of a primary transcript and grouped into five transcript classes (L1-L5).
@@
 Standard RNA-seq analysis programs, not primarily designed for such compact, gene-dense, and complex transcriptomes, further compound this challenge.
-Furthermore, in our case, no prior transcriptomic studies for THEV exist.
+Furthermore, in our case, no prior transcriptomic studies for THEV exist; hence, assembling the transcripts without any prior experimentally-derived annotation of THEV splicing using only short illumina reads proved difficult.
+Lastly, we had initially planned to sequence RNA from another time point (8 hpi); however, all the RNA samples from 8 hpi and one replicate sample from 12 hpi got too degraded during the library preparation steps to be yield any useful data.
+We believe that these would have contributed to better insights into the temporal expression levels and splicing.
 Our approach combines standard RNA-seq analysis programs with custom analyses and experimentally validating all splice junctions with independent methods.
@@
 
-Our work provides the first insights into THEV splicing, revealing 34 transcripts grouped into five transcription units (TUs).
+Our work provides the first insights into THEV splicing, revealing 34 transcripts grouped into five TUs.
 The general temporal gene expression regulation observed in MAdVs, with early regions peaking at earlier time points followed by MLTU predominance at later time points, seems to also apply to THEV.
@@
 However, the substantial overlapping nature of AdV mRNAs and fragmentation during library preparation make it challenging to map the exact TSS, TTS, and PASs of assembled transcripts.
-Also, transcripts with significant overlaps may be assembled as a single, longer mRNA, since the short reads alone do not provide enough context for the transcript assembler (StringTie) to distinguish them.
+As AdVs make heavy use of alternative polyadenylation, short read RNA-seq is ill-equipped to discriminate mRNA variants of the same gene produced via alternative polyadenylation.
+Thus, shorter variants of alternatively polyadenylated mRNAs may potentially be incorporated into the longer variants during transcript assembly, significantly diminishing the diversity of mRNA in the transcriptome.
+Also, independent transcripts with significant overlaps may be assembled as a single, longer mRNA, since the short reads alone do not provide enough context for the transcript assembler (StringTie) to distinguish them.
+Such fusions may affect the transcript expression level estimations by inflating or deflating the expression levels of the transcripts involved, affecting the proper understanding of the temporal gene expression regulation and also the diversity of the transcriptome.
+Transcripts that have reads mistakenly fused with them would have inflated expression levels while those whose reads are counted elsewhere would show false lower expression levels.
+In our case, since we used other independent methods to validate the splice junctions, we believe these drawbacks to be minimized.
 Our results show transcripts in the same TU initiating or terminating in similar areas, but not at the exact same position.
@@
 These mRNAs have unusually many exons and their last few exons are identical to some E3 mRNAs.
-Future studies using long read sequencing technologies will provide more precise mapping of the TSS and TTS and clarify the structures of the long MLTU transcripts.
+Future studies using long read sequencing technologies will provide more precise mapping of the TSS, TTS, and PASs and clarify the structures of the long MLTU transcripts.
 
@@
 And secondly, recent studies [@Donovan2020; @Zhao2014; @Westergren2021] are still discovering novel mRNA variants for even the best studied MAdVs decades later.
+These new potential proteins and isoforms significantly extend the repertoire of THEV gene products than predicted, adding a hefty number of proteins of undefined function to the previously predicted five (See **Figure 1**).
+These new potential proteins and isoforms of unknown functions may mediate or contribute to viral replication efficiency, or the immunosuppression associated with THEV.
+Hence, further studies of these potential proteins is urgently needed.
 
@@
 Ribosomal shunting or jumping mechanism is utilized for MLTU transcripts that have the TPL.
-This mechanism allows the ribosome to translocate to a downstream AUG, under the direction of the shunting elements in the TPL, even if a start codon in a good Kozak sequence context is bypassed.
+This mechanism allows the ribosome to translocate to a downstream AUG, under the direction of the shunting elements in the TPL, even if a SC in a good Kozak sequence context is bypassed.
 Thus, predicting the protein(s) expressed from an AdV mRNA is uncertain as any one of the AUGs may be selected [@Guimet2016; @Westergren2021].
@@
 The absence of these non-TPL leaders in our data could mean that the 5'-UTR diversity of THEV's MLTU mRNAs is more limited due to its smaller genome size or future studies could uncover more variety not seen in our results.
+We also note that although THEV genomic sequences show minimal differences between strains [@Beach2009a], the transcriptomes may have significant variations; hence, our results may vary from other THEV strains.
+Also, performing the study *in vivo* or with primary turkey cells may show different results.
+The potential new proteins identified in our work adds to the number of proteins with undefined functions in THEV; these may have roles in viral replication efficiency, or the immunosuppression associated with THEV.
+Hence, further studies of these proteins and other predicted proteins of unknown function should be useful in elucidating THEV-induced immunosuppression.
 Being the first transcriptomic characterization of THEV, this work should serve as useful resource to future THEV gene expression and transcriptomic studies, especially, mapping the mRNA splice sites.
+More importantly, this work characterizing the splicing of THEV mRNAs will allow researchers to accurately clone any THEV gene(s) of interest to study its potential role in inducing immunosuppression or other functions.
+
 \newpage
@@
 The stock virus was titrated using an in-house qPCR assay with titer expressed as genome copy number (GCN)/mL, similar to Mahshoub *et al* [@Mahsoub2017] with modifications.
-Cells were infected in triplicate at a multiplicity of infection (MOI) of 100 GCN/cell, incubated at 41^o^C for 1 hour, and washed three times with phosphate buffered saline (PBS) to get rid of free virus particles.
+Cells were infected in triplicate at MOI of 100 GCN/cell, incubated at 41^o^C for 1 hour, and washed three times with phosphate buffered saline (PBS) to get rid of free virus particles.
 Triplicate samples were harvested at 4-, 12-, 24-, and 72-hpi for total RNA extraction.
@@
 The novel splice junctions discovered in this work using the StringTie transcript assembler were validated by PCR, cloning, and Sanger Sequencing (**Supplementary PCR methods**).
-Briefly, primers spanning a range of novel exon-exon boundaries for each specific transcript in a transcription unit (TU) were designed.
+Briefly, primers spanning a range of novel exon-exon boundaries for each specific transcript in a TU were designed.
 Universal forward or reverse primers for each respective TU were designed and paired with primers binding specific positions in each transcript.
@@
 Briefly, sequencing reads were trimmed with the Trim-galore - version 0.6.6 [@TrimGalore] program to achieve an overall Mean Sequence Quality (Phred Score) of 36.
-Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent turkey hemorrhagic enteritis virus (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using Hisat2 - version 2.2.1 [@Pertea2016] with default settings.
+Trimmed reads were mapped simultaneously to the complete genomic sequence of avirulent THEV (<https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/>) and *Meleagris gallopavo* (<https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo>) using Hisat2 - version 2.2.1 [@Pertea2016] with default settings.
 The generated binary alignment (BAM) files from each infection time point were filtered for reads mapping to the THEV genome using Samtools - version 1.16.1 and fed into StringTie - version 2.2.1 [@Pertea2016] to assemble the transcripts, using a gene transfer format (GTF) annotation file derived from a gene feature format 3 (GFF3) annotation file obtained from NCBI, which contains the predicted ORFs of THEV as a guide.
@@
 
-We thank the Office of Research Computing at Brigham Young University for granting us access to the high performance computing systems to perform the memory-intensive steps in the analysis pipeline of this work.
+We thank the Office of Research Computing at Brigham Young University for granting us access to the high-performance computing systems to perform the memory-intensive steps in the analysis pipeline of this work.
 \newpage
@@
 pTP, DBP and 33K are predicted to be spliced and are shown as two exons connected with dashed lines.
-Shaded regions indicate regions containing "genus-specific" genes (colored red).
+Shaded regions indicate regions containing the five genus-specific genes of undefined functions (colored red).
 Genes colored in blue are "genus-common".
 The gene colored in light green is conserved in all but Atadenoviruses.
-Regions comprising the different transcription units are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.](results/r/figures/thev_orf_map.png)
+Regions comprising the different TUs are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise the MLTU.](results/r/figures/figure1.png)
 
@@
 The virus titer expands exponentially beginning from 48 hpi, increasing by orders of magnitude before reaching a plateau at 120 hpi.
-GCN: genome copy number.](results/r/figures/fig_2.png)
+GCN: genome copy number.](results/r/figures/figure2.png)
 
@@
 A) Transcriptome of THEV from RNA-seq.** THEV transcripts assembled from all time points by StringTie are unified forming this transcriptome (splicing map).
-Transcripts belonging to the same transcription unit (TU) are located in close proximity on the genome and are color coded and labeled in this figure as such.
+Transcripts belonging to the same TU are located in close proximity on the genome and are color coded and labeled in this figure as such.
 The organization of TUs in the THEV genome is unsurprisingly similar to MAdVs; however, the MAdV genome shows significantly more transcripts.
@@
 Note that the junction read counts are not normalized.
-**D) Relative abundances of junctions in transcriptome grouped by region/TU over time.** This is identical to **(C)**, except that only the junctions found in the full transcriptome obtained from the RNA-seq data were included.](results/r/figures/figure_4a_d.png)
+**D) Relative abundances of junctions in transcriptome grouped by region/TU over time.** This is identical to **(C)**, except that only the junctions found in the full transcriptome obtained from the RNA-seq data were included.](results/r/figures/figure4.png)
 
@@
 At early time points (4h.p.i and 12h.p.i **(A)** and **(B)**, respectively) the junction nucleotides used appear to be well scrutinized or restricted, utilizing mostly the canonical splice nucleotides.
-However, as the infection progresses to the late stages (24h.p.i and 72h.p.i **(C)** and **(D)**, respectively), the selectivity of specific splice acceptor-donor pairs seems to degenerate significantly, such that all combinations of nucleotides are utilized.](results/r/figures/figure_5a_d.png)
+However, as the infection progresses to the late stages (24h.p.i and 72h.p.i **(C)** and **(D)**, respectively), the selectivity of specific splice acceptor-donor pairs seems to degenerate significantly, such that all combinations of nucleotides are utilized.](results/r/figures/figure5.png)
 
-![**Figure 6: The splice map of the E1 transcription unit (TU).** Exons are depicted as boxes connected by introns (dotted lines).
+![**Figure 6: The splice map of the E1 TU.** Exons are depicted as boxes connected by introns (dotted lines).
 Transcripts from RNA-seq data are colored red, predicted ORFs are colored grey, and transcripts or ORFs discovered by other means are colored black.
 Each transcript or ORF is labelled with its name to the right.
-The start codon (SC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The SC and STC of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_6.png)
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure6.png)
 
@@
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_7.png)
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure7.png)
 
@@
 Each transcript or ORF is labelled with its name to the right.
-The start codon (SC) and stop codon (STC) of the 5'-most CDS of each transcript are indicated with the nucleotide position in brackets.
+The SC and STC of the 5'-most CDS of each transcript are indicated with the nucleotide position in brackets.
 Similarly, the secondary SC (secSC) and secondary STC (secSTC) are shown.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_8.png)
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure8.png)
 
@@
 The transcript and ORF are labelled with their names to the right.
-The start codon (SC) and stop codon (STC) of the 5'-most CDS are indicated with the nucleotide position in brackets.
+The SC and STC of the 5'-most CDS are indicated with the nucleotide position in brackets.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junction with its validation status using cloning and Sanger sequencing.](results/r/figures/figure_9.png)
+The table shows sequence reads covering the splice junction with its validation status using cloning and Sanger sequencing.](results/r/figures/figure9.png)
 
@@
 The transcripts and ORFs are labelled with their names to the right.
-The start codon (SC) and stop codon (STC) of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
+The SC and STC of the 5'-most CDS of each transcript is indicated with the nucleotide position in brackets.
 Similarly, the secondary SC (secSC) and secondary STC (secSTC) are shown.
 The region of the virus is depicted at the bottom as a black line with labels of the nucleotide positions for reference.
-The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure_10.png)
+The table shows sequence reads covering the splice junctions with information about their validation status using cloning and Sanger sequencing.](results/r/figures/figure10.png)
 

### 2024-07-09 manuscript_thev_transcriptome.tex
addressed reviewer comments from virology journal

@@
 strain, samples in triplicates were collected at 4-, 12-, 24-, and
-72-hours post-infection. Total RNA was extracted and poly-A-tailed mRNA
+72-hours post-infection. Total RNA was extracted, and poly-A-tailed mRNA
 sequenced. Reads were mapped to the THEV genome after trimming and
@@
 under temporal regulation and THEV also produces multiple distinctly
-spliced transcripts that code for the same protein.
+spliced transcripts that code for the same protein. Studies of the newly
+identified potential proteins should be urgently performed as these
+proteins may have roles in THEV-induced immunosuppression. Also, knowing
+the splicing of THEV genes should be invaluable to future research
+focusing of studying THEV genes, as this will allow accurate cloning of
+the mRNAs.
 
@@
 smallest genome size (\textasciitilde26 kb) and gene content of all
-known AdVs (see \textbf{Figure 1}) (1, 2, 6).
+known AdVs, with five genus-specific genes of undefined functions (see
+\textbf{Figure 1}) (1, 2, 6).
 
@@
 birds leading to substantial economic losses (11, 14--16). To eliminate
-the immunosupressive effect of the vaccine strain, a thorough
+the immunosuppressive effect of the vaccine strain, a thorough
 investigation of the culprit viral genes mediating this phenomenon is
@@
 early infection only a subset of the MLP-derived transcripts are
-expressed (10). MAdV makes an extensive use of alternative RNA splicing
-to produce a very complex array of mRNAs. All but the pIX mRNA undergo
-at least one splicing event. For instance, the MLTU produces over 20
-distinct splice variants all containing three non-coding exons at the
-5'-end (collectively known as the tripartite leader; TPL) (17, 18).
-There is also an alternate three-exon 5' non-coding leader sequence
-present in varying amounts on a subset of MLTU mRNAs (known as the x-,
-y-, and z-leaders). Lastly, there is the i-leader exon, which is
-infrequently included between the second and third TPL exons, and codes
-for the i-leader protein (20). Thus, the MLTU produces a complex
-repertoire of mRNA with diverse 5' untranslated regions (UTRs) spliced
-onto different 3' coding exons which are grouped into five different
-3'-end classes (L1-L5) based on polyadenylation site. Each transcription
-unit (TU) contains its own promoter driving the expression of the array
-of mRNA transcripts produced via alternative splicing in the unit (10,
-17, 18). The promoters are activated at different phases of infection by
-proteins from previously activated TUs. Paradoxically, the early-to-late
-phase transition during infection requires the L4 gene products, 22K and
-33K, which should only be available after the transition. However, a
-promoter in the L4 region (L4P) that directs the expression of these two
-proteins independent of the MLP was found, resolving the paradox (10,
-17, 21). During translation of AdV mRNA, recent studies using long-read
-direct RNA sequencing strongly suggest the potential usage of secondary
-start codons; adding to what was already a highly complex system for
-gene expression (17, 22).
+expressed (10). MAdVs make extensive use of alternative RNA splicing and
+polyadenylation to produce a very complex array of mRNAs. All but the
+pIX mRNA undergo at least one splicing event. For instance, the MLTU
+produces over 20 distinct splice variants all containing three
+non-coding exons at the 5'-end (collectively known as the tripartite
+leader; TPL) (17, 18). There is also an alternate three-exon 5'
+non-coding leader sequence present in varying amounts on a subset of
+MLTU mRNAs (known as the x-, y-, and z-leaders). Lastly, there is the
+i-leader exon, which is infrequently included between the second and
+third TPL exons, and codes for the i-leader protein (20). Thus, the MLTU
+produces a complex repertoire of mRNA with diverse 5' untranslated
+regions (UTRs) spliced onto different 3' coding exons which are grouped
+into five different 3'-end classes (L1-L5) based on polyadenylation
+site. Each transcription unit (TU) contains its own promoter driving the
+expression of the array of mRNA transcripts produced via alternative
+splicing in the unit (10, 17, 18). The promoters are activated at
+different phases of infection by proteins from previously activated TUs.
+Paradoxically, the early-to-late phase transition during infection
+requires the L4 gene products, 22K and 33K, which should only be
+available after the transition. However, a promoter in the L4 region
+(L4P) that directs the expression of these two proteins independent of
+the MLP was found, resolving the paradox (10, 17, 21). During
+translation of AdV mRNA, recent studies using long-read direct RNA
+sequencing strongly suggest the potential usage of secondary start
+codons; adding to what was already a highly complex system for gene
+expression (17, 22).
 
@@
 with one replication cycle concluding around 18 hpi (24). Consequently,
-we harvested infected MDTC-RP19 cells (MOI of 100 genome copy
-numbers/cell) at 4-, 12-, 24-, and 72-hpi to capture all transcripts
-within a broad time window. Our paired-end RNA sequencing (RNA-seq)
-experiment generated an average of 107.1 million total reads of 149 bp
-length per time-point. These reads were concurrently mapped to both the
-virus (THEV) and host (\emph{Meleagris gallopavo}) genomes using the
-Hisat2 (25) reference-based aligner. A total of 18.1 million reads from
-all time-points mapped to the virus genome, providing comprehensive
-coverage and leaving no regions unmapped. The mapped reads to the virus
-genome increased significantly from a scant 432 reads at 4 hpi to 16.9
-million reads at 72 hpi (\textbf{Table 1}, \textbf{Figure 2A}). From
-these mapped reads, we identified 2,457 unique THEV splice junctions
-across all time-points, with later time-points exhibiting significantly
-more sequence reads supporting the splice junctions than earlier
-time-points. For instance, all 13 unique junctions at 4 hpi had fewer
-than 10 supporting reads each, averaging only 2.8 reads per junction. In
-contrast, the 2374 unique junctions at 72 hpi averaged 898.4 reads per
-junction, with some junctions reaching as high as 322,677 reads. The
-marked increase in splice junction and mapping reads to the THEV genome
-over time indicates an active infection and successful viral
-replication, which is corroborated by our quantitative PCR (qPCR) assay
-that quantified the total number of viral genome copies over time
-(\textbf{Figure 2B}).
+we harvested infected MDTC-RP19 cells (multiplicity of infection (MOI)
+of 100 genome copy numbers/cell) at 4-, 12-, 24-, and 72-hpi to capture
+all transcripts within a broad time window. Our paired-end RNA
+sequencing (RNA-seq) experiment generated an average of 107.1 million
+total reads of 149 bp length per time-point. These reads were
+concurrently mapped to both the virus (THEV) and host (\emph{Meleagris
+gallopavo}) genomes using the Hisat2 (25) reference-based aligner. A
+total of 18.1 million reads from all time-points mapped to the virus
+genome, providing comprehensive coverage and leaving no regions
+unmapped. The mapped reads to the virus genome increased significantly
+from a scant 432 reads at 4 hpi to 16.9 million reads at 72 hpi
+(\textbf{Table 1}, \textbf{Figure 2A}). From these mapped reads, we
+identified 2,457 unique THEV splice junctions across all time-points,
+with later time-points exhibiting significantly more sequence reads
+supporting the splice junctions than earlier time-points. For instance,
+all 13 unique junctions at 4 hpi had fewer than 10 supporting reads
+each, averaging only 2.8 reads per junction. In contrast, the 2374
+unique junctions at 72 hpi averaged 898.4 reads per junction, with some
+junctions reaching as high as 322,677 reads. The marked increase in
+splice junction and mapping reads to the THEV genome over time indicates
+an active infection and successful viral replication, which is
+corroborated by our quantitative PCR (qPCR) assay that quantified the
+total number of viral genome copies over time (\textbf{Figure 2B}).
 
@@
 (pTP) remains unchanged. Ad-pol (polymerase) is encoded downstream of
-pTP with secondary start codon (secSC) usage. The CP of TRXPT\_6
-slightly differs from TRXPT\_7 because a new STC resulting from the
-extra splice site forms a minimal truncation of the Ad-pol encoded from
-its secSC.
+pTP with secondary SC (secSC) usage. The CP of TRXPT\_6 slightly differs
+from TRXPT\_7 because a new STC resulting from the extra splice site
+forms a minimal truncation of the Ad-pol encoded from its secSC.
 
@@
 
-\textbf{Major Late Transcription Unit (MLTU) or MLP Region
-transcripts}\\
+\textbf{MLTU or MLP Region transcripts}\\
 The MLTU transcripts, dominant in the late phase of the AdV infectious
@@
 compound this challenge. Furthermore, in our case, no prior
-transcriptomic studies for THEV exist. Our approach combines standard
-RNA-seq analysis programs with custom analyses and experimentally
-validating all splice junctions with independent methods. The transcript
-map for THEV produced from our analysis is strikingly similar to that of
-the MAdVs.
+transcriptomic studies for THEV exist; hence, assembling the transcripts
+without any prior experimentally-derived annotation of THEV splicing
+using only short illumina reads proved difficult. Lastly, we had
+initially planned to sequence RNA from another time point (8 hpi);
+however, all the RNA samples from 8 hpi and one replicate sample from 12
+hpi got too degraded during the library preparation steps to be yield
+any useful data. We believe that these would have contributed to better
+insights into the temporal expression levels and splicing. Our approach
+combines standard RNA-seq analysis programs with custom analyses and
+experimentally validating all splice junctions with independent methods.
+The transcript map for THEV produced from our analysis is strikingly
+similar to that of the MAdVs.
 
 Our work provides the first insights into THEV splicing, revealing 34
-transcripts grouped into five transcription units (TUs). The general
-temporal gene expression regulation observed in MAdVs, with early
-regions peaking at earlier time points followed by MLTU predominance at
-later time points, seems to also apply to THEV. An unexpected
-observation is that the pileup of mapped reads to THEV seems
-consistently skewed over similar regions of the genome at all time
-points. Given the temporal regulation of AdVs gene expression, we
-anticipated distinct differences in read pileups over the genome at
-different time points, indicating the different stages of infection.
-This may be due to an unsynchronized infection, leading to transcripts
-overlapping the time points. Further research is required to determine
-the precise temporal regulation of THEV.
+transcripts grouped into five TUs. The general temporal gene expression
+regulation observed in MAdVs, with early regions peaking at earlier time
+points followed by MLTU predominance at later time points, seems to also
+apply to THEV. An unexpected observation is that the pileup of mapped
+reads to THEV seems consistently skewed over similar regions of the
+genome at all time points. Given the temporal regulation of AdVs gene
+expression, we anticipated distinct differences in read pileups over the
+genome at different time points, indicating the different stages of
+infection. This may be due to an unsynchronized infection, leading to
+transcripts overlapping the time points. Further research is required to
+determine the precise temporal regulation of THEV.
 
@@
 library preparation make it challenging to map the exact TSS, TTS, and
-PASs of assembled transcripts. Also, transcripts with significant
-overlaps may be assembled as a single, longer mRNA, since the short
-reads alone do not provide enough context for the transcript assembler
-(StringTie) to distinguish them. Our results show transcripts in the
+PASs of assembled transcripts. As AdVs make heavy use of alternative
+polyadenylation, short read RNA-seq is ill-equipped to discriminate mRNA
+variants of the same gene produced via alternative polyadenylation.
+Thus, shorter variants of alternatively polyadenylated mRNAs may
+potentially be incorporated into the longer variants during transcript
+assembly, significantly diminishing the diversity of mRNA in the
+transcriptome. Also, independent transcripts with significant overlaps
+may be assembled as a single, longer mRNA, since the short reads alone
+do not provide enough context for the transcript assembler (StringTie)
+to distinguish them. Such fusions may affect the transcript expression
+level estimations by inflating or deflating the expression levels of the
+transcripts involved, affecting the proper understanding of the temporal
+gene expression regulation and also the diversity of the transcriptome.
+Transcripts that have reads mistakenly fused with them would have
+inflated expression levels while those whose reads are counted elsewhere
+would show false lower expression levels. In our case, since we used
+other independent methods to validate the splice junctions, we believe
+these drawbacks to be minimized. Our results show transcripts in the
 same TU initiating or terminating in similar areas, but not at the exact
@@
 to some E3 mRNAs. Future studies using long read sequencing technologies
-will provide more precise mapping of the TSS and TTS and clarify the
-structures of the long MLTU transcripts.
+will provide more precise mapping of the TSS, TTS, and PASs and clarify
+the structures of the long MLTU transcripts.
 
@@
 steps. And secondly, recent studies (17, 18, 22) are still discovering
-novel mRNA variants for even the best studied MAdVs decades later.
+novel mRNA variants for even the best studied MAdVs decades later. These
+new potential proteins and isoforms significantly extend the repertoire
+of THEV gene products than predicted, adding a hefty number of proteins
+of undefined function to the previously predicted five (See
+\textbf{Figure 1}). These new potential proteins and isoforms of unknown
+functions may mediate or contribute to viral replication efficiency, or
+the immunosuppression associated with THEV. Hence, further studies of
+these potential proteins is urgently needed.
 
@@
 downstream AUG, under the direction of the shunting elements in the TPL,
-even if a start codon in a good Kozak sequence context is bypassed.
-Thus, predicting the protein(s) expressed from an AdV mRNA is uncertain
-as any one of the AUGs may be selected (10, 22). Almost all the THEV
+even if a SC in a good Kozak sequence context is bypassed. Thus,
+predicting the protein(s) expressed from an AdV mRNA is uncertain as any
+one of the AUGs may be selected (10, 22). Almost all the THEV
 transcripts in our data have the CP for several ORFs, some spanning as
@@
 limited due to its smaller genome size or future studies could uncover
-more variety not seen in our results. Being the first transcriptomic
-characterization of THEV, this work should serve as useful resource to
-future THEV gene expression and transcriptomic studies, especially,
-mapping the mRNA splice sites. \newpage
+more variety not seen in our results. We also note that although THEV
+genomic sequences show minimal differences between strains (12), the
+transcriptomes may have significant variations; hence, our results may
+vary from other THEV strains. Also, performing the study \emph{in vivo}
+or with primary turkey cells may show different results. The potential
+new proteins identified in our work adds to the number of proteins with
+undefined functions in THEV; these may have roles in viral replication
+efficiency, or the immunosuppression associated with THEV. Hence,
+further studies of these proteins and other predicted proteins of
+unknown function should be useful in elucidating THEV-induced
+immunosuppression. Being the first transcriptomic characterization of
+THEV, this work should serve as useful resource to future THEV gene
+expression and transcriptomic studies, especially, mapping the mRNA
+splice sites. More importantly, this work characterizing the splicing of
+THEV mRNAs will allow researchers to accurately clone any THEV gene(s)
+of interest to study its potential role in inducing immunosuppression or
+other functions.
+
+\newpage
 
@@
 copy number (GCN)/mL, similar to Mahshoub \emph{et al} (31) with
-modifications. Cells were infected in triplicate at a multiplicity of
-infection (MOI) of 100 GCN/cell, incubated at 41\textsuperscript{o}C for
-1 hour, and washed three times with phosphate buffered saline (PBS) to
-get rid of free virus particles. Triplicate samples were harvested at
-4-, 12-, 24-, and 72-hpi for total RNA extraction. The infection was
-repeated but samples in triplicate were harvested at 12-, 24-, 36-, 48-,
-and 72-hpi for PCR validation of novel splice sites. Still one more
-independent infection was done at time points ranging from 12 to 168-hpi
-for qPCR quantification of virus titers.
+modifications. Cells were infected in triplicate at MOI of 100 GCN/cell,
+incubated at 41\textsuperscript{o}C for 1 hour, and washed three times
+with phosphate buffered saline (PBS) to get rid of free virus particles.
+Triplicate samples were harvested at 4-, 12-, 24-, and 72-hpi for total
+RNA extraction. The infection was repeated but samples in triplicate
+were harvested at 12-, 24-, 36-, 48-, and 72-hpi for PCR validation of
+novel splice sites. Still one more independent infection was done at
+time points ranging from 12 to 168-hpi for qPCR quantification of virus
+titers.
 
@@
 (\textbf{Supplementary PCR methods}). Briefly, primers spanning a range
-of novel exon-exon boundaries for each specific transcript in a
-transcription unit (TU) were designed. Universal forward or reverse
-primers for each respective TU were designed and paired with primers
-binding specific positions in each transcript. Each forward primer
-contained a KpnI restriction site and each reverse primer, an XbaI site
-in the primer 5' ends. After first-strand cDNA synthesis of total RNA
-obtained from THEV infected MDTC-RP19 cells was done using SuperScript™
-IV First-Strand Synthesis System, the primers were used in a targeted
-PCR amplification, the products analyzed with agarose gel
-electrophoresis to confirm expected band sizes, cloned by traditional
-restriction enzyme method, and Sanger sequenced to validate these splice
-junctions at the sequence level. The total RNA was extracted as
-described above, including the DNase I digestion step. We included
-infected total RNA controls with no reverse transcriptase (no RT) during
-the cDNA synthesis step and the parent RNA were digested using RNase H
-after cDNA synthesis was complete to ensured that the bands obtained
-from the targeted PCR amplifications did not originate from the viral
-genomic DNA. As seen in the agarose gel images in \textbf{Supplementary
-PCR methods}, DNA bands were not found in the ``no RT'' controls,
-indicating that the DNA bands seen are of cDNA origin.
+of novel exon-exon boundaries for each specific transcript in a TU were
+designed. Universal forward or reverse primers for each respective TU
+were designed and paired with primers binding specific positions in each
+transcript. Each forward primer contained a KpnI restriction site and
+each reverse primer, an XbaI site in the primer 5' ends. After
+first-strand cDNA synthesis of total RNA obtained from THEV infected
+MDTC-RP19 cells was done using SuperScript™ IV First-Strand Synthesis
+System, the primers were used in a targeted PCR amplification, the
+products analyzed with agarose gel electrophoresis to confirm expected
+band sizes, cloned by traditional restriction enzyme method, and Sanger
+sequenced to validate these splice junctions at the sequence level. The
+total RNA was extracted as described above, including the DNase I
+digestion step. We included infected total RNA controls with no reverse
+transcriptase (no RT) during the cDNA synthesis step and the parent RNA
+were digested using RNase H after cDNA synthesis was complete to ensured
+that the bands obtained from the targeted PCR amplifications did not
+originate from the viral genomic DNA. As seen in the agarose gel images
+in \textbf{Supplementary PCR methods}, DNA bands were not found in the
+``no RT'' controls, indicating that the DNA bands seen are of cDNA
+origin.
 
@@
 Score) of 36. Trimmed reads were mapped simultaneously to the complete
-genomic sequence of avirulent turkey hemorrhagic enteritis virus
+genomic sequence of avirulent THEV
 (\url{https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/}) and
@@
 We thank the Office of Research Computing at Brigham Young University
-for granting us access to the high performance computing systems to
+for granting us access to the high-performance computing systems to
 perform the memory-intensive steps in the analysis pipeline of this
@@
 \centering
-\includegraphics{results/r/figures/thev_orf_map.png}
+\includegraphics{results/r/figures/figure1.png}
 \caption{\textbf{Figure 1. Predicted ORF map of THEV avirulent strain.}
@@
 predicted to be spliced and are shown as two exons connected with dashed
-lines. Shaded regions indicate regions containing ``genus-specific''
-genes (colored red). Genes colored in blue are ``genus-common''. The
-gene colored in light green is conserved in all but Atadenoviruses.
-Regions comprising the different transcription units are labelled at the
-bottom (E1, E2A, E2B, E3, E4, and IM); the unlabeled regions comprise
-the MLTU.}
+lines. Shaded regions indicate regions containing the five
+genus-specific genes of undefined functions (colored red). Genes colored
+in blue are ``genus-common''. The gene colored in light green is
+conserved in all but Atadenoviruses. Regions comprising the different
+TUs are labelled at the bottom (E1, E2A, E2B, E3, E4, and IM); the
+unlabeled regions comprise the MLTU.}
 \end{figure}
@@
 \centering
-\includegraphics{results/r/figures/fig_2.png}
+\includegraphics{results/r/figures/figure2.png}
 \caption{\textbf{Figure 2: Increasing levels of THEV over time. A) Per
@@
 forming this transcriptome (splicing map). Transcripts belonging to the
-same transcription unit (TU) are located in close proximity on the
-genome and are color coded and labeled in this figure as such. The
-organization of TUs in the THEV genome is unsurprisingly similar to
-MAdVs; however, the MAdV genome shows significantly more transcripts.
-The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark
-grey, E4 - green, MLTU - blue. Predicted ORFs are also indicated here,
-colored light grey. \textbf{B) THEV transcripts identified at given time
-points.} Transcripts are color coded as explained in \textbf{(A)}.}
+same TU are located in close proximity on the genome and are color coded
+and labeled in this figure as such. The organization of TUs in the THEV
+genome is unsurprisingly similar to MAdVs; however, the MAdV genome
+shows significantly more transcripts. The TUs are color coded: E1
+transcripts - red, E2 - black, E3 - dark grey, E4 - green, MLTU - blue.
+Predicted ORFs are also indicated here, colored light grey. \textbf{B)
+THEV transcripts identified at given time points.} Transcripts are color
+coded as explained in \textbf{(A)}.}
 \end{figure}
@@
 \centering
-\includegraphics{results/r/figures/figure_4a_d.png}
+\includegraphics{results/r/figures/figure4.png}
 \caption{\textbf{Figure 4: Changes in splicing and expression profile of
@@
 \centering
-\includegraphics{results/r/figures/figure_5a_d.png}
+\includegraphics{results/r/figures/figure5.png}
 \caption{\textbf{Figure 5: Changes in splice donor-acceptor nucleotides
@@
 \centering
-\includegraphics{results/r/figures/figure_6.png}
-\caption{\textbf{Figure 6: The splice map of the E1 transcription unit
-(TU).} Exons are depicted as boxes connected by introns (dotted lines).
-Transcripts from RNA-seq data are colored red, predicted ORFs are
-colored grey, and transcripts or ORFs discovered by other means are
-colored black. Each transcript or ORF is labelled with its name to the
-right. The start codon (SC) and stop codon (STC) of the 5'-most CDS of
-each transcript is indicated with the nucleotide position in brackets.
-The region of the virus is depicted at the bottom as a black line with
-labels of the nucleotide positions for reference. The table shows
-sequence reads covering the splice junctions with information about
-their validation status using cloning and Sanger sequencing.}
+\includegraphics{results/r/figures/figure6.png}
+\caption{\textbf{Figure 6: The splice map of the E1 TU.} Exons are
+depicted as boxes connected by introns (dotted lines). Transcripts from
+RNA-seq data are colored red, predicted ORFs are colored grey, and
+transcripts or ORFs discovered by other means are colored black. Each
+transcript or ORF is labelled with its name to the right. The SC and STC
+of the 5'-most CDS of each transcript is indicated with the nucleotide
+position in brackets. The region of the virus is depicted at the bottom
+as a black line with labels of the nucleotide positions for reference.
+The table shows sequence reads covering the splice junctions with
+information about their validation status using cloning and Sanger
+sequencing.}
 \end{figure}
@@
 \centering
-\includegraphics{results/r/figures/figure_7.png}
+\includegraphics{results/r/figures/figure7.png}
 \caption{\textbf{Figure 7: The splice map of the E2 and IM TUs.} Exons
@@
 \centering
-\includegraphics{results/r/figures/figure_8.png}
+\includegraphics{results/r/figures/figure8.png}
 \caption{\textbf{Figure 8: The splice map of the E3 TU.} Exons are
@@
 Transcripts discovered by other means are colored black. Each transcript
-or ORF is labelled with its name to the right. The start codon (SC) and
-stop codon (STC) of the 5'-most CDS of each transcript are indicated
-with the nucleotide position in brackets. Similarly, the secondary SC
-(secSC) and secondary STC (secSTC) are shown. The region of the virus is
-depicted at the bottom as a black line with labels of the nucleotide
-positions for reference. The table shows sequence reads covering the
-splice junctions with information about their validation status using
-cloning and Sanger sequencing.}
+or ORF is labelled with its name to the right. The SC and STC of the
+5'-most CDS of each transcript are indicated with the nucleotide
+position in brackets. Similarly, the secondary SC (secSC) and secondary
+STC (secSTC) are shown. The region of the virus is depicted at the
+bottom as a black line with labels of the nucleotide positions for
+reference. The table shows sequence reads covering the splice junctions
+with information about their validation status using cloning and Sanger
+sequencing.}
 \end{figure}
@@
 \centering
-\includegraphics{results/r/figures/figure_9.png}
+\includegraphics{results/r/figures/figure9.png}
 \caption{\textbf{Figure 9: The splice map of the E4 TU.} Exons are
@@
 from RNA-seq data is colored red and the predicted ORF, grey. The
-transcript and ORF are labelled with their names to the right. The start
-codon (SC) and stop codon (STC) of the 5'-most CDS are indicated with
-the nucleotide position in brackets. The region of the virus is depicted
-at the bottom as a black line with labels of the nucleotide positions
-for reference. The table shows sequence reads covering the splice
-junction with its validation status using cloning and Sanger
-sequencing.}
+transcript and ORF are labelled with their names to the right. The SC
+and STC of the 5'-most CDS are indicated with the nucleotide position in
+brackets. The region of the virus is depicted at the bottom as a black
+line with labels of the nucleotide positions for reference. The table
+shows sequence reads covering the splice junction with its validation
+status using cloning and Sanger sequencing.}
 \end{figure}
@@
 \centering
-\includegraphics{results/r/figures/figure_10.png}
+\includegraphics{results/r/figures/figure10.png}
 \caption{\textbf{Figure 10: The splice map of the MLTU.} Exons are
@@
 from our RNA-seq data are colored red and the predicted ORFs, grey. The
-transcripts and ORFs are labelled with their names to the right. The
-start codon (SC) and stop codon (STC) of the 5'-most CDS of each
-transcript is indicated with the nucleotide position in brackets.
-Similarly, the secondary SC (secSC) and secondary STC (secSTC) are
-shown. The region of the virus is depicted at the bottom as a black line
-with labels of the nucleotide positions for reference. The table shows
-sequence reads covering the splice junctions with information about
-their validation status using cloning and Sanger sequencing.}
+transcripts and ORFs are labelled with their names to the right. The SC
+and STC of the 5'-most CDS of each transcript is indicated with the
+nucleotide position in brackets. Similarly, the secondary SC (secSC) and
+secondary STC (secSTC) are shown. The region of the virus is depicted at
+the bottom as a black line with labels of the nucleotide positions for
+reference. The table shows sequence reads covering the splice junctions
+with information about their validation status using cloning and Sanger
+sequencing.}
 \end{figure}
